### 2018-11-12 manuscript/manuscript.tex
add fitting result

\documentclass[apj]{emulateapj}
\usepackage{times}
%\newcommand{\mdot}{M$_{\odot}$\,}
\usepackage{natbib}

\usepackage[backref,breaklinks,colorlinks,citecolor=cyan]{hyperref} 
%\setlength{\parindent}{0pt}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{bm}
%\usepackage{deluxetable}
\usepackage{multirow}
\usepackage{enumitem}
\shorttitle{TDLMC. l}
\shortauthors{X. Ding et al.}

\begin{document}

\def\lcdm{$\Lambda$CDM}
\def\hst{{\it HST}}
\def\efr{$R_{\mathrm{eff}}$}
\def\galfit{\sc Galfit}
\def\mbh{$\mathcal M_{\rm BH}$}
\def\lhost{$L_{\rm host}$}
\def\jcap{Journal of Cosmology and Astroparticle Physics}
\def\halpha{${\it H}\alpha$}
\def\hbeta{${\it H}\beta$}

\title{QSO decomposition}

\author{Xuheng Ding\altaffilmark{1, 2}, Tommaso Treu\altaffilmark{2}, Anowar J. Shajib\altaffilmark{2}, Dandan Xu\altaffilmark{3}, Geoff C.-F. Chen\altaffilmark{4},  Anupreeta More\altaffilmark{5},
}
\email{dxh@astro.ucla.edu}
% Dandan Xu, Giulia, Anupreeta, Chih-Fan, Daniel, Chris, Phil Marshall, Dominique,

\altaffiltext{1}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{2}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{3}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
\altaffiltext{4}{Department of Physics, University of California, Davis, CA 95616, USA}
\altaffiltext{5}{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
\altaffiltext{6}{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Strasse 1, D-85740 Garching, Germany}
\altaffiltext{7}{Exzellenzcluster Universe, Boltzmannstr. 2, 85748 Garching, Germany}
\altaffiltext{8}{Ludwig-Maximilians-Universit{\"a}t, Universit{\"a}ts-Sternwarte, Scheinerstr. 1, 81679 M{\"u}nchen, Germany}
\altaffiltext{9}{Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA}
\altaffiltext{10}{STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium}

\begin{abstract}
To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. 
\end{abstract}

\keywords{galaxies: active --- galaxies: evolution}

\section{Introduction}
\label{sec:introduction}
skeleton
\\
1. The ML relation and why understand its evolution is important.\\
2. To understand this evolution, it is important to trace to high redshift. So, why it is difficult.\\
3. Introduce reference. Woo's. SS13, Treu's, Park79. In the theory, DeGraf...\\
4. This work, we introduces samples till redshift 1.7.

\section{Observations and data reduction}
\label{sec:data}
In this section, we summarize the sample selection, observations, and data reduction of our sample.

\subsection{Sample selection}
%How the samples are selection.\\
%Where are they from?
%\\The redshift range? In a table?

We aim to study the relation between the BH masses (\mbh) and their host galaxy properties including luminosities (\lhost) stellar mass to redshift at $z>1$. For this propose, we focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS \citep{Civano2016}, (E)-CDFS-S \citep{Lehmer2005, Xue2011}, and SXDS \citep{Ueda2008} fields. We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$. The Near IR spectra of AGNs are available from the survey of Subaru's Fiber Multi-Object Spectrograph \citep[FMOS, ][]{Kimura2010, Schulze2018}, a near-infrared (0.9-1.8 $\mu m$) spectrograph have with 400 apertures. The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$ \citep{Greene2005, Matsuoka2013, Nobuta2012}.

Our final sample is composed of 36  AGNs; 32 of them are new systems \textcolor{red}{\bf (32+4?, the information of these four sample?)}. To compare with the samples in the literature, we adopt the samples from ... \textcolor{blue}{\bf The samples from H0licow7}
For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point. Table ? list all the samples.

\subsection{Observation and reduction}
\label{observation}
Introduce the QSO surface photometry\\
Introduce the AGN broad line Emission

\subsubsection{HST image for photometry}
The QSO surface photometry in IR Channel Filters.\\
The ACS data.
\subsubsection{AGN Emission line}
\label{sec:bh_mass}
The introduction of the BH inferred by the board emission line.

\section{Analysis}
\label{sec:Analysis}

\subsection{QSO image decomposition}
\subsubsection{PSF library}	
\label{sec:psf_library}
Introduce the PSF library

\subsubsection{Modeling method}
Introduce the lenstronomy. Model the PSF in each library.\\
Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result.

\subsubsection{host luminosity and stellar mass estimates}
k-correction by the galaxy model assumption\\
stellar mass \\

\subsection{BH masses}
Introduce different recipes as used in the paper.

\section{Results}
\label{sec:result}

\section{Summary}
\label{sec:sum}
We presented the study of the Mbh and host property's evolution to high redshift until 1.8.

\section*{Acknowledgments}
We thank Vivien Bonvin, Simon Birrer, Matthew W. Auger, Xiao-Lei Meng for useful suggestions and technical supports. X.D. acknowledges support by China Postdoctoral Science Foundation Funded Project; he is also grateful for Zong-Hong Zhu's support and funding. T.T. acknowledges support by the Packard Foundation in the form of a Packard Research Fellowship.

\bibliographystyle{apj.bst}
\bibliography{references}

%\appendix
%\section{If needed}
%\label{app:warp}

\end{document}

### 2018-11-27 manuscript/manuscript.tex
git push at first day after thanksgiving

@@
 \usepackage{enumitem}
-\shorttitle{TDLMC. l}
+\usepackage{amsmath}
+
+\shorttitle{ShortTitle}
 \shortauthors{X. Ding et al.}
@@
 \def\hbeta{${\it H}\beta$}
+\def\sersic{S\'ersic}
+\def\lenstronomy{{\sc Lenstronomy}}
+\def\Reff{{$R_{\mathrm{eff}}$}}
+\def\kms{km~s$^{\rm -1}$}
 
@@
 
-\author{Xuheng Ding\altaffilmark{1, 2}, Tommaso Treu\altaffilmark{2}, Anowar J. Shajib\altaffilmark{2}, Dandan Xu\altaffilmark{3}, Geoff C.-F. Chen\altaffilmark{4},  Anupreeta More\altaffilmark{5},
+\author{Xuheng Ding\altaffilmark{1, 2}, Tommaso Treu\altaffilmark{2}, John Silverman\altaffilmark{5}, Simon Birrer\altaffilmark{3}, Malte Schramm\altaffilmark{2}, Federica, Angelea
  }
@@
 \altaffiltext{5}{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
-\altaffiltext{6}{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Strasse 1, D-85740 Garching, Germany}
-\altaffiltext{7}{Exzellenzcluster Universe, Boltzmannstr. 2, 85748 Garching, Germany}
-\altaffiltext{8}{Ludwig-Maximilians-Universit{\"a}t, Universit{\"a}ts-Sternwarte, Scheinerstr. 1, 81679 M{\"u}nchen, Germany}
-\altaffiltext{9}{Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA}
-\altaffiltext{10}{STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium}
 
@@
 
-We aim to study the relation between the BH masses (\mbh) and their host galaxy properties including luminosities (\lhost) stellar mass to redshift at $z>1$.
+We aim to study the relation between the BH masses (\mbh) and their host galaxy properties including luminosities (\lhost) and stellar mass to redshift at $z>1$.
 For this propose, we focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS \citep{Civano2016}, (E)-CDFS-S \citep{Lehmer2005, Xue2011}, and SXDS \citep{Ueda2008} fields.
@@
 \textcolor{blue}{\bf The samples from H0licow7}
-For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point. Table ? list all the samples.
+For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point.
+Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.
 
@@
 \label{observation}
-Introduce the QSO surface photometry\\
-Introduce the AGN broad line Emission
+\subsubsection{HST image Observation}
+% The QSO surface photometry in IR Channel Filters.\\
+The high spatial resolution of the host image is required for the decomposition of the nuclear/host emission and the accurate estimate of the stellar of the host stellar mass.
+All the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as the HST program GO-15115, PI: John Silverman.
+We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets.
+This selection could ensure that the broad \halpha line ($4000\AA$) is not present in the bandpass which could contaminate the host emissions due to the broad wings of the PSF.
 
-\subsubsection{HST image for photometry}
-The QSO surface photometry in IR Channel Filters.\\
-The ACS data.
-\subsubsection{AGN Emission line}
+%Drizzling, background noise...
+For the new 32 AGN systems, each target one has six separate exposures with $\sim399s$ (i.e.
+total exposure time $\sim2394s$).
+The six exposures for each dither image were combined by the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter of 0.8 and a \texttt{gaussian} kernel.
+The other four AGNs in our sample have been observed with WFC3 serendipitously (2 in COSMOS from Kartaltepe (PI); PID: 13657).
+The noise level maps of the imaging data are a requirement in the study.
+The origin of the noise in each pixel is stems from the read noise, background noise and Poisson noise by the astronomical sources themselves.
+To take them into account, we measure the read noise and background noise level directly from the empty regions of the data.
+We calculate the effective exposure time in each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level.
+To accurately measure the photometry, we also adopt the {\sc photutils} to estimate the background light which could come from both the sky and the detector.
+
+%With 27/36 of our AGNs having rest-frame UV imaging with HST (COSMOS: F814W, PI: Nicholas Scoville; GEMS: F606W+F850LP), we are able to infer the host color and assess the contribution of both the young and old stellar population to the stellar mass budge \textcolor{blue}{citet Gallazzi+Bell 2009}.
+
+With 18/32 of our sample have rest-frame UV images by \textcolor{blue}{Scoville, et al. 2007} %arxiv: 0702359}.
+Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures.
+The final image is drizzled to 0\farcs{03} pixel scale.
+Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population to the stellar mass budge \textcolor{blue}{citet Gallazzi+Bell 2009} which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR).
+
+\subsubsection{AGN Emission Line}
 \label{sec:bh_mass}
-The introduction of the BH inferred by the board emission line.
+% The introduction of the BH inferred by the board emission line.
+The \mbh\ of type-1 AGNs can be inferred using the so-called virial method.
+The kinematics of the broad-line region trace the gravitational field of the central black hole, assuming the motion of the broad-line region (BLR) gas is virialised.
+In this scenario, the width of the emission-line provide the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size.
+The virial method builds on these reverberation mapping results and is directly calibrated to the \mbh.
+
+For our targets, the \halpha\ and \hbeta\ emission-line properties have been investigated by \citet{Schulze2018} using the multi-object spectrograph Subaru/FMOS.
+We referred to this paper for the details of continuum fitting and emission line modeling.
+Since the other compared AGNs in the literature used different calibrations of the virial method, we adopt the list of consistent recipes \textcolor{blue}{McGill et al.
+(2008), H0licow7} to cross-calibrate the \mbh\ for all the samples in order to avoid any systematic bias in Section~\ref{mbh}.
 
@@
 
-\subsection{QSO image decomposition}
+\subsection{Surface Photometry}
 \subsubsection{PSF library}    
 \label{sec:psf_library}
-Introduce the PSF library
+%Introduce the PSF library
+The knowledge of the PSF is crucial for this study, especially when the nuclear image is unresolved with light distributed as the point source.
+Moreover, the PSF in known to be vary according to their frame position and the intensity.
+Thus, we build a library of PSFs which we select the bright, isolated, unsaturated PSF stars across all the observed field.
+Thanks to the available multi-wavelength data \textcolor{blue}{(Laigle et al.
+2016)}, we are able to know the positions of stars nearby the QSO field and thus select a proper position and orientation of the HST frame to cover as much PSFs stars as possible.
 
-\subsubsection{Modeling method}
-Introduce the lenstronomy. Model the PSF in each library.\\
-Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result.
+We claim that, by building this library, the assumption is that the overall PSFs herein indicates all the possible PSF shape for each QSO.
+Since two filter, i.e.
+F140W and F125W, are selected for different samples, we selected 74 and 34 PSFs for the samples observed by F140W and F125W, respectively.
 
-\subsubsection{host luminosity and stellar mass estimates}
-k-correction by the galaxy model assumption\\
-stellar mass \\
+In the next subsection, we carry out the QSO decomposition using each PSF.
+We rank their performance based on the goodness so that the final inference of the host properties are weighted from the top-rank PSFs.
+
+\subsubsection{Surface Photometry modeling method}
+%Introduce the lenstronomy. Model the PSF in each library.\\
+%Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
+We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underling host galaxy.
+Following common practice, we assume the unresolved nuclear as a scaled PSF image, while the host galaxy as a \sersic\ profile.
+Note that the actual morphologies of the host galaxies could be even more complicated (e.g.
+bulge+disk).
+However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux given the high redshift range of our sample.
+We fit the objects which close to the QSO as the another \sersic\ model, to minimize the impact of their light.
+
+%Introduce Lenstronomy:
+We adopt the imaging modeling tool \lenstronomy\ \textcolor{blue}{(arXiv:1803.09746)}, to decompose the host and nuclear image.
+The \lenstronomy\ is a multi-purpose open-source gravitational lens modeling python package.
+The flexibility of this package enable us to turn off the lensing channel and carry out the decomposition.
+We have tested that the inference by \lenstronomy\ could have consistent result compared to {\sc Galfit}. \textcolor{red}{Will talk more in this part.}
+
+%Introduce the final inference using fitting:
+For each QSO system, the final host properties is inferred in several steps.
+First, we fit the flux distribution using each PSFs in the library.
+Given the QSO imaging data, PSF and noise level, we are able to infer the posterior distribution in the parameter space and optimize the best-fit parameters with minimized residuals.
+In this step, we infer the best-fit parameters for each PSFs in the library and the corresponding $\chi^2$ value\footnote{The \lenstronomy\ enable one to infer also the parametric confidence interval.
+However, given a fixed PSF image, the $1-\sigma$ region of each parameter are extremely narrow}.
+In the second step, we rank the performance of each PSF based on the reduced $\chi^2$ value and select the top-8 PSFs so as to weight for the inferred property.
+The weights for each PSF is calculated by:
+\begin{eqnarray}
+\label{eq:weights}
+w_i = exp \big(-\frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2\alpha \chi_{best} ^2} \big),
+\end{eqnarray} 
+where the $\alpha$ is the inflation parameter so that when $i=8$:
+\begin{eqnarray}
+\label{eq:alpha}
+\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2
+\end{eqnarray}
+
+%ECDFS-358 and CID206
+
+In figure, we demonstrate the optimized result of each system inferred by \lenstronomy. We also show the weighting process for an example system -- CID1174 in Table~\ref{tab:weight_CID1174}.
+
+%The inference of F814w data.
+Likewise, for the 18 systems with ACS/F184W images, we infer their host properties using the same approach.
+There are in total 174 star-like PSFs in the fitting library.
+We assumed the shape of the galaxy are consistent between the ACS and WFC3.
+Since the effects of dust extinction and contrast between the (blue) AGN and (red) host is more favorable in IR band, we believe the inferred information of the galaxy shape by IR band are superior to the one by UV band.
+Thus, while fitting the host flux at ACS band, we fix the \Reff\ and \sersic\ $n$ to the value by IR.
+
+We list all the inference of the host galaxy properties in the Table.
+
+%The overall fitting plot: 1. Host-R-n corner for f140w and f814w. 2. The histogram with different selection.
+
+\subsubsection{Host luminosity}
+\textcolor{red}{To be written:}
+1.K-correction to infer the rest frame R-band.\\
+* The galaxy template inferred by the joint fitting of the SED and the host flux ratio by us.
+
+Having inferred the value of the rest-frame R-band magnitude, the luminosity is derived by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.
+
+We summarized the homogenized R-band luminosities
+in Table?
 
 \subsection{BH masses}
-Introduce different recipes as used in the paper.
+\label{mbh}
+Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g.
+McLure 2002; Shen 2013)}.
+This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
+
+To avoid any systematic bias between our samples and the literature samples, we cross-calibrate the \mbh\ by adopting the self-consistent recipes as used by \textcolor{blue}{H0licow7, McGill et al.
+(2008)}.
+Overall, we adopt the following virial formalism for the \halpha\ and \hbeta\ emission line:
+
+\begin{eqnarray}
+\label{eq:Hb}
+\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.882+0.518\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
+&~+~& 2 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
+\end {eqnarray}
+
+and
+
+\begin{eqnarray}
+\label{eq:Ha}
+\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.459+0.55 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
+&~+~& 2 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right) , 
+\end {eqnarray}
+
+With the self-consistent cross-calibration, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
+For the system with both \halpha\ and \hbeta\ emission line information, we adopt the average \mbh\ value by these two.
+We summarized the inference of the \mbh\ together with the details on the emission line in Table.
 
@@
 \label{sec:result}
+\subsection{M-L relation}
+\subsubsection{Stellar mass estimates}
+stellar mass \\
+\subsection{M-M$_*$ relation}
 
@@
 \section*{Acknowledgments}
-We thank Vivien Bonvin, Simon Birrer, Matthew W.
-Auger, Xiao-Lei Meng for useful suggestions and technical supports.
+We thank the people who discuss with the paper.
 X.D.
@@
 
+\begin{deluxetable*}{llccc}
+\tablecolumns{5}
+\tablewidth{0pt}
+\tablecaption{The sample information for the 32 systems.} 
+\tablehead{ 
+\colhead{Object ID} &
+\colhead{$z$} & 
+\colhead{WFC3/Filter} &
+\colhead{$RA$}&
+\colhead{$DEC$}
+ \\ 
+\colhead{(1)} &
+\colhead{(2)} &
+\colhead{(3)} &
+\colhead{(4)} &
+\colhead{(5)} 
+} 
+\startdata
+%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
+%\\
+COSMOS-CID1174 & 1.552 & F140W$^*$ & 150.2789 & 1.9595\\
+COSMOS-CID1281 & 1.445 & ??? & 150.4160 & 2.5258\\
+COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088\\
+COSMOS-CID216 & 1.567 & F140W$^*$ & 149.7918 & 1.8729\\
+COSMOS-CID237 & 1.618 & F140W$^*$ & 149.9916 & 1.7243\\
+COSMOS-CID255 & 1.664 & ???$^*$ & 150.1017 & 1.8483\\
+COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452\\
+COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076\\
+COSMOS-CID452 & 1.407 & F125W$^*$ & 150.0045 & 2.2371\\
+COSMOS-CID454 & 1.478 & F140W$^*$ & 149.8681 & 2.3307\\
+COSMOS-CID50 & 1.239 & F125W$^*$ & 150.2080 & 2.0833\\
+COSMOS-CID543 & 1.301 & F125W$^*$ & 150.4519 & 2.1448\\
+COSMOS-CID597 & 1.272 & ???$^*$ & 150.5262 & 2.2449\\
+COSMOS-CID607 & 1.294 & F125W$^*$ & 150.6097 & 2.3231\\
+COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701\\
+COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275\\
+COSMOS-LID1538 & 1.527 & F140W$^*$ & 150.6215 & 2.1588\\
+COSMOS-LID360 & 1.579 & F140W$^*$ & 150.1251 & 2.8617\\
+COSMOS-XID2138 & 1.551 & F140W$^*$ & 149.7036 & 2.5781\\
+COSMOS-XID2202 & 1.516 & F140W$^*$ & 150.6530 & 1.9969\\
+COSMOS-XID2396 & 1.600 & F140W$^*$ & 149.4779 & 2.6425\\
+CDFS-1 & 1.630 & F140W$^*$ & 52.8990 & -27.8600\\ 
+CDFS-229 & 1.326 & F125W$^*$ & 53.0680 & -27.6580\\ 
+CDFS-321 & 1.570 & F140W$^*$ & 53.0486 & -27.6239\\ 
+CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940\\ 
+ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370\\ 
+SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498\\ 
+SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602\\ 
+SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334\\ 
+SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781\\ 
+SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864\\ 
+SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291\\ 
+\enddata
+\label{tab:objlist}
+\tablecomments{
+Column 1: Object field and ID.
+Column 2: Redshifts.
+Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.
+}
+\end{deluxetable*}
+
+\begin{deluxetable*}{ccccccc}
+\tablecolumns{7}
+\tablewidth{0pt}
+\tablecaption{The process of weighting for COSMOS-CID1174 } 
+\tablehead{ 
+\colhead{PSF rank} &
+\colhead{total $\chi ^2$} & 
+\colhead{weights $w_i$} &
+\colhead{host flux (counts)} &
+\colhead{host flux ratio}&
+\colhead{\Reff (arcsec)}&
+\colhead{\sersic\ $n$}
+ \\ 
+\colhead{(1)} &
+\colhead{(2)} &
+\colhead{(3)} &
+\colhead{(4)} &
+\colhead{(5)} &
+\colhead{(6)} &
+\colhead{(7)} 
+} 
+\startdata
+%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
+%\\
+1 & 8646.711 & 1.000 & 99.102 & 41.9\% & 0\farcs{}298 & 1.932 \\
+2 & 8816.947 & 0.849 & 76.740 & 33.0\% & 0\farcs{}365 & 1.102 \\
+3 & 9304.841 & 0.530 & 128.618 & 54.7\% & 0\farcs{}231 & 2.780 \\
+4 & 9652.575 & 0.379 & 187.498 & 79.0\% & 0\farcs{}116 & 6.175 \\
+5 & 10018.324 & 0.267 & 75.061 & 32.3\%& 0\farcs{}365 & 1.226 \\
+6 & 10087.456 & 0.249 & 79.835 & 34.3\% & 0\farcs{}358 & 1.195 \\
+7 & 10457.811 & 0.174 & 108.580 & 46.4\% & 0\farcs{}262 & 2.190 \\
+8 & 10721.421 & 0.135 & 63.994 & 27.8\% & 0\farcs{}406 & 0.720 \\
+\hline\\
+Weighted value & & & 103.534 $\pm$ 34.267 & 44.0\%$\pm$14.2\%& 0\farcs{}296$\pm$0\farcs{}079 & 2.173$\pm$1.500  \\
+\enddata
+\label{tab:weight_CID1174}
+\tablecomments{
+The detailed information of the weights for the inference of CID1174. The inflation value $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
+}
+\end{deluxetable*}
+
+\begin{deluxetable*}
+{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
+\tablecolumns{9}
+\tablewidth{0pt}
+\tablecaption{The sample information for the 32 systems.} 
+\tablehead
+{ 
+\colhead{Target ID}&
+  \multicolumn{5}{c}{Inference by WFC3}&
+  \multicolumn{3}{c}{Inference by ACS} \\
+  \cline{2-6}  \cline{7-9} \\
+\colhead{}& 
+\colhead{reduced $\chi ^2$}& \colhead{host flux ratio}& 
+\colhead{\Reff}& \colhead{\sersic\ $n$}& 
+\colhead{magnitude}&
+\colhead{reduced $\chi ^2$}& \colhead{host flux ratio}& \colhead{magnitude}\\
+\colhead{}& 
+\colhead{}& \colhead{}& 
+\colhead{($\arcsec$)}& \colhead{}& 
+\colhead{(AB system)}& \colhead{}& 
+\colhead{}& \colhead{(AB system)} \\
+\colhead{(1)}& 
+\colhead{(2)}& \colhead{(3)}& 
+\colhead{(4)}& \colhead{(5)}& 
+\colhead{(6)}& \colhead{(7)}& 
+\colhead{(8)}& \colhead{(9)}
+}
+\startdata 
+CID1174 & 2.324 & 44.0\%$\pm$14.2\% & 0.296$\pm$0.079 & 2.173$\pm$1.5 & $21.415\substack{+0.436 \\ -0.31}$ & 2.484074 & 11.7\%$\pm$1.4\% & $23.165\substack{+0.138 \\ -0.122}$\\
+CID1281 & ... & ... & ... & ... & ... & ... & ... & ...\\
+CID206 & 2.054 & 35.7\%$\pm$24.1\% & 0.282$\pm$0.151 & 3.191$\pm$2.51 & $21.81\substack{+1.247 \\ -0.565}$ & 1.903449 & 7.7\%$\pm$2.4\% & $23.671\substack{+0.403 \\ -0.293}$\\
+CID216 & 1.514 & 93.9\%$\pm$4.7\% & 0.251$\pm$0.063 & 6.159$\pm$1.205 & $21.51\substack{+0.052 \\ -0.049}$ & 1.424993 & 35.1\%$\pm$1.5\% & $23.446\substack{+0.053 \\ -0.051}$\\
+CID237 & 2.349 & 29.9\%$\pm$6.3\% & 0.872$\pm$0.172 & 4.736$\pm$1.701 & $21.279\substack{+0.26 \\ -0.209}$ & 2.353571 & 3.2\%$\pm$2.0\% & $23.718\substack{+1.037 \\ -0.52}$\\
+CID255 & ... & ... & ... & ... & ... & ... & ... & ...\\
+CID3242 & 2.751 & 46.1\%$\pm$12.7\% & 0.201$\pm$0.159 & 6.142$\pm$1.874 & $21.161\substack{+0.35 \\ -0.264}$ & 2.595594 & 4.8\%$\pm$1.3\% & $23.595\substack{+0.337 \\ -0.257}$\\
+CID3570 & 1.665 & 76.5\%$\pm$1.6\% & 0.698$\pm$0.007 & 0.728$\pm$0.054 & $21.164\substack{+0.021 \\ -0.021}$ & 1.331913 & 85.6\%$\pm$1.5\% & $22.971\substack{+0.012 \\ -0.012}$\\
+CID452 & 1.684 & 75.4\%$\pm$3.9\% & 0.365$\pm$0.015 & 1.402$\pm$0.175 & $21.176\substack{+0.063 \\ -0.06}$ & 1.451608 & 37.8\%$\pm$0.7\% & $22.732\substack{+0.022 \\ -0.022}$\\
+CID454 & 2.203 & 35.3\%$\pm$2.1\% & 0.391$\pm$0.013 & 0.602$\pm$0.092 & $21.212\substack{+0.067 \\ -0.063}$ & 1.29101 & 9.2\%$\pm$0.5\% & $23.352\substack{+0.058 \\ -0.055}$\\
+CID50 & 5.576 & 16.8\%$\pm$8.7\% & 0.152$\pm$0.102 & 3.371$\pm$2.154 & $20.915\substack{+0.796 \\ -0.454}$ & 4.940352 & 5.0\%$\pm$3.3\% & $22.504\substack{+1.145 \\ -0.545}$\\
+CID543 & 1.902 & 31.8\%$\pm$10.0\% & 0.1$\pm$0.0 & 0.505$\pm$0.333 & $21.95\substack{+0.405 \\ -0.294}$ & 1.434799 & 5.2\%$\pm$2.0\% & $23.765\substack{+0.534 \\ -0.357}$\\
+CID597 & ... & ... & ... & ... & ... & ... & ... & ...\\
+CID607 & 1.692 & 43.6\%$\pm$17.9\% & 0.206$\pm$0.087 & 3.418$\pm$1.097 & $21.189\substack{+0.575 \\ -0.374}$ & 2.590398 & 4.7\%$\pm$1.8\% & $23.566\substack{+0.511 \\ -0.346}$\\
+CID70 & 2.041 & 19.6\%$\pm$5.1\% & 0.426$\pm$0.101 & 3.543$\pm$1.154 & $21.865\substack{+0.323 \\ -0.248}$ & 2.36054 & 2.3\%$\pm$1.1\% & $24.625\substack{+0.677 \\ -0.414}$\\
+LID1273 & 1.697 & 53.3\%$\pm$9.1\% & 0.302$\pm$0.04 & 1.22$\pm$0.49 & $20.939\substack{+0.211 \\ -0.176}$ & 2.136592 & 6.4\%$\pm$0.8\% & $23.289\substack{+0.153 \\ -0.134}$\\
+LID1538 & 2.362 & 43.5\%$\pm$7.8\% & 0.177$\pm$0.042 & 2.819$\pm$0.475 & $21.251\substack{+0.221 \\ -0.184}$ & 2.172992 & 7.5\%$\pm$1.2\% & $23.088\substack{+0.189 \\ -0.161}$\\
+LID360 & 3.918 & 17.9\%$\pm$1.1\% & 0.629$\pm$0.018 & 0.672$\pm$0.04 & $21.483\substack{+0.068 \\ -0.064}$ & 4.913659 & 3.7\%$\pm$0.5\% & $23.254\substack{+0.172 \\ -0.149}$\\
+XID2138 & 1.597 & 39.7\%$\pm$6.1\% & 0.49$\pm$0.035 & 1.293$\pm$0.437 & $21.845\substack{+0.188 \\ -0.16}$ & 2.73139 & 5.0\%$\pm$1.3\% & $23.898\substack{+0.313 \\ -0.243}$\\
+XID2202 & 3.23 & 33.3\%$\pm$8.0\% & 0.1$\pm$0.001 & 3.957$\pm$1.017 & $21.16\substack{+0.302 \\ -0.236}$ & 3.851762 & 8.3\%$\pm$1.9\% & $22.592\substack{+0.286 \\ -0.226}$\\
+XID2396 & 3.669 & 23.9\%$\pm$10.5\% & 0.584$\pm$0.085 & 0.772$\pm$1.36 & $21.404\substack{+0.652 \\ -0.404}$ & 5.346128 & 2.3\%$\pm$0.5\% & $23.364\substack{+0.243 \\ -0.198}$\\
+CDFS-1 & 1.358 & 54.4\%$\pm$17.3\% & 0.158$\pm$0.077 & 4.574$\pm$1.387 & $22.656\substack{+0.414 \\ -0.299}$ & ... & ... & ...\\
+CDFS-229 & 4.329 & 17.6\%$\pm$2.1\% & 0.507$\pm$0.026 & 0.463$\pm$0.195 & $21.568\substack{+0.144 \\ -0.127}$ & ... & ... & ...\\
+CDFS-321 & 3.998 & 24.5\%$\pm$11.7\% & 0.378$\pm$0.122 & 2.26$\pm$2.007 & $20.337\substack{+0.703 \\ -0.423}$ & ... & ... & ...\\
+CDFS-724 & 1.355 & 34.7\%$\pm$14.6\% & 0.118$\pm$0.03 & 1.618$\pm$1.099 & $23.695\substack{+0.582 \\ -0.377}$ & ... & ... & ...\\
+ECDFS-358 & 2.012 & 56.4\%$\pm$13.5\% & 0.359$\pm$0.043 & 1.671$\pm$0.542 & $21.34\substack{+0.302 \\ -0.236}$ & ... & ... & ...\\
+SXDS-X1136 & 1.937 & 40.5\%$\pm$7.8\% & 0.101$\pm$0.003 & 1.986$\pm$0.483 & $21.921\substack{+0.231 \\ -0.19}$ & ... & ... & ...\\
+SXDS-X50 & 1.423 & 42.4\%$\pm$9.1\% & 0.184$\pm$0.041 & 1.755$\pm$0.655 & $21.943\substack{+0.266 \\ -0.214}$ & ... & ... & ...\\
+SXDS-X717 & 1.426 & 61.4\%$\pm$9.1\% & 0.264$\pm$0.066 & 5.58$\pm$1.421 & $21.759\substack{+0.176 \\ -0.151}$ & ... & ... & ...\\
+SXDS-X735 & 2.203 & 32.4\%$\pm$8.5\% & 0.22$\pm$0.057 & 2.027$\pm$1.012 & $20.919\substack{+0.333 \\ -0.254}$ & ... & ... & ...\\
+SXDS-X763 & 2.376 & 6.0\%$\pm$4.0\% & 0.694$\pm$0.532 & 2.394$\pm$0.796 & $24.134\substack{+1.172 \\ -0.55}$ & ... & ... & ...\\
+SXDS-X969 & 1.613 & 29.0\%$\pm$11.7\% & 0.115$\pm$0.026 & 2.149$\pm$1.147 & $21.594\substack{+0.553 \\ -0.365}$ & ... & ... & ...\\
+\enddata
+\label{tab:result_sersic}
+\tablecomments{
+Column 1: Object field and ID.
+Column 2: Redshifts.
+Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.
+}
+\end{deluxetable*}
+
+\begin{deluxetable*}
+{@{\extracolsep{4pt}}lcccccc}   % need for the gap between the clines.
+\tablecolumns{7}
+\tablewidth{0pt}
+\tablecaption{The inference of the \mbh\ for the 32 systems.} 
+\tablehead
+{ 
+\colhead{Target ID}&
+  \multicolumn{3}{c}{using emission line \halpha}&
+  \multicolumn{3}{c}{using emission line \hbeta} \\
+  \cline{2-4}  \cline{5-7} \\
+\colhead{}& 
+\colhead{FWHM}& \colhead{$\lambda \rm L _{H\alpha}$}& \colhead{\mbh}&
+\colhead{FWHM(5100)}& \colhead{$\lambda \rm L _{\lambda5100}$}& \colhead{\mbh}\\
+\colhead{}& 
+\colhead{(\kms)}& \colhead{($10^{42}{\rm erg~s^{-1}}$)}& 
+\colhead{(M$_{\odot}$)}& \colhead{(\kms)}& 
+\colhead{($10^{44}{\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
+\colhead{(1)}& 
+\colhead{(2)}& \colhead{(3)}& 
+\colhead{(4)}& \colhead{(5)}& 
+\colhead{(6)}&\colhead{(7)}
+}
+\startdata 
+CID1174 & 1906.3037 & 43.43237 & 7.807 & 5898.264 & 44.76243 & 8.818 \\
+CID1281 & 1619.4891 & 43.23945 & 7.559 & ... & ... & ... \\
+CID206 & 3333.5527 & 43.4776 & 8.317 & ... & ... & ... \\
+CID216 & 2229.5232 & 42.84509 & 7.62 & ... & ... & ... \\
+CID237 & 2112.3306 & 43.85546 & 8.129 & ... & ... & ... \\
+CID255 & 1932.0933 & 43.9924 & 8.127 & 3709.241 & 45.37122 & 8.731 \\
+CID3242 & 2543.2202 & 43.83323 & 8.278 & 3774.503 & 45.09891 & 8.605 \\
+CID3570 & 1958.8551 & 43.16374 & 7.683 & ... & ... & ... \\
+CID452 & 3457.8801 & 42.92298 & 8.044 & 3127.3306 & 44.63353 & 8.201 \\
+CID454 & 2824.2693 & 43.34466 & 8.1 & ... & ... & ... \\
+CID50 & 2339.9104 & 43.93786 & 8.263 & 1938.5676 & 45.32766 & 8.145 \\
+CID543 & 2188.8447 & 43.57404 & 8.005 & ... & ... & ... \\
+CID597 & 1656.3296 & 43.32955 & 7.629 & ... & ... & ... \\
+CID607 & 3009.1816 & 43.67079 & 8.335 & 4241.526 & 44.78209 & 8.542 \\
+CID70 & 2480.4058 & 43.50531 & 8.076 & 3981.8574 & 45.1582 & 8.682 \\
+LID1273 & 3223.8484 & 43.61001 & 8.361 & ... & ... & ... \\
+LID1538 & 2941.422 & 43.59594 & 8.274 & ... & ... & ... \\
+LID360 & 2481.7253 & 43.88091 & 8.283 & 2868.8992 & 45.08676 & 8.36 \\
+XID2138 & 3185.8613 & 43.6148 & 8.354 & 2944.7766 & 44.80782 & 8.239 \\
+XID2202 & 2973.2378 & 43.56249 & 8.265 & ... & ... & ... \\
+XID2396 & 2271.2617 & 44.06196 & 8.306 & 2657.8386 & 45.50467 & 8.51 \\
+CDFS-1 & ... & ... & ... & ... & ... & ... \\
+CDFS-229 & ... & ... & ... & ... & ... & ... \\
+CDFS-321 & 2441.93 & 43.92714 & 8.294 & ... & ... & ... \\
+CDFS-724 & ... & ... & ... & ... & ... & ... \\
+ECDFS-358 & 2237.2314 & 43.39674 & 7.927 & ... & ... & ... \\
+SXDS-X1136 & 2759.8953 & 43.43305 & 8.129 & 6761.222 & 44.71429 & 8.912 \\
+SXDS-X50 & 1816.672 & 43.421 & 7.759 & ... & ... & ... \\
+SXDS-X717 & 2930.7417 & 43.04988 & 7.97 & ... & ... & ... \\
+SXDS-X735 & 2702.0962 & 43.69804 & 8.256 & 3519.6052 & 45.07463 & 8.532 \\
+SXDS-X763 & 2961.1743 & 43.57321 & 8.267 & 4508.5146 & 44.51285 & 8.456 \\
+SXDS-X969 & 2296.0566 & 43.50066 & 8.006 & 1695.7146 & 45.05337 & 7.886 \\
+\enddata
+\label{tab:result_sersic}
+\tablecomments{
+Column 1: Object field and ID.
+Column 2: Redshifts.
+Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.
+}
+\end{deluxetable*}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID206_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID216_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID237_SB_profile.pdf}
+\caption{\label{fig:ML} WFC3 F110W images for 12 objects.
+In each row, observed data (first column), best-fit models (second column), and residuals (third column) are presented with the object name.
+All images are $10.8\arcsec\times10.8\arcsec$ in size and
+ displayed with an inverted asinh stretch.
+	    The fourth column shows the corresponding one-dimensional surface brightness profiles.
+In each top panel, the profiles measured from the data (open circles), the best-fit model (black solid line), and the sub-components of the model for bulge (blue solid line), disk (green solid line), AGN (red solid line) are shown.
+Residuals (gray circles), the difference of the profiles between the data and the best-fit model, are presented in each bottom panel.
+Note that the one-dimensional surface brightness profiles are shown for illustration purposes only, the actual fitting made use of the full two-dimensional images.}
+}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID3242_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID3570_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID452_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID454_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID50_SB_profile.pdf}
+}
+\figurenum{1}
+\caption{\label{fig:ML} Continued.}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID543_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID607_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID70_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2138_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2202_SB_profile.pdf}
+}
+\figurenum{1}
+\caption{\label{fig:ML} Continued.}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2396_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_LID1273_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_LID1538_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_LID360_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X1136_SB_profile.pdf}
+}
+\figurenum{1}
+\caption{\label{fig:ML} Continued.}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X50_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X717_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X735_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X763_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X969_SB_profile.pdf}
+}
+\figurenum{1}
+\caption{\label{fig:ML} Continued.}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-1_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-229_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-321_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-724_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_ECDFS-358_SB_profile.pdf}
+}
+\figurenum{1}
+\caption{\label{fig:ML} Continued.}
+\end{figure*}
+
 %\appendix

### 2018-11-27 analysis_ACS/overall_fit_result.py

@@ -25,7 +25,7 @@ import pickle
 ratio_results, Re_results, n_results, total_flux_results, host_amp_results = [], [], [], [], []
 chisq_list, inf_list, best_PSF_id = [],[], []
 flux_dict, FWHM_dict, locs_dict, filter_dict, id_stars_dict=pickle.load(open('PSFs_lib_dict','rb'))
-folder = "fit_result_each_fix"
+folder = "fit_result_each_fix" #"fit_result_each_fix" or "fit_result_each"
 
 for j in range(len(ID)):
     f = open("{0}/{1}/each_PSF_fit_qso.txt".format(ID[j],folder),"r")
@@ -147,7 +147,7 @@ for i in range(len(ID)):
     mag_max =-2.5*log10(amp_max) + zp
 #    print "mag for", ID[i], "{0}~{1}~{2}".format(round(mag_min,3),round(mag,3),round(mag_max,3))
     fit_mag.append(mag)
-    fit_mag_lh.append([mag_min-mag, mag-mag_max])
+    fit_mag_lh.append([mag-mag_max, mag_min-mag])
 
 fig, ax = plt.subplots(figsize=(15,9))
 for i in range(len(ID)):

### 2018-11-27 analysis_Astrodrz/CID1174/analysis/best_fit_plot_for_paper.py

@@ -1,0 +1,159 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Mar 29 20:17:41 2018
+
+@author: Dartoon
+
+On the analysis of xxx
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pylab as plt
+import glob
+import sys
+sys.path.insert(0,'../../../py_tools')
+from psfs_average import psf_ave
+from flux_profile import QSO_psfs_compare, profiles_compare
+from matplotlib.colors import LogNorm
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-2]
+
+from filter_info import filt_info
+filt = filt_info[ID]
+
+import re
+f = open("fit_result_each/each_PSF_fit_qso.txt","r")
+string = f.read()
+Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+Chisq = [float(i) for i in Chisq]
+sort_Chisq = np.argsort(np.asarray(Chisq))
+print "best fit PSF ID:", sort_Chisq[0]
+psf_id = sort_Chisq[0]
+
+# =============================================================================
+# Read PSF and QSO image
+# =============================================================================
+QSO_bkg_value= 0.
+QSO_im = pyfits.getdata('{0}_cutout.fits'.format(ID)) - QSO_bkg_value
+QSO_msk = pyfits.getdata('{0}_msk.fits'.format(ID))
+frame_size = 61
+#frame = '{0}'.format(frame_size)
+QSO_fm = len(QSO_im)
+ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
+        
+import pickle
+PSFs_dict = {}
+QSOs_dict = {}
+for key in filt_info.keys():
+    PSFs, QSOs=pickle.load(open('../../{0}/analysis/{0}_PSFs_QSO'.format(key),'rb'))
+    PSFs_dict.update({'{0}'.format(key):PSFs})
+    QSOs_dict.update({'{0}'.format(key):QSOs})
+
+PSF_list = []
+PSF_id = []
+filter_list = []
+for key in PSFs_dict.keys():
+    if filt_info[key] == filt:
+        psfs_dict = PSFs_dict[key]
+        psfs = [psfs_dict[i] for i in range(len(psfs_dict))]
+        PSF_list += psfs
+        name_id = [key+"_"+str(i) for i in range(len(psfs_dict))]
+        PSF_id = PSF_id + name_id
[…]

### 2018-11-27 analysis_Astrodrz/CID206/analysis/best_fit_plot_for_paper.py

@@ -1,0 +1,166 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Mar 29 20:17:41 2018
+
+@author: Dartoon
+
+On the analysis of xxx
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pylab as plt
+import glob
+import sys
+sys.path.insert(0,'../../../py_tools')
+from psfs_average import psf_ave
+from flux_profile import QSO_psfs_compare, profiles_compare
+from matplotlib.colors import LogNorm
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-2]
+
+from filter_info import filt_info
+filt = filt_info[ID]
+
+import re
+f = open("fit_result_each/each_PSF_fit_qso.txt","r")
+string = f.read()
+Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+Chisq = [float(i) for i in Chisq]
+sort_Chisq = np.argsort(np.asarray(Chisq))
+print "best fit PSF ID:", sort_Chisq[0]
+psf_id = sort_Chisq[0]
+
+# =============================================================================
+# Read PSF and QSO image
+# =============================================================================
+QSO_bkg_value= 0.
+QSO_im = pyfits.getdata('{0}_cutout.fits'.format(ID)) - QSO_bkg_value
+QSO_msk = pyfits.getdata('{0}_msk.fits'.format(ID))
+frame_size = 61
+#frame = '{0}'.format(frame_size)
+QSO_fm = len(QSO_im)
+ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
+        
+import pickle
+PSFs_dict = {}
+QSOs_dict = {}
+for key in filt_info.keys():
+    PSFs, QSOs=pickle.load(open('../../{0}/analysis/{0}_PSFs_QSO'.format(key),'rb'))
+    PSFs_dict.update({'{0}'.format(key):PSFs})
+    QSOs_dict.update({'{0}'.format(key):QSOs})
+
+PSF_list = []
+PSF_id = []
+filter_list = []
+for key in PSFs_dict.keys():
+    if filt_info[key] == filt:
+        psfs_dict = PSFs_dict[key]
+        psfs = [psfs_dict[i] for i in range(len(psfs_dict))]
+        PSF_list += psfs
+        name_id = [key+"_"+str(i) for i in range(len(psfs_dict))]
[…]

### 2018-11-27 analysis_Astrodrz/CID237/analysis/best_fit_plot_for_paper.py

@@ -1,0 +1,167 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Mar 29 20:17:41 2018
+
+@author: Dartoon
+
+On the analysis of xxx
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pylab as plt
+import glob
+import sys
+sys.path.insert(0,'../../../py_tools')
+from psfs_average import psf_ave
+from flux_profile import QSO_psfs_compare, profiles_compare
+from matplotlib.colors import LogNorm
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-2]
+
+from filter_info import filt_info
+filt = filt_info[ID]
+
+import re
+f = open("fit_result_each/each_PSF_fit_qso.txt","r")
+string = f.read()
+Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+Chisq = [float(i) for i in Chisq]
+sort_Chisq = np.argsort(np.asarray(Chisq))
+print "best fit PSF ID:", sort_Chisq[0]
+psf_id = sort_Chisq[0]
+
+# =============================================================================
+# Read PSF and QSO image
+# =============================================================================
+QSO_bkg_value= 0.
+QSO_im = pyfits.getdata('{0}_cutout.fits'.format(ID)) - QSO_bkg_value
+QSO_msk = pyfits.getdata('{0}_msk.fits'.format(ID))
+frame_size = 61
+#frame = '{0}'.format(frame_size)
+QSO_fm = len(QSO_im)
+ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
+        
+import pickle
+PSFs_dict = {}
+QSOs_dict = {}
+for key in filt_info.keys():
+    PSFs, QSOs=pickle.load(open('../../{0}/analysis/{0}_PSFs_QSO'.format(key),'rb'))
+    PSFs_dict.update({'{0}'.format(key):PSFs})
+    QSOs_dict.update({'{0}'.format(key):QSOs})
+
+PSF_list = []
+PSF_id = []
+filter_list = []
+for key in PSFs_dict.keys():
+    if filt_info[key] == filt:
+        psfs_dict = PSFs_dict[key]
+        psfs = [psfs_dict[i] for i in range(len(psfs_dict))]
+        PSF_list += psfs
+        name_id = [key+"_"+str(i) for i in range(len(psfs_dict))]
[…]

### 2018-11-27 analysis_Astrodrz/CID454/analysis/best_fit_plot_for_paper.py

@@ -1,0 +1,159 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Mar 29 20:17:41 2018
+
+@author: Dartoon
+
+On the analysis of xxx
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pylab as plt
+import glob
+import sys
+sys.path.insert(0,'../../../py_tools')
+from psfs_average import psf_ave
+from flux_profile import QSO_psfs_compare, profiles_compare
+from matplotlib.colors import LogNorm
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-2]
+
+from filter_info import filt_info
+filt = filt_info[ID]
+
+import re
+f = open("fit_result_each/each_PSF_fit_qso.txt","r")
+string = f.read()
+Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+Chisq = [float(i) for i in Chisq]
+sort_Chisq = np.argsort(np.asarray(Chisq))
+print "best fit PSF ID:", sort_Chisq[0]
+psf_id = sort_Chisq[0]
+
+# =============================================================================
+# Read PSF and QSO image
+# =============================================================================
+QSO_bkg_value= 0.
+QSO_im = pyfits.getdata('{0}_cutout.fits'.format(ID)) - QSO_bkg_value
+QSO_msk = pyfits.getdata('{0}_msk.fits'.format(ID))
+frame_size = 61
+#frame = '{0}'.format(frame_size)
+QSO_fm = len(QSO_im)
+ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
+        
+import pickle
+PSFs_dict = {}
+QSOs_dict = {}
+for key in filt_info.keys():
+    PSFs, QSOs=pickle.load(open('../../{0}/analysis/{0}_PSFs_QSO'.format(key),'rb'))
+    PSFs_dict.update({'{0}'.format(key):PSFs})
+    QSOs_dict.update({'{0}'.format(key):QSOs})
+
+PSF_list = []
+PSF_id = []
+filter_list = []
+for key in PSFs_dict.keys():
+    if filt_info[key] == filt:
+        psfs_dict = PSFs_dict[key]
+        psfs = [psfs_dict[i] for i in range(len(psfs_dict))]
+        PSF_list += psfs
+        name_id = [key+"_"+str(i) for i in range(len(psfs_dict))]
+        PSF_id = PSF_id + name_id
[…]

### 2018-11-27 analysis_Astrodrz/CID607/analysis/best_fit_plot_for_paper.py

@@ -1,0 +1,159 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Mar 29 20:17:41 2018
+
+@author: Dartoon
+
+On the analysis of xxx
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pylab as plt
+import glob
+import sys
+sys.path.insert(0,'../../../py_tools')
+from psfs_average import psf_ave
+from flux_profile import QSO_psfs_compare, profiles_compare
+from matplotlib.colors import LogNorm
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-2]
+
+from filter_info import filt_info
+filt = filt_info[ID]
+
+import re
+f = open("fit_result_each/each_PSF_fit_qso.txt","r")
+string = f.read()
+Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+Chisq = [float(i) for i in Chisq]
+sort_Chisq = np.argsort(np.asarray(Chisq))
+print "best fit PSF ID:", sort_Chisq[0]
+psf_id = sort_Chisq[0]
+
+# =============================================================================
+# Read PSF and QSO image
+# =============================================================================
+QSO_bkg_value= 0.
+QSO_im = pyfits.getdata('{0}_cutout.fits'.format(ID)) - QSO_bkg_value
+QSO_msk = pyfits.getdata('{0}_msk.fits'.format(ID))
+frame_size = 101
+#frame = '{0}'.format(frame_size)
+QSO_fm = len(QSO_im)
+ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
+        
+import pickle
+PSFs_dict = {}
+QSOs_dict = {}
+for key in filt_info.keys():
+    PSFs, QSOs=pickle.load(open('../../{0}/analysis/{0}_PSFs_QSO'.format(key),'rb'))
+    PSFs_dict.update({'{0}'.format(key):PSFs})
+    QSOs_dict.update({'{0}'.format(key):QSOs})
+
+PSF_list = []
+PSF_id = []
+filter_list = []
+for key in PSFs_dict.keys():
+    if filt_info[key] == filt:
+        psfs_dict = PSFs_dict[key]
+        psfs = [psfs_dict[i] for i in range(len(psfs_dict))]
+        PSF_list += psfs
+        name_id = [key+"_"+str(i) for i in range(len(psfs_dict))]
+        PSF_id = PSF_id + name_id
[…]

### 2018-11-27 analysis_Astrodrz/LID1273/analysis/best_fit_plot_for_paper.py

@@ -1,0 +1,160 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Mar 29 20:17:41 2018
+
+@author: Dartoon
+
+On the analysis of xxx
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pylab as plt
+import glob
+import sys
+sys.path.insert(0,'../../../py_tools')
+from psfs_average import psf_ave
+from flux_profile import QSO_psfs_compare, profiles_compare
+from matplotlib.colors import LogNorm
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-2]
+
+from filter_info import filt_info
+filt = filt_info[ID]
+
+import re
+f = open("fit_result_each/each_PSF_fit_qso.txt","r")
+string = f.read()
+Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+Chisq = [float(i) for i in Chisq]
+sort_Chisq = np.argsort(np.asarray(Chisq))
+print "best fit PSF ID:", sort_Chisq[0]
+psf_id = sort_Chisq[0]
+
+
+# =============================================================================
+# Read PSF and QSO image
+# =============================================================================
+QSO_bkg_value= 0.
+QSO_im = pyfits.getdata('{0}_cutout.fits'.format(ID)) - QSO_bkg_value
+QSO_msk = pyfits.getdata('{0}_msk.fits'.format(ID))
+frame_size = 101
+#frame = '{0}'.format(frame_size)
+QSO_fm = len(QSO_im)
+ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
+        
+import pickle
+PSFs_dict = {}
+QSOs_dict = {}
+for key in filt_info.keys():
+    PSFs, QSOs=pickle.load(open('../../{0}/analysis/{0}_PSFs_QSO'.format(key),'rb'))
+    PSFs_dict.update({'{0}'.format(key):PSFs})
+    QSOs_dict.update({'{0}'.format(key):QSOs})
+
+PSF_list = []
+PSF_id = []
+filter_list = []
+for key in PSFs_dict.keys():
+    if filt_info[key] == filt:
+        psfs_dict = PSFs_dict[key]
+        psfs = [psfs_dict[i] for i in range(len(psfs_dict))]
+        PSF_list += psfs
+        name_id = [key+"_"+str(i) for i in range(len(psfs_dict))]
+        PSF_id = PSF_id + name_id
[…]

### 2018-11-27 analysis_Astrodrz/SXDS-X717/analysis/best_fit_plot_for_paper.py

@@ -1,0 +1,159 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Mar 29 20:17:41 2018
+
+@author: Dartoon
+
+On the analysis of xxx
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pylab as plt
+import glob
+import sys
+sys.path.insert(0,'../../../py_tools')
+from psfs_average import psf_ave
+from flux_profile import QSO_psfs_compare, profiles_compare
+from matplotlib.colors import LogNorm
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-2]
+
+from filter_info import filt_info
+filt = filt_info[ID]
+
+import re
+f = open("fit_result_each/each_PSF_fit_qso.txt","r")
+string = f.read()
+Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+Chisq = [float(i) for i in Chisq]
+sort_Chisq = np.argsort(np.asarray(Chisq))
+print "best fit PSF ID:", sort_Chisq[0]
+psf_id = sort_Chisq[0]
+
+# =============================================================================
+# Read PSF and QSO image
+# =============================================================================
+QSO_bkg_value= 0.
+QSO_im = pyfits.getdata('{0}_cutout.fits'.format(ID)) - QSO_bkg_value
+QSO_msk = pyfits.getdata('{0}_msk.fits'.format(ID))
+frame_size = 61
+#frame = '{0}'.format(frame_size)
+QSO_fm = len(QSO_im)
+ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
+        
+import pickle
+PSFs_dict = {}
+QSOs_dict = {}
+for key in filt_info.keys():
+    PSFs, QSOs=pickle.load(open('../../{0}/analysis/{0}_PSFs_QSO'.format(key),'rb'))
+    PSFs_dict.update({'{0}'.format(key):PSFs})
+    QSOs_dict.update({'{0}'.format(key):QSOs})
+
+PSF_list = []
+PSF_id = []
+filter_list = []
+for key in PSFs_dict.keys():
+    if filt_info[key] == filt:
+        psfs_dict = PSFs_dict[key]
+        psfs = [psfs_dict[i] for i in range(len(psfs_dict))]
+        PSF_list += psfs
+        name_id = [key+"_"+str(i) for i in range(len(psfs_dict))]
+        PSF_id = PSF_id + name_id
[…]

### 2018-11-27 analysis_Astrodrz/SXDS-X735/analysis/best_fit_plot_for_paper.py

@@ -1,0 +1,160 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Mar 29 20:17:41 2018
+
+@author: Dartoon
+
+On the analysis of xxx
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pylab as plt
+import glob
+import sys
+sys.path.insert(0,'../../../py_tools')
+from psfs_average import psf_ave
+from flux_profile import QSO_psfs_compare, profiles_compare
+from matplotlib.colors import LogNorm
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-2]
+
+from filter_info import filt_info
+filt = filt_info[ID]
+
+import re
+f = open("fit_result_each/each_PSF_fit_qso.txt","r")
+string = f.read()
+Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+Chisq = [float(i) for i in Chisq]
+sort_Chisq = np.argsort(np.asarray(Chisq))
+print "best fit PSF ID:", sort_Chisq[0]
+psf_id = sort_Chisq[0]
+
+
+# =============================================================================
+# Read PSF and QSO image
+# =============================================================================
+QSO_bkg_value= 0.
+QSO_im = pyfits.getdata('{0}_cutout.fits'.format(ID)) - QSO_bkg_value
+QSO_msk = pyfits.getdata('{0}_msk.fits'.format(ID))
+frame_size = 61
+#frame = '{0}'.format(frame_size)
+QSO_fm = len(QSO_im)
+ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
+        
+import pickle
+PSFs_dict = {}
+QSOs_dict = {}
+for key in filt_info.keys():
+    PSFs, QSOs=pickle.load(open('../../{0}/analysis/{0}_PSFs_QSO'.format(key),'rb'))
+    PSFs_dict.update({'{0}'.format(key):PSFs})
+    QSOs_dict.update({'{0}'.format(key):QSOs})
+
+PSF_list = []
+PSF_id = []
+filter_list = []
+for key in PSFs_dict.keys():
+    if filt_info[key] == filt:
+        psfs_dict = PSFs_dict[key]
+        psfs = [psfs_dict[i] for i in range(len(psfs_dict))]
+        PSF_list += psfs
+        name_id = [key+"_"+str(i) for i in range(len(psfs_dict))]
+        PSF_id = PSF_id + name_id
[…]

### 2018-11-27 analysis_Astrodrz/SXDS-X969/analysis/best_fit_plot_for_paper.py

@@ -1,0 +1,160 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Mar 29 20:17:41 2018
+
+@author: Dartoon
+
+On the analysis of xxx
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pylab as plt
+import glob
+import sys
+sys.path.insert(0,'../../../py_tools')
+from psfs_average import psf_ave
+from flux_profile import QSO_psfs_compare, profiles_compare
+from matplotlib.colors import LogNorm
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-2]
+
+from filter_info import filt_info
+filt = filt_info[ID]
+
+import re
+f = open("fit_result_each/each_PSF_fit_qso.txt","r")
+string = f.read()
+Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+Chisq = [float(i) for i in Chisq]
+sort_Chisq = np.argsort(np.asarray(Chisq))
+print "best fit PSF ID:", sort_Chisq[0]
+psf_id = sort_Chisq[0]
+
+
+# =============================================================================
+# Read PSF and QSO image
+# =============================================================================
+QSO_bkg_value= 0.
+QSO_im = pyfits.getdata('{0}_cutout.fits'.format(ID)) - QSO_bkg_value
+QSO_msk = pyfits.getdata('{0}_msk.fits'.format(ID))
+frame_size = 61
+#frame = '{0}'.format(frame_size)
+QSO_fm = len(QSO_im)
+ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
+        
+import pickle
+PSFs_dict = {}
+QSOs_dict = {}
+for key in filt_info.keys():
+    PSFs, QSOs=pickle.load(open('../../{0}/analysis/{0}_PSFs_QSO'.format(key),'rb'))
+    PSFs_dict.update({'{0}'.format(key):PSFs})
+    QSOs_dict.update({'{0}'.format(key):QSOs})
+
+PSF_list = []
+PSF_id = []
+filter_list = []
+for key in PSFs_dict.keys():
+    if filt_info[key] == filt:
+        psfs_dict = PSFs_dict[key]
+        psfs = [psfs_dict[i] for i in range(len(psfs_dict))]
+        PSF_list += psfs
+        name_id = [key+"_"+str(i) for i in range(len(psfs_dict))]
+        PSF_id = PSF_id + name_id
[…]

### 2018-11-27 analysis_Astrodrz/mag-K-correction.py

@@ -1,0 +1,177 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Nov 15 10:29:58 2018
+
+@author: Dartoon
+
+To do the K-correction and check compared to the ACS
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import re
+from math import log10
+from adjustText import adjust_text   # avoid the overlapping while ploting
+import sys
+sys.path.insert(0,'../py_tools')
+from filter_info import filt_info, redshift_info
+import pickle
+
+def load_result(ID, count_rank=8, sort_PSF_by='fit_result_each', cam = 'WFC3'):
+    '''
+    Read the fitting result by given the ID, 
+    
+    Parameter
+    --------
+        ID: The blash of blash
+        b: The blash of blash
+        sort_PSF_by: 'fit_result_each' or 'fit_ps_each'
+    Return
+    --------
+        A sth sth
+    '''
+    ratio_results, Re_results, n_results, total_flux_results, host_amp_results, mag_result, mag_lh_result = [], [], [], [], [], [], []
+    chisq_list, inf_list, best_PSF_id = [],[], []
+    flux_dict, FWHM_dict, locs_dict, filter_dict, id_stars_dict=pickle.load(open('PSFs_lib_dict','rb'))
+    for j in range(len(ID)):
+        if cam == 'WFC3':
+            filt = filt_info[ID[j]]
+            f = open("{0}/analysis/fit_result_each/each_PSF_fit_qso.txt".format(ID[j]),"r")
+            if sort_PSF_by == 'fit_result_each':
+                f_ps = open("{0}/analysis/fit_result_each/each_PSF_fit_qso.txt".format(ID[j]),"r")
+            elif sort_PSF_by == 'fit_ps_each':
+                f_ps = open("{0}/analysis/fit_ps_each/each_PSF_fit_ps.txt".format(ID[j]),"r")
+        elif cam == 'ACS':
+            filt = 'F814w'
+            folder = "fit_result_each_fix"
+            f = open("../analysis_ACS/{0}/{1}/each_PSF_fit_qso.txt".format(ID[j],folder),"r")
[…]

### 2018-11-27 material/creat_table_for_manscript.py

@@ -1,0 +1,200 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Nov 26 09:25:32 2018
+
+@author: Dartoon
+"""
+
+import sys
+sys.path.insert(0,'../py_tools')
+from filter_info import filt_info, redshift_info
+import pickle, re
+import numpy as np
+from math import log10
+
+def load_result(ID, flt, count_rank=8):
+    '''
+    Read the fitting result by given the ID, 
+    
+    Parameter
+    --------
+        ID: The blash of blash
+        b: The blash of blash
+        sort_PSF_by: 'fit_result_each' or 'fit_ps_each'
+    Return
+    --------
+        A sth sth
+    '''
+    ratio_results, Re_results, n_results, total_flux_results, host_amp_results, mag_result, mag_lh_result = [], [], [], [], [], [], []
+    chisq_list, inf_list, best_PSF_id = [],[], []
+    flux_dict, FWHM_dict, locs_dict, filter_dict, id_stars_dict=pickle.load(open('../analysis_Astrodrz/PSFs_lib_dict','rb'))
+    if flt == 'WFC3':
+        filt = filt_info[ID]
+        f = open("../analysis_Astrodrz/{0}/analysis/fit_result_each/each_PSF_fit_qso.txt".format(ID),"r")
+    elif flt == 'ACS':
+        filt = 'F814w'
+        f = open("../analysis_ACS/{0}/fit_result_each_fix/each_PSF_fit_qso.txt".format(ID),"r")
+    string = f.read()
+#    PSF_id = re.findall(r"by PSF(.*?):",string)
+    S_n_list = re.findall(r"n_sersic':(.*?),",string)
+    Re = re.findall(r"R_sersic':(.*?),",string)
+    host_flux_ratio = re.findall(r"host_flux_ratio_percent':(.*?)}",string)
+    Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+    re.findall(r"redu_Chisq':(.*?),",string)
+    QSO_amp = re.findall(r"QSO_amp':(.*?),",string)
+    host_amp = re.findall(r"host_amp':(.*?),",string)
+    
+    S_n_list = [float(value) for value in S_n_list]
+    Re = [float(i) for i in Re]
[…]

### 2018-11-27 py_tools/dmag.py

@@ -1,0 +1,50 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Nov 15 10:37:04 2018
+
+@author: Dartoon
+
+For doing the k-correction
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from scipy import interpolate
+
+def pass_dmag(z): 
+    '''
+    Calculate the changes of magntidues for the passive mag evolution.
+    '''
+    return 3.70*np.log10(1+z)
+
+def k_corr_R(z, filt = 'F140w', galaxy_age = '5Gyrs'):
+    filename = 'K_{0}.dat'.format(galaxy_age)
+    with open('../material/{0}'.format(filename)) as f:
+        content = f.readlines()
+    lines = [x.strip() for x in content] 
+    arr_lines = []
+    arr_lines = [line.split( ) for line in lines if '#' not in line]
+    K_array = np.array(arr_lines, dtype=float)
+    if filt == 'F140w':
+        k_grid = np.stack([K_array[:,0],K_array[:,1]])
+    elif filt == 'F125w':
+        k_grid = np.stack([K_array[:,0],K_array[:,2]])
+    elif filt == 'F814w':
+        k_grid = np.stack([K_array[:,0],K_array[:,3]])
+    x = k_grid[0]
+    y = k_grid[1]
+    f = interpolate.interp1d(x, y)
+    dm = f(z)
+    return dm
+
+##Plot TT's figure:
+#z_d = np.linspace(1,2,20)
+#k_c_140_5gy = k_corr_R(z_d, filt = 'F140w', galaxy_age = '5Gyrs')
+#k_c_814_5gy = k_corr_R(z_d, filt = 'F814w', galaxy_age = '5Gyrs')
+#k_c_140_1gy = k_corr_R(z_d, filt = 'F125w', galaxy_age = '1Gyrs')
+#k_c_814_1gy = k_corr_R(z_d, filt = 'F814w', galaxy_age = '1Gyrs')
+#plt.plot(z_d,k_c_140_5gy-k_c_814_5gy, label = '5gy', c='r')
+#plt.plot(z_d,k_c_140_1gy-k_c_814_1gy, label = '1gy', c='b')
+#plt.legend()
+#plt.show()

### 2018-11-27 py_tools/flux_profile.py

@@ -462,7 +462,7 @@ def cr_mask(image, filename='test_circle.reg', mask_reg_cut = 0.):
 def total_compare(label_list, flux_list,
                   facility = 'F140w' , plot_type= 4, target_ID = 'target_ID',
                   add_background=0.0, data_mask_list = None, data_cut = 0.,plot_compare=False,
-                  pix_sz = 'drz06', msk_image=None, if_annuli=False):
+                  pix_sz = 'drz06', msk_image=None, if_annuli=False, arrows=False):
     if facility == 'F140w':
         zp = 26.4524
     elif facility == 'F125w':
@@ -489,13 +489,14 @@ def total_compare(label_list, flux_list,
     im1 = ax1.imshow(flux_list[0] + add_background,origin='lower',cmap="gist_heat", norm=norm, vmax = flux_list[0].max())
     clim=im1.properties()['clim']
     frame_size = len(flux_list[0])
-    ax1.set_ylabel(target_ID, fontsize=15)
-    ax1.text(frame_size*0.05, frame_size*0.9, label_list[0],fontsize=20, color='white')
+    ax1.set_ylabel(target_ID, fontsize=15, weight='bold')
+    ax1.text(frame_size*0.05, frame_size*0.9, label_list[0],fontsize=20,weight='bold', color='white')
     ax1.get_xaxis().set_visible(False)
-    ax1.get_yaxis().set_visible(False)
+#    ax1.get_yaxis().set_visible(False)
     scale_bar(ax1, frame_size, dist=1/delatPixel, text='1"', color = 'white')
-    coordinate_arrows(ax1, frame_size, arrow_size=0.03, color = 'white')
-    cb1 = f.colorbar(im1, ax=ax1, shrink=0.55, pad=0.01,  orientation="horizontal", aspect=15, ticks= [1.e-4, 1.e-3, 1.e-2,1.e-1,0, 10])
+    if arrows == True:
+        coordinate_arrows(ax1, frame_size, arrow_size=0.03, color = 'white')
+    cb1 = f.colorbar(im1, ax=ax1, shrink=0.48, pad=0.01,  orientation="horizontal", aspect=15, ticks= [1.e-4, 1.e-3, 1.e-2,1.e-1,0, 10])
     cb1.set_ticks([1.e-5, 1.e-4, 1.e-3, 1.e-2,1.e-1,0,1])   
 #    cb1.ax.()
     
[…]

### 2018-11-27 py_tools/transfer_to_result.py

@@ -11,7 +11,7 @@ import numpy as np
 def transfer_to_result(data, source_result, ps_result, image_ps, image_host,
                        error_map, filt, fixcenter,ID, cut=0, plot_compare=True,
                        QSO_msk_list = "",pix_sz = 'drz06', QSO_msk = None,
-                       tag=None):
+                       tag=None, plot_annuli=False):
     #==============================================================================
     # Translate the e1, e2 to phi_G and q
     #==============================================================================
@@ -71,10 +71,10 @@ def transfer_to_result(data, source_result, ps_result, image_ps, image_host,
                   plot_compare = plot_compare, msk_image = QSO_mask)
     if tag is not None:
         fig.savefig("{0}_SB_profile.pdf".format(tag), bbox_inches = 'tight')
-    fig1 = total_compare(label_list = label, flux_list = flux_list, target_ID = ID, pix_sz=pix_sz,
-                  data_mask_list = mask_list, data_cut = cut, facility = filt,
-                  plot_compare = plot_compare, msk_image = QSO_mask, if_annuli=True)
-    if tag is not None:
+    if tag is not None and plot_annuli == True:
+        fig1 = total_compare(label_list = label, flux_list = flux_list, target_ID = ID, pix_sz=pix_sz,
+                      data_mask_list = mask_list, data_cut = cut, facility = filt,
+                      plot_compare = plot_compare, msk_image = QSO_mask, if_annuli=True)
         fig1.savefig("{0}_SB_profile_annuli.pdf".format(tag), bbox_inches = 'tight')
     
     # =============================================================================
@@ -85,7 +85,6 @@ def transfer_to_result(data, source_result, ps_result, image_ps, image_host,
     reduced_Chisq = chiq_map.sum()/pixels
     result=roundme(result)
     result['redu_Chisq'] = round(reduced_Chisq,6)
-    
     return result
 
 def transfer_to_result_ps(data, ps_result, image_ps, image_host,

### 2018-11-27 manuscript/manuscript.tex
re-fitting CID206 with 41 frame size, paper writing with more figures

@@
 \label{sec:introduction}
-skeleton
+skeleton of introduction
 \\
-1. The ML relation and why understand its evolution is important.\\
-2. To understand this evolution, it is important to trace to high redshift. So, why it is difficult.\\
-3. Introduce reference. Woo's. SS13, Treu's, Park79. In the theory, DeGraf...\\
-4. This work, we introduces samples till redshift 1.7.
+1. Introduce the ML relation and why understand its evolution is important.\\
+2. To understand this evolution, it is important to trace to high redshift. Why it is difficult.\\
+3. Introduce reference. Woo's. SS13, Treu's, Park79. In the theory, DeGraf...Highlight the redshift range $z>1.2$\\
+4. In this paper, we study the ML relation up to redshift 1.7.
 
@@
 
-In figure, we demonstrate the optimized result of each system inferred by \lenstronomy. We also show the weighting process for an example system -- CID1174 in Table~\ref{tab:weight_CID1174}.
+In Figure~\ref{fig:QSO_decomp}, we demonstrate the optimized result of each system inferred by \lenstronomy.
+We also show the weighting process for an example system -- CID1174 in Table~\ref{tab:weight_CID1174}.
+In Figure~\ref{fig:flux_r_n_corner}, we summarize the relation among the inferred values of: \Reff, \sersic\ $n$, and host to total flux ratio.
 
@@
 
-We list all the inference of the host galaxy properties in the Table.
+We list all the inference of the host galaxy properties in the Table~\ref{tab:result_sersic}.
 
@@
 
+\textcolor{blue}{Introduce the passive evolution?}
+To directly compare with local samples, we consider the passive evolution scenario for the inferred \lhost\ and transfer to its expected value at today.
+
 We summarized the homogenized R-band luminosities
-in Table?
+in Table~\ref{tab:result_sersic}.
 
@@
 For the system with both \halpha\ and \hbeta\ emission line information, we adopt the average \mbh\ value by these two.
-We summarized the inference of the \mbh\ together with the details on the emission line in Table.
+We summarized the inference of the \mbh\ together with the details on the emission line in Table~\ref{tab:result_mbh}.
 
@@
 \label{sec:result}
-\subsection{M-L relation}
+\subsection{\mbh-\lhost\ relation}
+
+\subsection{\mbh-M$_*$ relation}
 \subsubsection{Stellar mass estimates}
 stellar mass \\
-\subsection{M-M$_*$ relation}
 
@@
 
+\section{discuss}
+\label{sec:dis}
+\subsection{Systematic error}
+\subsection{Fitting mask for CID1174 and ECDFS-358}
+
 \section*{Acknowledgments}
 We thank the people who discuss with the paper.
-X.D.
-acknowledges support by China Postdoctoral Science Foundation Funded Project; he is also grateful for Zong-Hong Zhu's support and funding.
-T.T.
-acknowledges support by the Packard Foundation in the form of a Packard Research Fellowship.
 
@@
 
-\begin{deluxetable*}{llccc}
+\begin{deluxetable}{llccc}
 \tablecolumns{5}
@@
 Column 2: Redshifts.
-Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.
+Column 3: HST filter by WFC3. The marker $^*$ indicate the corresponding sample also has the ACS/F814W image.
+Column 4 and 5: The $RA$ and $DEC$ of the system.
 }
-\end{deluxetable*}
+\end{deluxetable}
 
@@
 \tablewidth{0pt}
-\tablecaption{The process of weighting for COSMOS-CID1174 } 
+\tablecaption{Details of the weighting for the inference of CID1174. } 
 \tablehead{ 
@@
 \tablecomments{
-The detailed information of the weights for the inference of CID1174. The inflation value $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
+Column~1: The rank of the PSF from the library.
+Column~2: Total $\chi ^2$ for the corresponding PSF.
+Column~3: Weights for co-adding the inference.
+Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
+For this sample, the inflation value $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
 }
@@
 \begin{deluxetable*}
-{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
+{@{\extracolsep{4pt}}lccccccccc}   % need for the gap between the clines.
 \tablecolumns{9}
 \tablewidth{0pt}
-\tablecaption{The sample information for the 32 systems.} 
+\tablecaption{The inference of the host information by the QSO decomposition for the 32 systems.} 
 \tablehead
@@
 \colhead{magnitude}&
-\colhead{reduced $\chi ^2$}& \colhead{host flux ratio}& \colhead{magnitude}\\
+\colhead{reduced $\chi ^2$}& \colhead{host flux ratio}& \colhead{magnitude} & \colhead{$\log L_R$}\\
 \colhead{}& 
@@
 \colhead{(AB system)}& \colhead{}& 
-\colhead{}& \colhead{(AB system)} \\
+\colhead{}& \colhead{(AB system)}&\colhead{($L_{\odot,R}$)} \\
 \colhead{(1)}& 
@@
 \colhead{(6)}& \colhead{(7)}& 
-\colhead{(8)}& \colhead{(9)}
+\colhead{(8)}& \colhead{(9)}&\colhead{(10)}
 }
@@
 \tablecomments{
-Column 1: Object field and ID.
-Column 2: Redshifts.
-Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.
+Column~1: Object ID.
+Column~2: Reduced $\chi ^2$ value by the best PSF in the library.
+Column~3-6: Host inference by the WFC3 image.
+Column~7-9: Host inference by the ACS image. 
+Column~10: The inferred host Luminosity in the rest-frame R band.
 }
@@
 \colhead{}& 
-\colhead{FWHM}& \colhead{$\lambda \rm L _{H\alpha}$}& \colhead{\mbh}&
-\colhead{FWHM(5100)}& \colhead{$\lambda \rm L _{\lambda5100}$}& \colhead{\mbh}\\
+\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}&
+\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}\\
 \colhead{}& 
-\colhead{(\kms)}& \colhead{($10^{42}{\rm erg~s^{-1}}$)}& 
+\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
 \colhead{(M$_{\odot}$)}& \colhead{(\kms)}& 
-\colhead{($10^{44}{\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
+\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
 \colhead{(1)}& 
@@
 CID206 & 3333.5527 & 43.4776 & 8.317 & ... & ... & ... \\
-CID216 & 2229.5232 & 42.84509 & 7.62 & ... & ... & ... \\
+CID216 & 2229.5232 & 42.84509 & 7.620 & ... & ... & ... \\
 CID237 & 2112.3306 & 43.85546 & 8.129 & ... & ... & ... \\
@@
 CID452 & 3457.8801 & 42.92298 & 8.044 & 3127.3306 & 44.63353 & 8.201 \\
-CID454 & 2824.2693 & 43.34466 & 8.1 & ... & ... & ... \\
+CID454 & 2824.2693 & 43.34466 & 8.100 & ... & ... & ... \\
 CID50 & 2339.9104 & 43.93786 & 8.263 & 1938.5676 & 45.32766 & 8.145 \\
@@
 SXDS-X1136 & 2759.8953 & 43.43305 & 8.129 & 6761.222 & 44.71429 & 8.912 \\
-SXDS-X50 & 1816.672 & 43.421 & 7.759 & ... & ... & ... \\
-SXDS-X717 & 2930.7417 & 43.04988 & 7.97 & ... & ... & ... \\
+SXDS-X50 & 1816.672 & 43.42100 & 7.759 & ... & ... & ... \\
+SXDS-X717 & 2930.7417 & 43.04988 & 7.970 & ... & ... & ... \\
 SXDS-X735 & 2702.0962 & 43.69804 & 8.256 & 3519.6052 & 45.07463 & 8.532 \\
@@
 \enddata
-\label{tab:result_sersic}
+\label{tab:result_mbh}
 \tablecomments{
-Column 1: Object field and ID.
-Column 2: Redshifts.
+Column 1: Object ID.
+Column 2: .
 Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.
@@
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID237_SB_profile.pdf}
-\caption{\label{fig:ML} WFC3 F110W images for 12 objects.
+\caption{\label{fig:QSO_decomp} 
+\textcolor{red}{need to be written:}
+%WFC3 images for 12 objects.
 In each row, observed data (first column), best-fit models (second column), and residuals (third column) are presented with the object name.
-All images are $10.8\arcsec\times10.8\arcsec$ in size and
- displayed with an inverted asinh stretch.
+All images are $10.8\arcsec\times10.8\arcsec$ in size and  displayed with an inverted asinh stretch.
 The fourth column shows the corresponding one-dimensional surface brightness profiles.
@@
 Residuals (gray circles), the difference of the profiles between the data and the best-fit model, are presented in each bottom panel.
-Note that the one-dimensional surface brightness profiles are shown for illustration purposes only, the actual fitting made use of the full two-dimensional images.}
-}
+Note that the one-dimensional surface brightness profiles are shown for illustration purposes only, the actual fitting made use of the full two-dimensional images.
+}}
 \end{figure*}
@@
 \figurenum{1}
-\caption{\label{fig:ML} Continued.}
+\caption{Continued.}
 \end{figure*}
@@
 \figurenum{1}
-\caption{\label{fig:ML} Continued.}
+\caption{Continued.}
+\end{figure*}
+
+\begin{figure*}
+\centering
+{
+\includegraphics[height=0.75\textwidth]{fig/flux_r_n_corner.pdf}
+}
+\caption{\label{fig:flux_r_n_corner} The relations among these values.}
 \end{figure*}

### 2018-12-03 manuscript/manuscript.tex
fit result before re-fit the other QSO using CID597 and CID1281's PSF

@@
 
-Our final sample is composed of 36  AGNs; 32 of them are new systems \textcolor{red}{\bf (32+4?, the information of these four sample?)}.
-To compare with the samples in the literature, we adopt the samples from ...
-\textcolor{blue}{\bf The samples from H0licow7}
+Our final sample is composed of 36  AGNs; 32 of them are new observations by HST/WFC3 \textcolor{red}{\bf (32+4?, the information of these four sample?)}.
+Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.
+
+To compare with the samples in the literature, we adopt the samples from ... \textcolor{blue}{\bf (H0licow7)}.
 For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point.
-Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.
 
@@
 
-With the self-consistent cross-calibration, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
-For the system with both \halpha\ and \hbeta\ emission line information, we adopt the average \mbh\ value by these two.
+Having defined the recipes, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
+14 of the overall systems have both \halpha\ and \hbeta\ emission line information; we adopt the average \mbh\ value by these two lines.
 We summarized the inference of the \mbh\ together with the details on the emission line in Table~\ref{tab:result_mbh}.
@@
 \subsection{Systematic error}
-\subsection{Fitting mask for CID1174 and ECDFS-358}
+\subsection{Fitting mask for CID206 and ECDFS-358}
 
@@
 \tablewidth{0pt}
-\tablecaption{Details of the weighting for the inference of CID1174. } 
+\tablecaption{Details of the weighting CID1174's inference. } 
 \tablehead{ 
@@
 \startdata 
-CID1174 & 1906.3037 & 43.43237 & 7.807 & 5898.264 & 44.76243 & 8.818 \\
-CID1281 & 1619.4891 & 43.23945 & 7.559 & ... & ... & ... \\
-CID206 & 3333.5527 & 43.4776 & 8.317 & ... & ... & ... \\
-CID216 & 2229.5232 & 42.84509 & 7.620 & ... & ... & ... \\
-CID237 & 2112.3306 & 43.85546 & 8.129 & ... & ... & ... \\
-CID255 & 1932.0933 & 43.9924 & 8.127 & 3709.241 & 45.37122 & 8.731 \\
-CID3242 & 2543.2202 & 43.83323 & 8.278 & 3774.503 & 45.09891 & 8.605 \\
-CID3570 & 1958.8551 & 43.16374 & 7.683 & ... & ... & ... \\
-CID452 & 3457.8801 & 42.92298 & 8.044 & 3127.3306 & 44.63353 & 8.201 \\
-CID454 & 2824.2693 & 43.34466 & 8.100 & ... & ... & ... \\
-CID50 & 2339.9104 & 43.93786 & 8.263 & 1938.5676 & 45.32766 & 8.145 \\
-CID543 & 2188.8447 & 43.57404 & 8.005 & ... & ... & ... \\
-CID597 & 1656.3296 & 43.32955 & 7.629 & ... & ... & ... \\
-CID607 & 3009.1816 & 43.67079 & 8.335 & 4241.526 & 44.78209 & 8.542 \\
-CID70 & 2480.4058 & 43.50531 & 8.076 & 3981.8574 & 45.1582 & 8.682 \\
-LID1273 & 3223.8484 & 43.61001 & 8.361 & ... & ... & ... \\
-LID1538 & 2941.422 & 43.59594 & 8.274 & ... & ... & ... \\
-LID360 & 2481.7253 & 43.88091 & 8.283 & 2868.8992 & 45.08676 & 8.36 \\
-XID2138 & 3185.8613 & 43.6148 & 8.354 & 2944.7766 & 44.80782 & 8.239 \\
-XID2202 & 2973.2378 & 43.56249 & 8.265 & ... & ... & ... \\
-XID2396 & 2271.2617 & 44.06196 & 8.306 & 2657.8386 & 45.50467 & 8.51 \\
+CID1174 & 1906.3037 & 43.43237 & 7.992 & 5898.264 & 44.76243 & 8.833 \\
+CID1281 & 1619.4891 & 43.23945 & 7.749 & ... & ... & ... \\
+CID206 & 3333.5527 & 43.4776 & 8.528 & ... & ... & ... \\
+CID216 & 2229.5232 & 42.84509 & 7.854 & ... & ... & ... \\
+CID237 & 2112.3306 & 43.85546 & 8.289 & ... & ... & ... \\
+CID255 & 1932.0933 & 43.9924 & 8.273 & 3709.241 & 45.37122 & 8.734 \\
+CID3242 & 2543.2202 & 43.83323 & 8.449 & 3774.503 & 45.09891 & 8.613 \\
+CID3570 & 1958.8551 & 43.16374 & 7.888 & ... & ... & ... \\
+CID452 & 3457.8801 & 42.92298 & 8.295 & 3127.3306 & 44.63353 & 8.217 \\
+CID454 & 2824.2693 & 43.34466 & 8.311 & ... & ... & ... \\
+CID50 & 2339.9104 & 43.93786 & 8.423 & 1938.5676 & 45.32766 & 8.149 \\
+CID543 & 2188.8447 & 43.57404 & 8.187 & ... & ... & ... \\
+CID597 & 1656.3296 & 43.32955 & 7.813 & ... & ... & ... \\
+CID607 & 3009.1816 & 43.67079 & 8.526 & 4241.526 & 44.78209 & 8.556 \\
+CID70 & 2480.4058 & 43.50531 & 8.269 & 3981.8574 & 45.1582 & 8.689 \\
+LID1273 & 3223.8484 & 43.61001 & 8.561 & ... & ... & ... \\
+LID1538 & 2941.422 & 43.59594 & 8.469 & ... & ... & ... \\
+LID360 & 2481.7253 & 43.88091 & 8.45 & 2868.8992 & 45.08676 & 8.369 \\
+XID2138 & 3185.8613 & 43.6148 & 8.552 & 2944.7766 & 44.80782 & 8.252 \\
+XID2202 & 2973.2378 & 43.56249 & 8.463 & ... & ... & ... \\
+XID2396 & 2271.2617 & 44.06196 & 8.455 & 2657.8386 & 45.50467 & 8.511 \\
 CDFS-1 & ... & ... & ... & ... & ... & ... \\
 CDFS-229 & ... & ... & ... & ... & ... & ... \\
-CDFS-321 & 2441.93 & 43.92714 & 8.294 & ... & ... & ... \\
+CDFS-321 & 2441.93 & 43.92714 & 8.457 & ... & ... & ... \\
 CDFS-724 & ... & ... & ... & ... & ... & ... \\
-ECDFS-358 & 2237.2314 & 43.39674 & 7.927 & ... & ... & ... \\
-SXDS-X1136 & 2759.8953 & 43.43305 & 8.129 & 6761.222 & 44.71429 & 8.912 \\
-SXDS-X50 & 1816.672 & 43.42100 & 7.759 & ... & ... & ... \\
-SXDS-X717 & 2930.7417 & 43.04988 & 7.970 & ... & ... & ... \\
-SXDS-X735 & 2702.0962 & 43.69804 & 8.256 & 3519.6052 & 45.07463 & 8.532 \\
-SXDS-X763 & 2961.1743 & 43.57321 & 8.267 & 4508.5146 & 44.51285 & 8.456 \\
-SXDS-X969 & 2296.0566 & 43.50066 & 8.006 & 1695.7146 & 45.05337 & 7.886 \\
+ECDFS-358 & 2237.2314 & 43.39674 & 8.122 & ... & ... & ... \\
+SXDS-X1136 & 2759.8953 & 43.43305 & 8.333 & 6761.222 & 44.71429 & 8.927 \\
+SXDS-X50 & 1816.672 & 43.421 & 7.942 & ... & ... & ... \\
+SXDS-X717 & 2930.7417 & 43.04988 & 8.204 & ... & ... & ... \\
+SXDS-X735 & 2702.0962 & 43.69804 & 8.44 & 3519.6052 & 45.07463 & 8.54 \\
+SXDS-X763 & 2961.1743 & 43.57321 & 8.465 & 4508.5146 & 44.51285 & 8.474 \\
+SXDS-X969 & 2296.0566 & 43.50066 & 8.196 & 1695.7146 & 45.05337 & 7.895 \\
 \enddata
@@
 Column 1: Object ID.
-Column 2: .
-Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.
+Column 2-4: The emission line width (FWHM), continuum luminosity and inferred \mbh by \halpha\ emission line. 
+Column 5-7: The inference by \hbeta\ emission line. 
 }
@@
 \textcolor{red}{need to be written:}
-%WFC3 images for 12 objects.
-In each row, observed data (first column), best-fit models (second column), and residuals (third column) are presented with the object name.
+Figure illustrates the inference by WFC3 images for the 34 objects.
+In each row, observed data (first column), best-fit models (second column), data subtracted by the inferred point source (third column),  normalized residuals (fourth column) are presented together with the target ID.
+In the fifth column, we present the 1-D surface brightness profiles and the corresponding residual.
+\textcolor{blue}{The different colors means blash blash...}
+%In each row, observed data (first column), best-fit models (second column), and residuals (third column) are presented with the object name.
 All images are $10.8\arcsec\times10.8\arcsec$ in size and  displayed with an inverted asinh stretch.

### 2018-12-03 analysis_Astrodrz/CID597/analysis/5_plt_each_psf_fitting.py

@@ -1,0 +1,86 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jul 24 21:46:04 2018
+
+@author: Dartoon
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import re
+import matplotlib
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-2]
+
+import sys
+sys.path.insert(0,'../../../py_tools')
+from filter_info import filt_info
+filt = filt_info[ID]
+
+f = open("fit_result_each/each_PSF_fit_qso.txt","r")
+string = f.read()
+
+PSF_id = re.findall(r"by PSF(.*?):",string)
+S_n_list = re.findall(r"n_sersic':(.*?),",string)
+Re = re.findall(r"R_sersic':(.*?),",string)
+host_flux_ratio = re.findall(r"host_flux_ratio_percent':(.*?)}",string)
+Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+QSO_amp = re.findall(r"QSO_amp':(.*?),",string)
+host_amp = re.findall(r"host_amp':(.*?),",string)
+
+S_n_list = [float(value) for value in S_n_list]
+Re = [float(i) for i in Re]
+host_flux_ratio = [float(i) for i in host_flux_ratio]
+Chisq = [float(i) for i in Chisq]
+QSO_amp = [float(i) for i in QSO_amp]
+host_amp =  [float(i) for i in host_amp]
+
+import pickle
+PSFs_dict = {}
+for key in filt_info.keys():
+    if filt_info[key] == filt:
+        PSFs, _=pickle.load(open('../../{0}/analysis/{0}_PSFs_QSO'.format(key),'rb'))
+        PSFs_dict.update({'{0}'.format(key):PSFs})
+
+flux_dict, FWHM_dict, locs_dict, filter_dict, id_stars_dict=pickle.load(open('../../PSFs_lib_dict','rb'))
+
+#for i in range(len(PSF_id)):
+#    print PSF_id[i], Chisq[i], host_flux_ratio[i], Re[i], S_n_list[i], filter_list[i]
+
+total_flux = np.asarray(QSO_amp) + np.asarray(host_amp)
+
+sort_Chisq = np.argsort(np.asarray(Chisq))
+count_n = 8
+Chisq_best = Chisq[sort_Chisq[0]]
+Chisq_last= Chisq[sort_Chisq[count_n-1]]
[…]

### 2018-12-03 analysis_Astrodrz/CID597/analysis/cut_PSFs.py

@@ -1,0 +1,217 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Mar  5 14:04:02 2018
+
+@author: Dartoon
+
+Cut PSF and QSO for xxx
+"""
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import sys
+sys.path.insert(0,'../../../py_tools')
+from cut_image import cut_image, cut_center_bright, save_loc_png, grab_pos
+import copy
+import astropy.io.fits as pyfits
+
+import os
+path = os.getcwd()
+
+ID = path.split('/')[-2]
+fitsFile = pyfits.open('../astrodrz/final_drz.fits')
+
+#img = fitsFile[1].data # check the back grounp
+#from astropy.visualization import SqrtStretch
+#from astropy.stats import SigmaClip
+#from photutils import Background2D, SExtractorBackground  
+#from astropy.visualization.mpl_normalize import ImageNormalize
+#import matplotlib.pyplot as plt
+#norm = ImageNormalize(stretch=SqrtStretch())         
+#sigma_clip = SigmaClip(sigma=3., iters=10)
+#bkg_estimator = SExtractorBackground()
+#from photutils import make_source_mask
+#mask_0 = make_source_mask(img, snr=2, npixels=5, dilate_size=11)
+#mask_1 = (np.isnan(img))
+#mask = mask_0 + mask_1
+#bkg = Background2D(img, (50, 50), filter_size=(3, 3),
+#                   sigma_clip=sigma_clip, bkg_estimator=bkg_estimator,
+#                   mask=mask)
+#from matplotlib.colors import LogNorm
+#fig=plt.figure(figsize=(15,15))
+#ax=fig.add_subplot(1,1,1)
+#ax.imshow(img, norm=LogNorm(), origin='lower') 
+##bkg.plot_meshes(outlines=True, color='#1f77b4')
+#ax.xaxis.set_visible(False)
+#ax.yaxis.set_visible(False)
+#plt.show()  
+#fig=plt.figure(figsize=(15,15))
+#ax=fig.add_subplot(1,1,1)
+#ax.imshow(mask, origin='lower') 
+##bkg.plot_meshes(outlines=True, color='#1f77b4')
+#ax.xaxis.set_visible(False)
+#ax.yaxis.set_visible(False)
+#plt.show()  
+#
[…]

### 2018-12-07 manuscript/manuscript.tex
git push after "The telecon"

@@
 \def\kms{km~s$^{\rm -1}$}
+\def\sigstar{{$\sigma_*$}}
+\def\smass{{$M_*$}}
+\newcommand{\Mgii}{Mg$_{\rm II}$}
+\newcommand{\Civ}{C$_{\rm IV}$}
 
@@
 To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
 \end{abstract}
@@
 \label{sec:introduction}
-skeleton of introduction
-\\
-1. Introduce the ML relation and why understand its evolution is important.\\
-2. To understand this evolution, it is important to trace to high redshift. Why it is difficult.\\
-3. Introduce reference. Woo's. SS13, Treu's, Park79. In the theory, DeGraf...Highlight the redshift range $z>1.2$\\
-4. In this paper, we study the ML relation up to redshift 1.7.
+%skeleton of introduction
+%\\
+%1. Introduce the ML relation and why understand its evolution is important.\\
+%2. To understand this evolution, it is important to trace to high redshift. Why it is difficult.\\
+%3. The 4000A by HST band.
+%3. Introduce reference. Woo's. SS13, Treu's, Park79. In the theory, DeGraf...Highlight the redshift range $z>1.2$. Recent works by H0liCOW7\\
+%4. In this paper, we study the ML relation up to redshift 1.7.
+
+Most galactic nuclei harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh- stellar mass (\smass)  and \mbh-stellar velocity dispersion(\sigstar).
+These tight correlations indicates a connection between nuclear activity and galaxy formation and evolution.
+Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy.
+In theory, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver.
+However, for a different view, \textcolor{blue}{Peng 2007 and Jahnke 2011} show that, without the need of a physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.
+
+One key is to trace their correlation to higher redshift, determining how and when they emerged and evolved over cosmic time.
+During past decade, there has been much progress on our understand at $z<1$ using the type 1 AGN.
+The work by \textcolor{blue}{Park, Treu, Woo, P06, H0licow7} demonstrated that, \mbh\ are elevated as compared to the bulge luminosity from the local relations, thus indicating that the supermassive BHs were built up first with galaxy then growing around their deep potential wells.
+Similarly, the recent works by \textcolor{blue}{Bennert et al.
+2011, Woo 2008} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations.
+Nevertheless, some studies are consistent with no evolution \textcolor{blue}{Schramm+Silverman 2013, Sun et al.
+2015, Cisternas et al.
+2011}.
+
+Despite the great amount of effort, there are still uncertainties stems from different aspects which could lead to the inconsistency among these works.
+First, the inherent uncertainties in BH mass estimates using the virial method.
+Especially, many studies rely on \mbh\ estimates using the \Mgii\ or \Civ\ line that may have unknown systematics when compared to local samples with masses based on broad Balmer lines (i.e.
+\halpha\ and \hbeta).
+Second, since the host information is swamped by the bright nuclear light, measurement systematics exist in the host galaxy properties.
+It is worth noting that strong gravitational lensing provides a unique opportunity to make progress in the study by extend the host image to lensed arcs \textcolor{blue}{H0licow6, Peng06, H0licow7}.
+Equally important,
+the selection effects and their impact on the observed need to be taken well into account.
+For instance, it has been demonstrated \textcolor{blue}{Schulze + Wisotzki (2011, 2014))} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample.
+Even considering this selection effect, an evolution of the scaling relations is expected from simulations \textcolor{blue}{DeGraf et al.
+(2015} and with respect to the bulge mass.
+
+To make progress, on one hand, it is essential to making use of a larger sample of high-quality data in respect of the measurement of both the host properties and the \mbh.
+On the other hand, extending the correlations to higher redshift ($z>1$) would effectively improves the statistics, where the \mbh-\lhost\ is steeper than the current observational measurements at lower redshift, before self-regulation slows the black hole growth and galaxies settle onto the local mass relation.
+
+In this study, we aim to determine whether AGN have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \textcolor{blue}{(Aird et al.
+2015)}.
+At this redshift range, we measure 32 host galaxies properties using \hst/WFC3 imaging data and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS.
+Our study overcomes the biases in the following way.
+First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function.
+Second, we estimate \mbh\ using Balmer lines which avoid the systematics by \Mgii.
+Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements.
+Moreover, 21/32 systems of our sample also have \hst/ACS-F814W image.
+The multi-band information provide reliable K-correction and stellar mass inference.
+Given the high-quality data at such redshift, we test whether the growth of BH predates that of the host by a factor of at least $1.7 (\sim0.23$ dex).
+
+The paper is organized as follows.
+We briefly describe the sample selection, observation and data reduction in Section~\ref{sec:data}.
+We infer the host galaxy surface photometry and \mbh\ in Section~\ref{sec:analysis}.
+In Section~\ref{sec:result}, we present our main result by adopting K-correction and SED fitting, to infer the rest-frame R band \lhost\ and \smass in order to compare with the local samples.
+Discussion and conclusion are presented in Section~\ref{sec:sum} and Section~\ref{sec:dis}.
+
+Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} =
+0.70$. Magnitudes are given in the AB system.
 
@@
 We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets.
-This selection could ensure that the broad \halpha line ($4000\AA$) is not present in the bandpass which could contaminate the host emissions due to the broad wings of the PSF.
+This selection could ensure that the broad \halpha\ line ($4000\AA$) is not present in the bandpass which could contaminate the host emissions due to the broad wings of the PSF.
 
@@
 
-With 18/32 of our sample have rest-frame UV images by \textcolor{blue}{Scoville, et al. 2007} %arxiv: 0702359}.
+21/32 of our sample have rest-frame UV images by \textcolor{blue}{Scoville, et al. 2007} %arxiv: 0702359}.
 Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures.
@@
 \section{Analysis}
-\label{sec:Analysis}
+\label{sec:analysis}
 
@@
 Since two filter, i.e.
-F140W and F125W, are selected for different samples, we selected 74 and 34 PSFs for the samples observed by F140W and F125W, respectively.
+F140W and F125W, are selected for different samples, we selected 78 and 36 PSFs for the samples observed by F140W and F125W, respectively.
 
@@
 \label{eq:Hb}
-\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.882+0.518\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
-&~+~& 2 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
+\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
+&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
 \end {eqnarray}
@@
 \label{eq:Ha}
-\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.459+0.55 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
-&~+~& 2 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right) , 
+\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.710+0.48 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
+&~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right) , 
 \end {eqnarray}
@@
 %\\
-COSMOS-CID1174 & 1.552 & F140W$^*$ & 150.2789 & 1.9595\\
-COSMOS-CID1281 & 1.445 & ??? & 150.4160 & 2.5258\\
+COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595\\
+COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258\\
 COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088\\
-COSMOS-CID216 & 1.567 & F140W$^*$ & 149.7918 & 1.8729\\
-COSMOS-CID237 & 1.618 & F140W$^*$ & 149.9916 & 1.7243\\
-COSMOS-CID255 & 1.664 & ???$^*$ & 150.1017 & 1.8483\\
+COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729\\
+COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243\\
+COSMOS-CID255 & 1.664 & F140W & 150.1017 & 1.8483\\
 COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452\\
 COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076\\
-COSMOS-CID452 & 1.407 & F125W$^*$ & 150.0045 & 2.2371\\
-COSMOS-CID454 & 1.478 & F140W$^*$ & 149.8681 & 2.3307\\
-COSMOS-CID50 & 1.239 & F125W$^*$ & 150.2080 & 2.0833\\
-COSMOS-CID543 & 1.301 & F125W$^*$ & 150.4519 & 2.1448\\
-COSMOS-CID597 & 1.272 & ???$^*$ & 150.5262 & 2.2449\\
-COSMOS-CID607 & 1.294 & F125W$^*$ & 150.6097 & 2.3231\\
+COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371\\
+COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307\\
+COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833\\
+COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448\\
+COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449\\
+COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231\\
 COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701\\
 COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275\\
-COSMOS-LID1538 & 1.527 & F140W$^*$ & 150.6215 & 2.1588\\
-COSMOS-LID360 & 1.579 & F140W$^*$ & 150.1251 & 2.8617\\
-COSMOS-XID2138 & 1.551 & F140W$^*$ & 149.7036 & 2.5781\\
-COSMOS-XID2202 & 1.516 & F140W$^*$ & 150.6530 & 1.9969\\
-COSMOS-XID2396 & 1.600 & F140W$^*$ & 149.4779 & 2.6425\\
-CDFS-1 & 1.630 & F140W$^*$ & 52.8990 & -27.8600\\ 
-CDFS-229 & 1.326 & F125W$^*$ & 53.0680 & -27.6580\\ 
-CDFS-321 & 1.570 & F140W$^*$ & 53.0486 & -27.6239\\ 
+COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588\\
+COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617\\
+COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781\\
+COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969\\
+COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425\\
+CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600\\ 
+CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580\\ 
+CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239\\ 
 CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940\\ 
@@
 Column 2: Redshifts.
-Column 3: HST filter by WFC3. The marker $^*$ indicate the corresponding sample also has the ACS/F814W image.
+Column 3: HST filter by WFC3. Note that the samples from COSMOS field also has the ACS/F814W image.
 Column 4 and 5: The $RA$ and $DEC$ of the system.
@@
 %\\
-1 & 8646.711 & 1.000 & 99.102 & 41.9\% & 0\farcs{}298 & 1.932 \\
-2 & 8816.947 & 0.849 & 76.740 & 33.0\% & 0\farcs{}365 & 1.102 \\
-3 & 9304.841 & 0.530 & 128.618 & 54.7\% & 0\farcs{}231 & 2.780 \\
-4 & 9652.575 & 0.379 & 187.498 & 79.0\% & 0\farcs{}116 & 6.175 \\
-5 & 10018.324 & 0.267 & 75.061 & 32.3\%& 0\farcs{}365 & 1.226 \\
-6 & 10087.456 & 0.249 & 79.835 & 34.3\% & 0\farcs{}358 & 1.195 \\
-7 & 10457.811 & 0.174 & 108.580 & 46.4\% & 0\farcs{}262 & 2.190 \\
-8 & 10721.421 & 0.135 & 63.994 & 27.8\% & 0\farcs{}406 & 0.720 \\
+1 & $8584.429$ & $1.000$ & $82.209$ & $35.4\%$ & $0\farcs{}345$ & $1.114$ \\
+2 & $8646.711$ & $0.920$ & $99.102$ & $41.9\%$ & $0\farcs{}298$ & $1.932$ \\
+3 & $8816.947$ & $0.734$ & $76.74$ & $33.0\%$ & $0\farcs{}365$ & $1.102$ \\
+4 & $9304.841$ & $0.383$ & $128.618$ & $54.7\%$ & $0\farcs{}231$ & $2.78$ \\
+5 & $9652.575$ & $0.241$ & $187.498$ & $79.0\%$ & $0\farcs{}116$ & $6.175$ \\
+6 & $9917.101$ & $0.170$ & $100.166$ & $42.3\%$ & $0\farcs{}287$ & $2.066$ \\
+7 & $10018.324$ & $0.148$ & $75.061$ & $32.3\%$ & $0\farcs{}365$ & $1.226$ \\
+8 & $10087.456$ & $0.135$ & $79.835$ & $34.3\%$ & $0\farcs{}358$ & $1.195$ \\
 \hline\\
-Weighted value & & & 103.534 $\pm$ 34.267 & 44.0\%$\pm$14.2\%& 0\farcs{}296$\pm$0\farcs{}079 & 2.173$\pm$1.500  \\
+Weighted value & & & $97.322\pm28.336$ & $41.5\%\pm11.7\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.862\pm1.26$  \\
 \enddata
@@
 
+\tabcolsep=0.05cm
 \begin{deluxetable*}
@@
 \startdata 
-CID1174 & 2.324 & 44.0\%$\pm$14.2\% & 0.296$\pm$0.079 & 2.173$\pm$1.5 & $21.415\substack{+0.436 \\ -0.31}$ & 2.484074 & 11.7\%$\pm$1.4\% & $23.165\substack{+0.138 \\ -0.122}$\\
-CID1281 & ... & ... & ... & ... & ... & ... & ... & ...\\
-CID206 & 2.054 & 35.7\%$\pm$24.1\% & 0.282$\pm$0.151 & 3.191$\pm$2.51 & $21.81\substack{+1.247 \\ -0.565}$ & 1.903449 & 7.7\%$\pm$2.4\% & $23.671\substack{+0.403 \\ -0.293}$\\
-CID216 & 1.514 & 93.9\%$\pm$4.7\% & 0.251$\pm$0.063 & 6.159$\pm$1.205 & $21.51\substack{+0.052 \\ -0.049}$ & 1.424993 & 35.1\%$\pm$1.5\% & $23.446\substack{+0.053 \\ -0.051}$\\
-CID237 & 2.349 & 29.9\%$\pm$6.3\% & 0.872$\pm$0.172 & 4.736$\pm$1.701 & $21.279\substack{+0.26 \\ -0.209}$ & 2.353571 & 3.2\%$\pm$2.0\% & $23.718\substack{+1.037 \\ -0.52}$\\
+CID1174 & $2.307$ & $41.5\%\pm11.7\%$ & $0\farcs{}309\pm0\farcs{}065$ & $1.862\pm1.26$ & $21.482\substack{+0.374\\-0.277}$ & $2.496$ & $11.2\%\pm1.1\%$ & $23.214\substack{+0.113\\-0.103}$ \\
+CID1281 & $1.322$ & $49.3\%\pm13.7\%$ & $0\farcs{}239\pm0\farcs{}094$ & $3.146\pm1.483$ & $22.879\substack{+0.362\\-0.271}$ & $1.378$ & $18.5\%\pm7.7\%$ & $24.828\substack{+0.595\\-0.382}$ \\
+CID206 & $2.054$ & $35.3\%\pm24.3\%$ & $0\farcs{}286\pm0\farcs{}146$ & $3.072\pm2.476$ & $21.822\substack{+1.298\\-0.575}$ & $1.903$ & $7.7\%\pm2.4\%$ & $23.671\substack{+0.403\\-0.293}$ \\
+CID216 & $1.514$ & $93.9\%\pm4.7\%$ & $0\farcs{}251\pm0\farcs{}063$ & $6.159\pm1.205$ & $21.51\substack{+0.052\\-0.049}$ & $1.425$ & $35.1\%\pm1.5\%$ & $23.446\substack{+0.053\\-0.051}$ \\
+CID237 & $2.349$ & $29.9\%\pm6.3\%$ & $0\farcs{}872\pm0\farcs{}172$ & $4.736\pm1.701$ & $21.279\substack{+0.26\\-0.209}$ & $2.354$ & $3.2\%\pm2.0\%$ & $23.718\substack{+1.037\\-0.52}$ \\
 CID255 & ... & ... & ... & ... & ... & ... & ... & ...\\
-CID3242 & 2.751 & 46.1\%$\pm$12.7\% & 0.201$\pm$0.159 & 6.142$\pm$1.874 & $21.161\substack{+0.35 \\ -0.264}$ & 2.595594 & 4.8\%$\pm$1.3\% & $23.595\substack{+0.337 \\ -0.257}$\\
-CID3570 & 1.665 & 76.5\%$\pm$1.6\% & 0.698$\pm$0.007 & 0.728$\pm$0.054 & $21.164\substack{+0.021 \\ -0.021}$ & 1.331913 & 85.6\%$\pm$1.5\% & $22.971\substack{+0.012 \\ -0.012}$\\
-CID452 & 1.684 & 75.4\%$\pm$3.9\% & 0.365$\pm$0.015 & 1.402$\pm$0.175 & $21.176\substack{+0.063 \\ -0.06}$ & 1.451608 & 37.8\%$\pm$0.7\% & $22.732\substack{+0.022 \\ -0.022}$\\
-CID454 & 2.203 & 35.3\%$\pm$2.1\% & 0.391$\pm$0.013 & 0.602$\pm$0.092 & $21.212\substack{+0.067 \\ -0.063}$ & 1.29101 & 9.2\%$\pm$0.5\% & $23.352\substack{+0.058 \\ -0.055}$\\
-CID50 & 5.576 & 16.8\%$\pm$8.7\% & 0.152$\pm$0.102 & 3.371$\pm$2.154 & $20.915\substack{+0.796 \\ -0.454}$ & 4.940352 & 5.0\%$\pm$3.3\% & $22.504\substack{+1.145 \\ -0.545}$\\
-CID543 & 1.902 & 31.8\%$\pm$10.0\% & 0.1$\pm$0.0 & 0.505$\pm$0.333 & $21.95\substack{+0.405 \\ -0.294}$ & 1.434799 & 5.2\%$\pm$2.0\% & $23.765\substack{+0.534 \\ -0.357}$\\
-CID597 & ... & ... & ... & ... & ... & ... & ... & ...\\
-CID607 & 1.692 & 43.6\%$\pm$17.9\% & 0.206$\pm$0.087 & 3.418$\pm$1.097 & $21.189\substack{+0.575 \\ -0.374}$ & 2.590398 & 4.7\%$\pm$1.8\% & $23.566\substack{+0.511 \\ -0.346}$\\
-CID70 & 2.041 & 19.6\%$\pm$5.1\% & 0.426$\pm$0.101 & 3.543$\pm$1.154 & $21.865\substack{+0.323 \\ -0.248}$ & 2.36054 & 2.3\%$\pm$1.1\% & $24.625\substack{+0.677 \\ -0.414}$\\
-LID1273 & 1.697 & 53.3\%$\pm$9.1\% & 0.302$\pm$0.04 & 1.22$\pm$0.49 & $20.939\substack{+0.211 \\ -0.176}$ & 2.136592 & 6.4\%$\pm$0.8\% & $23.289\substack{+0.153 \\ -0.134}$\\
-LID1538 & 2.362 & 43.5\%$\pm$7.8\% & 0.177$\pm$0.042 & 2.819$\pm$0.475 & $21.251\substack{+0.221 \\ -0.184}$ & 2.172992 & 7.5\%$\pm$1.2\% & $23.088\substack{+0.189 \\ -0.161}$\\
-LID360 & 3.918 & 17.9\%$\pm$1.1\% & 0.629$\pm$0.018 & 0.672$\pm$0.04 & $21.483\substack{+0.068 \\ -0.064}$ & 4.913659 & 3.7\%$\pm$0.5\% & $23.254\substack{+0.172 \\ -0.149}$\\
-XID2138 & 1.597 & 39.7\%$\pm$6.1\% & 0.49$\pm$0.035 & 1.293$\pm$0.437 & $21.845\substack{+0.188 \\ -0.16}$ & 2.73139 & 5.0\%$\pm$1.3\% & $23.898\substack{+0.313 \\ -0.243}$\\
-XID2202 & 3.23 & 33.3\%$\pm$8.0\% & 0.1$\pm$0.001 & 3.957$\pm$1.017 & $21.16\substack{+0.302 \\ -0.236}$ & 3.851762 & 8.3\%$\pm$1.9\% & $22.592\substack{+0.286 \\ -0.226}$\\
-XID2396 & 3.669 & 23.9\%$\pm$10.5\% & 0.584$\pm$0.085 & 0.772$\pm$1.36 & $21.404\substack{+0.652 \\ -0.404}$ & 5.346128 & 2.3\%$\pm$0.5\% & $23.364\substack{+0.243 \\ -0.198}$\\
-CDFS-1 & 1.358 & 54.4\%$\pm$17.3\% & 0.158$\pm$0.077 & 4.574$\pm$1.387 & $22.656\substack{+0.414 \\ -0.299}$ & ... & ... & ...\\
-CDFS-229 & 4.329 & 17.6\%$\pm$2.1\% & 0.507$\pm$0.026 & 0.463$\pm$0.195 & $21.568\substack{+0.144 \\ -0.127}$ & ... & ... & ...\\
-CDFS-321 & 3.998 & 24.5\%$\pm$11.7\% & 0.378$\pm$0.122 & 2.26$\pm$2.007 & $20.337\substack{+0.703 \\ -0.423}$ & ... & ... & ...\\
-CDFS-724 & 1.355 & 34.7\%$\pm$14.6\% & 0.118$\pm$0.03 & 1.618$\pm$1.099 & $23.695\substack{+0.582 \\ -0.377}$ & ... & ... & ...\\
-ECDFS-358 & 2.012 & 56.4\%$\pm$13.5\% & 0.359$\pm$0.043 & 1.671$\pm$0.542 & $21.34\substack{+0.302 \\ -0.236}$ & ... & ... & ...\\
-SXDS-X1136 & 1.937 & 40.5\%$\pm$7.8\% & 0.101$\pm$0.003 & 1.986$\pm$0.483 & $21.921\substack{+0.231 \\ -0.19}$ & ... & ... & ...\\
-SXDS-X50 & 1.423 & 42.4\%$\pm$9.1\% & 0.184$\pm$0.041 & 1.755$\pm$0.655 & $21.943\substack{+0.266 \\ -0.214}$ & ... & ... & ...\\
-SXDS-X717 & 1.426 & 61.4\%$\pm$9.1\% & 0.264$\pm$0.066 & 5.58$\pm$1.421 & $21.759\substack{+0.176 \\ -0.151}$ & ... & ... & ...\\
-SXDS-X735 & 2.203 & 32.4\%$\pm$8.5\% & 0.22$\pm$0.057 & 2.027$\pm$1.012 & $20.919\substack{+0.333 \\ -0.254}$ & ... & ... & ...\\
-SXDS-X763 & 2.376 & 6.0\%$\pm$4.0\% & 0.694$\pm$0.532 & 2.394$\pm$0.796 & $24.134\substack{+1.172 \\ -0.55}$ & ... & ... & ...\\
-SXDS-X969 & 1.613 & 29.0\%$\pm$11.7\% & 0.115$\pm$0.026 & 2.149$\pm$1.147 & $21.594\substack{+0.553 \\ -0.365}$ & ... & ... & ...\\
+CID3242 & $2.751$ & $46.1\%\pm12.7\%$ & $0\farcs{}201\pm0\farcs{}159$ & $6.142\pm1.874$ & $21.161\substack{+0.35\\-0.264}$ & $2.596$ & $4.8\%\pm1.3\%$ & $23.595\substack{+0.337\\-0.257}$ \\
+CID3570 & $1.665$ & $76.5\%\pm1.6\%$ & $0\farcs{}698\pm0\farcs{}007$ & $0.728\pm0.054$ & $21.164\substack{+0.021\\-0.021}$ & $1.332$ & $85.6\%\pm1.5\%$ & $22.971\substack{+0.012\\-0.012}$ \\
+CID452 & $1.684$ & $75.4\%\pm3.9\%$ & $0\farcs{}365\pm0\farcs{}015$ & $1.402\pm0.175$ & $21.176\substack{+0.063\\-0.06}$ & $1.452$ & $37.8\%\pm0.7\%$ & $22.732\substack{+0.022\\-0.022}$ \\
+CID454 & $2.203$ & $35.8\%\pm2.5\%$ & $0\farcs{}388\pm0\farcs{}016$ & $0.624\pm0.106$ & $21.196\substack{+0.08\\-0.074}$ & $1.291$ & $9.2\%\pm0.5\%$ & $23.352\substack{+0.058\\-0.055}$ \\
+CID50 & $5.576$ & $16.5\%\pm9.0\%$ & $0\farcs{}163\pm0\farcs{}11$ & $3.217\pm2.223$ & $20.934\substack{+0.863\\-0.475}$ & $4.940$ & $5.0\%\pm3.3\%$ & $22.504\substack{+1.145\\-0.545}$ \\
+CID543 & $1.902$ & $30.6\%\pm9.7\%$ & $0\farcs{}1\pm0\farcs{}0$ & $0.493\pm0.325$ & $21.994\substack{+0.406\\-0.295}$ & $1.435$ & $5.2\%\pm2.0\%$ & $23.765\substack{+0.534\\-0.357}$ \\
+CID597 & $1.565$ & $42.4\%\pm16.6\%$ & $0\farcs{}173\pm0\farcs{}058$ & $1.752\pm0.784$ & $21.868\substack{+0.543\\-0.36}$ & $1.254$ & $11.5\%\pm1.3\%$ & $23.563\substack{+0.126\\-0.113}$ \\
+CID607 & $1.692$ & $43.6\%\pm17.9\%$ & $0\farcs{}206\pm0\farcs{}087$ & $3.418\pm1.097$ & $21.189\substack{+0.575\\-0.374}$ & $2.590$ & $4.7\%\pm1.8\%$ & $23.566\substack{+0.511\\-0.346}$ \\
+CID70 & $2.041$ & $19.7\%\pm4.9\%$ & $0\farcs{}422\pm0\farcs{}095$ & $3.616\pm1.028$ & $21.862\substack{+0.304\\-0.237}$ & $2.361$ & $2.3\%\pm1.1\%$ & $24.625\substack{+0.677\\-0.414}$ \\
+LID1273 & $1.697$ & $53.3\%\pm9.1\%$ & $0\farcs{}302\pm0\farcs{}04$ & $1.22\pm0.49$ & $20.939\substack{+0.211\\-0.176}$ & $2.137$ & $6.4\%\pm0.8\%$ & $23.289\substack{+0.153\\-0.134}$ \\
+LID1538 & $2.362$ & $43.5\%\pm7.8\%$ & $0\farcs{}177\pm0\farcs{}042$ & $2.819\pm0.475$ & $21.251\substack{+0.221\\-0.184}$ & $2.173$ & $7.5\%\pm1.2\%$ & $23.088\substack{+0.189\\-0.161}$ \\
+LID360 & $3.918$ & $18.4\%\pm2.0\%$ & $0\farcs{}626\pm0\farcs{}02$ & $0.752\pm0.355$ & $21.455\substack{+0.136\\-0.121}$ & $4.914$ & $3.7\%\pm0.5\%$ & $23.254\substack{+0.172\\-0.149}$ \\
+XID2138 & $1.597$ & $38.9\%\pm5.5\%$ & $0\farcs{}498\pm0\farcs{}033$ & $1.24\pm0.391$ & $21.869\substack{+0.172\\-0.148}$ & $2.731$ & $5.0\%\pm1.3\%$ & $23.898\substack{+0.313\\-0.243}$ \\
+XID2202 & $3.23$ & $33.3\%\pm8.0\%$ & $0\farcs{}1\pm0\farcs{}001$ & $3.957\pm1.017$ & $21.16\substack{+0.302\\-0.236}$ & $3.852$ & $8.3\%\pm1.9\%$ & $22.592\substack{+0.286\\-0.226}$ \\
+XID2396 & $3.669$ & $23.9\%\pm10.5\%$ & $0\farcs{}584\pm0\farcs{}085$ & $0.772\pm1.36$ & $21.404\substack{+0.652\\-0.404}$ & $5.346$ & $2.3\%\pm0.5\%$ & $23.364\substack{+0.243\\-0.198}$ \\
+CDFS-1 & $1.358$ & $64.5\%\pm19.7\%$ & $0\farcs{}137\pm0\farcs{}069$ & $4.806\pm1.112$ & $22.468\substack{+0.397\\-0.29}$ & ... & ... & ... \\
+CDFS-229 & $4.329$ & $17.6\%\pm2.1\%$ & $0\farcs{}507\pm0\farcs{}026$ & $0.463\pm0.195$ & $21.568\substack{+0.144\\-0.127}$ & ... & ... & ... \\
+CDFS-321 & $3.998$ & $24.5\%\pm11.7\%$ & $0\farcs{}378\pm0\farcs{}122$ & $2.26\pm2.007$ & $20.337\substack{+0.703\\-0.423}$ & ... & ... & ... \\
+CDFS-724 & $1.355$ & $34.7\%\pm14.6\%$ & $0\farcs{}118\pm0\farcs{}03$ & $1.618\pm1.099$ & $23.695\substack{+0.582\\-0.377}$ & ... & ... & ... \\
+ECDFS-358 & $2.012$ & $56.4\%\pm13.5\%$ & $0\farcs{}359\pm0\farcs{}043$ & $1.671\pm0.542$ & $21.34\substack{+0.302\\-0.236}$ & ... & ... & ... \\
+SXDS-X1136 & $1.937$ & $40.5\%\pm7.8\%$ & $0\farcs{}101\pm0\farcs{}003$ & $1.986\pm0.483$ & $21.921\substack{+0.231\\-0.19}$ & ... & ... & ... \\
+SXDS-X50 & $1.423$ & $40.7\%\pm8.6\%$ & $0\farcs{}192\pm0\farcs{}04$ & $1.648\pm0.621$ & $21.988\substack{+0.267\\-0.214}$ & ... & ... & ... \\
+SXDS-X717 & $1.426$ & $61.4\%\pm9.1\%$ & $0\farcs{}264\pm0\farcs{}066$ & $5.58\pm1.421$ & $21.759\substack{+0.176\\-0.151}$ & ... & ... & ... \\
+SXDS-X735 & $2.203$ & $32.4\%\pm8.5\%$ & $0\farcs{}22\pm0\farcs{}057$ & $2.027\pm1.012$ & $20.919\substack{+0.333\\-0.254}$ & ... & ... & ... \\
+SXDS-X763 & $2.376$ & $6.0\%\pm4.0\%$ & $0\farcs{}694\pm0\farcs{}532$ & $2.394\pm0.796$ & $24.134\substack{+1.172\\-0.55}$ & ... & ... & ... \\
+SXDS-X969 & $1.613$ & $29.1\%\pm11.1\%$ & $0\farcs{}11\pm0\farcs{}019$ & $2.053\pm1.071$ & $21.591\substack{+0.515\\-0.348}$ & ... & ... & ... \\
 \enddata
@@
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1281_SB_profile.pdf}
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID206_SB_profile.pdf}
@@
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID454_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID50_SB_profile.pdf}
 }
@@
 {
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID50_SB_profile.pdf}
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID543_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID597_SB_profile.pdf}
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID607_SB_profile.pdf}
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID70_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2138_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2202_SB_profile.pdf}
 }
@@
 {
+\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2138_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2202_SB_profile.pdf}
 \includegraphics[height=0.25\textwidth]{fig/best_fit_XID2396_SB_profile.pdf}
@@
 \includegraphics[height=0.25\textwidth]{fig/best_fit_LID1538_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_LID360_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X1136_SB_profile.pdf}
 }
@@
 {
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X50_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X717_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X735_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X763_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X969_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_LID360_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-1_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-229_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-321_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-724_SB_profile.pdf}
 }
@@
 {
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-1_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-229_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-321_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-724_SB_profile.pdf}
 \includegraphics[height=0.25\textwidth]{fig/best_fit_ECDFS-358_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X1136_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X50_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X717_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X735_SB_profile.pdf}
+}
+\figurenum{1}
+\caption{Continued.}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X763_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X969_SB_profile.pdf}
 }

### 2018-12-07 M_BH_relation/ML_all_vz.py

@@ -322,5 +322,5 @@ else:
     "local AGNs",\
     "our new samples"
     ],scatterpoints=1,numpoints=1,loc=2,prop={'size':23},ncol=2,handletextpad=0)
-plt.savefig("MBHL-z.pdf")
+#plt.savefig("MBHL-z.pdf")
 plt.show()

### 2018-12-07 analysis_Astrodrz/library_PSF.py

@@ -76,7 +76,7 @@ common_params = dict(bins=30)
 plt.hist((fluxs), **common_params)
 plt.legend()
 plt.xticks(np.arange(0, 4500, step=500))
-plt.yticks(np.arange(0,65,step=5))
+plt.yticks(np.arange(0,40,step=5))
 plt.xlabel('Total Flux (counts)',fontsize=15)
 plt.ylabel('Number of PSFs', fontsize=15)
 plt.tick_params(labelsize=15)

### 2018-12-07 analysis_Astrodrz/overall_fit_result.py

@@ -20,7 +20,7 @@ ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'CDFS-321', 'CID1174
 'SXDS-X50', 'SXDS-X717','SXDS-X763','SXDS-X969','XID2138','XID2202',\
 'XID2396', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597', 'CID1281'\
 ]
-#ID = ['CID1174']
+#ID = ['CID1281']
 
 import pickle
 ratio_results, Re_results, n_results, total_flux_results, host_amp_results = [], [], [], [], []
@@ -61,8 +61,10 @@ for j in range(len(ID)):
     for i in sort_Chisq[:count_n]:
         weight[i] = np.exp(-1/2. * (Chisq[i]-Chisq_best)/(Chisq_best* inf_alp))
 #    for i in sort_Chisq:
-#        print PSF_id[i], Chisq[i], weight[i], host_flux_ratio[i], Re[i], S_n_list[i], round(total_flux[i],3),  round(host_amp[i],3),\
-    round(flux_dict[PSF_id[i]],3), round(FWHM_dict[PSF_id[i]],3), "[{0},{1}]".format(int(round(locs_dict[PSF_id[i]][0])) , int(round(locs_dict[PSF_id[i]][1]))), round(id_stars_dict[PSF_id[i]],3)
+##        print PSF_id[i], Chisq[i], weight[i], host_flux_ratio[i], Re[i], S_n_list[i], round(total_flux[i],3),  round(host_amp[i],3),\
+##    round(flux_dict[PSF_id[i]],3), round(FWHM_dict[PSF_id[i]],3), "[{0},{1}]".format(int(round(locs_dict[PSF_id[i]][0])) , int(round(locs_dict[PSF_id[i]][1]))), round(id_stars_dict[PSF_id[i]],3)
+#        print i, round(Chisq[i],3), round(weight[i],3),round(host_amp[i],3), round(host_flux_ratio[i],1),round(Re[i], 3), round(S_n_list[i],3)
+
     # =============================================================================
     # Weighting result
     # =============================================================================
@@ -108,7 +110,6 @@ for i in range(len(ID)):
         s = 's'
     ax.errorbar(Re_results[i][0], ratio_results[i][0], xerr= Re_results[i][1], yerr=ratio_results[i][1],
                 fmt=s, color=colors[i],ecolor='gray' )
[…]

### 2018-12-07 material/creat_table_for_manscript.py

@@ -111,9 +111,11 @@ WFC3_list = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'CDFS-321', '
     
 ACS_IDs = ['CID1174','CID216', 'CID50','CID70','XID2138','CID3242',\
 'LID1273','XID2202','CID206','CID3570','CID543','LID1538','XID2396','CID452',\
-'LID360','CID237','CID454','CID607']     
+'LID360','CID237','CID454','CID607', 'CID597', 'CID1281']     
 
 tab_list = ['CID1174', 'CID1281', 'CID206', 'CID216', 'CID237', 'CID255', 'CID3242', 'CID3570', 'CID452', 'CID454', 'CID50', 'CID543', 'CID597', 'CID607', 'CID70', 'LID1273', 'LID1538', 'LID360', 'XID2138', 'XID2202', 'XID2396', 'CDFS-1', 'CDFS-229', 'CDFS-321', 'CDFS-724', 'ECDFS-358', 'SXDS-X1136', 'SXDS-X50', 'SXDS-X717', 'SXDS-X735', 'SXDS-X763', 'SXDS-X969']
+
+'''
 filt_list, ACS_list = [],[]
 z_list = []
 IR_result, UV_result = [], []
@@ -139,7 +141,15 @@ for i in range(len(tab_list)):
     if UV_result[i]=='xxx':
         UV_result[i] = [np.asarray(UV_result[0][j])*0-99 for j in range(len(UV_result[0]))]
     print(tab_list[i], round(IR_result[i][-1],3),
-    "{0}%pm{1}%".format(round(IR_result[i][0][0],1), round(IR_result[i][0][1],1)))
+    "{0}%pm{1}%".format(round(IR_result[i][0][0],1), round(IR_result[i][0][1],1)),  #host flux ratio
+    "{0}pm{1}".format(round(IR_result[i][1][0],3), round(IR_result[i][1][1],3)),  #host Re
+    "{0}pm{1}".format(round(IR_result[i][2][0],3), round(IR_result[i][2][1],3)),  #host n
+    "{0}+{1}-{2}".format(round(IR_result[i][5],3), round(IR_result[i][6][0],3),round(IR_result[i][6][1],3)),  #host mag, l, h
+    UV_result[i][-1],
+    "{0}%pm{1}%".format(round(UV_result[i][0][0],1), round(UV_result[i][0][1],1)),  #host flux ratio
[…]

### 2018-12-12 manuscript/manuscript.tex
go again through the paper

@@
 
-\author{Xuheng Ding\altaffilmark{1, 2}, Tommaso Treu\altaffilmark{2}, John Silverman\altaffilmark{5}, Simon Birrer\altaffilmark{3}, Malte Schramm\altaffilmark{2}, Federica, Angelea
+\author{Xuheng Ding\altaffilmark{1, 2}, Tommaso Treu\altaffilmark{1}, John Silverman\altaffilmark{3}, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, Simon Birrer\altaffilmark{1}, Malte Schramm\altaffilmark{6}, Andreas Schulze\altaffilmark{6}
  }
  \email{dxh@astro.ucla.edu}
-% Dandan Xu, Giulia, Anupreeta, Chih-Fan, Daniel, Chris, Phil Marshall, Dominique,
-
-\altaffiltext{1}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
-\altaffiltext{2}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
-\altaffiltext{3}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
-\altaffiltext{4}{Department of Physics, University of California, Davis, CA 95616, USA}
-\altaffiltext{5}{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
+\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
+\altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
+\altaffiltext{3}{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
+\altaffiltext{4}{Dipartimento di Matematica e Fisica, Università Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
+\altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
+\altaffiltext{6}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
 
 \begin{abstract}
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
+To be written.
 To be written.
@@
 \label{sec:introduction}
-%skeleton of introduction
-%\\
-%1. Introduce the ML relation and why understand its evolution is important.\\
-%2. To understand this evolution, it is important to trace to high redshift. Why it is difficult.\\
-%3. The 4000A by HST band.
-%3. Introduce reference. Woo's. SS13, Treu's, Park79. In the theory, DeGraf...Highlight the redshift range $z>1.2$. Recent works by H0liCOW7\\
-%4. In this paper, we study the ML relation up to redshift 1.7.
+%\citep[e.g.,][]{Park15,Kormendy13}
 
-Most galactic nuclei harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh- stellar mass (\smass)  and \mbh-stellar velocity dispersion(\sigstar).
-These tight correlations indicates a connection between nuclear activity and galaxy formation and evolution.
+Most galactic nuclei harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar).
+These tight correlations indicates a connection between nuclear activity and galaxy formation and evolution\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
 Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy.
-In theory, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver.
-However, for a different view, \textcolor{blue}{Peng 2007 and Jahnke 2011} show that, without the need of a physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.
+On the other hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
+However, for a different view, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.
 
-One key is to trace their correlation to higher redshift, determining how and when they emerged and evolved over cosmic time.
+One key is to trace their correlation to higher redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}.
 During past decade, there has been much progress on our understand at $z<1$ using the type 1 AGN.
-The work by \textcolor{blue}{Park, Treu, Woo, P06, H0licow7} demonstrated that, \mbh\ are elevated as compared to the bulge luminosity from the local relations, thus indicating that the supermassive BHs were built up first with galaxy then growing around their deep potential wells.
-Similarly, the recent works by \textcolor{blue}{Bennert et al.
-2011, Woo 2008} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations.
-Nevertheless, some studies are consistent with no evolution \textcolor{blue}{Schramm+Silverman 2013, Sun et al.
-2015, Cisternas et al.
-2011}.
+The work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that, \mbh\ are elevated as compared to the bulge luminosity from the local relations, thus indicating that the supermassive BHs were built up first with galaxy then growing around their deep potential wells.
+Similarly, the works by \citet{Bennert11, Woo++08} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations.
+Nevertheless, some studies are consistent with no evolution \citet{SS13, Sun2015, Cisternas2011}.
 
@@
 First, the inherent uncertainties in BH mass estimates using the virial method.
-Especially, many studies rely on \mbh\ estimates using the \Mgii\ or \Civ\ line that may have unknown systematics when compared to local samples with masses based on broad Balmer lines (i.e.
-\halpha\ and \hbeta).
+Especially, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e.
+\halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}.
 Second, since the host information is swamped by the bright nuclear light, measurement systematics exist in the host galaxy properties.
-It is worth noting that strong gravitational lensing provides a unique opportunity to make progress in the study by extend the host image to lensed arcs \textcolor{blue}{H0licow6, Peng06, H0licow7}.
+It is worth noting that strong gravitational lensing provides a unique opportunity to make progress in the study by extend the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}.
 Equally important,
 the selection effects and their impact on the observed need to be taken well into account.
-For instance, it has been demonstrated \textcolor{blue}{Schulze + Wisotzki (2011, 2014))} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample.
-Even considering this selection effect, an evolution of the scaling relations is expected from simulations \textcolor{blue}{DeGraf et al.
-(2015} and with respect to the bulge mass.
+For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample.
+Even considering this selection effect, an evolution of the scaling relations is expected from simulations \citep{DeG++15} and with respect to the bulge mass.
 
-To make progress, on one hand, it is essential to making use of a larger sample of high-quality data in respect of the measurement of both the host properties and the \mbh.
-On the other hand, extending the correlations to higher redshift ($z>1$) would effectively improves the statistics, where the \mbh-\lhost\ is steeper than the current observational measurements at lower redshift, before self-regulation slows the black hole growth and galaxies settle onto the local mass relation.
+To make progress, it is essential to make use of the larger sample of high-quality data in respect of the measurement of both the host properties and the \mbh.
+On the other hand, extending the correlations to higher redshift ($z>1$) would effectively improves the statistics, where the \mbh-\lhost\ is steeper than the current observational measurements at lower redshift, before self-regulation slows the black hole growth and galaxies settle onto the local mass relation \citep{DeG++15}.
 
-In this study, we aim to determine whether AGN have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \textcolor{blue}{(Aird et al.
-2015)}.
-At this redshift range, we measure 32 host galaxies properties using \hst/WFC3 imaging data and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS.
+In this study, we aim to determine whether AGN have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.
+At this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS.
 Our study overcomes the biases in the following way.
 First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function.
-Second, we estimate \mbh\ using Balmer lines which avoid the systematics by \Mgii.
+Second, we estimate \mbh\ using Balmer lines which avoids the systematics by \Mgii.
 Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements.
-Moreover, 21/32 systems of our sample also have \hst/ACS-F814W image.
-The multi-band information provide reliable K-correction and stellar mass inference.
-Given the high-quality data at such redshift, we test whether the growth of BH predates that of the host by a factor of at least $1.7 (\sim0.23$ dex).
+Moreover, 21/32 systems of our sample have two-band \hst\ data (i.e.
+WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference.
+Given the high-quality data at such redshift, we test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex).
 
@@
 
-Our final sample is composed of 36  AGNs; 32 of them are new observations by HST/WFC3 \textcolor{red}{\bf (32+4?, the information of these four sample?)}.
+Our final sample is composed of 36  AGNs; 32 of them are new observations by HST/WFC3 \textcolor{blue}{\bf (32+4?, the information of these four sample?)}.
 Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.
 
-To compare with the samples in the literature, we adopt the samples from ... \textcolor{blue}{\bf (H0licow7)}.
 For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point.
+
+To compare with the samples in the literature, we also adopt the samples from \citet{Ding2017b}, which includes the measurements by \citet{Pen++06qsob, Park15} to study the \mbh-\lhost\ of 127 objects by \hst.
 
@@
 total exposure time $\sim2394s$).
-The six exposures for each dither image were combined by the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter of 0.8 and a \texttt{gaussian} kernel.
-The other four AGNs in our sample have been observed with WFC3 serendipitously (2 in COSMOS from Kartaltepe (PI); PID: 13657).
-The noise level maps of the imaging data are a requirement in the study.
-The origin of the noise in each pixel is stems from the read noise, background noise and Poisson noise by the astronomical sources themselves.
-To take them into account, we measure the read noise and background noise level directly from the empty regions of the data.
-We calculate the effective exposure time in each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level.
-To accurately measure the photometry, we also adopt the {\sc photutils} to estimate the background light which could come from both the sky and the detector.
+The six exposures for each dither image were combined by the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter of 0.8 with a \texttt{gaussian} kernel.
+\textcolor{blue}{The other four AGNs in our sample have been observed with WFC3 serendipitously (2 in COSMOS from Kartaltepe (PI); PID: 13657).}
+To accurately estimate the background light which could come from both the sky and the detector, we also adopt the {\sc photutils} to measure the photometry.
 
@@
 
-21/32 of our sample have rest-frame UV images by \textcolor{blue}{Scoville, et al. 2007} %arxiv: 0702359}.
+21/32 of our sample have rest-frame UV images by \citet{Scoville2007}. %arxiv: 0702359}.
 Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures.
 The final image is drizzled to 0\farcs{03} pixel scale.
-Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population to the stellar mass budge \textcolor{blue}{citet Gallazzi+Bell 2009} which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR).
+Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population to the stellar mass budge \citet{Gallazzi2009} which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR).
 
@@
 % The introduction of the BH inferred by the board emission line.
-The \mbh\ of type-1 AGNs can be inferred using the so-called virial method.
-The kinematics of the broad-line region trace the gravitational field of the central black hole, assuming the motion of the broad-line region (BLR) gas is virialised.
+The \mbh\ of type-1 AGNs can be inferred using the so-called virial method \citep{Peterson2004, Shen2013}.
+The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the motion of the BLR gas is virialised by the gravity.
 In this scenario, the width of the emission-line provide the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size.
-The virial method builds on these reverberation mapping results and is directly calibrated to the \mbh.
+As a result, the estimation of the \mbh\ is achieved by these measurements.
 
@@
 We referred to this paper for the details of continuum fitting and emission line modeling.
-Since the other compared AGNs in the literature used different calibrations of the virial method, we adopt the list of consistent recipes \textcolor{blue}{McGill et al.
-(2008), H0licow7} to cross-calibrate the \mbh\ for all the samples in order to avoid any systematic bias in Section~\ref{mbh}.
+Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt the list of consistent ones to cross-calibrate the \mbh\ for all the samples in order to avoid any systematic bias in Section~\ref{mbh}.
 
@@
 %Introduce the PSF library
-The knowledge of the PSF is crucial for this study, especially when the nuclear image is unresolved with light distributed as the point source.
-Moreover, the PSF in known to be vary according to their frame position and the intensity.
-Thus, we build a library of PSFs which we select the bright, isolated, unsaturated PSF stars across all the observed field.
-Thanks to the available multi-wavelength data \textcolor{blue}{(Laigle et al.
-2016)}, we are able to know the positions of stars nearby the QSO field and thus select a proper position and orientation of the HST frame to cover as much PSFs stars as possible.
+The knowledge of the PSF is crucial for the QSO imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source.
+The PSF is known to be varied with different frame position and the intensity, due to the effect of aberrations.
+The simulated PSF, such as {\sc TinyTim} ones, are usually poor matches to observations \citet{Mechtley2012}.
+Empirical PSF stars are considered better than the simulated ones, since they we observed simultaneously with the science target which were reduced and analyzed in the same way \citet{Kim2008, Park15}
 
-We claim that, by building this library, the assumption is that the overall PSFs herein indicates all the possible PSF shape for each QSO.
-Since two filter, i.e.
-F140W and F125W, are selected for different samples, we selected 78 and 36 PSFs for the samples observed by F140W and F125W, respectively.
+To minimize the impact of the mismatch, we build a PSF library by cutting out the isolated, unsaturated PSF stars with high S/N from the overall QSO field.
+We first collect the identified stars as candidates which are listed in the COSMOS2015 catalog by \citet{Laigle2016}.
+However, since a lot of bright stars with intensity similar to the QSOs are excluded by \citet{Laigle2016}, we visually select these star-like PSF as candidates.
+Finally, we remove the non-ideal PSF candidates by inspecting their intensity, FWHM, central symmetry and any that were contaminated by background objects.
+To summarize, we selected 78 and 36 PSFs from the field observed by filter F140W and F125W, respectively.
 
+We stress that, by building this library, we assume that the PSFs herein bracket all the possible PSF light distribution which fits our imaging data.
+Therefore, the inference from each PSF will include the true answer.
 In the next subsection, we carry out the QSO decomposition using each PSF.
-We rank their performance based on the goodness so that the final inference of the host properties are weighted from the top-rank PSFs.
+We rank their performance based on the goodness (i.e.
+$\chi^2$) so that the final inference of the host properties are weighted from the top-rank PSFs.
 
-\subsubsection{Surface Photometry modeling method}
+%\subsubsection{Surface Photometry modeling method}
+\subsubsection{AGN-host Decomposition}
 %Introduce the lenstronomy. Model the PSF in each library.\\
@@
 We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underling host galaxy.
-Following common practice, we assume the unresolved nuclear as a scaled PSF image, while the host galaxy as a \sersic\ profile.
+Following common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile.
 Note that the actual morphologies of the host galaxies could be even more complicated (e.g.
@@
 However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux given the high redshift range of our sample.
-We fit the objects which close to the QSO as the another \sersic\ model, to minimize the impact of their light.
+Furthermore, we fit the galaxies which close to the QSO as the \sersic\ model, to account for the contamination of their light.
 
 %Introduce Lenstronomy:
-We adopt the imaging modeling tool \lenstronomy\ \textcolor{blue}{(arXiv:1803.09746)}, to decompose the host and nuclear image.
+We adopt the imaging modeling tool \lenstronomy\ \citep{lenstronomy}, to decompose the host and nuclear light.
 The \lenstronomy\ is a multi-purpose open-source gravitational lens modeling python package.
-The flexibility of this package enable us to turn off the lensing channel and carry out the decomposition.
-We have tested that the inference by \lenstronomy\ could have consistent result compared to {\sc Galfit}. \textcolor{red}{Will talk more in this part.}
+The flexibility of this package enable us to turn off the lensing channel and carry out this task\footnote{For a sanity check, we compared the performance of \lenstronomy\ to the most commonly used galaxy modelling software {\sc Galfit} and confirm that the consistent result could be obtained with the same fitting ingredients provided.}.
+The input ingredients to \lenstronomy\ includes:
+\begin{enumerate}
+\item \hst\ AGN imaging data.
+-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ cover sufficient QSO light our samples.
+By default, we cut out the AGN image to a $61\times61$ pixels box (i.e.
+$4''\times 4''$).
+\item Noise level map -- The origin of the noise in each pixel is stems from the read noise, background noise and Poisson noise by the astronomical sources themselves.
+To take them into account, we measure the read noise and background noise level directly from the empty regions of the data.
+We calculate the effective exposure time in each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level.
+\item PSF -- The PSF are directly taken from the PSF library.
+Usually, mismatch exists when subtract the AGN as the scaled PSF, especially at the central parts.
+We assume that the overall inference based on each PSF bracket the best one as one can obtain, given the flexibility of the library.
+We also note that, in the lens modelling, this mismatch can be mitigated with PSF reconstruction by the iterative method \citep{Chen2016, Birrer2018}.
+However, this approach collects the information of the lensing feature which is not suitable to our case.
+If one forces to perform the PSF reconstruction, the iterative correction would absorb all mismatch information, result in a biased host inference.
+\end{enumerate}
 
 %Introduce the final inference using fitting:
-For each QSO system, the final host properties is inferred in several steps.
+Focusing on each QSO system, its host light information is inferred through several steps.
 First, we fit the flux distribution using each PSFs in the library.
-Given the QSO imaging data, PSF and noise level, we are able to infer the posterior distribution in the parameter space and optimize the best-fit parameters with minimized residuals.
-In this step, we infer the best-fit parameters for each PSFs in the library and the corresponding $\chi^2$ value\footnote{The \lenstronomy\ enable one to infer also the parametric confidence interval.
+Given the fitting ingredients, we are able to infer the posterior distribution in the parameter space and optimize the best-fit parameters with minimized residuals.
+In this step, we apply the Particle Swarm Optimizer (PSO) to optimize the best-fit parameters based on the imaging likelihood.
+Running through the library, we record the inference based on each PSF together with the corresponding $\chi^2$ value\footnote{The \lenstronomy\ enable one to infer also the parametric confidence interval.
 However, given a fixed PSF image, the $1-\sigma$ region of each parameter are extremely narrow}.
-In the second step, we rank the performance of each PSF based on the reduced $\chi^2$ value and select the top-8 PSFs so as to weight for the inferred property.
+In the second step, we rank the performance of each PSF based on the $\chi^2$ value and select the top-8 PSFs so as to weight for the inferred property.
 The weights for each PSF is calculated by:
@@
 \label{eq:weights}
-w_i = exp \big(-\frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2\alpha \chi_{best} ^2} \big),
+w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
 \end{eqnarray} 
@@
 \end{eqnarray} 
+Note that since each QSO system has different seeing condition, the top-8 PSFs are different for each system.
 
 %ECDFS-358 and CID206
-
-In Figure~\ref{fig:QSO_decomp}, we demonstrate the optimized result of each system inferred by \lenstronomy.
-We also show the weighting process for an example system -- CID1174 in Table~\ref{tab:weight_CID1174}.
-In Figure~\ref{fig:flux_r_n_corner}, we summarize the relation among the inferred values of: \Reff, \sersic\ $n$, and host to total flux ratio.
+In Figure~\ref{fig:QSO_decomp}, we demonstrate the optimized results inferred by \lenstronomy.
+In each, we show the images, best-fit models, image subtract point source (i.e.
+host) and the residuals for every systems.
+As an example, we also show the weighting process for system CID1174 in Table~\ref{tab:weight_CID1174}.
+To quickly overview our inference, we summarize them as relations between: 1) effective radius \Reff, 2) \sersic\ index $n$ and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.
 
 %The inference of F814w data.
-Likewise, for the 18 systems with ACS/F184W images, we infer their host properties using the same approach.
-There are in total 174 star-like PSFs in the fitting library.
-We assumed the shape of the galaxy are consistent between the ACS and WFC3.
-Since the effects of dust extinction and contrast between the (blue) AGN and (red) host is more favorable in IR band, we believe the inferred information of the galaxy shape by IR band are superior to the one by UV band.
-Thus, while fitting the host flux at ACS band, we fix the \Reff\ and \sersic\ $n$ to the value by IR.
+18/32 systems in COSMOS field have ACS/F184W imaging data.
+Likewise, we infer their host properties using the same approach.
+The field of view by ACS are larger than WFC3, and we collected in total 174 ACS PSFs in the library.
+While fitting the host light, we fix the \Reff\ and \sersic\ $n$ as the value inferred by WFC3/IR, assuming that the shape of the galaxy are consistent between ACS and WFC3.
+We believe the inferred information of the galaxy shape by IR imaging are superior to the one by UV band, considering the effects of dust extinction and contrast between the (blue) AGN and (red) host is more favorable in IR band.
 
@@
 
+\subsubsection{Host luminosity}
 %The overall fitting plot: 1. Host-R-n corner for f140w and f814w. 2. The histogram with different selection.
-
-\subsubsection{Host luminosity}
 \textcolor{red}{To be written:}
@@
 \label{mbh}
-Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g.
+ %Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g.
 McLure 2002; Shen 2013)}.
 This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
-
-To avoid any systematic bias between our samples and the literature samples, we cross-calibrate the \mbh\ by adopting the self-consistent recipes as used by \textcolor{blue}{H0licow7, McGill et al.
-(2008)}.
-Overall, we adopt the following virial formalism for the \halpha\ and \hbeta\ emission line:
-
+To avoid any systematic bias between our samples and the literature ones, we compared the recipes as used by \citet{Schulze2018, Ding2017b}.
+We find that the \hbeta\ estimator are very close between the two reference.
+Moreover, in \citet{Schulze2018}, the cross-calibrate between the \halpha\ and \hbeta\ are consistent.
+Therefore, we directly adopt virial formalism from \citet{Schulze2018}:
 \begin{eqnarray}

### 2019-01-14 manuscript/manuscript.tex
update for the paper draft

@@
 
-\shorttitle{ShortTitle}
+\shorttitle{Cosmic evolution of the \mbh-host relation}
 \shortauthors{X. Ding et al.}
@@
 
-\title{QSO decomposition}
+\title{Cosmic evolution of the correlation between supermassive black hole mass and host galaxy at redshift up to 1.7}
 
-\author{Xuheng Ding\altaffilmark{1, 2}, Tommaso Treu\altaffilmark{1}, John Silverman\altaffilmark{3}, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, Simon Birrer\altaffilmark{1}, Malte Schramm\altaffilmark{6}, Andreas Schulze\altaffilmark{6}
+\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{2}, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{2}, Knud Jahnke, et al.
  }
  \email{dxh@astro.ucla.edu}
-\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
-\altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
+\altaffiltext{1}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
+\altaffiltext{2}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
 \altaffiltext{3}{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
@@
 \begin{abstract}
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
+We investigate the cosmic evolution of the relation supermassive black hole and host galaxy properties at $1.2<z<1.7$, using a sample of 32 X-ray selected type-1 AGN obtained with the Hubble Space Telescope (\hst).
+The high-resolution \hst\ images enable us to decompose the AGN image and infer the host properties including luminosities (\lhost) and stellar masses (\smass).
+We estimate the BH masses (\mbh) with spectroscopic information of the \halpha, \hbeta.
+We compare the \mbh-\lhost and \mbh-\smass relation to the local active galaxies and taking the selection effects into account.
+Results to be written.
 To be written.
@@
 Most galactic nuclei harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar).
-These tight correlations indicates a connection between nuclear activity and galaxy formation and evolution\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
+These tight correlations indicates a connection between nuclear activity and galaxy formation and evolution \citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
 Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy.
 On the other hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
-However, for a different view, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.
+However, for a different view, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.
 
-One key is to trace their correlation to higher redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}.
-During past decade, there has been much progress on our understand at $z<1$ using the type 1 AGN.
-The work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that, \mbh\ are elevated as compared to the bulge luminosity from the local relations, thus indicating that the supermassive BHs were built up first with galaxy then growing around their deep potential wells.
+One key to this study is tracing their correlation to higher redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}.
+During the past decade, there has been much progress on our understanding at $z<1$ using the type 1 AGN.
+The work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that, \mbh\ is elevated as compared to the bulge luminosity from the local relations, thus indicating that the supermassive BHs were built up first with galaxy then growing around their deep potential wells.
 Similarly, the works by \citet{Bennert11, Woo++08} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations.
@@
 
-Despite the great amount of effort, there are still uncertainties stems from different aspects which could lead to the inconsistency among these works.
+Despite the enormous amount of effort, there are still uncertainties stems from different aspects which could lead to the inconsistency among these works.
 First, the inherent uncertainties in BH mass estimates using the virial method.
@@
 Second, since the host information is swamped by the bright nuclear light, measurement systematics exist in the host galaxy properties.
-It is worth noting that strong gravitational lensing provides a unique opportunity to make progress in the study by extend the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}.
-Equally important,
-the selection effects and their impact on the observed need to be taken well into account.
+It is worth noting that strong gravitational lensing provides a unique opportunity to make progress in the study by extending the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}.
+Equally important, the selection effects and their impact on the observed need to be taken well into account.
 For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample.
@@
 
-To make progress, it is essential to make use of the larger sample of high-quality data in respect of the measurement of both the host properties and the \mbh.
-On the other hand, extending the correlations to higher redshift ($z>1$) would effectively improves the statistics, where the \mbh-\lhost\ is steeper than the current observational measurements at lower redshift, before self-regulation slows the black hole growth and galaxies settle onto the local mass relation \citep{DeG++15}.
+To make progress, it is essential to make use of the larger sample to high-quality data in respect of the measurement of both the host properties and the \mbh.
+On the other hand, extending the correlations to higher redshift ($z>1$) would effectively improve the statistics, where the \mbh-\lhost\ is steeper than the current observational measurements at lower redshift, before self-regulation slows the black hole growth and galaxies settle onto the local mass relation \citep{DeG++15}.
 
-In this study, we aim to determine whether AGN have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.
+In this study, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.
 At this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS.
@@
 
-We aim to study the relation between the BH masses (\mbh) and their host galaxy properties including luminosities (\lhost) and stellar mass to redshift at $z>1$.
+We aim to study the relation between the BH masses (\mbh) and their host galaxy properties including luminosities (\lhost) and stellar mass (\smass) to redshift at $z>1$.
 For this propose, we focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS \citep{Civano2016}, (E)-CDFS-S \citep{Lehmer2005, Xue2011}, and SXDS \citep{Ueda2008} fields.
@@
 The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$ \citep{Greene2005, Matsuoka2013, Nobuta2012}.
-
-Our final sample is composed of 36  AGNs; 32 of them are new observations by HST/WFC3 \textcolor{blue}{\bf (32+4?, the information of these four sample?)}.
+Overall, our final sample is composed of 32 new observations by HST/WFC3.
 Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.
@@
 For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point. 
-
 To compare with the samples in the literature, we also adopt the samples from \citet{Ding2017b}, which includes the measurements by \citet{Pen++06qsob, Park15} to study the \mbh-\lhost\ of 127 objects by \hst.
@@
 \subsubsection{HST image Observation}
-% The QSO surface photometry in IR Channel Filters.\\
-The high spatial resolution of the host image is required for the decomposition of the nuclear/host emission and the accurate estimate of the stellar of the host stellar mass.
+% The AGN surface photometry in IR Channel Filters.\\
+The high spatial resolution of the host image is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass.
 All the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as the HST program GO-15115, PI: John Silverman.
@@
 total exposure time $\sim2394s$).
-The six exposures for each dither image were combined by the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter of 0.8 with a \texttt{gaussian} kernel.
-\textcolor{blue}{The other four AGNs in our sample have been observed with WFC3 serendipitously (2 in COSMOS from Kartaltepe (PI); PID: 13657).}
-To accurately estimate the background light which could come from both the sky and the detector, we also adopt the {\sc photutils} to measure the photometry.
+The six exposures for each dither image were combined by the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel.
+To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} to measure the photometry.
 
-%With 27/36 of our AGNs having rest-frame UV imaging with HST (COSMOS: F814W, PI: Nicholas Scoville; GEMS: F606W+F850LP), we are able to infer the host color and assess the contribution of both the young and old stellar population to the stellar mass budge \textcolor{blue}{citet Gallazzi+Bell 2009}.
-
-21/32 of our sample have rest-frame UV images by \citet{Scoville2007}. %arxiv: 0702359}.
+Multi-band information provides the spectral energy distributions (SED) at a more precise level.
+21/32 of our sample have rest-frame UV images by \citet{Scoville2007}.
 Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures.
@@
 The \mbh\ of type-1 AGNs can be inferred using the so-called virial method \citep{Peterson2004, Shen2013}.
-The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the motion of the BLR gas is virialised by the gravity.
-In this scenario, the width of the emission-line provide the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size.
+The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity virializes the motion of the BLR gas.
+In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size.
 As a result, the estimation of the \mbh\ is achieved by these measurements.
@@
 We referred to this paper for the details of continuum fitting and emission line modeling.
-Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt the list of consistent ones to cross-calibrate the \mbh\ for all the samples in order to avoid any systematic bias in Section~\ref{mbh}.
+Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt a list of consistent ones to cross-calibrate the \mbh\ for all the samples, in order to avoid any systematic bias in Section~\ref{mbh}.
 
@@
 %Introduce the PSF library
-The knowledge of the PSF is crucial for the QSO imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source.
+The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source.
 The PSF is known to be varied with different frame position and the intensity, due to the effect of aberrations.
 The simulated PSF, such as {\sc TinyTim} ones, are usually poor matches to observations \citet{Mechtley2012}.
-Empirical PSF stars are considered better than the simulated ones, since they we observed simultaneously with the science target which were reduced and analyzed in the same way \citet{Kim2008, Park15}
+Empirical PSF stars are considered better than the simulated ones, since they were observed simultaneously with the science target which were reduced and analyzed in the same way \citet{Kim2008, Park15}
 
-To minimize the impact of the mismatch, we build a PSF library by cutting out the isolated, unsaturated PSF stars with high S/N from the overall QSO field.
-We first collect the identified stars as candidates which are listed in the COSMOS2015 catalog by \citet{Laigle2016}.
-However, since a lot of bright stars with intensity similar to the QSOs are excluded by \citet{Laigle2016}, we visually select these star-like PSF as candidates.
-Finally, we remove the non-ideal PSF candidates by inspecting their intensity, FWHM, central symmetry and any that were contaminated by background objects.
-To summarize, we selected 78 and 36 PSFs from the field observed by filter F140W and F125W, respectively.
+To minimize the impact of the mismatch, we build a PSF library by selecting the isolated, unsaturated PSF-stars with high S/N from the overall AGN field.
+The selection is completed by the following steps.
+We first adopt the identified stars as candidates from the COSMOS2015 catalog by \citet{Laigle2016}.
+A lot of bright stars with intensity similar to the AGNs were excluded by \citet{Laigle2016}; in the second step, we manually select the PSF-like objects as candidates.
+We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects.
+Finally, the PSF library contains 78 and 36 PSFs for F140W and F125W, respectively.
 
-We stress that, by building this library, we assume that the PSFs herein bracket all the possible PSF light distribution which fits our imaging data.
-Therefore, the inference from each PSF will include the true answer.
-In the next subsection, we carry out the QSO decomposition using each PSF.
+We assume that the overall PSF-stars in the library cover all possible PSF light distribution. Therefore, when fitting to data, the entire inference would bracket the true answer.
+%In the next subsection, we carry out the AGN decomposition using each PSF.
 We rank their performance based on the goodness (i.e.
@@
 %Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
-We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underling host galaxy.
-Following common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile.
+We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underlying host galaxy.
+As a common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile.
 Note that the actual morphologies of the host galaxies could be even more complicated (e.g.
 bulge+disk).
-However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux given the high redshift range of our sample.
-Furthermore, we fit the galaxies which close to the QSO as the \sersic\ model, to account for the contamination of their light.
+However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux, given the high redshift range of our sample.
+Furthermore, we fit the galaxies which close to the AGN as the \sersic\ model, to account for the contamination of their light.
 
 %Introduce Lenstronomy:
-We adopt the imaging modeling tool \lenstronomy\ \citep{lenstronomy}, to decompose the host and nuclear light.
-The \lenstronomy\ is a multi-purpose open-source gravitational lens modeling python package.
-The flexibility of this package enable us to turn off the lensing channel and carry out this task\footnote{For a sanity check, we compared the performance of \lenstronomy\ to the most commonly used galaxy modelling software {\sc Galfit} and confirm that the consistent result could be obtained with the same fitting ingredients provided.}.
-The input ingredients to \lenstronomy\ includes:
+We adopt the imaging modeling tool \lenstronomy\ \citep{lenstronomy} to perform the decomposition of the host and nuclear light.
+\lenstronomy\ is a multi-purpose open-source gravitational lens image modeling python package.
+Its flexibility enables us to turn off the lensing channel and focus on the AGN decomposition\footnote{For a sanity check, we compared the performance of \lenstronomy\ to the most commonly used galaxy modeling software {\sc Galfit} and confirm that the consistent result could be obtained with the same fitting ingredients provided.}.
+The input ingredients to \lenstronomy\ include:
 \begin{enumerate}
-\item \hst\ AGN imaging data.
--- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ cover sufficient QSO light our samples.
+\item AGN imaging data. \\
+-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ covers sufficient AGN light our samples.
 By default, we cut out the AGN image to a $61\times61$ pixels box (i.e.
 $4''\times 4''$).
-\item Noise level map -- The origin of the noise in each pixel is stems from the read noise, background noise and Poisson noise by the astronomical sources themselves.
+If needed, the larger size box would be sufficient to include the nearby objects.
+\item Noise level map.\\
+-- The origin of the noise in each pixel stems from the read noise, background noise and Poisson noise by the astronomical sources themselves.
 To take them into account, we measure the read noise and background noise level directly from the empty regions of the data.
-We calculate the effective exposure time in each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level.
-\item PSF -- The PSF are directly taken from the PSF library.
-Usually, mismatch exists when subtract the AGN as the scaled PSF, especially at the central parts.
-We assume that the overall inference based on each PSF bracket the best one as one can obtain, given the flexibility of the library.
-We also note that, in the lens modelling, this mismatch can be mitigated with PSF reconstruction by the iterative method \citep{Chen2016, Birrer2018}.
-However, this approach collects the information of the lensing feature which is not suitable to our case.
-If one forces to perform the PSF reconstruction, the iterative correction would absorb all mismatch information, result in a biased host inference.
+We calculate the effective exposure time of each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level.
+\item PSF. \\
+-- 
+The PSF is directly taken from the PSF library.
+Usually, the mismatch exists when subtracting the AGN as the scaled PSF, especially at the central parts.
+We also note that, in the lens modeling, this mismatch can be mitigated with PSF reconstruction by the iterative method \citep{Chen2016, Birrer2018}.
+However, this approach incorporates with the information of the lensing feature which is not suitable for our case.
+If one enforces to perform the PSF reconstruction, the iterative correction would absorb all mismatch information, result in a biased host inference.
+Hopefully, our library contains sufficient information to cover all the possible PSF, and the entire inference would bracket the true answer.
 \end{enumerate}
@@
 %Introduce the final inference using fitting:
-Focusing on each QSO system, its host light information is inferred through several steps.
-First, we fit the flux distribution using each PSFs in the library.
-Given the fitting ingredients, we are able to infer the posterior distribution in the parameter space and optimize the best-fit parameters with minimized residuals.
-In this step, we apply the Particle Swarm Optimizer (PSO) to optimize the best-fit parameters based on the imaging likelihood.
-Running through the library, we record the inference based on each PSF together with the corresponding $\chi^2$ value\footnote{The \lenstronomy\ enable one to infer also the parametric confidence interval.
-However, given a fixed PSF image, the $1-\sigma$ region of each parameter are extremely narrow}.
-In the second step, we rank the performance of each PSF based on the $\chi^2$ value and select the top-8 PSFs so as to weight for the inferred property.
-The weights for each PSF is calculated by:
+The host properties of one AGN system is inferred through several steps.
+First, we decompose the AGN-host using each PSFs in the library.
+Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC.
+However, in our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow.}.
+To avoid any unphysical inference, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{}]$, and Sersic index $n\in[1,7]$.
+Since the inference by each PSF could be the right answer, we save all of them as our entire inference.
+Then, we extract the best answer from the entire inference.
+We rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs.
+We infer the host property (i.e., host flux, \Reff, Sersic index $n$) using weighted arithmetic mean, and the weight is calculated by:
 \begin{eqnarray}
@@
 \end{eqnarray} 
-Note that since each QSO system has different seeing condition, the top-8 PSFs are different for each system.
+Note that since each AGN system has different seeing condition, the top-eight PSFs are usually varies from one AGN system to another.
+Given the weights, the inferred value of host properties and the root-mean-square ($\sigma$) are calculated as:
+\begin{eqnarray}
+\label{eq:infer_value}
+\bar{x}  =  \frac{  \sum_{i=1}^{8}   x_i * w_i  }{\Sigma w_i} ,
+\end{eqnarray} 
+\begin{eqnarray}
+\sigma =   \sqrt{ \frac{  \sum_{i=1}^{8}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
+\end{eqnarray}
 
 %ECDFS-358 and CID206
-In Figure~\ref{fig:QSO_decomp}, we demonstrate the optimized results inferred by \lenstronomy.
-In each, we show the images, best-fit models, image subtract point source (i.e.
-host) and the residuals for every systems.
-As an example, we also show the weighting process for system CID1174 in Table~\ref{tab:weight_CID1174}.
-To quickly overview our inference, we summarize them as relations between: 1) effective radius \Reff, 2) \sersic\ index $n$ and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.
+In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e.
+host) and the residuals.
+As an example, the weighting values in the analysis of system COSMOS-CID1174 are listed in Table~\ref{tab:weight_CID1174}.
+In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index $n$ and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.
+
+The inference of the host properties is weighted by eight top-ranked PSFs.
+To understand how the amount of top-ranked PSF affects our inference, we compare to the one inferred by five and ten top-ranked PSFs.
+As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference is solid when the amount of selected PSF exceeds five.
 
 %The inference of F814w data.
-18/32 systems in COSMOS field have ACS/F184W imaging data.
+18/32 systems in the COSMOS field have ACS/F184W imaging data.
 Likewise, we infer their host properties using the same approach.
 The field of view by ACS are larger than WFC3, and we collected in total 174 ACS PSFs in the library.
-While fitting the host light, we fix the \Reff\ and \sersic\ $n$ as the value inferred by WFC3/IR, assuming that the shape of the galaxy are consistent between ACS and WFC3.
-We believe the inferred information of the galaxy shape by IR imaging are superior to the one by UV band, considering the effects of dust extinction and contrast between the (blue) AGN and (red) host is more favorable in IR band.
+In principle, the host inference by IR band is superior to the one by UV band, giving that the effects of dust extinction and contrast between the (blue) AGN and (red) host.
+Thus, we fix the \Reff\ and \sersic\ $n$ as the value inferred by IR band, assuming that the morphology of the galaxy is consistent between ACS and WFC3.
 
@@
 
-\subsubsection{Host luminosity}
+\subsubsection{Host luminosity and stellar mass}
 %The overall fitting plot: 1. Host-R-n corner for f140w and f814w. 2. The histogram with different selection.
 \textcolor{red}{To be written:}
-1.K-correction to infer the rest frame R-band.\\
-* The galaxy template inferred by the joint fitting of the SED and the host flux ratio by us.
+\\1. Describe the SED fitting and the ground-based photometry data.
+\\2. The comparison of our host-to-total flux ratios to the SED decomposed ones.
+\\3. The inferred rest-frame R band magnitude and stellar mass.
 
@@
 \textcolor{blue}{Introduce the passive evolution?}
-To directly compare with local samples, we consider the passive evolution scenario for the inferred \lhost\ and transfer to its expected value at today.
+\\To directly compare with local samples, we consider the passive evolution scenario for the inferred \lhost\ and transfer to its expected value at today.
 
-We summarized the homogenized R-band luminosities
-in Table~\ref{tab:result_sersic}.
+We summarized the inferred R-band luminosities in Table~\ref{tab:result_sersic}.
 
@@
 This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
-To avoid any systematic bias between our samples and the literature ones, we compared the recipes as used by \citet{Schulze2018, Ding2017b}.
-We find that the \hbeta\ estimator are very close between the two reference.
+To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}.
+We find that the \hbeta\ estimator is very consistent ($<0.03$~dex) between the two references.
 Moreover, in \citet{Schulze2018}, the cross-calibrate between the \halpha\ and \hbeta\ are consistent.
-Therefore, we directly adopt virial formalism from \citet{Schulze2018}:
+Thus, we adopt the virial formalism from \citet{Schulze2018}:
 \begin{eqnarray}
@@
 \label{eq:Ha}
-\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.710+0.48 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
-&~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right) , 
+\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.71+0.48 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
+&~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right).
 \end {eqnarray}
@@
 Having defined the recipes, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
-14 of the overall systems have both \halpha\ and \hbeta\ emission line information; we adopt the average \mbh\ value by these two lines.
-We summarized the inference of the \mbh\ together with the details on the emission line in Table~\ref{tab:result_mbh}.
+14 of the overall systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged \mbh\ value.
+We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}.
 
@@
 \label{sec:sum}
-We presented the study of the Mbh and host property's evolution to high redshift until 1.8.
+%We presented the study of the \mbh\ and host property's evolution to high redshift until 1.7.
 
@@
 \subsection{Systematic error}
-\subsection{Fitting mask for CID206 and ECDFS-358}
+\subsection{Masks objects for the COSMOS-CID206 and ECDFS-358}
 
@@
 Column 2: Redshifts.
-Column 3: HST filter by WFC3. Note that the samples from COSMOS field also has the ACS/F814W image.
+Column 3: HST filter by WFC3. Note that the samples from the COSMOS field also has the ACS/F814W image.
 Column 4 and 5: The $RA$ and $DEC$ of the system.
@@
 \tablewidth{0pt}
-\tablecaption{The inference of the host information by the QSO decomposition for the 32 systems.} 
+\tablecaption{The inference of the host information by the AGN decomposition for the 32 systems.} 
 \tablehead
@@
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID237_SB_profile.pdf}
-\caption{\label{fig:QSO_decomp} 
-\textcolor{red}{need to be written:}
-Figure illustrates the inference by WFC3 images for the 34 objects.
+\caption{\label{fig:AGN_decomp} 
+Figure illustrates the inference by WFC3 images for the 32 objects.
 In each row, observed data (first column), best-fit models (second column), data subtracted by the inferred point source (third column),  normalized residuals (fourth column) are presented together with the target ID.
-In the fifth column, we present the 1-D surface brightness profiles and the corresponding residual.
-\textcolor{blue}{The different colors means blash blash...}
-%In each row, observed data (first column), best-fit models (second column), and residuals (third column) are presented with the object name.
-All images are $10.8\arcsec\times10.8\arcsec$ in size and  displayed with an inverted asinh stretch.
-The fourth column shows the corresponding one-dimensional surface brightness profiles.
-In each top panel, the profiles measured from the data (open circles), the best-fit model (black solid line), and the sub-components of the model for bulge (blue solid line), disk (green solid line), AGN (red solid line) are shown.
-Residuals (gray circles), the difference of the profiles between the data and the best-fit model, are presented in each bottom panel.
-Note that the one-dimensional surface brightness profiles are shown for illustration purposes only, the actual fitting made use of the full two-dimensional images.
+In the fifth column, we present the 1-D surface brightness profiles (top) and the corresponding residual (bottom).
+The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects).
+Note that the showing for one-dimensional surface brightness profiles are only for illustration purposes.
+The actual fitting is based on the two-dimensional images.
 }}
@@
 }
-\caption{\label{fig:flux_r_n_corner} The relations among these values.}
+\caption{\label{fig:flux_r_n_corner}
+Illustration of the relations between the inferred host properties.}
+\end{figure*}
+
+\begin{figure*}
+\centering
+{
+\includegraphics[height=0.35\textwidth]{fig/hist_compare.pdf}
+}
+\caption{\label{fig:hist_compare} 
+The comparison of the histogram of the inferred host flux ratio, based on the different amount of the top-ranked PSFs.}
 \end{figure*}

### 2019-01-21 manuscript/manuscript.tex
The update by Tommaso

@@
 
-Most galactic nuclei harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar).
-These tight correlations indicates a connection between nuclear activity and galaxy formation and evolution \citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
+Most galactic nuclei are thought to harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar).
+These tight correlations indicate a connection between nuclear activity and galaxy formation and evolution \citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
 Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy.
-On the other hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
-However, for a different view, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.
+On the one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
+On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.
 
-One key to this study is tracing their correlation to higher redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}.
-During the past decade, there has been much progress on our understanding at $z<1$ using the type 1 AGN.
-The work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that, \mbh\ is elevated as compared to the bulge luminosity from the local relations, thus indicating that the supermassive BHs were built up first with galaxy then growing around their deep potential wells.
+A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}.
+During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs.
+For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed bulge luminosity compared to the local relations.
+This offset is consistent with a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells.
 Similarly, the works by \citet{Bennert11, Woo++08} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations.
-Nevertheless, some studies are consistent with no evolution \citet{SS13, Sun2015, Cisternas2011}.
+Nevertheless, the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution \citet{SS13, Sun2015, Cisternas2011}.
 
-Despite the enormous amount of effort, there are still uncertainties stems from different aspects which could lead to the inconsistency among these works.
-First, the inherent uncertainties in BH mass estimates using the virial method.
-Especially, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e.
+In order to make progress it is important to reduced as much as possible the uncertainties and take great care of selection effects and systematic errors.
+First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called "virial" method.
+In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e.
 \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}.
-Second, since the host information is swamped by the bright nuclear light, measurement systematics exist in the host galaxy properties.
-It is worth noting that strong gravitational lensing provides a unique opportunity to make progress in the study by extending the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}.
-Equally important, the selection effects and their impact on the observed need to be taken well into account.
+Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging.
+Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed quasars, since lensing magnifies the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}.
+Last but not least, the selection function needs to be taken into account when intepreting the observations \citep{Treu2007,Lauer2007}.
 For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample.
-Even considering this selection effect, an evolution of the scaling relations is expected from simulations \citep{DeG++15} and with respect to the bulge mass.
+It is also important to consider the selection function when comparing the observed scaling relations with simulated ones \citep{DeG++15}.
 
-To make progress, it is essential to make use of the larger sample to high-quality data in respect of the measurement of both the host properties and the \mbh.
-On the other hand, extending the correlations to higher redshift ($z>1$) would effectively improve the statistics, where the \mbh-\lhost\ is steeper than the current observational measurements at lower redshift, before self-regulation slows the black hole growth and galaxies settle onto the local mass relation \citep{DeG++15}.
-
-In this study, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.
-At this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS.
+In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest \citep{DeG++15}.
+In practice, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.
+In this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS.
 Our study overcomes the biases in the following way.
@@
 Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements.
-Moreover, 21/32 systems of our sample have two-band \hst\ data (i.e.
+Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e.
 WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference.
-Given the high-quality data at such redshift, we test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex).
+Given the high-quality data at such redshift, we can test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex).
 
@@
 
-For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point. 
-To compare with the samples in the literature, we also adopt the samples from \citet{Ding2017b}, which includes the measurements by \citet{Pen++06qsob, Park15} to study the \mbh-\lhost\ of 127 objects by \hst.
+For the calibration with the local relation, we use 19 local AGN measurements \citep{Ben++10, Peterson2004} which define the zero-point. 
+To compare with the samples in the literature, we also adopt the samples from \citet{Ding2017b}, which include the measurements by \citet{Pen++06qsob, Park15} to study the \mbh-\lhost\ of 127 objects by \hst.
 
@@
 We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets.
-This selection could ensure that the broad \halpha\ line ($4000\AA$) is not present in the bandpass which could contaminate the host emissions due to the broad wings of the PSF.
+This selection ensures that the broad \halpha\ line ($4000\AA$) is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.
 
 %Drizzling, background noise...
-For the new 32 AGN systems, each target one has six separate exposures with $\sim399s$ (i.e.
+For each of the 32 new AGNs we took six separate exposures with $\sim399s$ (i.e.
 total exposure time $\sim2394s$).
-The six exposures for each dither image were combined by the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel.
+The six exposures for each dither image were combined with the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel.
 To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} to measure the photometry.
@@
 The \mbh\ of type-1 AGNs can be inferred using the so-called virial method \citep{Peterson2004, Shen2013}.
-The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity virializes the motion of the BLR gas.
+The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas.
 In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size.
@@
 For our targets, the \halpha\ and \hbeta\ emission-line properties have been investigated by \citet{Schulze2018} using the multi-object spectrograph Subaru/FMOS.
-We referred to this paper for the details of continuum fitting and emission line modeling.
+We referred to that paper for the details of continuum fitting and emission line modeling.
 Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt a list of consistent ones to cross-calibrate the \mbh\ for all the samples, in order to avoid any systematic bias in Section~\ref{mbh}.
@@
 The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source.
-The PSF is known to be varied with different frame position and the intensity, due to the effect of aberrations.
-The simulated PSF, such as {\sc TinyTim} ones, are usually poor matches to observations \citet{Mechtley2012}.
-Empirical PSF stars are considered better than the simulated ones, since they were observed simultaneously with the science target which were reduced and analyzed in the same way \citet{Kim2008, Park15}
+The PSF is known to be vary across the detector and with time, due to the effect of aberrations and breathing.
+Simulated PSF, such as {\sc TinyTim} ones, are usually insufficient matches to observations for our purposes \citet{Mechtley2012}.
+Stars within the fields provide a better description than the simulated PSF, since they were observed simultaneously with the science targets and reduced and analyzed in the same way \citet{Kim2008, Park15}
 
-To minimize the impact of the mismatch, we build a PSF library by selecting the isolated, unsaturated PSF-stars with high S/N from the overall AGN field.
-The selection is completed by the following steps.
+To minimize the impact of the mismatch, we build a PSF library by selecting all the isolated, unsaturated PSF-stars with high S/N from our entire program.
+The selection consists of the following steps.
 We first adopt the identified stars as candidates from the COSMOS2015 catalog by \citet{Laigle2016}.
@@
 We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects.
-Finally, the PSF library contains 78 and 36 PSFs for F140W and F125W, respectively.
+In the end, the PSF library contains 78 and 36 PSFs for F140W and F125W, respectively.
 
-We assume that the overall PSF-stars in the library cover all possible PSF light distribution. Therefore, when fitting to data, the entire inference would bracket the true answer.
+We assume that the stars in the library are representative of the possible PSFs in our program.
+Therefore, we assume that the PSF library gives a good representation of the dominant source of uncertainty as well as the best fit.
 %In the next subsection, we carry out the AGN decomposition using each PSF.
@@
 We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underlying host galaxy.
-As a common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile.
-Note that the actual morphologies of the host galaxies could be even more complicated (e.g.
+Following common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile.
+Note that the actual morphologies of the host galaxies could be more complicated (e.g.
 bulge+disk).
 However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux, given the high redshift range of our sample.
-Furthermore, we fit the galaxies which close to the AGN as the \sersic\ model, to account for the contamination of their light.
+Furthermore, we fit other galaxies that happen to be close to the AGN as additional \sersic\ model, to account for any potential contamination.
 
@@
 Its flexibility enables us to turn off the lensing channel and focus on the AGN decomposition\footnote{For a sanity check, we compared the performance of \lenstronomy\ to the most commonly used galaxy modeling software {\sc Galfit} and confirm that the consistent result could be obtained with the same fitting ingredients provided.}.
+The maim advantage over {\sc Galfit} is that \lenstronomy returns the full posterior of the parameter and not just the best fit model and the Laplace approximation of the uncertanties.
 The input ingredients to \lenstronomy\ include:
@@
 The PSF is directly taken from the PSF library.
-Usually, the mismatch exists when subtracting the AGN as the scaled PSF, especially at the central parts.
-We also note that, in the lens modeling, this mismatch can be mitigated with PSF reconstruction by the iterative method \citep{Chen2016, Birrer2018}.
-However, this approach incorporates with the information of the lensing feature which is not suitable for our case.
-If one enforces to perform the PSF reconstruction, the iterative correction would absorb all mismatch information, result in a biased host inference.
-Hopefully, our library contains sufficient information to cover all the possible PSF, and the entire inference would bracket the true answer.
+Usually, a mismatch exists when subtracting the AGN as the scaled PSF, especially at the central parts.
+While modeling multiply imaged AGN, this mismatch can be mitigated with PSF reconstruction by the iterative method \citep{Chen2016, Birrer2018}.
+However, this approach requires multiple images which are not available in our case.
+We remedy this deficiency by using a broad library which should contain sufficient information to cover all the possible PSF.
 \end{enumerate}
@@
 %Introduce the final inference using fitting:
-The host properties of one AGN system is inferred through several steps.
-First, we decompose the AGN-host using each PSFs in the library.
+The host properties of one AGN system is inferred via the following steps.
+First, we model the AGN and host using each PSFs in the library.
 Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC.
 However, in our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow.}.
-To avoid any unphysical inference, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{}]$, and Sersic index $n\in[1,7]$.
-Since the inference by each PSF could be the right answer, we save all of them as our entire inference.
-Then, we extract the best answer from the entire inference.
-We rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs.
-We infer the host property (i.e., host flux, \Reff, Sersic index $n$) using weighted arithmetic mean, and the weight is calculated by:
+To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{}]$, and Sersic index $n\in[1,7]$.
+Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs.
+We infer the host property (i.e., host flux, \Reff, Sersic index $n$) using a weighted arithmetic mean.
+The weight is calculated by:
 \begin{eqnarray}
@@
 \end{eqnarray} 
-where the $\alpha$ is the inflation parameter so that when $i=8$:
+where the $\alpha$ is an inflation parameter so that when $i=8$:
 \begin{eqnarray}
 \label{eq:alpha}
-\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2
+\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2,
 \end{eqnarray} 
-Note that since each AGN system has different seeing condition, the top-eight PSFs are usually varies from one AGN system to another.
+The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties.
+The answers would not change significantly if we had chosen a different number of PSFs, as we show below.
+
+Note that since each AGN system was observed in different location of the detector and at a different time, the top-eight PSFs usually vary from one AGN system to another.
 Given the weights, the inferred value of host properties and the root-mean-square ($\sigma$) are calculated as:
@@
 host) and the residuals.
-As an example, the weighting values in the analysis of system COSMOS-CID1174 are listed in Table~\ref{tab:weight_CID1174}.
+As an example, the weights adopted in the analysis of system COSMOS-CID1174 are listed in Table~\ref{tab:weight_CID1174}.
 In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index $n$ and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.
@@
 The inference of the host properties is weighted by eight top-ranked PSFs.
-To understand how the amount of top-ranked PSF affects our inference, we compare to the one inferred by five and ten top-ranked PSFs.
+To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the one inferred by five and ten top-ranked PSFs.
 As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference is solid when the amount of selected PSF exceeds five.
+For a smaller number of PSFs one tends to underestimate the uncertainties.
 
@@
 18/32 systems in the COSMOS field have ACS/F184W imaging data.
-Likewise, we infer their host properties using the same approach.
+We infer their host properties using the same approach used for the WFC3-IR data.
 The field of view by ACS are larger than WFC3, and we collected in total 174 ACS PSFs in the library.
@@
 \tablewidth{0pt}
-\tablecaption{The sample information for the 32 systems.} 
+\tablecaption{Sample properties.} 
 \tablehead{ 
@@
 Column 2: Redshifts.
-Column 3: HST filter by WFC3. Note that the samples from the COSMOS field also has the ACS/F814W image.
-Column 4 and 5: The $RA$ and $DEC$ of the system.
+Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
+Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
 }
@@
 \tablewidth{0pt}
-\tablecaption{Details of the weighting CID1174's inference. } 
+\tablecaption{Details of CID1174's inference. } 
 \tablehead{ 
@@
 \tablecomments{
-Column~1: The rank of the PSF from the library.
+Column~1: Rank of the PSF from the library.
 Column~2: Total $\chi ^2$ for the corresponding PSF.
-Column~3: Weights for co-adding the inference.
+Column~3: Weights for the inference.
 Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
-For this sample, the inflation value $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
+For this sample, the inflation parameter $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
 }
@@
 \tablewidth{0pt}
-\tablecaption{The inference of the host information by the AGN decomposition for the 32 systems.} 
+\tablecaption{Inferred host galaxy parameters for the 32 systems.} 
 \tablehead
@@
 \colhead{Target ID}&
-  \multicolumn{5}{c}{Inference by WFC3}&
-  \multicolumn{3}{c}{Inference by ACS} \\
+  \multicolumn{5}{c}{WFC3}&
+  \multicolumn{3}{c}{ACS} \\
   \cline{2-6}  \cline{7-9} \\
 \colhead{}& 
-\colhead{reduced $\chi ^2$}& \colhead{host flux ratio}& 
+\colhead{reduced $\chi ^2$}& \colhead{host-to-total flux ratio}& 
 \colhead{\Reff}& \colhead{\sersic\ $n$}& 
 \colhead{magnitude}&
-\colhead{reduced $\chi ^2$}& \colhead{host flux ratio}& \colhead{magnitude} & \colhead{$\log L_R$}\\
+\colhead{reduced $\chi ^2$}& \colhead{host-to-total flux ratio}& \colhead{magnitude} & \colhead{$\log L_R$}\\
 \colhead{}& 
@@
 Column~2: Reduced $\chi ^2$ value by the best PSF in the library.
-Column~3-6: Host inference by the WFC3 image.
-Column~7-9: Host inference by the ACS image. 
-Column~10: The inferred host Luminosity in the rest-frame R band.
+Column~3-6: WFC3 inference.
+Column~7-9: ACS inference. 
+Column~10: Inferred host Luminosity in the rest-frame R band.
 }
@@
 \tablewidth{0pt}
-\tablecaption{The inference of the \mbh\ for the 32 systems.} 
+\tablecaption{Inferred \mbh\.} 
 \tablehead
@@
 Column 1: Object ID.
-Column 2-4: The emission line width (FWHM), continuum luminosity and inferred \mbh by \halpha\ emission line. 
-Column 5-7: The inference by \hbeta\ emission line. 
+Column 2-4: \halpha\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
+Column 5-7: \hbeta\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
 }
@@
 \caption{\label{fig:AGN_decomp} 
-Figure illustrates the inference by WFC3 images for the 32 objects.
+Figure illustrates the inference for the 32 objects based on the WFC3 images.
 In each row, observed data (first column), best-fit models (second column), data subtracted by the inferred point source (third column),  normalized residuals (fourth column) are presented together with the target ID.
@@
 The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects).
-Note that the showing for one-dimensional surface brightness profiles are only for illustration purposes.
+Note that the one-dimensional surface brightness profiles are only for illustration purposes.
 The actual fitting is based on the two-dimensional images.
@@
 \caption{\label{fig:hist_compare} 
-The comparison of the histogram of the inferred host flux ratio, based on the different amount of the top-ranked PSFs.}
+Comparison of the histogram of the inferred host flux ratio, based on the different amount of the top-ranked PSFs.}
 \end{figure*}

### 2019-02-25 manuscript/manuscript.tex
Update with John's comments

@@
 
-\title{Cosmic evolution of the correlation between supermassive black hole mass and host galaxy at redshift up to 1.7}
+\title{Cosmic evolution of the mass relation between supermassive black holes and their host galaxies up to $z\sim1.7$}
 
@@
 \altaffiltext{2}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
-\altaffiltext{3}{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
-\altaffiltext{4}{Dipartimento di Matematica e Fisica, Università Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
+\altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
+\altaffiltext{4}{Dipartimento di Matematica e Fisica, Universit√ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
 \altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
@@
 \begin{abstract}
-We investigate the cosmic evolution of the relation supermassive black hole and host galaxy properties at $1.2<z<1.7$, using a sample of 32 X-ray selected type-1 AGN obtained with the Hubble Space Telescope (\hst).
-The high-resolution \hst\ images enable us to decompose the AGN image and infer the host properties including luminosities (\lhost) and stellar masses (\smass).
-We estimate the BH masses (\mbh) with spectroscopic information of the \halpha, \hbeta.
-We compare the \mbh-\lhost and \mbh-\smass relation to the local active galaxies and taking the selection effects into account.
+We measure the relation between supermassive black hole and host galaxy properties at $1.2<z<1.7$ using a sample of 32 X-ray-selected broad-line (type-1) AGN in deep survey fields obtained with the Hubble Space Telescope (\hst) Wide-Field Camera 3.
+The high-resolution \hst\ images enable us to decompose the AGN image and infer the host properties including luminosity (\lhost) and stellar mass (\smass) in each case.
+Black holes masses (\mbh) are based on our published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines.
+We compare the \mbh-\lhost~and \mbh-\smass~relation to the local active galaxies while taking selection effects into account thus establishing the cosmic evolution in these relations.
 Results to be written.
@@
 
-\section{Observations and data reduction}
-\label{sec:data}
-In this section, we summarize the sample selection, observations, and data reduction of our sample.
+%\section{Observations and data reduction}
+%\label{sec:data}
+%In this section, we summarize the sample selection, observations, and data reduction of our sample.
 
-\subsection{Sample selection}
+\section{Sample selection}
 %How the samples are selection.\\
@@
 
-We aim to study the relation between the BH masses (\mbh) and their host galaxy properties including luminosities (\lhost) and stellar mass (\smass) to redshift at $z>1$.
-For this propose, we focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS \citep{Civano2016}, (E)-CDFS-S \citep{Lehmer2005, Xue2011}, and SXDS \citep{Ueda2008} fields.
+%We aim to study the relation between the BH masses (\mbh) and their host galaxy properties including luminosities (\lhost) and stellar mass (\smass) to redshift at $z>1$. For this propose,
+
+We focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS \citep{Civano2016}, (E)-CDFS-S \citep{Lehmer2005, Xue2011}, and SXDS \citep{Ueda2008} fields.
 We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$.
@@
 
+The \mbh\ of type-1 AGNs can be inferred using the so-called virial method \citep{Peterson2004, Shen2013}.
+The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas.
+In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size.
+As a result, the estimation of the \mbh\ is achieved by these measurements.
+
+For our targets, the \halpha\ and \hbeta\ emission-line properties have been investigated by \citet{Schulze2018} using the multi-object spectrograph Subaru/FMOS.
+We referred to that paper for the details of continuum fitting and emission line modeling.
+Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt a list of consistent ones to cross-calibrate the \mbh\ for all the samples, in order to avoid any systematic bias in Section~\ref{mbh}.
+
+\subsection{Local comparison sample}
 For the calibration with the local relation, we use 19 local AGN measurements \citep{Ben++10, Peterson2004} which define the zero-point. 
@@
 
-\subsection{Observation and reduction}
+\section{HST observations}
 \label{observation}
-\subsubsection{HST image Observation}
+%\subsubsection{HST image Observation}
 % The AGN surface photometry in IR Channel Filters.\\
@@
 
-\subsubsection{AGN Emission Line}
-\label{sec:bh_mass}
+%\subsubsection{AGN Emission Line}
+%\label{sec:bh_mass}
 % The introduction of the BH inferred by the board emission line.
-The \mbh\ of type-1 AGNs can be inferred using the so-called virial method \citep{Peterson2004, Shen2013}.
-The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas.
-In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size.
-As a result, the estimation of the \mbh\ is achieved by these measurements.
-
-For our targets, the \halpha\ and \hbeta\ emission-line properties have been investigated by \citet{Schulze2018} using the multi-object spectrograph Subaru/FMOS.
-We referred to that paper for the details of continuum fitting and emission line modeling.
-Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt a list of consistent ones to cross-calibrate the \mbh\ for all the samples, in order to avoid any systematic bias in Section~\ref{mbh}.
 
@@
 We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects.
-In the end, the PSF library contains 78 and 36 PSFs for F140W and F125W, respectively.
+In the end, the PSF library contains 78 and 37 PSFs for F140W and F125W, respectively.
 

### 2019-03-11 manuscript/manuscript.tex
Updates after John's visiting.

@@
 
-\title{Cosmic evolution of the mass relation between supermassive black holes and their host galaxies up to $z\sim1.7$}
+\title{The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3}
 
-\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{2}, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{2}, Knud Jahnke, et al.
+\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{2}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{2},  Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
  }
@@
 \altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
-\altaffiltext{4}{Dipartimento di Matematica e Fisica, Universit√ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
+\altaffiltext{4}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
 \altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
@@
 \begin{abstract}
-We measure the relation between supermassive black hole and host galaxy properties at $1.2<z<1.7$ using a sample of 32 X-ray-selected broad-line (type-1) AGN in deep survey fields obtained with the Hubble Space Telescope (\hst) Wide-Field Camera 3.
+
+The tight correlation between the mass of a supermassive black hole (\mbh) and its host galaxies properties indicates a connection of their evolution.
+The key to test this co-evolution scenario is to trace their correlation to more distant Universe.
+We measure using a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields obtained with the {\it Hubble Space Telescope} (\hst).
+%Wide-Field Camera 3.
 The high-resolution \hst\ images enable us to decompose the AGN image and infer the host properties including luminosity (\lhost) and stellar mass (\smass) in each case.
-Black holes masses (\mbh) are based on our published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines.
-We compare the \mbh-\lhost~and \mbh-\smass~relation to the local active galaxies while taking selection effects into account thus establishing the cosmic evolution in these relations.
-Results to be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
-To be written.
+The lower nuclear-to-host ratios and multi-band images of our samples provide accurate host properties.
+The estimation of \mbh\ is based on our published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids the systemic bias by the \Civ\ or \Mgii\ lines.
+We compare the \mbh-\lhost~and \mbh-\smass~relation to the local active galaxies while taking the selection effect into account thus establishing the cosmic evolution in these relations.
+Considering the passive luminosity effect, we inferred a positive evolution of \mbh-\lhost, indicating that the BHs at higher redshift resides in less luminous galaxies than today.
+The \mbh-\smass\ of our high redshift sample is consistent with the local \mbh-\smass$_{\rm bluge}$ relations.
+Considering that our sample are composed of bulge and disk components, we are forced to concluded that our results consistent to a scenario that the growth of the black hole predates that of the bulge.
 \end{abstract}
@@
 Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed quasars, since lensing magnifies the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}.
-Last but not least, the selection function needs to be taken into account when intepreting the observations \citep{Treu2007,Lauer2007}.
+Last but not least, the selection function needs to be taken into account when intepreting the observations \citep{Treu2007, Lauer2007}.
 For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample.
@@
 
-\section{Sample selection}
+\section{Sample selection and \mbh}
+\label{sec:data}
 %How the samples are selection.\\
@@
 
-\section{HST observations}
+\subsection{BH masses}
+\label{mbh}
+ %Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g.
+McLure 2002; Shen 2013)}.
+This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
+To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}.
+We find that the \hbeta\ estimator is very consistent ($<0.03$~dex) between the two references.
+Moreover, in \citet{Schulze2018}, the cross-calibrate between the \halpha\ and \hbeta\ are consistent.
+Thus, we adopt the virial formalism from \citet{Schulze2018}:
+\begin{eqnarray}
+\label{eq:Hb}
+\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
+&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
+\end {eqnarray}
+
+and
+
+\begin{eqnarray}
+\label{eq:Ha}
+\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.71+0.48 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
+&~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right).
+\end {eqnarray}
+
+Having defined the recipes, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
+14 of the overall systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged \mbh\ value.
+We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}.
+
+\section{\hst\ observations}
 \label{observation}
@@
 
-\section{Analysis}
-\label{sec:analysis}
-
-\subsection{Surface Photometry}
-\subsubsection{PSF library}    
+%\section{Analysis}
+\subsection{PSF library}
 \label{sec:psf_library}
@@
 
+%\label{sec:analysis}
+
+%\subsection{Surface Photometry}
+%\subsubsection{PSF library}    
 %\subsubsection{Surface Photometry modeling method}
-\subsubsection{AGN-host Decomposition}
+\section{AGN-host Decomposition}
 %Introduce the lenstronomy. Model the PSF in each library.\\
@@
 
-\subsubsection{Host luminosity and stellar mass}
+\subsection{Masks objects for the COSMOS-CID206 and ECDFS-358}
+
+\section{Results}
+\label{sec:result}
+
+\subsection{Host galaxy properties}
 %The overall fitting plot: 1. Host-R-n corner for f140w and f814w. 2. The histogram with different selection.
@@
 
-\subsection{BH masses}
-\label{mbh}
- %Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g.
-McLure 2002; Shen 2013)}.
-This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
-To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}.
-We find that the \hbeta\ estimator is very consistent ($<0.03$~dex) between the two references.
-Moreover, in \citet{Schulze2018}, the cross-calibrate between the \halpha\ and \hbeta\ are consistent.
-Thus, we adopt the virial formalism from \citet{Schulze2018}:
-\begin{eqnarray}
-\label{eq:Hb}
-\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
-&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
-\end {eqnarray}
-
-and
-
-\begin{eqnarray}
-\label{eq:Ha}
-\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.71+0.48 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
-&~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right).
-\end {eqnarray}
-
-Having defined the recipes, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
-14 of the overall systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged \mbh\ value.
-We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}.
-
-\section{Results}
-\label{sec:result}
 \subsection{\mbh-\lhost\ relation}
@@
 \subsection{\mbh-M$_*$ relation}
-\subsubsection{Stellar mass estimates}
-stellar mass \\
+
+\subsection{Selection effect}
+
+\section{discussion}
+\label{sec:dis}
+\subsection{Systematic error}
+\subsection{JWST}
 
@@
 %We presented the study of the \mbh\ and host property's evolution to high redshift until 1.7.
-
-\section{discuss}
-\label{sec:dis}
-\subsection{Systematic error}
-\subsection{Masks objects for the COSMOS-CID206 and ECDFS-358}
 
@@
 \tablewidth{0pt}
-\tablecaption{Inferred \mbh\.} 
+\tablecaption{Inferred \mbh\ .} 
 \tablehead

### 2019-03-12 manuscript/manuscript.tex
Re-sort the section with John's suggestion

@@
 Thus, we adopt the virial formalism from \citet{Schulze2018}:
+
 \begin{eqnarray}
-\label{eq:Hb}
-\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
-&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
+\label{eq:Ha}
+\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.71+0.48 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
+&~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right).
 \end {eqnarray}
@@
 \begin{eqnarray}
-\label{eq:Ha}
-\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.71+0.48 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
-&~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right).
+\label{eq:Hb}
+\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
+&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
 \end {eqnarray}
@@
 
-\begin{deluxetable}{llccc}
-\tablecolumns{5}
+\begin{deluxetable}{llcccc}
+\tablecolumns{6}
 \tablewidth{0pt}
@@
 \colhead{$RA$}&
-\colhead{$DEC$}
+\colhead{$DEC$}&
+\colhead{Observing date}
 \\ 
@@
 \colhead{(4)} &
-\colhead{(5)} 
+\colhead{(5)} &
+\colhead{(6)}
 } 
@@
 %\\
-COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595\\
-COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258\\
-COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088\\
-COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729\\
-COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243\\
-COSMOS-CID255 & 1.664 & F140W & 150.1017 & 1.8483\\
-COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452\\
-COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076\\
-COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371\\
-COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307\\
-COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833\\
-COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448\\
-COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449\\
-COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231\\
-COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701\\
-COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275\\
-COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588\\
-COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617\\
-COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781\\
-COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969\\
-COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425\\
-CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600\\ 
-CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580\\ 
-CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239\\ 
-CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940\\ 
-ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370\\ 
-SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498\\ 
-SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602\\ 
-SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334\\ 
-SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781\\ 
-SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864\\ 
-SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291\\ 
+COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 \\
+COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 \\
+COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 \\
+COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 \\
+COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 \\
+COSMOS-CID255 & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 \\
+COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 \\
+COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 \\
+COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 \\
+COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 \\
+COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 \\
+COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 \\
+COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 \\
+COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 \\
+COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 \\
+COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 \\
+COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 \\
+COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 \\
+COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 \\
+COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 \\
+COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12\\
+CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 \\ 
+CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 \\ 
+CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18\\ 
+CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 \\ 
+ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09\\ 
+SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29\\ 
+SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01\\ 
+SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 \\ 
+SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 \\ 
+SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 \\ 
+SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 \\ 
 \enddata
@@
 Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
+Column 6: The observing start date.
 }
@@
 XID2396 & 2271.2617 & 44.06196 & 8.455 & 2657.8386 & 45.50467 & 8.511 \\
-CDFS-1 & ... & ... & ... & ... & ... & ... \\
-CDFS-229 & ... & ... & ... & ... & ... & ... \\
+CDFS-1 & 5449.4022 & 43.08 & 8.789 & ... & ... & ... \\
+CDFS-229 & 2254.0105 & 43.3 & 8.082 & ... & ... & ... \\
 CDFS-321 & 2441.93 & 43.92714 & 8.457 & ... & ... & ... \\
-CDFS-724 & ... & ... & ... & ... & ... & ... \\
+CDFS-724 & 3342.3888 & 42.81 & 8.21 & ... & ... & ... \\
 ECDFS-358 & 2237.2314 & 43.39674 & 8.122 & ... & ... & ... \\

### 2019-03-18 manuscript/manuscript.tex
Create the figure and update the manuscript

@@
 
-\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{2}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{2},  Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
+\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{1},  Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
  }
  \email{dxh@astro.ucla.edu}
-\altaffiltext{1}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
-\altaffiltext{2}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
+\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
+\altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
 \altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
@@
 The paper is organized as follows.
-We briefly describe the sample selection, observation and data reduction in Section~\ref{sec:data}.
-We infer the host galaxy surface photometry and \mbh\ in Section~\ref{sec:analysis}.
-In Section~\ref{sec:result}, we present our main result by adopting K-correction and SED fitting, to infer the rest-frame R band \lhost\ and \smass in order to compare with the local samples.
-Discussion and conclusion are presented in Section~\ref{sec:sum} and Section~\ref{sec:dis}.
+We briefly describe the sample selection and the BH mass of the sample in Section~\ref{sec:data}.
+We describe the observation and collect the PSF library in Section~\ref{observation}.
+In Section~\ref{sec:analysis} we decompose our sample and study the host galaxy surface photometry.
+In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population, which we applied to derive the rest-frame R band \lhost\ and \smass and compared to the local samples.
+Discussion and conclusion are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}.
 
@@
 
-\subsection{Local comparison sample}
-For the calibration with the local relation, we use 19 local AGN measurements \citep{Ben++10, Peterson2004} which define the zero-point. 
-To compare with the samples in the literature, we also adopt the samples from \citet{Ding2017b}, which include the measurements by \citet{Pen++06qsob, Park15} to study the \mbh-\lhost\ of 127 objects by \hst.
+\subsection{Comparison sample}
+\textcolor{blue}{
+We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
+For calibrating with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11a) to define our zero-point.
+The sample by B10 consistent 19 \mbh-\lhost\ relations with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex).
+The work of B11 contain 25 \mbh-\smass\ local active AGN analysis, where the \mbh\ are measured from single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
+To increase the local \smass\ and \mbh\ to higher range, we also include the inactive galaxies (mainly ellipticals or S0) as done by \citet{H+R04}.
+It is worth note that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample.
+In other words, it is the local \mbh-\smass$_{Bulge}$ relation that we compared.
+}
+
+\textcolor{blue}{
+Including the compared samples at the intermediate redshift range would help to understand the redshift evolution of these correlations.
+We compared intermediate redshift AGNs for the \mbh-\lhost\ relation include 52 sample by \citet{Park15} at $0.36<z<0.57$ and 27 sample by \citet{Bennert11, SS13} at $0.5<z<1.9$.
+Moreover, \citet{SS13} also derive the \smass\ which enable us to compare to the \mbh-\smass\ relation at $0.5<z<1.2$.
+}
 
@@
 \section{AGN-host Decomposition}
+\label{sec:analysis}
 %Introduce the lenstronomy. Model the PSF in each library.\\
@@
 Furthermore, we fit other galaxies that happen to be close to the AGN as additional \sersic\ model, to account for any potential contamination.
+\textcolor{blue}{The systems CID206 and ECDFS-358 have nearby objects which cannot be described by \sersic\ model, we thus mask their objects out in the fitting.}
 
@@
 
-%ECDFS-358 and CID206
 In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e.
@@
 The inference of the host properties is weighted by eight top-ranked PSFs.
+For a smaller number of PSFs one tends to underestimate the uncertainties.
 To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the one inferred by five and ten top-ranked PSFs.
 As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference is solid when the amount of selected PSF exceeds five.
-For a smaller number of PSFs one tends to underestimate the uncertainties.
 
@@
 
-\subsection{Masks objects for the COSMOS-CID206 and ECDFS-358}
-
 \section{Results}
@@
 \subsection{Host galaxy properties}
-%The overall fitting plot: 1. Host-R-n corner for f140w and f814w. 2. The histogram with different selection.
-\textcolor{red}{To be written:}
-\\1. Describe the SED fitting and the ground-based photometry data.
-\\2. The comparison of our host-to-total flux ratios to the SED decomposed ones.
-\\3. The inferred rest-frame R band magnitude and stellar mass.
+We derive the rest-frame R band magnitude and luminosity of our sample based on their filter magnitude obtained last section.
+The 18/32 systems which has multi-band host magnitude able us to select the best stellar population that could fit to the overall sample.
+We find that the 1 Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these sample.
+Adopting this stellar population, we perform the K-correction and derive the rest-frame R band magnitude of our sample.
+We further derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.
+We estimate of the stellar mass content of each host galaxy by adopt the mass-to-light ratio (M/L) based on the stellar population we adopted.
+\textcolor{red}{Need to add the uncertainty level of their inference}.
 
-Having inferred the value of the rest-frame R-band magnitude, the luminosity is derived by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.
-
-\textcolor{blue}{Introduce the passive evolution?}
-\\To directly compare with local samples, we consider the passive evolution scenario for the inferred \lhost\ and transfer to its expected value at today.
-
-We summarized the inferred R-band luminosities in Table~\ref{tab:result_sersic}.
+The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare them to the \mbh.
 
 \subsection{\mbh-\lhost\ relation}
+We show the comparing between the \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (a). Following common practice, we fit the local relation as a linear relation,
+\begin{eqnarray}
+\label{eq:MLlocal}
+\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}})
+\end {eqnarray}
+which enable a direct comparison to the distant sample.
+The figure shows that the observed \mbh-\lhost\ relation for our measurements  are nearly identical to the local and intermediate ones, indicating that the black hole mass and the host luminosity located at a similar relation at different galaxy age.
+However, considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ relations to today so as to compare in an equivalent frame.
+Especially, in a passive evolution scenario, we expect \lhost\ to fade over time.
+Thus, we follow \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
+$d{\rm mag}_{\rm R} \sim d\log(1+z)$, i.e.,
+\begin{eqnarray}
+\label{eq:L_relation}
+\log(L_{R,0})=\log(L_{R}) - 1.48 \log (1+z).
+\end{eqnarray} 
+This formulism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer to the \citet[][section 5.4]{Ding2017b} for more details.
 
-\subsection{\mbh-M$_*$ relation}
+We show the evolution-corrected \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (b) and find that at fixed \mbh\ the BH in the more distant universe tends to reside in less luminous hosts.
+To quantitatively understand this trend, We fit this offset as a function of redshift in the form:
+\begin{eqnarray}
+\label{eq:offset}
+\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
+\end{eqnarray} 
+where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{L_{R,0}}{10^{10}L_{\odot}})$.
+The best-fit and  1-$\sigma$ inference are $\gamma = 0.59 \pm 0.16$.
+
+Given that the current fit does not take into account selection effects yet, we draw the conclusion in the section~\ref{select_eff}
+
+\subsection{\mbh-\smass\ relation}
+The correlation of the \mbh-\smass\ would be more beneficial to help understand the connection between their coevolution.
+In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample and visually see that the mass distributions for three samples are very similar.
+Similar to last section, we fit the offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$ and obtain $\gamma = 0.46 \pm 0.19$ which slightly indicates as positive, see Figure~\ref{fig:MM-vz}, left panel.
+In the of Figure~\ref{fig:MM-vz}, right panel, we show the ratio of \mbh-\smass of the three sample at different redshift.
+We highlight that our results are less biased in both the measurement of \mbh\ and \smass.
+
+Note that the local sample we adopt are bulge dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
+That is, we are comparing the \mbh-\smass$_{,total}$ at distant universe to the \mbh-\smass$_{,bulge}$ at the local.
+Considering that a major part of our measurements have indicated the disk component, i.e.
+the systems with fitted \sersic\ index close to 1.
+Thus, the \smass$_{,bluge}$ of our sample and the SS13 sample are supposed to be less.
+Without taking into account the selection effect, the direct comparison shows that the growth of the black hole predates that of the host bulge.
 
 \subsection{Selection effect}
+\label{select_eff}
 
@@
 
-\tabcolsep=0.05cm
+\tabcolsep=0.03cm
 \begin{deluxetable*}
-{@{\extracolsep{4pt}}lccccccccc}   % need for the gap between the clines.
+{@{\extracolsep{4pt}}lcccccccccc}   % need for the gap between the clines.
 \tablecolumns{9}
@@
   \multicolumn{5}{c}{WFC3}&
-  \multicolumn{3}{c}{ACS} \\
-  \cline{2-6}  \cline{7-9} \\
+  \multicolumn{3}{c}{ACS} &
+   \multicolumn{2}{c}{host properties} \\
+  \cline{2-6}  \cline{7-9} \cline{10-11}  \\
 \colhead{}& 
@@
 \colhead{magnitude}&
-\colhead{reduced $\chi ^2$}& \colhead{host-to-total flux ratio}& \colhead{magnitude} & \colhead{$\log L_R$}\\
+\colhead{reduced $\chi ^2$}& \colhead{host-to-total flux ratio}& \colhead{magnitude} &
+\colhead{$\log L_R$} &\colhead{$\log M_*$} \\
 \colhead{}& 
@@
 \colhead{(AB system)}& \colhead{}& 
-\colhead{}& \colhead{(AB system)}&\colhead{($L_{\odot,R}$)} \\
+\colhead{}& \colhead{(AB system)} &\colhead{($L_{\odot,R}$)} & \colhead{(M$_{\odot}$)}\\
 \colhead{(1)}& 
@@
 \colhead{(6)}& \colhead{(7)}& 
-\colhead{(8)}& \colhead{(9)}&\colhead{(10)}
+\colhead{(8)}& \colhead{(9)}&
+\colhead{(10)}& \colhead{(11)}
 }
 \startdata 
-CID1174 & $2.307$ & $41.5\%\pm11.7\%$ & $0\farcs{}309\pm0\farcs{}065$ & $1.862\pm1.26$ & $21.482\substack{+0.374\\-0.277}$ & $2.496$ & $11.2\%\pm1.1\%$ & $23.214\substack{+0.113\\-0.103}$ \\
-CID1281 & $1.322$ & $49.3\%\pm13.7\%$ & $0\farcs{}239\pm0\farcs{}094$ & $3.146\pm1.483$ & $22.879\substack{+0.362\\-0.271}$ & $1.378$ & $18.5\%\pm7.7\%$ & $24.828\substack{+0.595\\-0.382}$ \\
-CID206 & $2.054$ & $35.3\%\pm24.3\%$ & $0\farcs{}286\pm0\farcs{}146$ & $3.072\pm2.476$ & $21.822\substack{+1.298\\-0.575}$ & $1.903$ & $7.7\%\pm2.4\%$ & $23.671\substack{+0.403\\-0.293}$ \\
-CID216 & $1.514$ & $93.9\%\pm4.7\%$ & $0\farcs{}251\pm0\farcs{}063$ & $6.159\pm1.205$ & $21.51\substack{+0.052\\-0.049}$ & $1.425$ & $35.1\%\pm1.5\%$ & $23.446\substack{+0.053\\-0.051}$ \\
-CID237 & $2.349$ & $29.9\%\pm6.3\%$ & $0\farcs{}872\pm0\farcs{}172$ & $4.736\pm1.701$ & $21.279\substack{+0.26\\-0.209}$ & $2.354$ & $3.2\%\pm2.0\%$ & $23.718\substack{+1.037\\-0.52}$ \\
-CID255 & ... & ... & ... & ... & ... & ... & ... & ...\\
-CID3242 & $2.751$ & $46.1\%\pm12.7\%$ & $0\farcs{}201\pm0\farcs{}159$ & $6.142\pm1.874$ & $21.161\substack{+0.35\\-0.264}$ & $2.596$ & $4.8\%\pm1.3\%$ & $23.595\substack{+0.337\\-0.257}$ \\
-CID3570 & $1.665$ & $76.5\%\pm1.6\%$ & $0\farcs{}698\pm0\farcs{}007$ & $0.728\pm0.054$ & $21.164\substack{+0.021\\-0.021}$ & $1.332$ & $85.6\%\pm1.5\%$ & $22.971\substack{+0.012\\-0.012}$ \\
-CID452 & $1.684$ & $75.4\%\pm3.9\%$ & $0\farcs{}365\pm0\farcs{}015$ & $1.402\pm0.175$ & $21.176\substack{+0.063\\-0.06}$ & $1.452$ & $37.8\%\pm0.7\%$ & $22.732\substack{+0.022\\-0.022}$ \\
-CID454 & $2.203$ & $35.8\%\pm2.5\%$ & $0\farcs{}388\pm0\farcs{}016$ & $0.624\pm0.106$ & $21.196\substack{+0.08\\-0.074}$ & $1.291$ & $9.2\%\pm0.5\%$ & $23.352\substack{+0.058\\-0.055}$ \\
-CID50 & $5.576$ & $16.5\%\pm9.0\%$ & $0\farcs{}163\pm0\farcs{}11$ & $3.217\pm2.223$ & $20.934\substack{+0.863\\-0.475}$ & $4.940$ & $5.0\%\pm3.3\%$ & $22.504\substack{+1.145\\-0.545}$ \\
-CID543 & $1.902$ & $30.6\%\pm9.7\%$ & $0\farcs{}1\pm0\farcs{}0$ & $0.493\pm0.325$ & $21.994\substack{+0.406\\-0.295}$ & $1.435$ & $5.2\%\pm2.0\%$ & $23.765\substack{+0.534\\-0.357}$ \\
-CID597 & $1.565$ & $42.4\%\pm16.6\%$ & $0\farcs{}173\pm0\farcs{}058$ & $1.752\pm0.784$ & $21.868\substack{+0.543\\-0.36}$ & $1.254$ & $11.5\%\pm1.3\%$ & $23.563\substack{+0.126\\-0.113}$ \\
-CID607 & $1.692$ & $43.6\%\pm17.9\%$ & $0\farcs{}206\pm0\farcs{}087$ & $3.418\pm1.097$ & $21.189\substack{+0.575\\-0.374}$ & $2.590$ & $4.7\%\pm1.8\%$ & $23.566\substack{+0.511\\-0.346}$ \\
-CID70 & $2.041$ & $19.7\%\pm4.9\%$ & $0\farcs{}422\pm0\farcs{}095$ & $3.616\pm1.028$ & $21.862\substack{+0.304\\-0.237}$ & $2.361$ & $2.3\%\pm1.1\%$ & $24.625\substack{+0.677\\-0.414}$ \\
-LID1273 & $1.697$ & $53.3\%\pm9.1\%$ & $0\farcs{}302\pm0\farcs{}04$ & $1.22\pm0.49$ & $20.939\substack{+0.211\\-0.176}$ & $2.137$ & $6.4\%\pm0.8\%$ & $23.289\substack{+0.153\\-0.134}$ \\
-LID1538 & $2.362$ & $43.5\%\pm7.8\%$ & $0\farcs{}177\pm0\farcs{}042$ & $2.819\pm0.475$ & $21.251\substack{+0.221\\-0.184}$ & $2.173$ & $7.5\%\pm1.2\%$ & $23.088\substack{+0.189\\-0.161}$ \\
-LID360 & $3.918$ & $18.4\%\pm2.0\%$ & $0\farcs{}626\pm0\farcs{}02$ & $0.752\pm0.355$ & $21.455\substack{+0.136\\-0.121}$ & $4.914$ & $3.7\%\pm0.5\%$ & $23.254\substack{+0.172\\-0.149}$ \\
-XID2138 & $1.597$ & $38.9\%\pm5.5\%$ & $0\farcs{}498\pm0\farcs{}033$ & $1.24\pm0.391$ & $21.869\substack{+0.172\\-0.148}$ & $2.731$ & $5.0\%\pm1.3\%$ & $23.898\substack{+0.313\\-0.243}$ \\
-XID2202 & $3.23$ & $33.3\%\pm8.0\%$ & $0\farcs{}1\pm0\farcs{}001$ & $3.957\pm1.017$ & $21.16\substack{+0.302\\-0.236}$ & $3.852$ & $8.3\%\pm1.9\%$ & $22.592\substack{+0.286\\-0.226}$ \\
-XID2396 & $3.669$ & $23.9\%\pm10.5\%$ & $0\farcs{}584\pm0\farcs{}085$ & $0.772\pm1.36$ & $21.404\substack{+0.652\\-0.404}$ & $5.346$ & $2.3\%\pm0.5\%$ & $23.364\substack{+0.243\\-0.198}$ \\
-CDFS-1 & $1.358$ & $64.5\%\pm19.7\%$ & $0\farcs{}137\pm0\farcs{}069$ & $4.806\pm1.112$ & $22.468\substack{+0.397\\-0.29}$ & ... & ... & ... \\
-CDFS-229 & $4.329$ & $17.6\%\pm2.1\%$ & $0\farcs{}507\pm0\farcs{}026$ & $0.463\pm0.195$ & $21.568\substack{+0.144\\-0.127}$ & ... & ... & ... \\
-CDFS-321 & $3.998$ & $24.5\%\pm11.7\%$ & $0\farcs{}378\pm0\farcs{}122$ & $2.26\pm2.007$ & $20.337\substack{+0.703\\-0.423}$ & ... & ... & ... \\
-CDFS-724 & $1.355$ & $34.7\%\pm14.6\%$ & $0\farcs{}118\pm0\farcs{}03$ & $1.618\pm1.099$ & $23.695\substack{+0.582\\-0.377}$ & ... & ... & ... \\
-ECDFS-358 & $2.012$ & $56.4\%\pm13.5\%$ & $0\farcs{}359\pm0\farcs{}043$ & $1.671\pm0.542$ & $21.34\substack{+0.302\\-0.236}$ & ... & ... & ... \\
-SXDS-X1136 & $1.937$ & $40.5\%\pm7.8\%$ & $0\farcs{}101\pm0\farcs{}003$ & $1.986\pm0.483$ & $21.921\substack{+0.231\\-0.19}$ & ... & ... & ... \\
-SXDS-X50 & $1.423$ & $40.7\%\pm8.6\%$ & $0\farcs{}192\pm0\farcs{}04$ & $1.648\pm0.621$ & $21.988\substack{+0.267\\-0.214}$ & ... & ... & ... \\
-SXDS-X717 & $1.426$ & $61.4\%\pm9.1\%$ & $0\farcs{}264\pm0\farcs{}066$ & $5.58\pm1.421$ & $21.759\substack{+0.176\\-0.151}$ & ... & ... & ... \\
-SXDS-X735 & $2.203$ & $32.4\%\pm8.5\%$ & $0\farcs{}22\pm0\farcs{}057$ & $2.027\pm1.012$ & $20.919\substack{+0.333\\-0.254}$ & ... & ... & ... \\
-SXDS-X763 & $2.376$ & $6.0\%\pm4.0\%$ & $0\farcs{}694\pm0\farcs{}532$ & $2.394\pm0.796$ & $24.134\substack{+1.172\\-0.55}$ & ... & ... & ... \\
-SXDS-X969 & $1.613$ & $29.1\%\pm11.1\%$ & $0\farcs{}11\pm0\farcs{}019$ & $2.053\pm1.071$ & $21.591\substack{+0.515\\-0.348}$ & ... & ... & ... \\
+CID1174 & $2.307$ & $41.5\%\pm11.7\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.86\pm1.26$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11.2\%\pm1.1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.13$ &$10.85$\\
+CID1281 & $1.322$ & $49.3\%\pm13.7\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.15\pm1.48$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $18.5\%\pm7.7\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.49$ &$10.21$\\
+CID206 & $2.054$ & $35.3\%\pm24.3\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.07\pm2.48$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $7.7\%\pm2.4\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.95$ &$10.66$\\
+CID216 & $1.514$ & $93.9\%\pm4.7\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.16\pm1.21$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35.1\%\pm1.5\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.13$ &$10.85$\\
+CID237 & $2.349$ & $29.9\%\pm6.3\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.74\pm1.70$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3.2\%\pm2.0\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26$ &$10.98$\\
+CID255 & ... & ... & ... & ... & ... & ... & ... & ... & ... &...\\
+CID3242 & $2.751$ & $46.1\%\pm12.7\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.14\pm1.87$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $4.8\%\pm1.3\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25$ &$10.97$\\
+CID3570 & $1.665$ & $76.5\%\pm1.6\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.73\pm0.05$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $85.6\%\pm1.5\%$ & $22.97\substack{+0.01\\-0.01}$ & $11.07$ &$10.79$\\
+CID452 & $1.684$ & $75.4\%\pm3.9\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.40\pm0.18$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $37.8\%\pm0.7\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.21$ &$10.93$\\
+CID454 & $2.203$ & $35.8\%\pm2.5\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.62\pm0.11$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9.2\%\pm0.5\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.19$ &$10.91$\\
+CID50 & $5.576$ & $16.5\%\pm9.0\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.22\pm2.22$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5.0\%\pm3.3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.15$ &$10.87$\\
+CID543 & $1.902$ & $30.6\%\pm9.7\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.49\pm0.33$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5.2\%\pm2.0\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.79$ &$10.51$\\
+CID597 & $1.565$ & $42.4\%\pm16.6\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.75\pm0.78$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $11.5\%\pm1.3\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.81$ &$10.53$\\
+CID607 & $1.692$ & $43.6\%\pm17.9\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.42\pm1.10$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $4.7\%\pm1.8\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.10$ &$10.82$\\
+CID70 & $2.041$ & $19.7\%\pm4.9\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.62\pm1.03$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2.3\%\pm1.1\%$ & $24.63\substack{+0.68\\-0.41}$ & $11.07$ &$10.79$\\
+LID1273 & $1.697$ & $53.3\%\pm9.1\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.22\pm0.49$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6.4\%\pm0.8\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.40$ &$11.12$\\
+LID1538 & $2.362$ & $43.5\%\pm7.8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.82\pm0.48$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $7.5\%\pm1.2\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.21$ &$10.93$\\
+LID360 & $3.918$ & $18.4\%\pm2.0\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.75\pm0.36$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $3.7\%\pm0.5\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.17$ &$10.88$\\
+XID2138 & $1.597$ & $38.9\%\pm5.5\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.24\pm0.39$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5.0\%\pm1.3\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.98$ &$10.70$\\
+XID2202 & $3.23$ & $33.3\%\pm8.0\%$ & $0\farcs{}10\pm0\farcs{}00$ & $3.96\pm1.02$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8.3\%\pm1.9\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.24$ &$10.96$\\
+XID2396 & $3.669$ & $23.9\%\pm10.5\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.77\pm1.36$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2.3\%\pm0.5\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.20$ &$10.92$\\
+CDFS-1 & $1.358$ & $64.5\%\pm19.7\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.81\pm1.11$ & $22.47\substack{+0.40\\-0.29}$ & ... & ... & ... & $10.80$ &$10.52$\\
+CDFS-229 & $4.329$ & $17.6\%\pm2.1\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.46\pm0.20$ & $21.57\substack{+0.14\\-0.13}$ & ... & ... & ... & $10.98$ &$10.70$\\
+CDFS-321 & $3.998$ & $24.5\%\pm11.7\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.26\pm2.01$ & $20.34\substack{+0.70\\-0.42}$ & ... & ... & ... & $11.61$ &$11.33$\\
+CDFS-724 & $1.355$ & $34.7\%\pm14.6\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.62\pm1.10$ & $23.70\substack{+0.58\\-0.38}$ & ... & ... & ... & $10.14$ &$9.86$\\
+ECDFS-358 & $2.012$ & $56.4\%\pm13.5\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.67\pm0.54$ & $21.34\substack{+0.30\\-0.24}$ & ... & ... & ... & $11.25$ &$10.97$\\
+SXDS-X1136 & $1.937$ & $40.5\%\pm7.8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $1.99\pm0.48$ & $21.92\substack{+0.23\\-0.19}$ & ... & ... & ... & $10.84$ &$10.56$\\
+SXDS-X50 & $1.423$ & $40.7\%\pm8.6\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.65\pm0.62$ & $21.99\substack{+0.27\\-0.21}$ & ... & ... & ... & $10.89$ &$10.61$\\
+SXDS-X717 & $1.426$ & $61.4\%\pm9.1\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.58\pm1.42$ & $21.76\substack{+0.18\\-0.15}$ & ... & ... & ... & $10.86$ &$10.58$\\
+SXDS-X735 & $2.203$ & $32.4\%\pm8.5\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.03\pm1.01$ & $20.92\substack{+0.33\\-0.25}$ & ... & ... & ... & $11.28$ &$11.00$\\
+SXDS-X763 & $2.376$ & $6.0\%\pm4.0\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.39\pm0.80$ & $24.13\substack{+1.17\\-0.55}$ & ... & ... & ... & $10.03$ &$9.75$\\
+SXDS-X969 & $1.613$ & $29.1\%\pm11.1\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.05\pm1.07$ & $21.59\substack{+0.52\\-0.35}$ & ... & ... & ... & $11.12$ &$10.83$\\
 \enddata
@@
 Column~7-9: ACS inference. 
-Column~10: Inferred host Luminosity in the rest-frame R band.
+Column~10: Inferred observed host Luminosity in the rest-frame R band.
+Column~10: Inferred host total stellar mass.
 }
@@
 \begin{deluxetable*}
-{@{\extracolsep{4pt}}lcccccc}   % need for the gap between the clines.
-\tablecolumns{7}
+{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
+\tablecolumns{9}
 \tablewidth{0pt}
@@
 \colhead{Target ID}&
-  \multicolumn{3}{c}{using emission line \halpha}&
-  \multicolumn{3}{c}{using emission line \hbeta} \\
-  \cline{2-4}  \cline{5-7} \\
+  \multicolumn{4}{c}{using emission line \halpha}&
+  \multicolumn{4}{c}{using emission line \hbeta} \\
+  \cline{2-5}  \cline{6-9} \\
 \colhead{}& 
-\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}&
-\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}\\
+\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}& Eddington ratio &
+\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}& Eddington ratio \\
 \colhead{}& 
 \colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
-\colhead{(M$_{\odot}$)}& \colhead{(\kms)}& 
-\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
+\colhead{(M$_{\odot}$)}& (log$\lambda$)&
+\colhead{(\kms)}& 
+\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$\lambda$)\\
 \colhead{(1)}& 
@@
 \colhead{(4)}& \colhead{(5)}& 
-\colhead{(6)}&\colhead{(7)}
+\colhead{(6)}&\colhead{(7)}&
+\colhead{(8)}& \colhead{(9)}
 }
 \startdata 
-CID1174 & 1906.3037 & 43.43237 & 7.992 & 5898.264 & 44.76243 & 8.833 \\
-CID1281 & 1619.4891 & 43.23945 & 7.749 & ... & ... & ... \\
-CID206 & 3333.5527 & 43.4776 & 8.528 & ... & ... & ... \\
-CID216 & 2229.5232 & 42.84509 & 7.854 & ... & ... & ... \\
-CID237 & 2112.3306 & 43.85546 & 8.289 & ... & ... & ... \\
-CID255 & 1932.0933 & 43.9924 & 8.273 & 3709.241 & 45.37122 & 8.734 \\
-CID3242 & 2543.2202 & 43.83323 & 8.449 & 3774.503 & 45.09891 & 8.613 \\
-CID3570 & 1958.8551 & 43.16374 & 7.888 & ... & ... & ... \\
-CID452 & 3457.8801 & 42.92298 & 8.295 & 3127.3306 & 44.63353 & 8.217 \\
-CID454 & 2824.2693 & 43.34466 & 8.311 & ... & ... & ... \\
-CID50 & 2339.9104 & 43.93786 & 8.423 & 1938.5676 & 45.32766 & 8.149 \\
-CID543 & 2188.8447 & 43.57404 & 8.187 & ... & ... & ... \\
-CID597 & 1656.3296 & 43.32955 & 7.813 & ... & ... & ... \\
-CID607 & 3009.1816 & 43.67079 & 8.526 & 4241.526 & 44.78209 & 8.556 \\
-CID70 & 2480.4058 & 43.50531 & 8.269 & 3981.8574 & 45.1582 & 8.689 \\
-LID1273 & 3223.8484 & 43.61001 & 8.561 & ... & ... & ... \\
-LID1538 & 2941.422 & 43.59594 & 8.469 & ... & ... & ... \\
-LID360 & 2481.7253 & 43.88091 & 8.45 & 2868.8992 & 45.08676 & 8.369 \\
-XID2138 & 3185.8613 & 43.6148 & 8.552 & 2944.7766 & 44.80782 & 8.252 \\
-XID2202 & 2973.2378 & 43.56249 & 8.463 & ... & ... & ... \\
-XID2396 & 2271.2617 & 44.06196 & 8.455 & 2657.8386 & 45.50467 & 8.511 \\
-CDFS-1 & 5449.4022 & 43.08 & 8.789 & ... & ... & ... \\
-CDFS-229 & 2254.0105 & 43.3 & 8.082 & ... & ... & ... \\
-CDFS-321 & 2441.93 & 43.92714 & 8.457 & ... & ... & ... \\
-CDFS-724 & 3342.3888 & 42.81 & 8.21 & ... & ... & ... \\
-ECDFS-358 & 2237.2314 & 43.39674 & 8.122 & ... & ... & ... \\
-SXDS-X1136 & 2759.8953 & 43.43305 & 8.333 & 6761.222 & 44.71429 & 8.927 \\
-SXDS-X50 & 1816.672 & 43.421 & 7.942 & ... & ... & ... \\
-SXDS-X717 & 2930.7417 & 43.04988 & 8.204 & ... & ... & ... \\
-SXDS-X735 & 2702.0962 & 43.69804 & 8.44 & 3519.6052 & 45.07463 & 8.54 \\
-SXDS-X763 & 2961.1743 & 43.57321 & 8.465 & 4508.5146 & 44.51285 & 8.474 \\
-SXDS-X969 & 2296.0566 & 43.50066 & 8.196 & 1695.7146 & 45.05337 & 7.895 \\
+CID1174 & 1906.3037 & 43.43237 & 7.992 & -0.504 & 5898.264 & 44.76243 & 8.833& -1.353 \\
+CID1281 & 1619.4891 & 43.23945 & 7.749 & -0.446 & ... & ... & ...& ... \\
+CID206 & 3333.5527 & 43.4776 & 8.528 & -0.997 & ... & ... & ...& ... \\
+CID216 & 2229.5232 & 42.84509 & 7.854 & -0.929 & ... & ... & ...& ... \\
+CID237 & 2112.3306 & 43.85546 & 8.289 & -0.397 & ... & ... & ...& ... \\
+CID255 & 1932.0933 & 43.9924 & 8.273 & -0.249 & 3709.241 & 45.37122 & 8.734& -0.628 \\
+CID3242 & 2543.2202 & 43.83323 & 8.449 & -0.578 & 3774.503 & 45.09891 & 8.613& -0.779 \\
+CID3570 & 1958.8551 & 43.16374 & 7.888 & -0.658 & ... & ... & ...& ... \\
+CID452 & 3457.8801 & 42.92298 & 8.295 & -1.296 & 3127.3306 & 44.63353 & 8.217& -0.879 \\
+CID454 & 2824.2693 & 43.34466 & 8.311 & -0.908 & ... & ... & ...& ... \\
+CID50 & 2339.9104 & 43.93786 & 8.423 & -0.451 & 1938.5676 & 45.32766 & 8.149& -0.086 \\
+CID543 & 2188.8447 & 43.57404 & 8.187 & -0.564 & ... & ... & ...& ... \\
+CID597 & 1656.3296 & 43.32955 & 7.813 & -0.424 & ... & ... & ...& ... \\
+CID607 & 3009.1816 & 43.67079 & 8.526 & -0.811 & 4241.526 & 44.78209 & 8.556& -1.055 \\
+CID70 & 2480.4058 & 43.50531 & 8.269 & -0.712 & 3981.8574 & 45.1582 & 8.689& -0.796 \\
+LID1273 & 3223.8484 & 43.61001 & 8.561 & -0.903 & ... & ... & ...& ... \\
+LID1538 & 2941.422 & 43.59594 & 8.469 & -0.825 & ... & ... & ...& ... \\
+LID360 & 2481.7253 & 43.88091 & 8.45 & -0.533 & 2868.8992 & 45.08676 & 8.369& -0.547 \\
+XID2138 & 3185.8613 & 43.6148 & 8.552 & -0.890 & 2944.7766 & 44.80782 & 8.252& -0.723 \\
+XID2202 & 2973.2378 & 43.56249 & 8.463 & -0.851 & ... & ... & ...& ... \\
+XID2396 & 2271.2617 & 44.06196 & 8.455 & -0.365 & 2657.8386 & 45.50467 & 8.511& -0.272 \\
+CDFS-1 & 5449.4022 & 43.08 & 8.789 & ... & ... & ... & ...& ... \\
+CDFS-229 & 2254.0105 & 43.3 & 8.082 & ... & ... & ... & ...& ... \\
+CDFS-321 & 2441.93 & 43.92714 & 8.457 & -0.496 & ... & ... & ...& ... \\
+CDFS-724 & 3351.8522 & 42.56 & 8.093 & ... & ... & ... & ...& ... \\
+ECDFS-358 & 2237.2314 & 43.39674 & 8.122 & -0.669 & ... & ... & ...& ... \\
+SXDS-X1136 & 2759.8953 & 43.43305 & 8.333 & -0.845 & 6761.222 & 44.71429 & 8.927& -1.500 \\
+SXDS-X50 & 1816.672 & 43.421 & 7.942 & -0.465 & ... & ... & ...& ... \\
+SXDS-X717 & 2930.7417 & 43.04988 & 8.204 & -1.083 & ... & ... & ...& ... \\
+SXDS-X735 & 2702.0962 & 43.69804 & 8.44 & -0.698 & 3519.6052 & 45.07463 & 8.54& -0.731 \\
+SXDS-X763 & 2961.1743 & 43.57321 & 8.465 & -0.842 & 4508.5146 & 44.51285 & 8.474& -1.271 \\
+SXDS-X969 & 2296.0566 & 43.50066 & 8.196 & -0.643 & 1695.7146 & 45.05337 & 7.895& -0.107 \\
 \enddata
@@
 
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+{\includegraphics[width=0.5\textwidth]{fig/MBH-L_obs.pdf}}&
+{\includegraphics[width=0.5\textwidth]{fig/MBH-L_ev.pdf}}\\
+\end{tabular}
+\caption{\label{fig:ML} 
+Observed \mbh-\lhost\ relation (left), evolution-corrected relation (right).}
+\end{figure*}
+
+\begin{figure}
+\centering
+{
+\includegraphics[height=0.4\textwidth]{fig/MBH-L-vz.pdf}
+}
+\caption{\label{fig:ML-vz} 
+The offset as a function of redshift.}
+\end{figure}
+
+\begin{figure}
+\centering
+{
+\includegraphics[height=0.4\textwidth]{fig/MBH-Mstar.pdf}
+}
+\caption{\label{fig:MM} 
+Comparison of the histogram of the inferred host flux ratio, based on the different amount of the top-ranked PSFs.}
+\end{figure}
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
+{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
+\end{tabular}
+\caption{\label{fig:MM-vz} 
+The inference MM-z relation}
+\end{figure*}
+
 %\appendix

### 2019-03-18 M_BH_relation/MM_all_vz.py

@@ -1,0 +1,189 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Oct 26 15:50:27 2018
+
+@author: Dartoon
+"""
+import numpy as np
+np.set_printoptions(precision=4)
+import matplotlib.pyplot as plt
+import matplotlib as mat
+import matplotlib.lines as mlines
+from matplotlib import colors
+mat.rcParams['font.family'] = 'STIXGeneral'
+host=plt.figure(figsize=(14.5,12))
+ax=host.add_subplot(111)   #to get the log(1+z) and z label
+
+import matplotlib as mpl
+mpl.rc('image', cmap='jet')
+import sys
+sys.path.insert(0,'../py_tools')
+
+########## input local data ####
+#==============================================================================
+# The seleting for dm and host_total and dmag are in this local
+#==============================================================================
+from local_MM_vz import *
+#==============================================================================
+#input Park's data 
+#==============================================================================
+################ bulge or total relaiton? #################
+#host= input('with bulge or total relation??? 0 = bulge;   1= total:')
+####### input Park data ####
+#######in AB system, V band#######
+f0 ='data/SS13_MM.txt'
+ss = np.loadtxt(f0)[:,1:]  #0 redshift; 1 M*; 2 BH mass;
+#if inp_SS13 ==1:
+#    plt.scatter(ss[:,1],ss[:,2],c=ss[:,0],marker="^",s=180,zorder=100,vmin=0.5, vmax=2, edgecolors='white')
+
+#%%
+#==============================================================================
+# My new inference
+#==============================================================================
+from load_result import load_host_p, load_MBH
+from load_result import load_zs, load_n
[…]

### 2019-03-18 M_BH_relation/local_ML_vz.py

@@ -1,0 +1,91 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+############### with evolution-corrected or not? #################
+#select = 1
+host = 1
+
+select= 1 #input('with evolution-corrected or not??? 0 = no;   1= yes, with dmag using dmag.py:')
+if select == 0:
+   dm=0
+if select == 1:
+   dm=1
+import sys
+sys.path.insert(0,'../py_tools')
+from dmag import pass_dmag
+########input Park local data ############
+f1 ='data/parklocal'
+Pklc = np.loadtxt(f1)
+#print np.shape(Pklc), len(Pklc)
+ploc=np.zeros([len(Pklc),4])
+
+#host= input('with bulge or total relation??? 0 = bulge;   1= total:')
+if host == 0:
+   ploc[:,1]= Pklc[:,6]    #LgV_sph
+if host == 1:
+   ploc[:,1]= Pklc[:,5]    #LgV_total
+ploc[:,0]= Pklc[:,0]    #redshift
+ploc[:,1]=0.4*(4.61+0.46-4.83)+ploc[:,1]-0.4*dm*pass_dmag(ploc[:,0])  #Change to LgR_sph, -0.4 is in L, be fainter
+ploc[:,2]= Pklc[:,8]-0.03    #LogBHmass
+ploc[:,3]= Pklc[:,9]    #delta mass
+loc=np.zeros([len(ploc),3])
+loc[:,0]=ploc[:,1]
+loc[:,1]=ploc[:,2]
+loc[:,2]=ploc[:,3]
+#############################################################
+#############################################################
+###################fitting with MCMC#########################
+x=loc[:,0]
+y=loc[:,1]
+yerr=loc[:,2]
+def lnlike(theta, x, y, yerr):
+    m, b, sint= theta
+    model = m * x + b
+    sigma2 = (yerr**2 + sint**2)
+    if sint>=0 :
+      return -0.5*(np.sum((y-model)**2/sigma2)+np.sum(np.log(2*np.pi*sigma2)))
+    else:
+      return -np.inf
+
+import scipy.optimize as op
+nll = lambda *args: -lnlike(*args)
[…]

### 2019-03-18 compare_to_Simulation/Nicola/mstar_compare.py

@@ -1,0 +1,193 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Mar  5 09:58:05 2019
+
+@author: Dartoon
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import copy, matplotlib
+import matplotlib as matt
+matt.rcParams['font.family'] = 'STIXGeneral'
+cmap = matplotlib.cm.get_cmap('viridis')
+import matplotlib as mpl
+mpl.rc('image', cmap='jet')
+
+#%% Load Nicola's data
+#filename = 'contour_all.dat'
+filename = 'contour_eddvar.dat'
+data = np.loadtxt(filename)
+prop_host = data[:,0]
+prop_mbh = data[:,1]
+number_dens = data[:,2]
+norm_number_dens = data[:,3]
+
+#%% Load the BH mass and the stellar mass
+import sys
+sys.path.insert(0,'../../py_tools')
+from load_result import load_zs, load_mag, load_n
+import re
+ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'CDFS-321', 'CID1174',\
+'CID216', 'CID237','CID3242','CID3570','CID452', 'CID454',\
+'CID50','CID607','LID1273', 'LID1538','LID360','SXDS-X1136',\
+'SXDS-X50', 'SXDS-X717','SXDS-X763','SXDS-X969','XID2138','XID2202',\
+'XID2396', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597','CID1281']
+zs = np.asarray(load_zs(ID))
+#lumi_s = 0.4*(4.61-host_mags)
+f = open("../../M_BH_relation/fmos_MBH_table","r")
+with f as g:
+    lines = g.readlines()
+porp_list = lines[0].replace('#','').split(' ')
+samples = [lines[i].split(' ') for i in range(1,len(lines))]
+ID_ser_dic =  {}
+
+MB_ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'ECDFS-321', 'CID1174',\
+'CID216', 'CID237','CID3242','CID3570','CID452', 'CID454',\
+'CID50','CID607','LID1273', 'LID1538','LID360','SXDS-X1136',\
[…]

### 2019-03-18 compare_with_Simulation/Nicola/mstar_compare.py

@@ -1,190 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Mar  5 09:58:05 2019
-
-@author: Dartoon
-"""
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-import copy, matplotlib
-import matplotlib as matt
-matt.rcParams['font.family'] = 'STIXGeneral'
-cmap = matplotlib.cm.get_cmap('viridis')
-import matplotlib as mpl
-mpl.rc('image', cmap='jet')
-
-#%% Load Nicola's data
-#filename = 'contour_all.dat'
-filename = 'contour_eddvar.dat'
-data = np.loadtxt(filename)
-prop_host = data[:,0]
-prop_mbh = data[:,1]
-number_dens = data[:,2]
-norm_number_dens = data[:,3]
-
-#%% Load the BH mass and the stellar mass
-import sys
-sys.path.insert(0,'../../py_tools')
-from load_result import load_zs, load_mag, load_n
-import re
-ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'CDFS-321', 'CID1174',\
-'CID216', 'CID237','CID3242','CID3570','CID452', 'CID454',\
-'CID50','CID607','LID1273', 'LID1538','LID360','SXDS-X1136',\
-'SXDS-X50', 'SXDS-X717','SXDS-X763','SXDS-X969','XID2138','XID2202',\
-'XID2396', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597','CID1281']
-zs = np.asarray(load_zs(ID))
-#lumi_s = 0.4*(4.61-host_mags)
-f = open("../../M_BH_relation/fmos_MBH_table","r")
-with f as g:
-    lines = g.readlines()
-porp_list = lines[0].replace('#','').split(' ')
-samples = [lines[i].split(' ') for i in range(1,len(lines))]
-ID_ser_dic =  {}
-
-MB_ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'ECDFS-321', 'CID1174',\
-'CID216', 'CID237','CID3242','CID3570','CID452', 'CID454',\
-'CID50','CID607','LID1273', 'LID1538','LID360','SXDS-X1136',\
[…]

### 2019-03-18 material/CANDELS_catalog/compare_with_CANDLESCOSMOS.py

@@ -1,170 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Mon Mar 11 15:46:19 2019
-
-@author: Dartoon
-
-Read the CANDLES-COSMOS catalog and see if the stellar mass and Reff has any relations:
-
-"""
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib
-import matplotlib as matt
-matt.rcParams['font.family'] = 'STIXGeneral'
-cmap = matplotlib.cm.get_cmap('viridis')
-import matplotlib as mpl
-mpl.rc('image', cmap='jet')
-
-from scipy.integrate import quad
-h0=70.             #km/s/Mpc
-om=0.3
-c=299790.        #speed of light [km/s]
-def EZ(z,om):
-      return 1/np.sqrt(om*(1+z)**3+(1-om))
-def EE(z):
-      return quad(EZ, 0, z , args=(om))[0]
-vec_EE=np.vectorize(EE)
-
-#The COSMOS files in http://www.mpia.de/homes/vdwel/candels.html by van der Wel et al. (2012).
-#   NUMBER         RA        DEC          f        mag       dmag         re        dre          n         dn          q         dq         pa        dpa          sn
-galfit_loc = np.loadtxt('cos_2epoch_wfc3_f160w_060mas_v1.0_galfit.cat')[:,[1,2]]  #RA, DEC
-galfit = np.loadtxt('cos_2epoch_wfc3_f160w_060mas_v1.0_galfit.cat')[:,[4,6,8,3]] # mag, re, n, flag
-
-##The data from 3D HST
-stellar_loc = np.loadtxt('cosmos_3dhst.v4.1.cat')[:,[3,4]]  # RA, DEC
-stellar = np.loadtxt('cosmos_3dhst.v4.1.fout')[:,[1,6,8]]  # redshift, stellar mass, star formation rate
-
-## Check if they are in a same field.
-#plt.plot(galfit_loc[:,0], galfit_loc[:,1],'.')
-#plt.plot(stellar_loc[:,0], stellar_loc[:,1],'r.')
-#plt.show()
-
-def find_ind(inp_list, inp_ind, find_list):
-    diff = np.sqrt(np.sum((find_list-inp_list[inp_ind])**2,axis=1)) * 3600 # Their difference in arcsec
[…]

### 2019-03-18 material/CANDELS_catalog/compare_with_CANDLESCOSMOS_SSFR.py

@@ -1,0 +1,229 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Mar 11 15:46:19 2019
+
+@author: Dartoon
+
+Read the CANDLES-COSMOS catalog and see if the stellar mass and Reff has any relations:
+
+"""
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+import matplotlib as matt
+matt.rcParams['font.family'] = 'STIXGeneral'
+cmap = matplotlib.cm.get_cmap('viridis')
+import matplotlib as mpl
+mpl.rc('image', cmap='jet')
+
+from scipy.integrate import quad
+h0=70.             #km/s/Mpc
+om=0.3
+c=299790.        #speed of light [km/s]
+def EZ(z,om):
+      return 1/np.sqrt(om*(1+z)**3+(1-om))
+def EE(z):
+      return quad(EZ, 0, z , args=(om))[0]
+vec_EE=np.vectorize(EE)
+
+#The COSMOS files in http://www.mpia.de/homes/vdwel/candels.html by van der Wel et al. (2012).
+#   NUMBER         RA        DEC          f        mag       dmag         re        dre          n         dn          q         dq         pa        dpa          sn
+galfit_loc = np.loadtxt('cos_2epoch_wfc3_f160w_060mas_v1.0_galfit.cat')[:,[1,2]]  #RA, DEC
+galfit = np.loadtxt('cos_2epoch_wfc3_f160w_060mas_v1.0_galfit.cat')[:,[4,6,8,3]] # mag, re, n, flag
+
+##The data from 3D HST
+stellar_loc = np.loadtxt('cosmos_3dhst.v4.1.cat')[:,[3,4]]  # RA, DEC
+stellar_flux_ap = np.loadtxt('cosmos_3dhst.v4.1.cat')[:,[69,51,39]]  # flux, F140w, F125w, F814w.
+stellar = np.loadtxt('cosmos_3dhst.v4.1.fout')[:,[1,6,8]]  # redshift, stellar mass, star formation rate
+
+## Check if they are in a same field.
+#plt.plot(galfit_loc[:,0], galfit_loc[:,1],'.')
+#plt.plot(stellar_loc[:,0], stellar_loc[:,1],'r.')
+#plt.show()
+
+def find_ind(inp_list, inp_ind, find_list):
[…]

### 2019-03-18 py_tools/load_LR_Mstar.py

@@ -1,0 +1,107 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Sat Mar 16 19:09:55 2019
+
+@author: Dartoon
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from load_result import load_zs, load_mag
+from dmag import pass_dmag
+import copy
+
+h0=70.             #km/s/Mpc
+om=0.3
+c=299790.        #speed of light [km/s]
+
+from scipy.integrate import quad
+def EZ(z,om):
+      return 1/np.sqrt(om*(1+z)**3+(1-om))
+def EE(z):
+      return quad(EZ, 0, z , args=(om))[0]
+vec_EE=np.vectorize(EE)
+
+def load_host_p(ID, temp='1Gyr', dm = 0):
+    zs = np.asarray(load_zs(ID))
+    mags = np.array(load_mag(ID, folder = '../')[0])
+    from dmag import k_corr_R
+    from filter_info import filt_info
+    dm_k_R = []
+    for i in range(len(zs)):
+        dm_k_R.append(k_corr_R(zs[i],filt_info[ID[i]], galaxy_age = '1Gyrs'))
+    dm_k_R = np.asarray(dm_k_R) # Get the k-correction for each target as an array
+    dl=(1+zs)*c*vec_EE(zs)/h0 *10**6   #in pc
+    host_Mags = mags -5*(np.log10(dl)-1) + dm_k_R + dm*pass_dmag(zs) # This is in AB system
+    host_Mags = host_Mags - 0.21  # Transfer to Vega system
+    host_LR = 10 ** (0.4*(4.61-host_Mags))
+    Mstar = np.log10(host_LR * 0.54 * 0.684 * 1.4191)  
+    return np.log10(host_LR), Mstar
+
+def load_MBH(ID, MB_ID):
+    #ID change:
+    #XID2202 to LID1622
+    #XID2138 to LID1820
+    #XID2396 to LID1878
+    #CDFS321 to ECDFS321
+    f = open("../M_BH_relation/fmos_MBH_table","r")
+    with f as g:
+        lines = g.readlines()
+#    porp_list = lines[0].replace('#','').split(' ')
+    samples = [lines[i].split(' ') for i in range(1,len(lines))]
+    ID_ser_dic =  {}
+    
+    for j in range(len(MB_ID)):
[…]

### 2019-03-19 manuscript/manuscript.tex
Before show TT

@@
 \def\efr{$R_{\mathrm{eff}}$}
-\def\galfit{\sc Galfit}
+\def\galfit{{\sc Galfit}}
 \def\mbh{$\mathcal M_{\rm BH}$}
@@
 total exposure time $\sim2394s$).
+Table~\ref{tab:objlist} lists the details of the observation.
 The six exposures for each dither image were combined with the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel.
@@
 Furthermore, we fit other galaxies that happen to be close to the AGN as additional \sersic\ model, to account for any potential contamination.
-\textcolor{blue}{The systems CID206 and ECDFS-358 have nearby objects which cannot be described by \sersic\ model, we thus mask their objects out in the fitting.}
+\textcolor{blue}{The systems CID206 and ECDFS-358 have nearby objects which could not be described by \sersic\ model, we thus mask these objects in the fitting.}
 
@@
 We derive the rest-frame R band magnitude and luminosity of our sample based on their filter magnitude obtained last section.
-The 18/32 systems which has multi-band host magnitude able us to select the best stellar population that could fit to the overall sample.
+18/32 systems have multi-band host magnitude which ables us to select the best stellar population that could fit to the overall sample.
 We find that the 1 Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these sample.
@@
 We estimate of the stellar mass content of each host galaxy by adopt the mass-to-light ratio (M/L) based on the stellar population we adopted.
-\textcolor{red}{Need to add the uncertainty level of their inference}.
+
+%\textcolor{red}{Need to add the uncertainty level of their inference}.
 
@@
 \subsection{\mbh-\lhost\ relation}
-We show the comparing between the \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (a). Following common practice, we fit the local relation as a linear relation,
+We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}, panel (a). Following common practice, we fit the local relation as a linear relation,
 \begin{eqnarray}
 \label{eq:MLlocal}
-\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}})
+\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}}),
 \end {eqnarray}
-which enable a direct comparison to the distant sample.
+which enables a direct comparison to the distant sample.
 The figure shows that the observed \mbh-\lhost\ relation for our measurements  are nearly identical to the local and intermediate ones, indicating that the black hole mass and the host luminosity located at a similar relation at different galaxy age.
-However, considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ relations to today so as to compare in an equivalent frame.
+However, considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
 Especially, in a passive evolution scenario, we expect \lhost\ to fade over time.
-Thus, we follow \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
+
+We follow \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
 $d{\rm mag}_{\rm R} \sim d\log(1+z)$, i.e.,
@@
 \end{eqnarray} 
-This formulism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer to the \citet[][section 5.4]{Ding2017b} for more details.
+This formulism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$.
+We refer to the \citet[][section 5.4]{Ding2017b} for more details.
+Transfering the \lhost\ to today, we show the evolution-corrected \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (b) and find that, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts.
 
-We show the evolution-corrected \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (b) and find that at fixed \mbh\ the BH in the more distant universe tends to reside in less luminous hosts.
-To quantitatively understand this trend, We fit this offset as a function of redshift in the form:
+To quantitatively understand this trend, we fit the offset as a function of redshift in form as:
 \begin{eqnarray}
@@
 where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{L_{R,0}}{10^{10}L_{\odot}})$.
-The best-fit and  1-$\sigma$ inference are $\gamma = 0.59 \pm 0.16$.
+The best-fit and  1-$\sigma$ inference are $\gamma = 0.69 \pm 0.15$.
 
-Given that the current fit does not take into account selection effects yet, we draw the conclusion in the section~\ref{select_eff}
+Given that the current result does not take into account selection effects yet, we will draw the conclusion in the section~\ref{select_eff}
 
 \subsection{\mbh-\smass\ relation}
-The correlation of the \mbh-\smass\ would be more beneficial to help understand the connection between their coevolution.
-In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample and visually see that the mass distributions for three samples are very similar.
-Similar to last section, we fit the offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$ and obtain $\gamma = 0.46 \pm 0.19$ which slightly indicates as positive, see Figure~\ref{fig:MM-vz}, left panel.
-In the of Figure~\ref{fig:MM-vz}, right panel, we show the ratio of \mbh-\smass of the three sample at different redshift.
+Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution.
+In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample.
+We visually see that the mass distributions for three samples are very similar.
+Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$.
+We obtain the $\gamma  = 0.49 \pm 0.19$ which slightly indicates as the positive, see Figure~\ref{fig:MM-vz}, panel (a).
+In the of Figure~\ref{fig:MM-vz}, panel (b), we also show the ratio of \mbh-\smass of the three sample at different redshift.
 We highlight that our results are less biased in both the measurement of \mbh\ and \smass.
 
-Note that the local sample we adopt are bulge dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
+We highlight that the local sample employed are bulge dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
 That is, we are comparing the \mbh-\smass$_{,total}$ at distant universe to the \mbh-\smass$_{,bulge}$ at the local.
-Considering that a major part of our measurements have indicated the disk component, i.e.
-the systems with fitted \sersic\ index close to 1.
-Thus, the \smass$_{,bluge}$ of our sample and the SS13 sample are supposed to be less.
+Considering that a major part of the distant systems have indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.
+
 Without taking into account the selection effect, the direct comparison shows that the growth of the black hole predates that of the host bulge.
@@
 \label{select_eff}
+\textcolor{red}{To be written after Daeseong's analysis.}.
 
@@
 \subsection{Systematic error}
+In our analysis, we adopt one stellar population to the overall sample.
+We note that adopting the private stellar populations for these sample which have both multi-band host magnitude could be more robust in principle.
+However, considering that the host magnitude in ACS band are faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost.
+Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry.
+\textcolor{red}{Describe the ground-based data}.
+In this paper, we focus on the decomposing of the AGN and carry out a rapid analysis of the \mbh-host raltions.
+The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.
+
+\subsection{Comparison with the inactive galaxies}
+To understand how the AGNs activity affect their galaxies's morphology, we compared the 32 host measurements to the inactive galaxies in CANDLES imaging survey.
+We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) from the CANDLES-COSMOS catalog.
+Their \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar mass are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.
+
+We compare the \smass-\Reff\ relations in Figure~\ref{fig:Mstar-rn}. The inference shows that our AGN host are located at a higher end of the stellar mass.
+
 \subsection{JWST}
@@
 
-\begin{deluxetable}{llcccc}
-\tablecolumns{6}
+\begin{deluxetable}{llccccc}
+\tablecolumns{7}
 \tablewidth{0pt}
-\tablecaption{Sample properties.} 
+\tablecaption{Details of Observation} 
 \tablehead{ 
@@
 \colhead{$DEC$}&
-\colhead{Observing date}
+\colhead{Observing date}&
+\colhead{Expousre time (s)}
 \\ 
@@
 \colhead{(5)} &
-\colhead{(6)}
+\colhead{(6)} &
+\colhead{(7)}
 } 
@@
 %\\
-COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 \\
-COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 \\
-COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 \\
-COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 \\
-COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 \\
-COSMOS-CID255 & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 \\
-COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 \\
-COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 \\
-COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 \\
-COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 \\
-COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 \\
-COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 \\
-COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 \\
-COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 \\
-COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 \\
-COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 \\
-COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 \\
-COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 \\
-COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 \\
-COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 \\
-COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12\\
-CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 \\ 
-CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 \\ 
-CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18\\ 
-CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 \\ 
-ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09\\ 
-SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29\\ 
-SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01\\ 
-SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 \\ 
-SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 \\ 
-SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 \\ 
-SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 \\ 
+COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
+COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
+COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
+COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
+COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
+COSMOS-CID255$^a$ & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
+COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
+COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
+COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
+COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
+COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
+COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
+COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
+COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
+COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
+COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
+COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
+COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
+COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
+COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
+COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
+CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
+CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
+CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
+CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
+ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
+SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
+SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
+SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
+SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
+SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
+SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
 \enddata
@@
 Column 6: The observing start date.
+\\
+$^a$For CID255, 3/6 of the dither WFC3 images are corrupted. We analyze this sample by a same approach, taking the 3 avalible frames.
 }
@@
 \tablewidth{0pt}
-\tablecaption{Details of CID1174's inference. } 
+\tablecaption{The host inference of CID1174} 
 \tablehead{ 
@@
 \tablewidth{0pt}
-\tablecaption{Inferred host galaxy parameters for the 32 systems.} 
+\tablecaption{Inferred host galaxy properties for the 32 systems.} 
 \tablehead
@@
   \multicolumn{5}{c}{WFC3}&
-  \multicolumn{3}{c}{ACS} &
+  \multicolumn{3}{c}{ACS/F814W} &
    \multicolumn{2}{c}{host properties} \\
@@
 CID237 & $2.349$ & $29.9\%\pm6.3\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.74\pm1.70$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3.2\%\pm2.0\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26$ &$10.98$\\
-CID255 & ... & ... & ... & ... & ... & ... & ... & ... & ... &...\\
+CID255 & $1.625$ & $18.9\%\pm5.4\%$ & $0\farcs{}19\pm0\farcs{}06'$ & $4.21\pm1.49$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4.2\%\pm1.8\%$ & $22.89\substack{+0.60\\-0.39} $& $11.17$ & $10.89$\\
 CID3242 & $2.751$ & $46.1\%\pm12.7\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.14\pm1.87$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $4.8\%\pm1.3\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25$ &$10.97$\\
@@
 Column~1: Object ID.
+Column~2-6: WFC3 inference. 
 Column~2: Reduced $\chi ^2$ value by the best PSF in the library.
-Column~3-6: WFC3 inference.
 Column~7-9: ACS inference. 
-Column~10: Inferred observed host Luminosity in the rest-frame R band.
-Column~10: Inferred host total stellar mass.
+Column~10: Observed host luminosity in the rest-frame R band.
+Column~11: Host total stellar mass.
 }
@@
 XID2396 & 2271.2617 & 44.06196 & 8.455 & -0.365 & 2657.8386 & 45.50467 & 8.511& -0.272 \\
-CDFS-1 & 5449.4022 & 43.08 & 8.789 & ... & ... & ... & ...& ... \\
-CDFS-229 & 2254.0105 & 43.3 & 8.082 & ... & ... & ... & ...& ... \\
+CDFS-1 & 5449.4022 & 43.08 & 8.789 & -0.978 & ... & ... & ...& ... \\
+CDFS-229 & 2254.0105 & 43.30 & 8.082 & -0.481 & ... & ... & ...& ... \\
 CDFS-321 & 2441.93 & 43.92714 & 8.457 & -0.496 & ... & ... & ...& ... \\
-CDFS-724 & 3351.8522 & 42.56 & 8.093 & ... & ... & ... & ...& ... \\
+CDFS-724 & 3351.8522 & 42.56 & 8.093 & -1.222 & ... & ... & ...& ... \\
 ECDFS-358 & 2237.2314 & 43.39674 & 8.122 & -0.669 & ... & ... & ...& ... \\
@@
 {
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID255_SB_profile.pdf}
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID3242_SB_profile.pdf}
@@
 \caption{\label{fig:flux_r_n_corner}
-Illustration of the relations between the inferred host properties.}
+Illustration of the relations between the inferred host \sersic\ parameters.}
 \end{figure*}
@@
 
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+{\includegraphics[width=0.5\textwidth]{fig/Mstar-Reff.pdf}}&
+{\includegraphics[width=0.5\textwidth]{fig/Mstar-Sn.pdf}}\\
+\end{tabular}
+\caption{\label{fig:Mstar-rn} 
+The inference MM-z relation}
+\end{figure*}
+
 %\appendix

### 2019-03-20 manuscript/manuscript.tex
Updating the comparing CANDLES figures.

@@
 
-The tight correlation between the mass of a supermassive black hole (\mbh) and its host galaxies properties indicates a connection of their evolution.
-The key to test this co-evolution scenario is to trace their correlation to more distant Universe.
-We measure using a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields obtained with the {\it Hubble Space Telescope} (\hst).
-%Wide-Field Camera 3.
-The high-resolution \hst\ images enable us to decompose the AGN image and infer the host properties including luminosity (\lhost) and stellar mass (\smass) in each case.
-The lower nuclear-to-host ratios and multi-band images of our samples provide accurate host properties.
-The estimation of \mbh\ is based on our published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids the systemic bias by the \Civ\ or \Mgii\ lines.
-We compare the \mbh-\lhost~and \mbh-\smass~relation to the local active galaxies while taking the selection effect into account thus establishing the cosmic evolution in these relations.
-Considering the passive luminosity effect, we inferred a positive evolution of \mbh-\lhost, indicating that the BHs at higher redshift resides in less luminous galaxies than today.
+The tight correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties suggests an evolutionary connection.
+A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time.
+For this purpose, we obtained multi-band {\it Hubble Space Telescope} of  a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs).
+By applying state-of-the art tools to the images we obtained accurate host galaxy luminosity and stellar mass.
+The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts.
+We compare the \mbh-\lhost~and \mbh-\smass~relations to those of local active galaxies, accounting for selection effects, to infer their evolution.
+The \mbh-\lhost relation is inconsistent with the local one, accounting for passive evolution, indicating that the BHs at higher redshift resides in less luminous galaxies than today.
 The \mbh-\smass\ of our high redshift sample is consistent with the local \mbh-\smass$_{\rm bluge}$ relations.
@@
 The sample by B10 consistent 19 \mbh-\lhost\ relations with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex).
-The work of B11 contain 25 \mbh-\smass\ local active AGN analysis, where the \mbh\ are measured from single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
-To increase the local \smass\ and \mbh\ to higher range, we also include the inactive galaxies (mainly ellipticals or S0) as done by \citet{H+R04}.
+The work of B11 contains 25 \mbh-\smass\ local active AGN analysis, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
+To increase the local \smass\ and \mbh\ to the higher range, we also include the inactive galaxies (mainly ellipticals or S0) as done by \citet{H+R04}.
 It is worth note that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample.
@@
 \subsection{Host galaxy properties}
-We derive the rest-frame R band magnitude and luminosity of our sample based on their filter magnitude obtained last section.
-18/32 systems have multi-band host magnitude which ables us to select the best stellar population that could fit to the overall sample.
-We find that the 1 Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these sample.
-Adopting this stellar population, we perform the K-correction and derive the rest-frame R band magnitude of our sample.
-We further derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.
-We estimate of the stellar mass content of each host galaxy by adopt the mass-to-light ratio (M/L) based on the stellar population we adopted.
+We derive the rest-frame R band magnitude ($M_R$) and luminosity ($L_R$) of our sample based on their filter magnitude.
+18/32 systems have multi-band host magnitude which ables us to select the best stellar population that could fit the overall sample.
+We find that the 1~Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples.
+Adopting the color information, we perform the K-correction and derive the rest-frame R band magnitude of our sample.
+Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty level raised by this K-correction is within 0.05~mag.
+We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.
+
+Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted.
+The raised uncertainty level to the stellar mass is expected to be within 0.1~dex.
 
@@
 
-The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare them to the \mbh.
+The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare their relations to to the \mbh.
 
@@
 \end {eqnarray}
-which enables a direct comparison to the distant sample.
-The figure shows that the observed \mbh-\lhost\ relation for our measurements  are nearly identical to the local and intermediate ones, indicating that the black hole mass and the host luminosity located at a similar relation at different galaxy age.
+which enables direct comparison to the distant sample.
+The figure shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones, indicating that the black hole mass and the host luminosity located at a similar relation at different galaxy age.
 However, considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
@@
 \end{eqnarray} 
-This formulism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$.
-We refer to the \citet[][section 5.4]{Ding2017b} for more details.
-Transfering the \lhost\ to today, we show the evolution-corrected \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (b) and find that, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts.
+This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$.
+We refer to \citet[][section 5.4]{Ding2017b} for more details.
+Transferring the \lhost\ to today, we show the evolution-corrected \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (b) and find that, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts.
 
@@
 
-Given that the current result does not take into account selection effects yet, we will draw the conclusion in the section~\ref{select_eff}
+Given that the current result does not take into account selection effects yet, we will draw the conclusion in section~\ref{select_eff}.
 
@@
 In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample.
-We visually see that the mass distributions for three samples are very similar.
+We visually see that the mass distributions for the three samples are very similar.
 Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$.
 We obtain the $\gamma  = 0.49 \pm 0.19$ which slightly indicates as the positive, see Figure~\ref{fig:MM-vz}, panel (a).
-In the of Figure~\ref{fig:MM-vz}, panel (b), we also show the ratio of \mbh-\smass of the three sample at different redshift.
+We also show the ratio of \mbh-\smass of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).
 We highlight that our results are less biased in both the measurement of \mbh\ and \smass.
 
-We highlight that the local sample employed are bulge dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
-That is, we are comparing the \mbh-\smass$_{,total}$ at distant universe to the \mbh-\smass$_{,bulge}$ at the local.
-Considering that a major part of the distant systems have indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.
+We highlight that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
+That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at the local.
+Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.
 
@@
 In our analysis, we adopt one stellar population to the overall sample.
-We note that adopting the private stellar populations for these sample which have both multi-band host magnitude could be more robust in principle.
-However, considering that the host magnitude in ACS band are faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost.
+We note that adopting the private stellar populations for these samples which have both multi-band host magnitude could be more robust in principle.
+However, considering that the host magnitude in ACS band is faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost.
 Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry.
 \textcolor{red}{Describe the ground-based data}.
-In this paper, we focus on the decomposing of the AGN and carry out a rapid analysis of the \mbh-host raltions.
+In this paper, we focus on the decomposing of the AGN and carry out a rapid analysis of the \mbh-host relations.
 The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.
 
-\subsection{Comparison with the inactive galaxies}
-To understand how the AGNs activity affect their galaxies's morphology, we compared the 32 host measurements to the inactive galaxies in CANDLES imaging survey.
+\subsection{Comparison to the inactive galaxies}
+To understand whether AGNs activity affects their galaxies' morphology, we compared the 32 host measurements to the inactive galaxies in CANDLES imaging survey.
 We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) from the CANDLES-COSMOS catalog.
-Their \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar mass are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.
+Their \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.
 
-We compare the \smass-\Reff\ relations in Figure~\ref{fig:Mstar-rn}. The inference shows that our AGN host are located at a higher end of the stellar mass.
+\textcolor{blue}{ Description and comments to be written}:
+We show the \smass-\Reff\ relations and \smass-\sersic\ n in Figure~\ref{fig:Mstar-rn}. 
+The comparison the histogram of \Reff\ and \sersic\ n are shown in Figure~\ref{fig:hist_rn}.
+
+%high
+%The distribution shows that our AGN host are located at a higher end of the stellar mass at region where
 
@@
 %\\
-1 & $8584.429$ & $1.000$ & $82.209$ & $35.4\%$ & $0\farcs{}345$ & $1.114$ \\
-2 & $8646.711$ & $0.920$ & $99.102$ & $41.9\%$ & $0\farcs{}298$ & $1.932$ \\
-3 & $8816.947$ & $0.734$ & $76.74$ & $33.0\%$ & $0\farcs{}365$ & $1.102$ \\
+1 & $8584.429$ & $1.000$ & $82.209$ & $35.4\%$ & $0\farcs{}345$ & $1.11$ \\
+2 & $8646.711$ & $0.920$ & $99.102$ & $41.9\%$ & $0\farcs{}298$ & $1.93$ \\
+3 & $8816.947$ & $0.734$ & $76.74$ & $33.0\%$ & $0\farcs{}365$ & $1.10$ \\
 4 & $9304.841$ & $0.383$ & $128.618$ & $54.7\%$ & $0\farcs{}231$ & $2.78$ \\
-5 & $9652.575$ & $0.241$ & $187.498$ & $79.0\%$ & $0\farcs{}116$ & $6.175$ \\
-6 & $9917.101$ & $0.170$ & $100.166$ & $42.3\%$ & $0\farcs{}287$ & $2.066$ \\
-7 & $10018.324$ & $0.148$ & $75.061$ & $32.3\%$ & $0\farcs{}365$ & $1.226$ \\
-8 & $10087.456$ & $0.135$ & $79.835$ & $34.3\%$ & $0\farcs{}358$ & $1.195$ \\
+5 & $9652.575$ & $0.241$ & $187.498$ & $79.0\%$ & $0\farcs{}116$ & $6.18$ \\
+6 & $9917.101$ & $0.170$ & $100.166$ & $42.3\%$ & $0\farcs{}287$ & $2.07$ \\
+7 & $10018.324$ & $0.148$ & $75.061$ & $32.3\%$ & $0\farcs{}365$ & $1.23$ \\
+8 & $10087.456$ & $0.135$ & $79.835$ & $34.3\%$ & $0\farcs{}358$ & $1.20$ \\
 \hline\\
-Weighted value & & & $97.322\pm28.336$ & $41.5\%\pm11.7\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.862\pm1.26$  \\
+Weighted value & & & $97.322\pm28.336$ & $41.5\%\pm11.7\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.86\pm1.26$  \\
 \enddata
@@
 \colhead{}& 
-\colhead{reduced $\chi ^2$}& \colhead{host-to-total flux ratio}& 
+\colhead{reduced $\chi ^2$}& \colhead{host-total flux ratio}& 
 \colhead{\Reff}& \colhead{\sersic\ $n$}& 
 \colhead{magnitude}&
-\colhead{reduced $\chi ^2$}& \colhead{host-to-total flux ratio}& \colhead{magnitude} &
+\colhead{reduced $\chi ^2$}& \colhead{host-total flux ratio}& \colhead{magnitude} &
 \colhead{$\log L_R$} &\colhead{$\log M_*$} \\
@@
 \startdata 
-CID1174 & $2.307$ & $41.5\%\pm11.7\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.86\pm1.26$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11.2\%\pm1.1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.13$ &$10.85$\\
-CID1281 & $1.322$ & $49.3\%\pm13.7\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.15\pm1.48$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $18.5\%\pm7.7\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.49$ &$10.21$\\
-CID206 & $2.054$ & $35.3\%\pm24.3\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.07\pm2.48$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $7.7\%\pm2.4\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.95$ &$10.66$\\
-CID216 & $1.514$ & $93.9\%\pm4.7\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.16\pm1.21$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35.1\%\pm1.5\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.13$ &$10.85$\\
-CID237 & $2.349$ & $29.9\%\pm6.3\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.74\pm1.70$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3.2\%\pm2.0\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26$ &$10.98$\\
-CID255 & $1.625$ & $18.9\%\pm5.4\%$ & $0\farcs{}19\pm0\farcs{}06'$ & $4.21\pm1.49$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4.2\%\pm1.8\%$ & $22.89\substack{+0.60\\-0.39} $& $11.17$ & $10.89$\\
-CID3242 & $2.751$ & $46.1\%\pm12.7\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.14\pm1.87$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $4.8\%\pm1.3\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25$ &$10.97$\\
-CID3570 & $1.665$ & $76.5\%\pm1.6\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.73\pm0.05$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $85.6\%\pm1.5\%$ & $22.97\substack{+0.01\\-0.01}$ & $11.07$ &$10.79$\\
-CID452 & $1.684$ & $75.4\%\pm3.9\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.40\pm0.18$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $37.8\%\pm0.7\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.21$ &$10.93$\\
-CID454 & $2.203$ & $35.8\%\pm2.5\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.62\pm0.11$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9.2\%\pm0.5\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.19$ &$10.91$\\
-CID50 & $5.576$ & $16.5\%\pm9.0\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.22\pm2.22$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5.0\%\pm3.3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.15$ &$10.87$\\
-CID543 & $1.902$ & $30.6\%\pm9.7\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.49\pm0.33$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5.2\%\pm2.0\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.79$ &$10.51$\\
-CID597 & $1.565$ & $42.4\%\pm16.6\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.75\pm0.78$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $11.5\%\pm1.3\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.81$ &$10.53$\\
-CID607 & $1.692$ & $43.6\%\pm17.9\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.42\pm1.10$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $4.7\%\pm1.8\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.10$ &$10.82$\\
-CID70 & $2.041$ & $19.7\%\pm4.9\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.62\pm1.03$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2.3\%\pm1.1\%$ & $24.63\substack{+0.68\\-0.41}$ & $11.07$ &$10.79$\\
-LID1273 & $1.697$ & $53.3\%\pm9.1\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.22\pm0.49$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6.4\%\pm0.8\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.40$ &$11.12$\\
-LID1538 & $2.362$ & $43.5\%\pm7.8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.82\pm0.48$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $7.5\%\pm1.2\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.21$ &$10.93$\\
-LID360 & $3.918$ & $18.4\%\pm2.0\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.75\pm0.36$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $3.7\%\pm0.5\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.17$ &$10.88$\\
-XID2138 & $1.597$ & $38.9\%\pm5.5\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.24\pm0.39$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5.0\%\pm1.3\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.98$ &$10.70$\\
-XID2202 & $3.23$ & $33.3\%\pm8.0\%$ & $0\farcs{}10\pm0\farcs{}00$ & $3.96\pm1.02$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8.3\%\pm1.9\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.24$ &$10.96$\\
-XID2396 & $3.669$ & $23.9\%\pm10.5\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.77\pm1.36$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2.3\%\pm0.5\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.20$ &$10.92$\\
-CDFS-1 & $1.358$ & $64.5\%\pm19.7\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.81\pm1.11$ & $22.47\substack{+0.40\\-0.29}$ & ... & ... & ... & $10.80$ &$10.52$\\
-CDFS-229 & $4.329$ & $17.6\%\pm2.1\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.46\pm0.20$ & $21.57\substack{+0.14\\-0.13}$ & ... & ... & ... & $10.98$ &$10.70$\\
-CDFS-321 & $3.998$ & $24.5\%\pm11.7\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.26\pm2.01$ & $20.34\substack{+0.70\\-0.42}$ & ... & ... & ... & $11.61$ &$11.33$\\
-CDFS-724 & $1.355$ & $34.7\%\pm14.6\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.62\pm1.10$ & $23.70\substack{+0.58\\-0.38}$ & ... & ... & ... & $10.14$ &$9.86$\\
-ECDFS-358 & $2.012$ & $56.4\%\pm13.5\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.67\pm0.54$ & $21.34\substack{+0.30\\-0.24}$ & ... & ... & ... & $11.25$ &$10.97$\\
-SXDS-X1136 & $1.937$ & $40.5\%\pm7.8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $1.99\pm0.48$ & $21.92\substack{+0.23\\-0.19}$ & ... & ... & ... & $10.84$ &$10.56$\\
-SXDS-X50 & $1.423$ & $40.7\%\pm8.6\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.65\pm0.62$ & $21.99\substack{+0.27\\-0.21}$ & ... & ... & ... & $10.89$ &$10.61$\\
-SXDS-X717 & $1.426$ & $61.4\%\pm9.1\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.58\pm1.42$ & $21.76\substack{+0.18\\-0.15}$ & ... & ... & ... & $10.86$ &$10.58$\\
-SXDS-X735 & $2.203$ & $32.4\%\pm8.5\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.03\pm1.01$ & $20.92\substack{+0.33\\-0.25}$ & ... & ... & ... & $11.28$ &$11.00$\\
-SXDS-X763 & $2.376$ & $6.0\%\pm4.0\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.39\pm0.80$ & $24.13\substack{+1.17\\-0.55}$ & ... & ... & ... & $10.03$ &$9.75$\\
-SXDS-X969 & $1.613$ & $29.1\%\pm11.1\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.05\pm1.07$ & $21.59\substack{+0.52\\-0.35}$ & ... & ... & ... & $11.12$ &$10.83$\\
+CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.13\substack{+0.09\\-0.07}$ &$10.85\substack{+0.14\\-0.12}$\\
+CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.49\substack{+0.09\\-0.07}$ &$10.21\substack{+0.13\\-0.12}$\\
+CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.95\substack{+0.32\\-0.14}$ &$10.66\substack{+0.34\\-0.18}$\\
+CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.13\substack{+0.02\\-0.02}$ &$10.85\substack{+0.1\\-0.1}$\\
+CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26\substack{+0.07\\-0.05}$ &$10.98\substack{+0.12\\-0.11}$\\
+CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.17\substack{+0.09\\-0.07}$ &$10.89\substack{+0.14\\-0.12}$\\
+CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25\substack{+0.09\\-0.07}$ &$10.97\substack{+0.13\\-0.12}$\\
+CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $11.07\substack{+0.01\\-0.01}$ &$10.79\substack{+0.1\\-0.1}$\\
+CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.21\substack{+0.02\\-0.02}$ &$10.93\substack{+0.1\\-0.1}$\\
+CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.19\substack{+0.02\\-0.02}$ &$10.91\substack{+0.1\\-0.1}$\\
+CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.15\substack{+0.22\\-0.12}$ &$10.87\substack{+0.24\\-0.16}$\\
+CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.79\substack{+0.1\\-0.07}$ &$10.51\substack{+0.14\\-0.12}$\\
+CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.81\substack{+0.14\\-0.09}$ &$10.53\substack{+0.17\\-0.13}$\\
+CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.10\substack{+0.14\\-0.09}$ &$10.82\substack{+0.18\\-0.14}$\\
+CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $11.07\substack{+0.08\\-0.06}$ &$10.79\substack{+0.13\\-0.12}$\\
+LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.40\substack{+0.05\\-0.05}$ &$11.12\substack{+0.11\\-0.11}$\\
+LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.21\substack{+0.06\\-0.05}$ &$10.93\substack{+0.11\\-0.11}$\\
+LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.17\substack{+0.04\\-0.03}$ &$10.88\substack{+0.11\\-0.1}$\\
+XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.98\substack{+0.04\\-0.04}$ &$10.70\substack{+0.11\\-0.11}$\\
+XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.24\substack{+0.08\\-0.06}$ &$10.96\substack{+0.13\\-0.12}$\\
+XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.20\substack{+0.16\\-0.1}$ &$10.92\substack{+0.19\\-0.14}$\\
+CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ... & ... & ... & $10.80\substack{+0.1\\-0.07}$ &$10.52\substack{+0.14\\-0.12}$\\
+CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ... & ... & ... & $10.98\substack{+0.04\\-0.03}$ &$10.70\substack{+0.11\\-0.1}$\\
+CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ... & ... & ... & $11.61\substack{+0.18\\-0.11}$ &$11.33\substack{+0.2\\-0.15}$\\
+CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ... & ... & ... & $10.14\substack{+0.15\\-0.1}$ &$9.86\substack{+0.18\\-0.14}$\\
+ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ... & ... & ... & $11.25\substack{+0.08\\-0.06}$ &$10.97\substack{+0.13\\-0.12}$\\
+SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ... & ... & ... & $10.84\substack{+0.06\\-0.05}$ &$10.56\substack{+0.12\\-0.11}$\\
+SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ... & ... & ... & $10.89\substack{+0.07\\-0.05}$ &$10.61\substack{+0.12\\-0.11}$\\
+SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ... & ... & ... & $10.86\substack{+0.05\\-0.04}$ &$10.58\substack{+0.11\\-0.11}$\\
+SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ... & ... & ... & $11.28\substack{+0.08\\-0.06}$ &$11.00\substack{+0.13\\-0.12}$\\
+SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ... & ... & ... & $10.03\substack{+0.29\\-0.14}$ &$9.75\substack{+0.31\\-0.17}$\\
+SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ... & ... & ... & $11.12\substack{+0.13\\-0.09}$ &$10.83\substack{+0.16\\-0.13}$\\
 \enddata
@@
 \startdata 
-CID1174 & 1906.3037 & 43.43237 & 7.992 & -0.504 & 5898.264 & 44.76243 & 8.833& -1.353 \\
-CID1281 & 1619.4891 & 43.23945 & 7.749 & -0.446 & ... & ... & ...& ... \\
-CID206 & 3333.5527 & 43.4776 & 8.528 & -0.997 & ... & ... & ...& ... \\
-CID216 & 2229.5232 & 42.84509 & 7.854 & -0.929 & ... & ... & ...& ... \\
-CID237 & 2112.3306 & 43.85546 & 8.289 & -0.397 & ... & ... & ...& ... \\
-CID255 & 1932.0933 & 43.9924 & 8.273 & -0.249 & 3709.241 & 45.37122 & 8.734& -0.628 \\
-CID3242 & 2543.2202 & 43.83323 & 8.449 & -0.578 & 3774.503 & 45.09891 & 8.613& -0.779 \\
-CID3570 & 1958.8551 & 43.16374 & 7.888 & -0.658 & ... & ... & ...& ... \\
-CID452 & 3457.8801 & 42.92298 & 8.295 & -1.296 & 3127.3306 & 44.63353 & 8.217& -0.879 \\
-CID454 & 2824.2693 & 43.34466 & 8.311 & -0.908 & ... & ... & ...& ... \\
-CID50 & 2339.9104 & 43.93786 & 8.423 & -0.451 & 1938.5676 & 45.32766 & 8.149& -0.086 \\
-CID543 & 2188.8447 & 43.57404 & 8.187 & -0.564 & ... & ... & ...& ... \\
-CID597 & 1656.3296 & 43.32955 & 7.813 & -0.424 & ... & ... & ...& ... \\
-CID607 & 3009.1816 & 43.67079 & 8.526 & -0.811 & 4241.526 & 44.78209 & 8.556& -1.055 \\
-CID70 & 2480.4058 & 43.50531 & 8.269 & -0.712 & 3981.8574 & 45.1582 & 8.689& -0.796 \\
-LID1273 & 3223.8484 & 43.61001 & 8.561 & -0.903 & ... & ... & ...& ... \\
-LID1538 & 2941.422 & 43.59594 & 8.469 & -0.825 & ... & ... & ...& ... \\
-LID360 & 2481.7253 & 43.88091 & 8.45 & -0.533 & 2868.8992 & 45.08676 & 8.369& -0.547 \\
-XID2138 & 3185.8613 & 43.6148 & 8.552 & -0.890 & 2944.7766 & 44.80782 & 8.252& -0.723 \\
-XID2202 & 2973.2378 & 43.56249 & 8.463 & -0.851 & ... & ... & ...& ... \\
-XID2396 & 2271.2617 & 44.06196 & 8.455 & -0.365 & 2657.8386 & 45.50467 & 8.511& -0.272 \\
-CDFS-1 & 5449.4022 & 43.08 & 8.789 & -0.978 & ... & ... & ...& ... \\
-CDFS-229 & 2254.0105 & 43.30 & 8.082 & -0.481 & ... & ... & ...& ... \\
-CDFS-321 & 2441.93 & 43.92714 & 8.457 & -0.496 & ... & ... & ...& ... \\
-CDFS-724 & 3351.8522 & 42.56 & 8.093 & -1.222 & ... & ... & ...& ... \\
-ECDFS-358 & 2237.2314 & 43.39674 & 8.122 & -0.669 & ... & ... & ...& ... \\
-SXDS-X1136 & 2759.8953 & 43.43305 & 8.333 & -0.845 & 6761.222 & 44.71429 & 8.927& -1.500 \\
-SXDS-X50 & 1816.672 & 43.421 & 7.942 & -0.465 & ... & ... & ...& ... \\
-SXDS-X717 & 2930.7417 & 43.04988 & 8.204 & -1.083 & ... & ... & ...& ... \\
-SXDS-X735 & 2702.0962 & 43.69804 & 8.44 & -0.698 & 3519.6052 & 45.07463 & 8.54& -0.731 \\
-SXDS-X763 & 2961.1743 & 43.57321 & 8.465 & -0.842 & 4508.5146 & 44.51285 & 8.474& -1.271 \\
-SXDS-X969 & 2296.0566 & 43.50066 & 8.196 & -0.643 & 1695.7146 & 45.05337 & 7.895& -0.107 \\
+CID1174 & 1906 & 43.43 & 7.99 & -0.50 & 5898 & 44.76 & 8.83& -1.35 \\
+CID1281 & 1619 & 43.24 & 7.75 & -0.45 & ... & ... & ...& ... \\
+CID206 & 3334 & 43.48 & 8.53 & -1.00 & ... & ... & ...& ... \\
+CID216 & 2230 & 42.85 & 7.85 & -0.93 & ... & ... & ...& ... \\
+CID237 & 2112 & 43.86 & 8.29 & -0.40 & ... & ... & ...& ... \\
+CID255 & 1932 & 43.99 & 8.27 & -0.25 & 3709 & 45.37 & 8.73& -0.63 \\
+CID3242 & 2543 & 43.83 & 8.45 & -0.58 & 3775 & 45.10 & 8.61& -0.78 \\
+CID3570 & 1959 & 43.16 & 7.89 & -0.66 & ... & ... & ...& ... \\
+CID452 & 3458 & 42.92 & 8.30 & -1.30 & 3127 & 44.63 & 8.22& -0.88 \\
+CID454 & 2824 & 43.34 & 8.31 & -0.91 & ... & ... & ...& ... \\
+CID50 & 2340 & 43.94 & 8.42 & -0.45 & 1939 & 45.33 & 8.15& -0.09 \\
+CID543 & 2189 & 43.57 & 8.19 & -0.56 & ... & ... & ...& ... \\
+CID597 & 1656 & 43.33 & 7.81 & -0.42 & ... & ... & ...& ... \\
+CID607 & 3009 & 43.67 & 8.53 & -0.81 & 4242 & 44.78 & 8.56& -1.06 \\
+CID70 & 2480 & 43.51 & 8.27 & -0.71 & 3982 & 45.16 & 8.69& -0.80 \\
+LID1273 & 3224 & 43.61 & 8.56 & -0.90 & ... & ... & ...& ... \\
+LID1538 & 2941 & 43.60 & 8.47 & -0.83 & ... & ... & ...& ... \\
+LID360 & 2482 & 43.88 & 8.45 & -0.53 & 2869 & 45.09 & 8.37& -0.55 \\
+XID2138 & 3186 & 43.61 & 8.55 & -0.89 & 2945 & 44.81 & 8.25& -0.72 \\
+XID2202 & 2973 & 43.56 & 8.46 & -0.85 & ... & ... & ...& ... \\
+XID2396 & 2271 & 44.06 & 8.46 & -0.37 & 2658 & 45.50 & 8.51& -0.27 \\
+CDFS-1 & 5449 & 43.08 & 8.79 & -0.98 & ... & ... & ...& ... \\
+CDFS-229 & 2254 & 43.30 & 8.08 & -0.48 & ... & ... & ...& ... \\
+CDFS-321 & 2442 & 43.93 & 8.46 & -0.50 & ... & ... & ...& ... \\
+CDFS-724 & 3352 & 42.56 & 8.09 & -1.22 & ... & ... & ...& ... \\
+ECDFS-358 & 2237 & 43.40 & 8.12 & -0.67 & ... & ... & ...& ... \\
+SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.85 & 6761 & 44.71 & 8.93& -1.50 \\
+SXDS-X50 & 1817 & 43.42 & 7.94 & -0.47 & ... & ... & ...& ... \\
+SXDS-X717 & 2931 & 43.05 & 8.20 & -1.08 & ... & ... & ...& ... \\
+SXDS-X735 & 2702 & 43.70 & 8.44 & -0.70 & 3520 & 45.07 & 8.54& -0.73 \\
+SXDS-X763 & 2961 & 43.57 & 8.47 & -0.84 & 4509 & 44.51 & 8.47& -1.27 \\
+SXDS-X969 & 2296 & 43.50 & 8.20 & -0.64 & 1696 & 45.05 & 7.90& -0.11 \\
 \enddata
@@
 \begin{tabular}{c c}
-{\includegraphics[width=0.5\textwidth]{fig/Mstar-Reff.pdf}}&
-{\includegraphics[width=0.5\textwidth]{fig/Mstar-Sn.pdf}}\\
+ \hspace{-2.5em}
+{\includegraphics[trim = 0mm 0mm 90mm 0mm, clip, height=0.45\textwidth]{fig/Mstar-Reff.pdf}}&
+{\includegraphics[ height=0.45\textwidth]{fig/Mstar-Sn.pdf}}\\
 \end{tabular}
 \caption{\label{fig:Mstar-rn} 
-The inference MM-z relation}
+The comparison of the stellar mass - host \sersic\ parameters between our 32 AGNs to the 4400 CANDLES sample.
+}
+\end{figure*}
+
+\begin{figure*}
+\centering
+{\includegraphics[ height=0.35\textwidth]{fig/Hist_Reff.pdf}}\\
+{\includegraphics[ height=0.35\textwidth]{fig/Hist_Sn.pdf}}
+\caption{\label{fig:hist_rn} 
+The comparison of the histogram of the \sersic\ parameters distribution}
 \end{figure*}

### 2019-03-20 material/CANDELS_catalog/compare_with_CANDLESCOSMOS_color.py

@@ -67,9 +67,9 @@ for i in range(len(lists)):
     result3 = stellar[lists[i][1]][1]     #Stellar_mass
     result4 = galfit[lists[i][0]][3]      #flag
     result5 = stellar[lists[i][1]][2]     #Star formation rate
-    result6 = stellar_flux_ap[lists[i][1]][0]
-    result7 = stellar_flux_ap[lists[i][1]][1]
-    result8 = stellar_flux_ap[lists[i][1]][2]
+    result6 = stellar_flux_ap[lists[i][1]][0] #F140w
+    result7 = stellar_flux_ap[lists[i][1]][1] #F125w.
+    result8 = stellar_flux_ap[lists[i][1]][2] #F814w
     results.append([result0, result1, result2, result3, result4, result5, result6, result7, result8])  #Redshift, Reff(arcsec), Sersic_n, Stellar_mass, flag, SFR
 results = np.asarray(results)
 
@@ -91,8 +91,8 @@ da_result = 1/(1+results[:,0])*c*vec_EE(results[:,0])/h0  #in Mpc
 
 #%% Plot and input my sample
 
-relation = 1  # 0 M*- Reff ; 1 M*-Sersic_n
-z_range = [1,2]
+relation = 2  # 0 M*- Reff ; 1 M*-color; 2 M*-n
+z_range = [1.2,1.7]
 
 z_cut = ((results[:,0]>z_range[0]) * (results[:,0]<z_range[1]))
 
@@ -109,11 +109,14 @@ plt.figure(figsize=(15, 11))
 if relation == 0:
     Reff_kpc = da_result * 10 **3 * (results[:,1]/3600./180.*np.pi)
     plt.scatter(results[:,3][z_cut* red_galaxy],np.log10(Reff_kpc[z_cut * red_galaxy]),
-                c=(results[:,7][z_cut* red_galaxy]/results[:,8][z_cut * red_galaxy]),s=280,marker=".",zorder=100, vmin=0, vmax=7, alpha=0.6, edgecolors='white', cmap=cmap_r)
+                c=(results[:,7][z_cut* red_galaxy]/results[:,8][z_cut * red_galaxy]),s=280,marker=".",zorder=90, vmin=0, vmax=7, alpha=0.6, edgecolors='white', cmap=cmap_r)
 
 elif relation == 1:
[…]

### 2019-03-21 manuscript/manuscript.tex
Before "git pull" from overleaf

@@
 \subsection{Systematic error}
+
 In our analysis, we adopt one stellar population to the overall sample.
@@
 \subsection{Comparison to the inactive galaxies}
-To understand whether AGNs activity affects their galaxies' morphology, we compared the 32 host measurements to the inactive galaxies in CANDLES imaging survey.
-We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) from the CANDLES-COSMOS catalog.
-Their \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.
+We compared the morphology of AGNs host galaxies to the inactive galaxies in CANDLES imaging survey.
+We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.
 
-\textcolor{blue}{ Description and comments to be written}:
-We show the \smass-\Reff\ relations and \smass-\sersic\ n in Figure~\ref{fig:Mstar-rn}. 
-The comparison the histogram of \Reff\ and \sersic\ n are shown in Figure~\ref{fig:hist_rn}.
+In Figure~\ref{fig:Mstar-rn}, we plot the \smass\ versus the \Reff\ and \sersic\ index.
+The color coding is based on the filter flux ratio between WFC3 and ACS.
+The distribution of \smass-\Reff\ relation show that our AGN hosts concentrate at the high end of the stellar mass, close to the red sequence.
+
+We also compare the histogram of the inferred \Reff\ and \sersic\ n to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value.
+We perform the Kolmogorov?Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.
 
@@
 \section*{Acknowledgments}
-We thank the people who discuss with the paper.
+Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
+These observations are associated with programs
+\#15115.
+
+The authors fully appreciate the discussions with Vardha N. Bennert, Takahiro Morishita.
+
+SB, TT and AJS acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
+
+This work has made use of lenstronomy \citep{lenstronomy}, Astropy \citep{Astropy}, photutils, TOPCAT \citep{TOPCAT}, Matplotlib \citep{Matplotlib} and standard Python libraries.
 
@@
 %\\
-1 & $8584.429$ & $1.000$ & $82.209$ & $35.4\%$ & $0\farcs{}345$ & $1.11$ \\
-2 & $8646.711$ & $0.920$ & $99.102$ & $41.9\%$ & $0\farcs{}298$ & $1.93$ \\
-3 & $8816.947$ & $0.734$ & $76.74$ & $33.0\%$ & $0\farcs{}365$ & $1.10$ \\
-4 & $9304.841$ & $0.383$ & $128.618$ & $54.7\%$ & $0\farcs{}231$ & $2.78$ \\
-5 & $9652.575$ & $0.241$ & $187.498$ & $79.0\%$ & $0\farcs{}116$ & $6.18$ \\
-6 & $9917.101$ & $0.170$ & $100.166$ & $42.3\%$ & $0\farcs{}287$ & $2.07$ \\
-7 & $10018.324$ & $0.148$ & $75.061$ & $32.3\%$ & $0\farcs{}365$ & $1.23$ \\
-8 & $10087.456$ & $0.135$ & $79.835$ & $34.3\%$ & $0\farcs{}358$ & $1.20$ \\
+1 & $8584.429$ & $1.000$ & $82.2$ & $35\%$ & $0\farcs{}345$ & $1.1$ \\
+2 & $8646.711$ & $0.920$ & $99.1$ & $42\%$ & $0\farcs{}298$ & $1.9$ \\
+3 & $8816.947$ & $0.734$ & $76.7$ & $33\%$ & $0\farcs{}365$ & $1.1$ \\
+4 & $9304.841$ & $0.383$ & $128.6$ & $55\%$ & $0\farcs{}231$ & $2.8$ \\
+5 & $9652.575$ & $0.241$ & $187.5$ & $79\%$ & $0\farcs{}116$ & $6.2$ \\
+6 & $9917.101$ & $0.170$ & $100.2$ & $42\%$ & $0\farcs{}287$ & $2.1$ \\
+7 & $10018.324$ & $0.148$ & $75.1$ & $32\%$ & $0\farcs{}365$ & $1.2$ \\
+8 & $10087.456$ & $0.135$ & $79.8$ & $34\%$ & $0\farcs{}358$ & $1.2$ \\
 \hline\\
-Weighted value & & & $97.322\pm28.336$ & $41.5\%\pm11.7\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.86\pm1.26$  \\
+Weighted value & & & $97.322\pm28.336$ & $42\%\pm12\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.9\pm1.3$  \\
 \enddata
@@
 }
+\setlength{\tabcolsep}{20pt}
+\renewcommand{\arraystretch}{1.5}
 \startdata 
-CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.13\substack{+0.09\\-0.07}$ &$10.85\substack{+0.14\\-0.12}$\\
-CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.49\substack{+0.09\\-0.07}$ &$10.21\substack{+0.13\\-0.12}$\\
-CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.95\substack{+0.32\\-0.14}$ &$10.66\substack{+0.34\\-0.18}$\\
-CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.13\substack{+0.02\\-0.02}$ &$10.85\substack{+0.1\\-0.1}$\\
-CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26\substack{+0.07\\-0.05}$ &$10.98\substack{+0.12\\-0.11}$\\
-CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.17\substack{+0.09\\-0.07}$ &$10.89\substack{+0.14\\-0.12}$\\
-CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25\substack{+0.09\\-0.07}$ &$10.97\substack{+0.13\\-0.12}$\\
-CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $11.07\substack{+0.01\\-0.01}$ &$10.79\substack{+0.1\\-0.1}$\\
-CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.21\substack{+0.02\\-0.02}$ &$10.93\substack{+0.1\\-0.1}$\\
-CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.19\substack{+0.02\\-0.02}$ &$10.91\substack{+0.1\\-0.1}$\\
-CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.15\substack{+0.22\\-0.12}$ &$10.87\substack{+0.24\\-0.16}$\\
-CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.79\substack{+0.1\\-0.07}$ &$10.51\substack{+0.14\\-0.12}$\\
-CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.81\substack{+0.14\\-0.09}$ &$10.53\substack{+0.17\\-0.13}$\\
-CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.10\substack{+0.14\\-0.09}$ &$10.82\substack{+0.18\\-0.14}$\\
-CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $11.07\substack{+0.08\\-0.06}$ &$10.79\substack{+0.13\\-0.12}$\\
-LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.40\substack{+0.05\\-0.05}$ &$11.12\substack{+0.11\\-0.11}$\\
-LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.21\substack{+0.06\\-0.05}$ &$10.93\substack{+0.11\\-0.11}$\\
-LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.17\substack{+0.04\\-0.03}$ &$10.88\substack{+0.11\\-0.1}$\\
-XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.98\substack{+0.04\\-0.04}$ &$10.70\substack{+0.11\\-0.11}$\\
-XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.24\substack{+0.08\\-0.06}$ &$10.96\substack{+0.13\\-0.12}$\\
-XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.20\substack{+0.16\\-0.1}$ &$10.92\substack{+0.19\\-0.14}$\\
-CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ... & ... & ... & $10.80\substack{+0.1\\-0.07}$ &$10.52\substack{+0.14\\-0.12}$\\
-CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ... & ... & ... & $10.98\substack{+0.04\\-0.03}$ &$10.70\substack{+0.11\\-0.1}$\\
-CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ... & ... & ... & $11.61\substack{+0.18\\-0.11}$ &$11.33\substack{+0.2\\-0.15}$\\
-CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ... & ... & ... & $10.14\substack{+0.15\\-0.1}$ &$9.86\substack{+0.18\\-0.14}$\\
-ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ... & ... & ... & $11.25\substack{+0.08\\-0.06}$ &$10.97\substack{+0.13\\-0.12}$\\
-SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ... & ... & ... & $10.84\substack{+0.06\\-0.05}$ &$10.56\substack{+0.12\\-0.11}$\\
-SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ... & ... & ... & $10.89\substack{+0.07\\-0.05}$ &$10.61\substack{+0.12\\-0.11}$\\
-SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ... & ... & ... & $10.86\substack{+0.05\\-0.04}$ &$10.58\substack{+0.11\\-0.11}$\\
-SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ... & ... & ... & $11.28\substack{+0.08\\-0.06}$ &$11.00\substack{+0.13\\-0.12}$\\
-SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ... & ... & ... & $10.03\substack{+0.29\\-0.14}$ &$9.75\substack{+0.31\\-0.17}$\\
-SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ... & ... & ... & $11.12\substack{+0.13\\-0.09}$ &$10.83\substack{+0.16\\-0.13}$\\
+CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.13\substack{+0.15\\-0.11}$ &$10.85\substack{+0.18\\-0.15}$\\[3pt]
+CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.49\substack{+0.15\\-0.11}$ &$10.21\substack{+0.18\\-0.15}$\\[3pt]
+CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.95\substack{+0.52\\-0.23}$ &$10.66\substack{+0.53\\-0.25}$\\[3pt]
+CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.13\substack{+0.03\\-0.03}$ &$10.85\substack{+0.10\\-0.10}$\\[3pt]
+CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26\substack{+0.11\\-0.09}$ &$10.98\substack{+0.14\\-0.13}$\\[3pt]
+CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.17\substack{+0.15\\-0.11}$ &$10.89\substack{+0.18\\-0.15}$\\[3pt]
+CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25\substack{+0.14\\-0.11}$ &$10.97\substack{+0.17\\-0.15}$\\[3pt]
+CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $11.07\substack{+0.02\\-0.02}$ &$10.79\substack{+0.10\\-0.10}$\\[3pt]
+CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.21\substack{+0.03\\-0.03}$ &$10.93\substack{+0.10\\-0.10}$\\[3pt]
+CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.19\substack{+0.04\\-0.04}$ &$10.91\substack{+0.10\\-0.10}$\\[3pt]
+CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.15\substack{+0.35\\-0.19}$ &$10.87\substack{+0.36\\-0.21}$\\[3pt]
+CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.79\substack{+0.16\\-0.12}$ &$10.51\substack{+0.19\\-0.15}$\\[3pt]
+CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.81\substack{+0.22\\-0.15}$ &$10.53\substack{+0.24\\-0.18}$\\[3pt]
+CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.10\substack{+0.23\\-0.15}$ &$10.82\substack{+0.25\\-0.18}$\\[3pt]
+CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $11.07\substack{+0.12\\-0.10}$ &$10.79\substack{+0.16\\-0.14}$\\[3pt]
+LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.40\substack{+0.09\\-0.07}$ &$11.12\substack{+0.13\\-0.12}$\\[3pt]
+LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.21\substack{+0.09\\-0.08}$ &$10.93\substack{+0.13\\-0.12}$\\[3pt]
+LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.17\substack{+0.06\\-0.05}$ &$10.88\substack{+0.11\\-0.11}$\\[3pt]
+XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.98\substack{+0.07\\-0.06}$ &$10.70\substack{+0.12\\-0.12}$\\[3pt]
+XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.24\substack{+0.12\\-0.10}$ &$10.96\substack{+0.16\\-0.14}$\\[3pt]
+XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.20\substack{+0.26\\-0.16}$ &$10.92\substack{+0.28\\-0.19}$\\[3pt]
+CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ... & ... & ... & $10.80\substack{+0.16\\-0.12}$ &$10.52\substack{+0.19\\-0.15}$\\[3pt]
+CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ... & ... & ... & $10.98\substack{+0.06\\-0.05}$ &$10.70\substack{+0.12\\-0.11}$\\[3pt]
+CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ...
+& ...
+& ...
+& $11.61\substack{+0.28\\-0.17}$ &$11.33\substack{+0.30\\-0.20}$\\[3pt]
+CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ... & ... & ... & $10.14\substack{+0.23\\-0.15}$ &$9.86\substack{+0.25\\-0.18}$\\[3pt]
+ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ...
+& ...
+& ...
+& $11.25\substack{+0.12\\-0.10}$ &$10.97\substack{+0.16\\-0.14}$\\[3pt]
+SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ...
+& ...
+& ...
+& $10.84\substack{+0.09\\-0.08}$ &$10.56\substack{+0.14\\-0.13}$\\[3pt]
+SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ... & ... & ... & $10.89\substack{+0.11\\-0.09}$ &$10.61\substack{+0.15\\-0.13}$\\[3pt]
+SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ...
+& ...
+& ...
+& $10.86\substack{+0.07\\-0.06}$ &$10.58\substack{+0.12\\-0.12}$\\[3pt]
+SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ...
+& ...
+& ...
+& $11.28\substack{+0.13\\-0.10}$ &$11.00\substack{+0.17\\-0.14}$\\[3pt]
+SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ... & ... & ... & $10.03\substack{+0.47\\-0.22}$ &$9.75\substack{+0.48\\-0.24}$\\[3pt]
+SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ...
+& ...
+& ...
+& $11.12\substack{+0.21\\-0.14}$ &$10.83\substack{+0.23\\-0.17}$\\[3pt]
 \enddata
@@
 \caption{\label{fig:hist_compare} 
-Comparison of the histogram of the inferred host flux ratio, based on the different amount of the top-ranked PSFs.}
+Comparison of the histogram of the inferred host flux ratio, based on the different volum of the top-ranked PSFs.}
 \end{figure*}
@@
 \caption{\label{fig:ML} 
-Observed \mbh-\lhost\ relation (left), evolution-corrected relation (right).}
+Illustration of observed (left) and evolution-corrected (right) correlations between \mbh-\lhost, with local linear relation indicated.
+The redshift are color-coded, for distant and intermediate AGNs.
+}
 \end{figure*}
@@
 \caption{\label{fig:ML-vz} 
-The offset as a function of redshift.}
+Illustration of the offset in log\mbh\ (VS. $L_R$) as a function of redshift. The orange band is the intrinsic scatter of local linear relation.}
 \end{figure}
@@
 \caption{\label{fig:MM} 
-Comparison of the histogram of the inferred host flux ratio, based on the different amount of the top-ranked PSFs.}
+Similar to the Figure~\ref{fig:ML}, but the comparison of the \mbh-\smass\ relations.}
 \end{figure}
@@
 \caption{\label{fig:MM-vz} 
-The inference MM-z relation}
+Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. Right: redshift evolution of the \mbh/\smass.  }
 \end{figure*}
@@
 \caption{\label{fig:Mstar-rn} 
-The comparison of the stellar mass - host \sersic\ parameters between our 32 AGNs to the 4400 CANDLES sample.
+The comparison of the galaxy properties between our 32 AGNs' hosts to the 4401 CANDLES inactive sample (circles).
+The color coding is based on the filter flux ratio between WFC3 and ACS.
+For CANDLES sample, the WFC3/F125W flux is taken.
+The black squares are the AGN samples with only WFC3 band observation.
 }
@@
 \caption{\label{fig:hist_rn} 
-The comparison of the histogram of the \sersic\ parameters distribution}
+The comparison of the histogram of the \Reff\ and \sersic\ n, with median value indicated.}
 \end{figure*}

### 2019-03-24 manuscript/manuscript.tex
update the paper with corrected AB LR and "Vege-derived" Mstar.

@@
 We compare the \mbh-\lhost~and \mbh-\smass~relations to those of local active galaxies, accounting for selection effects, to infer their evolution.
-The \mbh-\lhost relation is inconsistent with the local one, accounting for passive evolution, indicating that the BHs at higher redshift resides in less luminous galaxies than today.
-The \mbh-\smass\ of our high redshift sample is consistent with the local \mbh-\smass$_{\rm bluge}$ relations.
-Considering that our sample are composed of bulge and disk components, we are forced to concluded that our results consistent to a scenario that the growth of the black hole predates that of the bulge.
+The \mbh-\lhost relation is inconsistent with the local one, accounting for passive evolution, indicating that at fixed mass BHs 8-10Gyrs ago reside in less luminous galaxies than today.
+Furthermore, the \mbh-\smass\ of our high redshift sample is consistent with the local \mbh-\smass$_{\rm bluge}$ relations.
+Considering that our sample are composed of bulge and disk components, the evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.
 \end{abstract}
@@
 
-Most galactic nuclei are thought to harbor a supermassive black hole (BH), whose mass (\mbh) is well known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar).
+Most galactic nuclei are thought to harbor a supermassive black hole (BH), whose mass (\mbh) is known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar).
 These tight correlations indicate a connection between nuclear activity and galaxy formation and evolution \citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
@@
 During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs.
-For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed bulge luminosity compared to the local relations.
-This offset is consistent with a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells.
-Similarly, the works by \citet{Bennert11, Woo++08} agreed to this scenario by studying the \mbh-\smass and \mbh-\sigstar relations.
-Nevertheless, the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution \citet{SS13, Sun2015, Cisternas2011}.
+For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today.
+This offset can be explained by a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells.
+Similarly, the works by \citet{Bennert11, Woo++08} supported this general scenario from the observation of the \mbh-\smass and \mbh-\sigstar relations.
+It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}.
 
@@
 First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called "virial" method.
-In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e.
+In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non gravitational component of the BLR gas dynamics, when compared to local samples with masses based on broad Balmer lines \citep[i.e.
 \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}.
@@
 In this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS.
-Our study overcomes the biases in the following way.
+Our study overcomes the limitations of previous studies in the following way.
 First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function.
-Second, we estimate \mbh\ using Balmer lines which avoids the systematics by \Mgii.
+Second, we estimate \mbh\ using Balmer lines which avoids potential systematic uncertainties in the UV-based estimators.
 Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements.
@@
 WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference.
-Given the high-quality data at such redshift, we can test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex).
+Given the high-quality of our data, we can test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex) [what does this mean?].
 
@@
 We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$.
-The Near IR spectra of AGNs are available from the survey of Subaru's Fiber Multi-Object Spectrograph \citep[FMOS, ][]{Kimura2010, Schulze2018}, a near-infrared (0.9-1.8 $\mu m$) spectrograph have with 400 apertures.
+The Near IR spectra of AGNs are available from the survey of Subaru's Fiber Multi-Object Spectrograph \citep[FMOS, ][]{Kimura2010, Schulze2018}, covering the wavelength range 0.9-1.8 $\mu m$.
 The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$ \citep{Greene2005, Matsuoka2013, Nobuta2012}.
@@
 We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
-For calibrating with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11a) to define our zero-point.
-The sample by B10 consistent 19 \mbh-\lhost\ relations with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex).
-The work of B11 contains 25 \mbh-\smass\ local active AGN analysis, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
+For comparison with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11a) to define our zero-point.
+The sample by B10 consists of 19 \mbh-\lhost\ measured with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex).
+The work of B11 contains 25 \mbh-\smass\ local active AGNs, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
 To increase the local \smass\ and \mbh\ to the higher range, we also include the inactive galaxies (mainly ellipticals or S0) as done by \citet{H+R04}.
-It is worth note that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample.
-In other words, it is the local \mbh-\smass$_{Bulge}$ relation that we compared.
+It is worth noting that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample.
+In other words, our local comparison is the \mbh-\smass$_{Bulge}$ and not those involving total quantities.
 }
@@
 \textcolor{blue}{
-Including the compared samples at the intermediate redshift range would help to understand the redshift evolution of these correlations.
-We compared intermediate redshift AGNs for the \mbh-\lhost\ relation include 52 sample by \citet{Park15} at $0.36<z<0.57$ and 27 sample by \citet{Bennert11, SS13} at $0.5<z<1.9$.
+We include in our analysis published samples at intermediate redshift range to understand the redshift evolution of these correlations.
+We select samples that were analyzed by members of our team, in order to ensure uniform measurements.
+The intermediate redshift AGNs that we consider include, for the \mbh-\lhost\ relation, 52 objects published by \citet{Park15} at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11, SS13} at $0.5<z<1.9$.
 Moreover, \citet{SS13} also derive the \smass\ which enable us to compare to the \mbh-\smass\ relation at $0.5<z<1.2$.
@@
 To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}.
-We find that the \hbeta\ estimator is very consistent ($<0.03$~dex) between the two references.
-Moreover, in \citet{Schulze2018}, the cross-calibrate between the \halpha\ and \hbeta\ are consistent.
+We find that the \hbeta\ estimator is very consistent ($<0.03$~dex r.m.s.
+or mean?) between the two references.
+Moreover, in \citet{Schulze2018}, the cross-calibration between the \halpha\ and \hbeta\ is consistent.
 Thus, we adopt the virial formalism from \citet{Schulze2018}:
@@
 
-Having defined the recipes, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
-14 of the overall systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged \mbh\ value.
+Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
+14 of the systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged \mbh\ value.
 We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}.
@@
 % The AGN surface photometry in IR Channel Filters.\\
-The high spatial resolution of the host image is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass.
-All the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as the HST program GO-15115, PI: John Silverman.
+
+High spatial resolution imaging is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass.
+For this purpose, all the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as part of the HST program GO-15115, PI: John Silverman.
 We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets.
-This selection ensures that the broad \halpha\ line ($4000\AA$) is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.
+This selection ensures that the broad \halpha\ line is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.
 
 %Drizzling, background noise...
-For each of the 32 new AGNs we took six separate exposures with $\sim399s$ (i.e.
+For each of the 32 new AGNs we obtained six separate exposures with $\sim399s$ (i.e.
 total exposure time $\sim2394s$).
@@
 The six exposures for each dither image were combined with the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel.
-To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} to measure the photometry.
+To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} tool.
 
 Multi-band information provides the spectral energy distributions (SED) at a more precise level.
-21/32 of our sample have rest-frame UV images by \citet{Scoville2007}.
+21/32 objects in our sample have rest-frame UV images by \citet{Scoville2007}.
 Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures.
@@
 %Introduce the PSF library
-The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source.
-The PSF is known to be vary across the detector and with time, due to the effect of aberrations and breathing.
+The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the point source is bright relative to the host.
+The PSF is known to be vary across the detector and with time, due to the effects of aberrations and breathing.
 Simulated PSF, such as {\sc TinyTim} ones, are usually insufficient matches to observations for our purposes \citet{Mechtley2012}.
@@
 We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects.
-In the end, the PSF library contains 78 and 37 PSFs for F140W and F125W, respectively.
+In the end, the PSF library contains 78 and 37 PSFs imaged through filters F140W and F125W, respectively.
 
@@
 We derive the rest-frame R band magnitude ($M_R$) and luminosity ($L_R$) of our sample based on their filter magnitude.
-18/32 systems have multi-band host magnitude which ables us to select the best stellar population that could fit the overall sample.
+18/32 systems have multi-band host magnitude which enables us to select the best stellar population that could fit the overall sample.
 We find that the 1~Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples.
 Adopting the color information, we perform the K-correction and derive the rest-frame R band magnitude of our sample.
-Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty level raised by this K-correction is within 0.05~mag.
+Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty introduced by this K-correction is within 0.05~mag.
 We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.
@@
 Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted.
-The raised uncertainty level to the stellar mass is expected to be within 0.1~dex.
+The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex, at fixed stellar initial mass function (changing the initial mass function would change all our stellar masses systematically).
 
@@
 Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$.
-We obtain the $\gamma  = 0.49 \pm 0.19$ which slightly indicates as the positive, see Figure~\ref{fig:MM-vz}, panel (a).
+We obtain the $\gamma  = 0.49 \pm 0.19$, i.e.
+tentative evidence for evolution , see Figure~\ref{fig:MM-vz}, panel (a).
 We also show the ratio of \mbh-\smass of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).
@@
 We perform the Kolmogorov?Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.
+We thus conclude that the host galaxies of our AGN are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.
 
@@
 These observations are associated with programs
-\#15115.
+\#15115. Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555
 
@@
 
-SB, TT and AJS acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
+XD and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
 
@@
 \startdata 
-CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.13\substack{+0.15\\-0.11}$ &$10.85\substack{+0.18\\-0.15}$\\[3pt]
-CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.49\substack{+0.15\\-0.11}$ &$10.21\substack{+0.18\\-0.15}$\\[3pt]
-CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.95\substack{+0.52\\-0.23}$ &$10.66\substack{+0.53\\-0.25}$\\[3pt]
-CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.13\substack{+0.03\\-0.03}$ &$10.85\substack{+0.10\\-0.10}$\\[3pt]
-CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26\substack{+0.11\\-0.09}$ &$10.98\substack{+0.14\\-0.13}$\\[3pt]
-CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.17\substack{+0.15\\-0.11}$ &$10.89\substack{+0.18\\-0.15}$\\[3pt]
-CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25\substack{+0.14\\-0.11}$ &$10.97\substack{+0.17\\-0.15}$\\[3pt]
-CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $11.07\substack{+0.02\\-0.02}$ &$10.79\substack{+0.10\\-0.10}$\\[3pt]
-CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.21\substack{+0.03\\-0.03}$ &$10.93\substack{+0.10\\-0.10}$\\[3pt]
-CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.19\substack{+0.04\\-0.04}$ &$10.91\substack{+0.10\\-0.10}$\\[3pt]
-CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.15\substack{+0.35\\-0.19}$ &$10.87\substack{+0.36\\-0.21}$\\[3pt]
-CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.79\substack{+0.16\\-0.12}$ &$10.51\substack{+0.19\\-0.15}$\\[3pt]
-CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.81\substack{+0.22\\-0.15}$ &$10.53\substack{+0.24\\-0.18}$\\[3pt]
-CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.10\substack{+0.23\\-0.15}$ &$10.82\substack{+0.25\\-0.18}$\\[3pt]
-CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $11.07\substack{+0.12\\-0.10}$ &$10.79\substack{+0.16\\-0.14}$\\[3pt]
-LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.40\substack{+0.09\\-0.07}$ &$11.12\substack{+0.13\\-0.12}$\\[3pt]
-LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.21\substack{+0.09\\-0.08}$ &$10.93\substack{+0.13\\-0.12}$\\[3pt]
-LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.17\substack{+0.06\\-0.05}$ &$10.88\substack{+0.11\\-0.11}$\\[3pt]
-XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.98\substack{+0.07\\-0.06}$ &$10.70\substack{+0.12\\-0.12}$\\[3pt]
-XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.24\substack{+0.12\\-0.10}$ &$10.96\substack{+0.16\\-0.14}$\\[3pt]
-XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.20\substack{+0.26\\-0.16}$ &$10.92\substack{+0.28\\-0.19}$\\[3pt]
-CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ... & ... & ... & $10.80\substack{+0.16\\-0.12}$ &$10.52\substack{+0.19\\-0.15}$\\[3pt]
-CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ... & ... & ... & $10.98\substack{+0.06\\-0.05}$ &$10.70\substack{+0.12\\-0.11}$\\[3pt]
+CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.05\substack{+0.15\\-0.11}$ &$10.78\substack{+0.18\\-0.15}$\\[3pt]
+CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.41\substack{+0.15\\-0.11}$ &$10.14\substack{+0.18\\-0.15}$\\[3pt]
+CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.86\substack{+0.52\\-0.23}$ &$10.59\substack{+0.53\\-0.25}$\\[3pt]
+CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.05\substack{+0.03\\-0.03}$ &$10.78\substack{+0.10\\-0.10}$\\[3pt]
+CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.18\substack{+0.11\\-0.09}$ &$10.91\substack{+0.14\\-0.13}$\\[3pt]
+CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.08\substack{+0.15\\-0.11}$ &$10.81\substack{+0.18\\-0.15}$\\[3pt]
+CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.16\substack{+0.14\\-0.11}$ &$10.89\substack{+0.17\\-0.15}$\\[3pt]
+CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $10.98\substack{+0.02\\-0.02}$ &$10.71\substack{+0.10\\-0.10}$\\[3pt]
+CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.13\substack{+0.03\\-0.03}$ &$10.86\substack{+0.10\\-0.10}$\\[3pt]
+CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.11\substack{+0.04\\-0.04}$ &$10.84\substack{+0.10\\-0.10}$\\[3pt]
+CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.07\substack{+0.35\\-0.19}$ &$10.80\substack{+0.36\\-0.21}$\\[3pt]
+CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.70\substack{+0.16\\-0.12}$ &$10.43\substack{+0.19\\-0.15}$\\[3pt]
+CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.73\substack{+0.22\\-0.15}$ &$10.46\substack{+0.24\\-0.18}$\\[3pt]
+CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.02\substack{+0.23\\-0.15}$ &$10.75\substack{+0.25\\-0.18}$\\[3pt]
+CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $10.98\substack{+0.12\\-0.10}$ &$10.72\substack{+0.16\\-0.14}$\\[3pt]
+LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.32\substack{+0.09\\-0.07}$ &$11.05\substack{+0.13\\-0.12}$\\[3pt]
+LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.12\substack{+0.09\\-0.08}$ &$10.86\substack{+0.13\\-0.12}$\\[3pt]
+LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.08\substack{+0.06\\-0.05}$ &$10.81\substack{+0.11\\-0.11}$\\[3pt]
+XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.89\substack{+0.07\\-0.06}$ &$10.63\substack{+0.12\\-0.12}$\\[3pt]
+XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.15\substack{+0.12\\-0.10}$ &$10.88\substack{+0.16\\-0.14}$\\[3pt]
+XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.12\substack{+0.26\\-0.16}$ &$10.85\substack{+0.28\\-0.19}$\\[3pt]
+CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ... & ... & ... & $10.71\substack{+0.16\\-0.12}$ &$10.45\substack{+0.19\\-0.15}$\\[3pt]
+CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ... & ... & ... & $10.90\substack{+0.06\\-0.05}$ &$10.63\substack{+0.12\\-0.11}$\\[3pt]
 CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ...
@@
 & ...
-& $11.61\substack{+0.28\\-0.17}$ &$11.33\substack{+0.30\\-0.20}$\\[3pt]
-CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ... & ... & ... & $10.14\substack{+0.23\\-0.15}$ &$9.86\substack{+0.25\\-0.18}$\\[3pt]
+& $11.52\substack{+0.28\\-0.17}$ &$11.25\substack{+0.30\\-0.20}$\\[3pt]
+CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ... & ... & ... & $10.06\substack{+0.23\\-0.15}$ &$9.79\substack{+0.25\\-0.18}$\\[3pt]
 ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ...
@@
 & ...
-& $11.25\substack{+0.12\\-0.10}$ &$10.97\substack{+0.16\\-0.14}$\\[3pt]
+& $11.16\substack{+0.12\\-0.10}$ &$10.89\substack{+0.16\\-0.14}$\\[3pt]
 SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ...
@@
 & ...
-& $10.84\substack{+0.09\\-0.08}$ &$10.56\substack{+0.14\\-0.13}$\\[3pt]
-SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ... & ... & ... & $10.89\substack{+0.11\\-0.09}$ &$10.61\substack{+0.15\\-0.13}$\\[3pt]
+& $10.75\substack{+0.09\\-0.08}$ &$10.49\substack{+0.14\\-0.13}$\\[3pt]
+SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ... & ... & ... & $10.80\substack{+0.11\\-0.09}$ &$10.54\substack{+0.15\\-0.13}$\\[3pt]
 SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ...
@@
 & ...
-& $10.86\substack{+0.07\\-0.06}$ &$10.58\substack{+0.12\\-0.12}$\\[3pt]
+& $10.77\substack{+0.07\\-0.06}$ &$10.51\substack{+0.12\\-0.12}$\\[3pt]
 SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ...
@@
 & ...
-& $11.28\substack{+0.13\\-0.10}$ &$11.00\substack{+0.17\\-0.14}$\\[3pt]
-SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ... & ... & ... & $10.03\substack{+0.47\\-0.22}$ &$9.75\substack{+0.48\\-0.24}$\\[3pt]
+& $11.19\substack{+0.13\\-0.10}$ &$10.92\substack{+0.17\\-0.14}$\\[3pt]
+SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ... & ... & ... & $9.95\substack{+0.47\\-0.22}$ &$9.68\substack{+0.48\\-0.24}$\\[3pt]
 SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ...
@@
 & ...
-& $11.12\substack{+0.21\\-0.14}$ &$10.83\substack{+0.23\\-0.17}$\\[3pt]
+& $11.03\substack{+0.21\\-0.14}$ &$10.76\substack{+0.23\\-0.17}$\\[3pt]
 \enddata

### 2019-04-03 manuscript/manuscript.tex
Update manuscript.tex

@@
 We also compare the histogram of the inferred \Reff\ and \sersic\ n to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value.
-We perform the Kolmogorov?Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.
+We perform the Kolmogorov-Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.
 We thus conclude that the host galaxies of our AGN are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.
@@
 
-XD and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
+XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
 

### 2019-04-24 manuscript/manuscript.tex
update manuscript

@@
 \usepackage{amsmath}
+\usepackage{float}
 
@@
 For this purpose, we obtained multi-band {\it Hubble Space Telescope} of  a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs).
-By applying state-of-the art tools to the images we obtained accurate host galaxy luminosity and stellar mass.
+By applying state-of-the-art tools to the images we obtained accurate host galaxy luminosity and stellar mass.
 The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts.
@@
 The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$ \citep{Greene2005, Matsuoka2013, Nobuta2012}.
-Overall, our final sample is composed of 32 new observations by HST/WFC3.
+Overall, our final sample is composed of 32 new observations by \hst/WFC3.
 Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.
+
+\begin{deluxetable*}{llccccc}
+\tablecolumns{7}
+\tablewidth{0pt}
+\tablecaption{Details of Observation} 
+\tablehead{ 
+\colhead{Object ID} &
+\colhead{$z$} & 
+\colhead{WFC3/Filter} &
+\colhead{$RA$}&
+\colhead{$DEC$}&
+\colhead{Observing date}&
+\colhead{Expousre time (s)}
+\\ 
+\colhead{(1)} &
+\colhead{(2)} &
+\colhead{(3)} &
+\colhead{(4)} &
+\colhead{(5)} &
+\colhead{(6)} &
+\colhead{(7)}
+} 
+\startdata
+%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
+%\\
+COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
+COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
+COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
+COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
+COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
+COSMOS-CID255$^a$ & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
+COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
+COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
+COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
+COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
+COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
+COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
+COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
+COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
+COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
+COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
+COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
+COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
+COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
+COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
+COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
+CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
+CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
+CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
+CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
+ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
+SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
+SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
+SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
+SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
+SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
+SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
+\enddata
+\label{tab:objlist}
+\tablecomments{
+Column 1: Object field and ID.
+Column 2: Redshifts.
+Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
+Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
+Column 6: The observing start date.
+\\
+$^a$For CID255, 3/6 of the dither WFC3 images are corrupted. We analyze this sample by a same approach, taking the 3 avalible frames.
+}
+\end{deluxetable*}
 
@@
 
+\begin{deluxetable*}
+{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
+\tablecolumns{9}
+\tablewidth{0pt}
+\tablecaption{Inferred \mbh\ .} 
+\tablehead
+{ 
+\colhead{Target ID}&
+  \multicolumn{4}{c}{using emission line \halpha}&
+  \multicolumn{4}{c}{using emission line \hbeta} \\
+  \cline{2-5}  \cline{6-9} \\
+\colhead{}& 
+\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}& Eddington ratio &
+\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}& Eddington ratio \\
+\colhead{}& 
+\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
+\colhead{(M$_{\odot}$)}& (log$\lambda$)&
+\colhead{(\kms)}& 
+\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$\lambda$)\\
+\colhead{(1)}& 
+\colhead{(2)}& \colhead{(3)}& 
+\colhead{(4)}& \colhead{(5)}& 
+\colhead{(6)}&\colhead{(7)}&
+\colhead{(8)}& \colhead{(9)}
+}
+\startdata 
+CID1174 & 1906 & 43.43 & 7.99 & -0.50 & 5898 & 44.76 & 8.83& -1.35 \\
+CID1281 & 1619 & 43.24 & 7.75 & -0.45 & ... & ... & ...& ... \\
+CID206 & 3334 & 43.48 & 8.53 & -1.00 & ... & ... & ...& ... \\
+CID216 & 2230 & 42.85 & 7.85 & -0.93 & ... & ... & ...& ... \\
+CID237 & 2112 & 43.86 & 8.29 & -0.40 & ... & ... & ...& ... \\
+CID255 & 1932 & 43.99 & 8.27 & -0.25 & 3709 & 45.37 & 8.73& -0.63 \\
+CID3242 & 2543 & 43.83 & 8.45 & -0.58 & 3775 & 45.10 & 8.61& -0.78 \\
+CID3570 & 1959 & 43.16 & 7.89 & -0.66 & ... & ... & ...& ... \\
+CID452 & 3458 & 42.92 & 8.30 & -1.30 & 3127 & 44.63 & 8.22& -0.88 \\
+CID454 & 2824 & 43.34 & 8.31 & -0.91 & ... & ... & ...& ... \\
+CID50 & 2340 & 43.94 & 8.42 & -0.45 & 1939 & 45.33 & 8.15& -0.09 \\
+CID543 & 2189 & 43.57 & 8.19 & -0.56 & ... & ... & ...& ... \\
+CID597 & 1656 & 43.33 & 7.81 & -0.42 & ... & ... & ...& ... \\
+CID607 & 3009 & 43.67 & 8.53 & -0.81 & 4242 & 44.78 & 8.56& -1.06 \\
+CID70 & 2480 & 43.51 & 8.27 & -0.71 & 3982 & 45.16 & 8.69& -0.80 \\
+LID1273 & 3224 & 43.61 & 8.56 & -0.90 & ... & ... & ...& ... \\
+LID1538 & 2941 & 43.60 & 8.47 & -0.83 & ... & ... & ...& ... \\
+LID360 & 2482 & 43.88 & 8.45 & -0.53 & 2869 & 45.09 & 8.37& -0.55 \\
+XID2138 & 3186 & 43.61 & 8.55 & -0.89 & 2945 & 44.81 & 8.25& -0.72 \\
+XID2202 & 2973 & 43.56 & 8.46 & -0.85 & ... & ... & ...& ... \\
+XID2396 & 2271 & 44.06 & 8.46 & -0.37 & 2658 & 45.50 & 8.51& -0.27 \\
+CDFS-1 & 5449 & 43.08 & 8.79 & -0.98 & ... & ... & ...& ... \\
+CDFS-229 & 2254 & 43.30 & 8.08 & -0.48 & ... & ... & ...& ... \\
+CDFS-321 & 2442 & 43.93 & 8.46 & -0.50 & ... & ... & ...& ... \\
+CDFS-724 & 3352 & 42.56 & 8.09 & -1.22 & ... & ... & ...& ... \\
+ECDFS-358 & 2237 & 43.40 & 8.12 & -0.67 & ... & ... & ...& ... \\
+SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.85 & 6761 & 44.71 & 8.93& -1.50 \\
+SXDS-X50 & 1817 & 43.42 & 7.94 & -0.47 & ... & ... & ...& ... \\
+SXDS-X717 & 2931 & 43.05 & 8.20 & -1.08 & ... & ... & ...& ... \\
+SXDS-X735 & 2702 & 43.70 & 8.44 & -0.70 & 3520 & 45.07 & 8.54& -0.73 \\
+SXDS-X763 & 2961 & 43.57 & 8.47 & -0.84 & 4509 & 44.51 & 8.47& -1.27 \\
+SXDS-X969 & 2296 & 43.50 & 8.20 & -0.64 & 1696 & 45.05 & 7.90& -0.11 \\
+\enddata
+\label{tab:result_mbh}
+\tablecomments{
+Column 1: Object ID.
+Column 2-4: \halpha\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
+Column 5-7: \hbeta\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
+}
+\end{deluxetable*}
+
 \section{\hst\ observations}
@@
 High spatial resolution imaging is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass.
-For this purpose, all the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as part of the HST program GO-15115, PI: John Silverman.
+For this purpose, all the new 32 AGN systems were observed with the \hst/WFC3 infrared channel, as part of the HST program GO-15115, PI: John Silverman.
 We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets.
@@
 
-The inference of the host properties is weighted by eight top-ranked PSFs.
-For a smaller number of PSFs one tends to underestimate the uncertainties.
-To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the one inferred by five and ten top-ranked PSFs.
-As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference is solid when the amount of selected PSF exceeds five.
-
-%The inference of F814w data.
-18/32 systems in the COSMOS field have ACS/F184W imaging data.
-We infer their host properties using the same approach used for the WFC3-IR data.
-The field of view by ACS are larger than WFC3, and we collected in total 174 ACS PSFs in the library.
-In principle, the host inference by IR band is superior to the one by UV band, giving that the effects of dust extinction and contrast between the (blue) AGN and (red) host.
-Thus, we fix the \Reff\ and \sersic\ $n$ as the value inferred by IR band, assuming that the morphology of the galaxy is consistent between ACS and WFC3.
-
-We list all the inference of the host galaxy properties in the Table~\ref{tab:result_sersic}.
-
-\section{Results}
-\label{sec:result}
-
-\subsection{Host galaxy properties}
-We derive the rest-frame R band magnitude ($M_R$) and luminosity ($L_R$) of our sample based on their filter magnitude.
-18/32 systems have multi-band host magnitude which enables us to select the best stellar population that could fit the overall sample.
-We find that the 1~Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples.
-Adopting the color information, we perform the K-correction and derive the rest-frame R band magnitude of our sample.
-Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty introduced by this K-correction is within 0.05~mag.
-We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.
-
-Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted.
-The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex, at fixed stellar initial mass function (changing the initial mass function would change all our stellar masses systematically).
-
-%\textcolor{red}{Need to add the uncertainty level of their inference}.
-
-The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare their relations to to the \mbh.
-
-\subsection{\mbh-\lhost\ relation}
-We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}, panel (a). Following common practice, we fit the local relation as a linear relation,
-\begin{eqnarray}
-\label{eq:MLlocal}
-\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}}),
-\end {eqnarray}
-which enables direct comparison to the distant sample.
-The figure shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones, indicating that the black hole mass and the host luminosity located at a similar relation at different galaxy age.
-However, considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
-Especially, in a passive evolution scenario, we expect \lhost\ to fade over time.
-
-We follow \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
-$d{\rm mag}_{\rm R} \sim d\log(1+z)$, i.e.,
-\begin{eqnarray}
-\label{eq:L_relation}
-\log(L_{R,0})=\log(L_{R}) - 1.48 \log (1+z).
-\end{eqnarray} 
-This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$.
-We refer to \citet[][section 5.4]{Ding2017b} for more details.
-Transferring the \lhost\ to today, we show the evolution-corrected \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (b) and find that, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts.
-
-To quantitatively understand this trend, we fit the offset as a function of redshift in form as:
-\begin{eqnarray}
-\label{eq:offset}
-\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
-\end{eqnarray} 
-where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{L_{R,0}}{10^{10}L_{\odot}})$.
-The best-fit and  1-$\sigma$ inference are $\gamma = 0.69 \pm 0.15$.
-
-Given that the current result does not take into account selection effects yet, we will draw the conclusion in section~\ref{select_eff}.
-
-\subsection{\mbh-\smass\ relation}
-Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution.
-In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample.
-We visually see that the mass distributions for the three samples are very similar.
-Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$.
-We obtain the $\gamma  = 0.49 \pm 0.19$, i.e.
-tentative evidence for evolution , see Figure~\ref{fig:MM-vz}, panel (a).
-We also show the ratio of \mbh-\smass of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).
-We highlight that our results are less biased in both the measurement of \mbh\ and \smass.
-
-We highlight that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
-That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at the local.
-Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.
-
-Without taking into account the selection effect, the direct comparison shows that the growth of the black hole predates that of the host bulge.
-
-\subsection{Selection effect}
-\label{select_eff}
-\textcolor{red}{To be written after Daeseong's analysis.}.
-
-\section{discussion}
-\label{sec:dis}
-\subsection{Systematic error}
-
-In our analysis, we adopt one stellar population to the overall sample.
-We note that adopting the private stellar populations for these samples which have both multi-band host magnitude could be more robust in principle.
-However, considering that the host magnitude in ACS band is faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost.
-Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry.
-\textcolor{red}{Describe the ground-based data}.
-In this paper, we focus on the decomposing of the AGN and carry out a rapid analysis of the \mbh-host relations.
-The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.
-
-\subsection{Comparison to the inactive galaxies}
-We compared the morphology of AGNs host galaxies to the inactive galaxies in CANDLES imaging survey.
-We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.
-
-In Figure~\ref{fig:Mstar-rn}, we plot the \smass\ versus the \Reff\ and \sersic\ index.
-The color coding is based on the filter flux ratio between WFC3 and ACS.
-The distribution of \smass-\Reff\ relation show that our AGN hosts concentrate at the high end of the stellar mass, close to the red sequence.
-
-We also compare the histogram of the inferred \Reff\ and \sersic\ n to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value.
-We perform the Kolmogorov-Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.
-We thus conclude that the host galaxies of our AGN are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.
-
-%high
-%The distribution shows that our AGN host are located at a higher end of the stellar mass at region where
-
-\subsection{JWST}
-
-\section{Summary}
-\label{sec:sum}
-%We presented the study of the \mbh\ and host property's evolution to high redshift until 1.7.
-
-\section*{Acknowledgments}
-Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
-These observations are associated with programs
-\#15115. Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555
-
-The authors fully appreciate the discussions with Vardha N. Bennert, Takahiro Morishita.
-
-XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
-
-This work has made use of lenstronomy \citep{lenstronomy}, Astropy \citep{Astropy}, photutils, TOPCAT \citep{TOPCAT}, Matplotlib \citep{Matplotlib} and standard Python libraries.
-
-\bibliographystyle{apj.bst}
-\bibliography{references}
-
-\begin{deluxetable}{llccccc}
-\tablecolumns{7}
-\tablewidth{0pt}
-\tablecaption{Details of Observation} 
-\tablehead{ 
-\colhead{Object ID} &
-\colhead{$z$} & 
-\colhead{WFC3/Filter} &
-\colhead{$RA$}&
-\colhead{$DEC$}&
-\colhead{Observing date}&
-\colhead{Expousre time (s)}
-\\ 
-\colhead{(1)} &
-\colhead{(2)} &
-\colhead{(3)} &
-\colhead{(4)} &
-\colhead{(5)} &
-\colhead{(6)} &
-\colhead{(7)}
-} 
-\startdata
-%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
-%\\
-COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
-COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
-COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
-COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
-COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
-COSMOS-CID255$^a$ & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
-COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
-COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
-COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
-COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
-COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
-COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
-COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
-COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
-COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
-COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
-COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
-COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
-COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
-COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
-COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
-CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
-CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
-CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
-CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
-ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
-SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
-SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
-SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
-SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
-SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
-SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
-\enddata
-\label{tab:objlist}
-\tablecomments{
-Column 1: Object field and ID.
-Column 2: Redshifts.
-Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
-Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
-Column 6: The observing start date.
-\\
-$^a$For CID255, 3/6 of the dither WFC3 images are corrupted. We analyze this sample by a same approach, taking the 3 avalible frames.
-}
-\end{deluxetable}
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
+\caption{\label{fig:AGN_decomp} 
+Figure illustrates the inference for the 32 objects based on the WFC3 images.
+In each row, observed data (first column), best-fit models (second column), data subtracted by the inferred point source (third column),  normalized residuals (fourth column) are presented together with the target ID.
+In the fifth column, we present the 1-D surface brightness profiles (top) and the corresponding residual (bottom).
+The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects).
+Note that the one-dimensional surface brightness profiles are only for illustration purposes.
+The actual fitting is based on the two-dimensional images.
+The remaining 31 objects of the sample are shown in appendix A.
+}}
+\end{figure*}
 
@@
 \end{deluxetable*}
+
+\begin{figure*}
+\centering
+{
+\includegraphics[height=0.75\textwidth]{fig/flux_r_n_corner.pdf}
+}
+\caption{\label{fig:flux_r_n_corner}
+Illustration of the relations between the inferred host \sersic\ parameters.}
+\end{figure*}
+
+The inference of the host properties is weighted by eight top-ranked PSFs.
+For a smaller number of PSFs one tends to underestimate the uncertainties.
+To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the one inferred by five and ten top-ranked PSFs.
+As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference is solid when the amount of selected PSF exceeds five.
+
+\begin{figure*}
+\centering
+{
+\includegraphics[height=0.35\textwidth]{fig/hist_compare.pdf}
+}
+\caption{\label{fig:hist_compare} 
+Comparison of the histogram of the inferred host flux ratio, based on the different volum of the top-ranked PSFs.}
+\end{figure*}
+
+%The inference of F814w data.
+18/32 systems in the COSMOS field have ACS/F184W imaging data.
+We infer their host flux ratio using the same approach used for the WFC3-IR data.
+The field of view by ACS are larger than WFC3, and we collected in total 174 ACS PSFs in the library.
+In principle, the host inference by IR band is superior to the one by UV band, giving that the effects of dust extinction and contrast between the (blue) AGN and (red) host.
+Thus, we fix the \Reff\ and \sersic\ $n$ as the value inferred by IR band, assuming that the morphology of the galaxy is consistent between ACS and WFC3.
+
+We list all the inference of the host galaxy properties in the Table~\ref{tab:result_sersic}.
 
@@
 
-\begin{deluxetable*}
-{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
-\tablecolumns{9}
-\tablewidth{0pt}
-\tablecaption{Inferred \mbh\ .} 
-\tablehead
-{ 
-\colhead{Target ID}&
-  \multicolumn{4}{c}{using emission line \halpha}&
-  \multicolumn{4}{c}{using emission line \hbeta} \\
-  \cline{2-5}  \cline{6-9} \\
-\colhead{}& 
-\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}& Eddington ratio &
-\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}& Eddington ratio \\
-\colhead{}& 
-\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
-\colhead{(M$_{\odot}$)}& (log$\lambda$)&
-\colhead{(\kms)}& 
-\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$\lambda$)\\
-\colhead{(1)}& 
-\colhead{(2)}& \colhead{(3)}& 
-\colhead{(4)}& \colhead{(5)}& 
-\colhead{(6)}&\colhead{(7)}&
-\colhead{(8)}& \colhead{(9)}
-}
-\startdata 
-CID1174 & 1906 & 43.43 & 7.99 & -0.50 & 5898 & 44.76 & 8.83& -1.35 \\
-CID1281 & 1619 & 43.24 & 7.75 & -0.45 & ... & ... & ...& ... \\
-CID206 & 3334 & 43.48 & 8.53 & -1.00 & ... & ... & ...& ... \\
-CID216 & 2230 & 42.85 & 7.85 & -0.93 & ... & ... & ...& ... \\
-CID237 & 2112 & 43.86 & 8.29 & -0.40 & ... & ... & ...& ... \\
-CID255 & 1932 & 43.99 & 8.27 & -0.25 & 3709 & 45.37 & 8.73& -0.63 \\
-CID3242 & 2543 & 43.83 & 8.45 & -0.58 & 3775 & 45.10 & 8.61& -0.78 \\
-CID3570 & 1959 & 43.16 & 7.89 & -0.66 & ... & ... & ...& ... \\
-CID452 & 3458 & 42.92 & 8.30 & -1.30 & 3127 & 44.63 & 8.22& -0.88 \\
-CID454 & 2824 & 43.34 & 8.31 & -0.91 & ... & ... & ...& ... \\
-CID50 & 2340 & 43.94 & 8.42 & -0.45 & 1939 & 45.33 & 8.15& -0.09 \\
-CID543 & 2189 & 43.57 & 8.19 & -0.56 & ... & ... & ...& ... \\
-CID597 & 1656 & 43.33 & 7.81 & -0.42 & ... & ... & ...& ... \\
-CID607 & 3009 & 43.67 & 8.53 & -0.81 & 4242 & 44.78 & 8.56& -1.06 \\
-CID70 & 2480 & 43.51 & 8.27 & -0.71 & 3982 & 45.16 & 8.69& -0.80 \\
-LID1273 & 3224 & 43.61 & 8.56 & -0.90 & ... & ... & ...& ... \\
-LID1538 & 2941 & 43.60 & 8.47 & -0.83 & ... & ... & ...& ... \\
-LID360 & 2482 & 43.88 & 8.45 & -0.53 & 2869 & 45.09 & 8.37& -0.55 \\
-XID2138 & 3186 & 43.61 & 8.55 & -0.89 & 2945 & 44.81 & 8.25& -0.72 \\
-XID2202 & 2973 & 43.56 & 8.46 & -0.85 & ... & ... & ...& ... \\
-XID2396 & 2271 & 44.06 & 8.46 & -0.37 & 2658 & 45.50 & 8.51& -0.27 \\
-CDFS-1 & 5449 & 43.08 & 8.79 & -0.98 & ... & ... & ...& ... \\
-CDFS-229 & 2254 & 43.30 & 8.08 & -0.48 & ... & ... & ...& ... \\
-CDFS-321 & 2442 & 43.93 & 8.46 & -0.50 & ... & ... & ...& ... \\
-CDFS-724 & 3352 & 42.56 & 8.09 & -1.22 & ... & ... & ...& ... \\
-ECDFS-358 & 2237 & 43.40 & 8.12 & -0.67 & ... & ... & ...& ... \\
-SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.85 & 6761 & 44.71 & 8.93& -1.50 \\
-SXDS-X50 & 1817 & 43.42 & 7.94 & -0.47 & ... & ... & ...& ... \\
-SXDS-X717 & 2931 & 43.05 & 8.20 & -1.08 & ... & ... & ...& ... \\
-SXDS-X735 & 2702 & 43.70 & 8.44 & -0.70 & 3520 & 45.07 & 8.54& -0.73 \\
-SXDS-X763 & 2961 & 43.57 & 8.47 & -0.84 & 4509 & 44.51 & 8.47& -1.27 \\
-SXDS-X969 & 2296 & 43.50 & 8.20 & -0.64 & 1696 & 45.05 & 7.90& -0.11 \\
-\enddata
-\label{tab:result_mbh}
-\tablecomments{
-Column 1: Object ID.
-Column 2-4: \halpha\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
-Column 5-7: \hbeta\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
-}
-\end{deluxetable*}
+\section{Results}
+\label{sec:result}
 
-\begin{figure*}
-\centering
-%\hspace{-5.5em}
-{
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1281_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID206_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID216_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID237_SB_profile.pdf}
-\caption{\label{fig:AGN_decomp} 
-Figure illustrates the inference for the 32 objects based on the WFC3 images.
-In each row, observed data (first column), best-fit models (second column), data subtracted by the inferred point source (third column),  normalized residuals (fourth column) are presented together with the target ID.
-In the fifth column, we present the 1-D surface brightness profiles (top) and the corresponding residual (bottom).
-The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects).
-Note that the one-dimensional surface brightness profiles are only for illustration purposes.
-The actual fitting is based on the two-dimensional images.
-}}
-\end{figure*}
+\subsection{Host galaxy properties}
+We derive the rest-frame R band magnitude ($M_R$) and luminosity ($L_R$) of our sample based on their filter magnitude.
+18/32 systems have multi-band host magnitude which enables us to select the best stellar population that could fit the overall sample.
+We find that the 1~Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples.
+Adopting the color information, we perform the K-correction and derive the rest-frame R band magnitude of our sample.
+Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty introduced by this K-correction is within 0.05~mag.
+We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.
 
-\begin{figure*}
-\centering
-%\hspace{-5.5em}
-{
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID255_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID3242_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID3570_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID452_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID454_SB_profile.pdf}
-}
-\figurenum{1}
-\caption{Continued.}
-\end{figure*}
+Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted.
+The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex, at fixed stellar initial mass function (changing the initial mass function would change all our stellar masses systematically).
 
-\begin{figure*}
-\centering
-%\hspace{-5.5em}
-{
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID50_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID543_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID597_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID607_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID70_SB_profile.pdf}
-}
-\figurenum{1}
-\caption{Continued.}
-\end{figure*}
+%\textcolor{red}{Need to add the uncertainty level of their inference}.
 
-\begin{figure*}
-\centering
-%\hspace{-5.5em}
-{
-\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2138_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2202_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2396_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_LID1273_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_LID1538_SB_profile.pdf}
-}
-\figurenum{1}
-\caption{Continued.}
-\end{figure*}
+The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare their relations to to the \mbh.
 
-\begin{figure*}
-\centering
-%\hspace{-5.5em}
-{
-\includegraphics[height=0.25\textwidth]{fig/best_fit_LID360_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-1_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-229_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-321_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-724_SB_profile.pdf}
-}
-\figurenum{1}
-\caption{Continued.}
-\end{figure*}
-
-\begin{figure*}
-\centering
-%\hspace{-5.5em}
-{
-\includegraphics[height=0.25\textwidth]{fig/best_fit_ECDFS-358_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X1136_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X50_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X717_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X735_SB_profile.pdf}
-}
-\figurenum{1}
-\caption{Continued.}
-\end{figure*}
-
-\begin{figure*}
-\centering
-%\hspace{-5.5em}
-{
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X763_SB_profile.pdf}
-\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X969_SB_profile.pdf}
-}
-\figurenum{1}
-\caption{Continued.}
-\end{figure*}
-
-\begin{figure*}
-\centering
-{
-\includegraphics[height=0.75\textwidth]{fig/flux_r_n_corner.pdf}
-}
-\caption{\label{fig:flux_r_n_corner}
-Illustration of the relations between the inferred host \sersic\ parameters.}
-\end{figure*}
-
-\begin{figure*}
-\centering
-{
-\includegraphics[height=0.35\textwidth]{fig/hist_compare.pdf}
-}
-\caption{\label{fig:hist_compare} 
-Comparison of the histogram of the inferred host flux ratio, based on the different volum of the top-ranked PSFs.}
-\end{figure*}
+\subsection{\mbh-\lhost\ relation}
+We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}, panel (a). Following common practice, we fit the local relation as a linear relation,
+\begin{eqnarray}
+\label{eq:MLlocal}
+\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}}),
+\end {eqnarray}
+which enables direct comparison to the distant sample.
+The figure shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones, indicating that the black hole mass and the host luminosity located at a similar relation at different galaxy age.
+However, considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
+Especially, in a passive evolution scenario, we expect \lhost\ to fade over time.
 
@@
 
+We follow \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
+$d{\rm mag}_{\rm R} \sim d\log(1+z)$, i.e.,
+\begin{eqnarray}
+\label{eq:L_relation}
+\log(L_{R,0})=\log(L_{R}) - 1.48 \log (1+z).
+\end{eqnarray} 
+This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$.
+We refer to \citet[][section 5.4]{Ding2017b} for more details.
+Transferring the \lhost\ to today, we show the evolution-corrected \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (b) and find that, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts.
+
+To quantitatively understand this trend, we fit the offset as a function of redshift in form as:
+\begin{eqnarray}
+\label{eq:offset}
+\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
+\end{eqnarray} 
+where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{L_{R,0}}{10^{10}L_{\odot}})$.
+The best-fit and  1-$\sigma$ inference are $\gamma = 0.69 \pm 0.15$, as shown in Figure~\ref{fig:ML-vz}
+
 \begin{figure}
@@
 \end{figure}
+
+Given that the current result does not take into account selection effects yet, we will draw the conclusion in section~\ref{select_eff}.
+
+\subsection{\mbh-\smass\ relation}
+Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution.
+In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample.
+We visually see that the mass distributions for the three samples are very similar.
+Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$.
+We obtain the $\gamma  = 0.49 \pm 0.19$, i.e.
+tentative evidence for evolution , see Figure~\ref{fig:MM-vz}, panel (a).
+We also show the ratio of \mbh-\smass of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).
+We highlight that our results are less biased in both the measurement of \mbh\ and \smass.
 
@@
 
+We highlight that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
+That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at the local.
+Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.
+
+Without taking into account the selection effect, the direct comparison shows that the growth of the black hole predates that of the host bulge.
+
+\subsection{Selection effect}
+\label{select_eff}
+\textcolor{red}{To be written after Daeseong's analysis.}.
+
+\section{discussion}
+\label{sec:dis}
+\subsection{Systematic error}
+
+In our analysis, we adopt one stellar population to the overall sample.
+We note that adopting the private stellar populations for these samples which have both multi-band host magnitude could be more robust in principle.
+However, considering that the host magnitude in ACS band is faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost.
+Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry.
+\textcolor{red}{Describe the ground-based data}.
+In this paper, we focus on the decomposing of the AGN and carry out a rapid analysis of the \mbh-host relations.
+The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.
+
+\subsection{Comparison to the inactive galaxies}
+We compared the morphology of AGNs host galaxies to the inactive galaxies in CANDLES imaging survey.
+We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.
+
+In Figure~\ref{fig:Mstar-rn}, we plot the \smass\ versus the \Reff\ and \sersic\ index.
+The color coding is based on the filter flux ratio between WFC3 and ACS.
+The distribution of \smass-\Reff\ relation show that our AGN hosts concentrate at the high end of the stellar mass, close to the red sequence.
+
 \begin{figure*}
@@
 
+We also compare the histogram of the inferred \Reff\ and \sersic\ n to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value.
+We perform the Kolmogorov-Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.
+We thus conclude that the host galaxies of our AGN are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.
+
 \begin{figure*}
@@
 
-%\appendix
-%\section{If needed}
-%\label{app:warp}
+%high
+%The distribution shows that our AGN host are located at a higher end of the stellar mass at region where
+
+\subsection{JWST}
+
+\section{Summary}
+\label{sec:sum}
+%We presented the study of the \mbh\ and host property's evolution to high redshift until 1.7.
+
+\section*{Acknowledgments}
+Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
+These observations are associated with programs
+\#15115. Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555
+
+The authors fully appreciate the discussions with Vardha N. Bennert, Anton M. Koekemoer, Takahiro Morishita.
+
+XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
+
+This work has made use of lenstronomy \citep{lenstronomy}, Astropy \citep{Astropy}, photutils, TOPCAT \citep{TOPCAT}, Matplotlib \citep{Matplotlib} and standard Python libraries.
+
+\bibliographystyle{apj.bst}
+\bibliography{references}
+
+\newpage
+\appendix
+\section{A. The demonstration of remaining 31 AGNs}\label{appA}
+The AGNs decomposition for the other 31 objects of our sample, presented in the same way as Figure~\ref{fig:AGN_decomp}.
+
+\begin{figure}[H]
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1281_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID206_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID216_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID237_SB_profile.pdf}
+}
+\end{figure}
+
+\begin{figure}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID255_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID3242_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID3570_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID452_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID454_SB_profile.pdf}
+}
+%\figurenum{1}
+%\caption{Continued.}
+\end{figure}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID50_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID543_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID597_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID607_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID70_SB_profile.pdf}
+}
+%\figurenum{1}
+%\caption{Continued.}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2138_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2202_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2396_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_LID1273_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_LID1538_SB_profile.pdf}
+}
+%\figurenum{1}
+%\caption{Continued.}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_LID360_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-1_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-229_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-321_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-724_SB_profile.pdf}
+}
+%\figurenum{1}
+%\caption{Continued.}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_ECDFS-358_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X1136_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X50_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X717_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X735_SB_profile.pdf}
+}
+%\figurenum{1}
+%\caption{Continued.}
+\end{figure*}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X763_SB_profile.pdf}
+\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X969_SB_profile.pdf}
+}
+%\figurenum{1}
+%\caption{Continued.}
+\end{figure*}
 

### 2019-04-24 manuscript_II/NA_temp/qso_paperII.tex
update manuscript

\documentclass{natureprintstyle}
%\documentclass{nature}
\bibliographystyle{naturemag}
\usepackage{epsfig,caption}
\usepackage{color}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{amssymb}
\usepackage{rotating}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{float}

%\usepackage[switch]{lineno}
%\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% comment for selecting the best figures to go on web for:
%@arxiver{jvds_sami_vsigma_ellip_LOESS_Age_paper.pdf,jvds_sami_vsigma_ellip_LOESS_Age_transform_paper_resubmit.pdf} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%journal commands
\newcommand{\apj}{Astrophys. J.}
\newcommand{\spie}{Proc. SPIE}
\newcommand{\pasp}{Publ. Astron. Soc. Pac.}
\newcommand{\apjs}{Astrophys. J. Supp.}
\newcommand{\araa}{Annu. Rev. Astron. Astrophys.}
\newcommand{\mnras}{Mon. Not. R. Astron. Soc.}
\newcommand{\apjl}{Astrophys. J. Let.}
\newcommand{\aap}{Astron. Astrophys.}
\newcommand{\aj}{Astron. J.}
\newcommand{\nat}{Nature}
\newcommand{\na}{New Astron. Rev.}
\newcommand{\aaps}{A\&AS}
\newcommand{\procspie}{Proc. SPIE}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% my commands

\newcommand{\lcdm}{$\Lambda$CDM}
\newcommand{\hst}{{\it HST}}
\newcommand{\efr}{$R_{\mathrm{eff}}$}
\newcommand{\galfit}{{\sc Galfit}}
\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\lhost}{$L_{\rm host}$}
\newcommand{\jcap}{Journal of Cosmology and Astroparticle Physics}
\newcommand{\halpha}{${\it H}\alpha$}
\newcommand{\hbeta}{${\it H}\beta$}
\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{{\sc Lenstronomy}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
%\newcommand{\kms}{km~s$^{\rm -1}$}
\newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
\newcommand{\sigstar}{{$\sigma_*$}}
\newcommand{\mstar}{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{
%From predictions to observation: scaling relations between supermassive black holes and their host galaxies at $1< z<2$
A successful observational test of black hole and galaxy co-evolution models since $z\sim1.7$
%The first comparison between the observation and simulation of the scaling relations between supermassive black holes and their host galaxies at $1.2< z<1.7$
}
\author{Xuheng Ding$^{1}$, 
Tommaso Treu$^{1,2}$, 
John Silverman$^{1}$,
et. al
}

\begin{document}

\maketitle

\let\thefootnote\relax\footnote{
\begin{affiliations}
\item {Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA} 
\item {School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\item {Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
\end{affiliations}
}

\begin{abstract}
Supermassive black holes (BH) harbor at the center of galaxies with their masses correlated to the properties of the host galaxies known as scaling relations (\mbh-\lhost and \mbh-\mstar). Observational evidence indicates the correlation is evolving with cosmic time, suggesting a scenario that the BH growth predates their host. In theory, current simulations have reproduced the relations match very close to the observational sample at low redshift ($z<1$) and local. Moreover, the positive evolution of the scaling relation is predicted by different simulating projects independently. It is important to make an unbiased comparison between the observations and the simulations at higher redshift ($z>1$), where the scaling relation is predicted to have the stronger evolution. To this end, here we use a large sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ and compare to the predicted sample from two state-of-the-art simulating projects, MassiveBlack-II (MBII) and semi-analytic models (SAMs). We use HST to measure the luminosity of the 32 AGNs in multi-bands, hence derive the trustworthy stellar mass measurements. The \mbh\ of our sample are estimated by the published near-infrared spectroscopic observations of the broad \halpha\ and \hbeta\ emission lines. We compare the scaling relations to the simulating ones based on the same selecting function. We find that our measurements of \mbh-\lhost\ and \mbh-\mstar\ closely match to the simulations. This consistency confirms the successful progress made by the simulations, which in turn would help to understand questions such as the origin of the scaling relation, the role of AGN feedback play, and the stellar components of galaxies which directly correlate to the BH growth.
\end{abstract}

\section{Introduction}
The discovery of the correlations between the masses (\mbh) of supermassive black holes (BHs) and the properties of their host galaxies, like stellar mass (\mstar) and luminosity (\lhost), indicates that the growth of BH is linked to its host galaxy formation. The best way to understand the physical mechanism of this connection is to rely on active galactic nuclei (AGN) and trace the scaling relations to higher redshifts, witnessing how and when does it happen.

More recently, there is increasing observational evidence indicating the positive offset exist in the correlation at intermediate redshift range ($0.3<z<1$), implying that galaxies built up around the massive potential wells of mature BHs. Stimulated by the observations, theoretical efforts have been made to include the growth of \mbh\ in the framework of cosmological galaxy formation simulations, and generated the predictions of local scaling relations which match the observations well. Moreover, the simulations predict that the positive offset could be even stronger at redshift range $1<z<2$.

A direct comparison between the observation and the simulation at high redshift range is beneficial in particular. First, it helps to directly verify the validity of the initial assumptions adopted in the simulation process, and point out the direction to improve in the simulations if needed. Second, in turn, the tested simulations could help to investigate the mechanism of the origin of the scaling relation. For example, the feedback originating in the surroundings of BHs, the major merging activities, and the growth of the \mbh\ and the stellar components as connected to the common gas supply have been invoked as the process leading to the co-evolution. Moreover, since the same selection functions are adopted when comparing the observational measurements to the predictions, the systematic bias lead by the selection effects could thus be avoided.

We study the scaling relations using 32 AGN systems from four X-ray coverage fields, including COSMOS (Civano et al. 2016), (E)- CDFS-S (Lehmer et al. 2005; Xue et al. 2011), and SXDS (Ueda et al. 2008) at redshift range $1.2<z<1.7$. We adopt the HST/WFC3 to obtain imaging data and preform the 2-D flux profile decomposition to infer the host galaxy flux value. The X-ray selected sample have low nuclear-to-host ratios, which facilitates the extraction of their host properties. 21/23 systems have HST/ACS observation, which provides the colors. Also, we combining the inference with the ground-based photometry to carry out their SED fitting, and thus derive the reliable host rest-frame R band luminosity and stellar mass. The \mbh\ of our sample are estimated using the published near-infrared spectroscopic observations of the broad \halpha\ and \hbeta\ emission lines.

We compare the obtained scaling relations to two state-of-art simulating projects, MassiveBlack-II (MBII) and semi-analytic models (SAMs). They are based on two independent simulating strategies, i.e. N-body simulation for MBII and semi-analytic model SAMs. The MassiveBlack-II (MBII) simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion and associated feedback. The large simulation volume enable the simulating objects evolve independently; the high enough mass and spatial resolution meets the requirements for the object details.  On the theoretical side, aimed, high-resolution N-body simulations such as MBII can study specific galaxy systems. However, understand the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models. We thus compare to the simulation based on a state-of-the-art semi-analytic models (SAMs) of galaxy formation.

\section{Results}
%Showing the result directly:
We take the same selection function as the observation to select the MBII sample at redshift range  $1.2 < z < 1.7$ to compare. 
In figure \ref{fig:MBII_comp}, we present the comparison between the observation to the simulation of the \mbh-\lhost and \mbh-\mstar. 
Inspiringly, we find that the simulation matched remarkably well to the observing result. This is the first comparison of the scaling relations at such redshift range.

\begin{figure*}%[!b]
\begin{tabular}{c c}
\includegraphics[width=0.5\linewidth]{MBII_ML.pdf} &
\includegraphics[width=0.5\linewidth]{MBII_MM.png} \\
\end{tabular}
\caption{
The selection function of our observation data.
Eddington ratios (LBol/LEdd) and BH masses (bottom panel) of our sample (in color) that fall well-below the knee of the BH mass function at z = 1.5 (top panel; Schulze et al. 2015). Dashed lines (vertical and horizontal) denote our selection window with the slanted line only shown to approximately illustrate the effect of a luminosity limit, inherent in the parent catalogs. For reference, we indicate the high-z luminous SDSS QSO samples (grey squares - Peng et al. 2006; grey circles - Decarli et al. 2010) with all falling above our chosen upper mass limit.
}
\label{fig:MBII_comp}
\end{figure*}

The results are presented in figure \ref{fig:SAM_comp}, demonstrating a consistency between the prediction by the model to the observation.

\begin{figure*}%[!b]
\begin{tabular}{c c}
\includegraphics[width=0.5\linewidth]{SAM_ML.pdf} &
\includegraphics[width=0.5\linewidth]{SAM_MMstar.pdf} \\
\end{tabular}
\caption{
The selection function of our observation data.
Eddington ratios (LBol/LEdd) and BH masses (bottom panel) of our sample (in color) that fall well-below the knee of the BH mass function at z = 1.5 (top panel; Schulze et al. 2015). Dashed lines (vertical and horizontal) denote our selection window with the slanted line only shown to approximately illustrate the effect of a luminosity limit, inherent in the parent catalogs. For reference, we indicate the high-z luminous SDSS QSO samples (grey squares - Peng et al. 2006; grey circles - Decarli et al. 2010) with all falling above our chosen upper mass limit.
}
\label{fig:SAM_comp}
\end{figure*}

%Discuss the result.
More detailed test:
0. Compare the color of the sample?
1. KS test? 
2. More insight from the simulation?
3. Discuss the future (More sample with JWST?)

Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$. Magnitudes are given in the AB system.

The ML relation that we discoverd.

\section{Discussion}

\begin{addendum}
 \item[Acknowledgements] 
X. Ding acknowledges support by China Postdoctoral Science Foundation Funded Project (No. 2017M622501).

%
\item[Correspondence] Correspondence and requests for materials should be addressed to Xuheng Ding ~(email:dxh@astro.ucla.edu).
\item[Author Contributions] xxx measure xxx, xxx extract the simulation from xx.
\end{addendum}

\clearpage
\newpage

\begin{center}
{\bf \Large \uppercase{Methods} }
\end{center}

%\textbf{Observation data.} Our 32 new AGN systems are selected from four X-ray coverage fields including COSMOS (Civano et al. 2016), (E)- CDFS-S (Lehmer et al. 2005; Xue et al. 2011), and SXDS (Ueda et al. 2008) at redshift range $1.2<z<1.7$. The X-ray selected sample have low nuclear-to-host ratios, which facilitates the extraction of the host properties. We adopt the \hst/WFC3 infrared channel to derive the high spatial resolution imaging data, to carry out the decomposition of the AGN-host using two-dimensional flux distribution. The details of the \hst\ observation and the study are presented in the companion paper. Moreover, 21/32 systems have \hst/ACS band, together with some other ground-based observations, which would provide the host information in the other bands. In the next section, we infer the reliable K-correction for the rest-frame R band luminosity and the SED to infer the stellar mass. The \mbh\ of our sample have been estimated by \halpha\ and \hbeta\ in the FMOS survey. Comparing to the \Mgii\ and \Civ, the \mbh\ by broad Balmer lines are more trustworthy. The estimated value of the \mbh\ are listed in the companion paper.
%\textcolor{blue}{Do we need to list the \mbh\ and host properties in a table in this paper?}

\textbf{Host properties inference.} We perform the 2-D AGN-host decomposition to infer the host flux. We briefly describe them here and refer the reader to the analytic paper (e.g. paper-I) for a more detailed description.

Assuming the unresolved AGN as a scaled point source and the host galaxy as a \sersic\ profile, we simultaneously fit the total 2-D flux distribution to infer the host flux ratio for the WFC3-IR data. Given that the host inference by IR band is superior to the one by UV band, we fix the \reff\ and \sersic\ index as the value inferred by WFC3-IR to infer the host ratio at ACS-UV for the 18/32 system.

We combining the HST inference to the ground-based photometry to carry out the SED fitting to infer the stellar template for each system. We adopt the best-fit SED model to derive the rest-frame R band magnitude and the stellar mass of our sample.

\textbf{Simulations and selection function.} To compare with the observation, we adopt the sample from two state-of-the-art simulating projects, i.e., MassiveBlack-II (BHII) and ab-initio semi-analytic models (SAMs).

%Introduce BHII: The high resolution. In paper?, the simulation result shows that the evolution is exists since ... Some other interesting results.
The BHII is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion and associated feedback. The large simulation volume enable the simulating objects evolve independently; the high enough mass and spatial resolution meets the requirements for the object details. A variety of predictions by the simulation have been examined by comparing to the observations, including 
the Galaxy stellar mass function, quasar bolometric luminosity function (Khandai et al. 2015). %More recently, the simulated AGN systems 
%The simulating result:
The GSMF, The AGN bol luminosity; The M-Mstar relations. The AGNs compared to the observation (Aklant two papers).

%Introduce SAMs: Similarly, the simulation of SAMs shows that, the \mbh-host relation have stronger evidence in the bulge than disk...
On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems, but understanding the way of AGN feeding modes requires implementing the physics of nuclear gas inflows into cosmological models of galaxy formation. In turn, this requires an analytical description of such processes to be implemented into existing semi-analytic models.

We adopt a similar selection function to allow a comparing between equivalent samples. We plot the selection function of the observation data the the simulation data, in figure.
\begin{figure}[t]
\centering
\includegraphics[width = 7cm]{MBII_selectfunc.pdf}
\caption{The sample selected from the BHII simulation.
}
\label{fig:bhII_selectfunc}
\end{figure}

\textbf{Code availability.} The data reduction package used to process the SAMI data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr. To derive the stellar kinematic parameters and the lick absorption line strengths, we use the publicly available penalised pixel-fitting (pPXF) code from M. Capppellari: {http://www-astro.physics.ox.ac.uk/~mxc/software/\#ppxf}. For the adaptive LOESS smoothing, we use the code from M. Cappellari obtained from: http://www-astro.physics.ox.ac.uk/~mxc/software/\#loess

\textbf{Data availability.} All reduced data-cubes in the GAMA fields used in this Letter are available on: http://datacentral.aao.gov.au/asvo/surveys/sami/, as part of the first SAMI Galaxy Survey data release \cite{Ding2017a}. Stellar kinematic data products will become available in the second SAMI Galaxy Survey data release.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{References}
\bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\newpage

\onecolumn

\begin{center}
{\bf \Large \uppercase{Supplementary information} }
\end{center}

\setcounter{figure}{0}
\vspace{2cm}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.8\linewidth]{hst_sample_bhmf.pdf}
\caption{
The selection function of our observation data.
Eddington ratios (LBol/LEdd) and BH masses (bottom panel) of our sample (in color) that fall well-below the knee of the BH mass function at z = 1.5 (top panel; Schulze et al. 2015). Dashed lines (vertical and horizontal) denote our selection window with the slanted line only shown to approximately illustrate the effect of a luminosity limit, inherent in the parent catalogs. For reference, we indicate the high-z luminous SDSS QSO samples (grey squares - Peng et al. 2006; grey circles - Decarli et al. 2010) with all falling above our chosen upper mass limit.
}
\label{fig:support}
\end{center}
\end{figure}

\end{document}

### 2019-05-08 manuscript/manuscript.tex
Update the manuscripts to share with John (before higer level comments)

@@
 \documentclass[apj]{emulateapj}
+
 \usepackage{times}
-%\newcommand{\mdot}{M$_{\odot}$\,}
 \usepackage{natbib}
-
 \usepackage[backref,breaklinks,colorlinks,citecolor=cyan]{hyperref} 
-%\setlength{\parindent}{0pt}
 \usepackage{booktabs}
@@
 \usepackage{float}
+\usepackage[caption=false]{subfig}
 
@@
 \begin{document}
-
 \def\lcdm{$\Lambda$CDM}
@@
 \newcommand{\Civ}{C$_{\rm IV}$}
+\newcommand{\sint}{$\sigma_{\rm int}$}
+\makeatletter
+\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}  %For share same footnote
+\makeatother
 
@@
 
-\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{1},  Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
+\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{1}, Daeseong Park, Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
  }
@@
 
-The tight correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties suggests an evolutionary connection.
+The tight correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties (e.g.
+stellar mass \smass, luminosity \lhost) suggests an evolutionary connection.
 A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time.
@@
 The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts.
-We compare the \mbh-\lhost~and \mbh-\smass~relations to those of local active galaxies, accounting for selection effects, to infer their evolution.
-The \mbh-\lhost relation is inconsistent with the local one, accounting for passive evolution, indicating that at fixed mass BHs 8-10Gyrs ago reside in less luminous galaxies than today.
-Furthermore, the \mbh-\smass\ of our high redshift sample is consistent with the local \mbh-\smass$_{\rm bluge}$ relations.
-Considering that our sample are composed of bulge and disk components, the evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.
+\textcolor{blue}{We enlarge the sample of the \mbh-\smass~and \mbh-\lhost~relations using previously published measurements and compare to the local to infer their evolution.
+We find the \mbh-\smass\ relation by our distant sample is inconsistent with the local \mbh-\smass$_{\rm, bluge}$ relation.
+We take selection effect into account to fit this offset as \mbh/\smass$\propto(1+z)^\gamma$, and obtain $\gamma = 0.80\pm0.30$.
+Considering that there is evidence showing our sample are composed of bulge and disk components, our result indicates BHs 8-10 Gyrs ago reside in bulges, if not entire galaxies, which contain lower \smass\ than today.
+Accounting for passive evolution, we find the \mbh-\lhost\ relation is also inconsistent with the local in a similar way.
+The evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.}
+
 \end{abstract}
@@
 
-Most galactic nuclei are thought to harbor a supermassive black hole (BH), whose mass (\mbh) is known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion(\sigstar).
-These tight correlations indicate a connection between nuclear activity and galaxy formation and evolution \citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
-Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere and their host galaxy.
-On the one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver \citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
+Most galactic nuclei are thought to harbor a supermassive black hole (BH), whose mass (\mbh) is known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion (\sigstar).
+These tight correlations indicate a connection between nuclear activity and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
+Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere ($\sim$pc) and their host galaxy ($\sim10$ kpc).
+On the one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
 On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.
 
-A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time \citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}.
+A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}.
 During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs.
@@
 
-In order to make progress it is important to reduced as much as possible the uncertainties and take great care of selection effects and systematic errors.
-First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called "virial" method.
-In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non gravitational component of the BLR gas dynamics, when compared to local samples with masses based on broad Balmer lines \citep[i.e.
+In order to make progress, it is important to reduce as much as possible the uncertainties and take great care of selection effects and systematic errors.
+First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method.
+In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-gravitational component of the BLR gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e.
 \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}.
 Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging.
-Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed quasars, since lensing magnifies the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}.
-Last but not least, the selection function needs to be taken into account when intepreting the observations \citep{Treu2007, Lauer2007}.
-For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample.
-It is also important to consider the selection function when comparing the observed scaling relations with simulated ones \citep{DeG++15}.
+Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed quasars, since lensing magnifies the host image to lensed arcs~\citep{Pen++06qsob, Ding2017a, Ding2017b}.
+Last but not least, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}.
+For instance, it has been demonstrated~\citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample.
+It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.
 
-In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest \citep{DeG++15}.
-In practice, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history \citep{Aird2015}.
+In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest~\citep{DeG++15}.
+In practice, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history~\citep{Aird2015}.
 In this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS.
@@
 Second, we estimate \mbh\ using Balmer lines which avoids potential systematic uncertainties in the UV-based estimators.
-Third, our X-ray selected sample have lower nuclear-to-host ratios which facilitate the galaxy mass measurements.
+Third, our X-ray selected sample has lower nuclear-to-host ratios which facilitate the galaxy mass measurements.
 Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e.
 WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference.
-Given the high-quality of our data, we can test whether the growth of BH predates that of the host by a factor of at least $1.7$ $(\sim0.23$ dex) [what does this mean?].
+Given the high-quality and sample size of our data, we can test whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e.
+$\sim0.23$ dex,][]{Schulze2014}.
 
@@
 
-We focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS \citep{Civano2016}, (E)-CDFS-S \citep{Lehmer2005, Xue2011}, and SXDS \citep{Ueda2008} fields.
-We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$.
-The Near IR spectra of AGNs are available from the survey of Subaru's Fiber Multi-Object Spectrograph \citep[FMOS, ][]{Kimura2010, Schulze2018}, covering the wavelength range 0.9-1.8 $\mu m$.
-The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$ \citep{Greene2005, Matsuoka2013, Nobuta2012}.
+We focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
+We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$, \textcolor{blue}{estimated using \halpha\ emission line.} We present the selection window that used to choose the sample in Figure~\ref{fig:selection}.
+We list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}.
 Overall, our final sample is composed of 32 new observations by \hst/WFC3.
-Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.
+
+\begin{figure}
+\centering
+{
+\includegraphics[height=0.4\textwidth]{fig/AGN_selection.pdf}
+}
+\caption{\label{fig:selection} 
+\textcolor{red}{Figure to be updated} We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($L_{\rm Bol}/L_{\rm Edd}$) and \mbh.
+Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}.
+For comparing propose, we plot the high$-z$ luminous SDSS QSO samples from the reference \citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}.
+}
+\end{figure}
 
@@
 COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
-COSMOS-CID255$^a$ & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
+COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
 COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
@@
 Column 6: The observing start date.
-\\
-$^a$For CID255, 3/6 of the dither WFC3 images are corrupted. We analyze this sample by a same approach, taking the 3 avalible frames.
 }
@@
 
-The \mbh\ of type-1 AGNs can be inferred using the so-called virial method \citep{Peterson2004, Shen2013}.
+The \mbh\ of type-1 AGNs can be inferred using the so-called virial method~\citep{Peterson2004, Shen2013}.
 The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas.
@@
 
-For our targets, the \halpha\ and \hbeta\ emission-line properties have been investigated by \citet{Schulze2018} using the multi-object spectrograph Subaru/FMOS.
+The Near IR spectra of our target AGNs are available from the survey of Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010}, covering the wavelength range 0.9-1.8~$\mu m$.
+The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$~\citep{Greene2005, Matsuoka2013, Nobuta2012}.
+Note that \citet{Schulze2018} has investigate the \halpha\ and \hbeta\ emission-line properties using the multi-object spectrograph Subaru/FMOS.
 We referred to that paper for the details of continuum fitting and emission line modeling.
@@
 
-\subsection{Comparison sample}
-\textcolor{blue}{
+\subsection{Comparison sample}\label{sec:compare_sample}
+
 We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
@@
 The work of B11 contains 25 \mbh-\smass\ local active AGNs, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
-To increase the local \smass\ and \mbh\ to the higher range, we also include the inactive galaxies (mainly ellipticals or S0) as done by \citet{H+R04}.
+To increase the local \smass\ and \mbh\ to the higher range, we also include 30 inactive galaxies (mainly ellipticals or S0) as measured by \citet{H+R04}.
 It is worth noting that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample.
 In other words, our local comparison is the \mbh-\smass$_{Bulge}$ and not those involving total quantities.
-}
 
-\textcolor{blue}{
 We include in our analysis published samples at intermediate redshift range to understand the redshift evolution of these correlations.
@@
 The intermediate redshift AGNs that we consider include, for the \mbh-\lhost\ relation, 52 objects published by \citet{Park15} at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11, SS13} at $0.5<z<1.9$.
-Moreover, \citet{SS13} also derive the \smass\ which enable us to compare to the \mbh-\smass\ relation at $0.5<z<1.2$.
-}
+Moreover, \citet{Bennert11, SS13} also derive the \smass\ for the 27 objects which enable us to compare to the \mbh-\smass\ relation.
 
@@
 To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}.
-We find that the \hbeta\ estimator is very consistent ($<0.03$~dex r.m.s.
-or mean?) between the two references.
-Moreover, in \citet{Schulze2018}, the cross-calibration between the \halpha\ and \hbeta\ is consistent.
+We find that the \hbeta\ estimator is very consistent (\mbh\ r.m.s.
+$<0.03$~dex) between the two references.
+Moreover, in \citet{Schulze2018}, the cross-calibration between the \halpha\ and \hbeta\ has better agreement.
 Thus, we adopt the virial formalism from \citet{Schulze2018}:
@@
 \log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.71+0.48 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
-&~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right).
+&~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right) ,
 \end {eqnarray}
@@
 \log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
-&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) , 
+&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) .
 \end {eqnarray}
@@
 Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
-14 of the systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged \mbh\ value.
+14/32 systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged value for log(\mbh).
+\textcolor{blue}{3/32 systems, CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}}.
+
 We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}.
@@
 \tablewidth{0pt}
-\tablecaption{Inferred \mbh\ .} 
+\tablecaption{Inferred BH properties for the 32 systems} 
 \tablehead
@@
 \colhead{}& 
-\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}& Eddington ratio &
-\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}& Eddington ratio \\
+\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
+\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
 \colhead{}& 
@@
 Column 5-7: \hbeta\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
+The typical uncertainty level for FWHM and $\log(\lambda \rm L)$ are $15\%$ and $\pm0.01$, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
 }
@@
 Table~\ref{tab:objlist} lists the details of the observation.
-The six exposures for each dither image were combined with the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel.
+The six exposures for each dither image were combined with the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted.
+We achieve to analyze this sample with a same approach, taking the 3 available frames.}.
 To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} tool.
@@
 The final image is drizzled to 0\farcs{03} pixel scale.
-Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population to the stellar mass budge \citet{Gallazzi2009} which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR).
+Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population %to the stellar mass budget
+which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR) \citep{Gallazzi2009} .
 
@@
 We assume that the stars in the library are representative of the possible PSFs in our program.
-Therefore, we assume that the PSF library gives a good representation of the dominant source of uncertainty as well as the best fit.
+Therefore, the PSF library gives a good representation of the dominant source of uncertainty as well as the best fit.
 %In the next subsection, we carry out the AGN decomposition using each PSF.
@@
 Furthermore, we fit other galaxies that happen to be close to the AGN as additional \sersic\ model, to account for any potential contamination.
-\textcolor{blue}{The systems CID206 and ECDFS-358 have nearby objects which could not be described by \sersic\ model, we thus mask these objects in the fitting.}
+The systems CID206 and ECDFS-358 have nearby objects which could not be described by \sersic\ model, we thus mask these objects in the fitting.
 
 %Introduce Lenstronomy:
-We adopt the imaging modeling tool \lenstronomy\ \citep{lenstronomy} to perform the decomposition of the host and nuclear light.
+We adopt the imaging modeling tool \lenstronomy~\citep{lenstronomy} to perform the decomposition of the host and nuclear light.
 \lenstronomy\ is a multi-purpose open-source gravitational lens image modeling python package.
 Its flexibility enables us to turn off the lensing channel and focus on the AGN decomposition\footnote{For a sanity check, we compared the performance of \lenstronomy\ to the most commonly used galaxy modeling software {\sc Galfit} and confirm that the consistent result could be obtained with the same fitting ingredients provided.}.
-The maim advantage over {\sc Galfit} is that \lenstronomy returns the full posterior of the parameter and not just the best fit model and the Laplace approximation of the uncertanties.
+The maim advantage over {\sc Galfit} is that \lenstronomy\ returns the full posterior of the parameter and not just the best fit model and the Laplace approximation of the uncertanties.
 The input ingredients to \lenstronomy\ include:
@@
 Usually, a mismatch exists when subtracting the AGN as the scaled PSF, especially at the central parts.
-While modeling multiply imaged AGN, this mismatch can be mitigated with PSF reconstruction by the iterative method \citep{Chen2016, Birrer2018}.
+While modeling multiply imaged AGN, this mismatch can be mitigated with PSF reconstruction by the iterative method~\citep{Chen2016, Birrer2018}.
 However, this approach requires multiple images which are not available in our case.
@@
 However, in our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow.}.
-To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{}]$, and Sersic index $n\in[1,7]$.
+To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{0}]$, and Sersic index $n\in[1,7]$.
 Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs.
-We infer the host property (i.e., host flux, \Reff, Sersic index $n$) using a weighted arithmetic mean.
+We infer the host \sersic\ parameters (i.e., host flux, \Reff, \sersic\ index) using a weighted arithmetic mean.
 The weight is calculated by:
@@
 In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e.
-host) and the residuals.
-As an example, the weights adopted in the analysis of system COSMOS-CID1174 are listed in Table~\ref{tab:weight_CID1174}.
-In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index $n$ and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.
+host) and the residuals, taking COSMOS-CID1174 as an example.
+The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}.
+In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.
 
@@
 \tablewidth{0pt}
-\tablecaption{The host inference of CID1174} 
+\tablecaption{Host inference of CID1174} 
 \tablehead{ 
@@
 The inference of the host properties is weighted by eight top-ranked PSFs.
-For a smaller number of PSFs one tends to underestimate the uncertainties.
-To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the one inferred by five and ten top-ranked PSFs.
-As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference is solid when the amount of selected PSF exceeds five.
+With a smaller amount of PSFs, one would possibly underestimate the uncertainties.
+To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the inference by five and ten top-ranked PSFs.
+As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference has been solid when the amount of selected PSF exceeds five.
 
@@
 18/32 systems in the COSMOS field have ACS/F184W imaging data.
-We infer their host flux ratio using the same approach used for the WFC3-IR data.
-The field of view by ACS are larger than WFC3, and we collected in total 174 ACS PSFs in the library.
+We infer their host flux ratio using the same approach used for the WFC3-IR.
+The field of view by ACS are larger than WFC3, hence we collected in total 174 ACS PSFs in the library.
 In principle, the host inference by IR band is superior to the one by UV band, giving that the effects of dust extinction and contrast between the (blue) AGN and (red) host.
@@
 18/32 systems have multi-band host magnitude which enables us to select the best stellar population that could fit the overall sample.
-We find that the 1~Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples.
+We find that the 1~Gyrs stellar population with solar metallicity by Chabrier initial mass function (IMF)~\citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples.
+
 Adopting the color information, we perform the K-correction and derive the rest-frame R band magnitude of our sample.
 Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty introduced by this K-correction is within 0.05~mag.
-We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.
+We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}.
 
@@
 
-The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare their relations to to the \mbh.
+The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare their relations to the \mbh.
 
-\subsection{\mbh-\lhost\ relation}
+\subsection{\mbh-\lhost\ relation}\label{sec:ml}
 We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}, panel (a). Following common practice, we fit the local relation as a linear relation,
@@
 where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{L_{R,0}}{10^{10}L_{\odot}})$.
-The best-fit and  1-$\sigma$ inference are $\gamma = 0.69 \pm 0.15$, as shown in Figure~\ref{fig:ML-vz}
+The best-fit and  1-$\sigma$ inference are $\gamma = 0.70 \pm 0.15$, as shown in Figure~\ref{fig:ML-vz}.
 
@@
 
-\subsection{\mbh-\smass\ relation}
+\subsection{\mbh-\smass\ relation}\label{sec:mm}
 Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution.
 In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample.
-We visually see that the mass distributions for the three samples are very similar.
+We visually see that the relations for the three samples are close from one to another.
 Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$.
-We obtain the $\gamma  = 0.49 \pm 0.19$, i.e.
-tentative evidence for evolution , see Figure~\ref{fig:MM-vz}, panel (a).
-We also show the ratio of \mbh-\smass of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).
+We obtain the $\gamma  = 0.74 \pm 0.17$, i.e.
+tentative evidence for evolution, see Figure~\ref{fig:MM-vz}, panel (a).
+We also show the ratio of \mbh-\smass\ of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).
 We highlight that our results are less biased in both the measurement of \mbh\ and \smass.
@@
 \label{select_eff}
-\textcolor{red}{To be written after Daeseong's analysis.}.
+\textcolor{blue}{
+Our AGN sample is selected based on the AGN luminosity and \halpha\ broad emission line, with lower nuclear-to-host ratios, which would introduce the bias in the inference of the evolution of the scaling relation if not properly taken into consideration~\citep{Tre++07, Bennert++2011, Schulze2014, Park15}, known as Malmquist bias.
+In theory, the simulation~\citep{DeG++15} also find the scaling relations by the selected samples have steeper feature than the random ones, highlighting the necessity of eliminating the selection biases.
+}
+
+\textcolor{blue}{
+We take selection effects into account using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}.
+Following \citet{Park15, Ding2017b}, we generate the simulating samples from a combination of the local active \mbh\ function by \cite{Schulze2010} and the local samples adopted in this work.
+We then added Gaussian random noise to the simulated samples as a function of two free parameters, $\gamma$ and \sint, where \sint\ is the intrinsic scatter when considering the scaling relation as linear.
+According to the observed distribution, we consider the observational selection of \mbh\ of our samples by lower and upper limits of $[7.7, 8.8]$ to model their distribution.
+To evaluate the posterior at the given $\gamma$ and \sint, for each object, we consider the likelihood of observing such object using the simulated sample, and consider whether the object would be selected or not, given the sensitivity.
+In addition, we adopt both uniform (flat) prior and lognormal prior for \sint\ (using the inference from linear fitting).
+}
+
+\textcolor{blue}{
+Combining the 32 AGNs together with the intermediate redshift sample, we present the inferred  $\gamma$ and \sint\ in the two-dimensional planes in Figure~\ref{fig:select_effect}.
+Both the \mbh-\lhost\ and \mbh-\smass\ correlations have been considered.
+With a lognormal prior for \sint, the fitted $\gamma$ are $0.6\pm0.3$ (\mbh-\lhost) and $0.8\pm0.3$ (\mbh-\smass), consistent with the inference by the flat prior.
+These inference are consistent with the previous values (Section~\ref{sec:ml} and Section~\ref{sec:mm}) without considering the selection effect, indicating that the evolution feature of our sample exist globally in the overall samples.
+Furthermore, we find that the final inferred scatter \sint$\sim 0.3-0.5$ are similar to the local scatter, suggesting that the scatter of the scaling relation at high redshift are similar to local ones and indicating that we have not significantly underestimated/overestimated our errors for high redshift samples.
+}
+
+\textcolor{blue}{
+We also study the selection effect by only consider the new 32 AGNs, result in a higher evolution trend with a higher value of $\gamma$.
+We show all the result of the $\gamma$ and \sint\ in the Table~\ref{table:gamma_sf}.
+}
+
+\begin{table}
+\centering
+    \caption{The summary for the different inference of $\gamma$.}\label{table:gamma_sf}
+     \resizebox{8cm}{!}{
+     \begin{tabular}{lccc}
+     \hline
+     Sample & Selection effects& \mbh-\lhost &  \mbh-\smass \\
+     &&&\\
+     \hline\hline
+Entire sample & No & 0.70$\pm$0.15 & 0.74$\pm$0.17 \\
+Entire sample & Yes & 0.60 $\pm$ 0.30 & 0.80 $\pm$ 0.30 \\
+Only 32 AGNs & No & 1.13$\pm$0.20 & 0.80$\pm$0.20\\
+Only 32 AGNs& Yes & 1.70$\pm$0.40 & 1.30$\pm$0.50\\
+     \hline
+     \end{tabular}}
+    \tablecomments{
+    Entire sample includes the 32 AGNs and the intermediate redshift AGNs from the reference in Section~\ref{sec:compare_sample}.
+The results of selection effects used the lognormal prior of \sint.
+}
+\end{table}
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+\subfloat[\mbh-\lhost, flat prior]
+{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
+\subfloat[\mbh-\lhost, lognormal prior]
+{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
+\subfloat[\mbh-\smass, flat prior]
+{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_flatprior.pdf}}&
+\subfloat[\mbh-\smass, lognormal prior]
+{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_lognormprior.pdf}}\\
+\end{tabular}
+\caption{\label{fig:select_effect} 
+Constraining the evolution factor $\gamma$ using Equation~\ref{eq:offset}, with intrinsic scatter \sint, using Monte Carlo simulation, by taking selection effects into account.
+The adopted sample includes 32 AGNs and the intermediate redshift AGNs.
+Upper panels: the $\gamma$ for the \mbh-\lhost\ relation, using flat prior of \sint panel-(a) and lognormal prior panel-(b).
+Bottom panel presents the result for \mbh-\smass\ relation.
+}
+\end{figure*}
 
@@
 
-In our analysis, we adopt one stellar population to the overall sample.
-We note that adopting the private stellar populations for these samples which have both multi-band host magnitude could be more robust in principle.
+\textcolor{blue}{
+In this work, we use the start-of-the-art techniques to derive the host flux from the AGN image.
+The fidelity of the inferred apparent magnitudes of the host galaxies are high.
+Nevertheless, we adopt one stellar population to the overall sample to derive the rest-frame R band luminosity and stellar mass.
+We note that adopting the private stellar populations for each samples which havs both multi-band host magnitude could be more robust in principle.
 However, considering that the host magnitude in ACS band is faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost.
 Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry.
-\textcolor{red}{Describe the ground-based data}.
-In this paper, we focus on the decomposing of the AGN and carry out a rapid analysis of the \mbh-host relations.
-The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.
+We highlight that, in this particular paper, we focus most on the decomposing of the AGN image to present our inference of the host.
+In the mean time, we carry out a rapid analysis of the \mbh\ and host properties relations.
+The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.}
+
+\textcolor{blue}{
+At last, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates.
+That is to say, the intrinsic scatter is not necessarily worse at high-$z$ than the low-$z$.}
 
@@
 We compared the morphology of AGNs host galaxies to the inactive galaxies in CANDLES imaging survey.
-We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.
+We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey~\citep{Momcheva2016, Brammer2012}.
 
@@
 \caption{\label{fig:Mstar-rn} 
-The comparison of the galaxy properties between our 32 AGNs' hosts to the 4401 CANDLES inactive sample (circles).
+The comparison of the galaxy properties between our 32 AGNs' hosts to the CANDLES sample including 4401 inactive galaxies (circles).
 The color coding is based on the filter flux ratio between WFC3 and ACS.
@@
 We perform the Kolmogorov-Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.
-We thus conclude that the host galaxies of our AGN are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.
+We thus conclude that the host galaxies of our AGN sample are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.
 
-\begin{figure*}
+\begin{figure}
 \centering
-{\includegraphics[ height=0.35\textwidth]{fig/Hist_Reff.pdf}}\\
-{\includegraphics[ height=0.35\textwidth]{fig/Hist_Sn.pdf}}
+{\includegraphics[ height=0.3\textwidth]{fig/Hist_Reff.pdf}}\\
+{\includegraphics[ height=0.3\textwidth]{fig/Hist_Sn.pdf}}
 \caption{\label{fig:hist_rn} 
 The comparison of the histogram of the \Reff\ and \sersic\ n, with median value indicated.}
-\end{figure*}
+\end{figure}
 
-%high
 %The distribution shows that our AGN host are located at a higher end of the stellar mass at region where
@@
 \subsection{JWST}
+\textcolor{red}{Xuheng: some comments on JWST have been made at the end of the Summary. Do we need to put more discussion here?}
 
-\section{Summary}
-\label{sec:sum}
-%We presented the study of the \mbh\ and host property's evolution to high redshift until 1.7.
+\section{Summary} \label{sec:sum}
+We studied the evolution of the correlations between the supermassive black hole and their host galaxies using new measurements of 32 X-ray selected AGNs at $1.2<z<1.7$.
+
+We used the published near-infrared spectroscopic observations \halpha\ and \hbeta\ emission lines to estimate the reliable values of BH mass.
+To obtain the properties of the AGN host galaxies, we performed the AGN image decomposition using the state-of-the-art techniques.
+We adopted the \hst/WFC3 infrared channel to observe the high-resolution AGN imaging data and collected the PSF-stars in across all the fields to build to a library of PSF for the fitting.
+Using the latest image modeling tool \lenstronomy, we decomposed the AGN image in 2-D plane taking each PSF in the library.
+We obtained the host \sersic\ property (i.e., host flux, effective radius, \sersic\ index) using a weighted arithmetic mean based on the inference by the eight top-ranked PSFs.
+Incorporating with the inference by \hst/ACS image, we selected the stellar population, hence derived the rest-frame R band Luminosity (\lhost) and stellar mass of the host (\smass).
+
+Combining out high-$z$ measurements with the intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13}, we compared the scaling relations to the ones by the local with main results summarized as follows:
+\begin{enumerate}
+\item The \mbh-\smass\ relations at higher redshift are inconsistent with the local ones, i.e. Figure~\ref{fig:MM}, \ref{fig:MM-vz}.
+\item Considering the correction for passive evolution of galaxy luminosity, the \mbh-\lhost\ relations at higher redshift are inconsistent with the local ones,  i.e.
+Figure~\ref{fig:ML}-(b), \ref{fig:ML-vz}.
+\item The offsets of by the evolution are well described by the form $\Delta\log\mathcal M_{\rm BH}= \gamma \log (1 + z)$.
+Taking intro account selection effect, we obtain $\gamma = 0.8\pm0.3$ (\mbh-\smass) and $\gamma = 0.6\pm0.3$ (\mbh-\lhost).
+\item We compare the properties of our active galaxy sample to the ones from inactive galaxy in the CANDLES imaging survey at the same redshift range, finding no significant discrepancy among them.
+\end{enumerate}
+
+Our inference indicates the evidence of disk component, i.e.
+the ones with \sersic\ $n<2$, and the local comparing samples are bulge dominated sample, we hence conclude that the BHs 8-10~Gyrs ago reside in bulges, if not entire galaxies, which are less massive/luminous than today.
+
+Towards a better estimation of the evolution of the scaling relations, we need to address the limitations of this work.
+First, most of the host-total ration in the \hst/ACS band, the fidelity of the host flux are thus limited at UV.
+We thus adopt a universal stellar template to the overall galaxies based on the general inference between UV band and IR band, rather than carry out the SED fitting for each galaxy, to derive the \lhost\ and \smass.
+Second, at this moment, the local scaling relations that we current have are not yet solid.
+We have found the values of $\gamma$ could vary from 0.8 to 2.0, using different local sample from different literature \citep{Ben++10, Bennert++2011, H+R04, Kormendy13, Bentz2018}.
+Thus, a solid sample served as the local anchor still needed to be well defined (Bennert et al., in prep).
+One the other hand, comparing the observational measurements to the ones by the simulation could avoid not only the dependency to the local anchor, but also the bias by selection effect \citep{DeG++15, Khandai2015, Menci2014}.
+To overcome these limitation, we are currently incorporating our measurement with the ground-based photometry to derive SED fitting, in order to compare with the sample by simulations, which will be presented in our coming up paper.
+
+Looking into the future, the forthcoming lunching of {\it James Webb Space Telescope} ({\it JWST}) would provide the high quality imaging data of AGN at higher redshift (up to $z\sim$7-10) and thus trace the evolution of correlation at more distant universe.
+Furthermore, {\it JWST} is capable of showing the morphology of structures feeding black hole accretion and feedback on the host galaxy~\citep{Ford2014}, thus providing the opportunity to understand the origin of the scaling relations and their evolution.
 
@@
 These observations are associated with programs
-\#15115. Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555
+\#15115. Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555.
 
-The authors fully appreciate the discussions with Vardha N. Bennert, Anton M. Koekemoer, Takahiro Morishita.
+The authors fully appreciate the discussions with Hyewon Suh, Vardha N. Bennert, Anton M. Koekemoer, Takahiro Morishita.
 
@@
 
-This work has made use of lenstronomy \citep{lenstronomy}, Astropy \citep{Astropy}, photutils, TOPCAT \citep{TOPCAT}, Matplotlib \citep{Matplotlib} and standard Python libraries.
+This work has made use of \lenstronomy~\citep{lenstronomy}, {\sc Astropy}~\citep{Astropy}, {\sc photutils}~\citep{photutils}, {\sc TOPCAT}~\citep{TOPCAT}, {\sc Matplotlib}~\citep{Matplotlib}, {\sc adjustText}~\citep{adjustText} and standard Python libraries.
 

### 2019-05-08 manuscript_II/NA_temp/qso_paperII.tex
Update the manuscripts to share with John (before higer level comments)

@@
 \newcommand{\Civ}{C$_{\rm IV}$}
+\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 }
-\author{Xuheng Ding$^{1}$, 
-Tommaso Treu$^{1,2}$, 
-John Silverman$^{1}$,
+\author{Xuheng Ding$^{1,2}$, 
+Tommaso Treu$^{1}$, 
+John Silverman$^{2}$,
+Tiziana Di Matteo$^{3}$,
 et. al
@@
 \item {Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
+\item{McWilliams Center for Cosmology, Dept. of Physics, Carnegie Mellon University, Pittsburgh PA 15213, USA}
 \end{affiliations}
@@
 \begin{abstract}
-Supermassive black holes (BH) harbor at the center of galaxies with their masses correlated to the properties of the host galaxies known as scaling relations (\mbh-\lhost and \mbh-\mstar).
-Observational evidence indicates the correlation is evolving with cosmic time, suggesting a scenario that the BH growth predates their host.
-In theory, current simulations have reproduced the relations match very close to the observational sample at low redshift ($z<1$) and local.
+Supermassive black holes (BH) harbor at the center of galaxies with their masses correlated to the properties of the host galaxies, known as scaling relations (\mbh-\lhost and \mbh-\mstar).
+Observational evidence indicates this correlation is evolving with cosmic time, suggesting a scenario that the BH growth predates their host.
+In theory, current simulations have reproduced the relations match very close to the observational sample at intermediate redshift ($0.3<z<1$) and local.
 Moreover, the positive evolution of the scaling relation is predicted by different simulating projects independently.
-It is important to make an unbiased comparison between the observations and the simulations at higher redshift ($z>1$), where the scaling relation is predicted to have the stronger evolution.
-To this end, here we use a large sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ and compare to the predicted sample from two state-of-the-art simulating projects, MassiveBlack-II (MBII) and semi-analytic models (SAMs).
+It is important to make an unbiased comparison between the observations and the simulations at higher redshift ($z>1$), where the scaling relation is predicted to have a stronger evolution.
+To this end, here we use a large sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim10$ billion years ago) and make the first comparison to the predicted sample from two state-of-the-art simulating projects, MassiveBlack-II (MBII) and semi-analytic models (SAMs).
 We use HST to measure the luminosity of the 32 AGNs in multi-bands, hence derive the trustworthy stellar mass measurements.
 The \mbh\ of our sample are estimated by the published near-infrared spectroscopic observations of the broad \halpha\ and \hbeta\ emission lines.
-We compare the scaling relations to the simulating ones based on the same selecting function.
-We find that our measurements of \mbh-\lhost\ and \mbh-\mstar\ closely match to the simulations.
+We adopt the same selection function to obtain the comparison simulating sample, finding good agreements to the observational relations of \mbh-\lhost\ and \mbh-\mstar by the 32 AGNs.
 This consistency confirms the successful progress made by the simulations, which in turn would help to understand questions such as the origin of the scaling relation, the role of AGN feedback play, and the stellar components of galaxies which directly correlate to the BH growth.
@@
 The best way to understand the physical mechanism of this connection is to rely on active galactic nuclei (AGN) and trace the scaling relations to higher redshifts, witnessing how and when does it happen.
-
 More recently, there is increasing observational evidence indicating the positive offset exist in the correlation at intermediate redshift range ($0.3<z<1$), implying that galaxies built up around the massive potential wells of mature BHs.
@@
 
-A direct comparison between the observation and the simulation at high redshift range is beneficial in particular.
-First, it helps to directly verify the validity of the initial assumptions adopted in the simulation process, and point out the direction to improve in the simulations if needed.
-Second, in turn, the tested simulations could help to investigate the mechanism of the origin of the scaling relation.
+Using the samples predicted by the simulation to compare to the observations is beneficial, in particular at high redshift.
+First, it helps to directly verify the validity of the initial physics prescriptions adopted in the simulation process, and point out the direction where to improve if needed.
+Second, in turn, the lessons learned in the simulations could be used to investigate the mechanism of the origin of the scaling relation.
 For example, the feedback originating in the surroundings of BHs, the major merging activities, and the growth of the \mbh\ and the stellar components as connected to the common gas supply have been invoked as the process leading to the co-evolution.
-Moreover, since the same selection functions are adopted when comparing the observational measurements to the predictions, the systematic bias lead by the selection effects could thus be avoided.
+Extending the comparison to high redshift help to explore the origin of the evolution directly.
+Furthermore, adopting the same selection function enable the particular comparison between two equivalent sample, so as to get rid of the systematic bias lead by the selection effects.
 
-We study the scaling relations using 32 AGN systems from four X-ray coverage fields, including COSMOS (Civano et al.
-2016), (E)- CDFS-S (Lehmer et al.
-2005; Xue et al.
-2011), and SXDS (Ueda et al.
-2008) at redshift range $1.2<z<1.7$.
-We adopt the HST/WFC3 to obtain imaging data and preform the 2-D flux profile decomposition to infer the host galaxy flux value.
-The X-ray selected sample have low nuclear-to-host ratios, which facilitates the extraction of their host properties.
-21/23 systems have HST/ACS observation, which provides the colors.
-Also, we combining the inference with the ground-based photometry to carry out their SED fitting, and thus derive the reliable host rest-frame R band luminosity and stellar mass.
+We study the scaling relations using 32 AGN systems selected from four X-ray coverage fields, including COSMOS \cite{Civano2016}, (E)-CDFS-S \cite{Lehmer2005, Xue2011}, and SXDS \cite{Ueda2008} fields at redshift range $1.2<z<1.7$.
+The redshift range of our targets is chosen to be high enough ($z>1$) to detect the existence of the evolution offsets, while low enough ($z<2$) to limit the effect of surface brightness dimming.
+We employ the HST/WFC3 to obtain high-resolution imaging data and perform the 2-D flux profile decomposition to infer the light of the host galaxy.
+The X-ray selected sample have lower nuclear-to-host ratios at IR band, result in reliable host inference.
+21/23 systems already have HST/ACS imaging data, which enable us to assess the host colors.
+We furthermore combining them with the ground-based photometry to carry out the SED fitting, and thus derive the reliable host rest-frame R band luminosity and stellar mass.
 The \mbh\ of our sample are estimated using the published near-infrared spectroscopic observations of the broad \halpha\ and \hbeta\ emission lines.
+These Balmer virial mass indicators remove the systematic with \Mgii\ or \Civ.
 
-We compare the obtained scaling relations to two state-of-art simulating projects, MassiveBlack-II (MBII) and semi-analytic models (SAMs).
-They are based on two independent simulating strategies, i.e.
-N-body simulation for MBII and semi-analytic model SAMs.
+The high redshift measurements by our sample would place unique constraints on the cosmological simulations.
+To achieve this goal, we compare the observed scaling relations to the results from two state-of-art simulating projects, including MassiveBlack-II (MBII) and semi-analytic models (SAM).
+Note that the two projects are based on two independent simulating strategies, i.e.
+hydrodynamic simulation for MBII and semi-analytic model for SAM.
 The MassiveBlack-II (MBII) simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion and associated feedback.
-The large simulation volume enable the simulating objects evolve independently; the high enough mass and spatial resolution meets the requirements for the object details.
-On the theoretical side, aimed, high-resolution N-body simulations such as MBII can study specific galaxy systems.
-However, understand the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models.
-We thus compare to the simulation based on a state-of-the-art semi-analytic models (SAMs) of galaxy formation.
+The large simulation volume enables the simulating objects evolve independently; the high enough mass and spatial resolution meet the requirements for the object details.
+On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems.
+However, understand the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as (SAM).
+The successful predictions have been made by MBII and SAM in previous works \cite{Menci2014, Menci2016, Khandai2015}. We refer the interested readers to these works for more details.
 
 \section{Results}
-%Showing the result directly:
-We take the same selection function as the observation to select the MBII sample at redshift range  $1.2 < z < 1.7$ to compare. 
-In figure \ref{fig:MBII_comp}, we present the comparison between the observation to the simulation of the \mbh-\lhost and \mbh-\mstar. 
-Inspiringly, we find that the simulation matched remarkably well to the observing result. This is the first comparison of the scaling relations at such redshift range.
+In figure~\ref{fig:MBII_comp}, we present the comparison between the observational measurements to the predictions from MBII, including the scaling relations of \mbh-\lhost and \mbh-\mstar.
+The samples from the simulation are chosen based on a same selection function in figure~\ref{fig:selectfunc}.
+Inspiringly, we find that the simulation matched remarkably well to the observing result.
 
@@
 \caption{
-The selection function of our observation data.
-Eddington ratios (LBol/LEdd) and BH masses (bottom panel) of our sample (in color) that fall well-below the knee of the BH mass function at z = 1.5 (top panel; Schulze et al.
-2015).
-Dashed lines (vertical and horizontal) denote our selection window with the slanted line only shown to approximately illustrate the effect of a luminosity limit, inherent in the parent catalogs.
-For reference, we indicate the high-z luminous SDSS QSO samples (grey squares - Peng et al.
-2006; grey circles - Decarli et al.
-2010) with all falling above our chosen upper mass limit.
+Comparing the scaling relations between the observed samples to the predicted samples by the MBII simulation.
+In the left and right panel, we present the \mbh-\lhost\ and \mbh-\mstar correlation, respectively.
+The blue grids are all galaxies that predicted in the MBII simulation.
+We find that the observations are perfectly overlapped with the simulations.
 }
@@
 
-The results are presented in figure \ref{fig:SAM_comp}, demonstrating a consistency between the prediction by the model to the observation.
+\begin{figure*}[t]
+\begin{tabular}{c c}
+\includegraphics[width=0.5\linewidth]{hst_sample_bhmf.pdf}&
+\includegraphics[width=0.5\linewidth]{MBII_selectfunc.pdf} \\
+\end{tabular}
+\caption{The selection function for the 32 AGN sample (left) and the predicted sample by MBII (right).
+}
+\label{fig:selectfunc}
+\end{figure*}
+
+In addition, we compare the observed measurements to the SAM simulation in figure~\ref{fig:SAM_comp}.
+The results also demonstrate a very consistency between the prediction by the model to the observation.
 
@@
 \caption{
-The selection function of our observation data.
-Eddington ratios (LBol/LEdd) and BH masses (bottom panel) of our sample (in color) that fall well-below the knee of the BH mass function at z = 1.5 (top panel; Schulze et al.
-2015).
-Dashed lines (vertical and horizontal) denote our selection window with the slanted line only shown to approximately illustrate the effect of a luminosity limit, inherent in the parent catalogs.
-For reference, we indicate the high-z luminous SDSS QSO samples (grey squares - Peng et al.
-2006; grey circles - Decarli et al.
-2010) with all falling above our chosen upper mass limit.
+Comparing the observation to the SAM simulation.
 }
@@
 
-%Discuss the result.
-More detailed test:
-0. Compare the color of the sample?
-1. KS test? 
-2. More insight from the simulation?
-3. Discuss the future (More sample with JWST?)
+\textcolor{blue}{The details of the results could be presented.\\
+0. Compare the color of the sample?\\
+1. 2D KS test? \\
+2. More insightful inference from the comparing?
+}
 
-Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$. Magnitudes are given in the AB system.
+%Discuss the result, What does this mean?
+The excellent match between the prediction of simulation and the observations highlights that the evolving scenario of the scaling relation is likely exist.
+In the distant Universe, the BHs at higher redshift typically reside in lower stellar mass galaxies than today.
+During this co-evolution process, in order to catch up on the local final relation, the stellar mass of the host galaxy would have to grow faster than its center BH.
 
-The ML relation that we discoverd.
+ \textcolor{blue}{If the final results show such feature:}
+The result also shows that the \mbh-\mstar\ relation has less scatter than the \mbh-\lhost\ relation, suggesting that the BH relation with \mstar\ are more fundamental than \lhost.
+
+This successful experience leads one conjecture that the other prediction by the simulations could likely to be right.
+For example, regarding the stellar components of galaxy which is the origin that related to the growth of BH, it is likely that the bulge masses are tightly related.
 
 \section{Discussion}
+Some discussions should be placed in this section.
 
-\begin{addendum}
- \item[Acknowledgements] 
-X. Ding acknowledges support by China Postdoctoral Science Foundation Funded Project (No. 2017M622501).
+On the observation side:\\
+0. The inferred host flux ratio by SED decomposition is consistent to the 2-D image decomposition, indicating the fidelity of these approaches?\\
+1. HST seems to reach its higher limit. In the future, the JWST is very promising to realize the evolution scenario at even higher redshift.\\
 
-%
-\item[Correspondence] Correspondence and requests for materials should be addressed to Xuheng Ding ~(email:dxh@astro.ucla.edu).
-\item[Author Contributions] xxx measure xxx, xxx extract the simulation from xx.
-\end{addendum}
+On the simulation side:
+\\0. Introduce some the other 
+\\1. How do we discuss the role of AGN feedback?.
 
@@
 
-\textbf{Host properties inference.} We perform the 2-D AGN-host decomposition to infer the host flux.
+\textbf{Inference of host galaxy light by HST/WFC3} We perform the 2-D AGN decomposition to infer the light of the host galaxy.
 We briefly describe them here and refer the reader to the analytic paper (e.g.
-paper-I) for a more detailed description.
+paper-I) for a more detailed description.%1.
+Observation.
+2.
+Fitting ingredients.
+3.
+Modelling approach.
 
-Assuming the unresolved AGN as a scaled point source and the host galaxy as a \sersic\ profile, we simultaneously fit the total 2-D flux distribution to infer the host flux ratio for the WFC3-IR data.
-Given that the host inference by IR band is superior to the one by UV band, we fix the \reff\ and \sersic\ index as the value inferred by WFC3-IR to infer the host ratio at ACS-UV for the 18/32 system.
+We adopted \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets, to observe the imaging data for the 32 AGN systems.
+We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to drizzle the final image with pixel scale as 0\farcs0642.
+We manually select the isolated-unsaturated PSF-stars from the 32 observed field, and assemble the PSF-library for the fitting.
+To decompose each AGN image, we assume the unresolved active nuclei as the scaled point source and the host galaxy as the \sersic\ profile.
+We adopt imaging modeling tool \lenstronomy\cite{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one by one from the library.
+Based on the reduced $\chi^2$, we are capable of evaluating the perform of each PSF.
+We adopt the result from the top-8 PSFs and infer the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.
 
-We combining the HST inference to the ground-based photometry to carry out the SED fitting to infer the stellar template for each system.
-We adopt the best-fit SED model to derive the rest-frame R band magnitude and the stellar mass of our sample.
+\textbf{SED fitting and host properties}
+We perform the SED fitting to derive the robust physical properties of the host galaxy, including the rest-frame R band luminosity and stellar mass.
 
-\textbf{Simulations and selection function.} To compare with the observation, we adopt the sample from two state-of-the-art simulating projects, i.e., MassiveBlack-II (BHII) and ab-initio semi-analytic models (SAMs).
+21/32 AGN systems have rest-frame UV imaging data by \hst-ACS/F814W\cite{Scoville2007}.
+We perform the same approach to decompose the photometry of the host light at UV.
+Since the host inference by IR band is superior to the one by UV band, while fitting UV image, we fix the \reff\ and \sersic\ index as the value inferred by \hst/WFC3 to derive the host flux.
 
-%Introduce BHII: The high resolution. In paper?, the simulation result shows that the evolution is exists since ... Some other interesting results.
-The BHII is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion and associated feedback.
-The large simulation volume enable the simulating objects evolve independently; the high enough mass and spatial resolution meets the requirements for the object details.
-A variety of predictions by the simulation have been examined by comparing to the observations, including
-the Galaxy stellar mass function, quasar bolometric luminosity function (Khandai et al. 2015). %More recently, the simulated AGN systems 
-%The simulating result:
-The GSMF, The AGN bol luminosity; The M-Mstar relations. The AGNs compared to the observation (Aklant two papers).
+We furthermore combine the \hst\ inference to the ground-based AGN photometry to carry out the SED fitting. \textcolor{blue}{Details and the figures need to be presented.}
 
-%Introduce SAMs: Similarly, the simulation of SAMs shows that, the \mbh-host relation have stronger evidence in the bulge than disk...
-On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems, but understanding the way of AGN feeding modes requires implementing the physics of nuclear gas inflows into cosmological models of galaxy formation.
-In turn, this requires an analytical description of such processes to be implemented into existing semi-analytic models.
+Adopting the best fit SED stellar template to the \hst/WFC3 flux, we derive the \lhost${,_R}$ and \mstar.
 
-We adopt a similar selection function to allow a comparing between equivalent samples. We plot the selection function of the observation data the the simulation data, in figure.
-\begin{figure}[t]
-\centering
-\includegraphics[width = 7cm]{MBII_selectfunc.pdf}
-\caption{The sample selected from the BHII simulation.
-}
-\label{fig:bhII_selectfunc}
-\end{figure}
-
-\textbf{Code availability.} The data reduction package used to process the SAMI data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr.
-To derive the stellar kinematic parameters and the lick absorption line strengths, we use the publicly available penalised pixel-fitting (pPXF) code from M.
-Capppellari: {http://www-astro.physics.ox.ac.uk/~mxc/software/\#ppxf}.
-For the adaptive LOESS smoothing, we use the code from M.
-Cappellari obtained from: http://www-astro.physics.ox.ac.uk/~mxc/software/\#loess
-
-\textbf{Data availability.} All reduced data-cubes in the GAMA fields used in this Letter are available on: http://datacentral.aao.gov.au/asvo/surveys/sami/, as part of the first SAMI Galaxy Survey data release \cite{Ding2017a}.
-Stellar kinematic data products will become available in the second SAMI Galaxy Survey data release.
+\textbf{Simulations and selection function.} 
+Describe the approaches used in the simulation.
 
@@
 
+\begin{addendum}
+ \item[Acknowledgements] 
+%X. Ding acknowledges support by China Postdoctoral Science Foundation Funded Project (No. 2017M622501).
+
+%
+\item[Correspondence] %Correspondence and requests for materials should be addressed to Xuheng Ding ~(email:dxh@astro.ucla.edu).
+\item[Author Contributions] xxx measure xxx, xxx extract the simulation from xx.
+\end{addendum}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Additional information}
+\textbf{Code availability.} The \lenstronomy, which is used to decompose the AGN image  
+%The data reduction package used to process the SAMI data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr.
+To derive the stellar kinematic parameters and the lick absorption line strengths, we use the publicly available penalised pixel-fitting (pPXF) code from M.
+Capppellari: {http://www-astro.physics.ox.ac.uk/~mxc/software/\#ppxf}.
+For the adaptive LOESS smoothing, we use the code from M.
+Cappellari obtained from: http://www-astro.physics.ox.ac.uk/~mxc/software/\#loess
+
+\textbf{Data availability.} All the inference of the AGN properties are presented in the companion paper.
+%All reduced data-cubes in the GAMA fields used in this Letter are available on: http://datacentral.aao.gov.au/asvo/surveys/sami/, as part of the first SAMI Galaxy Survey data release.
+Stellar kinematic data products will become available in the second SAMI Galaxy Survey data release.
 
@@
 
-\clearpage
-\newpage
-
-\onecolumn
-
-\begin{center}
-{\bf \Large \uppercase{Supplementary information} }
-\end{center}
-
-\setcounter{figure}{0}
-\vspace{2cm}
-
-\begin{figure}[!h]
-\begin{center}
-\includegraphics[width=0.8\linewidth]{hst_sample_bhmf.pdf}
-\caption{
-The selection function of our observation data.
+%\clearpage
+%\newpage
+%\onecolumn
+%\begin{center}
+%{\bf \Large \uppercase{Supplementary information} }
+%\end{center}
+%
+%\setcounter{figure}{0}
+%\vspace{2cm}
+%
+%\begin{figure}[!h]
+%\begin{center}
+%\includegraphics[width=0.8\linewidth]{hst_sample_bhmf.pdf}
+%\caption{
+%The selection function of our observation data.
 Eddington ratios (LBol/LEdd) and BH masses (bottom panel) of our sample (in color) that fall well-below the knee of the BH mass function at z = 1.5 (top panel; Schulze et al.
@@
 2010) with all falling above our chosen upper mass limit.
-}
-\label{fig:support}
-\end{center}
-\end{figure}
+%}
+%\label{fig:support}
+%\end{center}
+%\end{figure}
 

### 2019-05-08 M_BH_relation/ML_all_vz.py

@@ -44,8 +44,8 @@ pk[:,2]=4.83-pk[:,2]/0.4  # tansfer from L to Magnitude
 pk[:,2]=pk[:,2]-0.46  # transfer from V to R; 0.46 is the mean value of the data from Taka
 pk[:,2]=pk[:,2]+dm*pass_dmag(pk[:,0])  #evolution of stellar population makes the mag fainter.
 pk[:,2]=0.4*(4.61-pk[:,2])
-park=plt.errorbar(np.log10(1+pk[:,0]),pk[:,1]-(m_ml*pk[:,2]+b_ml),yerr=(0.4**2+0.2**2)**0.5,fmt='.',color='darkseagreen')#,markersize=1)
-SS13=plt.errorbar(np.log10(1+pk[63:,0]),pk[63:,1]-(m_ml*pk[63:,2]+b_ml),yerr=(0.4**2+0.2**2)**0.5,fmt='.',color='darkseagreen')#,markersize=1)  #used to be tomato
+park=plt.errorbar(np.log10(1+pk[:,0]),pk[:,1]-(m_ml*pk[:,2]+b_ml),yerr=(0.4**2+0.2**2)**0.5,fmt='^',color='darkseagreen',markersize=9)
+SS13=plt.errorbar(np.log10(1+pk[63:,0]),pk[63:,1]-(m_ml*pk[63:,2]+b_ml),yerr=(0.4**2+0.2**2)**0.5,fmt='^',color='darkseagreen',markersize=9)  #used to be tomato
 
 ##==============================================================================
 ## input Peng's data
@@ -109,7 +109,7 @@ SS13=plt.errorbar(np.log10(1+pk[63:,0]),pk[63:,1]-(m_ml*pk[63:,2]+b_ml),yerr=(0.
 #==============================================================================
 # My new inference
 #==============================================================================
-from load_result import load_host_p, load_MBH, load_mag
+from load_result import load_host_p, load_MBH, load_mag,load_err
 from load_result import load_zs, load_n
 
 ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'CDFS-321', 'CID1174',\
[…]

### 2019-05-08 M_BH_relation/local_ML_vz.py

@@ -53,7 +53,7 @@ result = op.minimize(nll, [1.036, -1.947, 0.3], args=(x, y, yerr))
 m_ml, b_ml,sint_ml= result["x"]
 #print m_ml, b_ml, sint_ml, "ka=",lnlike(theta=[m_ml, b_ml, sint_ml],x=loc[:,0], y=loc[:,1], yerr=loc[:,2])
 
-#m_ml, b_ml = 1.11, -3.7  # Park's first use
+#m_ml, b_ml = 1.11, 7.40-1.11*10  # Park's first use
 
 xp = np.array([5, 13])
 #plt.plot(xp, m_ml*xp+b_ml, 'r-')

### 2019-05-08 M_BH_relation/local_MM_vz.py

@@ -84,6 +84,7 @@ m_ml, b_ml,sint_ml= result["x"]
 #print m_ml, b_ml, sint_ml, "ka=",lnlike(theta=[m_ml, b_ml, sint_ml],x=loc[:,0], y=loc[:,1], yerr=loc[:,2])
 
 #m_ml, b_ml = 1.12, -4.12  # Park's first use
+m_ml, b_ml = 1.02, -2.91  # Park's inference from the two sample
 
 xp = np.array([5, 13])
 #plt.plot(xp, m_ml*xp+b_ml, 'r-')

### 2019-05-08 material/creat_table_for_manscript.py

@@ -265,19 +265,19 @@ for i in range(len(tab_list)):
 #    "{0}".format(round(Mstar[i],2)),  "+{0}-{1}".format(round(roots(IR_result[i][6][0]/2.5,0.1),2), round(roots(IR_result[i][6][1]/2.5,0.1),2)))
 
 ##%%
-#print "uncertainty for the LR:"
-#for i in range(len(tab_list)):
-#    if IR_result[i]=='xxx':
-#        IR_result[i] = [np.asarray(IR_result[0][j])*0-99 for j in range(len(IR_result[0]))]
-#    print(tab_list[i], 
-#    "+{0}-{1}".format(round(roots(IR_result[i][6][0],0.05)/2.5,2), round(roots(IR_result[i][6][1],0.05)/2.5,2)))
-#
-#print "uncertainty for the M*:"
-#for i in range(len(tab_list)):
-#    if IR_result[i]=='xxx':
-#        IR_result[i] = [np.asarray(IR_result[0][j])*0-99 for j in range(len(IR_result[0]))]
-#    print(tab_list[i],
-#    "+{0}-{1}".format(round(roots(IR_result[i][6][0]/2.5,0.1),2), round(roots(IR_result[i][6][1]/2.5,0.1),2)))
+print "uncertainty for the LR:"
+for i in range(len(tab_list)):
+    if IR_result[i]=='xxx':
+        IR_result[i] = [np.asarray(IR_result[0][j])*0-99 for j in range(len(IR_result[0]))]
+    print(tab_list[i], 
+    "+{0}-{1}".format(round(roots(IR_result[i][6][0],0.05)/2.5,2), round(roots(IR_result[i][6][1],0.05)/2.5,2)))
+
+print "uncertainty for the M*:"
+for i in range(len(tab_list)):
+    if IR_result[i]=='xxx':
+        IR_result[i] = [np.asarray(IR_result[0][j])*0-99 for j in range(len(IR_result[0]))]
+    print(tab_list[i],
+    "+{0}-{1}".format(round(roots(IR_result[i][6][0]/2.5,0.1),2), round(roots(IR_result[i][6][1]/2.5,0.1),2)))
     
 #%% To creat the tab for Aklant
 LR, Mstar, M_R =  load_host_p(tab_list)

### 2019-05-08 py_tools/load_result.py

@@ -303,6 +303,82 @@ def load_MBH(ID, MB_ID, if_reportHb=0,folder = '..'):
     MBs = np.asarray(MBs)    
     return MBs
 
+
+LR_error = {'CID1174': [-0.11, +0.15],
+'CID1281': [-0.11, +0.15],
+'CID206': [-0.23, +0.52],
+'CID216': [-0.03, +0.03],
+'CID237': [-0.09, +0.11],
+'CID255': [-0.11, +0.15],
+'CID3242': [-0.11, +0.14],
+'CID3570': [-0.02, +0.02],
+'CID452': [-0.03, +0.03],
+'CID454': [-0.04, +0.04],
+'CID50': [-0.19, +0.35],
+'CID543': [-0.12, +0.16],
+'CID597': [-0.15, +0.22],
+'CID607': [-0.15, +0.23],
+'CID70': [-0.1, +0.12],
+'LID1273': [-0.07, +0.09],
+'LID1538': [-0.08, +0.09],
+'LID360': [-0.05, +0.06],
+'XID2138': [-0.06, +0.07],
+'XID2202': [-0.1, +0.12],
+'XID2396': [-0.16, +0.26],
+'CDFS-1': [-0.12, +0.16],
+'CDFS-229': [-0.05, +0.06],
+'CDFS-321': [-0.17, +0.28],
+'CDFS-724': [-0.15, +0.23],
+'ECDFS-358': [-0.1, +0.12],
+'SXDS-X1136': [-0.08, +0.09],
+'SXDS-X50': [-0.09, +0.11],
+'SXDS-X717': [-0.06, +0.07],
+'SXDS-X735': [-0.1, +0.13],
+'SXDS-X763': [-0.22, +0.47],
+'SXDS-X969': [-0.14, +0.21]}
+
+Mstar_error = {'CID1174': [-0.15, +0.18],
+'CID1281': [-0.15, +0.18],
+'CID206': [-0.25, +0.53],
+'CID216': [-0.1, +0.1],
+'CID237': [-0.13, +0.14],
+'CID255': [-0.15, +0.18],
+'CID3242': [-0.15, +0.17],
+'CID3570': [-0.1, +0.1],
+'CID452': [-0.1, +0.1],
+'CID454': [-0.1, +0.1],
+'CID50': [-0.21, +0.36],
+'CID543': [-0.15, +0.19],
+'CID597': [-0.18, +0.24],
+'CID607': [-0.18, +0.25],
[…]

### 2019-05-17 manuscript/manuscript.tex
Upate paper darft

@@
 We focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
-We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$, \textcolor{blue}{estimated using \halpha\ emission line.} We present the selection window that used to choose the sample in Figure~\ref{fig:selection}.
+We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$ \textcolor{blue}{(\mbh\ estimated using \halpha\ emission line).} We present the selection window that used to choose the sample in Figure~\ref{fig:selection}.
 We list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}.
@@
 Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC.
-However, in our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow.}.
-To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{0}]$, and Sersic index $n\in[1,7]$.
+In our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow.
+Thus, we only take the best-fit inference using PSO for the further calcualtions.}.
+To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$.
 Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs.
@@
 \subsection{\mbh-\lhost\ relation}\label{sec:ml}
-We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}, panel (a). Following common practice, we fit the local relation as a linear relation,
+We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}. Following common practice, we fit the local relation as a linear relation,
 \begin{eqnarray}
@@
 The figure shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones, indicating that the black hole mass and the host luminosity located at a similar relation at different galaxy age.
+
+\begin{figure}
+\centering
+{\includegraphics[width=0.5\textwidth]{fig/MBH-L_obs.pdf}}
+\caption{\label{fig:ML} 
+Illustration of observed correlations between \mbh-\lhost, with local linear relation indicated. The redshift are color-coded, for distant and intermediate AGNs.
+}
+\end{figure}
+
 However, considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
 Especially, in a passive evolution scenario, we expect \lhost\ to fade over time.
-
-\begin{figure*}
-\centering
-\begin{tabular}{c c}
-{\includegraphics[width=0.5\textwidth]{fig/MBH-L_obs.pdf}}&
-{\includegraphics[width=0.5\textwidth]{fig/MBH-L_ev.pdf}}\\
-\end{tabular}
-\caption{\label{fig:ML} 
-Illustration of observed (left) and evolution-corrected (right) correlations between \mbh-\lhost, with local linear relation indicated.
-The redshift are color-coded, for distant and intermediate AGNs.
-}
-\end{figure*}
-
-We follow \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
+We consider this scenario following \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
 $d{\rm mag}_{\rm R} \sim d\log(1+z)$, i.e.,
@@
 This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$.
-We refer to \citet[][section 5.4]{Ding2017b} for more details.
-Transferring the \lhost\ to today, we show the evolution-corrected \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (b) and find that, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts.
-
+We refer to \citet[][section 5.4]{Ding2017b} for more details and find that, after transferring the \lhost\ to today, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts.
 To quantitatively understand this trend, we fit the offset as a function of redshift in form as:
@@
 where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{L_{R,0}}{10^{10}L_{\odot}})$.
-The best-fit and  1-$\sigma$ inference are $\gamma = 0.70 \pm 0.15$, as shown in Figure~\ref{fig:ML-vz}.
-
-\begin{figure}
-\centering
-{
-\includegraphics[height=0.4\textwidth]{fig/MBH-L-vz.pdf}
-}
-\caption{\label{fig:ML-vz} 
-Illustration of the offset in log\mbh\ (VS. $L_R$) as a function of redshift. The orange band is the intrinsic scatter of local linear relation.}
-\end{figure}
-
-Given that the current result does not take into account selection effects yet, we will draw the conclusion in section~\ref{select_eff}.
+The best-fit and  1-$\sigma$ inference are $\gamma = 0.70 \pm 0.15$.
+
+\textcolor{blue}{Of course, this is a simplified correction, as we only consider the evolution of the host galaxy but not the BH.
+Anyway, we couldn't exactly know how they were evolving to $z=0$.
+Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution.}
+
+%\begin{figure}
+%\centering
+%{
+%\includegraphics[height=0.4\textwidth]{fig/MBH-L-vz.pdf}
+%}
+%\caption{\label{fig:ML-vz} 
+%Illustration of the offset in log\mbh\ (VS. $L_R$) as a function of redshift. The orange band is the intrinsic scatter of local linear relation.}
+%\end{figure}
+
+%Given that the current result does not take into account selection effects yet, we will draw the conclusion in section~\ref{select_eff}.
 
 \subsection{\mbh-\smass\ relation}\label{sec:mm}
-Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution.
-In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample.
-We visually see that the relations for the three samples are close from one to another.
+In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample. We visually see that the relations for the three samples are close from one to another.
+
 Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$.
@@
 {
-\includegraphics[height=0.4\textwidth]{fig/MBH-Mstar.pdf}
+\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar.pdf}
 }
@@
 
+\textcolor{blue}{We also note that in Figure~\ref{fig:MM-vz}, panel (a), most of our new measurement is visually within the scatter of the local sample.
+The inference of the positive $\gamma$ seems to stem from the four outliers AGN systems which happens to have lower host mass relative to the BH mass.
+Thus, we only take the rest of the 28 sample and rerun the statistical analysis, aim to test if offset still exist among them only.
+As a result, we obtain the $\gamma  = 0.54 \pm 0.22$, indicating a slighter but still positive evolution.}
+
+\begin{figure}
+\centering
+{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_subsample.pdf}}
+\caption{\label{fig:MM_restsample} 
+Same as Figure~\ref{fig:MM-vz}, left, but excluding the 4 outliers systems. The result shows the evolution still exist among the other 28 AGN sample.
+}
+\end{figure}
+
 We highlight that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
@@
      \resizebox{8cm}{!}{
-     \begin{tabular}{lccc}
+     \begin{tabular}{cccc}
      \hline
@@
      \hline\hline
-Entire sample & No & 0.70$\pm$0.15 & 0.74$\pm$0.17 \\
-Entire sample & Yes & 0.60 $\pm$ 0.30 & 0.80 $\pm$ 0.30 \\
-Only 32 AGNs & No & 1.13$\pm$0.20 & 0.80$\pm$0.20\\
-Only 32 AGNs& Yes & 1.70$\pm$0.40 & 1.30$\pm$0.50\\
+32 AGNs + intermediate & No & 0.70$\pm$0.15 & 0.74$\pm$0.17 \\
+32 AGNs + intermediate& Yes & 0.60 $\pm$ 0.30 & 0.80 $\pm$ 0.30 \\
+32 AGNs & No & 1.13$\pm$0.20 & 0.80$\pm$0.20\\
+32 AGNs& Yes & 1.70$\pm$0.40 & 1.30$\pm$0.50\\
      \hline
@@
     Entire sample includes the 32 AGNs and the intermediate redshift AGNs from the reference in Section~\ref{sec:compare_sample}.
+Note that the adopted \lhost\ have been transferred to today assuming the passive evolution scenario using Equation~\ref{eq:L_relation}.
 The results of selection effects used the lognormal prior of \sint.

### 2019-05-23 manuscript/manuscript.tex
Update for the paper draft

@@
 The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts.
-\textcolor{blue}{We enlarge the sample of the \mbh-\smass~and \mbh-\lhost~relations using previously published measurements and compare to the local to infer their evolution.
+\textcolor{blue}{We enlarge the sample using previously published measurements and compare to the local to infer their evolution.
 We find the \mbh-\smass\ relation by our distant sample is inconsistent with the local \mbh-\smass$_{\rm, bluge}$ relation.
@@
 Considering that there is evidence showing our sample are composed of bulge and disk components, our result indicates BHs 8-10 Gyrs ago reside in bulges, if not entire galaxies, which contain lower \smass\ than today.
-Accounting for passive evolution, we find the \mbh-\lhost\ relation is also inconsistent with the local in a similar way.
+This indication also exist in the \mbh-\lhost\ relation, once account for the passive evolution of the host luminosity.
 The evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.}
@@
 We focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
-We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$ \textcolor{blue}{(\mbh\ estimated using \halpha\ emission line).} We present the selection window that used to choose the sample in Figure~\ref{fig:selection}.
-We list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}.
+We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$ \textcolor{blue}{(BH mass estimated using \halpha\ emission line).} We present the selection window that used to choose the sample in Figure~\ref{fig:selection} and list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}.
 Overall, our final sample is composed of 32 new observations by \hst/WFC3.
@@
 \caption{\label{fig:selection} 
-\textcolor{red}{Figure to be updated} We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($L_{\rm Bol}/L_{\rm Edd}$) and \mbh.
+\textcolor{red}{Figure needs to be updated.} We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($L_{\rm Bol}/L_{\rm Edd}$) and \mbh.
 Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}.
@@
 We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
-For comparison with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11a) to define our zero-point.
+For comparison with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point.
 The sample by B10 consists of 19 \mbh-\lhost\ measured with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex).
 The work of B11 contains 25 \mbh-\smass\ local active AGNs, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
-To increase the local \smass\ and \mbh\ to the higher range, we also include 30 inactive galaxies (mainly ellipticals or S0) as measured by \citet{H+R04}.
+To increase the local \smass\ and \mbh\ to the higher range, we also include 30 inactive galaxies (mainly ellipticals or S0) as measured by \citet{H+R04} (hereafter HR04).
+
 It is worth noting that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample.
@@
 
-%\textcolor{red}{Need to add the uncertainty level of their inference}.
-
 The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare their relations to the \mbh.
@@
 which enables direct comparison to the distant sample.
-The figure shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones, indicating that the black hole mass and the host luminosity located at a similar relation at different galaxy age.
+The inferred local relations are presented in the Figure~\ref{fig:ML}, showing that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones.
+The observational result shows that the black hole mass and the host luminosity located at a similar relation at different galaxy age.
+
+{\color{blue} 
+Considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
+We will present the discussion of this comparison in Section~\ref{sec:ml-ev}.
 
@@
 \caption{\label{fig:ML} 
-Illustration of observed correlations between \mbh-\lhost, with local linear relation indicated. The redshift are color-coded, for distant and intermediate AGNs.
+Illustration of observed correlations between \mbh-\lhost, with local linear relation indicated. 
+%The redshift are color-coded, for distant and intermediate AGNs.
+The black line and the blue colored equation indicates the best-fit result of local sample as Equation~\ref{eq:MLlocal}, with $1-\sigma$ confidence interval colored as gray region.
 }
@@
 
-However, considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
-Especially, in a passive evolution scenario, we expect \lhost\ to fade over time.
+\subsection{\mbh-\smass\ relation}\label{sec:mm}
+In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample.
+We visually see that the relations for the three samples are close from one to another.
+Similar as Equation~\ref{eq:MLlocal}, we consider the local \mbh-\smass\ relations as linear relation as:
+\begin{eqnarray}
+\label{eq:MMlocal}
+\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}),
+\end {eqnarray}
+
+To understand the evolution for high$-z$ relations, we fit the offset as a function of redshift in form as:
+\begin{eqnarray}
+\label{eq:offset}
+\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
+\end{eqnarray} 
+where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$.
+We obtain $\gamma  = 0.74 \pm 0.21$, i.e.
+tentative evidence for evolution, see Figure~\ref{fig:MM-vz}, panel (a).
+We also show the ratio of \mbh-\smass\ of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).
+
+\begin{figure}
+\centering
+{
+\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar.pdf}
+}
+\caption{\label{fig:MM} 
+Similar to the Figure~\ref{fig:ML}, but the comparison of the \mbh-\smass\ relations.}
+\end{figure}
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
+{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
+\end{tabular}
+\caption{\label{fig:MM-vz} 
+Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. Right: \mbh/\smass\ as a function of redshift.}
+\end{figure*}
+
+We also note that in Figure~\ref{fig:MM-vz}, panel (a), most of our new measurement is visually within the scatter of the local sample.
+The inference of the positive $\gamma$ seems to stem from the four outliers AGN systems which happens to have lower host mass relative to the BH mass.
+Thus, we only take the rest of the 28 sample and rerun the statistical analysis, aim to test if offset still exist among them only.
+As a result, we obtain the $\gamma  = 0.55 \pm 0.29$, indicating a slighter but still positive evolution, i.e.
+Figure~\ref{fig:MM_restsample}.
+
+\begin{figure}
+\centering
+{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_subsample.pdf}}
+\caption{\label{fig:MM_restsample} 
+Same as Figure~\ref{fig:MM-vz}, left, but excluding the 4 outliers systems. The result shows the evolution still exist among the other 28 AGN sample.
+}
+\end{figure}
+
+It is worth note that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
+That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at the local.
+Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.
+
+Without taking into account the selection effect, the direct comparison shows that the growth of the black hole predates that of the host bulge.
+
+\subsection{Selection effect}
+\label{select_eff}
+
+Our AGN sample is manually selected based on the mass of BH, the Eddington rates, and \halpha\ broad emission line, with low nuclear-to-host ratios.
+When adopting the inference from the selected sample to the overall sample without properly considering the selection effect, bias could be introduced~\citep{Tre++07, Bennert++2011, Schulze2014, Park15}.
+In theory, the simulation~\citep{DeG++15} also find the scaling relations by the selected samples have steeper feature than the random ones, highlighting the necessity of eliminating the selection biases.
+
+We take selection effects into account using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}.
+Following \citet{Park15, Ding2017b}, we generate the simulating samples from a combination of the local active \mbh\ function by \cite{Schulze2010} and the local samples adopted in this work.
+We then added Gaussian random noise to the simulated samples as a function of two free parameters, $\gamma$ and \sint, where \sint\ is the intrinsic scatter when considering the scaling relation as linear.
+According to the observed distribution, we consider the observational selection of \mbh\ of our samples by lower and upper limits of $[7.7, 8.8]$ to model their distribution.
+To evaluate the posterior at the given $\gamma$ and \sint, for each object, we consider the likelihood of observing such object using the simulated sample, and consider whether the object would be selected or not, given the sensitivity.
+In addition, we adopt both uniform (flat) prior and lognormal prior for \sint\ (using the inference from linear fitting).
+
+Combining the 32 AGNs together with the intermediate redshift sample, we present the inferred  $\gamma$ and \sint\ in the two-dimensional planes in Figure~\ref{fig:select_effect}.
+With a lognormal prior for \sint, the fitted $\gamma = 0.8\pm0.3$, consistent with the inference by the flat prior.
+These inference are consistent with the previous values without considering the selection effect in Section~\ref{sec:mm}, indicating that the evolution feature of our sample exist globally in the overall samples.
+Furthermore, we find that the final inferred scatter \sint$\sim 0.3$ are similar to the local scatter, suggesting that the scatter of the scaling relation at high redshift are similar to local ones and indicating that we have not significantly underestimated/overestimated our errors for high redshift samples.
+
+We also study the selection effect by only consider the new 32 AGNs, result in a higher evolution trend with a higher value of $\gamma$.
+We show all the result of the $\gamma$ and \sint\ in Table~\ref{table:gamma_sf}.
+
+\begin{table}
+\centering
+    \caption{The summary for the different inference of $\gamma$.}\label{table:gamma_sf}
+     \resizebox{8cm}{!}{
+     \begin{tabular}{cccc}
+     \hline
+     Sample & Selection effects &  \mbh-\smass & \mbh-\lhost \\
+     &&&\\
+     \hline\hline
+32 AGNs + intermediate & No & 0.74$\pm$0.21 & 0.70$\pm$0.18 \\
+32 AGNs + intermediate& Yes & 0.80 $\pm$ 0.30 & 0.60 $\pm$ 0.30 \\
+32 AGNs & No & 0.80$\pm$0.27  & 1.13$\pm$0.23\\
+32 AGNs& Yes & 1.30$\pm$0.50 & 1.70$\pm$0.40 \\
+     \hline
+     \end{tabular}}
+    \tablecomments{
+    Entire sample includes the 32 AGNs and the intermediate redshift AGNs from the reference in Section~\ref{sec:compare_sample}.
+Note that the adopted \lhost\ have been transferred to today assuming the passive evolution scenario using Equation~\ref{eq:L_relation}.
+The results of selection effects used the lognormal prior of \sint.
+}
+\end{table}
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+\subfloat[\mbh-\smass, flat prior]
+{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_flatprior.pdf}}&
+\subfloat[\mbh-\smass, lognormal prior]
+{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_lognormprior.pdf}}\\
+\end{tabular}
+\caption{\label{fig:select_effect} 
+Constraining the evolution factor $\gamma$ of \mbh-\smass\ relation using Equation~\ref{eq:offset}, with intrinsic scatter \sint, using Monte Carlo simulation, by taking selection effects into account.
+The adopted sample includes 32 AGNs and the intermediate redshift AGNs, using flat prior of \sint\ (left panel) and lognormal prior (right panel).
+}
+\end{figure*}
+
+\section{discussion}
+\label{sec:dis}
+
+\subsection{Host luminosity passive evolution correction}\label{sec:ml-ev}
+In a passive evolution scenario, we expect \lhost\ to fade over time. We transfer the \lhost\ for distant samples at today and compare them to the local in an equivalent frame
+
 We consider this scenario following \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
@@
 \end{eqnarray} 
-This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$.
-We refer to \citet[][section 5.4]{Ding2017b} for more details and find that, after transferring the \lhost\ to today, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts.
-To quantitatively understand this trend, we fit the offset as a function of redshift in form as:
-\begin{eqnarray}
-\label{eq:offset}
-\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
-\end{eqnarray} 
-where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{L_{R,0}}{10^{10}L_{\odot}})$.
-The best-fit and  1-$\sigma$ inference are $\gamma = 0.70 \pm 0.15$.
-
-\textcolor{blue}{Of course, this is a simplified correction, as we only consider the evolution of the host galaxy but not the BH.
-Anyway, we couldn't exactly know how they were evolving to $z=0$.
-Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution.}
-
-%\begin{figure}
-%\centering
-%{
-%\includegraphics[height=0.4\textwidth]{fig/MBH-L-vz.pdf}
-%}
-%\caption{\label{fig:ML-vz} 
-%Illustration of the offset in log\mbh\ (VS. $L_R$) as a function of redshift. The orange band is the intrinsic scatter of local linear relation.}
-%\end{figure}
-
-%Given that the current result does not take into account selection effects yet, we will draw the conclusion in section~\ref{select_eff}.
-
-\subsection{\mbh-\smass\ relation}\label{sec:mm}
-In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample. We visually see that the relations for the three samples are close from one to another.
-
-Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$.
-We obtain the $\gamma  = 0.74 \pm 0.17$, i.e.
-tentative evidence for evolution, see Figure~\ref{fig:MM-vz}, panel (a).
-We also show the ratio of \mbh-\smass\ of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).
-We highlight that our results are less biased in both the measurement of \mbh\ and \smass.
-
-\begin{figure}
-\centering
-{
-\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar.pdf}
-}
-\caption{\label{fig:MM} 
-Similar to the Figure~\ref{fig:ML}, but the comparison of the \mbh-\smass\ relations.}
-\end{figure}
+This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer to \citet[][section 5.4]{Ding2017b} for more details.
+
+We find that, as showing in Figure~\ref{fig:ML-vz}-(a), after transferring the \lhost\ to today, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation.
+To quantitatively understand this trend, we fit the offset as a function of redshift in form following Equation~\ref{eq:offset}.
+The best-fit and 1-$\sigma$ inference are $\gamma = 0.71 \pm 0.18$, i.e.
+Figure~\ref{fig:ML-vz}-(b).
+We consider the selection effect use the same approach as introduced in Section~\ref{select_eff}, and obtain $\gamma = 0.6\pm0.3$ with lognormal prior, showing in Figure~\ref{fig:ML-vz}-(c), (d).
+
+This section is based on a simplified correction, after all we are not clear exactly how they were evolving to $z=0$.
+Also, we only consider the evolution of the host galaxy but not the BH.
+Thus, the correlation of the \mbh-\smass\ would be more efficient to understand the co-evolution connection between BH and its host galaxy.
 
@@
 \begin{tabular}{c c}
-{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
-{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
-\end{tabular}
-\caption{\label{fig:MM-vz} 
-Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. Right: redshift evolution of the \mbh/\smass.  }
-\end{figure*}
-
-\textcolor{blue}{We also note that in Figure~\ref{fig:MM-vz}, panel (a), most of our new measurement is visually within the scatter of the local sample.
-The inference of the positive $\gamma$ seems to stem from the four outliers AGN systems which happens to have lower host mass relative to the BH mass.
-Thus, we only take the rest of the 28 sample and rerun the statistical analysis, aim to test if offset still exist among them only.
-As a result, we obtain the $\gamma  = 0.54 \pm 0.22$, indicating a slighter but still positive evolution.}
-
-\begin{figure}
-\centering
-{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_subsample.pdf}}
-\caption{\label{fig:MM_restsample} 
-Same as Figure~\ref{fig:MM-vz}, left, but excluding the 4 outliers systems. The result shows the evolution still exist among the other 28 AGN sample.
-}
-\end{figure}
-
-We highlight that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
-That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at the local.
-Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.
-
-Without taking into account the selection effect, the direct comparison shows that the growth of the black hole predates that of the host bulge.
-
-\subsection{Selection effect}
-\label{select_eff}
-\textcolor{blue}{
-Our AGN sample is selected based on the AGN luminosity and \halpha\ broad emission line, with lower nuclear-to-host ratios, which would introduce the bias in the inference of the evolution of the scaling relation if not properly taken into consideration~\citep{Tre++07, Bennert++2011, Schulze2014, Park15}, known as Malmquist bias.
-In theory, the simulation~\citep{DeG++15} also find the scaling relations by the selected samples have steeper feature than the random ones, highlighting the necessity of eliminating the selection biases.
-}
-
-\textcolor{blue}{
-We take selection effects into account using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}.
-Following \citet{Park15, Ding2017b}, we generate the simulating samples from a combination of the local active \mbh\ function by \cite{Schulze2010} and the local samples adopted in this work.
-We then added Gaussian random noise to the simulated samples as a function of two free parameters, $\gamma$ and \sint, where \sint\ is the intrinsic scatter when considering the scaling relation as linear.
-According to the observed distribution, we consider the observational selection of \mbh\ of our samples by lower and upper limits of $[7.7, 8.8]$ to model their distribution.
-To evaluate the posterior at the given $\gamma$ and \sint, for each object, we consider the likelihood of observing such object using the simulated sample, and consider whether the object would be selected or not, given the sensitivity.
-In addition, we adopt both uniform (flat) prior and lognormal prior for \sint\ (using the inference from linear fitting).
-}
-
-\textcolor{blue}{
-Combining the 32 AGNs together with the intermediate redshift sample, we present the inferred  $\gamma$ and \sint\ in the two-dimensional planes in Figure~\ref{fig:select_effect}.
-Both the \mbh-\lhost\ and \mbh-\smass\ correlations have been considered.
-With a lognormal prior for \sint, the fitted $\gamma$ are $0.6\pm0.3$ (\mbh-\lhost) and $0.8\pm0.3$ (\mbh-\smass), consistent with the inference by the flat prior.
-These inference are consistent with the previous values (Section~\ref{sec:ml} and Section~\ref{sec:mm}) without considering the selection effect, indicating that the evolution feature of our sample exist globally in the overall samples.
-Furthermore, we find that the final inferred scatter \sint$\sim 0.3-0.5$ are similar to the local scatter, suggesting that the scatter of the scaling relation at high redshift are similar to local ones and indicating that we have not significantly underestimated/overestimated our errors for high redshift samples.
-}
-
-\textcolor{blue}{
-We also study the selection effect by only consider the new 32 AGNs, result in a higher evolution trend with a higher value of $\gamma$.
-We show all the result of the $\gamma$ and \sint\ in the Table~\ref{table:gamma_sf}.
-}
-
-\begin{table}
-\centering
-    \caption{The summary for the different inference of $\gamma$.}\label{table:gamma_sf}
-     \resizebox{8cm}{!}{
-     \begin{tabular}{cccc}
-     \hline
-     Sample & Selection effects& \mbh-\lhost &  \mbh-\smass \\
-     &&&\\
-     \hline\hline
-32 AGNs + intermediate & No & 0.70$\pm$0.15 & 0.74$\pm$0.17 \\
-32 AGNs + intermediate& Yes & 0.60 $\pm$ 0.30 & 0.80 $\pm$ 0.30 \\
-32 AGNs & No & 1.13$\pm$0.20 & 0.80$\pm$0.20\\
-32 AGNs& Yes & 1.70$\pm$0.40 & 1.30$\pm$0.50\\
-     \hline
-     \end{tabular}}
-    \tablecomments{
-    Entire sample includes the 32 AGNs and the intermediate redshift AGNs from the reference in Section~\ref{sec:compare_sample}.
-Note that the adopted \lhost\ have been transferred to today assuming the passive evolution scenario using Equation~\ref{eq:L_relation}.
-The results of selection effects used the lognormal prior of \sint.
-}
-\end{table}
-
-\begin{figure*}
-\centering
-\begin{tabular}{c c}
+\subfloat[\mbh-\lhost\ relation, evolution-corrected]
+{\includegraphics[height=0.4\textwidth]{fig/MBH-L_ev.pdf}}&
+\subfloat[offset in log\mbh\ (VS. \lhost) as a function of redshift]
+{\includegraphics[height=0.4\textwidth]{fig/MBH-L-vz.pdf}}\\
 \subfloat[\mbh-\lhost, flat prior]
@@
 {\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
-\subfloat[\mbh-\smass, flat prior]
-{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_flatprior.pdf}}&
-\subfloat[\mbh-\smass, lognormal prior]
-{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_lognormprior.pdf}}\\
 \end{tabular}
-\caption{\label{fig:select_effect} 
-Constraining the evolution factor $\gamma$ using Equation~\ref{eq:offset}, with intrinsic scatter \sint, using Monte Carlo simulation, by taking selection effects into account.
-The adopted sample includes 32 AGNs and the intermediate redshift AGNs.
-Upper panels: the $\gamma$ for the \mbh-\lhost\ relation, using flat prior of \sint panel-(a) and lognormal prior panel-(b).
-Bottom panel presents the result for \mbh-\smass\ relation.
-}
-\end{figure*}
-
-\section{discussion}
-\label{sec:dis}
+\caption{\label{fig:ML-vz} 
+Same as previous figures but for \mbh-\lhost relation, considering the passive evolution correction for host galaxy luminosity.}
+\end{figure*}
+
 \subsection{Systematic error}
-
-\textcolor{blue}{
 In this work, we use the start-of-the-art techniques to derive the host flux from the AGN image.
@@
 In the mean time, we carry out a rapid analysis of the \mbh\ and host properties relations.
-The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.}
-
-\textcolor{blue}{
+The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.
+
 At last, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates.
-That is to say, the intrinsic scatter is not necessarily worse at high-$z$ than the low-$z$.}
+That is to say, the intrinsic scatter is not necessarily worse at high-$z$ than the low-$z$.
+
+\subsection{Affect using different local anchor}
+%Why we local anchor for this paper, for a consistency to the previous work.
+%However, the other local samples could be different.
+%The comparison of the local MM?
+%The corresponding systemic error?
+To determining the scaling relations at the local universe, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}.
+This adopting enable a direct comparison with the previous work \citep{Park15, SS13}, which adopted the same local sample.
+We realize that in the literature, there are other local measurements which could shift the local anchor hence affect the conclusion of the co-evolution.
+For example, we compare our local \mbh-\smass\ sample to the ones by \citet{Kormendy13} (hereafter K13), as showing in Figure~\ref{fig:local_MM_comp}.
+
+We compare the inference of the local linear relation using different combinations of the local sample.
+It turn out that the inference by HR04+B11 has a lower intercept value to the sample by K13+B11 by 0.3~dex.
+Apparently, adopting the local by K13+B11 would raise the local relation, hence mitigate the offset of $\Delta\log\mathcal M_{\rm BH}$ and $\gamma$ by a factor of 0.3~dex.
+Given the values in Table~\ref{fig:MM_restsample}, this mitigating wouldn't affect our inference of $\gamma$ from positive to negative, however, the current offset highlights the importance to build a solid local baseline for the future studies (Bennert et al., in prep).
+
+\begin{figure}
+\centering
+{\includegraphics[width=0.5\textwidth]{fig/local_MM_comparison.pdf}}
+\caption{\label{fig:local_MM_comp} 
+The local \mbh-\smass\ relations from different literature.
+The black and red line are the best-fit linear relation using the sample by combining B11+HR04 and B11+ K13, respectively, showing a 0.3~dex offset in the intercept value.
+}
+\end{figure}
 
@@
 \item The \mbh-\smass\ relations at higher redshift are inconsistent with the local ones, i.e. Figure~\ref{fig:MM}, \ref{fig:MM-vz}.
-\item Considering the correction for passive evolution of galaxy luminosity, the \mbh-\lhost\ relations at higher redshift are inconsistent with the local ones,  i.e.
-Figure~\ref{fig:ML}-(b), \ref{fig:ML-vz}.
+\item Considering the correction for passive evolution of galaxy luminosity, the \mbh-\lhost\ relations at higher redshift are inconsistent with the local ones,  i.e. Figure~\ref{fig:ML-vz}.
 \item The offsets of by the evolution are well described by the form $\Delta\log\mathcal M_{\rm BH}= \gamma \log (1 + z)$.
@@
 Furthermore, {\it JWST} is capable of showing the morphology of structures feeding black hole accretion and feedback on the host galaxy~\citep{Ford2014}, thus providing the opportunity to understand the origin of the scaling relations and their evolution.
+}
 
@@
 
-This work has made use of \lenstronomy~\citep{lenstronomy}, {\sc Astropy}~\citep{Astropy}, {\sc photutils}~\citep{photutils}, {\sc TOPCAT}~\citep{TOPCAT}, {\sc Matplotlib}~\citep{Matplotlib}, {\sc adjustText}~\citep{adjustText} and standard Python libraries.
+This work has made use of \lenstronomy~\citep{lenstronomy}, {\sc Astropy}~\citep{Astropy}, {\sc photutils}~\citep{photutils}, {\sc TOPCAT}~\citep{TOPCAT}, {\sc Matplotlib}~\citep{Matplotlib} %, {\sc adjustText}~\citep{adjustText}
+and standard Python libraries.
 

### 2019-05-29 manuscript/manuscript.tex
Before re-run the sample with n>4.5

@@
 \newcommand{\sint}{$\sigma_{\rm int}$}
+\newcommand{\angstrom}{\text{\normalfont\AA}}
 \makeatletter
@@
 
-\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{1}, Daeseong Park, Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
+\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{1}, Daeseong Park{7}, Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
  }
@@
 \altaffiltext{6}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
-
+\altaffiltext{7}{\textcolor{blue}{To be updated}}
 \begin{abstract}
 
-The tight correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties (e.g.
+The correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties (e.g.
 stellar mass \smass, luminosity \lhost) suggests an evolutionary connection.
 A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time.
-For this purpose, we obtained multi-band {\it Hubble Space Telescope} of  a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs).
+For this purpose, we obtained multi-band {\it Hubble Space Telescope} of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs).
 By applying state-of-the-art tools to the images we obtained accurate host galaxy luminosity and stellar mass.
 The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts.
-\textcolor{blue}{We enlarge the sample using previously published measurements and compare to the local to infer their evolution.
+We enlarge the sample using previously published measurements and compare their \mbh-\smass~and \mbh-\lhost~relations to the local to infer their evolution.
 We find the \mbh-\smass\ relation by our distant sample is inconsistent with the local \mbh-\smass$_{\rm, bluge}$ relation.
@@
 This indication also exist in the \mbh-\lhost\ relation, once account for the passive evolution of the host luminosity.
-The evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.}
+The evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.
 
@@
 Similarly, the works by \citet{Bennert11, Woo++08} supported this general scenario from the observation of the \mbh-\smass and \mbh-\sigstar relations.
-It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}.
+\textcolor{red}{[More reference to be added, such as positive evolution for Merloni et al.
+and other high-z studies such as Peng, non-evolution for Mechtley et al.
+Xuheng also need to also mention the observables some are stellar mass while others are velocity dispersion.
+]}It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}.
 
@@
 Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging.
-Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed quasars, since lensing magnifies the host image to lensed arcs~\citep{Pen++06qsob, Ding2017a, Ding2017b}.
+Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed AGNs, since lensing magnifies the host image to lensed arcs~\citep{Pen++06qsob, Ding2017a, Ding2017b}.
 Last but not least, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}.
@@
 It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.
-
-In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest~\citep{DeG++15}.
-In practice, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history~\citep{Aird2015}.
-In this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS.
-Our study overcomes the limitations of previous studies in the following way.
+\textcolor{blue}{
+In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest.}%~\citep{DeG++15}.
+
+The paper is organized as follows.
+We briefly describe the sample selection and the BH mass of the sample in Section~\ref{sec:data}.
+We describe the observation and collect the PSF library in Section~\ref{observation}.
+In Section~\ref{sec:analysis} we decompose our sample and study the host galaxy surface photometry.
+In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population, which we applied to derive the rest-frame R band \lhost\ and \smass\ and compared to the local samples.
+Discussion and conclusion are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}.
+
+Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} =
+0.70$. Magnitudes are given in the AB system.
+
+%\section{Observations and data reduction}
+%\label{sec:data}
+%In this section, we summarize the sample selection, observations, and data reduction of our sample.
+
+\section{Experimental design}
+\label{sec:data}
+%Our study overcomes the limitations of previous studies in the following way.
 First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function.
@@
 WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference.
-Given the high-quality and sample size of our data, we can test whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e.
+We aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history~\citep{Aird2015}.  
+We design to choose our sample that meets the following criterion to overcome the limitations of previous studies.
+\begin{enumerate}
+\item A sample of broad-line (type-1) AGNs that fall well below the knee of the black how mass function to minimize the bias which could raised by the selection effect.
+\item Sufficient Eddington ratios to assure the AGN contains accreting black hole.
+\item Balmer lines are available to estimate their \mbh, which avoids potential systematic uncertainties in the UV-based estimators \citep{Greene2005}.
+\item X-ray selected sample results in lower nuclear-to-host ratios facilitating the galaxy mass measurements.
+\item Images of the host galaxy observed by adopted \hst/WFC3 above the 4000 \angstrom\ break, given their redshift range.
+\item The large proportion of the sample has multi-band \hst\ imaging, providing extra color information to achieve reliable K-correction and stellar mass inference. 
+\end{enumerate}
+
+In redshift range $1.2<z<1.7$, we will measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS.
+Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e.
 $\sim0.23$ dex,][]{Schulze2014}.
 
-The paper is organized as follows.
-We briefly describe the sample selection and the BH mass of the sample in Section~\ref{sec:data}.
-We describe the observation and collect the PSF library in Section~\ref{observation}.
-In Section~\ref{sec:analysis} we decompose our sample and study the host galaxy surface photometry.
-In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population, which we applied to derive the rest-frame R band \lhost\ and \smass and compared to the local samples.
-Discussion and conclusion are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}.
-
-Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} =
-0.70$. Magnitudes are given in the AB system.
-
-%\section{Observations and data reduction}
-%\label{sec:data}
-%In this section, we summarize the sample selection, observations, and data reduction of our sample.
-
-\section{Sample selection and \mbh}
-\label{sec:data}
-%How the samples are selection.\\
-%Where are they from?
-%\\The redshift range? In a table?
-
-%We aim to study the relation between the BH masses (\mbh) and their host galaxy properties including luminosities (\lhost) and stellar mass (\smass) to redshift at $z>1$. For this propose,
-
-We focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
-We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$ \textcolor{blue}{(BH mass estimated using \halpha\ emission line).} We present the selection window that used to choose the sample in Figure~\ref{fig:selection} and list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}.
-Overall, our final sample is composed of 32 new observations by \hst/WFC3.
-
+\subsection{Target selection}
+We focus on broad-line AGNs as provided by the X-ray coverage of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields, with X-ray flux limited in 0.5-8 keV.
+The Near IR spectra of the AGNs in these fields are available from the survey of Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Matsuoka2013, Nobuta2012}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh.
+More recently, \citet{Schulze2018} present near-IR spectroscopy of a large sample of 243 X-ray AGN in these field.
+We referred to that paper for the details of continuum fitting and emission line modeling.
+\textcolor{red}{John comments to be included:
+[These were first identified through optical spectroscopy in most cases with zCOSMOS bright of faint samples (see Merloni et al. 2007) and then followed up with NIR spectroscopy.]}
+
+Using the \mbh\ estimator introduced in Section~\ref{mbh}, we estimate the value of \mbh\ and select the targets meets range $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$.
+The bolometric luminosities presented in \citet{Schulze2018} enable us to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$ and select the sample which meets our selection window, as shown in Figure~\ref{fig:selection}.
+Moreover, we have higher preference to select the target which has rest-frame UV images as provided by \citet{Scoville2007}.
+
+We list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}.
+
+%\subsection{Black hole mass and Eddington ratios}
 \begin{figure}
@@
 {
-\includegraphics[height=0.4\textwidth]{fig/AGN_selection.pdf}
+\includegraphics[height=0.5\textwidth]{fig/AGN_selection.pdf}
 }
 \caption{\label{fig:selection} 
-\textcolor{red}{Figure needs to be updated.} We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($L_{\rm Bol}/L_{\rm Edd}$) and \mbh.
+We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($\lambda = L_{\rm Bol}/L_{\rm Edd}$) and \mbh.
 Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}.
-For comparing propose, we plot the high$-z$ luminous SDSS QSO samples from the reference \citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}.
+For comparing propose, we plot the high-$z$ luminous SDSS QSO samples that has been studied based on the observation of \hst\ in the reference~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}.
 }
@@
 \colhead{Observing date}&
-\colhead{Expousre time (s)}
+\colhead{Exposure time (s)}
 \\ 
@@
 
+\subsection{BH masses}
+\label{mbh}
 The \mbh\ of type-1 AGNs can be inferred using the so-called virial method~\citep{Peterson2004, Shen2013}.
@@
 
-The Near IR spectra of our target AGNs are available from the survey of Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010}, covering the wavelength range 0.9-1.8~$\mu m$.
-The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$~\citep{Greene2005, Matsuoka2013, Nobuta2012}.
-Note that \citet{Schulze2018} has investigate the \halpha\ and \hbeta\ emission-line properties using the multi-object spectrograph Subaru/FMOS.
-We referred to that paper for the details of continuum fitting and emission line modeling.
-Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt a list of consistent ones to cross-calibrate the \mbh\ for all the samples, in order to avoid any systematic bias in Section~\ref{mbh}.
-
-\subsection{Comparison sample}\label{sec:compare_sample}
-
-We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
-For comparison with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point.
-The sample by B10 consists of 19 \mbh-\lhost\ measured with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex).
-The work of B11 contains 25 \mbh-\smass\ local active AGNs, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
-To increase the local \smass\ and \mbh\ to the higher range, we also include 30 inactive galaxies (mainly ellipticals or S0) as measured by \citet{H+R04} (hereafter HR04).
-
-It is worth noting that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample.
-In other words, our local comparison is the \mbh-\smass$_{Bulge}$ and not those involving total quantities.
-
-We include in our analysis published samples at intermediate redshift range to understand the redshift evolution of these correlations.
-We select samples that were analyzed by members of our team, in order to ensure uniform measurements.
-The intermediate redshift AGNs that we consider include, for the \mbh-\lhost\ relation, 52 objects published by \citet{Park15} at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11, SS13} at $0.5<z<1.9$.
-Moreover, \citet{Bennert11, SS13} also derive the \smass\ for the 27 objects which enable us to compare to the \mbh-\smass\ relation.
-
-\subsection{BH masses}
-\label{mbh}
- %Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g.
-McLure 2002; Shen 2013)}.
-This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
 To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}.
@@
 $<0.03$~dex) between the two references.
-Moreover, in \citet{Schulze2018}, the cross-calibration between the \halpha\ and \hbeta\ has better agreement.
+We also find that, in \citet{Schulze2018}, the cross-calibration between the \halpha\ and \hbeta\ has better agreement.
 Thus, we adopt the virial formalism from \citet{Schulze2018}:
@@
 14/32 systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged value for log(\mbh).
-\textcolor{blue}{3/32 systems, CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}}.
+\textcolor{blue}{3/32 systems, including CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}}.
 
@@
 
+\subsection{Comparison sample}\label{sec:compare_sample}
+
+We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
+For comparison with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point.
+The sample by B10 consists of 19 \mbh-\lhost\ measured with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex).
+The work of B11 contains 25 \mbh-\smass\ local active AGNs, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
+To increase the local \smass\ and \mbh\ to the higher range, we also include 30 inactive galaxies (mainly ellipticals or S0) as measured by \citet{H+R04} (hereafter HR04).
+It is worth noting that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample.
+In other words, our local comparison is the \mbh-\smass$_{Bulge}$ and not those involving total quantities.
+
+We include in our analysis published samples at intermediate redshift range to understand the redshift evolution of these correlations.
+We select samples that were analyzed by members of our team, in order to ensure uniform measurements.
+The intermediate redshift AGNs that we consider include, for the \mbh-\lhost\ relation, 52 objects published by \citet{Park15} at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11, SS13} at $0.5<z<1.9$.
+Moreover, \citet{Bennert11, SS13} also derive the \smass\ for the 27 objects which enable us to compare to the \mbh-\smass\ relation.
+We recalibrate the \mbh\ of the intermediate sample using the self-consistent recipes introduced in Section~\ref{mbh}.
+
 \section{\hst\ observations}
@@
 % The AGN surface photometry in IR Channel Filters.\\
-
 High spatial resolution imaging is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass.
@@
 which enables direct comparison to the distant sample.
-The inferred local relations are presented in the Figure~\ref{fig:ML}, showing that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones.
-The observational result shows that the black hole mass and the host luminosity located at a similar relation at different galaxy age.
+The inferred local relations, as presented in the Figure~\ref{fig:ML}, shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones.
+The observational result indicates that the relation between black hole mass and the host luminosity are similar at different period of the universe.
 
@@
 Considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
-We will present the discussion of this comparison in Section~\ref{sec:ml-ev}.
+We will make this comparison taking the evolution effect into account in Section~\ref{sec:ml-ev}.
 
@@
 \label{eq:MMlocal}
-\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}),
+\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}).
 \end {eqnarray}
 
-To understand the evolution for high$-z$ relations, we fit the offset as a function of redshift in form as:
+To understand the evolution for high-$z$ relations, we fit the offset as a function of redshift in form as:
 \begin{eqnarray}
@@
 
-We also note that in Figure~\ref{fig:MM-vz}, panel (a), most of our new measurement is visually within the scatter of the local sample.
-The inference of the positive $\gamma$ seems to stem from the four outliers AGN systems which happens to have lower host mass relative to the BH mass.
-Thus, we only take the rest of the 28 sample and rerun the statistical analysis, aim to test if offset still exist among them only.
-As a result, we obtain the $\gamma  = 0.55 \pm 0.29$, indicating a slighter but still positive evolution, i.e.
-Figure~\ref{fig:MM_restsample}.
+We visually see that in Figure~\ref{fig:MM-vz}, panel (a), most of our measurements locate within the scattering range of the local sample.
+We doubt whether the positivity of $\gamma$ stems from the four outliers (i.e., the top-four systems in Figure~\ref{fig:MM}).
+We thus exclude these systems and re-run the statistical analysis to see if offset still exists among the rest of our sample.
+As a result, we obtain that $\gamma  = 0.55 \pm 0.29$, indicating the positive evolution trend become weaker but still exists, as shown in Figure~\ref{fig:MM_restsample}.
 
@@
 It is worth note that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
-That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at the local.
+That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at today.
 Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.
@@
 
-Our AGN sample is manually selected based on the mass of BH, the Eddington rates, and \halpha\ broad emission line, with low nuclear-to-host ratios.
-When adopting the inference from the selected sample to the overall sample without properly considering the selection effect, bias could be introduced~\citep{Tre++07, Bennert++2011, Schulze2014, Park15}.
-In theory, the simulation~\citep{DeG++15} also find the scaling relations by the selected samples have steeper feature than the random ones, highlighting the necessity of eliminating the selection biases.
-
+Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios.
+The inference could be biased, when extending the selected sample to the global without properly considering the selection effect~\citep{Tre++07, Bennert++2011, Schulze2014, Park15}.
+In theory, the simulations~\citep{DeG++15} also find the scaling relations by the selected sample has steeper feature than the random ones, highlighting the necessity of eliminating the selection biases.
+
+\textcolor{red}{To be updated with Andres's result.}
 We take selection effects into account using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}.
@@
 \subsection{Host luminosity passive evolution correction}\label{sec:ml-ev}
-In a passive evolution scenario, we expect \lhost\ to fade over time. We transfer the \lhost\ for distant samples at today and compare them to the local in an equivalent frame
-
-We consider this scenario following \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
-$d{\rm mag}_{\rm R} \sim d\log(1+z)$, i.e.,
+In the passive evolution scenario, we expect the galaxy luminosity to fade over time.
+Thus, we transfer the \lhost\ for distant samples at today so as to compare the \mbh-\lhost\ relation to the local in the equivalent frame.
+We consider this scenario following \citet{Ding2017b} by parametrizing the luminosity evolution with the functional form as
+$d{\rm mag}_{\rm R}\sim~d\log(1+z)$, i.e.,
 \begin{eqnarray}
@@
 \end{eqnarray} 
-This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer to \citet[][section 5.4]{Ding2017b} for more details.
-
-We find that, as showing in Figure~\ref{fig:ML-vz}-(a), after transferring the \lhost\ to today, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation.
-To quantitatively understand this trend, we fit the offset as a function of redshift in form following Equation~\ref{eq:offset}.
-The best-fit and 1-$\sigma$ inference are $\gamma = 0.71 \pm 0.18$, i.e.
-Figure~\ref{fig:ML-vz}-(b).
-We consider the selection effect use the same approach as introduced in Section~\ref{select_eff}, and obtain $\gamma = 0.6\pm0.3$ with lognormal prior, showing in Figure~\ref{fig:ML-vz}-(c), (d).
-
-This section is based on a simplified correction, after all we are not clear exactly how they were evolving to $z=0$.
-Also, we only consider the evolution of the host galaxy but not the BH.
-Thus, the correlation of the \mbh-\smass\ would be more efficient to understand the co-evolution connection between BH and its host galaxy.
+This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer the interested readers to \citet[][section 5.4]{Ding2017b} for more details.
+
+Having transferred the \lhost\ to today, we find that, as showing in Figure~\ref{fig:ML-vz}-(a), at fixed mass, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation.
+We fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 0.71 \pm 0.18$, as showing in Figure~\ref{fig:ML-vz}-(b).
+We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.3$, with flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
+
+The inferred $\gamma$ here could have large systematic given the limitations in this section.
+First, the passive evolution is based on a simplified correction; after all, we are not clear exactly how the host evolves to $z=0$.
+Moreover, we only consider the evolution of the host galaxy and assume the \mbh\ does not change much.
+%Moreover, in the literature, the correlation of the \mbh-\smass\ is considered as more fundamental which would be more efficient to understand their co-evolution.
 
@@
 
-\subsection{Affect using different local anchor}
+\subsection{Systematic by different local anchor}
 %Why we local anchor for this paper, for a consistency to the previous work.
@@
 %The corresponding systemic error?
-To determining the scaling relations at the local universe, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}.
-This adopting enable a direct comparison with the previous work \citep{Park15, SS13}, which adopted the same local sample.
-We realize that in the literature, there are other local measurements which could shift the local anchor hence affect the conclusion of the co-evolution.
-For example, we compare our local \mbh-\smass\ sample to the ones by \citet{Kormendy13} (hereafter K13), as showing in Figure~\ref{fig:local_MM_comp}.
-
-We compare the inference of the local linear relation using different combinations of the local sample.
-It turn out that the inference by HR04+B11 has a lower intercept value to the sample by K13+B11 by 0.3~dex.
-Apparently, adopting the local by K13+B11 would raise the local relation, hence mitigate the offset of $\Delta\log\mathcal M_{\rm BH}$ and $\gamma$ by a factor of 0.3~dex.
-Given the values in Table~\ref{fig:MM_restsample}, this mitigating wouldn't affect our inference of $\gamma$ from positive to negative, however, the current offset highlights the importance to build a solid local baseline for the future studies (Bennert et al., in prep).
+To compare with the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}. 
+%This adopting enable a direct comparison with the previous work \citep{Park15, SS13}, which adopted the same local sample. 
+We realize that, in the literature, there are other local measurements have been studied which could also be considered as the local anchor.
+For example, we present our local \mbh-\smass\ sample and the ones by \citet{Kormendy13} (hereafter K13) together in Figure~\ref{fig:local_MM_comp}.
+To test whether different local sample changes the conclusion of the co-evolution, we use different combinations of the these sample and compare their difference by fitting them as linear relation, i.e.
+Equation~\ref{eq:MMlocal}.
+It turns out that the local anchor inferred by HR04+B11 has a lower intercept value $\alpha$ compared to the one by K13+B11 by 0.3~dex.
+As a consequence, adopting the local by K13+B11 would raise the local relation, hence mitigate the offset of $\Delta\log\mathcal M_{\rm BH}$ and $\gamma$ by a factor of 0.3~dex.
+Given the values in Table~\ref{fig:MM_restsample}, this mitigating wouldn't change our inference of $\gamma$ from positive to negative.
+However, this quick comparison of the local sample highlights the need of the solid local baseline for the future studies (Bennert et al., in prep).
 

### 2019-05-29 M_BH_relation/MM_all_vz_rest28.py

@@ -11,6 +11,7 @@ import matplotlib.pyplot as plt
 import matplotlib as mat
 import matplotlib.lines as mlines
 from matplotlib import colors
+#The four outliers ['CDFS-1', 'SXDS-X1136', 'SXDS-X763', 'CDFS-724']
 mat.rcParams['font.family'] = 'STIXGeneral'
 host=plt.figure(figsize=(14.5,12))
 ax=host.add_subplot(111)   #to get the log(1+z) and z label
@@ -62,7 +63,7 @@ MB_ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'ECDFS-321', 'CID
 zs = np.asarray(load_zs(ID))
 host_n = np.array(load_n(ID, folder = '../'))[:,0]
 Mstar = load_host_p(ID)[1]
-MBs = load_MBH(ID,MB_ID)
+MBs = load_MBH(ID,MB_ID, if_reportHb=1)
 Mstar_err = load_err(prop = 'Mstar', ID=ID)
 yerr_highz = [(Mstar_err[:,0]**2+0.4**2)**0.5, (Mstar_err[:,1]**2+0.4**2)**0.5]
 

### 2019-05-29 M_BH_relation/local_MM_v_others.py

@@ -1,0 +1,127 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.lines as mlines
+############### with evolution-corrected or not? #################
+#select = 1
+host = 1
+
+import sys
+sys.path.insert(0,'../py_tools')
+#from dmag import pass_dmag
+
+########input 25 local by Bennert++2011 ############
+f1 ='data/Bennert+2011_local.txt'
+local25 = np.loadtxt(f1)
+bloc = np.zeros([len(local25),5])
+bloc[:,0]= local25[:,1]    #Redshift
+bloc[:,1]= local25[:,5]    #LgMstar
+bloc[:,2]= local25[:,6]    #Sigma LgMstar
+bloc[:,3]= local25[:,7]    #LgMBH
+bloc[:,4]= local25[:,8]    #Sigma LgMBH
+#plt.errorbar(bloc[:,1],bloc[:,3], xerr=bloc[:,2] ,yerr=bloc[:,4],fmt='.',color='gray',markersize=15)
+#plt.plot(bloc[:,1],bloc[:,3], '.',color='gray',markersize=15)
+#Bkc=mlines.Line2D([], [], color='gray', ls='', marker='.', markersize=15)
+
+########input 30 local by Haring 04 ############
+f2 ='data/Haring04.txt'
+Haring04 = np.loadtxt(f2)
+hloc = np.zeros([len(Haring04),5])
+hloc[:,1]= np.log10(Haring04[:,0] * 10 ** Haring04[:,1])    #LgMstar
+hloc[:,2]= 0.18  # Mention in the Haring04 paper, note in fig 2
+hloc[:,3]= np.log10(Haring04[:,2] * 10 ** Haring04[:,5])    #LgMBH
+hloc[:,4]= (abs(np.log10(Haring04[:,2] + Haring04[:,3]) - np.log10(Haring04[:,2])) + abs(np.log10(Haring04[:,2] - Haring04[:,4]) - np.log10(Haring04[:,4])))/2
+
+from scipy import integrate
+from scipy.optimize import fsolve
+def Ez(z,om):
+    '''
+    Actually, this is the reverse of the E(z)
+    '''
+    w = -1
+    return   1/np.sqrt(om*(1+z)**3+(1-om)*(1+z)**(3*(1+w)))   
+def r(z,om):
[…]

### 2019-05-29 analysis_Astrodrz/CID452/analysis/best_fit_plot_for_paper.py

@@ -23,6 +23,7 @@ ID = path.split('/')[-2]
 
 from filter_info import filt_info
 filt = filt_info[ID]
+del filt_info['CID255']
 
 import re
 f = open("fit_result_each/each_PSF_fit_qso.txt","r")
@@ -133,17 +134,17 @@ fixcenter = False
 count = 0
 for i in np.array(range(psf_id, psf_id+1)):   #(psf_name_list))):
     print "{2} by PSF: {0}, PSF NO. {1}".format(psf_name_list[i], i, ID)
-    tag = '../../bestfit_plot/best_fit_{0}'.format(ID)
+#    tag = '../../bestfit_plot/best_fit_{0}'.format(ID)
     psf_i = psf_list[i] * PSF_mask_img_list[i]
     psf_i = psf_i[ct:-ct,ct:-ct]
     source_result, ps_result, image_ps, image_host, error_map=fit_qso(QSO_im, psf_ave=psf_i, psf_std = None,
                                                                      background_rms=background_rms,
                                                                      source_params=source_params, QSO_msk = QSO_msk, fixcenter=fixcenter,
-                                                                     pix_sz = 'drz06', no_MCMC =True,
-                                                                     QSO_std =QSO_std, tag=tag, image_plot=False)
+                                                                     pix_sz = 0.0642, no_MCMC =True, pltshow=1,
+                                                                     QSO_std =QSO_std, tag=None, image_plot=True)
     result = transfer_to_result(data=QSO_im, pix_sz = 'drz06',
             source_result=source_result, ps_result=ps_result, image_ps=image_ps, image_host=image_host, error_map=error_map,
-            filt=filt, fixcenter=fixcenter,ID=ID,QSO_msk =QSO_msk, tag=tag)
+            filt=filt, fixcenter=fixcenter,ID=ID,QSO_msk =QSO_msk, tag=None)
 #    if count == 0:
 #        fit_result.write("#QSO_img intensity: {0} \n".format(round(np.sum(QSO_im*QSO_msk),2)))
 #    fit_result.write("#fit by PSF{0}: \n".format(psf_name_list[i]))

### 2019-05-29 comparsion_Simulation_CANDEL/CANDELS_catalog/compare_with_CANDLESCOSMOS_color.py

@@ -91,7 +91,7 @@ da_result = 1/(1+results[:,0])*c*vec_EE(results[:,0])/h0  #in Mpc
 
 #%% Plot and input my sample
 
-relation = 2  # 0 M*- Reff ; 1 M*-color; 2 M*-n
+relation = 0  # 0 M*- Reff ; 1 M*-color; 2 M*-n; 3 Reff-n relation
 z_range = [1.2,1.7]
 
 z_cut = ((results[:,0]>z_range[0]) * (results[:,0]<z_range[1]))
@@ -99,8 +99,21 @@ z_cut = ((results[:,0]>z_range[0]) * (results[:,0]<z_range[1]))
 #ssfr_break =-10.5
 ssfr_break =100
 
+
+def logR_mstar(mstar, logA, alpha):
+    """
+    The R_Mstar relation in
+    http://adsabs.harvard.edu/abs/2014ApJ...788...28V
+    mstar in unit of log(M*/Msun)
+    """
+#    mstar = np.log10(10**mstar/7.*10**10.)
+#    logr = logA + alpha*(mstar) + 10*alpha + alpha*np.log10(1/7.)
+    r = 10**logA*(10**mstar/(5.*10**10))**alpha
+    logr = np.log10(r)
+    return logr
+
 #blue_galaxy = ([results[:,5]>ssfr_break])[0]
-red_galaxy = ([results[:,5]<ssfr_break])[0]
+all_galaxy = ([results[:,5]<ssfr_break])[0]  #As all galaxy
 #z_cut = ([results[:,0]>0]) 
 
 cmap_r = matplotlib.cm.get_cmap('jet')
@@ -108,15 +121,24 @@ cmap_r = matplotlib.cm.get_cmap('jet')
 plt.figure(figsize=(15, 11))
 if relation == 0:
     Reff_kpc = da_result * 10 **3 * (results[:,1]/3600./180.*np.pi)
-    plt.scatter(results[:,3][z_cut* red_galaxy],np.log10(Reff_kpc[z_cut * red_galaxy]),
-                c=(results[:,7][z_cut* red_galaxy]/results[:,8][z_cut * red_galaxy]),s=280,marker=".",zorder=90, vmin=0, vmax=7, alpha=0.6, edgecolors='white', cmap=cmap_r)
-
+    plt.scatter(results[:,3][z_cut* all_galaxy],np.log10(Reff_kpc[z_cut * all_galaxy]),
[…]

### 2019-05-29 py_tools/fit_qso_old.py

@@ -6,40 +6,15 @@ Created on Wed Mar 28 20:23:36 2018
 @author: Dartoon
 
 A func for fitting the QSO with a input PSF. The PSF std is optional.
-
-Update based on Lenstronomy version 0.7.0
-Imporve the way for to pickle.dump
-
-Update based on Lenstronomy version 0.8.1
-Including:
-    The lenstronomy package be universal to overall function
-        
-To do:
-    1. PSF std should be put to the PSF class.
 """
-
 from matplotlib.pylab import plt
 import numpy as np
 import corner
-import pickle
-import time
-
-import lenstronomy.Util.simulation_util as sim_util
-from lenstronomy.Data.imaging_data import ImageData
-from lenstronomy.Data.psf import PSF
-from lenstronomy.PointSource.point_source import PointSource
-from lenstronomy.ImSim.image_model import ImageModel
-from lenstronomy.LightModel.light_model import LightModel
-from lenstronomy.Workflow.fitting_sequence import FittingSequence
-from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
-from lenstronomy.Plots.output_plots import LensModelPlot  
-import lenstronomy.Plots.output_plots as out_plot  
-from lenstronomy.Sampling.parameters import Param
 
 def fit_qso(QSO_im, psf_ave, psf_std=None, source_params=None,ps_param=None, background_rms=0.04, pix_sz = 0.168,
             exp_time = 300., fix_n=None, image_plot = True, corner_plot=True,
             flux_ratio_plot=False, deep_seed = False, fixcenter = False, QSO_msk=None, QSO_std=None,
-            tag = None, no_MCMC= False, pltshow = 1, return_Chisq = False, dump_result = False, pso_diag=False):
+            tag = None, no_MCMC= False, pltshow = 1, return_Chisq = False):
     '''
     A quick fit for the QSO image with (so far) single sersice + one PSF. The input psf noise is optional.
     
@@ -68,11 +43,15 @@ def fit_qso(QSO_im, psf_ave, psf_std=None, source_params=None,ps_param=None, bac
     exp_time = exp_time  #  exposure time (arbitrary units, flux per pixel is in units #photons/exp_time unit)
     numPix = len(QSO_im)  #  cutout pixel size
     deltaPix = pix_sz
+    fwhm = 0.1  # full width half max of PSF (only valid when psf_type='gaussian')
[…]

### 2019-05-29 py_tools/load_result.py

@@ -247,7 +247,7 @@ def load_host_p(ID, folder='../', temp='1Gyrs', dm = 0):
     Mstar = np.log10(host_LR_Vega * 0.54 * 0.684 * 1.4191)  
     return np.log10(host_LR), Mstar, host_Mags
 
-def load_MBH(ID, MB_ID, if_reportHb=0,folder = '..'):
+def load_MBH(ID, MB_ID, if_reportHb=1,folder = '..'):
     #ID change:
     #XID2202 to LID1622
     #XID2138 to LID1820
@@ -282,9 +282,9 @@ def load_MBH(ID, MB_ID, if_reportHb=0,folder = '..'):
     #        cal_logMa = 6.459+0.55*(logLHadr-42)+2.*np.log10(FWMH_a/1000)  # as used in H0liCOW 7 and McGill
             mbh = cal_logMa
             MBs.append(mbh)
-        if ser!=-99 and float(samples[ser][21]) != 0:
-            if if_reportHb ==1:
-                print "use Hb for", ID[tar_in]
+        if ser!=-99 and float(samples[ser][21]) != 0 and if_reportHb==1:
+#            if if_reportHb ==1:
+            print "use Hb for", ID[tar_in]
             FWMH_b = float(samples[ser][19])
             logL5100dr = float(samples[ser][16])
             cal_logMb = 6.91+0.5*(logL5100dr-44)+2.*np.log10(FWMH_b/1000)  # as used in Andreas
@@ -378,7 +378,40 @@ def load_err(prop, ID):
     errs = [un_dict[ID[i]] for i in range(len(ID))]
     return np.array(errs)
     
-
+def load_Lbol(ID, folder='../'):
+    ext_ID = {'XID2202':'LID1622', 'XID2138':'LID1820', 'XID2396':'LID1878', 'CDFS-321':'ECDFS-321'}
+    f_mbh = open(folder+"M_BH_relation/fmos_MBH_table","r")
+    with f_mbh as g:
+        lines = g.readlines()
+    samples = [lines[i].split(' ') for i in range(1,len(lines))]
+    #outliers = ['CDFS-1', 'SXDS-X1136', 'SXDS-X763', 'CDFS-724']
+    ID_ser_dic =  {}
+    import copy
+    tab_sub_list = copy.deepcopy(ID)
+    for i in range(len(tab_sub_list)):
+        if tab_sub_list[i] in ext_ID.keys():
[…]

### 2019-06-04 manuscript/manuscript.tex
Push before add John's edits

@@
 For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today.
+Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass and \mbh-\sigstar relations.
+\textcolor{blue}{In addition, based on spectroscopic information, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components, finding a positive evolution of black holes to the galaxies in their correlation.
 This offset can be explained by a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells.
-Similarly, the works by \citet{Bennert11, Woo++08} supported this general scenario from the observation of the \mbh-\smass and \mbh-\sigstar relations.
-\textcolor{red}{[More reference to be added, such as positive evolution for Merloni et al.
-and other high-z studies such as Peng, non-evolution for Mechtley et al.
-Xuheng also need to also mention the observables some are stellar mass while others are velocity dispersion.
-]}It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}.
+It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars and limited size of the sample.
+For example, some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}.
+In addition, once considering the selection effect \citet{Mechtley2012, Schulze2014}, the observed apparent offset at high redshift is fully consistent with no intrinsic offset.}
 
@@
 \item X-ray selected sample results in lower nuclear-to-host ratios facilitating the galaxy mass measurements.
-\item Images of the host galaxy observed by adopted \hst/WFC3 above the 4000 \angstrom\ break, given their redshift range.
+\item Images of the host galaxy observed by adopted \hst/WFC3 above the 4000 \angstrom\ break and below the broad \halpha\ line (6563 \angstrom) given their redshift range.
 \item The large proportion of the sample has multi-band \hst\ imaging, providing extra color information to achieve reliable K-correction and stellar mass inference. 
@@
 Using the \mbh\ estimator introduced in Section~\ref{mbh}, we estimate the value of \mbh\ and select the targets meets range $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$.
-The bolometric luminosities presented in \citet{Schulze2018} enable us to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$ and select the sample which meets our selection window, as shown in Figure~\ref{fig:selection}.
+The bolometric luminosities presented in \citet{Schulze2018} help us to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
+We are able to select the sample which have higher Eddington ratios when \mbh\ is lower, to assure the AGN is still activate, as shown in Figure~\ref{fig:selection}.
 Moreover, we have higher preference to select the target which has rest-frame UV images as provided by \citet{Scoville2007}.
@@
 Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}.
+We also control the sample to have higher Eddington ratios when their \mbh\ is lower, to guarantee the AGN activity.
 For comparing propose, we plot the high-$z$ luminous SDSS QSO samples that has been studied based on the observation of \hst\ in the reference~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}.
@@
 \label{eq:Ha}
-\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.71+0.48 \log \left(\frac{ \lambda \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
+\log \left(\frac{\mathcal M_{\rm BH} (H\alpha)}{M_{\odot}}\right)&~=~& 6.71+0.48 \log \left(\frac{ \rm L _{H\alpha}}{10^{42}{\rm erg~s^{-1}}}\right) \nonumber\\
 &~+~& 2.12 \log \left(\frac{\rm FWHM(H\alpha)}{1000 ~{\rm km~s^{-1}}}\right) ,
@@
 \label{eq:Hb}
-\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \lambda \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
+\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
 &~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) .
@@
 Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
-14/32 systems have both \halpha\ and \hbeta\ emission line information; we adopt the averaged value for log(\mbh).
-\textcolor{blue}{3/32 systems, including CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}}.
+{\color{blue} 3/32 systems, including CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}.
+14/32 systems have both \halpha\ and \hbeta\ emission line information. However, we only adopt the value for \mbh\ using the \halpha emission line, to assure they are self-consistent.
+%Given that 18/32 sample are lack of \hbeta\ line, we thus adopt the \mbh\ estimated by \halpha\ to our sample in the rest of the work, to avoid the scatter of the \mbh\ by \hbeta\ unevenly spreading into the overall sample.
 
 We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}. 
+}
 
@@
 \colhead{}& 
-\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
-\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
+\colhead{FWHM}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
+\colhead{FWHM(5100)}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
 \colhead{}& 
@@
 
-Multi-band information provides the spectral energy distributions (SED) at a more precise level.
+Multi-band information provides the SED at a more precise level.
 21/32 objects in our sample have rest-frame UV images by \citet{Scoville2007}.
@@
 In our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow.
-Thus, we only take the best-fit inference using PSO for the further calcualtions.}.
-To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$.
+Thus, we only take the best-fit inference using PSO for the further calculations.}.
+To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$\footnote{{\color{blue}
+%As will see, three AGN systems would have finally inference with abnormally high \sersic\ index value (i.e., $n>5$).
+We test to reanalyze these sample and fix the \sersic\ index within $n\in[1,4]$ and find their results changes very little ---  $\Delta$\lhost\ and $\Delta$\smass\ within 0.1 dex.
+We also test to use $n\in[1,4]$ as prior, and find that the changes on the inference of the host properties are very limited.
+}}.
 Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs.
@@
 The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}.
-In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.
+In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index and 3) host to total flux ratio\footnote{We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive}.} in Figure~\ref{fig:flux_r_n_corner}.
 
@@
 The actual fitting is based on the two-dimensional images.
-The remaining 31 objects of the sample are shown in appendix A.
+The remaining 31 objects of the sample are shown in Appendix~\ref{sec:restsample}.
 }}
@@
 The inference of the host properties is weighted by eight top-ranked PSFs.
-With a smaller amount of PSFs, one would possibly underestimate the uncertainties.
-To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the inference by five and ten top-ranked PSFs.
+The smaller volume of top-ranked  PSFs would possibly underestimate the uncertainties of the inference.
+To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the inference by using five and ten top-ranked PSFs.
 As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference has been solid when the amount of selected PSF exceeds five.
@@
 
-{\color{blue} 
 Considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
@@
 We visually see that in Figure~\ref{fig:MM-vz}, panel (a), most of our measurements locate within the scattering range of the local sample.
-We doubt whether the positivity of $\gamma$ stems from the four outliers (i.e., the top-four systems in Figure~\ref{fig:MM}).
+We doubt whether the positivity of $\gamma$ stems from the three outliers (i.e., the top-three systems in Figure~\ref{fig:MM}).
 We thus exclude these systems and re-run the statistical analysis to see if offset still exists among the rest of our sample.
@@
 \caption{\label{fig:MM_restsample} 
-Same as Figure~\ref{fig:MM-vz}, left, but excluding the 4 outliers systems. The result shows the evolution still exist among the other 28 AGN sample.
+Same as Figure~\ref{fig:MM-vz}, left, but excluding the 3 outliers systems. The result shows the evolution still exist among the other 29 AGN sample.
 }
@@
 \subfloat[\mbh-\lhost\ relation, evolution-corrected]
-{\includegraphics[height=0.4\textwidth]{fig/MBH-L_ev.pdf}}&
+{\includegraphics[height=0.5\textwidth]{fig/MBH-L_ev.pdf}}&
 \subfloat[offset in log\mbh\ (VS. \lhost) as a function of redshift]
-{\includegraphics[height=0.4\textwidth]{fig/MBH-L-vz.pdf}}\\
+{\includegraphics[height=0.5\textwidth]{fig/MBH-L-vz.pdf}}\\
 \subfloat[\mbh-\lhost, flat prior]
@@
 
+{\color{blue}
+\subsection{The origin of the offset}
+We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift.
+We consider if the offset is related to the AGN activities.
+The straightforward way is to study such offset, i.e.
+$\Delta \log \mathcal M_{\rm BH}$, as a function of \mbh\ and Eddington ratios, showing in Figure~\ref{fig:offset_vs_MBH_edd}.
+Interestingly, we visually see the trend that the offset turns to be larger with at value of \mbh.
+However, at higher Eddington ratio, the offset turns to be lower.
+ {\color{red} Some interpretations need to be presented.}
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+\subfloat[Offset of the \mbh-\smass\ relation as a function of \mbh.]
+{\includegraphics[height=0.5\textwidth]{fig/offset_vs_MBH.pdf}}&
+\subfloat[Offset of the \mbh-\smass\ relation as a function of Eddington ratio.]
+{\includegraphics[height=0.5\textwidth]{fig/offset_vs_Edd.pdf}}\\
+\end{tabular}
+\caption{\label{fig:offset_vs_MBH_edd} 
+Illustration of the offset for high-$z$ \mbh-\smass\ sample as a function of \mbh\ (left) and Eddington ratio (right).}
+\end{figure*} 
+}
+
 \subsection{Systematic error}
@@
 Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry.
+
 We highlight that, in this particular paper, we focus most on the decomposing of the AGN image to present our inference of the host.
@@
 \subsection{Systematic by different local anchor}
-%Why we local anchor for this paper, for a consistency to the previous work.
-%However, the other local samples could be different.
-%The comparison of the local MM?
-%The corresponding systemic error?
-To compare with the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}. 
-%This adopting enable a direct comparison with the previous work \citep{Park15, SS13}, which adopted the same local sample. 
-We realize that, in the literature, there are other local measurements have been studied which could also be considered as the local anchor.
-For example, we present our local \mbh-\smass\ sample and the ones by \citet{Kormendy13} (hereafter K13) together in Figure~\ref{fig:local_MM_comp}.
-To test whether different local sample changes the conclusion of the co-evolution, we use different combinations of the these sample and compare their difference by fitting them as linear relation, i.e.
-Equation~\ref{eq:MMlocal}.
-It turns out that the local anchor inferred by HR04+B11 has a lower intercept value $\alpha$ compared to the one by K13+B11 by 0.3~dex.
-As a consequence, adopting the local by K13+B11 would raise the local relation, hence mitigate the offset of $\Delta\log\mathcal M_{\rm BH}$ and $\gamma$ by a factor of 0.3~dex.
-Given the values in Table~\ref{fig:MM_restsample}, this mitigating wouldn't change our inference of $\gamma$ from positive to negative.
-However, this quick comparison of the local sample highlights the need of the solid local baseline for the future studies (Bennert et al., in prep).
-
-\begin{figure}
-\centering
-{\includegraphics[width=0.5\textwidth]{fig/local_MM_comparison.pdf}}
-\caption{\label{fig:local_MM_comp} 
-The local \mbh-\smass\ relations from different literature.
+To compare our high-$z$ sample the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04} as the anchor at today.
+In the literature, there are other local measurements have been studied which could also be considered as the local anchor.
+We realize that the inconsistency in the different local samples shift our local anchor and thus changes the result of the co-evolutions.
+
+For example, we compare our local \mbh-\smass\ sample to the local quiescent galaxies in \citet{Kormendy13} (hereafter K13).
+We find that K13's local \mbh-\smass\ relation would raise the anchor by $\sim$0.3~dex.
+This could mitigate our offset value $\gamma$ by 0.3~dex.
+However, we also note that the \mbh-\sigstar\ relations in K13 is also higher than the one by our local sample.
+Note that the \mbh-\sigstar\ relations by the quiescent galaxy are usually used to determine the virial coefficient for AGNs.
+That is, adopting the K13 would boost the value of our \mbh\ by $\sim$0.3~dex as well.
+As a result, our inference of the fitted offset $\gamma$ still remains at the same level.
+
+This quick comparison of the local sample highlights the need of the solid local baseline for the future studies (Bennert et al., in prep).
+
+%\begin{figure}
+%\centering
+%{\includegraphics[width=0.5\textwidth]{fig/local_MM_comparison.pdf}}
+%\caption{\label{fig:local_MM_comp} 
+%The local \mbh-\smass\ relations from different literature.
 The black and red line are the best-fit linear relation using the sample by combining B11+HR04 and B11+ K13, respectively, showing a 0.3~dex offset in the intercept value.
-}
-\end{figure}
-
-\subsection{Comparison to the inactive galaxies}
-We compared the morphology of AGNs host galaxies to the inactive galaxies in CANDLES imaging survey.
-We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey~\citep{Momcheva2016, Brammer2012}.
-
-In Figure~\ref{fig:Mstar-rn}, we plot the \smass\ versus the \Reff\ and \sersic\ index.
-The color coding is based on the filter flux ratio between WFC3 and ACS.
-The distribution of \smass-\Reff\ relation show that our AGN hosts concentrate at the high end of the stellar mass, close to the red sequence.
-
-\begin{figure*}
-\centering
-\begin{tabular}{c c}
- \hspace{-2.5em}
-{\includegraphics[trim = 0mm 0mm 90mm 0mm, clip, height=0.45\textwidth]{fig/Mstar-Reff.pdf}}&
-{\includegraphics[ height=0.45\textwidth]{fig/Mstar-Sn.pdf}}\\
-\end{tabular}
-\caption{\label{fig:Mstar-rn} 
-The comparison of the galaxy properties between our 32 AGNs' hosts to the CANDLES sample including 4401 inactive galaxies (circles).
-The color coding is based on the filter flux ratio between WFC3 and ACS.
-For CANDLES sample, the WFC3/F125W flux is taken.
-The black squares are the AGN samples with only WFC3 band observation.
-}
-\end{figure*}
-
-We also compare the histogram of the inferred \Reff\ and \sersic\ n to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value.
-We perform the Kolmogorov-Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.
-We thus conclude that the host galaxies of our AGN sample are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.
-
-\begin{figure}
-\centering
-{\includegraphics[ height=0.3\textwidth]{fig/Hist_Reff.pdf}}\\
-{\includegraphics[ height=0.3\textwidth]{fig/Hist_Sn.pdf}}
-\caption{\label{fig:hist_rn} 
-The comparison of the histogram of the \Reff\ and \sersic\ n, with median value indicated.}
-\end{figure}
-
-%The distribution shows that our AGN host are located at a higher end of the stellar mass at region where
-
-\subsection{JWST}
-\textcolor{red}{Xuheng: some comments on JWST have been made at the end of the Summary. Do we need to put more discussion here?}
+%}
+%\end{figure}
 
@@
 Furthermore, {\it JWST} is capable of showing the morphology of structures feeding black hole accretion and feedback on the host galaxy~\citep{Ford2014}, thus providing the opportunity to understand the origin of the scaling relations and their evolution.
-}
 
@@
 \appendix
-\section{A. The demonstration of remaining 31 AGNs}\label{appA}
+
+\section{A. Comparison to the inactive galaxies}\label{sec:comp_inactive}
+We aim to compared the morphology of AGNs host galaxies to the inactive ones.
+From the CANDLES imaging survey.
+we collect 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey~\citep{Momcheva2016, Brammer2012}.
+%In Figure~\ref{fig:Mstar-rn}, we plot the \smass\ versus the \Reff\ and \sersic\ index.
+The color coding is based on the filter flux ratio between WFC3 and ACS.
+The distribution of \smass-\Reff\ relation show that our AGN hosts concentrate at the high end of the stellar mass, close to the red sequence.
+%\begin{figure*}
+%\centering
+%\begin{tabular}{c c}
+% \hspace{-2.5em}
+%{\includegraphics[trim = 0mm 0mm 90mm 0mm, clip, height=0.45\textwidth]{fig/Mstar-Reff.pdf}}&
+%{\includegraphics[ height=0.45\textwidth]{fig/Mstar-Sn.pdf}}\\
+%\end{tabular}
+%\caption{\label{fig:Mstar-rn} 
+%The comparison of the galaxy properties between our 32 AGNs' hosts to the CANDLES sample including 4401 inactive galaxies (circles).
+The color coding is based on the filter flux ratio between WFC3 and ACS.
+For CANDLES sample, the WFC3/F125W flux is taken.
+The black squares are the AGN samples with only WFC3 band observation.
+%}
+%\end{figure*} 
+We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value.
+We also compare the difference by performing the Kolmogorov-Smirnov test and inferring the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.
+
+We conclude that the host galaxies of our AGN sample are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.
+\begin{figure*}[ht]
+\centering
+\begin{tabular}{c c}
+{\includegraphics[ height=0.3\textwidth]{fig/Hist_Reff.pdf}}&
+{\includegraphics[ height=0.3\textwidth]{fig/Hist_Sn.pdf}}
+\end{tabular}
+\caption{\label{fig:hist_rn} 
+The comparison of the histogram of the \Reff\ and \sersic\ n, with median value indicated.}
+\end{figure*}
+
+\newpage
+\section{B. The demonstration of remaining 31 AGNs}\label{sec:restsample}
 The AGNs decomposition for the other 31 objects of our sample, presented in the same way as Figure~\ref{fig:AGN_decomp}.
 
-\begin{figure}[H]
+\begin{figure}[ht]
 \centering

### 2019-06-04 manuscript/manuscript.tex
push before update on overleaf

@@
 stellar mass \smass, luminosity \lhost) suggests an evolutionary connection.
-A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time.
-For this purpose, we obtained multi-band {\it Hubble Space Telescope} of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs).
-By applying state-of-the-art tools to the images we obtained accurate host galaxy luminosity and stellar mass.
-The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts.
-We enlarge the sample using previously published measurements and compare their \mbh-\smass~and \mbh-\lhost~relations to the local to infer their evolution.
-We find the \mbh-\smass\ relation by our distant sample is inconsistent with the local \mbh-\smass$_{\rm, bluge}$ relation.
-We take selection effect into account to fit this offset as \mbh/\smass$\propto(1+z)^\gamma$, and obtain $\gamma = 0.80\pm0.30$.
-Considering that there is evidence showing our sample are composed of bulge and disk components, our result indicates BHs 8-10 Gyrs ago reside in bulges, if not entire galaxies, which contain lower \smass\ than today.
-This indication also exist in the \mbh-\lhost\ relation, once account for the passive evolution of the host luminosity.
-The evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.
+A powerful test of this co-evolution hypothesis is to measure the relations \mbh-\lhost\ and \mbh-\smass~(total) at high redshift and compare with the local relation.
+For this purpose, we obtained multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
+By applying state-of-the-art tools to decompose the \hst\ emission, we obtained accurate measurements of the host galaxy luminosity and stellar mass.
+The black hole mass (\mbh) is based on near-infrared spectroscopic observations of the broad \halpha~line, which avoids potential uncertainties associated with \Mgii\ or \Civ\ .
+%We enlarge the sample using previously published measurements and compare their \mbh-\smass~and \mbh-\lhost~relations to the local to infer their evolution. 
+We find that the observed ratio of \mbh/\smass ~is 0.0035, a 0.24~dex offset as compared to the local relation that would lead to a evolution as \mbh/\smass$\propto(1+z)^\gamma$ with $\gamma = 0.80\pm0.30$.
+However, we expect an offset of 0.21 dex at these redshifts due to a selection bias thus the high-$z$ sample is consistent with the local sample if considering this effect.
+This is in agreement with the lack of evolution seen in the \mbh/\lhost ~ratios of our sample.
+Therefore, our results depict a scenario where SMBHs and their host galaxies co-evolve with the possibility for SMBHs to have slightly elevated masses, considering the observed ratios, that may indicate that galaxies with lower angular momentum at high-$z$ may be a bit more efficient to grow their black holes at earlier cosmic times.
+In any case, the bulge \smass ~mass at a given black hole mass is clearly discrepant with the local relation, since the hosts have a significant amount of stellar mass in a disk, thus leaving the open question as to whether the connection to the bulge is relevant for black hole growth.
 
@@
 
-Most galactic nuclei are thought to harbor a supermassive black hole (BH), whose mass (\mbh) is known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion (\sigstar).
-These tight correlations indicate a connection between nuclear activity and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
-Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere ($\sim$pc) and their host galaxy ($\sim10$ kpc).
-On the one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
-On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.
-
-A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}.
-During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs.
+Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass) and stellar velocity dispersion (\sigstar).
+These tight correlations may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
+Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc).
+On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering {\color{blue} either the active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or how the growth of these components is connected to the common gas supply~\citep{Cen2015, Menci2016}}.
+On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from galaxy assembly (i.e., mergers) which can reproduce the observed correlations.
+
+A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}.
+During the past decade, there has been much progress on this front at $z<1$ using type-1 AGNs.
 For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today.
-Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass and \mbh-\sigstar relations.
-\textcolor{blue}{In addition, based on spectroscopic information, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components, finding a positive evolution of black holes to the galaxies in their correlation.
-This offset can be explained by a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells.
-It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars and limited size of the sample.
-For example, some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}.
-In addition, once considering the selection effect \citet{Mechtley2012, Schulze2014}, the observed apparent offset at high redshift is fully consistent with no intrinsic offset.}
+Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass\ and \mbh-\sigstar\ relations.
+Of similar results, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies; although, the accuracy of such an approach has not yet been well established.
+If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.
+
+However, there are studies \citep{Cisternas2011,SS13,Mechtley2012} based on \hst\  imaging of deep survey fields such as COSMOS and CDFS that report no evolution in the \mbh - \smass ~ mass ratio as compared to the local relation.
+In support, \citet{Sun2015} has re-analyzed the mass ratios for BLAGN in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citep{Merloni2010} and finds no evolution when accounting for selection effects \citep{Schulze2014} that consider the black hole mass functions and Eddington rate distribution.
+As highlighted below, samples based on 2D image analysis using \hst\ at $z>1$ are limited thus the infrared capabilities of \hst/WFC3 have not been fully exploited to date on this topic.
 
@@
 It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.
-\textcolor{blue}{
-In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest.}%~\citep{DeG++15}.
-
+
+%~\citep{DeG++15}.
+%We aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch close to the peak in the accretion history of SMBHs~\citep[e.g.,][]{Aird2015}.
+
+In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to the highest redshifts where evolutionary effects should be strongest.
+In particular, we measure the properties of 32 host galaxies in redshift range $1.2<z<1.7$ using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS.
+Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e.
+$\sim0.23$ dex,][]{Schulze2014}.
 The paper is organized as follows.
@@
 Discussion and conclusion are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}.
-
-Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} =
-0.70$. Magnitudes are given in the AB system.
+Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.
+Magnitudes are given in the AB system.
 
@@
 WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference.
-We aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history~\citep{Aird2015}.  
-We design to choose our sample that meets the following criterion to overcome the limitations of previous studies.
-\begin{enumerate}
-\item A sample of broad-line (type-1) AGNs that fall well below the knee of the black how mass function to minimize the bias which could raised by the selection effect.
-\item Sufficient Eddington ratios to assure the AGN contains accreting black hole.
-\item Balmer lines are available to estimate their \mbh, which avoids potential systematic uncertainties in the UV-based estimators \citep{Greene2005}.
-\item X-ray selected sample results in lower nuclear-to-host ratios facilitating the galaxy mass measurements.
-\item Images of the host galaxy observed by adopted \hst/WFC3 above the 4000 \angstrom\ break and below the broad \halpha\ line (6563 \angstrom) given their redshift range.
-\item The large proportion of the sample has multi-band \hst\ imaging, providing extra color information to achieve reliable K-correction and stellar mass inference. 
-\end{enumerate}
-
-In redshift range $1.2<z<1.7$, we will measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS.
-Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e.
-$\sim0.23$ dex,][]{Schulze2014}.
+
+We construct a sample of broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that meet the following criterion to overcome limitations of previous studies.
+
+\begin{itemize}
+
+\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., H$\alpha$) which avoids potential systematic uncertainties in UV-based estimators \citep{Greene2005}.
+
+\item Black holes masses fall below the knee of the black hole mass function to minimize the selection biases.
+
+\item Eddington ratios typically above 1\% for most of the sample.
+
+\item A X-ray selected sample demonstrated to have lower nuclear-to-host ratios thus facilitating the galaxy mass measurements.
+
+\item \hst/WFC3 imaging of the host galaxy above the 4000~\angstrom\ break and not including the broad \halpha\ line (6563~\angstrom).
+
+\item The large fraction of the sample has addition \hst\ imaging (i.e., \hst/ACS, providing extra color information to achieve reliable K-corrections and stellar mass determinations. 
+\end{itemize}
 
 \subsection{Target selection}
-We focus on broad-line AGNs as provided by the X-ray coverage of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields, with X-ray flux limited in 0.5-8 keV.
-The Near IR spectra of the AGNs in these fields are available from the survey of Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Matsuoka2013, Nobuta2012}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh.
-More recently, \citet{Schulze2018} present near-IR spectroscopy of a large sample of 243 X-ray AGN in these field.
-We referred to that paper for the details of continuum fitting and emission line modeling.
-\textcolor{red}{John comments to be included:
-[These were first identified through optical spectroscopy in most cases with zCOSMOS bright of faint samples (see Merloni et al. 2007) and then followed up with NIR spectroscopy.]}
-
-Using the \mbh\ estimator introduced in Section~\ref{mbh}, we estimate the value of \mbh\ and select the targets meets range $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$.
-The bolometric luminosities presented in \citet{Schulze2018} help us to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
+
+The AGN sample is initially detected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
+In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck and Magellan.
+Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh.
+More recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields.
+It is from this catalog that we primarily select our targets.
+We refer the reader to that paper for the details of continuum fitting and emission-line modeling.
+
+Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$.
+The bolometric luminosities presented in \citet{Schulze2018} are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
 We are able to select the sample which have higher Eddington ratios when \mbh\ is lower, to assure the AGN is still activate, as shown in Figure~\ref{fig:selection}.
-Moreover, we have higher preference to select the target which has rest-frame UV images as provided by \citet{Scoville2007}.
-
-We list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}.
+Moreover, we have higher preference to select targets which have rest-frame UV images as provided by \citet{Scoville2007}.
+We list all the AGN systems analyzed in this work (Table~\ref{tab:objlist}).
 
@@
 
-\subsection{BH masses}
+\subsection{Details on BH mass estimates}
 \label{mbh}
@@
 {\color{blue} 3/32 systems, including CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}.
-14/32 systems have both \halpha\ and \hbeta\ emission line information. However, we only adopt the value for \mbh\ using the \halpha emission line, to assure they are self-consistent.
+14/32 systems have both \halpha\ and \hbeta\ emission line information. However, we only adopt the value for \mbh\ using the \halpha\ emission line, to assure they are self-consistent.
 %Given that 18/32 sample are lack of \hbeta\ line, we thus adopt the \mbh\ estimated by \halpha\ to our sample in the rest of the work, to avoid the scatter of the \mbh\ by \hbeta\ unevenly spreading into the overall sample.
@@
 High spatial resolution imaging is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass.
-For this purpose, all the new 32 AGN systems were observed with the \hst/WFC3 infrared channel, as part of the HST program GO-15115, PI: John Silverman.
+For this purpose, all the new 32 AGN systems were observed with the \hst/WFC3 infrared channel, as part of the \hst\ program GO-15115, PI: John Silverman.
 We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets.
@@
 Thus, we only take the best-fit inference using PSO for the further calculations.}.
-To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$\footnote{{\color{blue}
+To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$\footnote{{\color{blue}
 %As will see, three AGN systems would have finally inference with abnormally high \sersic\ index value (i.e., $n>5$).
 We test to reanalyze these sample and fix the \sersic\ index within $n\in[1,4]$ and find their results changes very little ---  $\Delta$\lhost\ and $\Delta$\smass\ within 0.1 dex.
-We also test to use $n\in[1,4]$ as prior, and find that the changes on the inference of the host properties are very limited.
+We test to use $n\in[1,4]$ as prior, and find that the changes on the inference of the host properties are very limited.
 }}.
@@
 \caption{\label{fig:MM-vz} 
-Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. Right: \mbh/\smass\ as a function of redshift.}
+Left: illustration of the offset in log\mbh\ (VS.
+\smass) as a function of redshift.
+The orange band is the intrinsic scatter of local linear relation.
+Right: \mbh/\smass\ as a function of redshift.
+We use open green circle to show the expected shifting of the median offset value before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.
+}
 \end{figure*}
@@
 In theory, the simulations~\citep{DeG++15} also find the scaling relations by the selected sample has steeper feature than the random ones, highlighting the necessity of eliminating the selection biases.
-
-\textcolor{red}{To be updated with Andres's result.}
+{\color{blue} We consider the selection effect using two independent approach introduced in the following two subsections.
+
+\subsubsection{Test selection effect using Monte Carlo simulation}
 We take selection effects into account using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}.
@@
 We then added Gaussian random noise to the simulated samples as a function of two free parameters, $\gamma$ and \sint, where \sint\ is the intrinsic scatter when considering the scaling relation as linear.
-According to the observed distribution, we consider the observational selection of \mbh\ of our samples by lower and upper limits of $[7.7, 8.8]$ to model their distribution.
+According to the observed distribution, we consider the observational selection of \mbh\ of our samples by their lower and upper limits to model their distribution.
 To evaluate the posterior at the given $\gamma$ and \sint, for each object, we consider the likelihood of observing such object using the simulated sample, and consider whether the object would be selected or not, given the sensitivity.
@@
 
+\subsubsection{Test selection effect using Bayesian framework} \label{sec:sf_framework}
+We use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias that could be raised by the selection window and local sample that we adopted.
+The framework considers the fact that, with the particular selection window, the intrinsic scatter in the BH-bulge relation has trend to decline regime of the stellar mass function, result in an average stellar masses lower than the relation.
+Moreover, the other relevant sources of bias are considered, for example the active fraction among SMBHs varies by the black hole mass function, in the sense that BHs with higher mass are less likely to be active than lower mass ones.
+
+Considering our specific selection limits: $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$, their is an expected bias of 0.21~dex in the inference of $\Delta\log($\mbh$)$ for samples at $z\sim1.5$.
+Interestingly, this bias could account for the offset that obtained in Section~\ref{sec:mm}.
+We use open green circle to point out the shifting of the expected population given the biases in Figure~\ref{fig:MM-vz}.
+
+Our conclusion is that the considering the selection effect using framework by \citet{Schulze2011}, we get consistent \mbh-\smass\ with the local sample.
+
+}
+
 \section{discussion}
@@
 \subsection{The origin of the offset}
+{\color{red}[Xuheng:  Given their larger uncertainty, do we still want to present this?]}
 We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift.
@@
 From the CANDLES imaging survey.
-we collect 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey~\citep{Momcheva2016, Brammer2012}.
+we collect 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-\hst\ spectroscopic survey~\citep{Momcheva2016, Brammer2012}.
 %In Figure~\ref{fig:Mstar-rn}, we plot the \smass\ versus the \Reff\ and \sersic\ index.

### 2019-06-04 M_BH_relation/local_MM_vz.py

@@ -3,7 +3,7 @@ import matplotlib.pyplot as plt
 import matplotlib.lines as mlines
 ############### with evolution-corrected or not? #################
 #select = 1
-host = 1
+#host = 1
 
 import sys
 sys.path.insert(0,'../py_tools')
@@ -84,7 +84,7 @@ m_ml, b_ml,sint_ml= result["x"]
 #print m_ml, b_ml, sint_ml, "ka=",lnlike(theta=[m_ml, b_ml, sint_ml],x=loc[:,0], y=loc[:,1], yerr=loc[:,2])
 
 #m_ml, b_ml = 1.12, -4.12  # Park's first use
-m_ml, b_ml = 1.02, -2.91  # Park's inference from the two sample
+#m_ml, b_ml = 1.02, -2.91  # Park's inference from the two sample
 
 xp = np.array([5, 13])
 #plt.plot(xp, m_ml*xp+b_ml, 'r-')

### 2019-06-06 manuscript/manuscript.tex
Before John's may edit

@@
 Moreover, \citet{Bennert11, SS13} also derive the \smass\ for the 27 objects which enable us to compare to the \mbh-\smass\ relation.
-We recalibrate the \mbh\ of the intermediate sample using the self-consistent recipes introduced in Section~\ref{mbh}.
+{\color{blue} In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample.
+
+Across the intermediate redshift sample, we recalibrate the \mbh\ by \halpha\ or \hbeta\ using the self-consistent recipes introduced in Section~\ref{mbh}.
+For \mbh\ estimated by \Mgii\, we adopt the recipe by \citet{Ding2017b} to recalibrate them.
+}
 
@@
 We test to reanalyze these sample and fix the \sersic\ index within $n\in[1,4]$ and find their results changes very little ---  $\Delta$\lhost\ and $\Delta$\smass\ within 0.1 dex.
-We test to use $n\in[1,4]$ as prior, and find that the changes on the inference of the host properties are very limited.
-}}.
+We test to use $n\in[1,4]$ as prior to fit the systemic with high \sersic\ index ($n>4.5$), and find that the changes on the inference of their host magnitude are very limited ($<0.03$ dex).}
+}.
 Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs.
@@
 The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}.
-In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index and 3) host to total flux ratio\footnote{We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive}.} in Figure~\ref{fig:flux_r_n_corner}.
+In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.
+We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive}.
 
@@
 \caption{\label{fig:MM-vz} 
-Left: illustration of the offset in log\mbh\ (VS.
-\smass) as a function of redshift.
-The orange band is the intrinsic scatter of local linear relation.
-Right: \mbh/\smass\ as a function of redshift.
-We use open green circle to show the expected shifting of the median offset value before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.
+Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. Right: \mbh/\smass\ as a function of redshift. 
+{\color{blue} We use green open circles to show the expected shifting of the median value of the $\Delta$\mbh\ before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.}
+{\color{red} [Xuheng: The blue points are from Cisternas et al. 2011, they are consistent to the local ones.]}
 }
@@
 \subsubsection{Test selection effect using Bayesian framework} \label{sec:sf_framework}
-We use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias that could be raised by the selection window and local sample that we adopted.
-The framework considers the fact that, with the particular selection window, the intrinsic scatter in the BH-bulge relation has trend to decline regime of the stellar mass function, result in an average stellar masses lower than the relation.
-Moreover, the other relevant sources of bias are considered, for example the active fraction among SMBHs varies by the black hole mass function, in the sense that BHs with higher mass are less likely to be active than lower mass ones.
-
-Considering our specific selection limits: $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$, their is an expected bias of 0.21~dex in the inference of $\Delta\log($\mbh$)$ for samples at $z\sim1.5$.
-Interestingly, this bias could account for the offset that obtained in Section~\ref{sec:mm}.
-We use open green circle to point out the shifting of the expected population given the biases in Figure~\ref{fig:MM-vz}.
+We use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias that could be raised by our selection window and local sample that adopted.
+Given the particular selection window (\mbh,  $L_{\rm bol}$ and Eddington ratio $\lambda$), the framework considers the fact that the intrinsic scatter in the BH-bulge relation has trend to decline regime of the stellar mass function, result in an average stellar masses lower than the relation.
+Moreover, the other relevant sources of bias are considered in this framework, for example the active fraction among SMBHs varies by the black hole mass function, in the sense that BHs with higher mass are less likely to be active than lower mass ones.
+
+Considering our specific selection limits: $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$, we infer an expected bias of 0.21~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$.
+Interestingly, this bias could account for the offset that obtained in the \mbh-\smass\ correlations in Section~\ref{sec:mm}.
+We use green open circles to point out the shifting of the expected population given these biases, as shown in Figure~\ref{fig:MM-vz}.
 
@@
 \subsection{The origin of the offset}
-{\color{red}[Xuheng:  Given their larger uncertainty, do we still want to present this?]}
+{\color{red}[Xuheng:  Given their larger uncertainty, do we still want to present these figures?]}
 We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift.
@@
 
-\subsection{Systematic by different local anchor}
-To compare our high-$z$ sample the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04} as the anchor at today.
-In the literature, there are other local measurements have been studied which could also be considered as the local anchor.
-We realize that the inconsistency in the different local samples shift our local anchor and thus changes the result of the co-evolutions.
-
-For example, we compare our local \mbh-\smass\ sample to the local quiescent galaxies in \citet{Kormendy13} (hereafter K13).
-We find that K13's local \mbh-\smass\ relation would raise the anchor by $\sim$0.3~dex.
-This could mitigate our offset value $\gamma$ by 0.3~dex.
+\subsection{Systematic with different local anchor}
+To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}.
+In the literature, there are other local sample have been measured which also usually be considered as the local anchor.
+We note that different local samples have inconsistency which could change the result of the co-evolutions.
+
+To estimate this effect, we compare our local \mbh-\smass\ sample to the local quiescent galaxies by \citet{Kormendy13} (hereafter K13).
+We find that K13's local \mbh-\smass\ relation would raise the anchor by $\sim$0.3~dex and totally erase the offset of $\Delta\log$\mbh.
 However, we also note that the \mbh-\sigstar\ relations in K13 is also higher than the one by our local sample.
@@
 
-Combining out high-$z$ measurements with the intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13}, we compared the scaling relations to the ones by the local with main results summarized as follows:
+Combining our high-$z$ measurements with the intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13, Cisternas2011}, we compared the scaling relations to the ones by the local with main results summarized as follows:
 \begin{enumerate}
@@
 
-Our inference indicates the evidence of disk component, i.e.
+Our inference indicates the evidence of disk+bluge component, i.e.
 the ones with \sersic\ $n<2$, and the local comparing samples are bulge dominated sample, we hence conclude that the BHs 8-10~Gyrs ago reside in bulges, if not entire galaxies, which are less massive/luminous than today.
@@
 
-The authors fully appreciate the discussions with Hyewon Suh, Vardha N. Bennert, Anton M. Koekemoer, Takahiro Morishita.
+The authors fully appreciate the discussions with Hyewon Suh, Vardha N. Bennert, Anton M. Koekemoer, Takahiro Morishita and Peter Williams.
 

### 2019-06-06 Comparsion/Nicola/calculate_hostratio/host_ratio_compare.py

@@ -1,0 +1,50 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Jun  5 08:58:27 2019
+
+@author: Dartoon
+
+Calculate the host flux ratio
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import sys
+sys.path.insert(0,'../../../py_tools')
+import matplotlib as matt
+matt.rcParams['font.family'] = 'STIXGeneral'
+
+ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'CDFS-321', 'CID1174',\
+'CID216', 'CID237','CID3242','CID3570','CID452', 'CID454',\
+'CID50','CID607','LID1273', 'LID1538','LID360','SXDS-X1136',\
+'SXDS-X50', 'SXDS-X717','SXDS-X763','SXDS-X969','XID2138','XID2202',\
+'XID2396', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597', 'CID1281','CID255']
+from load_result import load_host_ratio
+WFC3_ratio = np.array(load_host_ratio(ID, folder='../../../'))
+
+siml_mags = np.loadtxt('lagn_lhost_Vband.dat')
+host_f = 10.**(-0.4*(siml_mags[:,0]))
+agn_f = 10.**(-0.4*(siml_mags[:,1]))
+
+plt.figure(figsize=(8,6))
+high0, x0, _ = plt.hist(host_f/(agn_f+host_f)*100.,normed=True, histtype=u'step',
+         label=('Nicola sample'), linewidth = 2, color='orange')
+high1, x1, _ = plt.hist(WFC3_ratio[:,0],normed=True, histtype=u'step',
+         label=('WFC3 sample'), linewidth = 2, color='green')
+
+x0_m = np.median(host_f/(agn_f+host_f)*100.)
+high_m0 = high0[np.where(abs(x0_m-x0) == abs(x0_m-x0).min())[0][0]-1]
+x1_m = np.median(WFC3_ratio[:,0])
+high_m1 = high1[np.where(abs(x1_m-x1) == abs(x1_m-x1).min())[0][0]-1]
+plt.plot(np.linspace(0,high_m0)*0+np.median(x0_m) , np.linspace(0,high_m0), linewidth = 4,color='orange')
[…]

### 2019-06-06 M_BH_relation/MM_all.py

@@ -42,6 +42,13 @@ b11 = np.loadtxt(f1)[:,1:]  #0 redshift; 1 M*; 2 BH mass;
 if inp_b11 ==1:
     plt.scatter(b11[:,1],b11[:,2],c='darkseagreen',marker="^",s=180,zorder=100, edgecolors='white')
 
+inp_Cis= 1
+f2 = 'data/Cisternas_data.txt'
+cis11 = np.loadtxt(f2)  #0 redshift; 1 M*; 2 BH mass;
+if inp_Cis ==1:
+    plt.scatter(cis11[:,2],cis11[:,1],c='darkseagreen',marker="^",s=180,zorder=100, edgecolors='white')
+
+
 tx, ty = 11.85, 7.
 plt.text(tx, ty, "intermediate\n  sample\nuncertainties",  fontsize=20)
 plt.errorbar(tx+0.2,ty-0.08, xerr=0.2, yerr=0.4, color='darkseagreen',ecolor='black', fmt='^',zorder=-500,markersize=10)
@@ -111,5 +118,5 @@ plt.legend([Bkc,Hkc,SS13,new_sample],[
 "intermediate redshift AGNs",
 "This work"\
 ],scatterpoints=1,numpoints=1,loc=2,prop={'size':20},ncol=2)
-#plt.savefig("MBH-Mstar.pdf")
+plt.savefig("MBH-Mstar.pdf")
 plt.show()

### 2019-06-06 M_BH_relation/MM_all_vz_rest28.py

@@ -118,7 +118,7 @@ if style ==1:
     
 #    if exclude the top 4 y cosmos:
 #    bools = [[Re_results[:,0]>0.2][0] * [y_cosmos<0.844][0]]
-    bools = [y_cosmos<844]
+    bools = [y_cosmos<0.844]
     z=z_cosmos[bools]
     y=y_cosmos[bools]
     yerr = yerr_hz[bools]

### 2019-06-06 analysis_Astrodrz/view_each_sample.py

@@ -25,7 +25,7 @@ ID = ['CID3242']
 ID = ['CDFS-1']
 ID = ['CID237']
 ID = ['CID216']
-ID = ['CID255']
+#ID = ['CID255']
 
 
 import pickle

### 2019-06-18 manuscript/manuscript.tex
Before git pull on overleaf from TT

@@
 
-\subsection{Target selection}
+\subsection{Target selection}\label{sec:target_selection}
 
@@
 
-Across the intermediate redshift sample, we recalibrate the \mbh\ by \halpha\ or \hbeta\ using the self-consistent recipes introduced in Section~\ref{mbh}.
+Across the intermediate redshift sample, we recalibrate the \mbh\ by \halpha/\hbeta\ emission line using the self-consistent recipes introduced in Section~\ref{mbh}.
 For \mbh\ estimated by \Mgii\, we adopt the recipe by \citet{Ding2017b} to recalibrate them.
+
+\section{Expected selection effect bias} \label{sec:sf_framework}
+Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios It has been known that sample selection effects could influence the observed black hole-host relations and its evolution with redshift ~\citep{Schulze2011, Tre++07, Bennert++2011, Park15}.
+In theory, the simulations~\citep{DeG++15} also find the scaling relations by the selected sample has steeper feature than by the random ones.
+To highlight this influence, we study the expected bias of the \mbh\ given our target selection in Section~\ref{sec:target_selection}.
+
+We use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias.
+Given our particular selection window (\mbh,  $L_{\rm bol}$ and Eddington ratio $\lambda$) and the local sample, the framework considers the fact that the intrinsic scatter in the BH-bulge relation has trend to decline regime of the stellar mass function, result in an average stellar masses lower than the relation.
+Moreover, the other relevant sources of bias are considered in this framework, for example the active fraction among SMBHs varies by the black hole mass function, in the sense that BHs with higher mass are less likely to be active than lower mass ones.
+
+Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$.
+
+We would correct our inference by taking this select bias into account in the result sections.
+
+%Interestingly, this bias could account for the offset that obtained in the \mbh-\smass\ correlations in Section~\ref{sec:mm}.
+We use green open circles to point out the shifting of the expected population given these biases, as shown in Figure~\ref{fig:MM-vz}.
+
+%Our conclusion is that the considering the selection effect using framework by \citet{Schulze2011}, we get consistent \mbh-\smass\ with the local sample.
 }
@@
 Thus, we only take the best-fit inference using PSO for the further calculations.}.
-To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$\footnote{{\color{blue}
-%As will see, three AGN systems would have finally inference with abnormally high \sersic\ index value (i.e., $n>5$).
-We test to reanalyze these sample and fix the \sersic\ index within $n\in[1,4]$ and find their results changes very little ---  $\Delta$\lhost\ and $\Delta$\smass\ within 0.1 dex.
-We test to use $n\in[1,4]$ as prior to fit the systemic with high \sersic\ index ($n>4.5$), and find that the changes on the inference of their host magnitude are very limited ($<0.03$ dex).}
-}.
+To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$.
 Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs.
@@
 The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}.
-In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}.
-We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive}.
 
@@
 
-The inference of the host properties is weighted by eight top-ranked PSFs.
+We apply this approach to the overall AGN systems to infer the overall host galaxy information.
+To quickly overview, we plot the relations of the properties between effective radius (\Reff), \sersic\ index and host to total flux ratio in Figure~\ref{fig:flux_r_n_corner} and leave the detail descriptions in the next Section.
+We realize that the inference of the host properties is weighted by eight top-ranked PSFs.
 The smaller volume of top-ranked  PSFs would possibly underestimate the uncertainties of the inference.
@@
 \subsection{Host galaxy properties}
-We derive the rest-frame R band magnitude ($M_R$) and luminosity ($L_R$) of our sample based on their filter magnitude.
+In previous section, we carry out the AGN-host decomposition and derive the host galaxy \sersic\ properties of the overall sample, as shown in Figure~\ref{fig:hist_compare}.
+The optimized resulting images for each sample are presented in the figures in Appendix~\ref{sec:restsample}.
+Based on the third column of these resulting figures (i.e.
+the ``data-Point source'' stamps), we find that all the systems have shown the evidence for existence of the host galaxies.
+We also find that merger feature of the host galaxies are not strong, showing that our sample possibly not be dominated by the major merger.
+
+The host-total flux ratio of the sample are varies from 10\% to 90\% (concentrated between 20\% to 50\%).
+The effective radius and \sersic\ index are randomly distributed within the prior, rather than biased on upper/lower side.
+The inferred \Reff\ of our sample are between $\sim$1-7 kpc (peaked at $\sim$2.2kpc).
+15/32 systems have \sersic\ index $n<2$, indicating they are composed of disk+bulge components.
+Five systems have high \sersic\ index ($n>4.5$); we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
+
+We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive} and find that our high-$z$ AGN host have very similar distribution.
+
+We calculate the rest-frame R band magnitude ($M_R$) of our sample based on their filter magnitude.
 18/32 systems have multi-band host magnitude which enables us to select the best stellar population that could fit the overall sample.
@@
 
-Adopting the color information, we perform the K-correction and derive the rest-frame R band magnitude of our sample.
+\subsection{\mbh-\lhost\ relation}\label{sec:ml}
+Adopting the 1~Gyrs stellar population, we perform the K-correction to derive the rest-frame R band magnitude of our sample.
 Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty introduced by this K-correction is within 0.05~mag.
 We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}.
-
-Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted.
-The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex, at fixed stellar initial mass function (changing the initial mass function would change all our stellar masses systematically).
-
-The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare their relations to the \mbh.
-
-\subsection{\mbh-\lhost\ relation}\label{sec:ml}
+The inferred $L_R$ are ranged between $\log L_R \in [9.5, 11.5]$ ($L_{\odot,R}$), as summarized in Table~\ref{tab:result_sersic}.
+
 We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}. Following common practice, we fit the local relation as a linear relation,
@@
 
+We note three outlier measurements deviated from the distribution of overall sample, which are SXDS-X763, CDFS-1, CDFS-724.
+We expect that they could have abnormal host inference.
+Indeed, for SXDS-X763, the inferred host \Reff\ has large scatter ($\sim 75\%$) with the lowest host-total flux ratio in the overall sample ($<10\%$).
+For CDFS-1 and CDFS-724, their host are \Reff$<0\farcs{}15$, smaller than the PSF FWHM.
+Moreover, the broad emission line of \mbh\ are from \citet{Suh2015} which could have systemic to \citet{Schulze2018}.
+Thus, the measurements of these three systems have less fidelity.
+
 \begin{figure}
@@
 \subsection{\mbh-\smass\ relation}\label{sec:mm}
-In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample.
-We visually see that the relations for the three samples are close from one to another.
+
+Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted.
+The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex, at fixed stellar initial mass function (changing the initial mass function would change all our stellar masses systematically).
+The inferred $M_*$ are ranged between $\log M_* \in [9.7, 11.3]$ ($M_{\odot}$), listed in Table~\ref{tab:result_sersic}.
+
+In Figure~\ref{fig:MM}, we plot the our \mbh-\smass\ measurements and compare to the local and intermediate sample.
+We visually see that the relations for the three samples are close.
 Similar as Equation~\ref{eq:MLlocal}, we consider the local \mbh-\smass\ relations as linear relation as:
@@
 where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$.
-We obtain $\gamma  = 0.74 \pm 0.21$, i.e.
+We obtain $\gamma  = 0.84 \pm 0.26$, i.e.
 tentative evidence for evolution, see Figure~\ref{fig:MM-vz}, panel (a).
@@
 \caption{\label{fig:MM-vz} 
-Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. Right: \mbh/\smass\ as a function of redshift. 
-{\color{blue} We use green open circles to show the expected shifting of the median value of the $\Delta$\mbh\ before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.}
-{\color{red} [Xuheng: The blue points are from Cisternas et al. 2011, they are consistent to the local ones.]}
-}
+Left: illustration of the offset in  $\log($\mbh$)$ (VS.
+\smass) as a function of redshift.
+The orange band is the intrinsic scatter of local linear relation.
+The red line and gray band are the best-fit and $1-\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs.
+Right: \mbh/\smass\ as a function of redshift. 
+We use green open circles to show the expected shifting of the median value of the $\Delta \log$\mbh\ before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.}
 \end{figure*}
@@
 We visually see that in Figure~\ref{fig:MM-vz}, panel (a), most of our measurements locate within the scattering range of the local sample.
-We doubt whether the positivity of $\gamma$ stems from the three outliers (i.e., the top-three systems in Figure~\ref{fig:MM}).
-We thus exclude these systems and re-run the statistical analysis to see if offset still exists among the rest of our sample.
-As a result, we obtain that $\gamma  = 0.55 \pm 0.29$, indicating the positive evolution trend become weaker but still exists, as shown in Figure~\ref{fig:MM_restsample}.
-
-\begin{figure}
-\centering
-{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_subsample.pdf}}
-\caption{\label{fig:MM_restsample} 
-Same as Figure~\ref{fig:MM-vz}, left, but excluding the 3 outliers systems. The result shows the evolution still exist among the other 29 AGN sample.
-}
-\end{figure}
+We doubt whether the positivity of $\gamma$ stems from the three outliers discussed in last section.
+We thus exclude these outliers and re-run the statistical analysis to see if offset still exists.
+As a result, we obtain that $\gamma  = 0.65 \pm 0.27$, indicating the positive evolution trend become weaker but still exists.
+
+%\begin{figure}
+%\centering
+%{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_subsample.pdf}}
+%\caption{\label{fig:MM_restsample} 
+%Same as Figure~\ref{fig:MM-vz}, left, but excluding the 3 outliers systems. The result shows the evolution still exist among the other 29 AGN sample.
+%}
+%\end{figure}
 
 It is worth note that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
-That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at today.
-Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.
-
-Without taking into account the selection effect, the direct comparison shows that the growth of the black hole predates that of the host bulge.
+That is, we are comparing the \mbh-\smass$_{,total}$ relations at the distant universe to the \mbh-\smass$_{,bulge}$ relations at local.
+Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{, bluge}$ of them are supposed to be even less.
+Given that our 32 AGNs present the similar distribution to the inactive ones in CANDLES (see Appendix~\ref{sec:comp_inactive}), we expect the bulge-total ratio could be follow the similar ratio.
+
+{\color{red}
+[Xuheng will add one more section here, about the bulge \smass\ inference and the corresponding $\gamma$, after comparing to the CANDLES data.]
+}
+
+We summarize the inference of $\gamma$ using different combination of sample in Table~\ref{table:diff_sample_gam}.
+All the $\gamma$ by the observed \mbh-\smass\ are inferred as positive, indicating that the growth of the black hole predates that of the host bulge.
+
+\begin{table}
+\centering
+    \caption{The inference of $\gamma$ using \mbh-\smass\ by different sample combination.}\label{table:diff_sample_gam}
+     \resizebox{5.5cm}{!}{
+     \begin{tabular}{cc}
+     \hline
+     Sample combination & $\gamma$ \\
+     &\\
+     \hline\hline
+32 AGNs & 0.84$\pm$0.26\\    
+29 AGNs (excluded outliers) & 0.65$\pm$0.27\\    
+32 AGNs + intermediate &  0.62$\pm$0.20\\
+     \hline
+     \end{tabular}}
+\tablecomments{These values are directly inference for the observation, which haven't yet taken the selection effect into account.}
+\end{table}
 
@@
 \label{select_eff}
-
-Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios.
-The inference could be biased, when extending the selected sample to the global without properly considering the selection effect~\citep{Tre++07, Bennert++2011, Schulze2014, Park15}.
-In theory, the simulations~\citep{DeG++15} also find the scaling relations by the selected sample has steeper feature than the random ones, highlighting the necessity of eliminating the selection biases.
-{\color{blue} We consider the selection effect using two independent approach introduced in the following two subsections.
-
-\subsubsection{Test selection effect using Monte Carlo simulation}
-We take selection effects into account using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}.
+In Section~\ref{sec:sf_framework}, we adopt the Bayesian framework by \citet{Schulze2011} and find that there is an expected $+0.21$~dex bias in the inferred $\Delta \log$\mbh.
+Interestingly, this bias could account for the observed offset as obtained in the \mbh-\smass\ correlations in last Section.
+%~\ref{sec:mm}.
+To make it clear, we use green open circles to point out the shifting of the expected population given these biases in Figure~\ref{fig:MM-vz}.
+We also show, in Figure~\ref{fig:offset_hist}, the histogram the $\Delta \log$\mbh\ by the high-$z$ sample and compare to the local ones.
+Clearly, the correction by considering this selection effect could almost mitigate the offset.
+The result of the correction shows that the high-$z$ sample could have consistent \mbh-\smass$,_{\rm host}$ to the local sample.
+
+\begin{figure}
+\centering
+{
+\includegraphics[width=0.5\textwidth]{fig/hist_offset.pdf}
+}
+\caption{\label{fig:offset_hist} 
+Illustration of the histogram of the $\log($\mbh$)$ offset for the local samples and 32 high-$z$ sample.
+The gray/red vertical line shows the median value of the offset for the high-$z$ sample, before/after considering the selection effect.}
+\end{figure}
+
+%Our conclusion is that the considering the selection effect using framework by \citet{Schulze2011}, we get consistent \mbh-\smass\ with the local sample.
+Furthermore, we adopt an independent method to test the selection effect -- using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}.
 Following \citet{Park15, Ding2017b}, we generate the simulating samples from a combination of the local active \mbh\ function by \cite{Schulze2010} and the local samples adopted in this work.
@@
 
-\subsubsection{Test selection effect using Bayesian framework} \label{sec:sf_framework}
-We use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias that could be raised by our selection window and local sample that adopted.
-Given the particular selection window (\mbh,  $L_{\rm bol}$ and Eddington ratio $\lambda$), the framework considers the fact that the intrinsic scatter in the BH-bulge relation has trend to decline regime of the stellar mass function, result in an average stellar masses lower than the relation.
-Moreover, the other relevant sources of bias are considered in this framework, for example the active fraction among SMBHs varies by the black hole mass function, in the sense that BHs with higher mass are less likely to be active than lower mass ones.
-
-Considering our specific selection limits: $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$, we infer an expected bias of 0.21~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$.
-Interestingly, this bias could account for the offset that obtained in the \mbh-\smass\ correlations in Section~\ref{sec:mm}.
-We use green open circles to point out the shifting of the expected population given these biases, as shown in Figure~\ref{fig:MM-vz}.
-
-Our conclusion is that the considering the selection effect using framework by \citet{Schulze2011}, we get consistent \mbh-\smass\ with the local sample.
-
-}
-
 \section{discussion}
@@
 {\includegraphics[height=0.5\textwidth]{fig/MBH-L_ev.pdf}}&
-\subfloat[offset in log\mbh\ (VS. \lhost) as a function of redshift]
+\subfloat[offset in  $\log($\mbh$)$ (VS. \lhost) as a function of redshift]
 {\includegraphics[height=0.5\textwidth]{fig/MBH-L-vz.pdf}}\\
@@
 
-{\color{blue}
-\subsection{The origin of the offset}
-{\color{red}[Xuheng:  Given their larger uncertainty, do we still want to present these figures?]}
-We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift.
+%{\color{blue}
+%\subsection{The origin of the offset}
+%{\color{red}[Xuheng:  Given their larger uncertainty, do we still want to present these figures?]}
+%We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift.
 We consider if the offset is related to the AGN activities.
@@
 However, at higher Eddington ratio, the offset turns to be lower.
- {\color{red} Some interpretations need to be presented.}
-
-\begin{figure*}
-\centering
-\begin{tabular}{c c}
-\subfloat[Offset of the \mbh-\smass\ relation as a function of \mbh.]
-{\includegraphics[height=0.5\textwidth]{fig/offset_vs_MBH.pdf}}&
-\subfloat[Offset of the \mbh-\smass\ relation as a function of Eddington ratio.]
-{\includegraphics[height=0.5\textwidth]{fig/offset_vs_Edd.pdf}}\\
-\end{tabular}
-\caption{\label{fig:offset_vs_MBH_edd} 
-Illustration of the offset for high-$z$ \mbh-\smass\ sample as a function of \mbh\ (left) and Eddington ratio (right).}
-\end{figure*} 
-}
+% {\color{red} Some interpretations need to be presented.}
+%}
+%\begin{figure*}
+%\centering
+%\begin{tabular}{c c}
+%\subfloat[Offset of the \mbh-\smass\ relation as a function of \mbh.]
+%{\includegraphics[height=0.5\textwidth]{fig/offset_vs_MBH.pdf}}&
+%\subfloat[Offset of the \mbh-\smass\ relation as a function of Eddington ratio.]
+%{\includegraphics[height=0.5\textwidth]{fig/offset_vs_Edd.pdf}}\\
+%\end{tabular}
+%\caption{\label{fig:offset_vs_MBH_edd} 
+%Illustration of the offset for high-$z$ \mbh-\smass\ sample as a function of \mbh\ (left) and Eddington ratio (right).}
+%\end{figure*} 
+%
 
@@
 To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}.
-In the literature, there are other local sample have been measured which also usually be considered as the local anchor.
+In the literature, other local sample have been measured which could also be considered as the local anchor.
 We note that different local samples have inconsistency which could change the result of the co-evolutions.
-
-To estimate this effect, we compare our local \mbh-\smass\ sample to the local quiescent galaxies by \citet{Kormendy13} (hereafter K13).
-We find that K13's local \mbh-\smass\ relation would raise the anchor by $\sim$0.3~dex and totally erase the offset of $\Delta\log$\mbh.
-However, we also note that the \mbh-\sigstar\ relations in K13 is also higher than the one by our local sample.
-Note that the \mbh-\sigstar\ relations by the quiescent galaxy are usually used to determine the virial coefficient for AGNs.
-That is, adopting the K13 would boost the value of our \mbh\ by $\sim$0.3~dex as well.
-As a result, our inference of the fitted offset $\gamma$ still remains at the same level.
-
-This quick comparison of the local sample highlights the need of the solid local baseline for the future studies (Bennert et al., in prep).
+To estimate this effect, we compare our local \mbh-\smass\ sample to the local ones by \citet{Kormendy13} (hereafter K13).
+We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset to our local ones, and if adopted would totally erase the offset of $\Delta\log$\mbh\ for high redshift sample.
+
+However, we also realize that the \mbh-\sigstar\ relations by K13 also have a $\sim$0.3~dex offset to the ones by \citet{Woo2010}.
+Note that it is the local \mbh-\sigstar\ relation by \citet{Woo2010} that is used to determine the virial coefficient for our active BHs.
+Thus, if adopting the K13's sample, the \mbh\ of all the AGN sample should be increased by $\sim$0.3~dex.
+As a result, the different local measurement would only affect the level of the \mbh\ globally to both local and high-$z$ sample, with the offset unchanged.
+
+We thus conclude that, if adopt K13 sample, the inference of the high redshift $\Delta\log$\mbh\ would remain at the same level.
+However, this quick comparison of the local sample highlights the need of using the solid local baseline for the future studies (Bennert et al., in prep).
 

### 2019-06-18 Comparsion/CANDELS_catalog/hist_compare_with_CANDLESCOSMOS_SSFR.py

@@ -35,7 +35,7 @@ galfit = np.loadtxt('cos_2epoch_wfc3_f160w_060mas_v1.0_galfit.cat')[:,[4,6,8,3]]
 ##The data from 3D HST
 stellar_loc = np.loadtxt('cosmos_3dhst.v4.1.cat')[:,[3,4]]  # RA, DEC
 stellar_flux_ap = np.loadtxt('cosmos_3dhst.v4.1.cat')[:,[69,51,39]]  # flux, F140w, F125w, F814w.
-stellar = np.loadtxt('cosmos_3dhst.v4.1.fout')[:,[1,6,8]]  # redshift, stellar mass, star formation rate
+stellar = np.loadtxt('cosmos_3dhst.v4.1.fout')[:,[1,6,8]]  # redshift, stellar mass, sstar formation rate
 
 ## Check if they are in a same field.
 #plt.plot(galfit_loc[:,0], galfit_loc[:,1],'.')
@@ -65,7 +65,7 @@ for i in range(len(lists)):
     result2 = galfit[lists[i][0]][2]      #Sersic n
     result3 = stellar[lists[i][1]][1]     #Stellar_mass
     result4 = galfit[lists[i][0]][3]      #flag
-    result5 = stellar[lists[i][1]][2]     #Star formation rate
+    result5 = stellar[lists[i][1]][2]     #sStar formation rate
     result6 = stellar_flux_ap[lists[i][1]][0]
     result7 = stellar_flux_ap[lists[i][1]][1]
     result8 = stellar_flux_ap[lists[i][1]][2]
@@ -138,7 +138,7 @@ ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'CDFS-321', 'CID1174
 'CID216', 'CID237','CID3242','CID3570','CID452', 'CID454',\
 'CID50','CID607','LID1273', 'LID1538','LID360','SXDS-X1136',\
 'SXDS-X50', 'SXDS-X717','SXDS-X763','SXDS-X969','XID2138','XID2202',\
-'XID2396', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597','CID1281']
+'XID2396', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597','CID1281', 'CID255']
 zs = np.asarray(load_zs(ID))
 mags = np.array(load_mag(ID, folder = '../../')[0])
[…]

### 2019-06-18 M_BH_relation/ML_all.py

@@ -125,7 +125,7 @@ MB_ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'ECDFS-321', 'CID
 zs = np.asarray(load_zs(ID))
 host_n = np.array(load_n(ID, folder = '../'))[:,0]
 lumi_s = load_host_p(ID, dm = dm)[0] #!!! This dm is important 
-MBs = load_MBH(ID,MB_ID)
+MBs = load_MBH(ID,MB_ID,if_reportHb=0   )
 plt.scatter(lumi_s,MBs,c='tomato',s=580,marker="*",zorder=100, edgecolors='k')
 LR_err = load_err(prop = 'LR', ID=ID)
 #for i in range(len(lumi_s)):

### 2019-06-18 M_BH_relation/ML_all_vz.py

@@ -125,7 +125,7 @@ mags = np.array(load_mag(ID)[0])
 
 host_n = np.array(load_n(ID, folder = '../'))[:,0]
 lumi_s = load_host_p(ID, dm = dm)[0]  #!!! This dm is important 
-MBs = load_MBH(ID,MB_ID)
+MBs = load_MBH(ID,MB_ID,if_reportHb=0)
 plt.scatter(lumi_s,MBs,c=zs,s=580,marker="*",zorder=100, vmin=0.3, vmax=2, edgecolors='k')
 LR_err = load_err(prop = 'LR', ID=ID)
 yerr_highz = [(LR_err[:,0]**2+0.4**2)**0.5, (LR_err[:,1]**2+0.4**2)**0.5]

### 2019-06-18 M_BH_relation/MM_all.py

@@ -118,5 +118,5 @@ plt.legend([Bkc,Hkc,SS13,new_sample],[
 "intermediate redshift AGNs",
 "This work"\
 ],scatterpoints=1,numpoints=1,loc=2,prop={'size':20},ncol=2)
-plt.savefig("MBH-Mstar.pdf")
+#plt.savefig("MBH-Mstar.pdf")
 plt.show()

### 2019-06-18 M_BH_relation/MM_all_vz_rest28.py

@@ -53,12 +53,12 @@ from load_result import load_zs, load_n
 ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'CDFS-321', 'CID1174',\
 'CID216', 'CID237','CID3242','CID3570','CID452', 'CID454',\
 'CID50','CID607','LID1273', 'LID1538','LID360','SXDS-X1136',\
-'SXDS-X50', 'SXDS-X717','SXDS-X969','XID2138','XID2202',\
+'SXDS-X50', 'SXDS-X717','SXDS-X763','SXDS-X969','XID2138','XID2202',\
 'XID2396', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597','CID1281','CID255']
 MB_ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'ECDFS-321', 'CID1174',\
 'CID216', 'CID237','CID3242','CID3570','CID452', 'CID454',\
 'CID50','CID607','LID1273', 'LID1538','LID360','SXDS-X1136',\
-'SXDS-X50', 'SXDS-X717','SXDS-X969','LID1820','LID1622',\
+'SXDS-X50', 'SXDS-X717','SXDS-X763','SXDS-X969','LID1820','LID1622',\
 'LID1878', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597','CID1281','CID255']
 zs = np.asarray(load_zs(ID))
 host_n = np.array(load_n(ID, folder = '../'))[:,0]

### 2019-06-18 analysis_Astrodrz/view_each_sample.py

@@ -20,12 +20,15 @@ from filter_info import filt_info, redshift_info
 #'SXDS-X50', 'SXDS-X717','SXDS-X763','SXDS-X969','XID2138','XID2202',\
 #'XID2396', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597', 'CID1281'\
 #]
+
+#ID = ['CID216']
+#ID = ['CID255']
+#ID = ['CID237']
 ID = ['SXDS-X717']
 ID = ['CID3242']
 ID = ['CDFS-1']
-ID = ['CID237']
-ID = ['CID216']
-#ID = ['CID255']
+ID = ['CDFS-229']
+ID = ['CDFS-724']
 
 
 import pickle
@@ -73,10 +76,10 @@ for j in range(len(ID)):
     weight = np.zeros(len(Chisq))
     for i in sort_Chisq[:count_n]:
         weight[i] = np.exp(-1/2. * (Chisq[i]-Chisq_best)/(Chisq_best* inf_alp))
-    for i in sort_Chisq:
+#    for i in sort_Chisq:
 #        print PSF_id[i], Chisq[i], weight[i], host_flux_ratio[i], Re[i], S_n_list[i], round(total_flux[i],3),  round(host_amp[i],3),\
 #    round(flux_dict[PSF_id[i]],3), round(FWHM_dict[PSF_id[i]],3), "[{0},{1}]".format(int(round(locs_dict[PSF_id[i]][0])) , int(round(locs_dict[PSF_id[i]][1]))), round(id_stars_dict[PSF_id[i]],3)
-        print i, round(Chisq[i],3), round(weight[i],3),round(host_amp[i],3), round(host_flux_ratio[i],1),round(Re[i], 3), round(S_n_list[i],3)
+#        print i, round(Chisq[i],3), round(weight[i],3),round(host_amp[i],3), round(host_flux_ratio[i],1),round(Re[i], 3), round(S_n_list[i],3)
 
     # =============================================================================
     # Weighting result
@@ -91,16 +94,16 @@ for j in range(len(ID)):
     rms_total_flux = np.sqrt(np.sum((total_flux-weighted_total_flux)**2*weight) / np.sum(weight))
     weighted_host_flux = np.sum(np.asarray(host_amp)*weight) / np.sum(weight)
     rms_host_flux = np.sqrt(np.sum((np.asarray(host_amp)-weighted_host_flux)**2*weight) / np.sum(weight))
-    print "ID:{0}, filt:{1}".format(ID[j], filt[0])
[…]

### 2019-06-18 code_test/sersic_n_bulgedisk_ratio.py

@@ -1,0 +1,25 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Jun 12 17:54:56 2019
+
+@author: Dartoon
+
+The sersic n and B/D ratio
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+
+def n_bulge_ratio(n):
+#    n = 5., log(B/D) = 0
+#    n = 0.5, log(B/D) = - 2.4
+    b = -1.67752801
+    a = -b/np.log10(5.)
+    logbd = a * np.log10(n) + b
+    return 10**logbd
+    
+    
+print n_bulge_ratio(5)
+print n_bulge_ratio(0.5)
+    

### 2019-06-24 manuscript/manuscript.tex
Push before John's edit

@@
 \def\jcap{Journal of Cosmology and Astroparticle Physics}
-\def\halpha{${\it H}\alpha$}
-\def\hbeta{${\it H}\beta$}
+\def\halpha{${\rm H}\alpha$}
+\def\hbeta{${\rm H}\beta$}
 \def\sersic{S\'ersic}
@@
 
-\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{1}, Daeseong Park{7}, Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
+\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{4}, Malte Schramm\altaffilmark{4}, Simon Birrer\altaffilmark{1}, Daeseong Park\altaffilmark{5}, Knud Jahnke\altaffilmark{6}, {\color{blue} Federica Duras\altaffilmark{7, 8}, Angela Bongiorno\altaffilmark{8}}
  }
@@
 \altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
-\altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
-\altaffiltext{4}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
-\altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
-\altaffiltext{6}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
-\altaffiltext{7}{\textcolor{blue}{To be updated}}
+\altaffiltext{3}{{\color{blue} Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}}
+\altaffiltext{4}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
+\altaffiltext{5}{Korea Astronomy and Space Science Institute, Deajeon, 34055, Republic of Korea}
+\altaffiltext{6}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117, Heidelberg, Germany}
+\altaffiltext{7}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
+\altaffiltext{8}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
 \begin{abstract}
 
-The correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties (e.g.
+The correlations between the mass of a supermassive black hole (SMBH) and its host galaxy properties (e.g.
 stellar mass \smass, luminosity \lhost) suggests an evolutionary connection.
@@
 The black hole mass (\mbh) is based on near-infrared spectroscopic observations of the broad \halpha~line, which avoids potential uncertainties associated with \Mgii\ or \Civ\ .
-%We enlarge the sample using previously published measurements and compare their \mbh-\smass~and \mbh-\lhost~relations to the local to infer their evolution. 
-We find that the observed ratio of \mbh/\smass ~is 0.0035, a 0.24~dex offset as compared to the local relation that would lead to a evolution as \mbh/\smass$\propto(1+z)^\gamma$ with $\gamma = 0.80\pm0.30$.
+%We find that the observed ratio of \mbh/\smass ~is 0.0035, a 0.24~dex offset as compared to the local relation that would lead to a evolution as \mbh/\smass$\propto(1+z)^\gamma$ with $\gamma = 0.80\pm0.30$.
 However, we expect an offset of 0.21 dex at these redshifts due to a selection bias thus the high-$z$ sample is consistent with the local sample if considering this effect.
@@
 In any case, the bulge \smass ~mass at a given black hole mass is clearly discrepant with the local relation, since the hosts have a significant amount of stellar mass in a disk, thus leaving the open question as to whether the connection to the bulge is relevant for black hole growth.
+{\color{blue}
+We find that the observed ratio of \mbh/\smass is larger at $z\sim1.7$ than the one in the local universe.
+However, when accounting for the selection effect (using two independent methods), we find that the high redshift points can be consistent with the local relation, assuming the scatter is unchanged or larger.
+The relationship between \mbh\ and host galaxy total luminosity paints a similar picture: the ratio is larger than the local universe, but given the uncertainties and selection effects one cannot conclude that the offset is significant.
+Therefore, given the uncertainties, our results are consistent with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former is somewhat anticipated.
+Considering that the local relationships general apply to bulges, and our hosts have a significant amount of stellar mass in a disk, observations are consistent with a scenario in which stellar mass and luminosity is transferred from the angular momentum supported to the pressure supported component of the galaxy by secular processes or minor mergers at a faster rate than that of mass accretion onto the SMBH.
+}
 
@@
 
-\keywords{galaxies: active --- galaxies: evolution}
+\keywords{galaxies: active -- galaxies: evolution}
 
@@
 Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass) and stellar velocity dispersion (\sigstar).
-These tight correlations may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
+These tight correlations (known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
 Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc).
@@
 $\sim0.23$ dex,][]{Schulze2014}.
+
 The paper is organized as follows.
@@
 
-We construct a sample of broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that meet the following criterion to overcome limitations of previous studies.
+We construct a sample of broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that meet the following criteria to overcome limitations of previous studies:
 
@@
 
-\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., H$\alpha$) which avoids potential systematic uncertainties in UV-based estimators \citep{Greene2005}.
+\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., \halpha) which avoids potential systematic uncertainties in UV-based estimators \citep{Greene2005}.
 
@@
 
-\item The large fraction of the sample has addition \hst\ imaging (i.e., \hst/ACS, providing extra color information to achieve reliable K-corrections and stellar mass determinations. 
+\item The large fraction of the sample has addition \hst\ imaging (i.e., \hst/ACS), providing extra color information to achieve reliable K-corrections and stellar mass determinations. 
 \end{itemize}
 
-\subsection{Target selection}\label{sec:target_selection}
+\subsection{Sample selection}\label{sec:target_selection}
 
@@
 Column 6: The observing start date.
+Column 7: Total exposure time.
 }
 \end{deluxetable*}
+
+\subsection{Expected bias from the selection function}
+
+\label{sec:sf_framework}
+
+Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios.
+It is well known that sample selection effects must be taken into account in order to  interpret the observed black hole-host relations and measure its evolution with redshift avoiding bias ~\citep{Schulze2011, Tre++07, Bennert++2011, Park15}.
+The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (like AGN luminosity and line strength and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors.
+
+Correcting for observational biases requires a well-characterized selection function, such as the one we have for our sample, and a model of the black hole mass function, and the evolution of the correlations between \mbh, and other properties.
+
+In order to get a sense for the amount of bias that we can anticipate given our selection function, we use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias.
+In this framework, under the assumption of no evolution of the correlations between \mbh\ and host-galaxy properties, one can compute the expected bias for a given sample, prior to observations.
+The key ingredient of this model are the local \mbh\ host-galaxy property correlations, the black hole mass function and Eddington ratio distribution at the redshift of observation.
+The latter two quantities are estimated from the type-1 AGN distributions corrected to represent the parent population of all SMBH hosts, including the inactive ones.
+
+Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model.
+{\bf TT: we should say something about the uncertainty here for example the following.} This bias correction should be considered an approximate estimate, with an uncertainty that depends on the uncertainty of the inputs.
+Furthermore, if the scaling relations actually evolve, one needs to introduce a model for the evolution in order to infer the underlying bias-corrected trends.
+We will revisit these issues in Section~\ref{select_eff}.
 
@@
 The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas.
-In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size.
+Under these assumptions, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size.
 As a result, the estimation of the \mbh\ is achieved by these measurements.
@@
 Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
-{\color{blue} 3/32 systems, including CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}.
+There are 3/32 systems (i.e.
+CDFS-1, CDFS-229 and CDFS-724) not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}.
 14/32 systems have both \halpha\ and \hbeta\ emission line information. However, we only adopt the value for \mbh\ using the \halpha\ emission line, to assure they are self-consistent.
-%Given that 18/32 sample are lack of \hbeta\ line, we thus adopt the \mbh\ estimated by \halpha\ to our sample in the rest of the work, to avoid the scatter of the \mbh\ by \hbeta\ unevenly spreading into the overall sample.
 
 We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}.
-}
 
@@
 Column 1: Object ID.
-Column 2-4: \halpha\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
-Column 5-7: \hbeta\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
-The typical uncertainty level for FWHM and $\log(\lambda \rm L)$ are $15\%$ and $\pm0.01$, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
+Column 2-5: \halpha\ emission line width (FWHM), continuum luminosity, inferred \mbh\ and Eddington ratio.
+Column 6-9: \hbeta\ emission line BH properties. 
+The typical uncertainty level for FWHM and $\log( \rm L _{\lambda})$ are $15\%$ and $\pm0.01$, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
 }
@@
 
-\subsection{Comparison sample}\label{sec:compare_sample}
+\subsection{Comparison samples}\label{sec:compare_sample}
 
@@
 To increase the local \smass\ and \mbh\ to the higher range, we also include 30 inactive galaxies (mainly ellipticals or S0) as measured by \citet{H+R04} (hereafter HR04).
-It is worth noting that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample.
-In other words, our local comparison is the \mbh-\smass$_{Bulge}$ and not those involving total quantities.
+It is worth noting that for the local comparison sample, the bulge mass is equivalent to the total stellar mass.
+In other words, our local comparison is the \mbh-\smass$_{\rm ,bulge}$ and not those involving total quantities.
 
@@
 Moreover, \citet{Bennert11, SS13} also derive the \smass\ for the 27 objects which enable us to compare to the \mbh-\smass\ relation.
-{\color{blue} In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample.
+In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample.
 
@@
 For \mbh\ estimated by \Mgii\, we adopt the recipe by \citet{Ding2017b} to recalibrate them.
-
-\section{Expected selection effect bias} \label{sec:sf_framework}
-Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios It has been known that sample selection effects could influence the observed black hole-host relations and its evolution with redshift ~\citep{Schulze2011, Tre++07, Bennert++2011, Park15}.
-In theory, the simulations~\citep{DeG++15} also find the scaling relations by the selected sample has steeper feature than by the random ones.
-To highlight this influence, we study the expected bias of the \mbh\ given our target selection in Section~\ref{sec:target_selection}.
-
-We use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias.
-Given our particular selection window (\mbh,  $L_{\rm bol}$ and Eddington ratio $\lambda$) and the local sample, the framework considers the fact that the intrinsic scatter in the BH-bulge relation has trend to decline regime of the stellar mass function, result in an average stellar masses lower than the relation.
-Moreover, the other relevant sources of bias are considered in this framework, for example the active fraction among SMBHs varies by the black hole mass function, in the sense that BHs with higher mass are less likely to be active than lower mass ones.
-
-Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$.
-
-We would correct our inference by taking this select bias into account in the result sections.
-
-%Interestingly, this bias could account for the offset that obtained in the \mbh-\smass\ correlations in Section~\ref{sec:mm}.
-We use green open circles to point out the shifting of the expected population given these biases, as shown in Figure~\ref{fig:MM-vz}.
-
-%Our conclusion is that the considering the selection effect using framework by \citet{Schulze2011}, we get consistent \mbh-\smass\ with the local sample.
-}
 
@@
 %Drizzling, background noise...
-For each of the 32 new AGNs we obtained six separate exposures with $\sim399s$ (i.e.
+For each of the 32 new AGNs, we obtained six separate exposures with $\sim399s$ (i.e.
 total exposure time $\sim2394s$).
-Table~\ref{tab:objlist} lists the details of the observation.
 The six exposures for each dither image were combined with the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted.
-We achieve to analyze this sample with a same approach, taking the 3 available frames.}.
-To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} tool.
+We achieve to analyze this sample using the same approach, taking the 3 available frames.}.
+To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} tool. We list the details of the observation in Table~\ref{tab:objlist}.
 
@@
 The final image is drizzled to 0\farcs{03} pixel scale.
-Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population %to the stellar mass budget
-which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR) \citep{Gallazzi2009} .
+Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR) \citep{Gallazzi2009} .
 
@@
 We first adopt the identified stars as candidates from the COSMOS2015 catalog by \citet{Laigle2016}.
-A lot of bright stars with intensity similar to the AGNs were excluded by \citet{Laigle2016}; in the second step, we manually select the PSF-like objects as candidates.
+A lot of bright stars with intensity similar to the AGNs were excluded by \citet{Laigle2016}; besides the COSMOS2015 catalog, we manually select the PSF-like objects as candidates.
 We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects.
@@
 Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
-For this sample, the inflation parameter $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
+For this sample, the inflation parameter $\alpha$ calculated by Equation~\ref{eq:alpha} is 16.671.
 }
@@
 \caption{\label{fig:flux_r_n_corner}
-Illustration of the relations between the inferred host \sersic\ parameters.}
+Illustration of the corner relations between the inferred host \sersic\ parameters.}
 \end{figure*}
@@
 \caption{\label{fig:hist_compare} 
-Comparison of the histogram of the inferred host flux ratio, based on the different volum of the top-ranked PSFs.}
+Comparison of the histogram of the inferred host flux ratio, based on the different the top-ranked PSFs number.}
 \end{figure*}
@@
 The host-total flux ratio of the sample are varies from 10\% to 90\% (concentrated between 20\% to 50\%).
-The effective radius and \sersic\ index are randomly distributed within the prior, rather than biased on upper/lower side.
-The inferred \Reff\ of our sample are between $\sim$1-7 kpc (peaked at $\sim$2.2kpc).
+The effective radius and \sersic\ index are randomly distributed within the prior, rather than concentrating on upper/lower side.
+The inferred \Reff\ of our sample are between $\sim$1-7~kpc (peaked at $\sim$2.2~kpc).
 15/32 systems have \sersic\ index $n<2$, indicating they are composed of disk+bulge components.
@@
 We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive} and find that our high-$z$ AGN host have very similar distribution.
-
-We calculate the rest-frame R band magnitude ($M_R$) of our sample based on their filter magnitude.
+Thus, we assume the inactive galaxies and our AGN hosts have similar bulge-total ratio so that we can infer the bulge stellar mass of our sample, as shown below.
+
 18/32 systems have multi-band host magnitude which enables us to select the best stellar population that could fit the overall sample.
 We find that the 1~Gyrs stellar population with solar metallicity by Chabrier initial mass function (IMF)~\citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples.
+Given this template, we are capable of inferring the rest-frame R band luminosity (\lhost) and stellar mass (\smass) of our sample based on their filter magnitude, in the following sections.
 
@@
 
-We visually see that in Figure~\ref{fig:MM-vz}, panel (a), most of our measurements locate within the scattering range of the local sample.
+As shown in Figure~\ref{fig:MM-vz}, panel (a), most of our measurements locate within the scattering range of the local sample.
 We doubt whether the positivity of $\gamma$ stems from the three outliers discussed in last section.
-We thus exclude these outliers and re-run the statistical analysis to see if offset still exists.
+We thus exclude these outliers and re-perform the statistical analysis to see if the offset still exists.
 As a result, we obtain that $\gamma  = 0.65 \pm 0.27$, indicating the positive evolution trend become weaker but still exists.
@@
 It is worth note that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
-That is, we are comparing the \mbh-\smass$_{,total}$ relations at the distant universe to the \mbh-\smass$_{,bulge}$ relations at local.
+That is, we are comparing the \mbh-\smass$_{,total}$ relations at the distant universe to the \mbh-\smass$_{\rm ,bulge}$ relations at local.
 Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{, bluge}$ of them are supposed to be even less.
-Given that our 32 AGNs present the similar distribution to the inactive ones in CANDLES (see Appendix~\ref{sec:comp_inactive}), we expect the bulge-total ratio could be follow the similar ratio.
-
-{\color{red}
-[Xuheng will add one more section here, about the bulge \smass\ inference and the corresponding $\gamma$, after comparing to the CANDLES data.]
+{\color{blue}
+%1. B/T can be inferred by n
+%2. The sample we use and how to build up the relation.
+%3. take the relation and infer the bulge. Finally infer the result
+%4. We note the scatter could be larger.
+Given that the inferred morphology of our 32 AGN hosts presents the similarities to the CANDELS inactive ones (see Appendix~\ref{sec:comp_inactive}), we expect their B/T follows the similar distribution which can be roughly estimated by the single-\sersic\ index \citep{Bruce2014}.
+With this estimation, we could roughly infer the bulge stellar mass of our AGN host.
+
+To this end, we first study the relations between B/T and single-\sersic\ index for CANDELS inactive galaxies at the similar mass level, i.e \smass$\in [9.0, 11.5]$, using B/T measured by \citet{Dimauro2018}.
+Then, we calculate the local averaged  B/T value at different \sersic\ index value to build up their specific relation, as shown in Figure~\ref{fig:BT-n_relation}.
+Taking this relation, we estimate the B/T of our AGN sample using the inferred \sersic\ index as proxy and infer their \smass$_{, bulge}$.
+We take this \smass$_{, bulge}$ to study their co-evolution to the \mbh.
+As expected, we find a stronger evolution trend with $\gamma = 1.71\pm0.27$.
+Of course, this is a very rough estimate --- the systematic for the estimated \smass$_{, bulge}$ must be larger than the \smass$_{, total}$.
+
+\begin{figure}
+\centering
+{
+\includegraphics[width=0.5\textwidth]{fig/BT_relation.pdf}
+}
+\caption{\label{fig:BT-n_relation} 
+The relations between stellar mass bulge-total-ratio and single-\sersic\ index by CANDELS inactive galaxies with \smass$\in [9.0, 11.5]$.
+The red curve is the inferred specific relation taking the average B/T ratio at different \sersic\ index, used as proxy to infer the B/T for our AGN sample.
+}
+\end{figure} 
 }
@@
 32 AGNs + intermediate &  0.62$\pm$0.20\\
+32 AGNs bulge only & 1.71$\pm$0.27\\
      \hline
@@
 
-\subsection{Selection effect}
+\subsection{Taking into account the selection function}
 \label{select_eff}
-In Section~\ref{sec:sf_framework}, we adopt the Bayesian framework by \citet{Schulze2011} and find that there is an expected $+0.21$~dex bias in the inferred $\Delta \log$\mbh.
-Interestingly, this bias could account for the observed offset as obtained in the \mbh-\smass\ correlations in last Section.
+
+In Section~\ref{sec:sf_framework}, we used the Bayesian framework introduced by \citet{Schulze2011} to show that in the case of no intrinsic evolution of the correlations we would expect to measure an offset corresponding to a $+0.21$~dex bias in the inferred $\Delta \log$\mbh, owing to our selection function.
+Interestingly, this bias could account for the majority of the observed offset as obtained in the \mbh-\smass\ correlations in last Section.
 %~\ref{sec:mm}.
-To make it clear, we use green open circles to point out the shifting of the expected population given these biases in Figure~\ref{fig:MM-vz}.
+To illustrate the expected bias, we use green open circles to show the corresponding shift of the observed points if one were to correct for this bias in Figure~\ref{fig:MM-vz}.
 We also show, in Figure~\ref{fig:offset_hist}, the histogram the $\Delta \log$\mbh\ by the high-$z$ sample and compare to the local ones.
-Clearly, the correction by considering this selection effect could almost mitigate the offset.
-The result of the correction shows that the high-$z$ sample could have consistent \mbh-\smass$,_{\rm host}$ to the local sample.
+The plots show that the correlations between \mbh\ and host galaxy total stellar mass or luminosity could be consistent with those of the local samples given the uncertainties and selection function
 
@@
 \caption{\label{fig:offset_hist} 
-Illustration of the histogram of the $\log($\mbh$)$ offset for the local samples and 32 high-$z$ sample.
-The gray/red vertical line shows the median value of the offset for the high-$z$ sample, before/after considering the selection effect.}
+Histogram of the $\log($\mbh$)$ offset for the local samples and our 32 high-$z$ sample.
+The gray/red vertical line shows the mean value of the offset for the high-$z$ sample, before/after considering the selection effect.
+The median value of the offset are very close to the mean value ($+0.3$).
+%TT: we need to show the mean, not the median.
+Or at least both.
+The median excludes the pull from the higher points, which are probably what drives the inference later on, so for a proper comparison we need to include both.
+}
 \end{figure}
@@
 %Our conclusion is that the considering the selection effect using framework by \citet{Schulze2011}, we get consistent \mbh-\smass\ with the local sample.
-Furthermore, we adopt an independent method to test the selection effect -- using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}.
-Following \citet{Park15, Ding2017b}, we generate the simulating samples from a combination of the local active \mbh\ function by \cite{Schulze2010} and the local samples adopted in this work.
-We then added Gaussian random noise to the simulated samples as a function of two free parameters, $\gamma$ and \sint, where \sint\ is the intrinsic scatter when considering the scaling relation as linear.
-According to the observed distribution, we consider the observational selection of \mbh\ of our samples by their lower and upper limits to model their distribution.
-To evaluate the posterior at the given $\gamma$ and \sint, for each object, we consider the likelihood of observing such object using the simulated sample, and consider whether the object would be selected or not, given the sensitivity.
-In addition, we adopt both uniform (flat) prior and lognormal prior for \sint\ (using the inference from linear fitting).
+
+In order to evaluate the ``true" underlying evolution and its uncertainty, corrected for selection effects, taking into account the actual observations, we adopt an independent method based on the approach introduced by \citet{Tre++07} and developed by \citet{Park15, Ding2017b}.
+The method parametrizes the evolution of the correlations between \mbh\ and host galaxy properties as an offset from the local one $\gamma$ and an intrinsic scatter \sint, which can be a free parameter or tied to the local relation.
+It then imposes a selection function in \mbh\ (assuming that the distribution of Eddington radio is narrow and therefore has a second order effect) and calculates the intrinsic parameters of the model given the observations.
+In practice, we start from the local black hole mass function and the evolution model, generate mock samples using a Monte Carlo approach, apply the selection function and compare with the data to generate the likelihood.
+
+To illustrate the importance of the intrinsic scatter in the selection effects, we adopt both uniform (flat) prior and lognormal prior for \sint.
 
 Combining the 32 AGNs together with the intermediate redshift sample, we present the inferred  $\gamma$ and \sint\ in the two-dimensional planes in Figure~\ref{fig:select_effect}.
-With a lognormal prior for \sint, the fitted $\gamma = 0.8\pm0.3$, consistent with the inference by the flat prior.
-These inference are consistent with the previous values without considering the selection effect in Section~\ref{sec:mm}, indicating that the evolution feature of our sample exist globally in the overall samples.
-Furthermore, we find that the final inferred scatter \sint$\sim 0.3$ are similar to the local scatter, suggesting that the scatter of the scaling relation at high redshift are similar to local ones and indicating that we have not significantly underestimated/overestimated our errors for high redshift samples.
+The plots show that the inferred evolution is uncertain and depends crucially on the intrinsic scatter.
+Assuming the lognormal prior \sint, to mimic the assumption of the method discussed in Section~\ref{sec:sf_framework}, one sees that the best estimate of $\gamma$ is positive, but the 95\% confidence intervals extend to zero.
+Thus one cannot conclude that evolution is significantly detected in our data.
+
+When relaxing the prior on \sint\ we find that the scatter is consistent with being as low as in the local samples, with a one-sided interval including zero and peaking at around 0.5~dex.
 
@@
 We show all the result of the $\gamma$ and \sint\ in Table~\ref{table:gamma_sf}.
+
+A simple check using our a-priori estimate of the bias, yields a similar result.
+The mean offset of the sample of 32 objects from the local relationship is $0.35\pm0.06$ dex, which would correspond to $\gamma=0.88\pm0.15$.
+However, after correcting for the a priori bias the offset reduces to $0.14\pm0.06$ and thus $\gamma=0.35\pm0.15$, mildly positive but not significantly so, and consistent with the a posteriori method within the error bars and the uncertainty in the correction.
+We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
+Whereas we expect the negative tail to be suppressed by our selection function, and thus it should be accounted for in our treatment, it is true that those three objects contribute a large fraction of the object.
+If one computes the median offset instead of the mean, the offset is almost completely consistent with the expected bias.
+Larger samples are needed to establish whether the positive tail is real or due to small sample statistics.
 
@@
      \hline\hline
-32 AGNs + intermediate & No & 0.74$\pm$0.21 & 0.70$\pm$0.18 \\
-32 AGNs + intermediate& Yes & 0.80 $\pm$ 0.30 & 0.60 $\pm$ 0.30 \\
-32 AGNs & No & 0.80$\pm$0.27  & 1.13$\pm$0.23\\
+32 AGNs + intermediate & No & 0.62$\pm$0.20 & 0.66$\pm$0.18 \\
+32 AGNs + intermediate& Yes & 0.80$\pm$0.30 & 0.60 $\pm$ 0.30 \\
+32 AGNs & No & 0.84$\pm$0.26  & 1.07$\pm$0.23\\
 32 AGNs& Yes & 1.30$\pm$0.50 & 1.70$\pm$0.40 \\
@@
 \caption{\label{fig:select_effect} 
-Constraining the evolution factor $\gamma$ of \mbh-\smass\ relation using Equation~\ref{eq:offset}, with intrinsic scatter \sint, using Monte Carlo simulation, by taking selection effects into account.
-The adopted sample includes 32 AGNs and the intermediate redshift AGNs, using flat prior of \sint\ (left panel) and lognormal prior (right panel).
+Taking selection effects into account, figure illustrate the constraining on the evolution factor $\gamma$ of \mbh-\smass\ relation by Equation~\ref{eq:offset}, with intrinsic scatter \sint, using Monte Carlo simulation.
+The adopted sample includes our 32 AGNs and the intermediate redshift AGNs, using flat prior of \sint\ (left panel) and lognormal prior (right panel).
 }
@@
 
-The inferred $\gamma$ here could have large systematic given the limitations in this section.
+The inferred $\gamma$ here could have large systematic given the following limitations.
 First, the passive evolution is based on a simplified correction; after all, we are not clear exactly how the host evolves to $z=0$.
@@
 \caption{\label{fig:ML-vz} 
-Same as previous figures but for \mbh-\lhost relation, considering the passive evolution correction for host galaxy luminosity.}
+Same as previous figures but for \mbh-\lhost\ relation, considering the passive evolution correction for host galaxy luminosity.}
 \end{figure*}
@@
 
-\subsection{Systematic error}
+\subsection{Systematic errors}
+
 In this work, we use the start-of-the-art techniques to derive the host flux from the AGN image.
@@
 We highlight that, in this particular paper, we focus most on the decomposing of the AGN image to present our inference of the host.
-In the mean time, we carry out a rapid analysis of the \mbh\ and host properties relations.
+With the host inference, we then carry out a rapid analysis of the \mbh\ and host properties relations.
 The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.
@@
 
-\subsection{Systematic with different local anchor}
+\subsection{Systematic errors related to the choice of local anchor}
+\label{sec:local_sys}
 To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}.
-In the literature, other local sample have been measured which could also be considered as the local anchor.
-We note that different local samples have inconsistency which could change the result of the co-evolutions.
+In the literature, some other local sample have been measured which could also be considered as the local anchor.
+We note that different local samples have inconsistency which could affect our understand of the co-evolutions.
 To estimate this effect, we compare our local \mbh-\smass\ sample to the local ones by \citet{Kormendy13} (hereafter K13).
-We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset to our local ones, and if adopted would totally erase the offset of $\Delta\log$\mbh\ for high redshift sample.
-
-However, we also realize that the \mbh-\sigstar\ relations by K13 also have a $\sim$0.3~dex offset to the ones by \citet{Woo2010}.
+We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset to our local sample.
+Note that a $+0.3$~dex difference could totally erase the $\Delta\log$\mbh\ for the high redshift sample as described in last section.
+
+However, we realize that the \mbh-\sigstar\ relations by K13 also have a $\sim$0.3~dex offset to the ones by \citet{Woo2010}.
 Note that it is the local \mbh-\sigstar\ relation by \citet{Woo2010} that is used to determine the virial coefficient for our active BHs.
 Thus, if adopting the K13's sample, the \mbh\ of all the AGN sample should be increased by $\sim$0.3~dex.
-As a result, the different local measurement would only affect the level of the \mbh\ globally to both local and high-$z$ sample, with the offset unchanged.
-
-We thus conclude that, if adopt K13 sample, the inference of the high redshift $\Delta\log$\mbh\ would remain at the same level.
-However, this quick comparison of the local sample highlights the need of using the solid local baseline for the future studies (Bennert et al., in prep).
+As a result, adopting different local measurement would only globally affect the level of the \mbh\ to local and high-$z$ sample at the same time, with the result of  $\Delta\log$\mbh\ unchanged.
+
+We thus conclude that, if adopt K13 sample, the inference of the high redshift offset of $\Delta\log$\mbh\ would remain at the same level.
+However, this quick comparison of the local sample highlights the requirement of a solid local baseline for the future studies (Bennert et al., in prep).
 
@@
 
-We used the published near-infrared spectroscopic observations \halpha\ and \hbeta\ emission lines to estimate the reliable values of BH mass.
+We used the published near-infrared spectroscopic observations \halpha\ emission lines to estimate the reliable values of BH mass.
 To obtain the properties of the AGN host galaxies, we performed the AGN image decomposition using the state-of-the-art techniques.
@@
 We obtained the host \sersic\ property (i.e., host flux, effective radius, \sersic\ index) using a weighted arithmetic mean based on the inference by the eight top-ranked PSFs.
-Incorporating with the inference by \hst/ACS image, we selected the stellar population, hence derived the rest-frame R band Luminosity (\lhost) and stellar mass of the host (\smass).
-
-Combining our high-$z$ measurements with the intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13, Cisternas2011}, we compared the scaling relations to the ones by the local with main results summarized as follows:
+Incorporating with the inference by \hst/ACS image, we selected the stellar population, hence derived the rest-frame R band Luminosity (\lhost) and stellar mass (\smass) of the host.
+
+Combining our high-$z$ measurements with the intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13, Cisternas2011}, we compared the scaling relations to the ones from the local with main results summarized as follows:
 \begin{enumerate}
-\item The \mbh-\smass\ relations at higher redshift are inconsistent with the local ones, i.e. Figure~\ref{fig:MM}, \ref{fig:MM-vz}.
-\item Considering the correction for passive evolution of galaxy luminosity, the \mbh-\lhost\ relations at higher redshift are inconsistent with the local ones,  i.e. Figure~\ref{fig:ML-vz}.
-\item The offsets of by the evolution are well described by the form $\Delta\log\mathcal M_{\rm BH}= \gamma \log (1 + z)$.
-Taking intro account selection effect, we obtain $\gamma = 0.8\pm0.3$ (\mbh-\smass) and $\gamma = 0.6\pm0.3$ (\mbh-\lhost).
-\item We compare the properties of our active galaxy sample to the ones from inactive galaxy in the CANDLES imaging survey at the same redshift range, finding no significant discrepancy among them.
+\item The \mbh-\smass\ relations at higher redshift are inconsistent with the local ones, i.e.
+Figure~\ref{fig:MM}, \ref{fig:MM-vz}.
+Considering the correction for passive evolution of galaxy luminosity, the \mbh-\lhost\ relations at higher redshift are inconsistent with the local ones,  i.e.
+Figure~\ref{fig:ML-vz} - (a).
+\item The offsets of by the evolution are well described by the form $\Delta\log\mathcal M_{\rm BH}= \gamma \log (1 + z)$. We obtain $\gamma = 0.84\pm0.26$ for \mbh-\smass\ relation.
+
+\item However, when considering the selection effect (using two independent methods), we find that the high redshift measurements can be consistent with the local relations, i.e.
+Section~\ref{select_eff}.
+
+\item Our inference indicates the evidence of disk+bulge component (i.e.
+the ones with \sersic\ $n<2$), while the local comparing samples are bulge dominated.
+We take the inferred  \sersic\ $n$ as proxy to estimate the bulge-total-ratio stellar mass.
+Comparing to their \mbh, we find a strong evolution with $\gamma = 1.71\pm0.27$.
+Thus, the conclusion seems solid that the BHs 8-10~Gyrs ago reside in bulges which are less massive/luminous than today.
+
+\item We also compare the properties of our active galaxy sample to the ones from inactive galaxy in the CANDELS imaging survey at the same redshift range, finding no significant discrepancy among them.
 \end{enumerate}
 
-Our inference indicates the evidence of disk+bluge component, i.e.
+%Our inference indicates the evidence of disk+bulge component, i.e.
 the ones with \sersic\ $n<2$, and the local comparing samples are bulge dominated sample, we hence conclude that the BHs 8-10~Gyrs ago reside in bulges, if not entire galaxies, which are less massive/luminous than today.
 
-Towards a better estimation of the evolution of the scaling relations, we need to address the limitations of this work.
-First, most of the host-total ration in the \hst/ACS band, the fidelity of the host flux are thus limited at UV.
-We thus adopt a universal stellar template to the overall galaxies based on the general inference between UV band and IR band, rather than carry out the SED fitting for each galaxy, to derive the \lhost\ and \smass.
-Second, at this moment, the local scaling relations that we current have are not yet solid.
-We have found the values of $\gamma$ could vary from 0.8 to 2.0, using different local sample from different literature \citep{Ben++10, Bennert++2011, H+R04, Kormendy13, Bentz2018}.
-Thus, a solid sample served as the local anchor still needed to be well defined (Bennert et al., in prep).
-One the other hand, comparing the observational measurements to the ones by the simulation could avoid not only the dependency to the local anchor, but also the bias by selection effect \citep{DeG++15, Khandai2015, Menci2014}.
-To overcome these limitation, we are currently incorporating our measurement with the ground-based photometry to derive SED fitting, in order to compare with the sample by simulations, which will be presented in our coming up paper.
+Towards a better estimation of the evolution of the scaling relations, we address the limitations of this work.
+First, most of the host-total ration in the \hst/ACS band are low ($<20\%$), the fidelity of the host flux are thus limited at UV band.
+In addition, when deriving the \lhost\ and \smass, we adopt a universal stellar template to the overall galaxies based on the general inference between UV band and IR band, rather than carry out the SED fitting for each galaxy.
+Second, the local scaling relations that we currently adopted are not yet solid.
+We found a 0.3 dex systematic among different local sample \citep{Ben++10, Bennert++2011, H+R04, Kormendy13, Bentz2018}.
+Tough this systematic might not raise a severe issue in our study of $\Delta\log$\mbh\ (i.e.
+Section~\ref{sec:local_sys}), a solid sample served as the local anchor is still needed (Bennert et al., in prep).
+On the other hand, comparing the observational measurements to the ones by the simulation could avoid not only the dependency to the local anchor, but also the bias by selection effect \citep{DeG++15, Khandai2015, Menci2014}.
+To overcome these limitation, we are incorporating our measurement with the ground-based photometry to derive SED fitting, in order to compare with the sample by simulations, which will be presented in the coming up paper.
 
@@
 XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
+{\color{blue} More acknowledges to be updated. }
 
@@
 \section{A. Comparison to the inactive galaxies}\label{sec:comp_inactive}
-We aim to compared the morphology of AGNs host galaxies to the inactive ones.
-From the CANDLES imaging survey.
+We compare the morphology of AGNs host galaxies to the inactive ones from the CANDELS/COSMOS imaging survey.
 we collect 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-\hst\ spectroscopic survey~\citep{Momcheva2016, Brammer2012}.
@@
 %\caption{\label{fig:Mstar-rn} 
-%The comparison of the galaxy properties between our 32 AGNs' hosts to the CANDLES sample including 4401 inactive galaxies (circles).
+%The comparison of the galaxy properties between our 32 AGNs' hosts to the CANDELS sample including 4401 inactive galaxies (circles).
 The color coding is based on the filter flux ratio between WFC3 and ACS.
-For CANDLES sample, the WFC3/F125W flux is taken.
+For CANDELS sample, the WFC3/F125W flux is taken.
 The black squares are the AGN samples with only WFC3 band observation.
@@
 %\end{figure*} 
-We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value.
+We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where we find no significant difference between their distribution and median value.
 We also compare the difference by performing the Kolmogorov-Smirnov test and inferring the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.

### 2019-06-24 Comparsion/CANDELS_catalog/hist_compare_with_CANDLESCOSMOS_SSFR.py

@@ -201,7 +201,7 @@ plt.figure(figsize=(10,6))
 #                     label=('QSO sample Reff','CANDLES-COSMOS sample Reff'))
 #plt.hist([QSO_reff, Candles_reff], **common_params)
 high0, x0, _ =plt.hist(QSO_reff, normed=True, histtype=u'step', label=('AGN sample'), linewidth = 2, color='black')
-high1, x1, _ =plt.hist(Candles_reff, normed=True, histtype=u'step',linestyle=('dashed'), label=('CANDLES sample'), linewidth = 2, color='green')
+high1, x1, _ =plt.hist(Candles_reff, normed=True, histtype=u'step',linestyle=('dashed'), label=('CANDELS sample'), linewidth = 2, color='green')
 x0_m = np.median(QSO_reff)
 high_m0 = high0[np.where(abs(x0_m-x0) == abs(x0_m-x0).min())[0][0]]
 x1_m = np.median(Candles_reff)
@@ -239,7 +239,7 @@ plt.figure(figsize=(10,6))
 #plt.legend()
 #plt.show()
 high0, x0, _ =plt.hist(QSO_n, normed=True, histtype=u'step', label=('AGN sample'), linewidth = 2, color='black')
-high1, x1, _ =plt.hist(Candles_n, normed=True, histtype=u'step', linestyle=('dashed'), label=('CANDLES sample'), linewidth = 2, color='green')
+high1, x1, _ =plt.hist(Candles_n, normed=True, histtype=u'step', linestyle=('dashed'), label=('CANDELS sample'), linewidth = 2, color='green')
 x0_m = np.median(QSO_n)
 high_m0 = high0[np.where(abs(x0_m-x0) == abs(x0_m-x0).min())[0][0]-1]
 x1_m = np.median(Candles_n)

### 2019-06-24 M_BH_relation/ML_all_vz.py

@@ -197,6 +197,7 @@ b_ml, _ =np.percentile(samples, 50,axis=0)
 #print "lnlike=",lnlike(theta=[b_ml, sint_mid],x=x, y=y, yerr=yerr)
 xl = np.linspace(0, 5, 100)
 plt.plot(xl, xl*0+xl*b_ml, color="red", linewidth=4.0,zorder=0)
+plt.plot(xl, xl*0, color="black", linewidth=2.0,zorder=0)
 
 def find_n(array,value):           #get the corresponding b for a given m 
     idx= (np.abs(array-value)).argmin()
@@ -213,6 +214,7 @@ value=round(b_ml,2)
 #####################
 value,sig=round(b_ml,2),round((np.percentile(samples,84,axis=0)[0]-np.percentile(samples,16,axis=0)[0])/2,2)
 #print value,sig
+value,sig = 0.66, 0.18
 plt.text(0.15, -1.75, "$\Delta$log$M_{BH}$=$(%s\pm%s)$log$(1+z)$"%(value,sig),color='blue',fontsize=25)
 #plt.text(0.15, -1.75, "$M_{BH} $VS$ L_{host}\propto (1+z)^{%s\pm%s}$"%(value,sig),color='blue',fontsize=25)
 ##
@@ -255,5 +257,5 @@ plt.legend([Pkc, park, new_sample],[
 "Intermediate redshift AGNs",
 "This work"
 ],scatterpoints=1,numpoints=1,loc=2,prop={'size':30},ncol=2,handletextpad=0)
-plt.savefig("MBH-L-vz.pdf")
+#plt.savefig("MBH-L-vz.pdf")
 plt.show()

### 2019-06-24 M_BH_relation/MM_all_bulge.py

@@ -1,0 +1,132 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Oct 26 15:50:27 2018
+
+@author: Dartoon
+"""
+import numpy as np
+np.set_printoptions(precision=4)
+import matplotlib.pyplot as plt
+import matplotlib as mat
+import matplotlib.lines as mlines
+from matplotlib import colors
+mat.rcParams['font.family'] = 'STIXGeneral'
+plt.figure(figsize=(11.5,12))
+
+import matplotlib as mpl
+mpl.rc('image', cmap='jet')
+
+import sys
+sys.path.insert(0,'../py_tools')
+########## input local data ####
+#==============================================================================
+# The seleting for dm and host_total and dmag are in this local
+#==============================================================================
+from local_MMstar import *
+#==============================================================================
+#input SS13 and B11 data 
+#==============================================================================
+################ bulge or total relaiton? #################
+####### input SS13 data ####
+#######in AB system, V band#######
+#inp_SS13 = 1
+#f0 ='data/SS13_MM.txt'
+#ss = np.loadtxt(f0)[:,1:]  #0 redshift; 1 M*; 2 BH mass;
+#if inp_SS13 ==1:
+#    plt.scatter(ss[:,1],ss[:,2],c='darkseagreen',marker="^",s=180,zorder=100, edgecolors='white')
+#  
+#inp_b11= 1
+#f1 ='data/B11_MM.txt'
+#b11 = np.loadtxt(f1)[:,1:]  #0 redshift; 1 M*; 2 BH mass;
+#if inp_b11 ==1:
+#    plt.scatter(b11[:,1],b11[:,2],c='darkseagreen',marker="^",s=180,zorder=100, edgecolors='white')
+#
+#inp_Cis= 1
+#f2 = 'data/Cisternas_data.txt'
+#cis11 = np.loadtxt(f2)  #0 redshift; 1 M*; 2 BH mass;
+#if inp_Cis ==1:
+#    plt.scatter(cis11[:,2],cis11[:,1],c='darkseagreen',marker="^",s=180,zorder=100, edgecolors='white')
+#
+#
+#tx, ty = 11.85, 7.
[…]

### 2019-06-27 manuscript/manuscript.tex
git push John's edit, before my edit on self-consistent estimator

@@
 \label{mbh}
+
 The \mbh\ of type-1 AGNs can be inferred using the so-called virial method~\citep{Peterson2004, Shen2013}.
 The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas.
-Under these assumptions, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size.
+Under these assumptions, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establishes an empirical scale of the BLR size.
 As a result, the estimation of the \mbh\ is achieved by these measurements.
 
-To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}.
+To avoid any systematic bias between samples in the literature, we compare the recipes implemented in \citet{Schulze2018} and \citet{Ding2017b}.
 We find that the \hbeta\ estimator is very consistent (\mbh\ r.m.s.
-$<0.03$~dex) between the two references.
-We also find that, in \citet{Schulze2018}, the cross-calibration between the \halpha\ and \hbeta\ has better agreement.
-Thus, we adopt the virial formalism from \citet{Schulze2018}:
+$<0.03$~dex) between the two reference samples.
+We also find that the cross-calibration between the \halpha\ and \hbeta\ has better agreement in \citet{Schulze2018}.
+Thus, we adopt the scheme given in \citet{Schulze2018} that is based on the recalibration of these relations using luminous quasars out to high redshift \citep{Jun2015} :
 
@@
 
-Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}.
-There are 3/32 systems (i.e.
-CDFS-1, CDFS-229 and CDFS-724) not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}.
-14/32 systems have both \halpha\ and \hbeta\ emission line information. However, we only adopt the value for \mbh\ using the \halpha\ emission line, to assure they are self-consistent.
-
-We summarized the inference of the \mbh\ together with the properties of the emission line in Table~\ref{tab:result_mbh}.
+Using these recipes, we estimate \mbh\ by adopting the emission-line properties as measured by \citet{Schulze2018} for 29 of our 32 AGNs.
+The remaining three (i.e.
+CDFS-1, CDFS-229 and CDFS-724) have information on their \halpha\ emission lines provided by \citet{Suh2015}.
+While fourteen AGN have emission line properties for both \halpha\ and \hbeta\, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample.
+It is worth noting that the absolute flux calibration of the FMOS spectra is set to match ground-based IR imaging, ULTRAVISTA in the case of COSMOS thus amounting to an effective aperture correction.
+While most recipes are calibrated against \hbeta\, the line is typically weaker than H$\alpha$, hence of lower signal-to-noise.
+We provide the \mbh\ measurements together with the properties of the emission lines in Table~\ref{tab:result_mbh}.
 
@@
 
-We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
-For comparison with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point.
-The sample by B10 consists of 19 \mbh-\lhost\ measured with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex).
-The work of B11 contains 25 \mbh-\smass\ local active AGNs, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
-To increase the local \smass\ and \mbh\ to the higher range, we also include 30 inactive galaxies (mainly ellipticals or S0) as measured by \citet{H+R04} (hereafter HR04).
+We make use of the \mbh-\lhost\ and \mbh-\smass\ relations in the literature for comparison with our high-z data.
+For the local relation, we use the measurements of \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point for local AGN samples.
+The sample by B10 consists of 19 AGN with the \mbh-\lhost\ relation determined with reliable \mbh\ masses using reverberation mapping with an uncertainty level $\sim0.15$ dex.
+The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
+To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04).
 It is worth noting that for the local comparison sample, the bulge mass is equivalent to the total stellar mass.
@@
 
-We include in our analysis published samples at intermediate redshift range to understand the redshift evolution of these correlations.
+We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations.
 We select samples that were analyzed by members of our team, in order to ensure uniform measurements.
-The intermediate redshift AGNs that we consider include, for the \mbh-\lhost\ relation, 52 objects published by \citet{Park15} at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11, SS13} at $0.5<z<1.9$.
-Moreover, \citet{Bennert11, SS13} also derive the \smass\ for the 27 objects which enable us to compare to the \mbh-\smass\ relation.
+The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$.
 In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample.
-
-Across the intermediate redshift sample, we recalibrate the \mbh\ by \halpha/\hbeta\ emission line using the self-consistent recipes introduced in Section~\ref{mbh}.
-For \mbh\ estimated by \Mgii\, we adopt the recipe by \citet{Ding2017b} to recalibrate them.
+Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh}.
+For \mbh\ estimated from \Mgii\, we adopt the recipe by \citet{Ding2017b}.
 

### 2019-07-01 manuscript/manuscript0627.tex
Edit before back to China.

--- 2019-06-27 manuscript/manuscript.tex
@@
 
-To avoid any systematic bias between samples in the literature, we compare the recipes implemented in \citet{Schulze2018} and \citet{Ding2017b}.
-We find that the \hbeta\ estimator is very consistent (\mbh\ r.m.s.
-$<0.03$~dex) between the two reference samples.
-We also find that the cross-calibration between the \halpha\ and \hbeta\ has better agreement in \citet{Schulze2018}.
-Thus, we adopt the scheme given in \citet{Schulze2018} that is based on the recalibration of these relations using luminous quasars out to high redshift \citep{Jun2015} :
+{\color{red} To avoid any systematic bias between samples in the literature, we aim to adopt a class of self-consistent estimators for our sample.
+We first compare the estimators implemented in \citet{Schulze2018} to the self-consistent ones in \citet{Ding2017b}, and find that their \hbeta(FWHM(5100)) estimators are very consistent (\mbh\ r.m.s.
+$<0.03$~dex).
+However, there is a $\sim~0.2$ dex inconsistency in their \halpha\ estimators.
+Thus, we adopt all the AGNs in \citet{Schulze2018} which have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to select the \halpha\ estimator which has better consistency.
+The result show that the \halpha\ estimators in \citet{Schulze2018} demonstrate the better agreement, which are adopted by this work:
+%Thus, we adopt the scheme given in \citet{Schulze2018} that is based on the recalibration of these relations using luminous quasars out to high redshift \citep{Jun2015} :
+
+\begin{figure}
+\centering
+{
+\includegraphics[height=0.55\textwidth]{fig/cross-calibrate.pdf}
+}
+\caption{\label{fig:cross-calibrate} 
+Cross-calibration using the AGNs in \citet{Schulze2018} for \halpha\ and \hbeta\ estimators.
+The \citet{Schulze2018} demonstrate better agreement (\mbh\ mean offset $\sim~0.09$~dex) than \citet{Ding2017b} (\mbh\ mean offset $\sim~0.27$~dex).
+{\bf Xuheng: The Jun+2015's recipe has a 0.4 dex mismatch in this comparison.}}
+\end{figure} 
+}
 
@@
 In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample.
-Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh}.
-For \mbh\ estimated from \Mgii\, we adopt the recipe by \citet{Ding2017b}.
+
+{\color{red} For all the comparison AGN samples, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh}.
+For \mbh\ estimated using \Mgii\ and  \hbeta$(\sigma_{\rm H\beta})$ lines, we adopt the recipes by \citet{Ding2017b}.
+}
 

### 2019-07-01 Comparsion/Comparison_MBHMR_scatter.py

@@ -10,7 +10,6 @@ import astropy.io.fits as pyfits
 import matplotlib.pyplot as plt
 
 #%%Define the function to fit theas linear
-
 def lfit(x,m,c):
     return m*x+c
 
@@ -20,25 +19,25 @@ def lnlike(theta, x, y, err):
     model = a * x + b
     sigma2 = (err**2 + sint**2)
     if sint>=0 :
-      return -0.5*(np.sum((y-model)**2/sigma2)+np.sum(np.log(2*np.pi*sigma2)))
+      return -0.5*(np.sum((y-model)**2/sigma2)+np.sum(np.log(sigma2))) 
     else:
       return -np.inf
-  
 nll = lambda *args: -lnlike(*args)
 #result = op.minimize(nll, [1.036, -1.947, 0.3], args=(x, y, yerr))
 #m_ml, b_ml,sint_ml= result["x"]
 
-from scipy.integrate import quad
-h0=70.             #km/s/Mpc
-om=0.3
-c=299790.        #speed of light [km/s]
-def EZ(z,om):
-      return 1/np.sqrt(om*(1+z)**3+(1-om))
-def EE(z):
-      return quad(EZ, 0, z , args=(om))[0]
-vec_EE=np.vectorize(EE)
+#from scipy.integrate import quad
+#h0=70.             #km/s/Mpc
+#om=0.3
+#c=299790.        #speed of light [km/s]
+#def EZ(z,om):
+#      return 1/np.sqrt(om*(1+z)**3+(1-om))
+#def EE(z):
+#      return quad(EZ, 0, z , args=(om))[0]
+#vec_EE=np.vectorize(EE)
 
 #%%Calculate the scatter for the Aklant MBH-Mr
+plt.figure(figsize=(8,6))
 import scipy
 h=0.7
 #r_band_magnitudes_overall=np.load('Aklant/Aklant_scripts/r_band_magnitude_overall_population.npy')
@@ -48,28 +47,75 @@ L_r = (0.4*(4.61-r_band_magnitudes_selected)) #LR in AB
 ##log10_bhmass_overall=np.load('Aklant/Aklant_scripts/log10_bhmass_overall_population.npy')
 ##log10_bhmass_overall -= np.log10(h)
[…]

### 2019-07-01 M_BH_relation/MM_all_vz_rest_ourownMBH.py

@@ -74,8 +74,6 @@ Mstar_tot = load_host_p(ID)[1]
 Mstar = Mstar_tot
 #Mstar = np.log10(10**Mstar_tot*host_BT)  #Bulge Mstar
 
-
-
 MBs = load_MBH(ID,MB_ID, if_reportHb=0)
 Mstar_err = load_err(prop = 'Mstar', ID=ID)
 yerr_highz = [(Mstar_err[:,0]**2+0.4**2)**0.5, (Mstar_err[:,1]**2+0.4**2)**0.5]

### 2019-07-01 M_BH_relation/MM_offset_hist.py

@@ -48,10 +48,11 @@ MBs = load_MBH(ID,MB_ID,if_reportHb=0)
 #Mstar_err = load_err(prop = 'Mstar', ID=ID)
 #yerr_highz = [(Mstar_err[:,0]**2+0.4**2)**0.5, (Mstar_err[:,1]**2+0.4**2)**0.5]
 #%%
-local_offset = y -(m_ml*x+b_ml)
+#local_offset = y -(m_ml*x+b_ml)
+local_offset_bloc = bloc[:,3]- (m_ml*bloc[:,1]+b_ml)
+local_offset_hloc = hloc[:,3]- (m_ml*hloc[:,1]+b_ml)
+
 highz_offset = MBs-(m_ml*Mstar+b_ml)
-
-
 
 Mstar_err = load_err(prop = 'Mstar', ID=ID)
 yerr_highz = [(Mstar_err[:,0]**2+0.4**2)**0.5, (Mstar_err[:,1]**2+0.4**2)**0.5]
@@ -61,13 +62,17 @@ yerr_hz = yerr_hz#[highz_offset<0.9]
 highz_offset = highz_offset#[highz_offset<0.9]
 
 plt.figure(figsize=(8,6))
-high0, x0, _ = plt.hist(local_offset,normed=True, histtype=u'step', linestyle=('dashed'),
-         label=('local sample'), linewidth = 2, color='gray')
+#high0, x0, _ = plt.hist(local_offset,normed=True, histtype=u'step', linestyle=('dashed'),
+#         label=('local sample'), linewidth = 2, color='gray')
+plt.hist(local_offset_bloc,normed=True, histtype=u'step', linestyle=('dashed'),
+         label=('Local by Bennert+11'), linewidth = 2, color='gray')
+plt.hist(local_offset_hloc,normed=True, histtype=u'step', linestyle=(':'),
+         label=("Local by H&R"), linewidth = 2, color='gray')
 high1, x1, _ = plt.hist(highz_offset,normed=True, histtype=u'step',
-         label=('high z sample'), linewidth = 2, color='black')
+         label=('High z sample'), linewidth = 2, color='black')
 
-x0_m = np.median(local_offset)
-high_m0 = high0[np.where(abs(x0_m-x0) == abs(x0_m-x0).min())[0][0]]
+#x0_m = np.median(local_offset)
[…]

### 2019-07-01 py_tools/load_result.py

@@ -270,8 +270,10 @@ def load_MBH(ID, MB_ID, if_reportHb=0,folder = '..', return_line = 0):
             ID_ser_dic.update({ID[j]: -99})
     MBs = []
     LogLa_list, FWHMa_list =[], []
-    CDFS_FWHMa = {'CDFS-1': 5449.4022,'CDFS-229': 2254.0105, 'CDFS-724': 3351.852239}
-    CDFS_logLHadr = {'CDFS-1': 43.08,'CDFS-229': 43.30, 'CDFS-724': 42.561413}
+#    CDFS_FWHMa = {'CDFS-1': 5449.4022,'CDFS-229': 2254.0105, 'CDFS-724': 3351.852239}  # by Hyewon
+#    CDFS_logLHadr = {'CDFS-1': 43.08,'CDFS-229': 43.30, 'CDFS-724': 42.561413} # by Hyewon
+    CDFS_FWHMa = {'CDFS-1': 2000,'CDFS-229': 2190, 'CDFS-724': 2541}  # by Malte
+    CDFS_logLHadr = {'CDFS-1': 43.02,'CDFS-229': 43.60, 'CDFS-724': 42.95} # by Malte    
     for tar_in in range(len(ID)):       
         t_name = ID[tar_in]
         ser = ID_ser_dic[t_name]
@@ -280,7 +282,8 @@ def load_MBH(ID, MB_ID, if_reportHb=0,folder = '..', return_line = 0):
             FWHM_a = float(samples[ser][8])
             logLHadr = float(samples[ser][6])
             cal_logMa = 6.71+0.48*(logLHadr-42)+2.12*np.log10(FWHM_a/1000)  # as used in Andreas
-    #        cal_logMa = 6.459+0.55*(logLHadr-42)+2.*np.log10(FWHM_a/1000)  # as used in H0liCOW 7 and McGill
+#            cal_logMa = 6.301+0.55*(logLHadr-42)+2.06*np.log10(FWHM_a/1000)  # as used in GREENE & HO 2005
+#            cal_logMa = 6.459+0.55*(logLHadr-42)+2.*np.log10(FWHM_a/1000)  # as used in H0liCOW 7 and McGill
             mbh = cal_logMa
             MBs.append(mbh)
             LogLa_list.append(logLHadr)

### 2019-07-08 manuscript/manuscript_my_conflict_version.tex
edit befor include John's comments

--- 2019-06-27 manuscript/manuscript.tex
@@
 \def\smass{{$M_*$}}
+\def\bmass{{$M_{*, bulge}$}}
 \newcommand{\Mgii}{Mg$_{\rm II}$}
@@
 \altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
-\altaffiltext{3}{{\color{blue} Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}}
+\altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
 \altaffiltext{4}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
@@
 
-The correlations between the mass of a supermassive black hole (SMBH) and its host galaxy properties (e.g.
+Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g.
 stellar mass \smass, luminosity \lhost) suggests an evolutionary connection.
-A powerful test of this co-evolution hypothesis is to measure the relations \mbh-\lhost\ and \mbh-\smass~(total) at high redshift and compare with the local relation.
-For this purpose, we obtained multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
-By applying state-of-the-art tools to decompose the \hst\ emission, we obtained accurate measurements of the host galaxy luminosity and stellar mass.
-The black hole mass (\mbh) is based on near-infrared spectroscopic observations of the broad \halpha~line, which avoids potential uncertainties associated with \Mgii\ or \Civ\ .
-%We find that the observed ratio of \mbh/\smass ~is 0.0035, a 0.24~dex offset as compared to the local relation that would lead to a evolution as \mbh/\smass$\propto(1+z)^\gamma$ with $\gamma = 0.80\pm0.30$.
-However, we expect an offset of 0.21 dex at these redshifts due to a selection bias thus the high-$z$ sample is consistent with the local sample if considering this effect.
-This is in agreement with the lack of evolution seen in the \mbh/\lhost ~ratios of our sample.
-Therefore, our results depict a scenario where SMBHs and their host galaxies co-evolve with the possibility for SMBHs to have slightly elevated masses, considering the observed ratios, that may indicate that galaxies with lower angular momentum at high-$z$ may be a bit more efficient to grow their black holes at earlier cosmic times.
-In any case, the bulge \smass ~mass at a given black hole mass is clearly discrepant with the local relation, since the hosts have a significant amount of stellar mass in a disk, thus leaving the open question as to whether the connection to the bulge is relevant for black hole growth.
-{\color{blue}
-We find that the observed ratio of \mbh/\smass is larger at $z\sim1.7$ than the one in the local universe.
-However, when accounting for the selection effect (using two independent methods), we find that the high redshift points can be consistent with the local relation, assuming the scatter is unchanged or larger.
-The relationship between \mbh\ and host galaxy total luminosity paints a similar picture: the ratio is larger than the local universe, but given the uncertainties and selection effects one cannot conclude that the offset is significant.
-Therefore, given the uncertainties, our results are consistent with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former is somewhat anticipated.
-Considering that the local relationships general apply to bulges, and our hosts have a significant amount of stellar mass in a disk, observations are consistent with a scenario in which stellar mass and luminosity is transferred from the angular momentum supported to the pressure supported component of the galaxy by secular processes or minor mergers at a faster rate than that of mass accretion onto the SMBH.
-}
+A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates.
+For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
+By applying state-of-the-art tools to decompose the \hst\ emission, we measured the host galaxy luminosity and stellar mass along with other properties through 2D model fitting.
+The black hole mass (\mbh) is determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators.
+We find that the  {\it observed} ratio of \mbh/\smass~is larger at $z\sim1.5$ by $0.31\pm0.1$ dex as compared to that in the local universe, while the scatter is as low as in the local universe.
+However, when accounting for selection effects (estimated using two independent methods), we find that no-evolution is also consistent with the data at the 95\% CL, both using our sample by itself and in combination with literature data.
+The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
+Therefore, given the uncertainties, our results are in agreement with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former is somewhat slightly anticipated.
+We then use a matched sample of inactive galaxies to estimate the bulge-to-total mass fraction and show that the bulge \mbh/\smass~relation is significantly offset from the local one, even accounting for selection effects.
+Thus, our observations are consistent with a scenario in which stellar mass and luminosity is transferred from the angular momentum supported to the pressure supported component of the galaxy through secular processes or minor mergers at a faster rate than that of mass accretion onto the SMBH.
 
@@
 Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc).
-On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering {\color{blue} either the active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or how the growth of these components is connected to the common gas supply~\citep{Cen2015, Menci2016}}.
+On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering either the active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or how the growth of these components is connected to the common gas supply~\citep{Cen2015, Menci2016}.
 On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from galaxy assembly (i.e., mergers) which can reproduce the observed correlations.
@@
 Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass\ and \mbh-\sigstar\ relations.
-Of similar results, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies; although, the accuracy of such an approach has not yet been well established.
+Of similar results, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies; although, the accuracy of such an approach for luminous AGNs has not yet been well established.
 If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.
 
-However, there are studies \citep{Cisternas2011,SS13,Mechtley2012} based on \hst\  imaging of deep survey fields such as COSMOS and CDFS that report no evolution in the \mbh - \smass ~ mass ratio as compared to the local relation.
-In support, \citet{Sun2015} has re-analyzed the mass ratios for BLAGN in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citep{Merloni2010} and finds no evolution when accounting for selection effects \citep{Schulze2014} that consider the black hole mass functions and Eddington rate distribution.
-As highlighted below, samples based on 2D image analysis using \hst\ at $z>1$ are limited thus the infrared capabilities of \hst/WFC3 have not been fully exploited to date on this topic.
-
-In order to make progress, it is important to reduce as much as possible the uncertainties and take great care of selection effects and systematic errors.
+However, there are studies \citep{Cisternas2011,SS13,Mechtley2016} based on \hst\  imaging of deep survey fields such as COSMOS and CDFS that report no evolution in the \mbh - \smass ~ mass ratio as compared to the local relation.
+In support, \citet{Sun2015} has re-analyzed the mass ratios for BLAGN in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citet{Merloni2010} and finds no evolution when accounting for selection effects, as fully described in \citet{Schulze2014} that consider the black hole mass functions and Eddington rate distribution.
+
+In order to make progress, it is important to construct statistical high-$z$ samples that reduce as much as possible the uncertainties, and carefully consider selection effects and inherent systematic errors.
 First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method.
@@
 In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to the highest redshifts where evolutionary effects should be strongest.
-In particular, we measure the properties of 32 host galaxies in redshift range $1.2<z<1.7$ using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS.
+In particular, samples based on 2D image analysis using \hst\ at $z>1$ are limited thus the infrared capabilities of \hst/WFC3 have not been fully exploited to date on this topic.
+Here, we measure the properties of 32 host galaxies in redshift range $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS.
 Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e.
@@
 The paper is organized as follows.
-We briefly describe the sample selection and the BH mass of the sample in Section~\ref{sec:data}.
-We describe the observation and collect the PSF library in Section~\ref{observation}.
+We briefly describe the sample selection and the BH masses of the sample in Section~\ref{sec:data}.
+We describe the observations and construction of a PSF library in Section~\ref{observation}.
 In Section~\ref{sec:analysis} we decompose our sample and study the host galaxy surface photometry.
-In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population, which we applied to derive the rest-frame R band \lhost\ and \smass\ and compared to the local samples.
-Discussion and conclusion are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}.
+In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population for which we apply to derive the rest-frame R-band \lhost\,~and \smass\ to compare with local relations.
+In addition, we use the information on the radial light distribution (i.e., Sersic index) to infer the likely fraction of stars in the bulge to infer the \bmass\ relation.
+The discussion and conclusions are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}.
 Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.
 Magnitudes are given in the AB system.
+A Chabrier initial mass function (IMF) is employed consistently.
 
@@
 
-We construct a sample of broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that meet the following criteria to overcome limitations of previous studies:
+We utilize a sample of broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that have black hole mass measurements available and fall within deep extragalactic survey fields that offer rich ancillary data.
+Specifically, we focused on meeting the following criteria to overcome limitations of previous studies:
 
@@
 
-\item Eddington ratios typically above 1\% for most of the sample.
-
-\item A X-ray selected sample demonstrated to have lower nuclear-to-host ratios thus facilitating the galaxy mass measurements.
-
-\item \hst/WFC3 imaging of the host galaxy above the 4000~\angstrom\ break and not including the broad \halpha\ line (6563~\angstrom).
-
-\item The large fraction of the sample has addition \hst\ imaging (i.e., \hst/ACS), providing extra color information to achieve reliable K-corrections and stellar mass determinations. 
+\item Eddington ratios typically above 1\% for most of the sample to further ensure homogeneity.
+
+\item An X-ray selected sample demonstrated to have lower nuclear-to-host ratios thus facilitating the galaxy mass measurements. This is somewhat coupled to the second item in this list.
+
+\item \hst/WFC3 imaging of the host galaxy above the 4000~\angstrom\ break and not including the broad \halpha\ line (6563~\angstrom). This ensures sensitivity to the total stellar mass content.
+
+\item A large fraction of the sample has addition \hst\ imaging (i.e., ACS), providing color information to achieve reliable K-corrections and stellar mass determinations. 
 \end{itemize}
+
+\begin{figure}
+\centering
+{
+\includegraphics[height=0.5\textwidth]{fig/AGN_selection.pdf}
+}
+\caption{\label{fig:selection} Selection window used to choose our AGN sample based on  \mbh~and Eddington ratios ($\lambda = L_{\rm Bol}/L_{\rm Edd}$).
+As indicated by the vertical red line, our sample (color coded) falls below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}.
+On the right, we illustrate the shape of the Eddington rate distribution at these redshifts from the same reference.
+For comparison, we plot the high-$z$ luminous SDSS QSO samples that have been studied with \hst\ ~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}, mainly at the high mass end.}
+\end{figure}
 
@@
 Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh.
-More recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields.
+Recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields.
 It is from this catalog that we primarily select our targets.
@@
 The bolometric luminosities presented in \citet{Schulze2018} are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
-We are able to select the sample which have higher Eddington ratios when \mbh\ is lower, to assure the AGN is still activate, as shown in Figure~\ref{fig:selection}.
-Moreover, we have higher preference to select targets which have rest-frame UV images as provided by \citet{Scoville2007}.
-We list all the AGN systems analyzed in this work (Table~\ref{tab:objlist}).
-
-%\subsection{Black hole mass and Eddington ratios}
-\begin{figure}
-\centering
-{
-\includegraphics[height=0.5\textwidth]{fig/AGN_selection.pdf}
-}
-\caption{\label{fig:selection} 
-We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($\lambda = L_{\rm Bol}/L_{\rm Edd}$) and \mbh.
-Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}.
-We also control the sample to have higher Eddington ratios when their \mbh\ is lower, to guarantee the AGN activity.
-For comparing propose, we plot the high-$z$ luminous SDSS QSO samples that has been studied based on the observation of \hst\ in the reference~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}.
-}
-\end{figure}
-
-\begin{deluxetable*}{llccccc}
-\tablecolumns{7}
-\tablewidth{0pt}
-\tablecaption{Details of Observation} 
-\tablehead{ 
-\colhead{Object ID} &
-\colhead{$z$} & 
-\colhead{WFC3/Filter} &
-\colhead{$RA$}&
-\colhead{$DEC$}&
-\colhead{Observing date}&
-\colhead{Exposure time (s)}
-\\ 
-\colhead{(1)} &
-\colhead{(2)} &
-\colhead{(3)} &
-\colhead{(4)} &
-\colhead{(5)} &
-\colhead{(6)} &
-\colhead{(7)}
-} 
-\startdata
-%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
-%\\
-COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
-COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
-COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
-COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
-COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
-COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
-COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
-COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
-COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
-COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
-COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
-COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
-COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
-COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
-COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
-COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
-COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
-COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
-COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
-COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
-COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
-CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
-CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
-CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
-CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
-ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
-SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
-SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
-SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
-SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
-SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
-SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
-\enddata
-\label{tab:objlist}
-\tablecomments{
-Column 1: Object field and ID.
-Column 2: Redshifts.
-Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
-Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
-Column 6: The observing start date.
-Column 7: Total exposure time.
-}
-\end{deluxetable*}
-
-\subsection{Expected bias from the selection function}
-
-\label{sec:sf_framework}
-
-Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios.
-It is well known that sample selection effects must be taken into account in order to  interpret the observed black hole-host relations and measure its evolution with redshift avoiding bias ~\citep{Schulze2011, Tre++07, Bennert++2011, Park15}.
-The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (like AGN luminosity and line strength and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors.
-
-Correcting for observational biases requires a well-characterized selection function, such as the one we have for our sample, and a model of the black hole mass function, and the evolution of the correlations between \mbh, and other properties.
-
-In order to get a sense for the amount of bias that we can anticipate given our selection function, we use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias.
-In this framework, under the assumption of no evolution of the correlations between \mbh\ and host-galaxy properties, one can compute the expected bias for a given sample, prior to observations.
-The key ingredient of this model are the local \mbh\ host-galaxy property correlations, the black hole mass function and Eddington ratio distribution at the redshift of observation.
-The latter two quantities are estimated from the type-1 AGN distributions corrected to represent the parent population of all SMBH hosts, including the inactive ones.
-
-Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model.
-{\bf TT: we should say something about the uncertainty here for example the following.} This bias correction should be considered an approximate estimate, with an uncertainty that depends on the uncertainty of the inputs.
-Furthermore, if the scaling relations actually evolve, one needs to introduce a model for the evolution in order to infer the underlying bias-corrected trends.
-We will revisit these issues in Section~\ref{select_eff}.
+The flux-limited nature of the sample results in higher Eddington ratios when \mbh\ is lower as shown in Figure~\ref{fig:selection}.
+Moreover, we have higher preference to select targets which have rest-frame UV images as provided by \citet{Scoville2007} and \citet{Koekemoer2007} in the COSMOS field and REFS for the (E)-CDF-S.
+We list the AGNs observed with \hst/WFC3 and analyzed in this work in Table~\ref{tab:objlist} sorted by field and redshift.
 
@@
 
-To avoid any systematic bias between samples in the literature, we compare the recipes implemented in \citet{Schulze2018} and \citet{Ding2017b}.
+%To avoid any systematic bias between samples in the literature, we compare the recipes implemented in \citet{Schulze2018} and \citet{Ding2017b}.
 We find that the \hbeta\ estimator is very consistent (\mbh\ r.m.s.
@@
 Thus, we adopt the scheme given in \citet{Schulze2018} that is based on the recalibration of these relations using luminous quasars out to high redshift \citep{Jun2015} :
+
+To avoid any systematic bias between samples in the literature, we aim to adopt a class of self-consistent estimators for our sample.
+We first compare the estimators implemented in \citet{Schulze2018} to the those in \citet{Ding2017b}, and find that their \hbeta(FWHM(5100)) estimators are very consistent (\mbh\ r.m.s.
+$<0.03$~dex).
+However, there is a $\sim~0.2$ dex inconsistency in their \halpha\ estimators.
+Thus, we utilize the AGNs in \citet{Schulze2018} that have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to determine which \halpha\ estimator has been agreement between the two lines.
+As a  result, the \halpha\ estimator in \citet{Schulze2018} has better agreement with \hbeta\  .
+Thus, we adopt the scheme given in \citet{Schulze2018} for all AGN samples used in this study including the comparison samples described below.
 
@@
 
-Using these recipes, we estimate \mbh\ by adopting the emission-line properties as measured by \citet{Schulze2018} for 29 of our 32 AGNs.
-The remaining three (i.e.
-CDFS-1, CDFS-229 and CDFS-724) have information on their \halpha\ emission lines provided by \citet{Suh2015}.
+Using these recipes, we estimate \mbh\ by adopting the emission-line properties as measured by \citet{Schulze2018} for all 32 AGNs.
+The three objects (i.e.
+CDFS-1, CDFS-229 and CDFS-724) have infrared spectra provided by \citet{Suh2015}.
 While fourteen AGN have emission line properties for both \halpha\ and \hbeta\, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample.
@@
 
-\begin{deluxetable*}
-{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
-\tablecolumns{9}
-\tablewidth{0pt}
-\tablecaption{Inferred BH properties for the 32 systems} 
-\tablehead
-{ 
-\colhead{Target ID}&
-  \multicolumn{4}{c}{using emission line \halpha}&
-  \multicolumn{4}{c}{using emission line \hbeta} \\
-  \cline{2-5}  \cline{6-9} \\
-\colhead{}& 
-\colhead{FWHM}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
-\colhead{FWHM(5100)}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
-\colhead{}& 
-\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
-\colhead{(M$_{\odot}$)}& (log$\lambda$)&
-\colhead{(\kms)}& 
-\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$\lambda$)\\
-\colhead{(1)}& 
-\colhead{(2)}& \colhead{(3)}& 
-\colhead{(4)}& \colhead{(5)}& 
-\colhead{(6)}&\colhead{(7)}&
-\colhead{(8)}& \colhead{(9)}
-}
-\startdata 
-CID1174 & 1906 & 43.43 & 7.99 & -0.50 & 5898 & 44.76 & 8.83& -1.35 \\
-CID1281 & 1619 & 43.24 & 7.75 & -0.45 & ... & ... & ...& ... \\
-CID206 & 3334 & 43.48 & 8.53 & -1.00 & ... & ... & ...& ... \\
-CID216 & 2230 & 42.85 & 7.85 & -0.93 & ... & ... & ...& ... \\
-CID237 & 2112 & 43.86 & 8.29 & -0.40 & ... & ... & ...& ... \\
-CID255 & 1932 & 43.99 & 8.27 & -0.25 & 3709 & 45.37 & 8.73& -0.63 \\
-CID3242 & 2543 & 43.83 & 8.45 & -0.58 & 3775 & 45.10 & 8.61& -0.78 \\
-CID3570 & 1959 & 43.16 & 7.89 & -0.66 & ... & ... & ...& ... \\
-CID452 & 3458 & 42.92 & 8.30 & -1.30 & 3127 & 44.63 & 8.22& -0.88 \\
-CID454 & 2824 & 43.34 & 8.31 & -0.91 & ... & ... & ...& ... \\
-CID50 & 2340 & 43.94 & 8.42 & -0.45 & 1939 & 45.33 & 8.15& -0.09 \\
-CID543 & 2189 & 43.57 & 8.19 & -0.56 & ... & ... & ...& ... \\
-CID597 & 1656 & 43.33 & 7.81 & -0.42 & ... & ... & ...& ... \\
-CID607 & 3009 & 43.67 & 8.53 & -0.81 & 4242 & 44.78 & 8.56& -1.06 \\
-CID70 & 2480 & 43.51 & 8.27 & -0.71 & 3982 & 45.16 & 8.69& -0.80 \\
-LID1273 & 3224 & 43.61 & 8.56 & -0.90 & ... & ... & ...& ... \\
-LID1538 & 2941 & 43.60 & 8.47 & -0.83 & ... & ... & ...& ... \\
-LID360 & 2482 & 43.88 & 8.45 & -0.53 & 2869 & 45.09 & 8.37& -0.55 \\
-XID2138 & 3186 & 43.61 & 8.55 & -0.89 & 2945 & 44.81 & 8.25& -0.72 \\
-XID2202 & 2973 & 43.56 & 8.46 & -0.85 & ... & ... & ...& ... \\
-XID2396 & 2271 & 44.06 & 8.46 & -0.37 & 2658 & 45.50 & 8.51& -0.27 \\
-CDFS-1 & 5449 & 43.08 & 8.79 & -0.98 & ... & ... & ...& ... \\
-CDFS-229 & 2254 & 43.30 & 8.08 & -0.48 & ... & ... & ...& ... \\
-CDFS-321 & 2442 & 43.93 & 8.46 & -0.50 & ... & ... & ...& ... \\
-CDFS-724 & 3352 & 42.56 & 8.09 & -1.22 & ... & ... & ...& ... \\
-ECDFS-358 & 2237 & 43.40 & 8.12 & -0.67 & ... & ... & ...& ... \\
-SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.85 & 6761 & 44.71 & 8.93& -1.50 \\
-SXDS-X50 & 1817 & 43.42 & 7.94 & -0.47 & ... & ... & ...& ... \\
-SXDS-X717 & 2931 & 43.05 & 8.20 & -1.08 & ... & ... & ...& ... \\
-SXDS-X735 & 2702 & 43.70 & 8.44 & -0.70 & 3520 & 45.07 & 8.54& -0.73 \\
-SXDS-X763 & 2961 & 43.57 & 8.47 & -0.84 & 4509 & 44.51 & 8.47& -1.27 \\
-SXDS-X969 & 2296 & 43.50 & 8.20 & -0.64 & 1696 & 45.05 & 7.90& -0.11 \\
-\enddata
-\label{tab:result_mbh}
-\tablecomments{
-Column 1: Object ID.
-Column 2-5: \halpha\ emission line width (FWHM), continuum luminosity, inferred \mbh\ and Eddington ratio.
-Column 6-9: \hbeta\ emission line BH properties. 
-The typical uncertainty level for FWHM and $\log( \rm L _{\lambda})$ are $15\%$ and $\pm0.01$, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
-}
-\end{deluxetable*}
+\subsection{Expected bias from the selection function}
+
+\label{sec:sf_framework}
+
+Our AGN sample is primarily selected based on the value of \mbh~and Eddington ratio.
+It is well known that sample selection effects must be taken into account in order to  interpret the observed black hole-host relations and measure its evolution with redshift thus avoiding well understood biases ~\citep{Tre++07,Schulze2011,Bennert++2011, Schulze2014,Park15}.
+The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (like AGN luminosity and line strength and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors.
+Correcting for observational biases requires a well-characterized selection function, such as the one we have for our sample, and a model of the black hole mass function, and the evolution of the correlations between \mbh, and other properties.
+
+To assess the amount of bias that we can anticipate given our selection function, we use the Bayesian framework introduced by \citet{Schulze2011,Schulze2014} to estimate the expected bias.
+In this framework, under the assumption of no evolution of the correlations between \mbh\ and host-galaxy properties, one can compute the expected bias for a given sample, prior to the observations.
+The key ingredient of this model are the local \mbh\ host-galaxy property correlations, the black hole mass function and Eddington ratio distribution at the redshift of observation.
+The latter two quantities are estimated from the type-1 AGN distributions \citep{Schulze2015} and corrected to represent the parent population of all active SMBH hosts thus including the obscured cases.
+
+Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model.
+{\bf TT: we should say something about the uncertainty here for example the following.} This bias correction should be considered an approximate estimate, with an uncertainty that depends on the uncertainty of the inputs.
+Furthermore, if the scaling relations actually evolve, one needs to introduce a model for the evolution in order to infer the underlying bias-corrected trends.
+We will revisit these issues in Section~\ref{select_eff}.
 
@@
 
-We make use of the \mbh-\lhost\ and \mbh-\smass\ relations in the literature for comparison with our high-z data.
+We make use of the \mbh-\lhost\ and \mbh-\smass\ relations in the literature for comparison with our high-$z$ data.
 For the local relation, we use the measurements of \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point for local AGN samples.
@@
 We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations.
-We select samples that were analyzed by members of our team, in order to ensure uniform measurements.
+We select samples that were analyzed by members of our team, to ensure uniform measurements.
 The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$.
@@
 For \mbh\ estimated from \Mgii\, we adopt the recipe by \citet{Ding2017b}.
+For all comparison AGN samples, we recalibrate the \mbh\ using the recipes given in Section~\ref{mbh}.
+For \mbh\ estimated using the \Mgii\ and  \hbeta$(\sigma_{\rm H\beta})$ lines, we adopt the recipes by \citet{Ding2017b}.
 
@@
 % The AGN surface photometry in IR Channel Filters.\\
-High spatial resolution imaging is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass.
-For this purpose, all the new 32 AGN systems were observed with the \hst/WFC3 infrared channel, as part of the \hst\ program GO-15115, PI: John Silverman.
-We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets.
-This selection ensures that the broad \halpha\ line is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.
+High spatial resolution imaging is required for the decomposition of the nuclear and host emission to accurately estimate the luminosity and stellar mass of the host galaxy.
+For this purpose, we observed the sample of 32 AGNs, as described above, with the \hst/WFC3 infrared channel, through the \hst\ program GO-15115 (PI: John Silverman).
+We elected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets so that the rest-frame spectral window was well above the 4000~\angstrom\ break.
+This selection further ensures that the broad \halpha\ line is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.
 
 %Drizzling, background noise...
-For each of the 32 new AGNs, we obtained six separate exposures with $\sim399s$ (i.e.
-total exposure time $\sim2394s$).
-The six exposures for each dither image were combined with the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted.
+For each target, we obtained six separate exposures of {\bf 399s (i.e., total exposure time 2394s)}.
+The six exposures were dithered and combined with the {\sc astrodrizzle} software package that resulted in an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 and using a \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted.
 We achieve to analyze this sample using the same approach, taking the 3 available frames.}.
-To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} tool. We list the details of the observation in Table~\ref{tab:objlist}.
+We use the {\sc photutils} tools to accurately estimate the background light which could come from both the sky and the detector.
+In Table~\ref{tab:objlist}, we list the details of the individual observations.
 
 Multi-band information provides the SED at a more precise level.
-21/32 objects in our sample have rest-frame UV images by \citet{Scoville2007}.
-Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures.
+A substantial fraction (21/32) of our objects have rest-frame UV images for those in COSMOS \citep{Koekemoer2007} and CDFS.
+Here, we utilize images taken with ACS/F814W filter.
 The final image is drizzled to 0\farcs{03} pixel scale.
-Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR) \citep{Gallazzi2009} .
+Given the multi-band images for our AGN, we are able to infer their host color and assess the contribution of both the young and old stellar population which insures an accurate inference of rest-frame R-band luminosity (including a K-correction) and stellar mass \citep{Gallazzi2009}.
 
@@
 %Introduce the PSF library
-The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the point source is bright relative to the host.
-The PSF is known to be vary across the detector and with time, due to the effects of aberrations and breathing.
-Simulated PSF, such as {\sc TinyTim} ones, are usually insufficient matches to observations for our purposes \citet{Mechtley2012}.
-Stars within the fields provide a better description than the simulated PSF, since they were observed simultaneously with the science targets and reduced and analyzed in the same way \citet{Kim2008, Park15}
-
-To minimize the impact of the mismatch, we build a PSF library by selecting all the isolated, unsaturated PSF-stars with high S/N from our entire program.
+
+The knowledge of the PSF is crucial for imaging decomposition of the AGN and its host, especially when the point source contributes to the majority of the total emission.
+The PSF is known to vary across the detector and in time due to the effects of aberration and breathing.
+Simulated PSF, such those based on {\sc TinyTim}, are usually insufficient for our purposes \citep{Mechtley2012}.
+Stars within the field-of-view of each observation provide a better description than the simulated PSF since they are observed simultaneously with the science targets, and reduced and analyzed in a consistent manner \citet{Kim2008, Park15}.
+{\bf Actually, we have found that such stars do not provide an ideal PSF for de-blending the AGN and host galaxy through extensive tests.
+The issues have to due with an insufficient number of bright stars near our targets, color differences, and other effects not fully understood.}
+
+To minimize the impact of such mismatches, we build a PSF library by selecting all the isolated, unsaturated PSF-stars with high S/N from our entire program.
 The selection consists of the following steps.
-We first adopt the identified stars as candidates from the COSMOS2015 catalog by \citet{Laigle2016}.
-A lot of bright stars with intensity similar to the AGNs were excluded by \citet{Laigle2016}; besides the COSMOS2015 catalog, we manually select the PSF-like objects as candidates.
-We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects.
-In the end, the PSF library contains 78 and 37 PSFs imaged through filters F140W and F125W, respectively.
-
+First, we identify stars from the COSMOS2015 catalog \citep{Laigle2016}.
+Unfortunately, many bright stars with an intensity similar to our AGN sample were excluded in this catalog.
+Therefore, we manually select PSF-like objects as candidates from the HST/WFC3 imaging.
+We then discard non-ideal PSF candidates based on their intensity, FWHM, central symmetry, and presence of nearby contaminants.
+In total, the PSF library contains 78 and 37 stars imaged through filters F140W and F125W, respectively.
 We assume that the stars in the library are representative of the possible PSFs in our program.
-Therefore, the PSF library gives a good representation of the dominant source of uncertainty as well as the best fit.
+The dispersion of PSF shapes within our library provides us with a good representation of the level of uncertainty in our measurements resulting from the image decomposition.
 %In the next subsection, we carry out the AGN decomposition using each PSF.
@@
 %\subsubsection{Surface Photometry modeling method}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
+\caption{\label{fig:AGN_decomp} AGN-host galaxy decomposition of COSMOS-CID1174 based on the HST/WFC3 F140W image.The panels from left to right are as follows: (1) observed data, (2) best-fit model (AGN+host), (3) data minus the model PSF (i.e., host galaxy free of the AGN), (4) residuals divided by the variance and (5) 1-D surface brightness profiles (top) and the corresponding residual (bottom).
+The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects).
+Note that the 1-D surface brightness profiles are only for illustration purposes.
+The actual fitting is based on the two-dimensional images.
+The remaining 31 objects in the sample are shown in Appendix~\ref{sec:restsample}.
+}}
+\end{figure*}
+
 \section{AGN-host Decomposition}
@@
 %Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
-We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underlying host galaxy.
-Following common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile.
-Note that the actual morphologies of the host galaxies could be more complicated (e.g.
-bulge+disk).
-However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux, given the high redshift range of our sample.
-Furthermore, we fit other galaxies that happen to be close to the AGN as additional \sersic\ model, to account for any potential contamination.
-The systems CID206 and ECDFS-358 have nearby objects which could not be described by \sersic\ model, we thus mask these objects in the fitting.
+We simultaneously fit the two-dimensional flux distribution of the central AGN and the underlying host galaxy.
+Following common practice, we model the central AGN as a scaled point source and the host galaxy as a \sersic\ profile.
+Note that the actual morphologies of the host galaxies could be more complicated (e.g., bulge+disk).
+However, the \sersic\ model is an adequate first-order approximation of the surface brightness distribution with a flexible parameterization that provides sufficient freedom to infer the total host flux even for our high redshift sample.
+We simultaneously fit the nearby galaxies, that happen to be close enough to the AGN, with a \sersic\ model to account for any potential contamination from their extended profiles.
+The systems CID206 and ECDFS-358 have nearby objects which could not be described by \sersic\ model thus we mask these objects in the fitting procedure.
 
 %Introduce Lenstronomy:
-We adopt the imaging modeling tool \lenstronomy~\citep{lenstronomy} to perform the decomposition of the host and nuclear light.
-\lenstronomy\ is a multi-purpose open-source gravitational lens image modeling python package.
-Its flexibility enables us to turn off the lensing channel and focus on the AGN decomposition\footnote{For a sanity check, we compared the performance of \lenstronomy\ to the most commonly used galaxy modeling software {\sc Galfit} and confirm that the consistent result could be obtained with the same fitting ingredients provided.}.
-The maim advantage over {\sc Galfit} is that \lenstronomy\ returns the full posterior of the parameter and not just the best fit model and the Laplace approximation of the uncertanties.
+We use the image modeling tool \lenstronomy~\citep{lenstronomy} to perform the decomposition of the host and nuclear light.
+\lenstronomy\ is a multi-purpose open-source gravitational lens image forward-modeling package written in Python.
+Its flexibility enables us to turn off the lensing channel and focus on the AGN and host decomposition\footnote{As a check, we compared the results from \lenstronomy\ to the commonly used galaxy modeling software {\sc Galfit} and confirm that the results are consistent between the two.}.
+The main advantage of \lenstronomy\ is that it returns the full posterior distribution of each parameter (i.e., not just the best fit model) and the Laplace approximation of the uncertainties.
 The input ingredients to \lenstronomy\ include:
@@
 \item AGN imaging data. \\
--- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ covers sufficient AGN light our samples.
-By default, we cut out the AGN image to a $61\times61$ pixels box (i.e.
+-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample.
+By default, we extract an image of $61\times61$ pixels (i.e.
 $4''\times 4''$).
-If needed, the larger size box would be sufficient to include the nearby objects.
+If needed, a larger box size would be sufficient to include nearby objects.
 \item Noise level map.\\
--- The origin of the noise in each pixel stems from the read noise, background noise and Poisson noise by the astronomical sources themselves.
-To take them into account, we measure the read noise and background noise level directly from the empty regions of the data.
-We calculate the effective exposure time of each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level.
+-- The origin of the noise in each pixel stems from the read noise, background noise, and Poisson noise from the astronomical sources themselves.
+We measure these directly from the empty regions of the data.
+We then calculate the effective exposure time of each pixel based on the drizzled \texttt{WHT} array maps to infer the Poisson noise level.
+A final noise map includes all of these sources of error.
+
 \item PSF. \\
--- 
-The PSF is directly taken from the PSF library.
+-- The PSF is directly taken from the PSF library.
 Usually, a mismatch exists when subtracting the AGN as the scaled PSF, especially at the central parts.
@@
 %Introduce the final inference using fitting:
-The host properties of one AGN system is inferred via the following steps.
+
+The host property of an AGN is determined by the following steps.
 First, we model the AGN and host using each PSFs in the library.
-Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC.
-In our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow.
-Thus, we only take the best-fit inference using PSO for the further calculations.}.
-To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$.
-Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs.
-We infer the host \sersic\ parameters (i.e., host flux, \Reff, \sersic\ index) using a weighted arithmetic mean.
-The weight is calculated by:
+With the input ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC.
+In our case, given a fixed PSF, the $1\sigma$ inference of each parameter is extremely narrow.
+Thus, we only take the best-fit inference using PSO for further calculations.
+The errors on the fit parameters are assessed by using different PSFs for each object in the sample.}.
+To avoid any unphysical results, we set the upper and lower limits on the parameters: effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, \sersic\ index $n\in[1,7]$.
+Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best-fit PSFs.
+We determine the host \sersic\ parameters (i.e., flux, \Reff, \sersic\ index) using a weighted arithmetic mean, calculated as follows:
+
 \begin{eqnarray}
@@
 The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties.
-The answers would not change significantly if we had chosen a different number of PSFs, as we show below.
-
-Note that since each AGN system was observed in different location of the detector and at a different time, the top-eight PSFs usually vary from one AGN system to another.
-Given the weights, the inferred value of host properties and the root-mean-square ($\sigma$) are calculated as:
+The results do not change significantly if we chose a different number of PSFs, as shown below.
+
+Note that since each AGN was observed in different location of the detector and at a different time, the top-eight PSFs usually vary from one AGN to another.
+Given the weights, the value of host properties and the root-mean-square ($\sigma$) error are calculated as:
 \begin{eqnarray}
@@
 
-In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e.
-host) and the residuals, taking COSMOS-CID1174 as an example.
-The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}.
-
-\begin{figure*}
-\centering
-%\hspace{-5.5em}
-{
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
-\caption{\label{fig:AGN_decomp} 
-Figure illustrates the inference for the 32 objects based on the WFC3 images.
-In each row, observed data (first column), best-fit models (second column), data subtracted by the inferred point source (third column),  normalized residuals (fourth column) are presented together with the target ID.
-In the fifth column, we present the 1-D surface brightness profiles (top) and the corresponding residual (bottom).
-The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects).
-Note that the one-dimensional surface brightness profiles are only for illustration purposes.
-The actual fitting is based on the two-dimensional images.
-The remaining 31 objects of the sample are shown in Appendix~\ref{sec:restsample}.
-}}
-\end{figure*}
-
-\begin{deluxetable*}{ccccccc}
-\tablecolumns{7}
-\tablewidth{0pt}
-\tablecaption{Host inference of CID1174} 
-\tablehead{ 
-\colhead{PSF rank} &
-\colhead{total $\chi ^2$} & 
-\colhead{weights $w_i$} &
-\colhead{host flux (counts)} &
-\colhead{host flux ratio}&
-\colhead{\Reff (arcsec)}&
-\colhead{\sersic\ $n$}
- \\ 
-\colhead{(1)} &
-\colhead{(2)} &
-\colhead{(3)} &
-\colhead{(4)} &
-\colhead{(5)} &
-\colhead{(6)} &
-\colhead{(7)} 
-} 
-\startdata
-%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
-%\\
-1 & $8584.429$ & $1.000$ & $82.2$ & $35\%$ & $0\farcs{}345$ & $1.1$ \\
-2 & $8646.711$ & $0.920$ & $99.1$ & $42\%$ & $0\farcs{}298$ & $1.9$ \\
-3 & $8816.947$ & $0.734$ & $76.7$ & $33\%$ & $0\farcs{}365$ & $1.1$ \\
-4 & $9304.841$ & $0.383$ & $128.6$ & $55\%$ & $0\farcs{}231$ & $2.8$ \\
-5 & $9652.575$ & $0.241$ & $187.5$ & $79\%$ & $0\farcs{}116$ & $6.2$ \\
-6 & $9917.101$ & $0.170$ & $100.2$ & $42\%$ & $0\farcs{}287$ & $2.1$ \\
-7 & $10018.324$ & $0.148$ & $75.1$ & $32\%$ & $0\farcs{}365$ & $1.2$ \\
-8 & $10087.456$ & $0.135$ & $79.8$ & $34\%$ & $0\farcs{}358$ & $1.2$ \\
-\hline\\
-Weighted value & & & $97.322\pm28.336$ & $42\%\pm12\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.9\pm1.3$  \\
-\enddata
-\label{tab:weight_CID1174}
-\tablecomments{
-Column~1: Rank of the PSF from the library.
-Column~2: Total $\chi ^2$ for the corresponding PSF.
-Column~3: Weights for the inference.
-Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
-For this sample, the inflation parameter $\alpha$ calculated by Equation~\ref{eq:alpha} is 16.671.
-}
-\end{deluxetable*}
-
-\begin{figure*}
-\centering
-{
-\includegraphics[height=0.75\textwidth]{fig/flux_r_n_corner.pdf}
-}
-\caption{\label{fig:flux_r_n_corner}
-Illustration of the corner relations between the inferred host \sersic\ parameters.}
-\end{figure*}
-
-We apply this approach to the overall AGN systems to infer the overall host galaxy information.
-To quickly overview, we plot the relations of the properties between effective radius (\Reff), \sersic\ index and host to total flux ratio in Figure~\ref{fig:flux_r_n_corner} and leave the detail descriptions in the next Section.
-We realize that the inference of the host properties is weighted by eight top-ranked PSFs.
-The smaller volume of top-ranked  PSFs would possibly underestimate the uncertainties of the inference.
-To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the inference by using five and ten top-ranked PSFs.
-As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference has been solid when the amount of selected PSF exceeds five.
-
-\begin{figure*}
-\centering
-{
-\includegraphics[height=0.35\textwidth]{fig/hist_compare.pdf}
+\noindent In Figure~\ref{fig:AGN_decomp}, we demonstrate the results for COSMOS-CID1174. The adopted weights are listed in Table~\ref{tab:weight_CID1174}.
+
+%\begin{figure*}
+%\centering
+%{
+%\includegraphics[height=0.5\textwidth]{fig/flux_r_n_corner.pdf}
+%}
+%\caption{\label{fig:flux_r_n_corner}
+%Relations between the measured host galaxy parameters.}
+%\end{figure*}
+
+We apply this approach to all AGNs to determine the global characteristics of the hosts of type 1 AGNs at these high redshifts.
+We measure the effective radius (\Reff), \sersic\ index and host-to-total flux ratio and describe each of these in the following section.
+We recognize that these measurements are weighted by the eight top-ranked PSFs.
+The limited number of top-ranked PSFs may underestimate actual uncertainties.
+To gauge how the number of top-ranked PSF affects our results, we compare results when also using five and ten top-ranked PSFs.
+As shown in Figure~\ref{fig:hist_compare}, the results are consistent.
+
+\begin{figure}
+\centering
+{
+\includegraphics[height=0.25\textwidth]{fig/hist_compare.pdf}
 }
 \caption{\label{fig:hist_compare} 
-Comparison of the histogram of the inferred host flux ratio, based on the different the top-ranked PSFs number.}
-\end{figure*}
+Distribution of the host-to-total flux ratio when implementing a different number of top-ranked PSFs.}
+\end{figure}
 
 %The inference of F814w data.
-18/32 systems in the COSMOS field have ACS/F184W imaging data.
-We infer their host flux ratio using the same approach used for the WFC3-IR.
-The field of view by ACS are larger than WFC3, hence we collected in total 174 ACS PSFs in the library.
-In principle, the host inference by IR band is superior to the one by UV band, giving that the effects of dust extinction and contrast between the (blue) AGN and (red) host.
-Thus, we fix the \Reff\ and \sersic\ $n$ as the value inferred by IR band, assuming that the morphology of the galaxy is consistent between ACS and WFC3.
-
-We list all the inference of the host galaxy properties in the Table~\ref{tab:result_sersic}.
-
-\tabcolsep=0.03cm
-\begin{deluxetable*}
-{@{\extracolsep{4pt}}lcccccccccc}   % need for the gap between the clines.
-\tablecolumns{9}
-\tablewidth{0pt}
-\tablecaption{Inferred host galaxy properties for the 32 systems.} 
-\tablehead
-{ 
-\colhead{Target ID}&
-  \multicolumn{5}{c}{WFC3}&
-  \multicolumn{3}{c}{ACS/F814W} &
-   \multicolumn{2}{c}{host properties} \\
-  \cline{2-6}  \cline{7-9} \cline{10-11}  \\
-\colhead{}& 
-\colhead{reduced $\chi ^2$}& \colhead{host-total flux ratio}& 
-\colhead{\Reff}& \colhead{\sersic\ $n$}& 
-\colhead{magnitude}&
-\colhead{reduced $\chi ^2$}& \colhead{host-total flux ratio}& \colhead{magnitude} &
-\colhead{$\log L_R$} &\colhead{$\log M_*$} \\
-\colhead{}& 
-\colhead{}& \colhead{}& 
-\colhead{($\arcsec$)}& \colhead{}& 
-\colhead{(AB system)}& \colhead{}& 
-\colhead{}& \colhead{(AB system)} &\colhead{($L_{\odot,R}$)} & \colhead{(M$_{\odot}$)}\\
-\colhead{(1)}& 
-\colhead{(2)}& \colhead{(3)}& 
-\colhead{(4)}& \colhead{(5)}& 
-\colhead{(6)}& \colhead{(7)}& 
-\colhead{(8)}& \colhead{(9)}&
-\colhead{(10)}& \colhead{(11)}
-}
-\setlength{\tabcolsep}{20pt}
-\renewcommand{\arraystretch}{1.5}
-\startdata 
-CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.05\substack{+0.15\\-0.11}$ &$10.78\substack{+0.18\\-0.15}$\\[3pt]
-CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.41\substack{+0.15\\-0.11}$ &$10.14\substack{+0.18\\-0.15}$\\[3pt]
-CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.86\substack{+0.52\\-0.23}$ &$10.59\substack{+0.53\\-0.25}$\\[3pt]
-CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.05\substack{+0.03\\-0.03}$ &$10.78\substack{+0.10\\-0.10}$\\[3pt]
-CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.18\substack{+0.11\\-0.09}$ &$10.91\substack{+0.14\\-0.13}$\\[3pt]
-CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.08\substack{+0.15\\-0.11}$ &$10.81\substack{+0.18\\-0.15}$\\[3pt]
-CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.16\substack{+0.14\\-0.11}$ &$10.89\substack{+0.17\\-0.15}$\\[3pt]
-CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $10.98\substack{+0.02\\-0.02}$ &$10.71\substack{+0.10\\-0.10}$\\[3pt]
-CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.13\substack{+0.03\\-0.03}$ &$10.86\substack{+0.10\\-0.10}$\\[3pt]
-CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.11\substack{+0.04\\-0.04}$ &$10.84\substack{+0.10\\-0.10}$\\[3pt]
-CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.07\substack{+0.35\\-0.19}$ &$10.80\substack{+0.36\\-0.21}$\\[3pt]
-CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.70\substack{+0.16\\-0.12}$ &$10.43\substack{+0.19\\-0.15}$\\[3pt]
-CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.73\substack{+0.22\\-0.15}$ &$10.46\substack{+0.24\\-0.18}$\\[3pt]
-CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.02\substack{+0.23\\-0.15}$ &$10.75\substack{+0.25\\-0.18}$\\[3pt]
-CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $10.98\substack{+0.12\\-0.10}$ &$10.72\substack{+0.16\\-0.14}$\\[3pt]
-LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.32\substack{+0.09\\-0.07}$ &$11.05\substack{+0.13\\-0.12}$\\[3pt]
-LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.12\substack{+0.09\\-0.08}$ &$10.86\substack{+0.13\\-0.12}$\\[3pt]
-LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.08\substack{+0.06\\-0.05}$ &$10.81\substack{+0.11\\-0.11}$\\[3pt]
-XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.89\substack{+0.07\\-0.06}$ &$10.63\substack{+0.12\\-0.12}$\\[3pt]
-XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.15\substack{+0.12\\-0.10}$ &$10.88\substack{+0.16\\-0.14}$\\[3pt]
-XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.12\substack{+0.26\\-0.16}$ &$10.85\substack{+0.28\\-0.19}$\\[3pt]
-CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ... & ... & ... & $10.71\substack{+0.16\\-0.12}$ &$10.45\substack{+0.19\\-0.15}$\\[3pt]
-CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ... & ... & ... & $10.90\substack{+0.06\\-0.05}$ &$10.63\substack{+0.12\\-0.11}$\\[3pt]
-CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ...
-& ...
-& ...
-& $11.52\substack{+0.28\\-0.17}$ &$11.25\substack{+0.30\\-0.20}$\\[3pt]
-CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ... & ... & ... & $10.06\substack{+0.23\\-0.15}$ &$9.79\substack{+0.25\\-0.18}$\\[3pt]
-ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ...
-& ...
-& ...
-& $11.16\substack{+0.12\\-0.10}$ &$10.89\substack{+0.16\\-0.14}$\\[3pt]
-SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ...
-& ...
-& ...
-& $10.75\substack{+0.09\\-0.08}$ &$10.49\substack{+0.14\\-0.13}$\\[3pt]
-SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ... & ... & ... & $10.80\substack{+0.11\\-0.09}$ &$10.54\substack{+0.15\\-0.13}$\\[3pt]
-SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ...
-& ...
-& ...
-& $10.77\substack{+0.07\\-0.06}$ &$10.51\substack{+0.12\\-0.12}$\\[3pt]
-SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ...
-& ...
-& ...
-& $11.19\substack{+0.13\\-0.10}$ &$10.92\substack{+0.17\\-0.14}$\\[3pt]
-SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ... & ... & ... & $9.95\substack{+0.47\\-0.22}$ &$9.68\substack{+0.48\\-0.24}$\\[3pt]
-SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ...
-& ...
-& ...
-& $11.03\substack{+0.21\\-0.14}$ &$10.76\substack{+0.23\\-0.17}$\\[3pt]
-\enddata
-\label{tab:result_sersic}
-\tablecomments{
-Column~1: Object ID.
-Column~2-6: WFC3 inference. 
-Column~2: Reduced $\chi ^2$ value by the best PSF in the library.
-Column~7-9: ACS inference. 
-Column~10: Observed host luminosity in the rest-frame R band.
-Column~11: Host total stellar mass.
-}
-\end{deluxetable*}
+We carry out a similar analysis for18/32 AGNs in the COSMOS field with ACS/F184W imaging data.
+We assess their host flux ratio using the same approach as done for the WFC3-IR.
+The ACS FOV is larger than WFC3 thus we generated 174 PSFs for use.
+As expected, the detection of the host galaxy in the IR band is of higher significance than the UV due to the effects of dust extinction and the contrast between the (blue) AGN and (red) host.
+Thus, we fix the \Reff\ and \sersic\ $n$ as the value determined by IR band thus amounting to an assumption that the morphology of the galaxy is consistent between ACS and WFC3 bands.
+In this case, the only free parameters are the total host and AGN flux.
+We report the host galaxy properties in Table~\ref{tab:result_sersic}.
 
@@
 
+From our AGN-host decomposition, we detect the host galaxy in essentially all cases.
+HST/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data-point source'' stamps) shown in Figures~\ref{fig:AGN_decomp} and ~\ref{sec:restsample}.
+While some of the galaxies have nearby neighbors, most are isolated and do not show strong signs of interaction or ongoing mergers.
+This is relevant for model fitting with smooth Sersic profiles and the subsequent determination of the stellar mass.
+In the following subsections, we described the properties of our ensemble of type 1 AGN host galaxies.
+
 \subsection{Host galaxy properties}
-In previous section, we carry out the AGN-host decomposition and derive the host galaxy \sersic\ properties of the overall sample, as shown in Figure~\ref{fig:hist_compare}.
-The optimized resulting images for each sample are presented in the figures in Appendix~\ref{sec:restsample}.
-Based on the third column of these resulting figures (i.e.
-the ``data-Point source'' stamps), we find that all the systems have shown the evidence for existence of the host galaxies.
-We also find that merger feature of the host galaxies are not strong, showing that our sample possibly not be dominated by the major merger.
-
-The host-total flux ratio of the sample are varies from 10\% to 90\% (concentrated between 20\% to 50\%).
-The effective radius and \sersic\ index are randomly distributed within the prior, rather than concentrating on upper/lower side.
-The inferred \Reff\ of our sample are between $\sim$1-7~kpc (peaked at $\sim$2.2~kpc).
-15/32 systems have \sersic\ index $n<2$, indicating they are composed of disk+bulge components.
-Five systems have high \sersic\ index ($n>4.5$); we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
-
-We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive} and find that our high-$z$ AGN host have very similar distribution.
-Thus, we assume the inactive galaxies and our AGN hosts have similar bulge-total ratio so that we can infer the bulge stellar mass of our sample, as shown below.
-
-18/32 systems have multi-band host magnitude which enables us to select the best stellar population that could fit the overall sample.
-We find that the 1~Gyrs stellar population with solar metallicity by Chabrier initial mass function (IMF)~\citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples.
-Given this template, we are capable of inferring the rest-frame R band luminosity (\lhost) and stellar mass (\smass) of our sample based on their filter magnitude, in the following sections.
+\label{sec:result-hosts}
+As shown in Figure~\ref{fig:hist_compare}, the host-to-total flux ratio of the sample spans a wide range from 10\% to 90\% with most of the sample concentrated between 20\% to 50\%.
+Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the very few cases around 10\% should be considered as marginal detections.
+
+The distributions of effective radius \Reff\ and Sersic Index \sersic\ are shown in Figure~\ref{fig:hist_rn}.
+These values are distributed within the allowed range and not concentrated on either the upper or lower bound.
+The \Reff\ of our sample are between $\sim$1-7~kpc (peaked at $\sim$2.2~kpc).
+Nearly half (15/32) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge.
+Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
+
+We compare the morphology of AGNs host galaxies to the inactive ones from the CANDELS/COSMOS imaging survey.
+We identify 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} using \galfit, and their stellar masses are derived based on 3-D-\hst\ spectroscopic survey~\citep{Momcheva2016, Brammer2012}.
+We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where we find no significant difference between their distributions and median value.
+We also test whether the distributions can be drawn from the same parent population using a Kolmogorov-Smirnov test and determining the p-value to be 0.42 and 0.04 for \Reff\ and $n$, respectively.
+We conclude that the host galaxies of our AGN sample are representative of the overall population of galaxies, with a significant disk component, at comparable luminosity and stellar mass at the same redshift.
+In Section~\ref{sec:bh_bulge}, we use this information to infer the likely bulge masses, hence the \mbh\ -- \bmass\ relation.
+
+%In Figure~\ref{fig:Mstar-rn}, we plot the \smass\ versus the \Reff\ and \sersic\ index.
+The color coding is based on the filter flux ratio between WFC3 and ACS.
+The distribution of \smass-\Reff\ relation show that our AGN hosts concentrate at the high end of the stellar mass, close to the red sequence.
+%\begin{figure*}
+%\centering
+%\begin{tabular}{c c}
+% \hspace{-2.5em}
+%{\includegraphics[trim = 0mm 0mm 90mm 0mm, clip, height=0.45\textwidth]{fig/Mstar-Reff.pdf}}&
+%{\includegraphics[ height=0.45\textwidth]{fig/Mstar-Sn.pdf}}\\
+%\end{tabular}
+%\caption{\label{fig:Mstar-rn} 
+%The comparison of the galaxy properties between our 32 AGNs' hosts to the CANDELS sample including 4401 inactive galaxies (circles).
+The color coding is based on the filter flux ratio between WFC3 and ACS.
+For CANDELS sample, the WFC3/F125W flux is taken.
+The black squares are the AGN samples with only WFC3 band observation.
+%}
+%\end{figure*}
+
+\begin{figure}[ht]
+%\centering
+%\begin{tabular}{c c}
+%{\includegraphics[ height=0.3\textwidth]{fig/Hist_Reff.pdf}}&
+%{\includegraphics[ height=0.3\textwidth]{fig/Hist_Sn.pdf}}
+%\end{tabular}
+\epsscale{1.2}
+\plotone{fig/Hist_Reff.pdf}
+\plotone{fig/Hist_Sn.pdf}
+\caption{\label{fig:hist_rn} 
+The comparison of the histogram of the \Reff\ (top panel) and \sersic\ $n_s$ (bottom panel), with median value indicated.
+For comparison, we show the distribution of CANDELS galaxies at similar redshifts and stellar masses to our type 1 AGN sample.}
+\end{figure} 
+%
+
+%We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive} and find that our high-$z$ AGN host have very similar distribution.
+%Thus, we assume the inactive galaxies and our AGN hosts have similar bulge-total ratio so that we can infer the bulge stellar mass of our sample, as shown below.
+
+\subsection{Rest-frame colors (THIS SECTION MAY NEED TO BE EXPANDED ON)}
+
+For 18/32 AGNs, we have multi-band host magnitudes which enables us to select the best stellar population template that could be applicable to determine rest-frame luminosities and stellar masses for the overall sample.
+We find that a 1~Gyr stellar population with solar metallicity for a Chabrier IMF~\citep{Bruzual2003} could well match the colors of our sample based on WFC3 and ACS band magnitudes.
 
 \subsection{\mbh-\lhost\ relation}\label{sec:ml}
-Adopting the 1~Gyrs stellar population, we perform the K-correction to derive the rest-frame R band magnitude of our sample.
-Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty introduced by this K-correction is within 0.05~mag.
-We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}.
-The inferred $L_R$ are ranged between $\log L_R \in [9.5, 11.5]$ ($L_{\odot,R}$), as summarized in Table~\ref{tab:result_sersic}.
-
-We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}. Following common practice, we fit the local relation as a linear relation,
+
+Adopting the 1~Gyr stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample.
+With the WFC3 filter already close to the rest-frame R-band, we expect the $M_R$ uncertainty introduced by this K-correction to be within 0.05~mag.
+We derive the rest-frame R band luminosity from $\log L_R/L_{R, \odot} = 0.4\times(M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}.
+$L_R$ ranges between $\log L_R \in [9.5, 11.5]$ ($L_{\odot,R}$) with individual values listed in Table~\ref{tab:result_sersic}.
+
+We show the relation between \mbh and \lhost\ in Figure~\ref{fig:ML} with comparison samples. For reference, we fit the local data with a linear relation,
+
 \begin{eqnarray}
@@
 \end {eqnarray}
-which enables direct comparison to the distant sample.
-The inferred local relations, as presented in the Figure~\ref{fig:ML}, shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones.
-The observational result indicates that the relation between black hole mass and the host luminosity are similar at different period of the universe.
-
-Considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
+
+\noindent which enables comparison between our high-$z$ sample and the local relation.
+The distribution of our data appears to be in good agreement with the local relation and the other AGN samples at lower redshift.
+Therefore, the observational data indicate that the relation between black hole mass and the host luminosity are similar at different period of the universe.
+In Appendix~\ref{sec:ml-ev}, we explore how the high-$z$  sample would evolve in this plane solely with luminosity evolution of the host galaxy as done in past studies \citep[e.g., ][]{Ding2017b}.
+
+We note that there are outliers that deviate from the distribution of overall sample, such as SXDS-X763.
+We suspect that this source may have abnormal host properties.
+Indeed, the value of \Reff\ has a large uncertainty ($\sim 75\%$) and the host-to-total flux ratio is the lowest of the high-$z$ sample ($<10\%$).
+
+%Considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
 We will make this comparison taking the evolution effect into account in Section~\ref{sec:ml-ev}.
 
-We note three outlier measurements deviated from the distribution of overall sample, which are SXDS-X763, CDFS-1, CDFS-724.
-We expect that they could have abnormal host inference.
-Indeed, for SXDS-X763, the inferred host \Reff\ has large scatter ($\sim 75\%$) with the lowest host-total flux ratio in the overall sample ($<10\%$).
-For CDFS-1 and CDFS-724, their host are \Reff$<0\farcs{}15$, smaller than the PSF FWHM.
+%For CDFS-1 and CDFS-724, their host are \Reff$<0\farcs{}15$, smaller than the PSF FWHM.
 Moreover, the broad emission line of \mbh\ are from \citet{Suh2015} which could have systemic to \citet{Schulze2018}.
@@
 \caption{\label{fig:ML} 
-Illustration of observed correlations between \mbh-\lhost, with local linear relation indicated. 
-%The redshift are color-coded, for distant and intermediate AGNs.
-The black line and the blue colored equation indicates the best-fit result of local sample as Equation~\ref{eq:MLlocal}, with $1-\sigma$ confidence interval colored as gray region.
+Black hole mass vs.
+R-band luminosity relation.
+The black line and the blue colored equation indicates the best-fit result of local sample as given in Equation~\ref{eq:MLlocal}, with $1-\sigma$ confidence interval indicated by gray region.
 }
@@
 
-Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted.
-The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex, at fixed stellar initial mass function (changing the initial mass function would change all our stellar masses systematically).
-The inferred $M_*$ are ranged between $\log M_* \in [9.7, 11.3]$ ($M_{\odot}$), listed in Table~\ref{tab:result_sersic}.
-
-In Figure~\ref{fig:MM}, we plot the our \mbh-\smass\ measurements and compare to the local and intermediate sample.
-We visually see that the relations for the three samples are close.
-Similar as Equation~\ref{eq:MLlocal}, we consider the local \mbh-\smass\ relations as linear relation as:
+To fulfill our purpose of acquiring the NIR imaging with HST, we use the host luminosity along with color information to estimate the stellar mass content of each host galaxy  based on the mass-to-light ratio of the adopted stellar population.
+The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex (changing the IMF would effect all our stellar masses systematically).
+We find $M_*$ ranges between $\log M_* \in [9.7, 11.3]$ ($M_{\odot}$).
+These values are listed in Table~\ref{tab:result_sersic}.
+
+In Figure~\ref{fig:MM}, we plot the our \mbh -- \smass\ measurements and find that the distributions in this plane for the four samples are similar.
+However, there is a slight shift of the high-$z$ data towards higher black hole masses at a fixed host mass.
+In Figure~\ref{fig:MM-vz}, we plot, as a function of redshift, the mass ratio ($right$ panel) and the mass ratio difference ($\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$ which is considered as the difference between the high redshift data and the best-fit local relation; $left$ panel).
+For our high-$z$ sample, we find the average $\Delta \log \mathcal M_{\rm BH}$ to be 0.3, a factor of two higher than the local mass ratio as indicated by the top green circle in Figure~\ref{fig:MM-vz}.
+
+As with Equation~\ref{eq:MLlocal}, we fit the \mbh-\smass\ data with a linear relation as:
 \begin{eqnarray}
@@
 
-To understand the evolution for high-$z$ relations, we fit the offset as a function of redshift in form as:
+\noindent and an evolution term parameterized in the following form:
+
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$.
-We obtain $\gamma  = 0.84 \pm 0.26$, i.e.
-tentative evidence for evolution, see Figure~\ref{fig:MM-vz}, panel (a).
-We also show the ratio of \mbh-\smass\ of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).
+
+If we perform such a fit based on the {\it observed} data (i.e., no correction for selection effects), we obtain $\gamma  = 0.78 \pm 0.26$ that may be tentatively considered as evidence for evolution.
+Even with the exclusion of the few outliers, there is an evolution in the relation with $\gamma  = 0.65 \pm 0.27$.
+The best-fit {\it observed} evolution model is shown in Figure~\ref{fig:MM-vz}.
 
@@
 \caption{\label{fig:MM} 
-Similar to the Figure~\ref{fig:ML}, but the comparison of the \mbh-\smass\ relations.}
+Black hole mass vs. stellar mass relation ( \mbh -- \smass\ ). The best-fit local relation is shown as described in Fig.~\ref{eq:MLlocal}.
+}
 \end{figure}
@@
 \caption{\label{fig:MM-vz} 
-Left: illustration of the offset in  $\log($\mbh$)$ (VS.
+Left: Offset in  $\log($\mbh$)$ (vs.
 \smass) as a function of redshift.
 The orange band is the intrinsic scatter of local linear relation.
-The red line and gray band are the best-fit and $1-\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs.
+The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs.
 Right: \mbh/\smass\ as a function of redshift. 
@@
 
-As shown in Figure~\ref{fig:MM-vz}, panel (a), most of our measurements locate within the scattering range of the local sample.
-We doubt whether the positivity of $\gamma$ stems from the three outliers discussed in last section.
-We thus exclude these outliers and re-perform the statistical analysis to see if the offset still exists.
-As a result, we obtain that $\gamma  = 0.65 \pm 0.27$, indicating the positive evolution trend become weaker but still exists.
+{\bf [Include a full paragraph on the scatter]} As shown in these panels, there is some scatter similar in magnitude to the local relation.
 
@@
 
-It is worth note that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
-That is, we are comparing the \mbh-\smass$_{,total}$ relations at the distant universe to the \mbh-\smass$_{\rm ,bulge}$ relations at local.
-Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{, bluge}$ of them are supposed to be even less.
-{\color{blue}
-%1. B/T can be inferred by n
-%2. The sample we use and how to build up the relation.
-%3. take the relation and infer the bulge. Finally infer the result
-%4. We note the scatter could be larger.
-Given that the inferred morphology of our 32 AGN hosts presents the similarities to the CANDELS inactive ones (see Appendix~\ref{sec:comp_inactive}), we expect their B/T follows the similar distribution which can be roughly estimated by the single-\sersic\ index \citep{Bruce2014}.
-With this estimation, we could roughly infer the bulge stellar mass of our AGN host.
-
-To this end, we first study the relations between B/T and single-\sersic\ index for CANDELS inactive galaxies at the similar mass level, i.e \smass$\in [9.0, 11.5]$, using B/T measured by \citet{Dimauro2018}.
-Then, we calculate the local averaged  B/T value at different \sersic\ index value to build up their specific relation, as shown in Figure~\ref{fig:BT-n_relation}.
-Taking this relation, we estimate the B/T of our AGN sample using the inferred \sersic\ index as proxy and infer their \smass$_{, bulge}$.
-We take this \smass$_{, bulge}$ to study their co-evolution to the \mbh.
-As expected, we find a stronger evolution trend with $\gamma = 1.71\pm0.27$.
-Of course, this is a very rough estimate --- the systematic for the estimated \smass$_{, bulge}$ must be larger than the \smass$_{, total}$.
-
-\begin{figure}
-\centering
-{
-\includegraphics[width=0.5\textwidth]{fig/BT_relation.pdf}
-}
-\caption{\label{fig:BT-n_relation} 
-The relations between stellar mass bulge-total-ratio and single-\sersic\ index by CANDELS inactive galaxies with \smass$\in [9.0, 11.5]$.
-The red curve is the inferred specific relation taking the average B/T ratio at different \sersic\ index, used as proxy to infer the B/T for our AGN sample.
-}
-\end{figure} 
-}
-
-We summarize the inference of $\gamma$ using different combination of sample in Table~\ref{table:diff_sample_gam}.
+%We summarize the inference of $\gamma$ using different combination of sample in Table~\ref{table:diff_sample_gam}.
 All the $\gamma$ by the observed \mbh-\smass\ are inferred as positive, indicating that the growth of the black hole predates that of the host bulge.
-
-\begin{table}
-\centering
-    \caption{The inference of $\gamma$ using \mbh-\smass\ by different sample combination.}\label{table:diff_sample_gam}
-     \resizebox{5.5cm}{!}{
-     \begin{tabular}{cc}
-     \hline
-     Sample combination & $\gamma$ \\
-     &\\
-     \hline\hline
-32 AGNs & 0.84$\pm$0.26\\    
-29 AGNs (excluded outliers) & 0.65$\pm$0.27\\    
-32 AGNs + intermediate &  0.62$\pm$0.20\\
-32 AGNs bulge only & 1.71$\pm$0.27\\
-     \hline
-     \end{tabular}}
-\tablecomments{These values are directly inference for the observation, which haven't yet taken the selection effect into account.}
-\end{table}
 
@@
 
-In order to evaluate the ``true" underlying evolution and its uncertainty, corrected for selection effects, taking into account the actual observations, we adopt an independent method based on the approach introduced by \citet{Tre++07} and developed by \citet{Park15, Ding2017b}.
+In order to evaluate the ``true" underlying evolution and its uncertainty, corrected for selection effects, taking into account the actual observations, we adopt an independent method based on the approach introduced by \citet{Tre++07} and developed by \citet{Park15} and \citet{Ding2017b}.
 The method parametrizes the evolution of the correlations between \mbh\ and host galaxy properties as an offset from the local one $\gamma$ and an intrinsic scatter \sint, which can be a free parameter or tied to the local relation.
@@
 In practice, we start from the local black hole mass function and the evolution model, generate mock samples using a Monte Carlo approach, apply the selection function and compare with the data to generate the likelihood.
-
 To illustrate the importance of the intrinsic scatter in the selection effects, we adopt both uniform (flat) prior and lognormal prior for \sint.
@@
 Combining the 32 AGNs together with the intermediate redshift sample, we present the inferred  $\gamma$ and \sint\ in the two-dimensional planes in Figure~\ref{fig:select_effect}.
-The plots show that the inferred evolution is uncertain and depends crucially on the intrinsic scatter.
+The plots show that the inferred evolution is uncertain and depends crucially on the intrinsic scatter, especially when applying a luminosity evolution for the host (See Appendix~\ref{sec:ml-ev}).
 Assuming the lognormal prior \sint, to mimic the assumption of the method discussed in Section~\ref{sec:sf_framework}, one sees that the best estimate of $\gamma$ is positive, but the 95\% confidence intervals extend to zero.
@@
 A simple check using our a-priori estimate of the bias, yields a similar result.
-The mean offset of the sample of 32 objects from the local relationship is $0.35\pm0.06$ dex, which would correspond to $\gamma=0.88\pm0.15$.
-However, after correcting for the a priori bias the offset reduces to $0.14\pm0.06$ and thus $\gamma=0.35\pm0.15$, mildly positive but not significantly so, and consistent with the a posteriori method within the error bars and the uncertainty in the correction.
+The mean offset of the sample of 32 objects from the local relationship is $0.34$ dex, which would correspond to $\gamma=0.85$.
+However, after correcting for the a priori bias the offset reduces to $0.13$ and thus $\gamma=0.33$, mildly positive but not significantly so, and consistent with the a posteriori method within the error bars and the uncertainty in the correction.
 We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
@@
 Larger samples are needed to establish whether the positive tail is real or due to small sample statistics.
-
-\begin{table}
-\centering
-    \caption{The summary for the different inference of $\gamma$.}\label{table:gamma_sf}
-     \resizebox{8cm}{!}{
-     \begin{tabular}{cccc}
-     \hline
-     Sample & Selection effects &  \mbh-\smass & \mbh-\lhost \\
-     &&&\\
-     \hline\hline
-32 AGNs + intermediate & No & 0.62$\pm$0.20 & 0.66$\pm$0.18 \\
-32 AGNs + intermediate& Yes & 0.80$\pm$0.30 & 0.60 $\pm$ 0.30 \\
-32 AGNs & No & 0.84$\pm$0.26  & 1.07$\pm$0.23\\
-32 AGNs& Yes & 1.30$\pm$0.50 & 1.70$\pm$0.40 \\
-     \hline
-     \end{tabular}}
-    \tablecomments{
-    Entire sample includes the 32 AGNs and the intermediate redshift AGNs from the reference in Section~\ref{sec:compare_sample}.
-Note that the adopted \lhost\ have been transferred to today assuming the passive evolution scenario using Equation~\ref{eq:L_relation}.
-The results of selection effects used the lognormal prior of \sint.
-}
-\end{table}
 
@@
 
-\section{discussion}
+\subsection{\mbh-\bmass\ relation}\label{sec:bh_bulge}
+
+The local sample of inactive galaxies used in this analysis is mainly comprised of bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
+That is, we are comparing the \mbh-\smass$_{\rm ,total}$ relations in the distant universe to the \mbh-\smass$_{\rm ,bulge}$ relations locally.
+Considering that a significant stellar component of the high-$z$ AGNs have a disk component (i.e., AGN hosts with fitted \sersic\ index close to 1),  \smass$_{\rm , bulge}$ will be smaller than \smass$_{\rm ,total}$.
+
+Given that the structure of our 32 AGN hosts are similar to inactive
+galaxies at the same redshifts and stellar masses
+(Section~\ref{sec:result-hosts}), we expect their B/T ratios follow
+a similar distribution which can estimated using the single-\sersic\
+index \citep{Bruce2014}. With this estimation, we can infer the
+bulge stellar mass of our AGN host.
+
+Under these assumptions, we first establish the relation between the
+single-\sersic\ index and B/T ratios for CANDELS inactive galaxies
+at the similar mass level, i.e \smass$\in [9.0, 11.5]$, using B/T
+measured by \citet{Dimauro2018}. Then, we calculate the average B/T
+ratio at different \sersic\ index to construct a relation for our
+use, as shown in Figure~\ref{fig:BT-n_relation}. Taking this
+relation, we estimate the B/T of our AGN sample using the \sersic\
+index as proxy and infer their \smass$_{\rm, bulge}$ from the total
+stellar mass. We can now compare this \smass$_{\rm, bulge}$ to that
+of the black hole \mbh. As expected, we find a stronger evolutionary
+trend with $\gamma = 1.63\pm0.27$, which corresponds to an offset of
+$0.65\pm0.11$ dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
+local relation. Since selection effects are independent of B/T in
+our framework we can apply our a-priori estimate of the selection
+effect correction by removing 0.21~dex, leaving a significant offset
+of $0.44\pm0.11$.
+
+Even with the uncertainty associated with our estimate of the
+bulge-to-total ratio it is clear that there is significant evolution
+in the \mbh\ -- \smass$_{\rm , bulge}$ relation, considering the
+marginal evidence for evolution in the \mbh-\smass$_{\rm, total}$
+relation and that our galaxies are not pure bulges. This finding
+confirms with higher fidelity the concusion by \citet{Bennert11}
+based on optical data of a smaller sample of 11 objects in the same
+redshift range.
+
+\begin{figure}
+\centering
+{
+\includegraphics[width=0.5\textwidth]{fig/BT_relation.pdf}
+}
+\caption{\label{fig:BT-n_relation} 
+Relation between bulge-to-total stellar mass ratio and single-\sersic\ index using CANDELS inactive galaxies with \smass$\in [9.0, 11.5]$.
+The red curve is the inferred specific relation taking the average B/T ratio at different \sersic\ index, used as proxy to infer the B/T for our AGN sample.
+}
+\end{figure}
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+{\includegraphics[width=0.5\textwidth]{fig/MBH-Mbulge-style1.pdf}}&
+{\includegraphics[width=0.5\textwidth]{fig/MBH-Mbulge-style0.pdf}}\\
+\end{tabular}
+\caption{\label{fig:MM_bulge-vz} 
+---For bulge}
+\end{figure*}
+
+\section{Final technical remarks}
 \label{sec:dis}
-
-\subsection{Host luminosity passive evolution correction}\label{sec:ml-ev}
-In the passive evolution scenario, we expect the galaxy luminosity to fade over time.
-Thus, we transfer the \lhost\ for distant samples at today so as to compare the \mbh-\lhost\ relation to the local in the equivalent frame.
-We consider this scenario following \citet{Ding2017b} by parametrizing the luminosity evolution with the functional form as
-$d{\rm mag}_{\rm R}\sim~d\log(1+z)$, i.e.,
-\begin{eqnarray}
-\label{eq:L_relation}
-\log(L_{R,0})=\log(L_{R}) - 1.48 \log (1+z).
-\end{eqnarray} 
-This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer the interested readers to \citet[][section 5.4]{Ding2017b} for more details.
-
-Having transferred the \lhost\ to today, we find that, as showing in Figure~\ref{fig:ML-vz}-(a), at fixed mass, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation.
-We fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 0.71 \pm 0.18$, as showing in Figure~\ref{fig:ML-vz}-(b).
-We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.3$, with flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
-
-The inferred $\gamma$ here could have large systematic given the following limitations.
-First, the passive evolution is based on a simplified correction; after all, we are not clear exactly how the host evolves to $z=0$.
-Moreover, we only consider the evolution of the host galaxy and assume the \mbh\ does not change much.
-%Moreover, in the literature, the correlation of the \mbh-\smass\ is considered as more fundamental which would be more efficient to understand their co-evolution.
-
-\begin{figure*}
-\centering
-\begin{tabular}{c c}
-\subfloat[\mbh-\lhost\ relation, evolution-corrected]
-{\includegraphics[height=0.5\textwidth]{fig/MBH-L_ev.pdf}}&
-\subfloat[offset in  $\log($\mbh$)$ (VS. \lhost) as a function of redshift]
-{\includegraphics[height=0.5\textwidth]{fig/MBH-L-vz.pdf}}\\
-\subfloat[\mbh-\lhost, flat prior]
-{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
-\subfloat[\mbh-\lhost, lognormal prior]
-{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
-\end{tabular}
-\caption{\label{fig:ML-vz} 
-Same as previous figures but for \mbh-\lhost\ relation, considering the passive evolution correction for host galaxy luminosity.}
-\end{figure*}
 
@@
 The fidelity of the inferred apparent magnitudes of the host galaxies are high.
-Nevertheless, we adopt one stellar population to the overall sample to derive the rest-frame R band luminosity and stellar mass.
-We note that adopting the private stellar populations for each samples which havs both multi-band host magnitude could be more robust in principle.
-However, considering that the host magnitude in ACS band is faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost.
-Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry.
-
-We highlight that, in this particular paper, we focus most on the decomposing of the AGN image to present our inference of the host.
+Nevertheless, we adopt one stellar population for the full sample to derive the rest-frame R-band luminosity and stellar mass.
+We note that adopting a stellar population model separately for each AGN host could be more robust in principle.
+However, considering that the host magnitude in the HST/ACS band is faint (host-to-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost.
+Perhaps the best way to derive the stellar population is to combine our measurements with ground-based photometry.
+This is currently beyond the scope of this analysis.
+
+%We highlight that, in this particular paper, we focus most on the decomposing of the AGN image to present our inference of the host.
 With the host inference, we then carry out a rapid analysis of the \mbh\ and host properties relations.
@@
 
-At last, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates.
+We highlight that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates.
 That is to say, the intrinsic scatter is not necessarily worse at high-$z$ than the low-$z$.
@@
 \label{sec:local_sys}
-To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}.
-In the literature, some other local sample have been measured which could also be considered as the local anchor.
-We note that different local samples have inconsistency which could affect our understand of the co-evolutions.
-To estimate this effect, we compare our local \mbh-\smass\ sample to the local ones by \citet{Kormendy13} (hereafter K13).
-We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset to our local sample.
+
+To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011} and  \citet{H+R04}.
+In the literature, other analyses of the local sample are available which could also be considered as the local anchor.
+We note that the different local samples have inconsistencies which could affect our understand of co-evolution.
+To estimate this effect, we compare our local \mbh-\smass\ sample to that in \citet{Kormendy13} (hereafter K13).
+We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset relative to our local sample.
 Note that a $+0.3$~dex difference could totally erase the $\Delta\log$\mbh\ for the high redshift sample as described in last section.
 
-However, we realize that the \mbh-\sigstar\ relations by K13 also have a $\sim$0.3~dex offset to the ones by \citet{Woo2010}.
+However, we realize that the \mbh-\sigstar\ relations by K13 also have a $\sim$0.3~dex offset to those in \citet{Woo2010}.
 Note that it is the local \mbh-\sigstar\ relation by \citet{Woo2010} that is used to determine the virial coefficient for our active BHs.
-Thus, if adopting the K13's sample, the \mbh\ of all the AGN sample should be increased by $\sim$0.3~dex.
+Thus, if adopting the K13 normalization, the \mbh\ of all the AGN sample should be increased by $\sim$0.3~dex.
 As a result, adopting different local measurement would only globally affect the level of the \mbh\ to local and high-$z$ sample at the same time, with the result of  $\Delta\log$\mbh\ unchanged.
-
 We thus conclude that, if adopt K13 sample, the inference of the high redshift offset of $\Delta\log$\mbh\ would remain at the same level.
@@
 
-\section{Summary} \label{sec:sum}
+\section{Conclusions} \label{sec:sum}
+
 We studied the evolution of the correlations between the supermassive black hole and their host galaxies using new measurements of 32 X-ray selected AGNs at $1.2<z<1.7$.
-
-We used the published near-infrared spectroscopic observations \halpha\ emission lines to estimate the reliable values of BH mass.
-To obtain the properties of the AGN host galaxies, we performed the AGN image decomposition using the state-of-the-art techniques.
-We adopted the \hst/WFC3 infrared channel to observe the high-resolution AGN imaging data and collected the PSF-stars in across all the fields to build to a library of PSF for the fitting.
+Near-infrared spectroscopic observations with Subaru/FMOS of the \halpha\ emission line are available that provide reliable BH masses.
+To obtain the properties of the AGN host galaxies, we performed an image decomposition using the state-of-the-art techniques on \hst/WFC3 IR data to obtain high-resolution imaging of the AGN and its host.
+This required us to construct a collection of PSF-stars across all the fields to build to a library of PSFs.
 Using the latest image modeling tool \lenstronomy, we decomposed the AGN image in 2-D plane taking each PSF in the library.
-We obtained the host \sersic\ property (i.e., host flux, effective radius, \sersic\ index) using a weighted arithmetic mean based on the inference by the eight top-ranked PSFs.
-Incorporating with the inference by \hst/ACS image, we selected the stellar population, hence derived the rest-frame R band Luminosity (\lhost) and stellar mass (\smass) of the host.
-
-Combining our high-$z$ measurements with the intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13, Cisternas2011}, we compared the scaling relations to the ones from the local with main results summarized as follows:
-\begin{enumerate}
-\item The \mbh-\smass\ relations at higher redshift are inconsistent with the local ones, i.e.
-Figure~\ref{fig:MM}, \ref{fig:MM-vz}.
-Considering the correction for passive evolution of galaxy luminosity, the \mbh-\lhost\ relations at higher redshift are inconsistent with the local ones,  i.e.
-Figure~\ref{fig:ML-vz} - (a).
-\item The offsets of by the evolution are well described by the form $\Delta\log\mathcal M_{\rm BH}= \gamma \log (1 + z)$. We obtain $\gamma = 0.84\pm0.26$ for \mbh-\smass\ relation.
-
-\item However, when considering the selection effect (using two independent methods), we find that the high redshift measurements can be consistent with the local relations, i.e.
-Section~\ref{select_eff}.
-
-\item Our inference indicates the evidence of disk+bulge component (i.e.
-the ones with \sersic\ $n<2$), while the local comparing samples are bulge dominated.
-We take the inferred  \sersic\ $n$ as proxy to estimate the bulge-total-ratio stellar mass.
-Comparing to their \mbh, we find a strong evolution with $\gamma = 1.71\pm0.27$.
-Thus, the conclusion seems solid that the BHs 8-10~Gyrs ago reside in bulges which are less massive/luminous than today.
-
-\item We also compare the properties of our active galaxy sample to the ones from inactive galaxy in the CANDELS imaging survey at the same redshift range, finding no significant discrepancy among them.
-\end{enumerate}
+We obtained the host properties (i.e., host flux, effective radius, \sersic\ index) using a weighted arithmetic mean based on the inference from the eight top-ranked PSFs.
+With additional \hst/ACS image in the optical, we identified the appropriate stellar population and derived the rest-frame R-band Luminosity (\lhost) and stellar mass (\smass) of the host with the corresponding mass-to-light ratio.
+
+We then determine the mass relations at high-$z$ and establish any signs of evolution by combining our high-$z$ measurements with local and intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13, Cisternas2011}.
+With consideration of selection biases, we find the average ratio between the mass of a supermassive black hole and either their total host luminosity or stellar mass at $z\sim1.5$ does not exhibit a significant deviation, as compared to local values, for which we can consider to be evidence of the growth of one preceding the other.
+Thus a co-evolutionary scenario is favorable.
+However, there is marginal room for the black hole to overshoot the growth of its host, although less than a factor of two, since there may be selection effects that accounted for as precisely as needed.
+
+Regarding the black hole mass relative to the bulge mass that is primarily the quantities that are responsible for the local relations, we find that our high-$z$ AGN sample clearly has elevated black hole masses thus indicative of strong evolution.
+Comparing to their \mbh, we find evolution with the ratio evolving as $(1+z)^{1.63\pm0.27}$.
+This analysis is based on an inference of the B/T ratio from the measured Sersic indices.
+A proper measure of the bulge mass at high-$z$ may need to wait for the next generation ground-based 20-30m class telescopes.
+Even so, this conclusion seems solid that the BHs 8-10~Gyrs ago reside in bulges which are less massive/luminous than today.
+
+Of further interest, the scatter in the \mbh-\smass\ ratios at high-$z$ is similar to the local scatter.
+This was unexpected since the measurements of the masses of both the black holes and their hosts should have more uncertainty that local estimates.
+If true, this may indicate that cosmic averaging of initially unrelated states are not driving the relation between SMBHs and their host galaxies thus there is likely a connection between the two yet to be fully understood, contenders include AGN feedback or links to common gas reservoirs.
+
+Finally, the forthcoming launch of the {\it James Webb Space Telescope} ({\it JWST}) may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim$7) and thus trace the evolution of correlations at more distant universe.
+Although, galaxies, as we know, are smaller at high-$z$ thus may remain challenging to detect under the glare of a luminous AGN.
+In the lower redshift Universe, wide area surveys with Subaru/HSC, LSST and WFIRST offer much promise to build samples for studying these mass ratios and dependencies on other factors (e.g., environment).
 
@@
 
-Towards a better estimation of the evolution of the scaling relations, we address the limitations of this work.
+%Towards a better estimation of the evolution of the scaling relations, we address the limitations of this work.
 First, most of the host-total ration in the \hst/ACS band are low ($<20\%$), the fidelity of the host flux are thus limited at UV band.
@@
 
-Looking into the future, the forthcoming lunching of {\it James Webb Space Telescope} ({\it JWST}) would provide the high quality imaging data of AGN at higher redshift (up to $z\sim$7-10) and thus trace the evolution of correlation at more distant universe.
-Furthermore, {\it JWST} is capable of showing the morphology of structures feeding black hole accretion and feedback on the host galaxy~\citep{Ford2014}, thus providing the opportunity to understand the origin of the scaling relations and their evolution.
+%
 
@@
 \newpage
+
 \appendix
 
-\section{A. Comparison to the inactive galaxies}\label{sec:comp_inactive}
-We compare the morphology of AGNs host galaxies to the inactive ones from the CANDELS/COSMOS imaging survey.
-we collect 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-\hst\ spectroscopic survey~\citep{Momcheva2016, Brammer2012}.
-%In Figure~\ref{fig:Mstar-rn}, we plot the \smass\ versus the \Reff\ and \sersic\ index.
-The color coding is based on the filter flux ratio between WFC3 and ACS.
-The distribution of \smass-\Reff\ relation show that our AGN hosts concentrate at the high end of the stellar mass, close to the red sequence.
-%\begin{figure*}
-%\centering
-%\begin{tabular}{c c}
-% \hspace{-2.5em}
-%{\includegraphics[trim = 0mm 0mm 90mm 0mm, clip, height=0.45\textwidth]{fig/Mstar-Reff.pdf}}&
-%{\includegraphics[ height=0.45\textwidth]{fig/Mstar-Sn.pdf}}\\
-%\end{tabular}
-%\caption{\label{fig:Mstar-rn} 
-%The comparison of the galaxy properties between our 32 AGNs' hosts to the CANDELS sample including 4401 inactive galaxies (circles).
-The color coding is based on the filter flux ratio between WFC3 and ACS.
-For CANDELS sample, the WFC3/F125W flux is taken.
-The black squares are the AGN samples with only WFC3 band observation.
-%}
-%\end{figure*} 
-We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where we find no significant difference between their distribution and median value.
-We also compare the difference by performing the Kolmogorov-Smirnov test and inferring the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.
-
-We conclude that the host galaxies of our AGN sample are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.
-\begin{figure*}[ht]
-\centering
-\begin{tabular}{c c}
-{\includegraphics[ height=0.3\textwidth]{fig/Hist_Reff.pdf}}&
-{\includegraphics[ height=0.3\textwidth]{fig/Hist_Sn.pdf}}
-\end{tabular}
-\caption{\label{fig:hist_rn} 
-The comparison of the histogram of the \Reff\ and \sersic\ n, with median value indicated.}
-\end{figure*}
-
-\newpage
-\section{B. The demonstration of remaining 31 AGNs}\label{sec:restsample}
+\section{A. AGN - host galaxy decomposition for the remaining 31 AGNs}\label{sec:restsample}
 The AGNs decomposition for the other 31 objects of our sample, presented in the same way as Figure~\ref{fig:AGN_decomp}.
@@
 
+\newpage
+\section{B. AGN host galaxy luminosity with a correction for passive evolution}\label{sec:ml-ev}
+In the passive evolution scenario, we expect the galaxy luminosity to fade over time.
+Thus, we transfer the \lhost\ for distant samples at today so as to compare the \mbh-\lhost\ relation to the local in the equivalent frame.
+We consider this scenario following \citet{Ding2017b} by parametrizing the luminosity evolution with the functional form as
+$d{\rm mag}_{\rm R}\sim~d\log(1+z)$, i.e.,
+\begin{eqnarray}
+\label{eq:L_relation}
+\log(L_{R,0})=\log(L_{R}) - 1.48 \log (1+z).
+\end{eqnarray} 
+This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer the interested readers to \citet[][section 5.4]{Ding2017b} for more details.
+
+Having transferred the \lhost\ to today, we find that, as showing in Figure~\ref{fig:ML-vz}-(a), at fixed mass, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation.
+We fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 0.71 \pm 0.18$, as showing in Figure~\ref{fig:ML-vz}-(b).
+We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.3$, with flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
+
+The inferred $\gamma$ here could have large systematic given the following limitations.
+First, the passive evolution is based on a simplified correction; after all, we are not clear exactly how the host evolves to $z=0$.
+Moreover, we only consider the evolution of the host galaxy and assume the \mbh\ does not change much.
+%Moreover, in the literature, the correlation of the \mbh-\smass\ is considered as more fundamental which would be more efficient to understand their co-evolution.
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+\subfloat[\mbh-\lhost\ relation, evolution-corrected]
+{\includegraphics[height=0.5\textwidth]{fig/MBH-L_ev.pdf}}&
+\subfloat[offset in  $\log($\mbh$)$ (VS. \lhost) as a function of redshift]
+{\includegraphics[height=0.5\textwidth]{fig/MBH-L-vz.pdf}}\\
+\subfloat[\mbh-\lhost, flat prior]
+{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
+\subfloat[\mbh-\lhost, lognormal prior]
+{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
+\end{tabular}
+\caption{\label{fig:ML-vz} 
+Same as previous figures but for \mbh-\lhost\ relation, considering the passive evolution correction for host galaxy luminosity.}
+\end{figure*}
+
+\begin{deluxetable*}{llccccc}
+\tablecolumns{7}
+\tablewidth{0pt}
+\tablecaption{Details of Observation} 
+\tablehead{ 
+\colhead{Object ID} &
+\colhead{$z$} & 
+\colhead{WFC3/Filter} &
+\colhead{$RA$}&
+\colhead{$DEC$}&
+\colhead{Observing date}&
+\colhead{Exposure time (s)}
+\\ 
+\colhead{(1)} &
+\colhead{(2)} &
+\colhead{(3)} &
+\colhead{(4)} &
+\colhead{(5)} &
+\colhead{(6)} &
+\colhead{(7)}
+} 
+\startdata
+%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
+%\\
+COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
+COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
+COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
+COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
+COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
+COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
+COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
+COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
+COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
+COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
+COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
+COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
+COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
+COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
+COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
+COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
+COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
+COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
+COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
+COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
+COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
+CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
+CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
+CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
+ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
+CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
+SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
+SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
+SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
+SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
+SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
+SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
+\enddata
+\label{tab:objlist}
+\tablecomments{
+Column 1: Object field and ID.
+Column 2: Spectroscopic redshift.
+Column 3: WFC3 filter. Note that the targets from the COSMOS and (E)-CDF-S fields also have ACS imaging.
+Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
+Column 6: The observing start date.
+Column 7: Total exposure time.
+}
+\end{deluxetable*}
+
+\begin{deluxetable*}{ccccccc}
+\tablecolumns{7}
+\tablewidth{0pt}
+\tablecaption{Host inference of CID1174} 
+\tablehead{ 
+\colhead{PSF rank} &
+\colhead{total $\chi ^2$} & 
+\colhead{weights $w_i$} &
+\colhead{host flux (counts)} &
+\colhead{host flux ratio}&
+\colhead{\Reff (arcsec)}&
+\colhead{\sersic\ $n$}
+ \\ 
+\colhead{(1)} &
+\colhead{(2)} &
+\colhead{(3)} &
+\colhead{(4)} &
+\colhead{(5)} &
+\colhead{(6)} &
+\colhead{(7)} 
+} 
+\startdata
+%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
+%\\
+1 & $8584.429$ & $1.000$ & $82.2$ & $35\%$ & $0\farcs{}345$ & $1.1$ \\
+2 & $8646.711$ & $0.920$ & $99.1$ & $42\%$ & $0\farcs{}298$ & $1.9$ \\
+3 & $8816.947$ & $0.734$ & $76.7$ & $33\%$ & $0\farcs{}365$ & $1.1$ \\
+4 & $9304.841$ & $0.383$ & $128.6$ & $55\%$ & $0\farcs{}231$ & $2.8$ \\
+5 & $9652.575$ & $0.241$ & $187.5$ & $79\%$ & $0\farcs{}116$ & $6.2$ \\
+6 & $9917.101$ & $0.170$ & $100.2$ & $42\%$ & $0\farcs{}287$ & $2.1$ \\
+7 & $10018.324$ & $0.148$ & $75.1$ & $32\%$ & $0\farcs{}365$ & $1.2$ \\
+8 & $10087.456$ & $0.135$ & $79.8$ & $34\%$ & $0\farcs{}358$ & $1.2$ \\
+\hline\\
+Weighted value & & & $97.322\pm28.336$ & $42\%\pm12\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.9\pm1.3$  \\
+\enddata
+\label{tab:weight_CID1174}
+\tablecomments{
+Column~1: Rank of the PSF from the library.
+Column~2: Total $\chi ^2$ for the corresponding PSF.
+Column~3: Weights for the inference.
+Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
+For this sample, the inflation parameter $\alpha$ calculated by Equation~\ref{eq:alpha} is 16.671.
+}
+\end{deluxetable*}
+
+\begin{deluxetable*}
+{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
+\tablecolumns{9}
+\tablewidth{0pt}
+\tablecaption{Inferred BH properties for the 32 systems} 
+\tablehead
+{ 
+\colhead{Target ID}&
+  \multicolumn{4}{c}{using emission line \halpha}&
+  \multicolumn{4}{c}{using emission line \hbeta} \\
+  \cline{2-5}  \cline{6-9} \\
+\colhead{}& 
+\colhead{FWHM}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
+\colhead{FWHM(5100)}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
+\colhead{}& 
+\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
+\colhead{(M$_{\odot}$)}& (log$\lambda$)&
+\colhead{(\kms)}& 
+\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$\lambda$)\\
+\colhead{(1)}& 
+\colhead{(2)}& \colhead{(3)}& 
+\colhead{(4)}& \colhead{(5)}& 
+\colhead{(6)}&\colhead{(7)}&
+\colhead{(8)}& \colhead{(9)}
+}
+\startdata 
+CID1174 & 1906 & 43.43 & 7.99 & -0.47 & 5898 & 44.76 & 8.83& -1.34 \\
+CID1281 & 1619 & 43.24 & 7.75 & -0.41 & ... & ... & ... & ... \\
+CID206 & 3334 & 43.48 & 8.53 & -0.97 & ... & ... & ...& ... \\
+CID216 & 2230 & 42.85 & 7.85 & -0.90 & ... & ... & ...& ... \\
+CID237 & 2112 & 43.86 & 8.29 & -0.36 & ... & ... & ...& ... \\
+CID255 & 1932 & 43.99 & 8.27 & -0.22 & 3709 & 45.37 & 8.73& -0.60 \\
+CID3242 & 2543 & 43.83 & 8.45 & -0.55 & 3775 & 45.10 & 8.61& -0.75 \\
+CID3570 & 1959 & 43.16 & 7.89 & -0.63 & ... & ... & ...& ... \\
+CID452 & 3458 & 42.92 & 8.30 & -1.26 & 3127 & 44.63 & 8.22& -0.88 \\
+CID454 & 2824 & 43.34 & 8.31 & -0.88 & ... & ... & ...& ... \\
+CID50 & 2340 & 43.94 & 8.42 & -0.42 & 1939 & 45.33 & 8.15& -0.06 \\
+CID543 & 2189 & 43.57 & 8.19 & -0.53 & ... & ... & ...& ... \\
+CID597 & 1656 & 43.33 & 7.81 & -0.39 & ... & ... & ...& ... \\
+CID607 & 3009 & 43.67 & 8.53 & -0.78 & 4242 & 44.78 & 8.56& -1.04 \\
+CID70 & 2480 & 43.51 & 8.27 & -0.68 & 3982 & 45.16 & 8.69& -0.77 \\
+LID1273 & 3224 & 43.61 & 8.56 & -0.87 & ... & ... & ...& ... \\
+LID1538 & 2941 & 43.60 & 8.47 & -0.79 & ... & ... & ...& ... \\
+LID360 & 2482 & 43.88 & 8.45 & -0.50 & 2869 & 45.09 & 8.37& -0.52 \\
+XID2138 & 3186 & 43.61 & 8.55 & -0.86 & 2945 & 44.81 & 8.25& -0.71 \\
+XID2202 & 2973 & 43.56 & 8.46 & -0.82 & ... & ... & ...& ... \\
+XID2396 & 2271 & 44.06 & 8.46 & -0.33 & 2658 & 45.50 & 8.51& -0.24 \\
+CDFS-1 & 2000 & 43.02 & 7.83 & -0.03 & ... & ... & ...& ... \\
+CDFS-229 & 2190 & 43.60 & 8.20 & -0.60 & ... & ... & ...& ... \\
+CDFS-321 & 2442 & 43.93 & 8.46 & -0.46 & ... & ... & ...& ... \\
+CDFS-724 & 2541 & 42.95 & 8.03 & -1.15 & ... & ... & ...& ... \\
+ECDFS-358 & 2237 & 43.40 & 8.12 & -0.64 & ... & ... & ...& ... \\
+SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.81 & 6761 & 44.71 & 8.93& -1.49 \\
+SXDS-X50 & 1817 & 43.42 & 7.94 & -0.43 & ... & ... & ...& ... \\
+SXDS-X717 & 2931 & 43.05 & 8.20 & -1.05 & ... & ... & ...& ... \\
+SXDS-X735 & 2702 & 43.70 & 8.44 & -0.67 & 3520 & 45.07 & 8.54& -0.70 \\
+SXDS-X763 & 2961 & 43.57 & 8.47 & -0.81 & 4509 & 44.51 & 8.47& -1.29 \\
+SXDS-X969 & 2296 & 43.50 & 8.20 & -0.61 & 1696 & 45.05 & 7.90& -0.08 \\
+\enddata
+\label{tab:result_mbh}
+\tablecomments{
+Column 1: Object ID.
+Column 2-5: \halpha\ emission line width (FWHM), continuum luminosity, inferred \mbh\ and Eddington ratio.
+Column 6-9: \hbeta\ emission line BH properties. 
+The typical uncertainty level for FWHM and $\log( \rm L _{\lambda})$ are $15\%$ and $\pm0.01$, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
+}
+\end{deluxetable*}
+
+\tabcolsep=0.03cm
+\begin{deluxetable*}
+{@{\extracolsep{2pt}}lccccccccccc}   % need for the gap between the clines.
+\tablecolumns{10}
+\tablewidth{0pt}
+\tablecaption{Inferred host galaxy properties for the 32 systems.} 
+\tablehead
+{ 
+\colhead{Target ID}&
+  \multicolumn{5}{c}{WFC3}&
+  \multicolumn{3}{c}{ACS/F814W} &
+   \multicolumn{2}{c}{host properties} \\
+  \cline{2-6}  \cline{7-9} \cline{10-12}  \\
+\colhead{}& 
+\colhead{$\chi ^2$}& \colhead{host-total flux ratio}& 
+\colhead{\Reff}& \colhead{\sersic\ $n$}& 
+\colhead{magnitude}&
+\colhead{$\chi ^2$}& \colhead{host-total flux ratio}& \colhead{magnitude} &
+\colhead{$\log L_R$} &\colhead{$\log M_*$} &\colhead{$\log M_{*, bulge}$} \\
+\colhead{}& 
+\colhead{(reduced)}& \colhead{}& 
+\colhead{($\arcsec$)}& \colhead{}& 
+\colhead{(AB system)}& \colhead{(reduced)}& 
+\colhead{}& \colhead{(AB system)} &\colhead{($L_{\odot,R}$)} & \colhead{(M$_{\odot}$)} &  \colhead{(M$_{\odot}$)}\\
+\colhead{(1)}& 
+\colhead{(2)}& \colhead{(3)}& 
+\colhead{(4)}& \colhead{(5)}& 
+\colhead{(6)}& \colhead{(7)}& 
+\colhead{(8)}& \colhead{(9)}&
+\colhead{(10)}& \colhead{(11)} &  \colhead{(12)}
+}
+\setlength{\tabcolsep}{20pt}
+\renewcommand{\arraystretch}{1.5}
+\startdata 
+CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.05\substack{+0.15\\-0.11}$ &$10.78\substack{+0.18\\-0.15}$ & $10.45\substack{+0.18\\-0.15}$ \\[3pt]
+CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.41\substack{+0.15\\-0.11}$ &$10.14\substack{+0.18\\-0.15}$ & $9.99\substack{+0.18\\-0.15}$ \\[3pt]
+CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.86\substack{+0.52\\-0.23}$ &$10.59\substack{+0.53\\-0.25}$ & $10.43\substack{+0.53\\-0.25}$ \\[3pt]
+CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.05\substack{+0.03\\-0.03}$ &$10.78\substack{+0.10\\-0.10}$ & $10.64\substack{+0.10\\-0.10}$ \\[3pt]
+CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.18\substack{+0.11\\-0.09}$ &$10.91\substack{+0.14\\-0.13}$ & $10.77\substack{+0.14\\-0.13}$ \\[3pt]
+CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.08\substack{+0.15\\-0.11}$ &$10.81\substack{+0.18\\-0.15}$ & $10.69\substack{+0.18\\-0.15}$ \\[3pt]
+CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.16\substack{+0.14\\-0.11}$ &$10.89\substack{+0.17\\-0.15}$ & $10.75\substack{+0.17\\-0.15}$ \\[3pt]
+CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $10.98\substack{+0.02\\-0.02}$ &$10.71\substack{+0.10\\-0.10}$ & $10.02\substack{+0.10\\-0.10}$ \\[3pt]
+CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.13\substack{+0.03\\-0.03}$ &$10.86\substack{+0.10\\-0.10}$ & $10.25\substack{+0.10\\-0.10}$ \\[3pt]
+CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.11\substack{+0.04\\-0.04}$ &$10.84\substack{+0.10\\-0.10}$ & $10.21\substack{+0.10\\-0.10}$ \\[3pt]
+CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.07\substack{+0.35\\-0.19}$ &$10.80\substack{+0.36\\-0.21}$ & $10.65\substack{+0.36\\-0.21}$ \\[3pt]
+CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.70\substack{+0.16\\-0.12}$ &$10.43\substack{+0.19\\-0.15}$ & $9.73\substack{+0.19\\-0.15}$ \\[3pt]
+CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.73\substack{+0.22\\-0.15}$ &$10.46\substack{+0.24\\-0.18}$ & $10.12\substack{+0.24\\-0.18}$ \\[3pt]
+CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.02\substack{+0.23\\-0.15}$ &$10.75\substack{+0.25\\-0.18}$ & $10.59\substack{+0.25\\-0.18}$ \\[3pt]
+CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $10.98\substack{+0.12\\-0.10}$ &$10.72\substack{+0.16\\-0.14}$ & $10.58\substack{+0.16\\-0.14}$ \\[3pt]
+LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.32\substack{+0.09\\-0.07}$ &$11.05\substack{+0.13\\-0.12}$ & $10.46\substack{+0.13\\-0.12}$ \\[3pt]
+LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.12\substack{+0.09\\-0.08}$ &$10.86\substack{+0.13\\-0.12}$ & $10.69\substack{+0.13\\-0.12}$ \\[3pt]
+LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.08\substack{+0.06\\-0.05}$ &$10.81\substack{+0.11\\-0.11}$ & $10.08\substack{+0.11\\-0.11}$ \\[3pt]
+XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.89\substack{+0.07\\-0.06}$ &$10.63\substack{+0.12\\-0.12}$ & $10.04\substack{+0.12\\-0.12}$ \\[3pt]
+XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.15\substack{+0.12\\-0.10}$ &$10.88\substack{+0.16\\-0.14}$ & $10.76\substack{+0.16\\-0.14}$ \\[3pt]
+XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.12\substack{+0.26\\-0.16}$ &$10.85\substack{+0.28\\-0.19}$ & $10.10\substack{+0.28\\-0.19}$ \\[3pt]
+CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ...
+& ...
+& ...
+& $10.71\substack{+0.16\\-0.12}$ &$10.45\substack{+0.19\\-0.15}$ & $10.3\substack{+0.19\\-0.15}$ \\[3pt]
+CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ...
+& ...
+& ...
+& $10.90\substack{+0.06\\-0.05}$ &$10.63\substack{+0.12\\-0.11}$ & $9.90\substack{+0.12\\-0.11}$ \\[3pt]
+CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ...
+& ...
+& ...
+& $11.52\substack{+0.28\\-0.17}$ &$11.25\substack{+0.30\\-0.20}$ & $11.03\substack{+0.30\\-0.20}$ \\[3pt]
+CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ...
+& ...
+& ...
+& $10.06\substack{+0.23\\-0.15}$ &$9.79\substack{+0.25\\-0.18}$ & $9.39\substack{+0.25\\-0.18}$ \\[3pt]
+ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ...
+& ...
+& ...
+& $11.16\substack{+0.12\\-0.10}$ &$10.89\substack{+0.16\\-0.14}$ & $10.53\substack{+0.16\\-0.14}$ \\[3pt]
+SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ...
+& ...
+& ...
+& $10.75\substack{+0.09\\-0.08}$ &$10.49\substack{+0.14\\-0.13}$ & $10.16\substack{+0.14\\-0.13}$ \\[3pt]
+SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ...
+& ...
+& ...
+& $10.80\substack{+0.11\\-0.09}$ &$10.54\substack{+0.15\\-0.13}$ & $10.15\substack{+0.15\\-0.13}$ \\[3pt]
+SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ...
+& ...
+& ...
+& $10.77\substack{+0.07\\-0.06}$ &$10.51\substack{+0.12\\-0.12}$ & $10.34\substack{+0.12\\-0.12}$ \\[3pt]
+SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ...
+& ...
+& ...
+& $11.19\substack{+0.13\\-0.10}$ &$10.92\substack{+0.17\\-0.14}$ & $10.62\substack{+0.17\\-0.14}$ \\[3pt]
+SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ...
+& ...
+& ...
+& $9.95\substack{+0.47\\-0.22}$ &$9.68\substack{+0.48\\-0.24}$ & $9.48\substack{+0.48\\-0.24}$ \\[3pt]
+SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ...
+& ...
+& ...
+& $11.03\substack{+0.21\\-0.14}$ &$10.76\substack{+0.23\\-0.17}$ & $10.47\substack{+0.23\\-0.17}$ \\[3pt]\enddata
+\label{tab:result_sersic}
+\tablecomments{
+Column~1: Object ID.
+Column~2-6: WFC3 inference. 
+Column~2: Reduced $\chi ^2$ value by the best PSF in the library.
+Column~7-9: ACS inference. 
+Column~10: Observed host luminosity in the rest-frame R band.
+Column~11: Host total stellar mass.
+Column~12: Bulge stellar mass, based on Section~\ref{sec:bh_bulge} and Figure~\ref{fig:BT-n_relation}.
+}
+\end{deluxetable*}
+
+\begin{table}
+\centering
+    \caption{The inference of $\gamma$ using \mbh-\smass\ by different sample combination.}\label{table:diff_sample_gam}
+     \resizebox{5.5cm}{!}{
+     \begin{tabular}{cc}
+     \hline
+     Sample combination & $\gamma$ \\
+     &\\
+     \hline\hline
+32 AGNs & 0.78$\pm$0.26\\    
+30 AGNs (excluded outliers) & 0.65$\pm$0.27\\    
+32 AGNs + intermediate &  0.58$\pm$0.20\\
+32 AGNs bulge only & 1.63$\pm$0.27\\
+     \hline
+     \end{tabular}}
+\tablecomments{These values are directly inference for the observation, which haven't yet taken the selection effect into account.}
+\end{table}
+
+\begin{table}
+\centering
+    \caption{The summary for the different inference of $\gamma$.}\label{table:gamma_sf}
+     \resizebox{8cm}{!}{
+     \begin{tabular}{cccc}
+     \hline
+     Sample & Selection effects &  \mbh-\smass & \mbh-\lhost \\
+     &&&\\
+     \hline\hline
+32 AGNs + intermediate & No &  0.58$\pm$0.20 & 0.61$\pm$0.18 \\
+32 AGNs + intermediate& Yes & 0.80$\pm$0.30 & 0.60 $\pm$ 0.30 \\
+32 AGNs & No & 0.78$\pm$0.26  & 0.99$\pm$0.23\\
+32 AGNs& Yes & 1.30$\pm$0.50 & 1.70$\pm$0.40 \\
+     \hline
+     \end{tabular}}
+    \tablecomments{
+    Entire sample includes the 32 AGNs and the intermediate redshift AGNs from the reference in Section~\ref{sec:compare_sample}.
+Note that the adopted \lhost\ have been transferred to today assuming the passive evolution scenario using Equation~\ref{eq:L_relation}.
+The results of selection effects used the lognormal prior of \sint.
+}
+\end{table}
+
 \end{document}

### 2019-07-08 M_BH_relation/MM_all_vz_bulge.py

@@ -168,8 +168,8 @@ if style ==1:
     #####################
     value,sig=round(b_ml_offset,2),round((np.percentile(samples,84,axis=0)[0]-np.percentile(samples,16,axis=0)[0])/2,2)
     print value,sig
-    value,sig = 1.71, 0.27
-    plt.text(0.15, -1.75, "$\Delta$log$M_{BH}$=$(%s\pm%s)$log$(1+z)$"%(value,sig),color='blue',fontsize=25)
+#    value,sig = 1.71, 0.27
+#    plt.text(0.15, -1.75, "$\Delta$log$M_{BH}$=$(%s\pm%s)$log$(1+z)$"%(value,sig),color='blue',fontsize=25)
 
 
 plt.xlabel("log$(1+z)$",fontsize=35)
@@ -204,5 +204,16 @@ plt.legend([Bkc, Hkc, new_sample],[
 "Local by H&R",
 "High-z bulge"
 ],scatterpoints=1,numpoints=1,loc=2,prop={'size':28},ncol=2,handletextpad=0)
-plt.savefig("MBH-Mbulge-style{0}.pdf".format(style))
+#plt.savefig("MBH-Mbulge-style{0}.pdf".format(style))
 plt.show()
+
+##%%Print the Mstar:
+#tab_list = ['CID1174', 'CID1281', 'CID206', 'CID216', 'CID237', 'CID255', 'CID3242', 'CID3570',
+#            'CID452', 'CID454', 'CID50', 'CID543', 'CID597', 'CID607', 'CID70', 'LID1273',
+#            'LID1538', 'LID360', 'XID2138', 'XID2202', 'XID2396', 'CDFS-1', 'CDFS-229',
+#            'CDFS-321', 'CDFS-724', 'ECDFS-358', 'SXDS-X1136', 'SXDS-X50', 'SXDS-X717', 'SXDS-X735', 'SXDS-X763', 'SXDS-X969']
+#for i in range(len(tab_list)):
+#    j = [jj for jj in range(len(ID)) if tab_list[i] == ID[jj]][0]
+##    print tab_list[i], ID[j]
+#    print tab_list[i], round(Mstar[j],2)
+#

### 2019-07-08 M_BH_relation/MM_all_vz_rest_ourownMBH.py

@@ -85,24 +85,9 @@ Re_results = np.asarray(load_re(ID))
 #####fit the evolution##########
 ################################
 z_cosmos, y_cosmos = zs, MBs-(m_ml*Mstar+b_ml)
-                              
 
-#    z=np.concatenate((z_cosmos),axis=0)
-#    y=np.concatenate((y_cosmos),axis=0)
-
-#    yerr_imd= np.zeros(len(z_ss)+len(z_b11))+(0.4**2+0.2**2)**0.5   # the error for the fitting
 yerr_hz = (yerr_highz[0]+ yerr_highz[1])/2
-#    yerr = np.concatenate((yerr_imd, yerr_hz),axis=0)
-#    yerr = np.sqrt(yerr**2 + sint_ml**2)
 
-##if consider 32 AGN only:
-#z=z_cosmos
-#y=y_cosmos
-#yerr = yerr_hz    
-
-#if exclude the top 4 y cosmos:
-#bools = [[Re_results[:,0]>0.2][0] * [y_cosmos<0.844][0]]
-#bools = [y_cosmos<0.844]
 bools = [Re_results[:,0]>0][0]  #Select all sample
 z=z_cosmos[bools]
 y=y_cosmos[bools]
@@ -130,11 +115,9 @@ def lnlike(theta, x, y, yerr):
 import scipy.optimize as op
 nll = lambda *args: -lnlike(*args)
 result = op.minimize(nll, [1.8, 0.3], args=(x, y, yerr))
-b_ml, _= result["x"]
-#print b_ml, sint_ml, "ka=",lnlike(theta=[b_ml, sint_ml],x=loc[:,0], y=loc[:,1], yerr=loc[:,2])
+b_ml_z, _= result["x"]
 
 xp = np.array([5, 13])
-#plt.plot(xp, m_ml*xp+b_ml, 'r-')
 def lnprior(theta):
     b, sint	 = theta
     if -10 < b < 10.0 and 0 < sint < 10:
@@ -152,10 +135,10 @@ sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(x, y, yerr))
 sampler.run_mcmc(pos, 500)
 samples = sampler.chain[:, 50:, :].reshape((-1, ndim))
 
-b_ml, _ =np.percentile(samples, 50,axis=0)
-#print "lnlike=",lnlike(theta=[b_ml, sint_mid],x=x, y=y, yerr=yerr)
+b_mid_z, _ =np.percentile(samples, 50,axis=0)
[…]

### 2019-07-10 manuscript/manuscript.tex
Push before circulate

@@
 
-\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{4}, Malte Schramm\altaffilmark{4}, Simon Birrer\altaffilmark{1}, Daeseong Park\altaffilmark{5}, Knud Jahnke\altaffilmark{6}, {\color{blue} Federica Duras\altaffilmark{7, 8}, Angela Bongiorno\altaffilmark{8}}
+\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{4}, Malte Schramm\altaffilmark{4}, Simon Birrer\altaffilmark{1}, Daeseong Park\altaffilmark{5}, Knud Jahnke\altaffilmark{6}, ???, ???
+% {\color{blue} Federica Duras\altaffilmark{7, 8}, Angela Bongiorno\altaffilmark{8}}
  }
@@
 \altaffiltext{6}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117, Heidelberg, Germany}
-\altaffiltext{7}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
-\altaffiltext{8}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
+%\altaffiltext{7}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
+%\altaffiltext{8}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
 \begin{abstract}
 
-The correlations between the mass of a supermassive black hole (SMBH) and its host galaxy properties (e.g.
-stellar mass \smass, luminosity \lhost) suggests an evolutionary connection.
-A powerful test of this co-evolution hypothesis is to measure the relations \mbh-\lhost\ and \mbh-\smass~(total) at high redshift and compare with the local relation.
-For this purpose, we obtained multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
-By applying state-of-the-art tools to decompose the \hst\ emission, we obtained accurate measurements of the host galaxy luminosity and stellar mass.
-The black hole mass (\mbh) is based on near-infrared spectroscopic observations of the broad \halpha~line, which avoids potential uncertainties associated with \Mgii\ or \Civ\ .
-%We find that the observed ratio of \mbh/\smass ~is 0.0035, a 0.24~dex offset as compared to the local relation that would lead to a evolution as \mbh/\smass$\propto(1+z)^\gamma$ with $\gamma = 0.80\pm0.30$.
-However, we expect an offset of 0.21 dex at these redshifts due to a selection bias thus the high-$z$ sample is consistent with the local sample if considering this effect.
-This is in agreement with the lack of evolution seen in the \mbh/\lhost ~ratios of our sample.
-Therefore, our results depict a scenario where SMBHs and their host galaxies co-evolve with the possibility for SMBHs to have slightly elevated masses, considering the observed ratios, that may indicate that galaxies with lower angular momentum at high-$z$ may be a bit more efficient to grow their black holes at earlier cosmic times.
-In any case, the bulge \smass ~mass at a given black hole mass is clearly discrepant with the local relation, since the hosts have a significant amount of stellar mass in a disk, thus leaving the open question as to whether the connection to the bulge is relevant for black hole growth.
-{\color{blue}
-We find that the observed ratio of \mbh/\smass is larger at $z\sim1.7$ than the one in the local universe.
-However, when accounting for the selection effect (using two independent methods), we find that the high redshift points can be consistent with the local relation, assuming the scatter is unchanged or larger.
-The relationship between \mbh\ and host galaxy total luminosity paints a similar picture: the ratio is larger than the local universe, but given the uncertainties and selection effects one cannot conclude that the offset is significant.
-Therefore, given the uncertainties, our results are consistent with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former is somewhat anticipated.
-Considering that the local relationships general apply to bulges, and our hosts have a significant amount of stellar mass in a disk, observations are consistent with a scenario in which stellar mass and luminosity is transferred from the angular momentum supported to the pressure supported component of the galaxy by secular processes or minor mergers at a faster rate than that of mass accretion onto the SMBH.
-}
+Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g.
+stellar mass \smass, luminosity \lhost) suggest an evolutionary connection.
+A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates.
+For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
+By applying state-of-the-art tools to decompose the \hst\ emission, we measured the host galaxy luminosity and stellar mass along with other properties through 2D model fitting.
+The black hole mass (\mbh) is determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators.
+We find that the  {\it observed} ratio of \mbh/\smass~is larger at $z\sim1.5$ by a factor of $\sim2.2$ as compared to that in the local universe, while the scatter is as low as in the local universe.
+However, when accounting for selection effects (estimated using two independent and complementary methods), we find that no-evolution is consistent with the data at the 95\% CL, both using our sample by itself and in combination with literature data.
+The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
+Therefore, given the uncertainties, our results are in agreement with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former is somewhat slightly anticipated.
+Using a mass-matched sample of inactive galaxies to infer the bulge-to-total mass fraction we show that the bulge \mbh/\bmass~relation is significantly offset from the local one by a factor of $\sim4.5$; this offset is still present even after accounting for selection effects.
+Thus, our observations are consistent with a scenario in which stellar mass is transferred from an angular momentum supported to the pressure supported component of the galaxy through secular processes or minor mergers at a faster rate than the mass accretion onto the SMBH.
 
@@
 For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today.
-Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass\ and \mbh-\sigstar\ relations.
-Of similar results, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies; although, the accuracy of such an approach has not yet been well established.
+Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass\ and \mbh-\sigstar\ relations, especially when the data are sufficiently good to isolate the luminosity or stellar mass of the bulge or spheroidal component.
+Of similar results, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies; although, the accuracy of such an approach for luminous AGNs has not yet been well established.
 If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.
-
-However, there are studies \citep{Cisternas2011,SS13,Mechtley2012} based on \hst\  imaging of deep survey fields such as COSMOS and CDFS that report no evolution in the \mbh - \smass ~ mass ratio as compared to the local relation.
-In support, \citet{Sun2015} has re-analyzed the mass ratios for BLAGN in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citep{Merloni2010} and finds no evolution when accounting for selection effects \citep{Schulze2014} that consider the black hole mass functions and Eddington rate distribution.
-As highlighted below, samples based on 2D image analysis using \hst\ at $z>1$ are limited thus the infrared capabilities of \hst/WFC3 have not been fully exploited to date on this topic.
-
-In order to make progress, it is important to reduce as much as possible the uncertainties and take great care of selection effects and systematic errors.
+A possible mechanism to account for the latter part of the growth of the galaxy without increasing \mbh\ is the transfer of stellar mass from the disk to the bulge \citep{Bennert++2011}.
+
+However, there are studies \citep{Cisternas2011,SS13,Mechtley2016} based on \hst\  imaging of deep survey fields such as COSMOS and CDFS that report no evolution in the \mbh - \smass ~ mass ratio as compared to the local relation.
+In support, \citet{Sun2015} has re-analyzed the mass ratios for BLAGN in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citet{Merloni2010} and finds no evolution when accounting for selection effects, as fully described in \citet{Schulze2014} that consider the black hole mass functions and Eddington rate distribution.
+
+In order to make progress, it is important to construct statistical high-$z$ samples that reduce as much as possible the uncertainties, and carefully consider selection effects and inherent systematic errors.
 First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method.
@@
 
-Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$.
+Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$~(M$_{\odot}$).
 The bolometric luminosities presented in \citet{Schulze2018} are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
-We are able to select the sample which have higher Eddington ratios when \mbh\ is lower, to assure the AGN is still activate, as shown in Figure~\ref{fig:selection}.
-Moreover, we have higher preference to select targets which have rest-frame UV images as provided by \citet{Scoville2007}.
-We list all the AGN systems analyzed in this work (Table~\ref{tab:objlist}).
-
-%\subsection{Black hole mass and Eddington ratios}
-\begin{figure}
-\centering
-{
-\includegraphics[height=0.5\textwidth]{fig/AGN_selection.pdf}
-}
-\caption{\label{fig:selection} 
-We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($\lambda = L_{\rm Bol}/L_{\rm Edd}$) and \mbh.
-Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}.
-We also control the sample to have higher Eddington ratios when their \mbh\ is lower, to guarantee the AGN activity.
-For comparing propose, we plot the high-$z$ luminous SDSS QSO samples that has been studied based on the observation of \hst\ in the reference~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}.
-}
-\end{figure}
-
-\begin{deluxetable*}{llccccc}
-\tablecolumns{7}
-\tablewidth{0pt}
-\tablecaption{Details of Observation} 
-\tablehead{ 
-\colhead{Object ID} &
-\colhead{$z$} & 
-\colhead{WFC3/Filter} &
-\colhead{$RA$}&
-\colhead{$DEC$}&
-\colhead{Observing date}&
-\colhead{Exposure time (s)}
-\\ 
-\colhead{(1)} &
-\colhead{(2)} &
-\colhead{(3)} &
-\colhead{(4)} &
-\colhead{(5)} &
-\colhead{(6)} &
-\colhead{(7)}
-} 
-\startdata
-%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
-%\\
-COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
-COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
-COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
-COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
-COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
-COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
-COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
-COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
-COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
-COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
-COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
-COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
-COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
-COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
-COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
-COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
-COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
-COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
-COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
-COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
-COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
-CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
-CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
-CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
-CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
-ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
-SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
-SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
-SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
-SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
-SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
-SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
-\enddata
-\label{tab:objlist}
-\tablecomments{
-Column 1: Object field and ID.
-Column 2: Redshifts.
-Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
-Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
-Column 6: The observing start date.
-Column 7: Total exposure time.
-}
-\end{deluxetable*}
-
-\subsection{Expected bias from the selection function}
-
-\label{sec:sf_framework}
-
-Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios.
-It is well known that sample selection effects must be taken into account in order to  interpret the observed black hole-host relations and measure its evolution with redshift avoiding bias ~\citep{Schulze2011, Tre++07, Bennert++2011, Park15}.
-The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (like AGN luminosity and line strength and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors.
-
-Correcting for observational biases requires a well-characterized selection function, such as the one we have for our sample, and a model of the black hole mass function, and the evolution of the correlations between \mbh, and other properties.
-
-In order to get a sense for the amount of bias that we can anticipate given our selection function, we use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias.
-In this framework, under the assumption of no evolution of the correlations between \mbh\ and host-galaxy properties, one can compute the expected bias for a given sample, prior to observations.
-The key ingredient of this model are the local \mbh\ host-galaxy property correlations, the black hole mass function and Eddington ratio distribution at the redshift of observation.
-The latter two quantities are estimated from the type-1 AGN distributions corrected to represent the parent population of all SMBH hosts, including the inactive ones.
-
-Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model.
-{\bf TT: we should say something about the uncertainty here for example the following.} This bias correction should be considered an approximate estimate, with an uncertainty that depends on the uncertainty of the inputs.
-Furthermore, if the scaling relations actually evolve, one needs to introduce a model for the evolution in order to infer the underlying bias-corrected trends.
-We will revisit these issues in Section~\ref{select_eff}.
+The flux-limited nature of the sample results in higher Eddington ratios when \mbh\ is lower as shown in Figure~\ref{fig:selection}.
+Moreover, we have higher preference to select targets which have rest-frame UV images as provided by \citet{Scoville2007} and \citet{Koekemoer2007} in the COSMOS field and REFS for the (E)-CDF-S.
+We list the AGNs observed with \hst/WFC3 and analyzed in this work in Table~\ref{tab:objlist} sorted by field and redshift.
 
@@
 Thus, we adopt the scheme given in \citet{Schulze2018} that is based on the recalibration of these relations using luminous quasars out to high redshift \citep{Jun2015} :
+
+To avoid any systematic bias between samples in the literature, we aim to adopt a class of self-consistent estimators for our sample.
+We first compare the estimators implemented in \citet{Schulze2018} to the those in \citet{Ding2017b}, and find that their \hbeta(FWHM(5100)) estimators are very consistent (\mbh\ r.m.s.
+$<0.03$~dex).
+However, there is a $\sim~0.2$~dex inconsistency in their \halpha\ estimators.
+Thus, we utilize the AGNs in \citet{Schulze2018} that have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to determine which \halpha\ estimator has been agreement between the two lines.
+As a  result, the \halpha\ estimator in \citet{Schulze2018} has better agreement with \hbeta\  .
+Thus, we adopt the scheme given in \citet{Schulze2018} for all AGN samples used in this study including the comparison samples described below.
 
@@
 
-Using these recipes, we estimate \mbh\ by adopting the emission-line properties as measured by \citet{Schulze2018} for 29 of our 32 AGNs.
-The remaining three (i.e.
-CDFS-1, CDFS-229 and CDFS-724) have information on their \halpha\ emission lines provided by \citet{Suh2015}.
-While fourteen AGN have emission line properties for both \halpha\ and \hbeta\, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample.
+Using these recipes, we estimate \mbh\ by adopting the emission-line properties as measured by \citet{Schulze2018} for all 32 AGNs.
+The three objects (i.e.
+CDFS-1, CDFS-229 and CDFS-724) have infrared spectra provided by \citet{Suh2015}.
+While fourteen AGN have emission line properties for both \halpha\ and \hbeta, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample.
 It is worth noting that the absolute flux calibration of the FMOS spectra is set to match ground-based IR imaging, ULTRAVISTA in the case of COSMOS thus amounting to an effective aperture correction.
@@
 
-\begin{deluxetable*}
-{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
-\tablecolumns{9}
-\tablewidth{0pt}
-\tablecaption{Inferred BH properties for the 32 systems} 
-\tablehead
-{ 
-\colhead{Target ID}&
-  \multicolumn{4}{c}{using emission line \halpha}&
-  \multicolumn{4}{c}{using emission line \hbeta} \\
-  \cline{2-5}  \cline{6-9} \\
-\colhead{}& 
-\colhead{FWHM}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
-\colhead{FWHM(5100)}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
-\colhead{}& 
-\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
-\colhead{(M$_{\odot}$)}& (log$\lambda$)&
-\colhead{(\kms)}& 
-\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$\lambda$)\\
-\colhead{(1)}& 
-\colhead{(2)}& \colhead{(3)}& 
-\colhead{(4)}& \colhead{(5)}& 
-\colhead{(6)}&\colhead{(7)}&
-\colhead{(8)}& \colhead{(9)}
-}
-\startdata 
-CID1174 & 1906 & 43.43 & 7.99 & -0.50 & 5898 & 44.76 & 8.83& -1.35 \\
-CID1281 & 1619 & 43.24 & 7.75 & -0.45 & ... & ... & ...& ... \\
-CID206 & 3334 & 43.48 & 8.53 & -1.00 & ... & ... & ...& ... \\
-CID216 & 2230 & 42.85 & 7.85 & -0.93 & ... & ... & ...& ... \\
-CID237 & 2112 & 43.86 & 8.29 & -0.40 & ... & ... & ...& ... \\
-CID255 & 1932 & 43.99 & 8.27 & -0.25 & 3709 & 45.37 & 8.73& -0.63 \\
-CID3242 & 2543 & 43.83 & 8.45 & -0.58 & 3775 & 45.10 & 8.61& -0.78 \\
-CID3570 & 1959 & 43.16 & 7.89 & -0.66 & ... & ... & ...& ... \\
-CID452 & 3458 & 42.92 & 8.30 & -1.30 & 3127 & 44.63 & 8.22& -0.88 \\
-CID454 & 2824 & 43.34 & 8.31 & -0.91 & ... & ... & ...& ... \\
-CID50 & 2340 & 43.94 & 8.42 & -0.45 & 1939 & 45.33 & 8.15& -0.09 \\
-CID543 & 2189 & 43.57 & 8.19 & -0.56 & ... & ... & ...& ... \\
-CID597 & 1656 & 43.33 & 7.81 & -0.42 & ... & ... & ...& ... \\
-CID607 & 3009 & 43.67 & 8.53 & -0.81 & 4242 & 44.78 & 8.56& -1.06 \\
-CID70 & 2480 & 43.51 & 8.27 & -0.71 & 3982 & 45.16 & 8.69& -0.80 \\
-LID1273 & 3224 & 43.61 & 8.56 & -0.90 & ... & ... & ...& ... \\
-LID1538 & 2941 & 43.60 & 8.47 & -0.83 & ... & ... & ...& ... \\
-LID360 & 2482 & 43.88 & 8.45 & -0.53 & 2869 & 45.09 & 8.37& -0.55 \\
-XID2138 & 3186 & 43.61 & 8.55 & -0.89 & 2945 & 44.81 & 8.25& -0.72 \\
-XID2202 & 2973 & 43.56 & 8.46 & -0.85 & ... & ... & ...& ... \\
-XID2396 & 2271 & 44.06 & 8.46 & -0.37 & 2658 & 45.50 & 8.51& -0.27 \\
-CDFS-1 & 5449 & 43.08 & 8.79 & -0.98 & ... & ... & ...& ... \\
-CDFS-229 & 2254 & 43.30 & 8.08 & -0.48 & ... & ... & ...& ... \\
-CDFS-321 & 2442 & 43.93 & 8.46 & -0.50 & ... & ... & ...& ... \\
-CDFS-724 & 3352 & 42.56 & 8.09 & -1.22 & ... & ... & ...& ... \\
-ECDFS-358 & 2237 & 43.40 & 8.12 & -0.67 & ... & ... & ...& ... \\
-SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.85 & 6761 & 44.71 & 8.93& -1.50 \\
-SXDS-X50 & 1817 & 43.42 & 7.94 & -0.47 & ... & ... & ...& ... \\
-SXDS-X717 & 2931 & 43.05 & 8.20 & -1.08 & ... & ... & ...& ... \\
-SXDS-X735 & 2702 & 43.70 & 8.44 & -0.70 & 3520 & 45.07 & 8.54& -0.73 \\
-SXDS-X763 & 2961 & 43.57 & 8.47 & -0.84 & 4509 & 44.51 & 8.47& -1.27 \\
-SXDS-X969 & 2296 & 43.50 & 8.20 & -0.64 & 1696 & 45.05 & 7.90& -0.11 \\
-\enddata
-\label{tab:result_mbh}
-\tablecomments{
-Column 1: Object ID.
-Column 2-5: \halpha\ emission line width (FWHM), continuum luminosity, inferred \mbh\ and Eddington ratio.
-Column 6-9: \hbeta\ emission line BH properties. 
-The typical uncertainty level for FWHM and $\log( \rm L _{\lambda})$ are $15\%$ and $\pm0.01$, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
-}
-\end{deluxetable*}
+\subsection{Expected bias from the selection function}
+
+\label{sec:sf_framework}
+
+Our AGN sample is primarily selected based on the value of \mbh~and Eddington ratio.
+It is well known that sample selection effects must be taken into account in order to  interpret the observed black hole-host relations and measure its evolution with redshift thus avoiding well understood biases ~\citep{Tre++07,Schulze2011,Bennert++2011, Schulze2014,Park15}.
+The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (like AGN luminosity and line strength and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors.
+Correcting for observational biases requires a well-characterized selection function, such as the one we have for our sample, and a model of the black hole mass function, and the evolution of the correlations between \mbh, and other properties.
+
+To assess the amount of bias that we can anticipate given our selection function, we use the Bayesian framework introduced by \citet{Schulze2011,Schulze2014} to estimate the expected bias.
+In this framework, under the assumption of no evolution of the correlations between \mbh\ and host-galaxy properties, one can compute the expected bias for a given sample, prior to the observations.
+The key ingredient of this model are the local \mbh\ host-galaxy property correlations, the black hole mass function and Eddington ratio distribution at the redshift of observation.
+The latter two quantities are estimated from the type-1 AGN distributions \citep{Schulze2015} and corrected to represent the parent population of all active SMBH hosts thus including the obscured cases.
+
+Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model.
+This bias correction should be considered an approximate estimate, with an uncertainty that depends on the uncertainty of the inputs.
+Furthermore, if the scaling relations actually evolve, one needs to introduce a model for the evolution in order to infer the underlying bias-corrected trends.
+We will revisit these issues in Section~\ref{select_eff}.
 
@@
 % The AGN surface photometry in IR Channel Filters.\\
-High spatial resolution imaging is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass.
-For this purpose, all the new 32 AGN systems were observed with the \hst/WFC3 infrared channel, as part of the \hst\ program GO-15115, PI: John Silverman.
-We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets.
-This selection ensures that the broad \halpha\ line is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.
+High spatial resolution imaging is required for the decomposition of the nuclear and host emission to accurately estimate the luminosity and stellar mass of the host galaxy.
+For this purpose, we observed the sample of 32 AGNs, as described above, with the \hst/WFC3 infrared channel, through the \hst\ program GO-15115 (PI: John Silverman).
+We elected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets so that the rest-frame spectral window was well above the 4000~\angstrom\ break.
+This selection further ensures that the broad \halpha\ line is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.
 
 %Drizzling, background noise...
-For each of the 32 new AGNs, we obtained six separate exposures with $\sim399s$ (i.e.
-total exposure time $\sim2394s$).
-The six exposures for each dither image were combined with the {\sc astrodrizzle} software package, with an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 using the \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted.
+For each target, we obtained six separate exposures of 399s (i.e., total exposure time 2394s).
+The six exposures were dithered and combined with the {\sc astrodrizzle} software package that resulted in an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 and using a \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted.
 We achieve to analyze this sample using the same approach, taking the 3 available frames.}.
-To accurately estimate the background light which could come from both the sky and the detector, we adopt the {\sc photutils} tool. We list the details of the observation in Table~\ref{tab:objlist}.
+We use the {\sc photutils} tools to accurately estimate the background light which could come from both the sky and the detector.
+In Table~\ref{tab:objlist}, we list the details of the individual observations.
 
 Multi-band information provides the SED at a more precise level.
-21/32 objects in our sample have rest-frame UV images by \citet{Scoville2007}.
-Images were taken through the wide ACS/F814W filter at four dither pointing with $507s$ exposures.
+A substantial fraction (21/32) of our objects have rest-frame UV images for those in COSMOS \citep{Koekemoer2007} and CDFS.
+Here, we utilize images taken with ACS/F814W filter.
 The final image is drizzled to 0\farcs{03} pixel scale.
-Given the multi-band image for these systems, we are able to infer their host color and assess the contribution of both the young and old stellar population which insures an accurate inference of rest-frame R-band luminosity by K-correction, stellar mass and star formation rate (SFR) \citep{Gallazzi2009} .
+Given the multi-band images for our AGN, we are able to infer their host color and assess the contribution of both the young and old stellar population which insures an accurate inference of rest-frame R-band luminosity (including a K-correction) and stellar mass \citep{Gallazzi2009}.
 
@@
 %Introduce the PSF library
-The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the point source is bright relative to the host.
-The PSF is known to be vary across the detector and with time, due to the effects of aberrations and breathing.
-Simulated PSF, such as {\sc TinyTim} ones, are usually insufficient matches to observations for our purposes \citet{Mechtley2012}.
-Stars within the fields provide a better description than the simulated PSF, since they were observed simultaneously with the science targets and reduced and analyzed in the same way \citet{Kim2008, Park15}
-
-To minimize the impact of the mismatch, we build a PSF library by selecting all the isolated, unsaturated PSF-stars with high S/N from our entire program.
+
+The knowledge of the PSF is crucial for imaging decomposition of the AGN and its host, especially when the point source contributes to the majority of the total emission.
+The PSF is known to vary across the detector and in time due to the effects of aberration and breathing.
+Simulated PSF, such those based on {\sc TinyTim}, are usually insufficient for our purposes \citep{Mechtley2012}.
+Stars within the field-of-view of each observation provide a better description than the simulated PSF since they are observed simultaneously with the science targets, and reduced and analyzed in a consistent manner \citet{Kim2008, Park15}.
+Actually, we have found that such stars usually do not provide an ideal PSF for de-blending the AGN and host galaxy through extensive tests.
+The issues have to due with an insufficient number of bright stars near our targets, color differences, and other effects not fully understood.
+
+To minimize the impact of such mismatches, we build a PSF library by selecting all the isolated, unsaturated PSF-stars with high S/N from our entire program.
 The selection consists of the following steps.
-We first adopt the identified stars as candidates from the COSMOS2015 catalog by \citet{Laigle2016}.
-A lot of bright stars with intensity similar to the AGNs were excluded by \citet{Laigle2016}; besides the COSMOS2015 catalog, we manually select the PSF-like objects as candidates.
-We then remove the non-ideal PSF candidates based on their intensity, FWHM, central symmetry and any that were contaminated by nearby objects.
-In the end, the PSF library contains 78 and 37 PSFs imaged through filters F140W and F125W, respectively.
-
+First, we identify stars from the COSMOS2015 catalog \citep{Laigle2016}.
+Unfortunately, many bright stars with an intensity similar to our AGN sample were excluded in this catalog.
+Therefore, we manually select PSF-like objects as candidates from the \hst/WFC3 imaging.
+We then discard non-ideal PSF candidates based on their intensity, FWHM, central symmetry, and presence of nearby contaminants.
+In total, the PSF library contains 78 and 37 stars imaged through filters F140W and F125W, respectively.
 We assume that the stars in the library are representative of the possible PSFs in our program.
-Therefore, the PSF library gives a good representation of the dominant source of uncertainty as well as the best fit.
+The dispersion of PSF shapes within our library provides us with a good representation of the level of uncertainty in our measurements resulting from the image decomposition.
 %In the next subsection, we carry out the AGN decomposition using each PSF.
@@
 %\subsubsection{Surface Photometry modeling method}
+
+\begin{figure*}
+\centering
+%\hspace{-5.5em}
+{
+\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
+\caption{\label{fig:AGN_decomp} AGN-host galaxy decomposition of COSMOS-CID1174 based on the \hst/WFC3 F140W image.The panels from left to right are as follows: (1) observed data, (2) best-fit model (AGN+host), (3) data minus the model PSF (i.e., host galaxy free of the AGN), (4) residuals divided by the variance and (5) 1-D surface brightness profiles (top) and the corresponding residual (bottom).
+The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects).
+Note that the 1-D surface brightness profiles are only for illustration purposes.
+The actual fitting is based on the two-dimensional images.
+The remaining 31 objects in the sample are shown in Appendix~\ref{sec:restsample}.
+}}
+\end{figure*}
+
 \section{AGN-host Decomposition}
@@
 The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties.
-The answers would not change significantly if we had chosen a different number of PSFs, as we show below.
-
-Note that since each AGN system was observed in different location of the detector and at a different time, the top-eight PSFs usually vary from one AGN system to another.
-Given the weights, the inferred value of host properties and the root-mean-square ($\sigma$) are calculated as:
+The results do not change significantly if we chose a different number of PSFs, as shown below.
+
+Note that since each AGN was observed in different location of the detector and at a different time, the top-eight PSFs usually vary from one AGN to another.
+Given the weights, the value of host properties and the root-mean-square ($\sigma$) error are calculated as:
 \begin{eqnarray}
 \label{eq:infer_value}
-\bar{x}  =  \frac{  \sum_{i=1}^{8}   x_i * w_i  }{\Sigma w_i} ,
+\bar{x}  =  \frac{  \sum_{i=1}^{N}   x_i * w_i  }{\Sigma w_i} ,
 \end{eqnarray} 
 \begin{eqnarray}
-\sigma =   \sqrt{ \frac{  \sum_{i=1}^{8}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
+\sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} },
 \end{eqnarray} 
-
-In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e.
-host) and the residuals, taking COSMOS-CID1174 as an example.
-The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}.
-
-\begin{figure*}
-\centering
-%\hspace{-5.5em}
-{
-\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
-\caption{\label{fig:AGN_decomp} 
-Figure illustrates the inference for the 32 objects based on the WFC3 images.
-In each row, observed data (first column), best-fit models (second column), data subtracted by the inferred point source (third column),  normalized residuals (fourth column) are presented together with the target ID.
-In the fifth column, we present the 1-D surface brightness profiles (top) and the corresponding residual (bottom).
-The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects).
-Note that the one-dimensional surface brightness profiles are only for illustration purposes.
-The actual fitting is based on the two-dimensional images.
-The remaining 31 objects of the sample are shown in Appendix~\ref{sec:restsample}.
-}}
-\end{figure*}
-
-\begin{deluxetable*}{ccccccc}
-\tablecolumns{7}
-\tablewidth{0pt}
-\tablecaption{Host inference of CID1174} 
-\tablehead{ 
-\colhead{PSF rank} &
-\colhead{total $\chi ^2$} & 
-\colhead{weights $w_i$} &
-\colhead{host flux (counts)} &
-\colhead{host flux ratio}&
-\colhead{\Reff (arcsec)}&
-\colhead{\sersic\ $n$}
- \\ 
-\colhead{(1)} &
-\colhead{(2)} &
-\colhead{(3)} &
-\colhead{(4)} &
-\colhead{(5)} &
-\colhead{(6)} &
-\colhead{(7)} 
-} 
-\startdata
-%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
-%\\
-1 & $8584.429$ & $1.000$ & $82.2$ & $35\%$ & $0\farcs{}345$ & $1.1$ \\
-2 & $8646.711$ & $0.920$ & $99.1$ & $42\%$ & $0\farcs{}298$ & $1.9$ \\
-3 & $8816.947$ & $0.734$ & $76.7$ & $33\%$ & $0\farcs{}365$ & $1.1$ \\
-4 & $9304.841$ & $0.383$ & $128.6$ & $55\%$ & $0\farcs{}231$ & $2.8$ \\
-5 & $9652.575$ & $0.241$ & $187.5$ & $79\%$ & $0\farcs{}116$ & $6.2$ \\
-6 & $9917.101$ & $0.170$ & $100.2$ & $42\%$ & $0\farcs{}287$ & $2.1$ \\
-7 & $10018.324$ & $0.148$ & $75.1$ & $32\%$ & $0\farcs{}365$ & $1.2$ \\
-8 & $10087.456$ & $0.135$ & $79.8$ & $34\%$ & $0\farcs{}358$ & $1.2$ \\
-\hline\\
-Weighted value & & & $97.322\pm28.336$ & $42\%\pm12\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.9\pm1.3$  \\
-\enddata
-\label{tab:weight_CID1174}
-\tablecomments{
-Column~1: Rank of the PSF from the library.
-Column~2: Total $\chi ^2$ for the corresponding PSF.
-Column~3: Weights for the inference.
-Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
-For this sample, the inflation parameter $\alpha$ calculated by Equation~\ref{eq:alpha} is 16.671.
-}
-\end{deluxetable*}
-
-\begin{figure*}
-\centering
-{
-\includegraphics[height=0.75\textwidth]{fig/flux_r_n_corner.pdf}
-}
-\caption{\label{fig:flux_r_n_corner}
-Illustration of the corner relations between the inferred host \sersic\ parameters.}
-\end{figure*}
-
-We apply this approach to the overall AGN systems to infer the overall host galaxy information.
-To quickly overview, we plot the relations of the properties between effective radius (\Reff), \sersic\ index and host to total flux ratio in Figure~\ref{fig:flux_r_n_corner} and leave the detail descriptions in the next Section.
-We realize that the inference of the host properties is weighted by eight top-ranked PSFs.
-The smaller volume of top-ranked  PSFs would possibly underestimate the uncertainties of the inference.
-To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the inference by using five and ten top-ranked PSFs.
-As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference has been solid when the amount of selected PSF exceeds five.
-
-\begin{figure*}
-\centering
-{
-\includegraphics[height=0.35\textwidth]{fig/hist_compare.pdf}
+where $N$ is the number of the ranking PSF, i.e., 8.
+
+\noindent In Figure~\ref{fig:AGN_decomp}, we demonstrate the results for COSMOS-CID1174. The adopted weights are listed in Table~\ref{tab:weight_CID1174}.
+
+%\begin{figure*}
+%\centering
+%{
+%\includegraphics[height=0.5\textwidth]{fig/flux_r_n_corner.pdf}
+%}
+%\caption{\label{fig:flux_r_n_corner}
+%Relations between the measured host galaxy parameters.}
+%\end{figure*}
+
+We apply this approach to all AGNs to determine the global characteristics of the hosts of type-1 AGNs at these high redshifts.
+We measure the effective radius (\Reff), \sersic\ index and host-to-total flux ratio and describe each of these in the following section.
+We recognize that these measurements are weighted by the eight top-ranked PSFs.
+The limited number of top-ranked PSFs may underestimate actual uncertainties.
+To gauge how the number of top-ranked PSF affects our results, we compare results when also using five and ten top-ranked PSFs.
+As shown in Figure~\ref{fig:hist_compare}, the results are consistent.
+
+\begin{figure}
+\centering
+{
+\includegraphics[height=0.25\textwidth]{fig/hist_compare.pdf}
 }
 \caption{\label{fig:hist_compare} 
-Comparison of the histogram of the inferred host flux ratio, based on the different the top-ranked PSFs number.}
-\end{figure*}
+Distribution of the host-to-total flux ratio when implementing a different number of top-ranked PSFs.}
+\end{figure}
 
 %The inference of F814w data.
-18/32 systems in the COSMOS field have ACS/F184W imaging data.
-We infer their host flux ratio using the same approach used for the WFC3-IR.
-The field of view by ACS are larger than WFC3, hence we collected in total 174 ACS PSFs in the library.
-In principle, the host inference by IR band is superior to the one by UV band, giving that the effects of dust extinction and contrast between the (blue) AGN and (red) host.
-Thus, we fix the \Reff\ and \sersic\ $n$ as the value inferred by IR band, assuming that the morphology of the galaxy is consistent between ACS and WFC3.
-
-We list all the inference of the host galaxy properties in the Table~\ref{tab:result_sersic}.
-
-\tabcolsep=0.03cm
-\begin{deluxetable*}
-{@{\extracolsep{4pt}}lcccccccccc}   % need for the gap between the clines.
-\tablecolumns{9}
-\tablewidth{0pt}
-\tablecaption{Inferred host galaxy properties for the 32 systems.} 
-\tablehead
-{ 
-\colhead{Target ID}&
-  \multicolumn{5}{c}{WFC3}&
-  \multicolumn{3}{c}{ACS/F814W} &
-   \multicolumn{2}{c}{host properties} \\
-  \cline{2-6}  \cline{7-9} \cline{10-11}  \\
-\colhead{}& 
-\colhead{reduced $\chi ^2$}& \colhead{host-total flux ratio}& 
-\colhead{\Reff}& \colhead{\sersic\ $n$}& 
-\colhead{magnitude}&
-\colhead{reduced $\chi ^2$}& \colhead{host-total flux ratio}& \colhead{magnitude} &
-\colhead{$\log L_R$} &\colhead{$\log M_*$} \\
-\colhead{}& 
-\colhead{}& \colhead{}& 
-\colhead{($\arcsec$)}& \colhead{}& 
-\colhead{(AB system)}& \colhead{}& 
-\colhead{}& \colhead{(AB system)} &\colhead{($L_{\odot,R}$)} & \colhead{(M$_{\odot}$)}\\
-\colhead{(1)}& 
-\colhead{(2)}& \colhead{(3)}& 
-\colhead{(4)}& \colhead{(5)}& 
-\colhead{(6)}& \colhead{(7)}& 
-\colhead{(8)}& \colhead{(9)}&
-\colhead{(10)}& \colhead{(11)}
-}
-\setlength{\tabcolsep}{20pt}
-\renewcommand{\arraystretch}{1.5}
-\startdata 
-CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.05\substack{+0.15\\-0.11}$ &$10.78\substack{+0.18\\-0.15}$\\[3pt]
-CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.41\substack{+0.15\\-0.11}$ &$10.14\substack{+0.18\\-0.15}$\\[3pt]
-CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.86\substack{+0.52\\-0.23}$ &$10.59\substack{+0.53\\-0.25}$\\[3pt]
-CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.05\substack{+0.03\\-0.03}$ &$10.78\substack{+0.10\\-0.10}$\\[3pt]
-CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.18\substack{+0.11\\-0.09}$ &$10.91\substack{+0.14\\-0.13}$\\[3pt]
-CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.08\substack{+0.15\\-0.11}$ &$10.81\substack{+0.18\\-0.15}$\\[3pt]
-CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.16\substack{+0.14\\-0.11}$ &$10.89\substack{+0.17\\-0.15}$\\[3pt]
-CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $10.98\substack{+0.02\\-0.02}$ &$10.71\substack{+0.10\\-0.10}$\\[3pt]
-CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.13\substack{+0.03\\-0.03}$ &$10.86\substack{+0.10\\-0.10}$\\[3pt]
-CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.11\substack{+0.04\\-0.04}$ &$10.84\substack{+0.10\\-0.10}$\\[3pt]
-CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.07\substack{+0.35\\-0.19}$ &$10.80\substack{+0.36\\-0.21}$\\[3pt]
-CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.70\substack{+0.16\\-0.12}$ &$10.43\substack{+0.19\\-0.15}$\\[3pt]
-CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.73\substack{+0.22\\-0.15}$ &$10.46\substack{+0.24\\-0.18}$\\[3pt]
-CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.02\substack{+0.23\\-0.15}$ &$10.75\substack{+0.25\\-0.18}$\\[3pt]
-CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $10.98\substack{+0.12\\-0.10}$ &$10.72\substack{+0.16\\-0.14}$\\[3pt]
-LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.32\substack{+0.09\\-0.07}$ &$11.05\substack{+0.13\\-0.12}$\\[3pt]
-LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.12\substack{+0.09\\-0.08}$ &$10.86\substack{+0.13\\-0.12}$\\[3pt]
-LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.08\substack{+0.06\\-0.05}$ &$10.81\substack{+0.11\\-0.11}$\\[3pt]
-XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.89\substack{+0.07\\-0.06}$ &$10.63\substack{+0.12\\-0.12}$\\[3pt]
-XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.15\substack{+0.12\\-0.10}$ &$10.88\substack{+0.16\\-0.14}$\\[3pt]
-XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.12\substack{+0.26\\-0.16}$ &$10.85\substack{+0.28\\-0.19}$\\[3pt]
-CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ... & ... & ... & $10.71\substack{+0.16\\-0.12}$ &$10.45\substack{+0.19\\-0.15}$\\[3pt]
-CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ... & ... & ... & $10.90\substack{+0.06\\-0.05}$ &$10.63\substack{+0.12\\-0.11}$\\[3pt]
-CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ...
-& ...
-& ...
-& $11.52\substack{+0.28\\-0.17}$ &$11.25\substack{+0.30\\-0.20}$\\[3pt]
-CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ... & ... & ... & $10.06\substack{+0.23\\-0.15}$ &$9.79\substack{+0.25\\-0.18}$\\[3pt]
-ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ...
-& ...
-& ...
-& $11.16\substack{+0.12\\-0.10}$ &$10.89\substack{+0.16\\-0.14}$\\[3pt]
-SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ...
-& ...
-& ...
-& $10.75\substack{+0.09\\-0.08}$ &$10.49\substack{+0.14\\-0.13}$\\[3pt]
-SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ... & ... & ... & $10.80\substack{+0.11\\-0.09}$ &$10.54\substack{+0.15\\-0.13}$\\[3pt]
-SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ...
-& ...
-& ...
-& $10.77\substack{+0.07\\-0.06}$ &$10.51\substack{+0.12\\-0.12}$\\[3pt]
-SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ...
-& ...
-& ...
-& $11.19\substack{+0.13\\-0.10}$ &$10.92\substack{+0.17\\-0.14}$\\[3pt]
-SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ... & ... & ... & $9.95\substack{+0.47\\-0.22}$ &$9.68\substack{+0.48\\-0.24}$\\[3pt]
-SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ...
-& ...
-& ...
-& $11.03\substack{+0.21\\-0.14}$ &$10.76\substack{+0.23\\-0.17}$\\[3pt]
-\enddata
-\label{tab:result_sersic}
-\tablecomments{
-Column~1: Object ID.
-Column~2-6: WFC3 inference. 
-Column~2: Reduced $\chi ^2$ value by the best PSF in the library.
-Column~7-9: ACS inference. 
-Column~10: Observed host luminosity in the rest-frame R band.
-Column~11: Host total stellar mass.
-}
-\end{deluxetable*}
+We carry out a similar analysis for 18/32 AGNs in the COSMOS field with ACS/F184W imaging data.
+We assess their host flux ratio using the same approach as done for the WFC3-IR.
+The ACS FOV is larger than WFC3 thus we generated 174 PSFs for use.
+As expected, the detection of the host galaxy in the IR band is of higher significance than the UV due to the effects of dust extinction and the contrast between the (blue) AGN and (red) host.
+Thus, we fix the \Reff\ and \sersic\ $n$ as the value determined by IR band thus amounting to an assumption that the morphology of the galaxy is consistent between ACS and WFC3 bands.
+In this case, the only free parameters are the total host and AGN flux.
+We report the host galaxy properties in Table~\ref{tab:result_sersic}.
 
@@
 
+From our AGN-host decomposition, we detect the host galaxy in essentially all cases.
+\hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data-point source'' stamps) shown in Figures~\ref{fig:AGN_decomp} and Appendix~\ref{sec:restsample}.
+While some of the galaxies have nearby neighbors, most are isolated and do not show strong signs of interaction or ongoing mergers.
+This is relevant for model fitting with smooth \sersic\ profiles and the subsequent determination of the stellar mass.
+In the following subsections, we described the properties of our ensemble of type-1 AGN host galaxies.
+
 \subsection{Host galaxy properties}
-In previous section, we carry out the AGN-host decomposition and derive the host galaxy \sersic\ properties of the overall sample, as shown in Figure~\ref{fig:hist_compare}.
-The optimized resulting images for each sample are presented in the figures in Appendix~\ref{sec:restsample}.
-Based on the third column of these resulting figures (i.e.
-the ``data-Point source'' stamps), we find that all the systems have shown the evidence for existence of the host galaxies.
-We also find that merger feature of the host galaxies are not strong, showing that our sample possibly not be dominated by the major merger.
-
-The host-total flux ratio of the sample are varies from 10\% to 90\% (concentrated between 20\% to 50\%).
-The effective radius and \sersic\ index are randomly distributed within the prior, rather than concentrating on upper/lower side.
-The inferred \Reff\ of our sample are between $\sim$1-7~kpc (peaked at $\sim$2.2~kpc).
-15/32 systems have \sersic\ index $n<2$, indicating they are composed of disk+bulge components.
-Five systems have high \sersic\ index ($n>4.5$); we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
-
-We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive} and find that our high-$z$ AGN host have very similar distribution.
-Thus, we assume the inactive galaxies and our AGN hosts have similar bulge-total ratio so that we can infer the bulge stellar mass of our sample, as shown below.
-
-18/32 systems have multi-band host magnitude which enables us to select the best stellar population that could fit the overall sample.
-We find that the 1~Gyrs stellar population with solar metallicity by Chabrier initial mass function (IMF)~\citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples.
-Given this template, we are capable of inferring the rest-frame R band luminosity (\lhost) and stellar mass (\smass) of our sample based on their filter magnitude, in the following sections.
+\label{sec:result-hosts}
+As shown in Figure~\ref{fig:hist_compare}, the host-to-total flux ratio of the sample spans a wide range from 10\% to 90\% with most of the sample concentrated between 20\% to 50\%.
+Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the very few cases around 10\% should be considered as marginal detections.
+
+The distributions of effective radius \Reff\ and \sersic\ index are shown in Figure~\ref{fig:hist_rn}.
+These values are distributed within the allowed range and not concentrated on either the upper or lower bound.
+The \Reff\ of our sample are between $\sim$1-7~kpc (peaked at $\sim$2.2~kpc).
+Nearly half (15/32) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge.
+Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
+
+We compare the morphology of AGNs host galaxies to the inactive ones from the CANDELS/COSMOS imaging survey.
+We identify 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} using \galfit, and their stellar masses are derived based on 3-D-\hst\ spectroscopic survey~\citep{Momcheva2016, Brammer2012}.
+We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where we find no significant difference between their distributions and median value.
+We also test whether the distributions can be drawn from the same parent population using a Kolmogorov-Smirnov test and determining the p-value to be 0.42 and 0.04 for \Reff\ and $n$, respectively.
+We conclude that the host galaxies of our AGN sample are representative of the overall population of galaxies, with a significant disk component, at comparable luminosity and stellar mass at the same redshift.
+In Section~\ref{sec:bh_bulge}, we use this information to infer the likely bulge masses, hence the \mbh\ -- \bmass\ relation.
+
+%In Figure~\ref{fig:Mstar-rn}, we plot the \smass\ versus the \Reff\ and \sersic\ index.
+The color coding is based on the filter flux ratio between WFC3 and ACS.
+The distribution of \smass-\Reff\ relation show that our AGN hosts concentrate at the high end of the stellar mass, close to the red sequence.
+%\begin{figure*}
+%\centering
+%\begin{tabular}{c c}
+% \hspace{-2.5em}
+%{\includegraphics[trim = 0mm 0mm 90mm 0mm, clip, height=0.45\textwidth]{fig/Mstar-Reff.pdf}}&
+%{\includegraphics[ height=0.45\textwidth]{fig/Mstar-Sn.pdf}}\\
+%\end{tabular}
+%\caption{\label{fig:Mstar-rn} 
+%The comparison of the galaxy properties between our 32 AGNs' hosts to the CANDELS sample including 4401 inactive galaxies (circles).
+The color coding is based on the filter flux ratio between WFC3 and ACS.
+For CANDELS sample, the WFC3/F125W flux is taken.
+The black squares are the AGN samples with only WFC3 band observation.
+%}
+%\end{figure*}
+
+\begin{figure}[ht]
+%\centering
+%\begin{tabular}{c c}
+%{\includegraphics[ height=0.3\textwidth]{fig/Hist_Reff.pdf}}&
+%{\includegraphics[ height=0.3\textwidth]{fig/Hist_Sn.pdf}}
+%\end{tabular}
+\epsscale{1.2}
+\plotone{fig/Hist_Reff.pdf}
+\plotone{fig/Hist_Sn.pdf}
+\caption{\label{fig:hist_rn} 
+The comparison of the histogram of the \Reff\ (top panel) and \sersic\ $n_s$ (bottom panel), with median value indicated.
+For comparison, we show the distribution of CANDELS galaxies at similar redshifts and stellar masses to our type-1 AGN sample.}
+\end{figure} 
+%
+
+%We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive} and find that our high-$z$ AGN host have very similar distribution.
+%Thus, we assume the inactive galaxies and our AGN hosts have similar bulge-total ratio so that we can infer the bulge stellar mass of our sample, as shown below.
+
+\subsection{Rest-frame colors}
+
+For 18/32 AGNs, we have multi-band host magnitudes that enable us to select an appropriate stellar population template to determine rest-frame luminosities and stellar masses for the overall sample.
+To minimize the uncertainty associated with these corrections, we use this template to interpolate to the rest-frame R band which is very close to the observed wavelengths.
+We find that a 1~Gyr stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} provides a good match to the observed colors of our sample (see Figure~\ref{fig:compare_temp}).
+We note that the choice is not unique, and other combinations of ages and metallicities and star formation history could match the observed colors and would provide very similar R-band magnitudes, and also stellar masses \citep{Bell2000, Bell2001}.
+%(cite Bell \& de Jong 2001, 2003),
+
+\begin{figure}
+\centering
+{\includegraphics[width=0.4\textwidth]{fig/comp_gtemp_1Gyrs.pdf}}
+\caption{\label{fig:compare_temp} 
+Comparison of the inferred rest-frame R band magnitude based on the adopted stellar population, using 18/32 AGNs which have both WFC3 and ACS imaging data.
+}
+\end{figure}
 
 \subsection{\mbh-\lhost\ relation}\label{sec:ml}
-Adopting the 1~Gyrs stellar population, we perform the K-correction to derive the rest-frame R band magnitude of our sample.
-Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty introduced by this K-correction is within 0.05~mag.
-We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}.
-The inferred $L_R$ are ranged between $\log L_R \in [9.5, 11.5]$ ($L_{\odot,R}$), as summarized in Table~\ref{tab:result_sersic}.
-
-We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}. Following common practice, we fit the local relation as a linear relation,
+
+Adopting the 1~Gyr stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample.
+As mentioned above, since the WFC3 filter is already close to the rest-frame R-band, we expect the $M_R$ uncertainty introduced by this K-correction to be within 0.05~mag.
+We derive the rest-frame R band luminosity from $\log L_R/L_{R, \odot} = 0.4\times(M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}.
+$L_R$ ranges between $\log L_R \in [9.5, 11.5]$ ($L_{\odot,R}$) with individual values listed in Table~\ref{tab:result_sersic}.
+
+We show the relation between \mbh\ and \lhost\ in Figure~\ref{fig:ML} with comparison samples. For reference, we fit the local data with a linear relation,
+
 \begin{eqnarray}
@@
 \end {eqnarray}
-which enables direct comparison to the distant sample.
-The inferred local relations, as presented in the Figure~\ref{fig:ML}, shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones.
-The observational result indicates that the relation between black hole mass and the host luminosity are similar at different period of the universe.
-
-Considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
+
+\noindent which enables a direct comparison between our high-$z$ sample and the local relation.
+The distribution of our data appears to be in good agreement with the local relation and the other AGN samples at lower redshift.
+Therefore, the observational data indicate that the relation between black hole mass and the host luminosity are similar at different period of the universe.
+In Appendix~\ref{sec:ml-ev}, we explore how the high-$z$  sample would evolve in this plane solely with luminosity evolution of the host galaxy as done in past studies \citep[e.g., ][]{Ding2017b}.
+
+We note that there are outliers that deviate from the distribution of overall sample, such as SXDS-X763.
+We suspect that this source may have abnormal host properties.
+Indeed, the value of \Reff\ has a large uncertainty ($\sim 75\%$) and the host-to-total flux ratio is the lowest of the high-$z$ sample ($<10\%$).
+
+%Considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
 We will make this comparison taking the evolution effect into account in Section~\ref{sec:ml-ev}.
 
-We note three outlier measurements deviated from the distribution of overall sample, which are SXDS-X763, CDFS-1, CDFS-724.
-We expect that they could have abnormal host inference.
-Indeed, for SXDS-X763, the inferred host \Reff\ has large scatter ($\sim 75\%$) with the lowest host-total flux ratio in the overall sample ($<10\%$).
-For CDFS-1 and CDFS-724, their host are \Reff$<0\farcs{}15$, smaller than the PSF FWHM.
+%For CDFS-1 and CDFS-724, their host are \Reff$<0\farcs{}15$, smaller than the PSF FWHM.
 Moreover, the broad emission line of \mbh\ are from \citet{Suh2015} which could have systemic to \citet{Schulze2018}.
@@
 
-Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted.
-The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex, at fixed stellar initial mass function (changing the initial mass function would change all our stellar masses systematically).
-The inferred $M_*$ are ranged between $\log M_* \in [9.7, 11.3]$ ($M_{\odot}$), listed in Table~\ref{tab:result_sersic}.
-
-In Figure~\ref{fig:MM}, we plot the our \mbh-\smass\ measurements and compare to the local and intermediate sample.
-We visually see that the relations for the three samples are close.
-Similar as Equation~\ref{eq:MLlocal}, we consider the local \mbh-\smass\ relations as linear relation as:
+To fulfill our purpose of acquiring the NIR imaging with \hst, we use the host luminosity along with color information to estimate the stellar mass content of each host galaxy  based on the mass-to-light ratio of the adopted stellar population.
+The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex (changing the IMF would effect all our stellar masses systematically).
+We find $M_*$ ranges between $\log M_* \in [9.7, 11.3]$ ($M_{\odot}$).
+These values are listed in Table~\ref{tab:result_sersic}.
+
+In Figure~\ref{fig:MM}, we plot the our \mbh -- \smass\ measurements and find that the distributions in this plane for the four samples are similar.
+However, there is a slight shift of the high-$z$ data towards higher black hole masses at a fixed host mass.
+In Figure~\ref{fig:MM-vz}, we plot, as a function of redshift, the mass ratio ($right$ panel) and the mass ratio difference ($\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$ which is considered as the difference between the high redshift data and the best-fit local relation; $left$ panel).
+For our high-$z$ sample, we find the average $\Delta \log \mathcal M_{\rm BH}$ to be 0.3, a factor of two higher than the local mass ratio as indicated by the top green circle in Figure~\ref{fig:MM-vz}.
+
+As with Equation~\ref{eq:MLlocal}, we fit the \mbh-\smass\ data with a linear relation as:
 \begin{eqnarray}
 \label{eq:MMlocal}
-\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}).
+\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}),
 \end {eqnarray}
 
-To understand the evolution for high-$z$ relations, we fit the offset as a function of redshift in form as:
+\noindent and an evolution term parameterized in the following form:
+
 \begin{eqnarray}
 \label{eq:offset}
-\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
+\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z).
 \end{eqnarray}
-where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$.
-We obtain $\gamma  = 0.84 \pm 0.26$, i.e.
-tentative evidence for evolution, see Figure~\ref{fig:MM-vz}, panel (a).
-We also show the ratio of \mbh-\smass\ of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).
+
+If perform such a fit based on the {\it observed} data (i.e., no correction for selection effects), we obtain $\gamma  = 0.78 \pm 0.26$ that may be tentatively considered as evidence for evolution.
+Even with the exclusion of the few outliers, there is an evolution in the relation with $\gamma  = 0.65 \pm 0.27$.
+The best-fit {\it observed} evolution model is shown in Figure~\ref{fig:MM-vz}.
 
@@
 
-As shown in Figure~\ref{fig:MM-vz}, panel (a), most of our measurements locate within the scattering range of the local sample.
-We doubt whether the positivity of $\gamma$ stems from the three outliers discussed in last section.
-We thus exclude these outliers and re-perform the statistical analysis to see if the offset still exists.
-As a result, we obtain that $\gamma  = 0.65 \pm 0.27$, indicating the positive evolution trend become weaker but still exists.
+%{\bf [Include a full paragraph on the scatter]}
+As shown in these panels, the scatter of the high-$z$ correlation presents a similarity to the local relation.
+To quantitively make this comparison, we calculate the scatter of their offset value, based on Equation~\ref{eq:infer_value}, and obtain $0.33$ for high-$z$ and $0.40$ for local samples, respectively.
+This result is against the scenario where the random merger is the origin of the correlation \citep{Peng2007}, indicating that there is likely to be a connection between the SMBHs and their host galaxies during their formation.
 
@@
 
-In order to evaluate the ``true" underlying evolution and its uncertainty, corrected for selection effects, taking into account the actual observations, we adopt an independent method based on the approach introduced by \citet{Tre++07} and developed by \citet{Park15, Ding2017b}.
+In order to further evaluate the ``true" underlying evolution and its uncertainty, corrected for selection effects, taking into account the actual observations, we adopt an independent method based on the approach introduced by \citet{Tre++07} and developed by \citet{Park15} and \citet{Ding2017b}.
 The method parametrizes the evolution of the correlations between \mbh\ and host galaxy properties as an offset from the local one $\gamma$ and an intrinsic scatter \sint, which can be a free parameter or tied to the local relation.
-It then imposes a selection function in \mbh\ (assuming that the distribution of Eddington radio is narrow and therefore has a second order effect) and calculates the intrinsic parameters of the model given the observations.
+It then imposes a selection function in \mbh\ and calculates the intrinsic parameters of the model given the observations.
 In practice, we start from the local black hole mass function and the evolution model, generate mock samples using a Monte Carlo approach, apply the selection function and compare with the data to generate the likelihood.
-
 To illustrate the importance of the intrinsic scatter in the selection effects, we adopt both uniform (flat) prior and lognormal prior for \sint.
+Note that this method assumes a narrow Eddington radio distribution which is different to the one by \citet{Schulze2011}, as described in Section~\ref{sec:sf_framework}.
+Also, this method adopts the local black hole mass function rather than high-$z$ BH mass function.
+These differences have a second order effect and could be responsible to the different magnitude of the selection effect.
+On the other hand, this method probes the importance of the scatter at high-$z$, which is complementary.
+%Thus each is complementary that should be stressed maybe in the abstract (see my suggested change).
 
 Combining the 32 AGNs together with the intermediate redshift sample, we present the inferred  $\gamma$ and \sint\ in the two-dimensional planes in Figure~\ref{fig:select_effect}.
-The plots show that the inferred evolution is uncertain and depends crucially on the intrinsic scatter.
+The plots show that the inferred evolution is uncertain and depends crucially on the intrinsic scatter, especially when applying a luminosity evolution for the host (see Appendix~\ref{sec:ml-ev}).
 Assuming the lognormal prior \sint, to mimic the assumption of the method discussed in Section~\ref{sec:sf_framework}, one sees that the best estimate of $\gamma$ is positive, but the 95\% confidence intervals extend to zero.
 Thus one cannot conclude that evolution is significantly detected in our data.
-
 When relaxing the prior on \sint\ we find that the scatter is consistent with being as low as in the local samples, with a one-sided interval including zero and peaking at around 0.5~dex. 
-
 We also study the selection effect by only consider the new 32 AGNs, result in a higher evolution trend with a higher value of $\gamma$.
@@
 A simple check using our a-priori estimate of the bias, yields a similar result.
-The mean offset of the sample of 32 objects from the local relationship is $0.35\pm0.06$ dex, which would correspond to $\gamma=0.88\pm0.15$.
-However, after correcting for the a priori bias the offset reduces to $0.14\pm0.06$ and thus $\gamma=0.35\pm0.15$, mildly positive but not significantly so, and consistent with the a posteriori method within the error bars and the uncertainty in the correction.
+The mean offset of the sample of 32 objects from the local relationship is $0.34\pm0.06$ dex, which would correspond to $\gamma=0.85\pm0.15$.
+However, after correcting for the selection bias ($0.21$~dex, see Section~\ref{sec:sf_framework}), the offset reduces to $0.13\pm0.06$ and thus $\gamma=0.33\pm0.15$, mildly positive but not significantly so, and consistent with the a posteriori method within the error bars and the uncertainty in the correction.
 We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
@@
 
-\section{discussion}
+\subsection{\mbh-\bmass\ relation}\label{sec:bh_bulge}
+
+The local sample of inactive galaxies used in this analysis is mainly comprised of bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
+That is, in previous sections, we are comparing the \mbh-\smass$_{\rm ,total}$ relations in the distant universe to the \mbh-\smass$_{\rm ,bulge}$ relations locally.
+Considering that a significant stellar component of the high-$z$ AGNs have a disk component (i.e., AGN hosts with fitted \sersic\ index close to 1),  \smass$_{\rm , bulge}$ will be smaller than \smass$_{\rm ,total}$.
+
+Given that the structure of our 32 AGN hosts are similar to inactive
+galaxies at the same redshifts and stellar masses
+(Section~\ref{sec:result-hosts}), we expect their B/T ratios follow
+a similar distribution which can estimated using the single-\sersic\
+index \citep{Bruce2014}. With this estimation, we can infer the
+bulge stellar mass of our AGN host.
+
+Under these assumptions, we first establish the relation between the
+single-\sersic\ index and B/T ratios for CANDELS inactive galaxies
+at the similar mass level, i.e \smass$\in [9.0, 11.5]$, using B/T
+measured by \citet{Dimauro2018}. Then, we calculate the average B/T
+ratio at different \sersic\ index to construct a relation for our
+use, as shown in Figure~\ref{fig:BT-n_relation}. Taking this
+relation, we estimate the B/T of our AGN sample using the \sersic\
+index as proxy and infer their \smass$_{\rm, bulge}$ from the total
+stellar mass.
+
+We can now compare this \smass$_{\rm, bulge}$ to that
+of the black hole \mbh. As expected, we find a stronger offset of
+$0.65\pm0.11$~dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
+local relation, which corresponds to an evolutionary trend with
+$\gamma = 1.63\pm0.27$. Since selection effects are independent of B/T in
+our framework we can apply our a-priori estimate of the selection
+effect correction by removing 0.21~dex, leaving a significant offset
+of $0.44\pm0.11$.
+
+Even with the uncertainty associated with our estimate of the
+bulge-to-total ratio it is clear that there is significant evolution
+in the \mbh\ -- \smass$_{\rm , bulge}$ relation, considering the
+marginal evidence for evolution in the \mbh-\smass$_{\rm, total}$
+relation and that our galaxies are not pure bulges. This finding
+confirms with higher fidelity the conclusion by \citet{Bennert11}
+based on optical data of a smaller sample of 11 objects in the same
+redshift range \citep[see][for similar results.]{SS13, Jah++09, Cisternas2011}
+
+\begin{figure}
+\centering
+{
+\includegraphics[width=0.5\textwidth]{fig/BT_relation.pdf}
+}
+\caption{\label{fig:BT-n_relation} 
+Relation between bulge-to-total stellar mass ratio and single-\sersic\ index using CANDELS inactive galaxies with \smass$\in [9.0, 11.5]$.
+The red curve is the inferred specific relation taking the average B/T ratio at different \sersic\ index, used as proxy to infer the B/T for our AGN sample.
+}
+\end{figure}
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+{\includegraphics[width=0.5\textwidth]{fig/MBH-Mbulge-style1.pdf}}&
+{\includegraphics[width=0.5\textwidth]{fig/MBH-Mbulge-style0.pdf}}\\
+\end{tabular}
+\caption{\label{fig:MM_bulge-vz}
+Same as Figure~\ref{fig:MM-vz}, but for \mbh-\bmass\ relations.}
+\end{figure*}
+
+\section{Final technical remarks}
 \label{sec:dis}
-
-\subsection{Host luminosity passive evolution correction}\label{sec:ml-ev}
-In the passive evolution scenario, we expect the galaxy luminosity to fade over time.
-Thus, we transfer the \lhost\ for distant samples at today so as to compare the \mbh-\lhost\ relation to the local in the equivalent frame.
-We consider this scenario following \citet{Ding2017b} by parametrizing the luminosity evolution with the functional form as
-$d{\rm mag}_{\rm R}\sim~d\log(1+z)$, i.e.,
-\begin{eqnarray}
-\label{eq:L_relation}
-\log(L_{R,0})=\log(L_{R}) - 1.48 \log (1+z).
-\end{eqnarray} 
-This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer the interested readers to \citet[][section 5.4]{Ding2017b} for more details.
-
-Having transferred the \lhost\ to today, we find that, as showing in Figure~\ref{fig:ML-vz}-(a), at fixed mass, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation.
-We fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 0.71 \pm 0.18$, as showing in Figure~\ref{fig:ML-vz}-(b).
-We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.3$, with flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
-
-The inferred $\gamma$ here could have large systematic given the following limitations.
-First, the passive evolution is based on a simplified correction; after all, we are not clear exactly how the host evolves to $z=0$.
-Moreover, we only consider the evolution of the host galaxy and assume the \mbh\ does not change much.
-%Moreover, in the literature, the correlation of the \mbh-\smass\ is considered as more fundamental which would be more efficient to understand their co-evolution.
-
-\begin{figure*}
-\centering
-\begin{tabular}{c c}
-\subfloat[\mbh-\lhost\ relation, evolution-corrected]
-{\includegraphics[height=0.5\textwidth]{fig/MBH-L_ev.pdf}}&
-\subfloat[offset in  $\log($\mbh$)$ (VS. \lhost) as a function of redshift]
-{\includegraphics[height=0.5\textwidth]{fig/MBH-L-vz.pdf}}\\
-\subfloat[\mbh-\lhost, flat prior]
-{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
-\subfloat[\mbh-\lhost, lognormal prior]
-{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
-\end{tabular}
-\caption{\label{fig:ML-vz} 
-Same as previous figures but for \mbh-\lhost\ relation, considering the passive evolution correction for host galaxy luminosity.}
-\end{figure*}
 
@@
 
-In this work, we use the start-of-the-art techniques to derive the host flux from the AGN image.
-The fidelity of the inferred apparent magnitudes of the host galaxies are high.
-Nevertheless, we adopt one stellar population to the overall sample to derive the rest-frame R band luminosity and stellar mass.
-We note that adopting the private stellar populations for each samples which havs both multi-band host magnitude could be more robust in principle.
-However, considering that the host magnitude in ACS band is faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost.
-Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry.
-
-We highlight that, in this particular paper, we focus most on the decomposing of the AGN image to present our inference of the host.
+In this work, we use the start-of-the-art techniques to measure the host galaxy flux separating it from that of the point source.
+The fidelity of the host galaxy magnitude is high as demonstrated by the robustness with respect to the choice of PSF which is the main source of uncertainty.
+However, we introduce some uncertainty by adopting a simple stellar population template to derive the rest-frame R-band luminosity and stellar mass for the full population.
+In principle, if we had more information, we could improve on this source of uncertainty by a adopting a specific stellar population model for each.
+However, considering that the host magnitude in the \hst/ACS band is faint (host-to-total flux ratio $< 30\%$), the individual color that we measure is insufficient to further discriminate between templates and thus we adopt a single one for simplicity and to facilitate reproduction of our work.
+
+%We highlight that, in this particular paper, we focus most on the decomposing of the AGN image to present our inference of the host.
 With the host inference, we then carry out a rapid analysis of the \mbh\ and host properties relations.
@@
 
-At last, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates.
-That is to say, the intrinsic scatter is not necessarily worse at high-$z$ than the low-$z$.
+In any case, We stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates, and not by uncertainties in the photometry or stellar mass estimates.
+Thus, the choice of template is a vastly subdominant source of error.
+A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.
 
@@
 \label{sec:local_sys}
-To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}.
-In the literature, some other local sample have been measured which could also be considered as the local anchor.
-We note that different local samples have inconsistency which could affect our understand of the co-evolutions.
-To estimate this effect, we compare our local \mbh-\smass\ sample to the local ones by \citet{Kormendy13} (hereafter K13).
-We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset to our local sample.
-Note that a $+0.3$~dex difference could totally erase the $\Delta\log$\mbh\ for the high redshift sample as described in last section.
-
-However, we realize that the \mbh-\sigstar\ relations by K13 also have a $\sim$0.3~dex offset to the ones by \citet{Woo2010}.
-Note that it is the local \mbh-\sigstar\ relation by \citet{Woo2010} that is used to determine the virial coefficient for our active BHs.
-Thus, if adopting the K13's sample, the \mbh\ of all the AGN sample should be increased by $\sim$0.3~dex.
-As a result, adopting different local measurement would only globally affect the level of the \mbh\ to local and high-$z$ sample at the same time, with the result of  $\Delta\log$\mbh\ unchanged.
-
-We thus conclude that, if adopt K13 sample, the inference of the high redshift offset of $\Delta\log$\mbh\ would remain at the same level.
-However, this quick comparison of the local sample highlights the requirement of a solid local baseline for the future studies (Bennert et al., in prep).
+
+To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011} and  \citet{H+R04}.
+In the literature, other analyses of the local sample are available which could also be considered as the local anchor.
+We note that the different local samples have inconsistencies which could affect our measurement of the co-evolution.
+Since the local correlations are used to calibrate the single epoch black hole mass estimates, one needs to be self-consistent in the choice of local anchors and calibration of black hole mass estimators.
+Unfortunately, this is a thorny issue, since not all the local correlations are mutually consistent especially when considering different galaxy properties like luminosity stellar mass and velocity dispersion.
+
+To illustrate the problem, we compare our local \mbh-\smass\ sample to that published in \citet{Kormendy13} (hereafter K13).
+We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset relative to our local sample.
+Note that a $+0.3$~dex difference could totally erase the $\Delta\log$\mbh\ for the high redshift sample as described in last section, if it were independent from the black hole mass calibration.
+
+However, the \mbh-\sigstar\ relations by K13 are also offset by  $\sim+0.3$~dex with respect to those given by \citet{Woo2010}, which is the baseline for our adopted black hole mass estimators.
+Thus, if we were to adopt the K13 normalization instead, the \mbh\ of all the AGN sample should be increased by $\sim$0.3~dex.
+As a result, adopting a different local anchor would only globally affect the level of the \mbh\ to local and high-$z$ sample at the same time, with the result of leaving $\Delta\log$\mbh\ unchanged.
+
+In conclusion, whereas the uncertainty in the local anchor does not affect our measurement of evolution, it is important to keep in mind this issue in evolutionary studies and verify that the measurements are as self-consistent as possible in the local and distant universe.
+In order to further reduce the uncertainty, one should perform a self-consistent measurement with identical techniques and data quality both in the local and distant universe.
+This effort is currently in progress and when completed should enable us to completely eliminate this source of uncertainty \citep{Bennert11,Harris2012, Bennert2015}.
 
@@
 
-\section{Summary} \label{sec:sum}
+\section{Conclusions} \label{sec:sum}
+
 We studied the evolution of the correlations between the supermassive black hole and their host galaxies using new measurements of 32 X-ray selected AGNs at $1.2<z<1.7$.
-
-We used the published near-infrared spectroscopic observations \halpha\ emission lines to estimate the reliable values of BH mass.
-To obtain the properties of the AGN host galaxies, we performed the AGN image decomposition using the state-of-the-art techniques.
-We adopted the \hst/WFC3 infrared channel to observe the high-resolution AGN imaging data and collected the PSF-stars in across all the fields to build to a library of PSF for the fitting.
-Using the latest image modeling tool \lenstronomy, we decomposed the AGN image in 2-D plane taking each PSF in the library.
-We obtained the host \sersic\ property (i.e., host flux, effective radius, \sersic\ index) using a weighted arithmetic mean based on the inference by the eight top-ranked PSFs.
-Incorporating with the inference by \hst/ACS image, we selected the stellar population, hence derived the rest-frame R band Luminosity (\lhost) and stellar mass (\smass) of the host.
-
-Combining our high-$z$ measurements with the intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13, Cisternas2011}, we compared the scaling relations to the ones from the local with main results summarized as follows:
-\begin{enumerate}
-\item The \mbh-\smass\ relations at higher redshift are inconsistent with the local ones, i.e.
-Figure~\ref{fig:MM}, \ref{fig:MM-vz}.
-Considering the correction for passive evolution of galaxy luminosity, the \mbh-\lhost\ relations at higher redshift are inconsistent with the local ones,  i.e.
-Figure~\ref{fig:ML-vz} - (a).
-\item The offsets of by the evolution are well described by the form $\Delta\log\mathcal M_{\rm BH}= \gamma \log (1 + z)$. We obtain $\gamma = 0.84\pm0.26$ for \mbh-\smass\ relation.
-
-\item However, when considering the selection effect (using two independent methods), we find that the high redshift measurements can be consistent with the local relations, i.e.
-Section~\ref{select_eff}.
-
-\item Our inference indicates the evidence of disk+bulge component (i.e.
-the ones with \sersic\ $n<2$), while the local comparing samples are bulge dominated.
-We take the inferred  \sersic\ $n$ as proxy to estimate the bulge-total-ratio stellar mass.
-Comparing to their \mbh, we find a strong evolution with $\gamma = 1.71\pm0.27$.
-Thus, the conclusion seems solid that the BHs 8-10~Gyrs ago reside in bulges which are less massive/luminous than today.
-
-\item We also compare the properties of our active galaxy sample to the ones from inactive galaxy in the CANDELS imaging survey at the same redshift range, finding no significant discrepancy among them.
-\end{enumerate}
+Near-infrared spectroscopic observations with Subaru/FMOS of the \halpha\ emission line are available that provide reliable BH masses.
+To obtain the properties of the AGN host galaxies, we performed an image decomposition using the state-of-the-art techniques on \hst/WFC3 IR data to obtain high-resolution imaging of the AGN and its host.
+This required us to collect PSF-stars across all the fields to build to a library of PSFs.
+Using the state-of-the art image modeling tool \lenstronomy, we decomposed the AGN image in 2-D plane taking each PSF in the library.
+We obtained the host properties (i.e., host flux, effective radius, \sersic\ index) using a weighted arithmetic mean based on the inference from the eight top-ranked PSFs.
+With additional \hst/ACS image in the optical, we identified the appropriate stellar population and derived the rest-frame R-band luminosity (\lhost) and stellar mass (\smass) of the host with the corresponding mass-to-light ratio.
+We then determine the mass relations at high-$z$ and establish any signs of evolution by combining our high-$z$ measurements with local and intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13, Cisternas2011}.
+
+We find the average ratio between the mass of a supermassive black hole and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, by factor of $\sim2.2$ and $\sim2.5$ respectively, as compared to that in the local universe.
+However, taking into account selection bias, these correlations are
+consistent with the local universe within the 95\% confidence limits. 
+%Therefore, for a fixed black hole mass, the host galaxy total stellar mass and luminosity could be larger than in the local universe by a factor of two, or equal to the local universe which is consistent with no evolution.
+Even with the remaining uncertainties in the corrections for selection, we are confident that any evolution in the \mbh/\smass\ relation is at the most a factor of two with the case of no evolution entirely plausible.
+
+Considering the bulge component instead to be the main driver of the local correlations \citep{Bennert11, Woo++08}, we find that our high-$z$ AGN sample has significantly lower mass/luminosity bulges at fixed black hole mass than in the local universe.
+Comparing to their \mbh, we find evolution with the ratio evolving as $(1+z)^{1.63\pm0.27}$, which is significant even accounting for selection effects.
+We caution that the evolution of the bulge component is more uncertain than our measurement of the total galaxy components, since it is based on an estimate of the B/T ratio from the measured Sersic indices from a matched sample of inactive galaxies.
+Nevertheless, since the signal is stronger than for the integrated quantities, the measurement is more significant even in presence of larger uncertainties.
+Thus, we can conclude that the BHs 8-10~Gyrs ago reside in bulges which are less massive/luminous than today \citep[see also][]{Bennert11,Park15}, even though a proper measure of the bulge mass at high-$z$ may need to wait for the next generation ground-based 20-30m class telescopes.
+
+Given that the total-\mbh\ relation is closer to or consistent with the local relation, the inferred evolution of the bulge-\mbh\ correlations is qualitatively consistent with a scenario where the assembly of the black hole predates that of the bulge, which is completed by the transfer of stellar mass from the disk via mergers or secular processes \citep{Croton2006}.
+The stellar mass need to build the bulge appears to be present in the disk component at high-$z$.
+
+Of further interest, the scatter in the \mbh-\smass\ ratios at high-$z$ is similar to the local one.
+This was unexpected since the measurements of the masses of both the black holes and their hosts should have more uncertainty that local estimates.
+If true, this may indicate that cosmic averaging of initially unrelated states \citep{Peng2007} are not driving the relation between SMBHs and their host galaxies thus there is likely a connection between the two yet to be fully understood, contenders include AGN feedback or links to common gas reservoirs.
+
+Finally, the forthcoming launch of the {\it James Webb Space Telescope} ({\it JWST}) may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim$7) and thus trace the evolution of correlations at more distant universe.
+Although, galaxies, as we know, are smaller at high-$z$ thus may remain challenging to detect under the glare of a luminous AGN.
+In the lower redshift Universe, wide area surveys with Subaru/HSC, LSST and WFIRST offer much promise to build samples for studying these mass ratios and dependencies on other factors (e.g., environment).
 
@@
 
-Looking into the future, the forthcoming lunching of {\it James Webb Space Telescope} ({\it JWST}) would provide the high quality imaging data of AGN at higher redshift (up to $z\sim$7-10) and thus trace the evolution of correlation at more distant universe.
-Furthermore, {\it JWST} is capable of showing the morphology of structures feeding black hole accretion and feedback on the host galaxy~\citep{Ford2014}, thus providing the opportunity to understand the origin of the scaling relations and their evolution.
-
+%
+
+\clearpage
 \section*{Acknowledgments}
@@
 
-The authors fully appreciate the discussions with Hyewon Suh, Vardha N. Bennert, Anton M. Koekemoer, Takahiro Morishita and Peter Williams.
+%The authors fully appreciate the discussions with Hyewon Suh, Vardha N. Bennert, Anton M. Koekemoer, Takahiro Morishita and Peter Williams.
 
 XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
-{\color{blue} More acknowledges to be updated. }
+
+{\color{red} More acknowledges to be updated.}
 
@@
 
+\clearpage
+\section{B. AGN host galaxy luminosity with a correction for passive evolution}\label{sec:ml-ev}
+In the passive evolution scenario, we expect the galaxy luminosity to fade over time.
+Thus, we transfer the \lhost\ for distant samples at today so as to compare the \mbh-\lhost\ relation to the local in the equivalent frame.
+We consider this scenario following \citet{Ding2017b} by parametrizing the luminosity evolution with the functional form as
+$d{\rm mag}_{\rm R}\sim~d\log(1+z)$, i.e.,
+\begin{eqnarray}
+\label{eq:L_relation}
+\log(L_{R,0})=\log(L_{R}) - 1.48 \log (1+z).
+\end{eqnarray} 
+This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer the interested readers to \citet[][section 5.4]{Ding2017b} for more details.
+
+Having transferred the \lhost\ to today, we find that, as showing in Figure~\ref{fig:ML-vz}-(a), at fixed mass, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation.
+We fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 0.71 \pm 0.18$, as showing in Figure~\ref{fig:ML-vz}-(b).
+We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.3$, with flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
+
+The inferred $\gamma$ here could have large systematic given the following limitations.
+First, the passive evolution is based on a simplified correction; after all, we are not clear exactly how the host evolves to $z=0$.
+Moreover, we only consider the evolution of the host galaxy and assume the \mbh\ does not change much.
+%Moreover, in the literature, the correlation of the \mbh-\smass\ is considered as more fundamental which would be more efficient to understand their co-evolution.
+
+\begin{figure*}[ht]
+\centering
+\begin{tabular}{c c}
+\subfloat[\mbh-\lhost\ relation, evolution-corrected]
+{\includegraphics[height=0.5\textwidth]{fig/MBH-L_ev.pdf}}&
+\subfloat[offset in  $\log($\mbh$)$ (VS. \lhost) as a function of redshift]
+{\includegraphics[height=0.5\textwidth]{fig/MBH-L-vz.pdf}}\\
+\subfloat[\mbh-\lhost, flat prior]
+{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
+\subfloat[\mbh-\lhost, lognormal prior]
+{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
+\end{tabular}
+\caption{\label{fig:ML-vz} 
+Same as previous figures but for \mbh-\lhost\ relation, considering the passive evolution correction for host galaxy luminosity.}
+\end{figure*}
+
+\begin{deluxetable*}{llccccc}
+\tablecolumns{7}
+\tablewidth{0pt}
+\tablecaption{Details of Observation} 
+\tablehead{ 
+\colhead{Object ID} &
+\colhead{$z$} & 
+\colhead{WFC3/Filter} &
+\colhead{$RA$}&
+\colhead{$DEC$}&
+\colhead{Observing date}&
+\colhead{Exposure time (s)}
+\\ 
+\colhead{(1)} &
+\colhead{(2)} &
+\colhead{(3)} &
+\colhead{(4)} &
+\colhead{(5)} &
+\colhead{(6)} &
+\colhead{(7)}
+} 
+\startdata
+%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
+%\\
+COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
+COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
+COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
+COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
+COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
+COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
+COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
+COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
+COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
+COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
+COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
+COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
+COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
+COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
+COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
+COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
+COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
+COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
+COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
+COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
+COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
+CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
+CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
+CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
+ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
+CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
+SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
+SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
+SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
+SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
+SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
+SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
+\enddata
+\label{tab:objlist}
+\tablecomments{
+Column 1: Object field and ID.
+Column 2: Spectroscopic redshift.
+Column 3: WFC3 filter. Note that the targets from the COSMOS and (E)-CDF-S fields also have ACS imaging.
+Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
+Column 6: The observing start date.
+Column 7: Total exposure time.
+}
+\end{deluxetable*}
+
+\begin{deluxetable*}{ccccccc}
+\tablecolumns{7}
+\tablewidth{0pt}
+\tablecaption{Host inference of CID1174} 
+\tablehead{ 
+\colhead{PSF rank} &
+\colhead{total $\chi ^2$} & 
+\colhead{weights $w_i$} &
+\colhead{host flux (counts)} &
+\colhead{host flux ratio}&
+\colhead{\Reff (arcsec)}&
+\colhead{\sersic\ $n$}
+ \\ 
+\colhead{(1)} &
+\colhead{(2)} &
+\colhead{(3)} &
+\colhead{(4)} &
+\colhead{(5)} &
+\colhead{(6)} &
+\colhead{(7)} 
+} 
+\startdata
+%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
+%\\
+1 & $8584.429$ & $1.000$ & $82.2$ & $35\%$ & $0\farcs{}345$ & $1.1$ \\
+2 & $8646.711$ & $0.920$ & $99.1$ & $42\%$ & $0\farcs{}298$ & $1.9$ \\
+3 & $8816.947$ & $0.734$ & $76.7$ & $33\%$ & $0\farcs{}365$ & $1.1$ \\
+4 & $9304.841$ & $0.383$ & $128.6$ & $55\%$ & $0\farcs{}231$ & $2.8$ \\
+5 & $9652.575$ & $0.241$ & $187.5$ & $79\%$ & $0\farcs{}116$ & $6.2$ \\
+6 & $9917.101$ & $0.170$ & $100.2$ & $42\%$ & $0\farcs{}287$ & $2.1$ \\
+7 & $10018.324$ & $0.148$ & $75.1$ & $32\%$ & $0\farcs{}365$ & $1.2$ \\
+8 & $10087.456$ & $0.135$ & $79.8$ & $34\%$ & $0\farcs{}358$ & $1.2$ \\
+\hline\\
+Weighted value & & & $97.322\pm28.336$ & $42\%\pm12\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.9\pm1.3$  \\
+\enddata
+\label{tab:weight_CID1174}
+\tablecomments{
+Column~1: Rank of the PSF from the library.
+Column~2: Total $\chi ^2$ for the corresponding PSF.
+Column~3: Weights for the inference.
+Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
+For this sample, the inflation parameter $\alpha$ calculated by Equation~\ref{eq:alpha} is 16.671.
+}
+\end{deluxetable*}
+
+\begin{deluxetable*}
+{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
+\tablecolumns{9}
+\tablewidth{0pt}
+\tablecaption{Inferred BH properties for the 32 systems} 
+\tablehead
+{ 
+\colhead{Target ID}&
+  \multicolumn{4}{c}{using emission line \halpha}&
+  \multicolumn{4}{c}{using emission line \hbeta} \\
+  \cline{2-5}  \cline{6-9} \\
+\colhead{}& 
+\colhead{FWHM}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
+\colhead{FWHM(5100)}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
+\colhead{}& 
+\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
+\colhead{(M$_{\odot}$)}& (log$\lambda$)&
+\colhead{(\kms)}& 
+\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$\lambda$)\\
+\colhead{(1)}& 
+\colhead{(2)}& \colhead{(3)}& 
+\colhead{(4)}& \colhead{(5)}& 
+\colhead{(6)}&\colhead{(7)}&
+\colhead{(8)}& \colhead{(9)}
+}
+\startdata 
+CID1174 & 1906 & 43.43 & 7.99 & -0.47 & 5898 & 44.76 & 8.83& -1.34 \\
+CID1281 & 1619 & 43.24 & 7.75 & -0.41 & ... & ... & ... & ... \\
+CID206 & 3334 & 43.48 & 8.53 & -0.97 & ... & ... & ...& ... \\
+CID216 & 2230 & 42.85 & 7.85 & -0.90 & ... & ... & ...& ... \\
+CID237 & 2112 & 43.86 & 8.29 & -0.36 & ... & ... & ...& ... \\
+CID255 & 1932 & 43.99 & 8.27 & -0.22 & 3709 & 45.37 & 8.73& -0.60 \\
+CID3242 & 2543 & 43.83 & 8.45 & -0.55 & 3775 & 45.10 & 8.61& -0.75 \\
+CID3570 & 1959 & 43.16 & 7.89 & -0.63 & ... & ... & ...& ... \\
+CID452 & 3458 & 42.92 & 8.30 & -1.26 & 3127 & 44.63 & 8.22& -0.88 \\
+CID454 & 2824 & 43.34 & 8.31 & -0.88 & ... & ... & ...& ... \\
+CID50 & 2340 & 43.94 & 8.42 & -0.42 & 1939 & 45.33 & 8.15& -0.06 \\
+CID543 & 2189 & 43.57 & 8.19 & -0.53 & ... & ... & ...& ... \\
+CID597 & 1656 & 43.33 & 7.81 & -0.39 & ... & ... & ...& ... \\
+CID607 & 3009 & 43.67 & 8.53 & -0.78 & 4242 & 44.78 & 8.56& -1.04 \\
+CID70 & 2480 & 43.51 & 8.27 & -0.68 & 3982 & 45.16 & 8.69& -0.77 \\
+LID1273 & 3224 & 43.61 & 8.56 & -0.87 & ... & ... & ...& ... \\
+LID1538 & 2941 & 43.60 & 8.47 & -0.79 & ... & ... & ...& ... \\
+LID360 & 2482 & 43.88 & 8.45 & -0.50 & 2869 & 45.09 & 8.37& -0.52 \\
+XID2138 & 3186 & 43.61 & 8.55 & -0.86 & 2945 & 44.81 & 8.25& -0.71 \\
+XID2202 & 2973 & 43.56 & 8.46 & -0.82 & ... & ... & ...& ... \\
+XID2396 & 2271 & 44.06 & 8.46 & -0.33 & 2658 & 45.50 & 8.51& -0.24 \\
+CDFS-1 & 2000 & 43.02 & 7.83 & -0.03 & ... & ... & ...& ... \\
+CDFS-229 & 2190 & 43.60 & 8.20 & -0.60 & ... & ... & ...& ... \\
+CDFS-321 & 2442 & 43.93 & 8.46 & -0.46 & ... & ... & ...& ... \\
+CDFS-724 & 2541 & 42.95 & 8.03 & -1.15 & ... & ... & ...& ... \\
+ECDFS-358 & 2237 & 43.40 & 8.12 & -0.64 & ... & ... & ...& ... \\
+SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.81 & 6761 & 44.71 & 8.93& -1.49 \\
+SXDS-X50 & 1817 & 43.42 & 7.94 & -0.43 & ... & ... & ...& ... \\
+SXDS-X717 & 2931 & 43.05 & 8.20 & -1.05 & ... & ... & ...& ... \\
+SXDS-X735 & 2702 & 43.70 & 8.44 & -0.67 & 3520 & 45.07 & 8.54& -0.70 \\
+SXDS-X763 & 2961 & 43.57 & 8.47 & -0.81 & 4509 & 44.51 & 8.47& -1.29 \\
+SXDS-X969 & 2296 & 43.50 & 8.20 & -0.61 & 1696 & 45.05 & 7.90& -0.08 \\
+\enddata
+\label{tab:result_mbh}
+\tablecomments{
+Column 1: Object ID.
+Column 2-5: \halpha\ emission line width (FWHM), continuum luminosity, inferred \mbh\ and Eddington ratio.
+Column 6-9: \hbeta\ emission line BH properties. 
+The typical uncertainty level for FWHM and $\log( \rm L _{\lambda})$ are $15\%$ and $\pm0.01$, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
+}
+\end{deluxetable*}
+
+\tabcolsep=0.03cm
+\begin{deluxetable*}
+{@{\extracolsep{2pt}}lccccccccccc}   % need for the gap between the clines.
+\tablecolumns{10}
+\tablewidth{0pt}
+\tablecaption{Inferred host galaxy properties for the 32 systems.} 
+\tablehead
+{ 
+\colhead{Target ID}&
+  \multicolumn{5}{c}{WFC3}&
+  \multicolumn{3}{c}{ACS/F814W} &
+   \multicolumn{2}{c}{host properties} \\
+  \cline{2-6}  \cline{7-9} \cline{10-12}  \\
+\colhead{}& 
+\colhead{$\chi ^2$}& \colhead{host-total flux ratio}& 
+\colhead{\Reff}& \colhead{\sersic\ $n$}& 
+\colhead{magnitude}&
+\colhead{$\chi ^2$}& \colhead{host-total flux ratio}& \colhead{magnitude} &
+\colhead{$\log L_R$} &\colhead{$\log M_*$} &\colhead{$\log M_{*, bulge}$} \\
+\colhead{}& 
+\colhead{(reduced)}& \colhead{}& 
+\colhead{($\arcsec$)}& \colhead{}& 
+\colhead{(AB system)}& \colhead{(reduced)}& 
+\colhead{}& \colhead{(AB system)} &\colhead{($L_{\odot,R}$)} & \colhead{(M$_{\odot}$)} &  \colhead{(M$_{\odot}$)}\\
+\colhead{(1)}& 
+\colhead{(2)}& \colhead{(3)}& 
+\colhead{(4)}& \colhead{(5)}& 
+\colhead{(6)}& \colhead{(7)}& 
+\colhead{(8)}& \colhead{(9)}&
+\colhead{(10)}& \colhead{(11)} &  \colhead{(12)}
+}
+\setlength{\tabcolsep}{20pt}
+\renewcommand{\arraystretch}{1.5}
+\startdata 
+CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.05\substack{+0.15\\-0.11}$ &$10.78\substack{+0.18\\-0.15}$ & $10.45\substack{+0.18\\-0.15}$ \\[3pt]
+CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.41\substack{+0.15\\-0.11}$ &$10.14\substack{+0.18\\-0.15}$ & $9.99\substack{+0.18\\-0.15}$ \\[3pt]
+CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.86\substack{+0.52\\-0.23}$ &$10.59\substack{+0.53\\-0.25}$ & $10.43\substack{+0.53\\-0.25}$ \\[3pt]
+CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.05\substack{+0.03\\-0.03}$ &$10.78\substack{+0.10\\-0.10}$ & $10.64\substack{+0.10\\-0.10}$ \\[3pt]
+CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.18\substack{+0.11\\-0.09}$ &$10.91\substack{+0.14\\-0.13}$ & $10.77\substack{+0.14\\-0.13}$ \\[3pt]
+CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.08\substack{+0.15\\-0.11}$ &$10.81\substack{+0.18\\-0.15}$ & $10.69\substack{+0.18\\-0.15}$ \\[3pt]
+CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.16\substack{+0.14\\-0.11}$ &$10.89\substack{+0.17\\-0.15}$ & $10.75\substack{+0.17\\-0.15}$ \\[3pt]
+CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $10.98\substack{+0.02\\-0.02}$ &$10.71\substack{+0.10\\-0.10}$ & $10.02\substack{+0.10\\-0.10}$ \\[3pt]
+CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.13\substack{+0.03\\-0.03}$ &$10.86\substack{+0.10\\-0.10}$ & $10.25\substack{+0.10\\-0.10}$ \\[3pt]
+CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.11\substack{+0.04\\-0.04}$ &$10.84\substack{+0.10\\-0.10}$ & $10.21\substack{+0.10\\-0.10}$ \\[3pt]
+CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.07\substack{+0.35\\-0.19}$ &$10.80\substack{+0.36\\-0.21}$ & $10.65\substack{+0.36\\-0.21}$ \\[3pt]
+CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.70\substack{+0.16\\-0.12}$ &$10.43\substack{+0.19\\-0.15}$ & $9.73\substack{+0.19\\-0.15}$ \\[3pt]
+CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.73\substack{+0.22\\-0.15}$ &$10.46\substack{+0.24\\-0.18}$ & $10.12\substack{+0.24\\-0.18}$ \\[3pt]
+CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.02\substack{+0.23\\-0.15}$ &$10.75\substack{+0.25\\-0.18}$ & $10.59\substack{+0.25\\-0.18}$ \\[3pt]
+CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $10.98\substack{+0.12\\-0.10}$ &$10.72\substack{+0.16\\-0.14}$ & $10.58\substack{+0.16\\-0.14}$ \\[3pt]
+LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.32\substack{+0.09\\-0.07}$ &$11.05\substack{+0.13\\-0.12}$ & $10.46\substack{+0.13\\-0.12}$ \\[3pt]
+LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.12\substack{+0.09\\-0.08}$ &$10.86\substack{+0.13\\-0.12}$ & $10.69\substack{+0.13\\-0.12}$ \\[3pt]
+LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.08\substack{+0.06\\-0.05}$ &$10.81\substack{+0.11\\-0.11}$ & $10.08\substack{+0.11\\-0.11}$ \\[3pt]
+XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.89\substack{+0.07\\-0.06}$ &$10.63\substack{+0.12\\-0.12}$ & $10.04\substack{+0.12\\-0.12}$ \\[3pt]
+XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.15\substack{+0.12\\-0.10}$ &$10.88\substack{+0.16\\-0.14}$ & $10.76\substack{+0.16\\-0.14}$ \\[3pt]
+XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.12\substack{+0.26\\-0.16}$ &$10.85\substack{+0.28\\-0.19}$ & $10.10\substack{+0.28\\-0.19}$ \\[3pt]
+CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ...
+& ...
+& ...
+& $10.71\substack{+0.16\\-0.12}$ &$10.45\substack{+0.19\\-0.15}$ & $10.3\substack{+0.19\\-0.15}$ \\[3pt]
+CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ...
+& ...
+& ...
+& $10.90\substack{+0.06\\-0.05}$ &$10.63\substack{+0.12\\-0.11}$ & $9.90\substack{+0.12\\-0.11}$ \\[3pt]
+CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ...
+& ...
+& ...
+& $11.52\substack{+0.28\\-0.17}$ &$11.25\substack{+0.30\\-0.20}$ & $11.03\substack{+0.30\\-0.20}$ \\[3pt]
+CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ...
+& ...
+& ...
+& $10.06\substack{+0.23\\-0.15}$ &$9.79\substack{+0.25\\-0.18}$ & $9.39\substack{+0.25\\-0.18}$ \\[3pt]
+ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ...
+& ...
+& ...
+& $11.16\substack{+0.12\\-0.10}$ &$10.89\substack{+0.16\\-0.14}$ & $10.53\substack{+0.16\\-0.14}$ \\[3pt]
+SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ...
+& ...
+& ...
+& $10.75\substack{+0.09\\-0.08}$ &$10.49\substack{+0.14\\-0.13}$ & $10.16\substack{+0.14\\-0.13}$ \\[3pt]
+SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ...
+& ...
+& ...
+& $10.80\substack{+0.11\\-0.09}$ &$10.54\substack{+0.15\\-0.13}$ & $10.15\substack{+0.15\\-0.13}$ \\[3pt]
+SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ...
+& ...
+& ...
+& $10.77\substack{+0.07\\-0.06}$ &$10.51\substack{+0.12\\-0.12}$ & $10.34\substack{+0.12\\-0.12}$ \\[3pt]
+SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ...
+& ...
+& ...
+& $11.19\substack{+0.13\\-0.10}$ &$10.92\substack{+0.17\\-0.14}$ & $10.62\substack{+0.17\\-0.14}$ \\[3pt]
+SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ...
+& ...
+& ...
+& $9.95\substack{+0.47\\-0.22}$ &$9.68\substack{+0.48\\-0.24}$ & $9.48\substack{+0.48\\-0.24}$ \\[3pt]
+SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ...
+& ...
+& ...
+& $11.03\substack{+0.21\\-0.14}$ &$10.76\substack{+0.23\\-0.17}$ & $10.47\substack{+0.23\\-0.17}$ \\[3pt]\enddata
+\label{tab:result_sersic}
+\tablecomments{
+Column~1: Object ID.
+Column~2-6: WFC3 inference. 
+Column~2: Reduced $\chi ^2$ value by the best PSF in the library.
+Column~7-9: ACS inference. 
+Column~10: Observed host luminosity in the rest-frame R band.
+Column~11: Host total stellar mass.
+Column~12: Bulge stellar mass, using \sersic\ index as B/T proxy, based on Section~\ref{sec:bh_bulge} and Figure~\ref{fig:BT-n_relation}.
+}
+\end{deluxetable*}
+
+\begin{table}
+\centering
+    \caption{The inference of $\gamma$ using \mbh-\smass\ by different sample combination.}\label{table:diff_sample_gam}
+     \resizebox{5.5cm}{!}{
+     \begin{tabular}{cc}
+     \hline
+     Sample combination & $\gamma$ \\
+     &\\
+     \hline\hline
+32 AGNs & 0.78$\pm$0.26\\    
+30 AGNs (excluded outliers) & 0.65$\pm$0.27\\    
+32 AGNs + intermediate &  0.58$\pm$0.20\\
+32 AGNs bulge only & 1.63$\pm$0.27\\
+     \hline
+     \end{tabular}}
+\tablecomments{These values are directly inference for the observation, which haven't yet taken the selection effect into account.}
+\end{table}
+
+\begin{table}
+\centering
+    \caption{The summary for the different inference of $\gamma$.}\label{table:gamma_sf}
+     \resizebox{8cm}{!}{
+     \begin{tabular}{cccc}
+     \hline
+     Sample & Selection effects &  \mbh-\smass & \mbh-\lhost \\
+     &&&\\
+     \hline\hline
+32 AGNs + intermediate & No &  0.58$\pm$0.20 & 0.61$\pm$0.18 \\
+32 AGNs + intermediate& Yes & 0.80$\pm$0.40 & 0.50 $\pm$ 0.50 \\
+32 AGNs & No & 0.78$\pm$0.26  & 0.99$\pm$0.23\\
+32 AGNs& Yes & 1.20$\pm$0.80 & 1.60$\pm$0.80 \\
+     \hline
+     \end{tabular}}
+    \tablecomments{
+    Entire sample includes the 32 AGNs and the intermediate redshift AGNs from the reference in Section~\ref{sec:compare_sample}.
+Note that the adopted \lhost\ have been transferred to today assuming the passive evolution scenario using Equation~\ref{eq:L_relation}.
+The results of selection effects used the uniform (flat) prior of \sint.
+}
+\end{table}
+
 \end{document}

### 2019-07-10 analysis_Astrodrz/compare_K-correction.py

@@ -18,6 +18,9 @@ sys.path.insert(0,'../py_tools')
 from filter_info import filt_info, redshift_info
 import pickle
 
+import matplotlib as mat
+mat.rcParams['font.family'] = 'STIXGeneral'
+
 def load_result(ID, count_rank=8, sort_PSF_by='fit_result_each', cam = 'WFC3'):
     '''
     Read the fitting result by given the ID, 
@@ -157,25 +160,26 @@ mag_k_corrected_UV=mags_obs_UV-5*(np.log10(dl)-1) + dm_k_UV
 #    print ID[i], mag_k_corrected_IR[i], mag_k_corrected_UV[i]
 #if needed lumi_s = 0.4*(4.61-mag_k_corrected)
 
-plt.figure(figsize=(10, 10))
+plt.figure(figsize=(9, 9))
 plt.errorbar(mag_k_corrected_IR, mag_k_corrected_UV,xerr= mag_IR_err.T, yerr=mag_UV_err.T,color='red', fmt='o',ecolor='gray' )
-texts = []
-for i in range(len(ID)):
-    texts.append(plt.text(mag_k_corrected_IR[i], mag_k_corrected_UV[i], ID[i], fontsize=17))
-adjust_text(texts, arrowprops=dict(arrowstyle='->', color='red'))
+#texts = []
+#for i in range(len(ID)):
+#    texts.append(plt.text(mag_k_corrected_IR[i], mag_k_corrected_UV[i], ID[i], fontsize=17))
+#adjust_text(texts, arrowprops=dict(arrowstyle='->', color='red'))
 x=np.linspace(-26,-20,15)
 y = x
 plt.plot(x,y,'b')
-plt.title('Galaxy age: '+galay_temp, fontsize=30)
-plt.xlabel('Absolute rest-frame R mag by WFC3',fontsize=25)
-plt.ylabel('Absolute rest-frame R mag by ACS', fontsize=25)
+#plt.title('Galaxy age: '+galay_temp, fontsize=24)
+plt.xlabel('Absolute rest-frame R mag by WFC3',fontsize=21)
+plt.ylabel('Absolute rest-frame R mag by ACS', fontsize=21)
 val_min, val_max = np.min([mag_k_corrected_UV, mag_k_corrected_IR]), np.max([mag_k_corrected_UV, mag_k_corrected_IR])
 plt.xlim(val_min-0.5, val_max+0.5)
[…]

### 2019-07-29 manuscript/manuscript.tex
Update the paper with people's feedback

@@
 \def\smass{{$M_*$}}
-\def\bmass{{$M_{*, bulge}$}}
+\def\bmass{{$M_{*, \rm {bulge}}$}}
 \newcommand{\Mgii}{Mg$_{\rm II}$}
@@
 
-\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{4}, Malte Schramm\altaffilmark{4}, Simon Birrer\altaffilmark{1}, Daeseong Park\altaffilmark{5}, Knud Jahnke\altaffilmark{6}, ???, ???
-% {\color{blue} Federica Duras\altaffilmark{7, 8}, Angela Bongiorno\altaffilmark{8}}
+\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{4}, Malte Schramm\altaffilmark{4}, Simon Birrer\altaffilmark{1}, Daeseong Park\altaffilmark{5}, Knud Jahnke\altaffilmark{6}, Vardha N.
+Bennert\altaffilmark{7}, Jeyhan S.
+Kartaltepe\altaffilmark{8}, Anton M.
+Koekemoer\altaffilmark{9},  Matthew A.
+Malkan\altaffilmark{1}  % {\color{blue} Federica Duras\altaffilmark{7, 8}, Angela Bongiorno\altaffilmark{8}}
  }
@@
 \altaffiltext{6}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117, Heidelberg, Germany}
+\altaffiltext{7}{Physics Department, California Polytechnic State University, San Luis Obispo CA 93407, USA}
+\altaffiltext{8}{School of Physics and Astronomy, Rochester Institute of Technology, Rochester, NY 14623, USA}
+\altaffiltext{9}{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
 %\altaffiltext{7}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
@@
 For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
-By applying state-of-the-art tools to decompose the \hst\ emission, we measured the host galaxy luminosity and stellar mass along with other properties through 2D model fitting.
+By applying state-of-the-art tools to decompose the \hst\ image, we measured the host galaxy luminosity and stellar mass along with other properties through 2D model fitting.
 The black hole mass (\mbh) is determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators.
@@
 The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
-Therefore, given the uncertainties, our results are in agreement with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former is somewhat slightly anticipated.
-Using a mass-matched sample of inactive galaxies to infer the bulge-to-total mass fraction we show that the bulge \mbh/\bmass~relation is significantly offset from the local one by a factor of $\sim4.5$; this offset is still present even after accounting for selection effects.
-Thus, our observations are consistent with a scenario in which stellar mass is transferred from an angular momentum supported to the pressure supported component of the galaxy through secular processes or minor mergers at a faster rate than the mass accretion onto the SMBH.
+Therefore, given the uncertainties, our results are in agreement with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter.
+Using a mass-matched sample of inactive galaxies to infer the bulge-to-total mass fraction we show that the bulge \mbh/\bmass~relation is significantly offset from the local one by a factor of $\sim$$+5.5$; this offset is still present even after accounting for selection effects.
+Thus, our observations are consistent with a scenario in which stellar mass is transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than the mass accretion onto the SMBH.
 
@@
 Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass) and stellar velocity dispersion (\sigstar).
-These tight correlations (known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
+The tightness of these correlations (also known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
 Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc).
 On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering either the active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or how the growth of these components is connected to the common gas supply~\citep{Cen2015, Menci2016}.
-On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from galaxy assembly (i.e., mergers) which can reproduce the observed correlations.
+On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, the statistical convergence from galaxy assembly alone (i.e., mergers) can reproduce the observed correlations.
 
@@
 If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.
-A possible mechanism to account for the latter part of the growth of the galaxy without increasing \mbh\ is the transfer of stellar mass from the disk to the bulge \citep{Bennert++2011}.
+A possible mechanism to account for the latter part of the growth of the galaxy without increasing \mbh\ is the transfer of stellar mass from the disk to the bulge \citep{Bennert++2011} through bar instabilities or minor mergers.
 
 However, there are studies \citep{Cisternas2011,SS13,Mechtley2016} based on \hst\  imaging of deep survey fields such as COSMOS and CDFS that report no evolution in the \mbh - \smass ~ mass ratio as compared to the local relation.
-In support, \citet{Sun2015} has re-analyzed the mass ratios for BLAGN in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citet{Merloni2010} and finds no evolution when accounting for selection effects, as fully described in \citet{Schulze2014} that consider the black hole mass functions and Eddington rate distribution.
+In support, \citet{Sun2015} has re-analyzed the mass ratios for broad-line AGNs in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citet{Merloni2010} and finds no evolution when accounting for selection effects, as fully described in \citet{Schulze2014} that consider the black hole mass functions and Eddington rate distribution.
 
@@
 First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method.
-In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-gravitational component of the BLR gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e.
+In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-gravitational component of the broad-line region (BLR) gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e.
 \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}.
@@
 In particular, samples based on 2D image analysis using \hst\ at $z>1$ are limited thus the infrared capabilities of \hst/WFC3 have not been fully exploited to date on this topic.
-Here, we measure the properties of 32 host galaxies in redshift range $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS.
+Here, we measure the properties of 32 host galaxies within a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS.
 Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e.
@@
 In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population for which we apply to derive the rest-frame R-band \lhost\,~and \smass\ to compare with local relations.
-In addition, we use the information on the radial light distribution (i.e., Sersic index) to infer the likely fraction of stars in the bulge to infer the \bmass\ relation.
+In addition, we use the information on the radial light distribution (i.e., Sersic index) to infer the likely fraction of stars in the bulge (\bmass) and its relation to the \mbh.
 The discussion and conclusions are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}.
@@
 
-We utilize a sample of broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that have black hole mass measurements available and fall within deep extragalactic survey fields that offer rich ancillary data.
+We utilize a sample size of 32 broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that have black hole mass measurements available and fall within deep extragalactic survey fields that offer rich ancillary data.
 Specifically, we focused on meeting the following criteria to overcome limitations of previous studies:
@@
 
-\item Eddington ratios typically above 1\% for most of the sample to further ensure homogeneity.
-
-\item An X-ray selected sample demonstrated to have lower nuclear-to-host ratios thus facilitating the galaxy mass measurements. This is somewhat coupled to the second item in this list.
-
-\item \hst/WFC3 imaging of the host galaxy above the 4000~\angstrom\ break and not including the broad \halpha\ line (6563~\angstrom). This ensures sensitivity to the total stellar mass content.
-
-\item A large fraction of the sample has addition \hst\ imaging (i.e., ACS), providing color information to achieve reliable K-corrections and stellar mass determinations. 
+\item Eddington ratios are typically above 1\% for most of the sample to further ensure homogeneity.
+
+\item The lower nuclear-to-host ratios of our sample facilitates the galaxy mass measurements, given that they are 
+X-ray selected. This is somewhat coupled to the second item in this list.
+
+\item \hst/WFC3 imaging of the host galaxy is above the 4000~\angstrom\ break and does not include the broad \halpha\ line (6563~\angstrom). This ensures sensitivity to the total stellar mass content.
+
+\item A large fraction of the sample has additional \hst\ imaging (i.e., ACS), providing color information to achieve reliable K-corrections and stellar mass determinations. 
 \end{itemize}
@@
 
-The AGN sample is initially detected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
+The 32 AGNs are initially selected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
 In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck and Magellan.
@@
 We refer the reader to that paper for the details of continuum fitting and emission-line modeling.
+Note that three CDFS objects (i.e.
+CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015}.
 
 Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$~(M$_{\odot}$).
-The bolometric luminosities presented in \citet{Schulze2018} are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
+The bolometric luminosities are measured from AGN broad lines by \citet[][Section 3.3]{Schulze2018} which are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
 The flux-limited nature of the sample results in higher Eddington ratios when \mbh\ is lower as shown in Figure~\ref{fig:selection}.
 Moreover, we have higher preference to select targets which have rest-frame UV images as provided by \citet{Scoville2007} and \citet{Koekemoer2007} in the COSMOS field and REFS for the (E)-CDF-S.
-We list the AGNs observed with \hst/WFC3 and analyzed in this work in Table~\ref{tab:objlist} sorted by field and redshift.
+We list the 32 AGNs observed with \hst/WFC3 and analyzed in this work in Table~\ref{tab:objlist} sorted by field and redshift.
 
@@
 The \mbh\ of type-1 AGNs can be inferred using the so-called virial method~\citep{Peterson2004, Shen2013}.
-The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas.
-Under these assumptions, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establishes an empirical scale of the BLR size.
-As a result, the estimation of the \mbh\ is achieved by these measurements.
+The kinematics of the BLR trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas.
+Under these assumptions, the width of the emission-line provides the scale of the velocity dispersion ($\Delta V$), while the AGN continuum luminosity establishes an empirical scale of the BLR size ($R_{\rm BLR}$).
+As a result, the estimation of the \mbh\ is achieved by these measurements, i.e., \mbh$\simeq G^{-1} R_{\rm BLR} \Delta V^2$ \citep{McLure2004}.
 
@@
 To avoid any systematic bias between samples in the literature, we aim to adopt a class of self-consistent estimators for our sample.
-We first compare the estimators implemented in \citet{Schulze2018} to the those in \citet{Ding2017b}, and find that their \hbeta(FWHM(5100)) estimators are very consistent (\mbh\ r.m.s.
+We first compare the estimators implemented in \citet{Schulze2018} to those in \citet{Ding2017b}, and find that their \hbeta(FWHM(5100)) estimators are very consistent (\mbh\ r.m.s.
 $<0.03$~dex).
@@
 Thus, we utilize the AGNs in \citet{Schulze2018} that have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to determine which \halpha\ estimator has been agreement between the two lines.
-As a  result, the \halpha\ estimator in \citet{Schulze2018} has better agreement with \hbeta\  .
+As a  result, the \halpha\ estimator in \citet{Schulze2018} has better agreement with \hbeta.
 Thus, we adopt the scheme given in \citet{Schulze2018} for all AGN samples used in this study including the comparison samples described below.
@@
 
+Note that these recipes are first provided by \citet{Vestergaard2006}.
 Using these recipes, we estimate \mbh\ by adopting the emission-line properties as measured by \citet{Schulze2018} for all 32 AGNs.
-The three objects (i.e.
-CDFS-1, CDFS-229 and CDFS-724) have infrared spectra provided by \citet{Suh2015}.
-While fourteen AGN have emission line properties for both \halpha\ and \hbeta, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample.
+While fourteen AGNs have emission line properties for both \halpha\ and \hbeta, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample.
 It is worth noting that the absolute flux calibration of the FMOS spectra is set to match ground-based IR imaging, ULTRAVISTA in the case of COSMOS thus amounting to an effective aperture correction.
@@
 Our AGN sample is primarily selected based on the value of \mbh~and Eddington ratio.
-It is well known that sample selection effects must be taken into account in order to  interpret the observed black hole-host relations and measure its evolution with redshift thus avoiding well understood biases ~\citep{Tre++07,Schulze2011,Bennert++2011, Schulze2014,Park15}.
-The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (like AGN luminosity and line strength and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors.
+It is well known that sample selection effects must be taken into account in order to  interpret the observed black hole-host relations and measure its evolution with redshift thus avoiding biases~\citep{Tre++07,Schulze2011,Bennert++2011, Schulze2014,Park15}.
+The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (such as AGN luminosity, line strength and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors.
 Correcting for observational biases requires a well-characterized selection function, such as the one we have for our sample, and a model of the black hole mass function, and the evolution of the correlations between \mbh, and other properties.
 
-To assess the amount of bias that we can anticipate given our selection function, we use the Bayesian framework introduced by \citet{Schulze2011,Schulze2014} to estimate the expected bias.
+Given our selection function, we use the Bayesian framework introduced by \citet{Schulze2011,Schulze2014} to estimate the expected bias.
 In this framework, under the assumption of no evolution of the correlations between \mbh\ and host-galaxy properties, one can compute the expected bias for a given sample, prior to the observations.
@@
 To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04).
-It is worth noting that for the local comparison sample, the bulge mass is equivalent to the total stellar mass.
+It is worth noting that the local comparison sample are mainly bulge dominated, and their bulge mass is adopted in this work.
 In other words, our local comparison is the \mbh-\smass$_{\rm ,bulge}$ and not those involving total quantities.
@@
 For this purpose, we observed the sample of 32 AGNs, as described above, with the \hst/WFC3 infrared channel, through the \hst\ program GO-15115 (PI: John Silverman).
-We elected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets so that the rest-frame spectral window was well above the 4000~\angstrom\ break.
+We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets so that the rest-frame spectral window is well above the 4000~\angstrom\ break.
 This selection further ensures that the broad \halpha\ line is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.
@@
 For each target, we obtained six separate exposures of 399s (i.e., total exposure time 2394s).
-The six exposures were dithered and combined with the {\sc astrodrizzle} software package that resulted in an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 and using a \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted.
+The six exposures were dithered and combined with the {\sc astrodrizzle} software package following standard procedures, and resulted in an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 and using a \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted.
 We achieve to analyze this sample using the same approach, taking the 3 available frames.}.
@@
 
-The knowledge of the PSF is crucial for imaging decomposition of the AGN and its host, especially when the point source contributes to the majority of the total emission.
+The knowledge of the PSF is crucial for imaging decomposition of the AGN and its host, especially when the point source contributes the majority of the total emission.
 The PSF is known to vary across the detector and in time due to the effects of aberration and breathing.
@@
 Actually, we have found that such stars usually do not provide an ideal PSF for de-blending the AGN and host galaxy through extensive tests.
-The issues have to due with an insufficient number of bright stars near our targets, color differences, and other effects not fully understood.
+The issues have to make due with an insufficient number of bright stars near our targets, color differences, and other effects not fully understood.
 
@@
 %Introduce Lenstronomy:
-We use the image modeling tool \lenstronomy~\citep{lenstronomy} to perform the decomposition of the host and nuclear light.
+We use the image modeling tool \lenstronomy~\citep{Birrer2015, lenstronomy} to perform the decomposition of the host and nuclear light.
 \lenstronomy\ is a multi-purpose open-source gravitational lens image forward-modeling package written in Python.
@@
 Thus, we only take the best-fit inference using PSO for further calculations.
-The errors on the fit parameters are assessed by using different PSFs for each object in the sample.}.
-To avoid any unphysical results, we set the upper and lower limits on the parameters: effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, \sersic\ index $n\in[1,7]$.
+The errors on the fit parameters are assessed by using different PSFs for each object in the sample.} \citep{PSO}.
+To avoid any unphysical results, we set the upper and lower limits on the parameters: effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, \sersic\ index $n\in[0.3,7]$.
 Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best-fit PSFs.
@@
 
-Note that since each AGN was observed in different location of the detector and at a different time, the top-eight PSFs usually vary from one AGN to another.
+Note that since each AGN was observed at a different location of the detector and at a different time, the top-eight PSFs usually vary from one AGN to another.
 Given the weights, the value of host properties and the root-mean-square ($\sigma$) error are calculated as:
@@
 \begin{eqnarray}
+\label{eq:infer_scatter}
 \sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} },
 \end{eqnarray} 
-where $N$ is the number of the ranking PSF, i.e., 8.
-
+where $N$ is the number of the ranking PSF, i.e., $N=8$.
 \noindent In Figure~\ref{fig:AGN_decomp}, we demonstrate the results for COSMOS-CID1174. The adopted weights are listed in Table~\ref{tab:weight_CID1174}.
@@
 %The inference of F814w data.
-We carry out a similar analysis for 18/32 AGNs in the COSMOS field with ACS/F184W imaging data.
+We carry out a similar analysis for 21/32 AGNs in the COSMOS field with ACS/F184W imaging data.
 We assess their host flux ratio using the same approach as done for the WFC3-IR.
@@
 From our AGN-host decomposition, we detect the host galaxy in essentially all cases.
-\hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data-point source'' stamps) shown in Figures~\ref{fig:AGN_decomp} and Appendix~\ref{sec:restsample}.
-While some of the galaxies have nearby neighbors, most are isolated and do not show strong signs of interaction or ongoing mergers.
-This is relevant for model fitting with smooth \sersic\ profiles and the subsequent determination of the stellar mass.
-In the following subsections, we described the properties of our ensemble of type-1 AGN host galaxies.
+\hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data-point source'' stamps) of Figures~\ref{fig:AGN_decomp} and Appendix~\ref{sec:restsample}.
+While some of the galaxies have nearby neighbors, most are isolated and do not show strong signs of interaction or ongoing mergers, {\bf which indicates the fueling of AGNs seems not from major mergers for our sample.} This is also relevant for model fitting with smooth \sersic\ profiles and the subsequent determination of the stellar mass.
+In the following subsections, we describe the properties of our ensemble of type-1 AGN host galaxies.
 
@@
 \label{sec:result-hosts}
-As shown in Figure~\ref{fig:hist_compare}, the host-to-total flux ratio of the sample spans a wide range from 10\% to 90\% with most of the sample concentrated between 20\% to 50\%.
+As shown in Figure~\ref{fig:hist_compare}, the host-to-total flux ratio (total=host+nuclear) of the sample spans a wide range from $10\%$ to $90\%$ with most of the sample concentrated between $20\%$ to $50\%$ (median value $37\%$).
 Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the very few cases around 10\% should be considered as marginal detections.
@@
 These values are distributed within the allowed range and not concentrated on either the upper or lower bound.
-The \Reff\ of our sample are between $\sim$1-7~kpc (peaked at $\sim$2.2~kpc).
-Nearly half (15/32) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge.
+The \Reff\ of our sample are between $\sim1-7$~kpc (peaked at $\sim2.2$~kpc).
+Nearly half ($15/32$) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge.
 Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
+{\bf The inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus their scatters are zero.
+This means the size inference of these three systems could be biased.
+However, the inference of their host luminosities and stellar masses are still reliable given the small scatter in the host flux ($<10\%$).}
 
@@
 
-For 18/32 AGNs, we have multi-band host magnitudes that enable us to select an appropriate stellar population template to determine rest-frame luminosities and stellar masses for the overall sample.
+For $21/32$ AGNs, we have multi-band host magnitudes that enable us to select an appropriate stellar population template to determine rest-frame luminosities and stellar masses for the overall sample.
 To minimize the uncertainty associated with these corrections, we use this template to interpolate to the rest-frame R band which is very close to the observed wavelengths.
-We find that a 1~Gyr stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} provides a good match to the observed colors of our sample (see Figure~\ref{fig:compare_temp}).
+We find that a $1$~Gyr stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} provides a good match to the observed colors of our sample (see Figure~\ref{fig:compare_temp}).
 We note that the choice is not unique, and other combinations of ages and metallicities and star formation history could match the observed colors and would provide very similar R-band magnitudes, and also stellar masses \citep{Bell2000, Bell2001}.
@@
 \caption{\label{fig:compare_temp} 
-Comparison of the inferred rest-frame R band magnitude based on the adopted stellar population, using 18/32 AGNs which have both WFC3 and ACS imaging data.
+Comparison of the inferred rest-frame R band magnitude based on the adopted stellar population, using $21/32$ AGNs which have both WFC3 and ACS imaging data.
 }
@@
 
-Adopting the 1~Gyr stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample.
+Adopting the $1$~Gyr stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample.
 As mentioned above, since the WFC3 filter is already close to the rest-frame R-band, we expect the $M_R$ uncertainty introduced by this K-correction to be within 0.05~mag.
@@
 \label{eq:MLlocal}
-\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}}),
+\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha_0 + \beta_0 \log(\frac{L_R}{10^{10}L_{\odot}}),
 \end {eqnarray}
@@
 
-We note that there are outliers that deviate from the distribution of overall sample, such as SXDS-X763.
+We note that there are outliers that deviate from the distribution of the overall sample, such as SXDS-X763.
 We suspect that this source may have abnormal host properties.
@@
 \caption{\label{fig:ML} 
-Black hole mass vs.
+The {\it observed} black hole mass vs.
 R-band luminosity relation.
@@
 
-To fulfill our purpose of acquiring the NIR imaging with \hst, we use the host luminosity along with color information to estimate the stellar mass content of each host galaxy  based on the mass-to-light ratio of the adopted stellar population.
-The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex (changing the IMF would effect all our stellar masses systematically).
+Using the NIR imaging with \hst, we take the host luminosity along with color information to estimate the stellar mass content of each host galaxy based on the mass-to-light ratio of the adopted  $1$~Gyr stellar population.
+The uncertainty level associated with the stellar mass is expected to be of order $0.1$~dex (changing the IMF would effect all our stellar masses systematically).
 We find $M_*$ ranges between $\log M_* \in [9.7, 11.3]$ ($M_{\odot}$).
@@
 However, there is a slight shift of the high-$z$ data towards higher black hole masses at a fixed host mass.
-In Figure~\ref{fig:MM-vz}, we plot, as a function of redshift, the mass ratio ($right$ panel) and the mass ratio difference ($\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$ which is considered as the difference between the high redshift data and the best-fit local relation; $left$ panel).
+In Figure~\ref{fig:MM-vz}, we plot, as a function of redshift, the mass ratio ({\it right} panel) and the mass ratio difference ($\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$ which is considered as the difference between the high redshift data and the best-fit local relation; {\it left} panel).
 For our high-$z$ sample, we find the average $\Delta \log \mathcal M_{\rm BH}$ to be 0.3, a factor of two higher than the local mass ratio as indicated by the top green circle in Figure~\ref{fig:MM-vz}.
@@
 \label{eq:MMlocal}
-\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}),
+\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha_1 + \beta_1 \log(\frac{M_*}{10^{10}M_{\odot}}),
 \end {eqnarray}
@@
 \caption{\label{fig:MM} 
-Black hole mass vs. stellar mass relation ( \mbh -- \smass\ ). The best-fit local relation is shown as described in Fig.~\ref{eq:MLlocal}.
+Black hole mass vs. stellar mass relation ( \mbh -- \smass\ ). The best-fit local relation is shown as described in Figure~\ref{fig:ML}.
 }
@@
 The orange band is the intrinsic scatter of local linear relation.
-The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs.
+The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, with slope value $\gamma  = 0.78 \pm 0.26$.
 Right: \mbh/\smass\ as a function of redshift. 
@@
 As shown in these panels, the scatter of the high-$z$ correlation presents a similarity to the local relation.
-To quantitively make this comparison, we calculate the scatter of their offset value, based on Equation~\ref{eq:infer_value}, and obtain $0.33$ for high-$z$ and $0.40$ for local samples, respectively.
+To quantitively make this comparison, we calculate the intrinsic scatter of their offset value, based on Equation~\ref{eq:infer_value}, and obtain $0.33$ for high-$z$ and $0.40$ for local samples, respectively.
 This result is against the scenario where the random merger is the origin of the correlation \citep{Peng2007}, indicating that there is likely to be a connection between the SMBHs and their host galaxies during their formation.
-
-%\begin{figure}
-%\centering
-%{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_subsample.pdf}}
-%\caption{\label{fig:MM_restsample} 
-%Same as Figure~\ref{fig:MM-vz}, left, but excluding the 3 outliers systems. The result shows the evolution still exist among the other 29 AGN sample.
-%}
-%\end{figure}
 
@@
 
-In Section~\ref{sec:sf_framework}, we used the Bayesian framework introduced by \citet{Schulze2011} to show that in the case of no intrinsic evolution of the correlations we would expect to measure an offset corresponding to a $+0.21$~dex bias in the inferred $\Delta \log$\mbh, owing to our selection function.
-Interestingly, this bias could account for the majority of the observed offset as obtained in the \mbh-\smass\ correlations in last Section.
+In Section~\ref{sec:sf_framework}, we used the Bayesian framework introduced by \citet{Schulze2011} to forward model the distribution functions through a selection convolution.
+The result show that in the case of no intrinsic evolution of the correlations we would expect to measure an offset corresponding to a $+0.21$~dex bias in the inferred $\Delta \log$\mbh, owing to our selection function.
+Interestingly, this bias could account for the majority of the observed offset as obtained in the \mbh-\smass\ correlations in the last section.
 %~\ref{sec:mm}.
 To illustrate the expected bias, we use green open circles to show the corresponding shift of the observed points if one were to correct for this bias in Figure~\ref{fig:MM-vz}.
-We also show, in Figure~\ref{fig:offset_hist}, the histogram the $\Delta \log$\mbh\ by the high-$z$ sample and compare to the local ones.
+We also show, in Figure~\ref{fig:offset_hist}, the histogram $\Delta \log$\mbh\ by the high-$z$ sample and compare to the local ones.
 The plots show that the correlations between \mbh\ and host galaxy total stellar mass or luminosity could be consistent with those of the local samples given the uncertainties and selection function
@@
 
-In order to further evaluate the ``true" underlying evolution and its uncertainty, corrected for selection effects, taking into account the actual observations, we adopt an independent method based on the approach introduced by \citet{Tre++07} and developed by \citet{Park15} and \citet{Ding2017b}.
+In order to further evaluate the ``true" underlying evolution and its uncertainty, corrected for selection effects, taking into account the actual observations, we adopt an independent method based on the approach introduced by \citet{Tre++07} and developed by \citet{Ben++10}, \citet{Park15} and \citet{Ding2017b}.
 The method parametrizes the evolution of the correlations between \mbh\ and host galaxy properties as an offset from the local one $\gamma$ and an intrinsic scatter \sint, which can be a free parameter or tied to the local relation.
@@
 To illustrate the importance of the intrinsic scatter in the selection effects, we adopt both uniform (flat) prior and lognormal prior for \sint.
-Note that this method assumes a narrow Eddington radio distribution which is different to the one by \citet{Schulze2011}, as described in Section~\ref{sec:sf_framework}.
+Note that this method assumes a narrow Eddington ratio distribution which is different to the one by \citet{Schulze2011}, as described in Section~\ref{sec:sf_framework}.
 Also, this method adopts the local black hole mass function rather than high-$z$ BH mass function.
-These differences have a second order effect and could be responsible to the different magnitude of the selection effect.
+These differences have a second order effect and could be responsible for the different magnitude of the selection effect.
 On the other hand, this method probes the importance of the scatter at high-$z$, which is complementary.
@@
 Thus one cannot conclude that evolution is significantly detected in our data.
-When relaxing the prior on \sint\ we find that the scatter is consistent with being as low as in the local samples, with a one-sided interval including zero and peaking at around 0.5~dex. 
-We also study the selection effect by only consider the new 32 AGNs, result in a higher evolution trend with a higher value of $\gamma$.
+When relaxing the prior on \sint\ we find that the scatter is consistent with being as low as in the local samples, with a one-sided interval including zero and with $1-\sigma$ upper limit at around $0.5$~dex.
+We also study the selection effect by only considering the new 32 AGNs, resulting in a higher evolutionary trend with a higher value of $\gamma$.
 We show all the result of the $\gamma$ and \sint\ in Table~\ref{table:gamma_sf}.
 
-A simple check using our a-priori estimate of the bias, yields a similar result.
+A simple check using our priori estimate of the bias, yields a similar result.
 The mean offset of the sample of 32 objects from the local relationship is $0.34\pm0.06$ dex, which would correspond to $\gamma=0.85\pm0.15$.
@@
 We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
-Whereas we expect the negative tail to be suppressed by our selection function, and thus it should be accounted for in our treatment, it is true that those three objects contribute a large fraction of the object.
+Whereas we expect the negative tail to be suppressed by our selection function, and thus it should be accounted for in our treatment.
+%, it is true that those three objects contribute a large fraction of the object.
 If one computes the median offset instead of the mean, the offset is almost completely consistent with the expected bias.
-Larger samples are needed to establish whether the positive tail is real or due to small sample statistics.
+Larger samples with different selection function are needed to establish whether the positive tail is real or due to small sample statistics.
 
@@
 
-The local sample of inactive galaxies used in this analysis is mainly comprised of bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses.
+The local sample of inactive galaxies used in this analysis is mainly comprised of bulge-dominated galaxies and the \smass\ we adopted are their bulge masses.
 That is, in previous sections, we are comparing the \mbh-\smass$_{\rm ,total}$ relations in the distant universe to the \mbh-\smass$_{\rm ,bulge}$ relations locally.
@@
 (Section~\ref{sec:result-hosts}), we expect their B/T ratios follow
-a similar distribution which can estimated using the single-\sersic\
-index \citep{Bruce2014}. With this estimation, we can infer the
+a similar distribution which can be estimated using a single-\sersic\
+index \citep{Bruce2014}. With this B/T estimation, we can infer the
 bulge stellar mass of our AGN host.
 
-Under these assumptions, we first establish the relation between the
+Under these assumptions, we first collect the relation between the
 single-\sersic\ index and B/T ratios for CANDELS inactive galaxies
 at the similar mass level, i.e \smass$\in [9.0, 11.5]$, using B/T
-measured by \citet{Dimauro2018}. Then, we calculate the average B/T
-ratio at different \sersic\ index to construct a relation for our
-use, as shown in Figure~\ref{fig:BT-n_relation}. Taking this
-relation, we estimate the B/T of our AGN sample using the \sersic\
-index as proxy and infer their \smass$_{\rm, bulge}$ from the total
-stellar mass.
-
-We can now compare this \smass$_{\rm, bulge}$ to that
-of the black hole \mbh. As expected, we find a stronger offset of
-$0.65\pm0.11$~dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
+measured by \citet{Dimauro2018}. {\bf We then adopt the Monte Carlo approach
+and take random sample of the \sersic\ index for each AGN, based on their
+inference in Table~\ref{tab:result_sersic}. In the next step, we randomly
+sample the B/T ratio based on its distribution in \citet{Dimauro2018}
+at sampling \sersic\ index. To avoid any unphysical faint bulge flux, we
+set the lower limit for B/T ratio as $0.1$. 
+To demonstrate the expected B/T ratio, we plot its averaged value at
+different \sersic\ index, as shown in Figure~\ref{fig:BT-n_relation}. 
+We list the sampling result for the \bmass\ in Table~\ref{tab:result_sersic}.
+
+In each realization, we compare the
+\smass$_{\rm, bulge}$ to that of the \mbh\ and estimate the offset and $\gamma$. 
+We take 10,000 times of realization to make sure the distribution of the
+random sampling has become stable. Note that the Monte Carlo approach would
+take the scatter into account, including the \sersic\ index
+and its relation between B/T ratio.
+}
+
+%Then, we calculate the average B/T
+%ratio at different \sersic\ index to construct a relation for our
+%use, as shown in Figure~\ref{fig:BT-n_relation}. Taking this
+%relation, we estimate the B/T of our AGN sample using the \sersic\
+%index as proxy and infer their \smass$_{\rm, bulge}$ from the total
+%stellar mass.
+%We can now compare this \smass$_{\rm, bulge}$ to that
+%of the black hole \mbh.
+As expected, we find a stronger offset of
+$0.74\pm0.12$~dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
 local relation, which corresponds to an evolutionary trend with
-$\gamma = 1.63\pm0.27$. Since selection effects are independent of B/T in
+$\gamma = 1.86\pm0.30$. Since selection effects are independent of B/T in
 our framework we can apply our a-priori estimate of the selection
-effect correction by removing 0.21~dex, leaving a significant offset
-of $0.44\pm0.11$.
+effect correction by removing $0.21$~dex, leaving a significant offset
+of $0.53\pm0.12$. {\bf We show the histogram of $\gamma$ inferred by
+the Monte Carlo approach in Figure~\ref{fig:gamma_hist}. Same as
+Figure~\ref{fig:MM-vz}, we illustrate the offset between bulge and BH
+as a function of redshift, in Figure~\ref{fig:MM_bulge-vz}.}
 
@@
 bulge-to-total ratio it is clear that there is significant evolution
-in the \mbh\ -- \smass$_{\rm , bulge}$ relation, considering the
+in the \mbh\ -- \bmass\ relation, considering the
 marginal evidence for evolution in the \mbh-\smass$_{\rm, total}$
@@
 based on optical data of a smaller sample of 11 objects in the same
-redshift range \citep[see][for similar results.]{SS13, Jah++09, Cisternas2011}
+redshift range \citep[see][for similar results]{SS13, Jah++09, Cisternas2011}.
+
+We list the inferred $\gamma$ using the different combination of sample in this section in
+Table~\ref{table:diff_sample_gam}.
 
@@
 Relation between bulge-to-total stellar mass ratio and single-\sersic\ index using CANDELS inactive galaxies with \smass$\in [9.0, 11.5]$.
-The red curve is the inferred specific relation taking the average B/T ratio at different \sersic\ index, used as proxy to infer the B/T for our AGN sample.
+The red curve is the averaged B/T ratio at different \sersic\ index.
+{\bf Note that this curve is only for demonstrating the expected B/T value at different \sersic\ index.
+In this work we adopt the Monte Carlo approach to randomly sample the B/T to account for the scatter.}
+}
+\end{figure}
+
+\begin{figure}
+\centering
+{
+\includegraphics[width=0.5\textwidth]{fig/gamma_hist.pdf}
+}
+\caption{\label{fig:gamma_hist} 
+Illustration of the $\gamma$ distribution from the $10,000$ time realization.
 }
@@
 \caption{\label{fig:MM_bulge-vz}
-Same as Figure~\ref{fig:MM-vz}, but for \mbh-\bmass\ relations.}
+Same as Figure~\ref{fig:MM-vz}, but for \mbh-\bmass\ relations.
+{\bf For intermediate sample, \citet{Cisternas2011} haven't provide any inference for the bulge; the intermediate sample is consist of 27 objects by \citet{Bennert11} and \citet{SS13}.}}
 \end{figure*}
@@
 
-In this work, we use the start-of-the-art techniques to measure the host galaxy flux separating it from that of the point source.
+In this work, we use state-of-the-art techniques to measure the host galaxy flux separating it from that of the point source.
 The fidelity of the host galaxy magnitude is high as demonstrated by the robustness with respect to the choice of PSF which is the main source of uncertainty.
 However, we introduce some uncertainty by adopting a simple stellar population template to derive the rest-frame R-band luminosity and stellar mass for the full population.
-In principle, if we had more information, we could improve on this source of uncertainty by a adopting a specific stellar population model for each.
+In principle, if we had more information, we could improve on this source of uncertainty by adopting a specific stellar population model for each target.
 However, considering that the host magnitude in the \hst/ACS band is faint (host-to-total flux ratio $< 30\%$), the individual color that we measure is insufficient to further discriminate between templates and thus we adopt a single one for simplicity and to facilitate reproduction of our work.
@@
 
-In any case, We stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates, and not by uncertainties in the photometry or stellar mass estimates.
-Thus, the choice of template is a vastly subdominant source of error.
+In any case, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates, and not by uncertainties in the photometry or stellar mass estimates.
+Thus, the choice of template is a subdominant source of error.
 A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.
@@
 Since the local correlations are used to calibrate the single epoch black hole mass estimates, one needs to be self-consistent in the choice of local anchors and calibration of black hole mass estimators.
-Unfortunately, this is a thorny issue, since not all the local correlations are mutually consistent especially when considering different galaxy properties like luminosity stellar mass and velocity dispersion.
+Unfortunately, this is a thorny issue, since not all the local correlations are mutually consistent especially when considering different galaxy properties like luminosity, stellar mass, and velocity dispersion.
 
@@
 We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset relative to our local sample.
-Note that a $+0.3$~dex difference could totally erase the $\Delta\log$\mbh\ for the high redshift sample as described in last section, if it were independent from the black hole mass calibration.
+Note that a $+0.3$~dex difference could totally erase the $\Delta\log$\mbh\ for the high redshift sample as described in the last section, if it were independent from the black hole mass calibration.
 
@@
 Near-infrared spectroscopic observations with Subaru/FMOS of the \halpha\ emission line are available that provide reliable BH masses.
-To obtain the properties of the AGN host galaxies, we performed an image decomposition using the state-of-the-art techniques on \hst/WFC3 IR data to obtain high-resolution imaging of the AGN and its host.
-This required us to collect PSF-stars across all the fields to build to a library of PSFs.
-Using the state-of-the art image modeling tool \lenstronomy, we decomposed the AGN image in 2-D plane taking each PSF in the library.
+To obtain the properties of the AGN host galaxies, we performed an image decomposition using state-of-the-art techniques on \hst/WFC3 IR data to obtain high-resolution imaging of the AGN and its host.
+This required us to collect PSF-stars across all the fields to build a library of PSFs.
+Using state-of-the-art image modeling tool \lenstronomy, we decomposed the AGN image in the 2-D plane taking each PSF in the library.
 We obtained the host properties (i.e., host flux, effective radius, \sersic\ index) using a weighted arithmetic mean based on the inference from the eight top-ranked PSFs.
@@
 However, taking into account selection bias, these correlations are
-consistent with the local universe within the 95\% confidence limits. 
+consistent with those in the local universe within the 95\% confidence limits. 
 %Therefore, for a fixed black hole mass, the host galaxy total stellar mass and luminosity could be larger than in the local universe by a factor of two, or equal to the local universe which is consistent with no evolution.
@@
 Considering the bulge component instead to be the main driver of the local correlations \citep{Bennert11, Woo++08}, we find that our high-$z$ AGN sample has significantly lower mass/luminosity bulges at fixed black hole mass than in the local universe.
-Comparing to their \mbh, we find evolution with the ratio evolving as $(1+z)^{1.63\pm0.27}$, which is significant even accounting for selection effects.
+Comparing to their \mbh, we find evolution with the ratio evolving as $(1+z)^{1.86\pm0.30}$, which is significant even when accounting for selection effects.
 We caution that the evolution of the bulge component is more uncertain than our measurement of the total galaxy components, since it is based on an estimate of the B/T ratio from the measured Sersic indices from a matched sample of inactive galaxies.
-Nevertheless, since the signal is stronger than for the integrated quantities, the measurement is more significant even in presence of larger uncertainties.
-Thus, we can conclude that the BHs 8-10~Gyrs ago reside in bulges which are less massive/luminous than today \citep[see also][]{Bennert11,Park15}, even though a proper measure of the bulge mass at high-$z$ may need to wait for the next generation ground-based 20-30m class telescopes.
-
-Given that the total-\mbh\ relation is closer to or consistent with the local relation, the inferred evolution of the bulge-\mbh\ correlations is qualitatively consistent with a scenario where the assembly of the black hole predates that of the bulge, which is completed by the transfer of stellar mass from the disk via mergers or secular processes \citep{Croton2006}.
+Nevertheless, since the signal is stronger than for the integrated quantities, the measurement is more significant even given larger uncertainties.
+Thus, we can conclude that the BHs $8-10$~Gyrs ago reside in bulges which are less massive/luminous than today \citep[see also][]{Bennert11,Park15}, even though a proper measure of the bulge mass at high-$z$ may need to wait for the next generation ground-based 20-30m class telescopes.
+
+Given that the \smass$_{\rm ,total}$-\mbh\ relation is closer to or consistent with the local relation, the inferred evolution of the \bmass-\mbh\ correlations is qualitatively consistent with a scenario where the assembly of the black hole predates that of the bulge, which is processed by the transfer of stellar mass from the disk via mergers or secular processes \citep{Croton2006}.
 The stellar mass need to build the bulge appears to be present in the disk component at high-$z$.
@@
 Of further interest, the scatter in the \mbh-\smass\ ratios at high-$z$ is similar to the local one.
-This was unexpected since the measurements of the masses of both the black holes and their hosts should have more uncertainty that local estimates.
-If true, this may indicate that cosmic averaging of initially unrelated states \citep{Peng2007} are not driving the relation between SMBHs and their host galaxies thus there is likely a connection between the two yet to be fully understood, contenders include AGN feedback or links to common gas reservoirs.
-
-Finally, the forthcoming launch of the {\it James Webb Space Telescope} ({\it JWST}) may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim$7) and thus trace the evolution of correlations at more distant universe.
+This was unexpected since the measurements of the masses of both the black holes and their hosts should have more uncertainty than local estimates.
+If true, this may indicate that cosmic averaging of initially unrelated states \citep{Peng2007} are not driving the relation between SMBHs and their host galaxies, since then a larger scatter at higher redshifts would be expected.
+Thus, there is likely a connection between the two yet to be fully understood, contenders include AGN feedback or links to common gas reservoirs.
+
+Finally, the forthcoming launch of the {\it James Webb Space Telescope} ({\it JWST}) may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim7$) and thus trace the evolution of correlations at more distant universe.
 Although, galaxies, as we know, are smaller at high-$z$ thus may remain challenging to detect under the glare of a luminous AGN.
@@
 
-\clearpage
+%\clearpage
 \section*{Acknowledgments}
@@
 
-%The authors fully appreciate the discussions with Hyewon Suh, Vardha N. Bennert, Anton M. Koekemoer, Takahiro Morishita and Peter Williams.
+The authors fully appreciate the discussions with Hyewon Suh, Takahiro Morishita and Peter Williams.
 
@@
 
-The inferred $\gamma$ here could have large systematic given the following limitations.
+The inferred $\gamma$ here could have large systematics given the following limitations.
 First, the passive evolution is based on a simplified correction; after all, we are not clear exactly how the host evolves to $z=0$.
@@
 
-\begin{deluxetable*}{ccccccc}
-\tablecolumns{7}
-\tablewidth{0pt}
-\tablecaption{Host inference of CID1174} 
-\tablehead{ 
-\colhead{PSF rank} &
-\colhead{total $\chi ^2$} & 
-\colhead{weights $w_i$} &
-\colhead{host flux (counts)} &
-\colhead{host flux ratio}&
-\colhead{\Reff (arcsec)}&
-\colhead{\sersic\ $n$}
- \\ 
-\colhead{(1)} &
-\colhead{(2)} &
-\colhead{(3)} &
-\colhead{(4)} &
-\colhead{(5)} &
-\colhead{(6)} &
-\colhead{(7)} 
-} 
-\startdata
-%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
-%\\
-1 & $8584.429$ & $1.000$ & $82.2$ & $35\%$ & $0\farcs{}345$ & $1.1$ \\
-2 & $8646.711$ & $0.920$ & $99.1$ & $42\%$ & $0\farcs{}298$ & $1.9$ \\
-3 & $8816.947$ & $0.734$ & $76.7$ & $33\%$ & $0\farcs{}365$ & $1.1$ \\
-4 & $9304.841$ & $0.383$ & $128.6$ & $55\%$ & $0\farcs{}231$ & $2.8$ \\
-5 & $9652.575$ & $0.241$ & $187.5$ & $79\%$ & $0\farcs{}116$ & $6.2$ \\
-6 & $9917.101$ & $0.170$ & $100.2$ & $42\%$ & $0\farcs{}287$ & $2.1$ \\
-7 & $10018.324$ & $0.148$ & $75.1$ & $32\%$ & $0\farcs{}365$ & $1.2$ \\
-8 & $10087.456$ & $0.135$ & $79.8$ & $34\%$ & $0\farcs{}358$ & $1.2$ \\
-\hline\\
-Weighted value & & & $97.322\pm28.336$ & $42\%\pm12\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.9\pm1.3$  \\
-\enddata
-\label{tab:weight_CID1174}
-\tablecomments{
-Column~1: Rank of the PSF from the library.
-Column~2: Total $\chi ^2$ for the corresponding PSF.
-Column~3: Weights for the inference.
-Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
-For this sample, the inflation parameter $\alpha$ calculated by Equation~\ref{eq:alpha} is 16.671.
-}
-\end{deluxetable*}
-
 \begin{deluxetable*}
@@
 
+\begin{deluxetable*}{ccccccc}
+\tablecolumns{7}
+\tablewidth{0pt}
+\tablecaption{Host inference of CID1174} 
+\tablehead{ 
+\colhead{PSF rank} &
+\colhead{total $\chi ^2$} & 
+\colhead{weights $w_i$} &
+\colhead{host flux (counts)} &
+\colhead{host flux ratio}&
+\colhead{\Reff (arcsec)}&
+\colhead{\sersic\ $n$}
+ \\ 
+\colhead{(1)} &
+\colhead{(2)} &
+\colhead{(3)} &
+\colhead{(4)} &
+\colhead{(5)} &
+\colhead{(6)} &
+\colhead{(7)} 
+} 
+\startdata
+%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
+%\\
+1 & $8584.429$ & $1.000$ & $82.2$ & $35\%$ & $0\farcs{}345$ & $1.1$ \\
+2 & $8646.711$ & $0.920$ & $99.1$ & $42\%$ & $0\farcs{}298$ & $1.9$ \\
+3 & $8816.947$ & $0.734$ & $76.7$ & $33\%$ & $0\farcs{}365$ & $1.1$ \\
+4 & $9304.841$ & $0.383$ & $128.6$ & $55\%$ & $0\farcs{}231$ & $2.8$ \\
+5 & $9652.575$ & $0.241$ & $187.5$ & $79\%$ & $0\farcs{}116$ & $6.2$ \\
+6 & $9917.101$ & $0.170$ & $100.2$ & $42\%$ & $0\farcs{}287$ & $2.1$ \\
+7 & $10018.324$ & $0.148$ & $75.1$ & $32\%$ & $0\farcs{}365$ & $1.2$ \\
+8 & $10087.456$ & $0.135$ & $79.8$ & $34\%$ & $0\farcs{}358$ & $1.2$ \\
+\hline\\
+Weighted value & & & $97.322\pm28.336$ & $42\%\pm12\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.9\pm1.3$  \\
+\enddata
+\label{tab:weight_CID1174}
+\tablecomments{
+Column~1: Rank of the PSF from the library.
+Column~2: Total $\chi ^2$ for the corresponding PSF.
+Column~3: Weights for the inference.
+Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
+For this sample, the inflation parameter $\alpha$ calculated by Equation~\ref{eq:alpha} is 16.671.
+}
+\end{deluxetable*}
+
 \tabcolsep=0.03cm
@@
 \startdata 
-CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.05\substack{+0.15\\-0.11}$ &$10.78\substack{+0.18\\-0.15}$ & $10.45\substack{+0.18\\-0.15}$ \\[3pt]
-CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.41\substack{+0.15\\-0.11}$ &$10.14\substack{+0.18\\-0.15}$ & $9.99\substack{+0.18\\-0.15}$ \\[3pt]
-CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.86\substack{+0.52\\-0.23}$ &$10.59\substack{+0.53\\-0.25}$ & $10.43\substack{+0.53\\-0.25}$ \\[3pt]
-CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.05\substack{+0.03\\-0.03}$ &$10.78\substack{+0.10\\-0.10}$ & $10.64\substack{+0.10\\-0.10}$ \\[3pt]
-CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.18\substack{+0.11\\-0.09}$ &$10.91\substack{+0.14\\-0.13}$ & $10.77\substack{+0.14\\-0.13}$ \\[3pt]
-CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.08\substack{+0.15\\-0.11}$ &$10.81\substack{+0.18\\-0.15}$ & $10.69\substack{+0.18\\-0.15}$ \\[3pt]
-CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.16\substack{+0.14\\-0.11}$ &$10.89\substack{+0.17\\-0.15}$ & $10.75\substack{+0.17\\-0.15}$ \\[3pt]
-CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $10.98\substack{+0.02\\-0.02}$ &$10.71\substack{+0.10\\-0.10}$ & $10.02\substack{+0.10\\-0.10}$ \\[3pt]
-CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.13\substack{+0.03\\-0.03}$ &$10.86\substack{+0.10\\-0.10}$ & $10.25\substack{+0.10\\-0.10}$ \\[3pt]
-CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.11\substack{+0.04\\-0.04}$ &$10.84\substack{+0.10\\-0.10}$ & $10.21\substack{+0.10\\-0.10}$ \\[3pt]
-CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.07\substack{+0.35\\-0.19}$ &$10.80\substack{+0.36\\-0.21}$ & $10.65\substack{+0.36\\-0.21}$ \\[3pt]
-CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.70\substack{+0.16\\-0.12}$ &$10.43\substack{+0.19\\-0.15}$ & $9.73\substack{+0.19\\-0.15}$ \\[3pt]
-CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.73\substack{+0.22\\-0.15}$ &$10.46\substack{+0.24\\-0.18}$ & $10.12\substack{+0.24\\-0.18}$ \\[3pt]
-CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.02\substack{+0.23\\-0.15}$ &$10.75\substack{+0.25\\-0.18}$ & $10.59\substack{+0.25\\-0.18}$ \\[3pt]
-CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $10.98\substack{+0.12\\-0.10}$ &$10.72\substack{+0.16\\-0.14}$ & $10.58\substack{+0.16\\-0.14}$ \\[3pt]
-LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.32\substack{+0.09\\-0.07}$ &$11.05\substack{+0.13\\-0.12}$ & $10.46\substack{+0.13\\-0.12}$ \\[3pt]
-LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.12\substack{+0.09\\-0.08}$ &$10.86\substack{+0.13\\-0.12}$ & $10.69\substack{+0.13\\-0.12}$ \\[3pt]
-LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.08\substack{+0.06\\-0.05}$ &$10.81\substack{+0.11\\-0.11}$ & $10.08\substack{+0.11\\-0.11}$ \\[3pt]
-XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.89\substack{+0.07\\-0.06}$ &$10.63\substack{+0.12\\-0.12}$ & $10.04\substack{+0.12\\-0.12}$ \\[3pt]
-XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.15\substack{+0.12\\-0.10}$ &$10.88\substack{+0.16\\-0.14}$ & $10.76\substack{+0.16\\-0.14}$ \\[3pt]
-XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.12\substack{+0.26\\-0.16}$ &$10.85\substack{+0.28\\-0.19}$ & $10.10\substack{+0.28\\-0.19}$ \\[3pt]
+CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.05\substack{+0.15\\-0.11}$ &$10.78\substack{+0.18\\-0.15}$ & $10.36\substack{+0.41\\-0.54}$ \\[3pt]
+CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.41\substack{+0.15\\-0.11}$ &$10.14\substack{+0.18\\-0.15}$ & $9.91\substack{+0.28\\-0.50}$ \\[3pt]
+CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.86\substack{+0.52\\-0.23}$ &$10.59\substack{+0.53\\-0.25}$ & $10.27\substack{+0.54\\-0.61}$ \\[3pt]
+CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.05\substack{+0.03\\-0.03}$ &$10.78\substack{+0.10\\-0.10}$ & $10.66\substack{+0.15\\-0.25}$ \\[3pt]
+CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.18\substack{+0.11\\-0.09}$ &$10.91\substack{+0.14\\-0.13}$ & $10.77\substack{+0.20\\-0.34}$ \\[3pt]
+CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.08\substack{+0.15\\-0.11}$ &$10.81\substack{+0.18\\-0.15}$ & $10.65\substack{+0.23\\-0.36}$ \\[3pt]
+CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.16\substack{+0.14\\-0.11}$ &$10.89\substack{+0.17\\-0.15}$ & $10.76\substack{+0.21\\-0.28}$ \\[3pt]
+CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $10.98\substack{+0.02\\-0.02}$ &$10.71\substack{+0.10\\-0.10}$ & $9.78\substack{+0.68\\-0.13}$ \\[3pt]
+CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.13\substack{+0.03\\-0.03}$ &$10.86\substack{+0.10\\-0.10}$ & $10.14\substack{+0.48\\-0.30}$ \\[3pt]
+CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.11\substack{+0.04\\-0.04}$ &$10.84\substack{+0.10\\-0.10}$ & $9.91\substack{+0.74\\-0.14}$ \\[3pt]
+CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.07\substack{+0.35\\-0.19}$ &$10.80\substack{+0.36\\-0.21}$ & $10.51\substack{+0.4\\-0.57}$ \\[3pt]
+CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.70\substack{+0.16\\-0.12}$ &$10.43\substack{+0.19\\-0.15}$ & $9.55\substack{+0.63\\-0.23}$ \\[3pt]
+CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.73\substack{+0.22\\-0.15}$ &$10.46\substack{+0.24\\-0.18}$ & $9.97\substack{+0.44\\-0.49}$ \\[3pt]
+CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.02\substack{+0.23\\-0.15}$ &$10.75\substack{+0.25\\-0.18}$ & $10.55\substack{+0.29\\-0.40}$ \\[3pt]
+CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $10.98\substack{+0.12\\-0.10}$ &$10.72\substack{+0.16\\-0.14}$ & $10.54\substack{+0.22\\-0.36}$ \\[3pt]
+LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.32\substack{+0.09\\-0.07}$ &$11.05\substack{+0.13\\-0.12}$ & $10.29\substack{+0.58\\-0.28}$ \\[3pt]
+LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.12\substack{+0.09\\-0.08}$ &$10.86\substack{+0.13\\-0.12}$ & $10.66\substack{+0.23\\-0.38}$ \\[3pt]
+LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.08\substack{+0.06\\-0.05}$ &$10.81\substack{+0.11\\-0.11}$ & $9.91\substack{+0.67\\-0.16}$ \\[3pt]
+XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.89\substack{+0.07\\-0.06}$ &$10.63\substack{+0.12\\-0.12}$ & $9.85\substack{+0.57\\-0.27}$ \\[3pt]
+XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.15\substack{+0.12\\-0.10}$ &$10.88\substack{+0.16\\-0.14}$ & $10.73\substack{+0.21\\-0.32}$ \\[3pt]
+XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.12\substack{+0.26\\-0.16}$ &$10.85\substack{+0.28\\-0.19}$ & $10.15\substack{+0.59\\-0.41}$ \\[3pt]
 CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ...
@@
 & ...
-& $10.71\substack{+0.16\\-0.12}$ &$10.45\substack{+0.19\\-0.15}$ & $10.3\substack{+0.19\\-0.15}$ \\[3pt]
+& $10.71\substack{+0.16\\-0.12}$ &$10.45\substack{+0.19\\-0.15}$ & $10.30\substack{+0.22\\-0.30}$ \\[3pt]
 CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ...
@@
 & ...
-& $10.90\substack{+0.06\\-0.05}$ &$10.63\substack{+0.12\\-0.11}$ & $9.90\substack{+0.12\\-0.11}$ \\[3pt]
+& $10.90\substack{+0.06\\-0.05}$ &$10.63\substack{+0.12\\-0.11}$ & $9.70\substack{+0.69\\-0.16}$ \\[3pt]
 CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ...
@@
 & ...
-& $11.52\substack{+0.28\\-0.17}$ &$11.25\substack{+0.30\\-0.20}$ & $11.03\substack{+0.30\\-0.20}$ \\[3pt]
+& $11.52\substack{+0.28\\-0.17}$ &$11.25\substack{+0.30\\-0.20}$ & $10.88\substack{+0.42\\-0.58}$ \\[3pt]
 CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ...
@@
 & ...
-& $10.06\substack{+0.23\\-0.15}$ &$9.79\substack{+0.25\\-0.18}$ & $9.39\substack{+0.25\\-0.18}$ \\[3pt]
+& $10.06\substack{+0.23\\-0.15}$ &$9.79\substack{+0.25\\-0.18}$ & $9.27\substack{+0.48\\-0.51}$ \\[3pt]
 ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ...
@@
 & ...
-& $11.16\substack{+0.12\\-0.10}$ &$10.89\substack{+0.16\\-0.14}$ & $10.53\substack{+0.16\\-0.14}$ \\[3pt]
+& $11.16\substack{+0.12\\-0.10}$ &$10.89\substack{+0.16\\-0.14}$ & $10.37\substack{+0.44\\-0.46}$ \\[3pt]
 SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ...
@@
 & ...
-& $10.75\substack{+0.09\\-0.08}$ &$10.49\substack{+0.14\\-0.13}$ & $10.16\substack{+0.14\\-0.13}$ \\[3pt]
+& $10.75\substack{+0.09\\-0.08}$ &$10.49\substack{+0.14\\-0.13}$ & $10.11\substack{+0.35\\-0.50}$ \\[3pt]
 SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ...
@@
 & ...
-& $10.80\substack{+0.11\\-0.09}$ &$10.54\substack{+0.15\\-0.13}$ & $10.15\substack{+0.15\\-0.13}$ \\[3pt]
+& $10.80\substack{+0.11\\-0.09}$ &$10.54\substack{+0.15\\-0.13}$ & $10.02\substack{+0.44\\-0.46}$ \\[3pt]
 SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ...
@@
 & ...
-& $10.77\substack{+0.07\\-0.06}$ &$10.51\substack{+0.12\\-0.12}$ & $10.34\substack{+0.12\\-0.12}$ \\[3pt]
+& $10.77\substack{+0.07\\-0.06}$ &$10.51\substack{+0.12\\-0.12}$ & $10.38\substack{+0.17\\-0.28}$ \\[3pt]
 SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ...
@@
 & ...
-& $11.19\substack{+0.13\\-0.10}$ &$10.92\substack{+0.17\\-0.14}$ & $10.62\substack{+0.17\\-0.14}$ \\[3pt]
+& $11.19\substack{+0.13\\-0.10}$ &$10.92\substack{+0.17\\-0.14}$ & $10.54\substack{+0.38\\-0.55}$ \\[3pt]
 SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ...
@@
 & ...
-& $9.95\substack{+0.47\\-0.22}$ &$9.68\substack{+0.48\\-0.24}$ & $9.48\substack{+0.48\\-0.24}$ \\[3pt]
+& $9.95\substack{+0.47\\-0.22}$ &$9.68\substack{+0.48\\-0.24}$ & $9.36\substack{+0.48\\-0.54}$ \\[3pt]
 SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ...
@@
 & ...
-& $11.03\substack{+0.21\\-0.14}$ &$10.76\substack{+0.23\\-0.17}$ & $10.47\substack{+0.23\\-0.17}$ \\[3pt]\enddata
+& $11.03\substack{+0.21\\-0.14}$ &$10.76\substack{+0.23\\-0.17}$ & $10.37\substack{+0.40\\-0.53}$ \\[3pt]
+\enddata
 \label{tab:result_sersic}
@@
 \end{deluxetable*}
-
-\begin{table}
-\centering
-    \caption{The inference of $\gamma$ using \mbh-\smass\ by different sample combination.}\label{table:diff_sample_gam}
-     \resizebox{5.5cm}{!}{
-     \begin{tabular}{cc}
-     \hline
-     Sample combination & $\gamma$ \\
-     &\\
-     \hline\hline
-32 AGNs & 0.78$\pm$0.26\\    
-30 AGNs (excluded outliers) & 0.65$\pm$0.27\\    
-32 AGNs + intermediate &  0.58$\pm$0.20\\
-32 AGNs bulge only & 1.63$\pm$0.27\\
-     \hline
-     \end{tabular}}
-\tablecomments{These values are directly inference for the observation, which haven't yet taken the selection effect into account.}
-\end{table}
 
@@
 
+\begin{table}
+\centering
+    \caption{The inference of $\gamma$ for \mbh-\smass\ by different sample combination.}\label{table:diff_sample_gam}
+     \resizebox{5.5cm}{!}{
+     \begin{tabular}{cc}
+     \hline
+     Sample combination & $\gamma$ \\
+     &\\
+     \hline\hline
+32 AGNs & 0.78$\pm$0.26\\    
+30 AGNs (excluded outliers) & 0.65$\pm$0.27\\    
+32 AGNs + intermediate &  0.58$\pm$0.20\\
+32 AGNs bulge only & 1.86$\pm$0.30\\
+     \hline
+     \end{tabular}}
+\tablecomments{These values are directly inference for the observation, which haven't yet taken the selection effect into account.}
+\end{table}
+
 \end{document}

### 2019-07-29 M_BH_relation/read_bulge_MC_result.py

@@ -1,0 +1,228 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Jul 25 23:06:35 2019
+
+@author: Dartoon
+
+Read the inference from gamma
+"""
+import numpy as np
+np.set_printoptions(precision=4)
+import matplotlib.pyplot as plt
+import matplotlib as mat
+mat.rcParams['font.family'] = 'STIXGeneral'
+import matplotlib.lines as mlines
+from matplotlib import colors
+import pickle
+
+gamma,Mstar_samp = pickle.load(open('gamma_Mbulge_result_(BT_min_0.1)_part2.pkl','rb'))
+Mstar_samp = np.asarray(Mstar_samp)
+hist_value = gamma #Mstar_samp[:,1]
+plt.figure(figsize=(10,8))
+l =np.percentile(hist_value,16,axis=0)
+m =np.percentile(hist_value,50,axis=0)
+h =np.percentile(hist_value,84,axis=0)
+yl = np.linspace(0,4,100)
+x_l = yl*0+ l
+x_m = yl*0 + m
+x_h = yl*0 + h
+plt.plot(x_l, yl, 'k--',linewidth=4.0)
+plt.plot(x_m, yl, 'blue',linewidth=4.0)
+plt.plot(x_h, yl, 'k--',linewidth=4.0)
+plt.axis([m-4*(m-l),m+(h-m)*4,0,1.5])
+plt.hist(hist_value,bins=30, normed=True)
+plt.xlabel('$\gamma$',fontsize=35)
+plt.ylabel('PDF',fontsize=35)
+plt.tick_params(labelsize=25)
+plt.yticks([])
+#plt.savefig("gamma_hist.pdf")
+plt.show()
+
+#%%
+ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'CDFS-321', 'CID1174',\
+'CID216', 'CID237','CID3242','CID3570','CID452', 'CID454',\
+'CID50','CID607','LID1273', 'LID1538','LID360','SXDS-X1136',\
+'SXDS-X50', 'SXDS-X717','SXDS-X763','SXDS-X969','XID2138','XID2202',\
+'XID2396', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597','CID1281','CID255']
+
[…]

### 2019-07-29 analysis_ACS/Comparsion_Re_to_WFC3.py

@@ -1,0 +1,86 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jul 22 17:10:00 2019
+
+@author: Dartoon
+
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import re
+import matplotlib
+from adjustText import adjust_text   # avoid the overlapping while ploting
+import sys
+sys.path.insert(0,'../py_tools')
+from filter_info import redshift_info
+
+ID = ['CID1174','CID216', 'CID50','CID70','XID2138','CID3242',\
+'LID1273','XID2202','CID206','CID543','LID1538','XID2396','CID452',\
+'LID360','CID237','CID454','CID607','CID3570', 'CID1281', 'CID597', 'CID255']
+
+#CID1281, CID255, CID526, CID597 is not in our targets
+
+import pickle
+
+Re_results= []
+flux_dict, FWHM_dict, locs_dict, filter_dict, id_stars_dict=pickle.load(open('PSFs_lib_dict','rb'))
+folder = "fit_result_each" #"fit_result_each_fix" or "fit_result_each"
+
+from load_result import load_re
+WFC3_re = np.array(load_re(ID, folder = '../', flt='WFC3'))
+
+
+for j in range(len(ID)):
+    f = open("{0}/first_analysis/{1}/each_PSF_fit_qso.txt".format(ID[j],folder),"r")
+    string = f.read()
+    PSF_id = re.findall(r"by PSF(.*?):",string)
+    Re = re.findall(r"R_sersic':(.*?),",string)
+    Chisq = re.findall(r"redu_Chisq':(.*?),",string)
+    
+    Re = [float(i) for i in Re]
+    Chisq = [float(i) for i in Chisq]
+    
+#    PSFs_dict = {}
+#    for key in filt_info.keys():
+#        if filt_info[key] == filt:
+#            PSFs, _=pickle.load(open('{0}/{0}_PSFs_QSO'.format(key),'rb'))
+#            PSFs_dict.update({'{0}'.format(key):PSFs})
+    
+    sort_Chisq = np.argsort(np.asarray(Chisq))
+    count_n = 8
+    Chisq_best = Chisq[sort_Chisq[0]]
+    Chisq_last= Chisq[sort_Chisq[count_n-1]]
+    inf_alp = (Chisq_last-Chisq_best) / (2*2.* Chisq_best)
[…]

### 2019-07-29 analysis_Astrodrz/compare_K-correction.py

@@ -160,7 +160,7 @@ mag_k_corrected_UV=mags_obs_UV-5*(np.log10(dl)-1) + dm_k_UV
 #    print ID[i], mag_k_corrected_IR[i], mag_k_corrected_UV[i]
 #if needed lumi_s = 0.4*(4.61-mag_k_corrected)
 
-plt.figure(figsize=(9, 9))
+plt.figure(figsize=(10, 10))
 plt.errorbar(mag_k_corrected_IR, mag_k_corrected_UV,xerr= mag_IR_err.T, yerr=mag_UV_err.T,color='red', fmt='o',ecolor='gray' )
 #texts = []
 #for i in range(len(ID)):
@@ -168,10 +168,10 @@ plt.errorbar(mag_k_corrected_IR, mag_k_corrected_UV,xerr= mag_IR_err.T, yerr=mag
 #adjust_text(texts, arrowprops=dict(arrowstyle='->', color='red'))
 x=np.linspace(-26,-20,15)
 y = x
-plt.plot(x,y,'b')
+plt.plot(x,y,'b',linewidth=4.0,alpha=0.5)
 #plt.title('Galaxy age: '+galay_temp, fontsize=24)
-plt.xlabel('Absolute rest-frame R mag by WFC3',fontsize=21)
-plt.ylabel('Absolute rest-frame R mag by ACS', fontsize=21)
+plt.xlabel('Absolute rest-frame R mag by WFC3',fontsize=30)
+plt.ylabel('Absolute rest-frame R mag by ACS', fontsize=30)
 val_min, val_max = np.min([mag_k_corrected_UV, mag_k_corrected_IR]), np.max([mag_k_corrected_UV, mag_k_corrected_IR])
 plt.xlim(val_min-0.5, val_max+0.5)
 plt.ylim(val_min-0.5, val_max+0.5)
@@ -204,9 +204,9 @@ for i in range(len(ID)):
         plt.plot(zs[i], mags_obs_UV[i] - mags_obs_IR[i], 'ko')
     texts.append(plt.text(zs[i], mags_obs_UV[i] - mags_obs_IR[i], ID[i], fontsize=17))
 adjust_text(texts, arrowprops=dict(arrowstyle='->', color='green'))  
-plt.xlabel('redshift',fontsize=25)
-plt.ylabel('Observed Color', fontsize=25)
-plt.tick_params(labelsize=15)    
+plt.xlabel('redshift',fontsize=35)
[…]

### 2019-07-29 material/list_for_John_paper.py

@@ -1,0 +1,89 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Jul 24 13:45:03 2019
+
+@author: Dartoon
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import sys
+sys.path.insert(0,'../py_tools')
+
+from load_result import load_host_p, load_MBH, load_err, load_re, load_zs
+
+ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'CDFS-321', 'CID1174',\
+'CID216', 'CID237','CID3242','CID3570','CID452', 'CID454',\
+'CID50','CID607','LID1273', 'LID1538','LID360','SXDS-X1136',\
+'SXDS-X50', 'SXDS-X717','SXDS-X763','SXDS-X969','XID2138','XID2202',\
+'XID2396', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597','CID1281','CID255']
+MB_ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'ECDFS-321', 'CID1174',\
+'CID216', 'CID237','CID3242','CID3570','CID452', 'CID454',\
+'CID50','CID607','LID1273', 'LID1538','LID360','SXDS-X1136',\
+'SXDS-X50', 'SXDS-X717','SXDS-X763','SXDS-X969','LID1820','LID1622',\
+'LID1878', 'CID206', 'ECDFS-358', 'CDFS-724', 'CID597','CID1281','CID255']
+
+MBs = load_MBH(ID,MB_ID,if_reportHb=0)
+Mstar = load_host_p(ID)[1]
+Mstar_err = load_err(prop = 'Mstar', ID=ID)
+zs = np.asarray(load_zs(ID))
+
+Reffs = np.array(load_re(ID))
+
+tab_list = ['CID1174', 'CID1281', 'CID206', 'CID216', 'CID237', 'CID255', 'CID3242', 'CID3570',
+            'CID452', 'CID454', 'CID50', 'CID543', 'CID597', 'CID607', 'CID70', 'LID1273',
+            'LID1538', 'LID360', 'XID2138', 'XID2202', 'XID2396', 'CDFS-1', 'CDFS-229',
[…]

### 2019-07-30 manuscript/manuscript.tex
Add Tommaso's comments

@@
 Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
-{\bf The inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus their scatters are zero.
-This means the size inference of these three systems could be biased.
+{\bf The inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero.
+This means the size inference of these three systems should really be considered an upper limit, rather than a measurement.
 However, the inference of their host luminosities and stellar masses are still reliable given the small scatter in the host flux ($<10\%$).}
@@
 
-\begin{figure}
-\centering
-{\includegraphics[width=0.4\textwidth]{fig/comp_gtemp_1Gyrs.pdf}}
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+{\includegraphics[height=0.4\textwidth]{fig/comp_gtemp_1Gyrs.pdf}}&
+{\includegraphics[height=0.4\textwidth]{fig/colorVSz.pdf}}\\
+\end{tabular}
 \caption{\label{fig:compare_temp} 
-Comparison of the inferred rest-frame R band magnitude based on the adopted stellar population, using $21/32$ AGNs which have both WFC3 and ACS imaging data.
-}
-\end{figure}
+ {\it Left}: Comparison of the inferred rest-frame R band magnitude based on the adopted stellar population, using $21/32$ AGNs which have both WFC3 and ACS imaging data.
+{\it Right}: The observed color as a function of redshift.
+Note that the filter WFC3/F125W and WFC3/F140W are adopted for sample at $z<1.44$ and $z>1.44$, respectively.
+The blue curve is the predicted model by the $1$~Gyr stellar population.
+As comparison, we plot the predicted model by the $5$~Gyr stellar population.
+}
+\end{figure*}
 
@@
 \caption{\label{fig:MM-vz} 
-Left: Offset in  $\log($\mbh$)$ (vs.
+ {\it Left}: Offset in  $\log($\mbh$)$ (vs.
 \smass) as a function of redshift.
@@
 The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, with slope value $\gamma  = 0.78 \pm 0.26$.
-Right: \mbh/\smass\ as a function of redshift. 
+ {\it Right}: \mbh/\smass\ as a function of redshift. 
 We use green open circles to show the expected shifting of the median value of the $\Delta \log$\mbh\ before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.}
@@
 We also show, in Figure~\ref{fig:offset_hist}, the histogram $\Delta \log$\mbh\ by the high-$z$ sample and compare to the local ones.
-The plots show that the correlations between \mbh\ and host galaxy total stellar mass or luminosity could be consistent with those of the local samples given the uncertainties and selection function
+The plots show that the correlations between \mbh\ and host galaxy total stellar mass or luminosity could be consistent with those of the local samples given the uncertainties and selection function.
 

### 2019-07-31 manuscript/manuscript.tex
Before move to new Mac

@@
 The orange band is the intrinsic scatter of local linear relation.
-The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, with slope value $\gamma  = 0.78 \pm 0.26$.
+The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, with slope value $\gamma  = 0.78 \pm 0.26$.\\
  {\it Right}: \mbh/\smass\ as a function of redshift. 
@@
 effect correction by removing $0.21$~dex, leaving a significant offset
-of $0.53\pm0.12$. {\bf We show the histogram of $\gamma$ inferred by
+of $0.53\pm0.12$. {\bf We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
 the Monte Carlo approach in Figure~\ref{fig:gamma_hist}. Same as
@@
 
-\begin{figure}
-\centering
-{
-\includegraphics[width=0.5\textwidth]{fig/gamma_hist.pdf}
-}
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+{\includegraphics[height=0.39\textwidth]{fig/realizations_M_BH_M_star.pdf}}&
+{\includegraphics[height=0.39\textwidth]{fig/gamma_hist.pdf}}\\
+\end{tabular}
 \caption{\label{fig:gamma_hist} 
-Illustration of the $\gamma$ distribution from the $10,000$ time realization.
-}
-\end{figure}
+Illustration of the distribution from the $10,000$ time realization. {\it Left}: \mbh/\smass\ distribution for 32 high-$z$ sample, compared to the local one. {\it Right}: $\gamma$ distribution.
+}
+\end{figure*}
 

### 2019-07-31 Comparsion/CANDELS_catalog/compare_with_CANDLESCOSMOS_color.py

@@ -197,7 +197,7 @@ cl.ax.tick_params(labelsize=30)
 
 
 if relation == 0:
-    f1 ='../../M_BH_relation/data//Bennert+2011_local.txt'
+    f1 ='../../M_BH_relation/data/Bennert+2011_local.txt'
     b11_l = np.loadtxt(f1)[:,1:]  #0 redshift; 1 M*; 2 BH mass;
     b11_local_Reff = b11_l[:,-1]
     b11_local_mstar = b11_l[:,4]

### 2019-07-31 M_BH_relation/read_bulge_MC_result.py

@@ -179,14 +179,15 @@ if style ==1:
 #    #print "lnlike=",lnlike(theta=[b_ml_offset, sint_mid],x=x, y=y, yerr=yerr)
 #    xl = np.linspace(0, 5, 100)
 #    b=np.percentile(samples,50,axis=0)[0]
-#    yerr_highz = [(Mstar_err[:,0]**2+0.4**2)**0.5, (Mstar_err[:,1]**2+0.4**2)**0.5]
 #    #print samples[:,1][samples[:,0]==find_n(samples[:,0],m)]
+#    plt.plot(xl, xl*0+xl*b_ml_offset, color="red", linewidth=4.0,zorder=0)
     
+    yerr_highz = [(Mstar_err[:,0]**2+0.4**2)**0.5, (Mstar_err[:,1]**2+0.4**2)**0.5]
     for i in range(100):
         posi=np.random.uniform(16,84)
         b=np.percentile(samples,posi,axis=0)#[0]
         plt.plot(xl, xl*0+xl*b, color="lightgray", alpha=0.2,linewidth=7.0,zorder=-1)
-    plt.plot(xl, xl*0+xl*b_ml_offset, color="red", linewidth=4.0,zorder=0)
+    plt.plot(xl, xl*0+xl*np.percentile(gamma,50,axis=0), color="red", linewidth=4.0,zorder=0)        
     plt.plot(xl, xl*0, color="black", linewidth=2.0,zorder=0)
     plt.scatter(np.log10(1+zs),MBs-(m_ml*Mstar+b_ml),c='tomato',
                 s=580,marker="*",zorder=300, vmin=0.3, vmax=5, edgecolors='k')
@@ -224,5 +225,48 @@ plt.legend([Bkc, Hkc, SS13, new_sample],[
 ],scatterpoints=1,numpoints=1,loc=2,prop={'size':28},ncol=2,handletextpad=0)
 #plt.savefig("MBH-Mbulge-style{0}.pdf".format(style))
 plt.show()
+
+#%% Plot Figure12-b:
+#The histogram of the M_BH/M_star.
+high_ratio = []
+fig = plt.figure(figsize=(12,9))
+ax = fig.add_subplot(111)
+for i in range(len(Mstar_samp)):
+    high_ratio.append(10**(MBs-Mstar_samp[i,:])) 
+dis0 = np.asarray(high_ratio)
+dis0 = dis0.flatten()
[…]

### 2019-08-02 manuscript/manuscript.tex
FInish before sharing to John

@@
 \altaffiltext{7}{Physics Department, California Polytechnic State University, San Luis Obispo CA 93407, USA}
-\altaffiltext{8}{School of Physics and Astronomy, Rochester Institute of Technology, Rochester, NY 14623, USA}
+\altaffiltext{8}{School of Physics and Astronomy, Rochester Institute of Technology, 84 Lomb Memorial Drive, Rochester, NY 14623, USA}
 \altaffiltext{9}{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
@@
 
-Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g.
-stellar mass \smass, luminosity \lhost) suggest an evolutionary connection.
+Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., stellar mass \smass, luminosity \lhost) suggest an evolutionary connection.
 A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates.
 For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
-By applying state-of-the-art tools to decompose the \hst\ image, we measured the host galaxy luminosity and stellar mass along with other properties through 2D model fitting.
+By applying state-of-the-art tools to decompose the \hst\ image, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting.
 The black hole mass (\mbh) is determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators.
@@
 
-Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass) and stellar velocity dispersion (\sigstar).
+Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass), and stellar velocity dispersion (\sigstar).
 The tightness of these correlations (also known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
@@
 On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering either the active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or how the growth of these components is connected to the common gas supply~\citep{Cen2015, Menci2016}.
-On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, the statistical convergence from galaxy assembly alone (i.e., mergers) can reproduce the observed correlations.
+On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, the statistical convergence from galaxy assembly alone (i.e., mergers) can reproduce the observed correlations.
 
@@
 For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today.
-Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass\ and \mbh-\sigstar\ relations, especially when the data are sufficiently good to isolate the luminosity or stellar mass of the bulge or spheroidal component.
+Similarly, studying the observation of the \mbh-\smass\ and \mbh-\sigstar\ relations, the works by \citet{Bennert11, Woo++08} find a positive evolution of \mbh, especially when the data are sufficiently robust to isolate the luminosity or stellar mass of the bulge or spheroidal component.
 Of similar results, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies; although, the accuracy of such an approach for luminous AGNs has not yet been well established.
@@
 However, there are studies \citep{Cisternas2011,SS13,Mechtley2016} based on \hst\  imaging of deep survey fields such as COSMOS and CDFS that report no evolution in the \mbh - \smass ~ mass ratio as compared to the local relation.
-In support, \citet{Sun2015} has re-analyzed the mass ratios for broad-line AGNs in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citet{Merloni2010} and finds no evolution when accounting for selection effects, as fully described in \citet{Schulze2014} that consider the black hole mass functions and Eddington rate distribution.
+In support, \citet{Sun2015} has re-analyzed the mass ratios for broad-line AGNs in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citet{Merloni2010} and finds no evolution when accounting for selection effects, as fully described in \citet{Schulze2014} who consider the black hole mass functions and Eddington rate distribution.
 
@@
 First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method.
-In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-gravitational component of the broad-line region (BLR) gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e.
-\halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}.
+In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as a non-gravitational component of the broad-line region (BLR) gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e., \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}.
 Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging.
@@
 Last but not least, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}.
-For instance, it has been demonstrated~\citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample.
+For instance, it has been demonstrated~\citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results would display \mbh - \smass\ with a steeper slope than random ones, suggesting the selection effects can exhibit faster evolution than a random sample.
 It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.
@@
 In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to the highest redshifts where evolutionary effects should be strongest.
-In particular, samples based on 2D image analysis using \hst\ at $z>1$ are limited thus the infrared capabilities of \hst/WFC3 have not been fully exploited to date on this topic.
+In particular, samples based on 2D image analysis using \hst\ at $z>1$ are limited.
+To date, the infrared capabilities of \hst/WFC3 have not been fully exploited on this topic.
 Here, we measure the properties of 32 host galaxies within a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS.
-Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e.
-$\sim0.23$ dex,][]{Schulze2014}.
+Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e., $\sim0.23$ dex,][]{Schulze2014}.
 
@@
 We describe the observations and construction of a PSF library in Section~\ref{observation}.
-In Section~\ref{sec:analysis} we decompose our sample and study the host galaxy surface photometry.
-In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population for which we apply to derive the rest-frame R-band \lhost\,~and \smass\ to compare with local relations.
-In addition, we use the information on the radial light distribution (i.e., Sersic index) to infer the likely fraction of stars in the bulge (\bmass) and its relation to the \mbh.
+In Section~\ref{sec:analysis}, we decompose our sample and study the host galaxy surface photometry.
+In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population from which we apply to derive the rest-frame R-band \lhost\,~and \smass\ to compare with local relations.
+In addition, we use the information on the radial light distribution (i.e., \sersic\ index) to infer the likely fraction of stars in the bulge (\bmass) and its relation to the \mbh.
 The discussion and conclusions are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}.
@@
 Third, our X-ray selected sample has lower nuclear-to-host ratios which facilitate the galaxy mass measurements.
-Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e.
-WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference.
+Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e., WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference.
 
 We utilize a sample size of 32 broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that have black hole mass measurements available and fall within deep extragalactic survey fields that offer rich ancillary data.
-Specifically, we focused on meeting the following criteria to overcome limitations of previous studies:
+Specifically, we focused on meeting the following criteria to overcome the limitations of previous studies:
 
@@
 \item The lower nuclear-to-host ratios of our sample facilitates the galaxy mass measurements, given that they are 
-X-ray selected. This is somewhat coupled to the second item in this list.
-
-\item \hst/WFC3 imaging of the host galaxy is above the 4000~\angstrom\ break and does not include the broad \halpha\ line (6563~\angstrom). This ensures sensitivity to the total stellar mass content.
+X-ray selected.
+
+\item \hst/WFC3 imaging of the host galaxy is above the 4000~\angstrom\ break and does not include the broad \halpha\ line (6563~\angstrom).
+This ensures sensitivity to the total stellar mass content.
+This is somewhat coupled to the previous item in this list.
 
@@
 The 32 AGNs are initially selected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
-In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck and Magellan.
+In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan.
 Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh.
@@
 We refer the reader to that paper for the details of continuum fitting and emission-line modeling.
-Note that three CDFS objects (i.e.
-CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015}.
-
-Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$~(M$_{\odot}$).
-The bolometric luminosities are measured from AGN broad lines by \citet[][Section 3.3]{Schulze2018} which are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
-The flux-limited nature of the sample results in higher Eddington ratios when \mbh\ is lower as shown in Figure~\ref{fig:selection}.
-Moreover, we have higher preference to select targets which have rest-frame UV images as provided by \citet{Scoville2007} and \citet{Koekemoer2007} in the COSMOS field and REFS for the (E)-CDF-S.
+Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015}.
+
+Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~(\mbh/$M_{\odot})\lesssim8.5$.
+The bolometric luminosities are measured from AGN broad lines by \citet[][Section 3.3]{Schulze2018}, which are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
+The flux-limited nature of the sample results in higher Eddington ratios when \mbh\ is lower, as shown in Figure~\ref{fig:selection}.
+Moreover, we have a higher preference to select targets which have rest-frame UV images (i.e., \hst/ACS) as provided by \citet{Scoville2007} and \citet{Koekemoer2007} in the COSMOS field.
 We list the 32 AGNs observed with \hst/WFC3 and analyzed in this work in Table~\ref{tab:objlist} sorted by field and redshift.
@@
 However, there is a $\sim~0.2$~dex inconsistency in their \halpha\ estimators.
-Thus, we utilize the AGNs in \citet{Schulze2018} that have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to determine which \halpha\ estimator has been agreement between the two lines.
+Thus, we utilize the AGNs in \citet{Schulze2018} that have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to determine which \halpha\ estimator has the best agreement between the two lines.
 As a  result, the \halpha\ estimator in \citet{Schulze2018} has better agreement with \hbeta.
-Thus, we adopt the scheme given in \citet{Schulze2018} for all AGN samples used in this study including the comparison samples described below.
+Thus, we adopt the scheme given in \citet{Schulze2018} for all AGN samples used in this study, including the comparison samples described below.
 
@@
 While fourteen AGNs have emission line properties for both \halpha\ and \hbeta, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample.
-It is worth noting that the absolute flux calibration of the FMOS spectra is set to match ground-based IR imaging, ULTRAVISTA in the case of COSMOS thus amounting to an effective aperture correction.
-While most recipes are calibrated against \hbeta\, the line is typically weaker than H$\alpha$, hence of lower signal-to-noise.
+It is worth noting that the absolute flux calibration of the FMOS spectra is set to match ground-based IR imaging, UltraVISTA in the case of COSMOS, thus amounting to an effective aperture correction.
+While most recipes are calibrated against \hbeta\, the line is typically weaker than H$\alpha$, hence lower signal-to-noise.
 We provide the \mbh\ measurements together with the properties of the emission lines in Table~\ref{tab:result_mbh}.
@@
 It is well known that sample selection effects must be taken into account in order to  interpret the observed black hole-host relations and measure its evolution with redshift thus avoiding biases~\citep{Tre++07,Schulze2011,Bennert++2011, Schulze2014,Park15}.
-The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (such as AGN luminosity, line strength and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors.
+The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (such as AGN luminosity, line strength, and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors.
 Correcting for observational biases requires a well-characterized selection function, such as the one we have for our sample, and a model of the black hole mass function, and the evolution of the correlations between \mbh, and other properties.
@@
 In this framework, under the assumption of no evolution of the correlations between \mbh\ and host-galaxy properties, one can compute the expected bias for a given sample, prior to the observations.
-The key ingredient of this model are the local \mbh\ host-galaxy property correlations, the black hole mass function and Eddington ratio distribution at the redshift of observation.
-The latter two quantities are estimated from the type-1 AGN distributions \citep{Schulze2015} and corrected to represent the parent population of all active SMBH hosts thus including the obscured cases.
+The key ingredient of this model are the local \mbh\ host-galaxy property correlations, the black hole mass function, and Eddington ratio distribution at the redshift of observation.
+The latter two quantities are estimated from the type-1 AGN distributions \citep{Schulze2015} and corrected to represent the parent population of all active SMBH hosts, thus including the obscured cases.
 
@@
 To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04).
-It is worth noting that the local comparison sample are mainly bulge dominated, and their bulge mass is adopted in this work.
+It is worth noting that the local inactive sample is mainly bulge dominated, and we adopt the bulge mass for the entire local sample.
 In other words, our local comparison is the \mbh-\smass$_{\rm ,bulge}$ and not those involving total quantities.
@@
 We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations.
-We select samples that were analyzed by members of our team, to ensure uniform measurements.
+We select samples that were analyzed by members of our team to ensure uniform measurements.
 The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$.
@@
 Multi-band information provides the SED at a more precise level.
-A substantial fraction (21/32) of our objects have rest-frame UV images for those in COSMOS \citep{Koekemoer2007} and CDFS.
+A substantial fraction (21/32) of our objects have rest-frame UV images for those in COSMOS \citep{Koekemoer2007}.
 Here, we utilize images taken with ACS/F814W filter.
 The final image is drizzled to 0\farcs{03} pixel scale.
-Given the multi-band images for our AGN, we are able to infer their host color and assess the contribution of both the young and old stellar population which insures an accurate inference of rest-frame R-band luminosity (including a K-correction) and stellar mass \citep{Gallazzi2009}.
+Given the multi-band images for our AGN, we are able to infer their host color and assess the contribution of both the young and old stellar population which ensures an accurate inference of rest-frame R-band luminosity (including a K-correction) and stellar mass \citep{Gallazzi2009}.
 
@@
 
-The knowledge of the PSF is crucial for imaging decomposition of the AGN and its host, especially when the point source contributes the majority of the total emission.
-The PSF is known to vary across the detector and in time due to the effects of aberration and breathing.
-Simulated PSF, such those based on {\sc TinyTim}, are usually insufficient for our purposes \citep{Mechtley2012}.
+The knowledge of the PSF is crucial for imaging decomposition of the AGN and its host, especially when the point source contributes to the majority of the total emission.
+The PSF is known to vary across the detector and over time due to the effects of aberration and breathing.
+Simulated PSF, such as those based on {\sc TinyTim}, are usually insufficient for our purposes \citep{Mechtley2012}.
 Stars within the field-of-view of each observation provide a better description than the simulated PSF since they are observed simultaneously with the science targets, and reduced and analyzed in a consistent manner \citet{Kim2008, Park15}.
-Actually, we have found that such stars usually do not provide an ideal PSF for de-blending the AGN and host galaxy through extensive tests.
-The issues have to make due with an insufficient number of bright stars near our targets, color differences, and other effects not fully understood.
+However, we have found that such stars usually do not provide an ideal PSF for de-blending the AGN and host galaxy through extensive tests.
+The issues are associated with an insufficient number of bright stars near our targets, color differences, and other effects not fully understood.
 
@@
 First, we identify stars from the COSMOS2015 catalog \citep{Laigle2016}.
-Unfortunately, many bright stars with an intensity similar to our AGN sample were excluded in this catalog.
-Therefore, we manually select PSF-like objects as candidates from the \hst/WFC3 imaging.
+However, many bright stars with an intensity similar to our AGN sample were excluded in this catalog.
+Therefore, we also manually select PSF-like objects as candidates from the \hst/WFC3 imaging.
 We then discard non-ideal PSF candidates based on their intensity, FWHM, central symmetry, and presence of nearby contaminants.
@@
 %In the next subsection, we carry out the AGN decomposition using each PSF.
-We rank their performance based on the goodness (i.e.
-$\chi^2$) so that the final inference of the host properties are weighted from the top-rank PSFs.
+We rank their performance based on the goodness (i.e., $\chi^2$) so that the final inference of the host properties are weighted from the top-rank PSFs.
 
@@
 We simultaneously fit the nearby galaxies, that happen to be close enough to the AGN, with a \sersic\ model to account for any potential contamination from their extended profiles.
-The systems CID206 and ECDFS-358 have nearby objects which could not be described by \sersic\ model thus we mask these objects in the fitting procedure.
+The systems CID206 and ECDFS-358 have nearby objects which could not be described by \sersic\ model; thus, we mask these objects in the fitting procedure.
 
@@
 \lenstronomy\ is a multi-purpose open-source gravitational lens image forward-modeling package written in Python.
-Its flexibility enables us to turn off the lensing channel and focus on the AGN and host decomposition\footnote{As a check, we compared the results from \lenstronomy\ to the commonly used galaxy modeling software {\sc Galfit} and confirm that the results are consistent between the two.}.
+Its flexibility enables us to turn off the lensing channel and focus on the AGN and host decomposition\footnote{As a check, we compared the results from \lenstronomy\ to the commonly used galaxy modeling software {\sc Galfit} and confirmed that the results are consistent between the two.}.
 The main advantage of \lenstronomy\ is that it returns the full posterior distribution of each parameter (i.e., not just the best fit model) and the Laplace approximation of the uncertainties.
@@
 -- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample.
-By default, we extract an image of $61\times61$ pixels (i.e.
-$4''\times 4''$).
+By default, we extract an image of $61\times61$ pixels (i.e., $4''\times 4''$).
 If needed, a larger box size would be sufficient to include nearby objects.
@@
 The host property of an AGN is determined by the following steps.
-First, we model the AGN and host using each PSFs in the library.
+First, we model the AGN and host using each PSF in the library.
 With the input ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC.
@@
 \end{eqnarray} 
-where the $\alpha$ is an inflation parameter so that when $i=8$:
+where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter literally means that it has to be larger than~$1$.
+If $\alpha<1$, the relative likelihood between different PSFs would be too close and introducing $\alpha$ would have a side-effect.} so that when $i=8$:
 \begin{eqnarray}
 \label{eq:alpha}
-\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2,
+\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2.
 \end{eqnarray} 
@@
 where $N$ is the number of the ranking PSF, i.e., $N=8$.
-\noindent In Figure~\ref{fig:AGN_decomp}, we demonstrate the results for COSMOS-CID1174. The adopted weights are listed in Table~\ref{tab:weight_CID1174}.
+\noindent In Figure~\ref{fig:AGN_decomp}, we demonstrate the best-fit result for COSMOS-CID1174. The adopted weights are listed in Table~\ref{tab:weight_CID1174}.
 
@@
 We apply this approach to all AGNs to determine the global characteristics of the hosts of type-1 AGNs at these high redshifts.
-We measure the effective radius (\Reff), \sersic\ index and host-to-total flux ratio and describe each of these in the following section.
+We measure the effective radius (\Reff), \sersic\ index, and host-to-total flux ratio and describe each of these in the following section.
 We recognize that these measurements are weighted by the eight top-ranked PSFs.
@@
 %The inference of F814w data.
-We carry out a similar analysis for 21/32 AGNs in the COSMOS field with ACS/F184W imaging data.
+We carry out a similar analysis for 21/32 AGNs in the COSMOS field which have ACS/F184W imaging data.
 We assess their host flux ratio using the same approach as done for the WFC3-IR.
-The ACS FOV is larger than WFC3 thus we generated 174 PSFs for use.
+The ACS FOV is more extensive than WFC3 one; thus we generated 174 PSFs for use.
 As expected, the detection of the host galaxy in the IR band is of higher significance than the UV due to the effects of dust extinction and the contrast between the (blue) AGN and (red) host.
@@
 
-From our AGN-host decomposition, we detect the host galaxy in essentially all cases.
+From our AGN-host decomposition, we detect the host galaxy essentially in all cases.
 \hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data-point source'' stamps) of Figures~\ref{fig:AGN_decomp} and Appendix~\ref{sec:restsample}.
@@
 We compare the morphology of AGNs host galaxies to the inactive ones from the CANDELS/COSMOS imaging survey.
-We identify 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} using \galfit, and their stellar masses are derived based on 3-D-\hst\ spectroscopic survey~\citep{Momcheva2016, Brammer2012}.
+We identify 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} using \galfit.
+Their stellar masses are derived based on 3-D-\hst/CANDELS spectroscopic survey~\citep{Momcheva2016, Brammer2012}, which are comparable to our AGNs host stellar ($9.5< \log (M_* /M_{\odot})< 11.5$) as estimated in Section~\ref{sec:mm}.
 We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where we find no significant difference between their distributions and median value.
@@
 
-%In Figure~\ref{fig:Mstar-rn}, we plot the \smass\ versus the \Reff\ and \sersic\ index.
-The color coding is based on the filter flux ratio between WFC3 and ACS.
-The distribution of \smass-\Reff\ relation show that our AGN hosts concentrate at the high end of the stellar mass, close to the red sequence.
-%\begin{figure*}
-%\centering
-%\begin{tabular}{c c}
-% \hspace{-2.5em}
-%{\includegraphics[trim = 0mm 0mm 90mm 0mm, clip, height=0.45\textwidth]{fig/Mstar-Reff.pdf}}&
-%{\includegraphics[ height=0.45\textwidth]{fig/Mstar-Sn.pdf}}\\
-%\end{tabular}
-%\caption{\label{fig:Mstar-rn} 
-%The comparison of the galaxy properties between our 32 AGNs' hosts to the CANDELS sample including 4401 inactive galaxies (circles).
-The color coding is based on the filter flux ratio between WFC3 and ACS.
-For CANDELS sample, the WFC3/F125W flux is taken.
-The black squares are the AGN samples with only WFC3 band observation.
-%}
-%\end{figure*}
-
 \begin{figure}[ht]
-%\centering
-%\begin{tabular}{c c}
-%{\includegraphics[ height=0.3\textwidth]{fig/Hist_Reff.pdf}}&
-%{\includegraphics[ height=0.3\textwidth]{fig/Hist_Sn.pdf}}
-%\end{tabular}
 \epsscale{1.2}
@@
 \end{figure}
-%
-
-%We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive} and find that our high-$z$ AGN host have very similar distribution.
-%Thus, we assume the inactive galaxies and our AGN hosts have similar bulge-total ratio so that we can infer the bulge stellar mass of our sample, as shown below.
 
@@
 To minimize the uncertainty associated with these corrections, we use this template to interpolate to the rest-frame R band which is very close to the observed wavelengths.
-We find that a $1$~Gyr stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} provides a good match to the observed colors of our sample (see Figure~\ref{fig:compare_temp}).
+We find that a $1$~Gyr stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} provides an excellent match to the observed colors of our sample (see Figure~\ref{fig:compare_temp}).
 We note that the choice is not unique, and other combinations of ages and metallicities and star formation history could match the observed colors and would provide very similar R-band magnitudes, and also stellar masses \citep{Bell2000, Bell2001}.
@@
 Adopting the $1$~Gyr stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample.
-As mentioned above, since the WFC3 filter is already close to the rest-frame R-band, we expect the $M_R$ uncertainty introduced by this K-correction to be within 0.05~mag.
+As mentioned above, since the WFC3 filter is already close to the rest-frame R-band, we expect the $M_R$ uncertainty introduced by this K-correction to be within $0.05$~mag.
 We derive the rest-frame R band luminosity from $\log L_R/L_{R, \odot} = 0.4\times(M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}.
@@
 The distribution of our data appears to be in good agreement with the local relation and the other AGN samples at lower redshift.
-Therefore, the observational data indicate that the relation between black hole mass and the host luminosity are similar at different period of the universe.
-In Appendix~\ref{sec:ml-ev}, we explore how the high-$z$  sample would evolve in this plane solely with luminosity evolution of the host galaxy as done in past studies \citep[e.g., ][]{Ding2017b}.
+Therefore, the observational data indicate that the relation between black hole mass and the host luminosity are similar at different periods of the universe.
+In Appendix~\ref{sec:ml-ev}, we explore how the high-$z$  sample would evolve in this plane solely with the luminosity evolution of the host galaxy as done in past studies \citep[e.g., ][]{Ding2017b}.
 
@@
 We suspect that this source may have abnormal host properties.
-Indeed, the value of \Reff\ has a large uncertainty ($\sim 75\%$) and the host-to-total flux ratio is the lowest of the high-$z$ sample ($<10\%$).
-
-%Considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame.
-We will make this comparison taking the evolution effect into account in Section~\ref{sec:ml-ev}.
-
-%For CDFS-1 and CDFS-724, their host are \Reff$<0\farcs{}15$, smaller than the PSF FWHM.
-Moreover, the broad emission line of \mbh\ are from \citet{Suh2015} which could have systemic to \citet{Schulze2018}.
-Thus, the measurements of these three systems have less fidelity.
+Indeed, the value of \Reff\ has a large uncertainty ($\sim 75\%$), and the host-to-total flux ratio is the lowest of the high-$z$ sample ($<10\%$).
 
@@
 R-band luminosity relation.
-The black line and the blue colored equation indicates the best-fit result of local sample as given in Equation~\ref{eq:MLlocal}, with $1-\sigma$ confidence interval indicated by gray region.
+The black line and the blue colored equation indicates the best-fit result of the local sample as given in Equation~\ref{eq:MLlocal}, with $1\sigma$ confidence interval indicated by the gray region.
 }
@@
 Using the NIR imaging with \hst, we take the host luminosity along with color information to estimate the stellar mass content of each host galaxy based on the mass-to-light ratio of the adopted  $1$~Gyr stellar population.
-The uncertainty level associated with the stellar mass is expected to be of order $0.1$~dex (changing the IMF would effect all our stellar masses systematically).
+The uncertainty level associated with the stellar mass is expected to be of order $0.1$~dex (changing the IMF would affect all our stellar masses systematically).
 We find $M_*$ ranges between $\log M_* \in [9.7, 11.3]$ ($M_{\odot}$).
@@
 However, there is a slight shift of the high-$z$ data towards higher black hole masses at a fixed host mass.
-In Figure~\ref{fig:MM-vz}, we plot, as a function of redshift, the mass ratio ({\it right} panel) and the mass ratio difference ($\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$ which is considered as the difference between the high redshift data and the best-fit local relation; {\it left} panel).
-For our high-$z$ sample, we find the average $\Delta \log \mathcal M_{\rm BH}$ to be 0.3, a factor of two higher than the local mass ratio as indicated by the top green circle in Figure~\ref{fig:MM-vz}.
+In Figure~\ref{fig:MM-vz}, we plot the mass ratio as a function of redshift ({\it right} panel) and the mass ratio difference ($\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$ which is considered as the difference between the high redshift data and the best-fit local relation; {\it left} panel).
+For our high-$z$ sample, we find the averaged $\Delta \log \mathcal M_{\rm BH}$ to be $0.32$, a factor of two higher than the local mass ratio as indicated by the top blue circle in Figure~\ref{fig:MM-vz}.
 
@@
 \end{eqnarray} 
-
-If perform such a fit based on the {\it observed} data (i.e., no correction for selection effects), we obtain $\gamma  = 0.78 \pm 0.26$ that may be tentatively considered as evidence for evolution.
-Even with the exclusion of the few outliers, there is an evolution in the relation with $\gamma  = 0.65 \pm 0.27$.
+Performing such a fit based on the {\it observed} data (i.e., no correction for selection effects), we obtain $\gamma  = 0.78 \pm 0.26$ that may be tentatively considered as evidence for evolution.
+Even with the exclusion of the few outliers, there is an evolution in the correlation with $\gamma  = 0.65 \pm 0.27$.
 The best-fit {\it observed} evolution model is shown in Figure~\ref{fig:MM-vz}.
@@
 The orange band is the intrinsic scatter of local linear relation.
-The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, with slope value $\gamma  = 0.78 \pm 0.26$.\\
+The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, with slope value $\gamma  = 0.78 \pm 0.26$.
 {\it Right}: \mbh/\smass\ as a function of redshift.
-We use green open circles to show the expected shifting of the median value of the $\Delta \log$\mbh\ before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.}
+{\bf In both panels, we use blue open circles to show the expected bias of the median value for the $\Delta \log$\mbh.
+We use framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework} and show that even if there were no evolution, but selection effect would shift the expectation towards the measurements.}}
 \end{figure*}
@@
 To quantitively make this comparison, we calculate the intrinsic scatter of their offset value, based on Equation~\ref{eq:infer_value}, and obtain $0.33$ for high-$z$ and $0.40$ for local samples, respectively.
-This result is against the scenario where the random merger is the origin of the correlation \citep{Peng2007}, indicating that there is likely to be a connection between the SMBHs and their host galaxies during their formation.
+The fact that the intrinsic scatter for the high-$z$ sample is no larger than the local one is against the scenario where the random merger is the origin of the correlation \citep{Peng2007}, indicating that there is likely to be a connection between the SMBHs and their host galaxies during their formation.
 
@@
 
-In Section~\ref{sec:sf_framework}, we used the Bayesian framework introduced by \citet{Schulze2011} to forward model the distribution functions through a selection convolution.
-The result show that in the case of no intrinsic evolution of the correlations we would expect to measure an offset corresponding to a $+0.21$~dex bias in the inferred $\Delta \log$\mbh, owing to our selection function.
+In Section~\ref{sec:sf_framework}, we used the Bayesian framework introduced by \citet{Schulze2011} and find that in the case of no intrinsic evolution of the correlations we would expect to measure an offset corresponding to a $+0.21$~dex bias in the inferred $\Delta \log$\mbh, owing to our selection function.
 Interestingly, this bias could account for the majority of the observed offset as obtained in the \mbh-\smass\ correlations in the last section.
 %~\ref{sec:mm}.
-To illustrate the expected bias, we use green open circles to show the corresponding shift of the observed points if one were to correct for this bias in Figure~\ref{fig:MM-vz}.
-We also show, in Figure~\ref{fig:offset_hist}, the histogram $\Delta \log$\mbh\ by the high-$z$ sample and compare to the local ones.
+To demonstrate, we use blue open circles to show the expected bias raised by this selection effect in Figure~\ref{fig:MM-vz}.
+We also show, in Figure~\ref{fig:offset_hist}, the histogram $\Delta \log$\mbh\ of the high-$z$ sample and compare it to the local ones.
 The plots show that the correlations between \mbh\ and host galaxy total stellar mass or luminosity could be consistent with those of the local samples given the uncertainties and selection function.
@@
 The gray/red vertical line shows the mean value of the offset for the high-$z$ sample, before/after considering the selection effect.
-The median value of the offset are very close to the mean value ($+0.3$).
+The median value of the offset is very close to the mean value ($+0.30$).
 %TT: we need to show the mean, not the median.
@@
 In order to further evaluate the ``true" underlying evolution and its uncertainty, corrected for selection effects, taking into account the actual observations, we adopt an independent method based on the approach introduced by \citet{Tre++07} and developed by \citet{Ben++10}, \citet{Park15} and \citet{Ding2017b}.
-The method parametrizes the evolution of the correlations between \mbh\ and host galaxy properties as an offset from the local one $\gamma$ and an intrinsic scatter \sint, which can be a free parameter or tied to the local relation.
+The method parametrizes the evolution of the correlations between \mbh\ and host properties as an offset from the local one $\gamma$, and an intrinsic scatter \sint, which can be a free parameter or tied to the local relation.
 It then imposes a selection function in \mbh\ and calculates the intrinsic parameters of the model given the observations.
@@
 To illustrate the importance of the intrinsic scatter in the selection effects, we adopt both uniform (flat) prior and lognormal prior for \sint.
-Note that this method assumes a narrow Eddington ratio distribution which is different to the one by \citet{Schulze2011}, as described in Section~\ref{sec:sf_framework}.
-Also, this method adopts the local black hole mass function rather than high-$z$ BH mass function.
-These differences have a second order effect and could be responsible for the different magnitude of the selection effect.
+Note that this method assumes a narrow Eddington ratio distribution, which is different from the one by \citet{Schulze2011}, as described in Section~\ref{sec:sf_framework}.
+Also, this method adopts the local black hole mass function rather than the high-$z$ BH mass function.
+These differences have a second-order effect and could be responsible for the different magnitude of the selection effect.
 On the other hand, this method probes the importance of the scatter at high-$z$, which is complementary.
@@
 Thus one cannot conclude that evolution is significantly detected in our data.
-When relaxing the prior on \sint\ we find that the scatter is consistent with being as low as in the local samples, with a one-sided interval including zero and with $1-\sigma$ upper limit at around $0.5$~dex.
+When relaxing the prior on \sint\ we find that the scatter is consistent with being as low as in the local samples, with a one-sided interval including zero and $1\sigma$ upper limit at around $0.5$~dex.
 We also study the selection effect by only considering the new 32 AGNs, resulting in a higher evolutionary trend with a higher value of $\gamma$.
@@
 
-A simple check using our priori estimate of the bias, yields a similar result.
-The mean offset of the sample of 32 objects from the local relationship is $0.34\pm0.06$ dex, which would correspond to $\gamma=0.85\pm0.15$.
-However, after correcting for the selection bias ($0.21$~dex, see Section~\ref{sec:sf_framework}), the offset reduces to $0.13\pm0.06$ and thus $\gamma=0.33\pm0.15$, mildly positive but not significantly so, and consistent with the a posteriori method within the error bars and the uncertainty in the correction.
+A simple check using our prior estimate of the bias yields a similar result.
+The mean offset of the sample of 32 objects from the local relationship is $0.32\pm0.06$ dex, which would correspond to $\gamma=0.80\pm0.15$.
+However, after correcting for the selection bias ($0.21$~dex, see Section~\ref{sec:sf_framework}), the offset reduces to $0.11\pm0.06$ and thus $\gamma=0.28\pm0.15$, mildly positive but not significantly so, and consistent with the a posteriori method within the error bars and the uncertainty in the correction.
 We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
@@
 Taking selection effects into account, figure illustrate the constraining on the evolution factor $\gamma$ of \mbh-\smass\ relation by Equation~\ref{eq:offset}, with intrinsic scatter \sint, using Monte Carlo simulation.
-The adopted sample includes our 32 AGNs and the intermediate redshift AGNs, using flat prior of \sint\ (left panel) and lognormal prior (right panel).
+The adopted sample includes our 32 AGNs and the intermediate redshift AGNs, using flat prior of \sint\ ({\it left} panel) and lognormal prior ({\it right} panel).
 }
@@
 
-The local sample of inactive galaxies used in this analysis is mainly comprised of bulge-dominated galaxies and the \smass\ we adopted are their bulge masses.
+The local sample of inactive galaxies used in this analysis is mainly comprised of bulge-dominated galaxies, and the entire local \smass\ we adopted are their bulge masses.
 That is, in previous sections, we are comparing the \mbh-\smass$_{\rm ,total}$ relations in the distant universe to the \mbh-\smass$_{\rm ,bulge}$ relations locally.
-Considering that a significant stellar component of the high-$z$ AGNs have a disk component (i.e., AGN hosts with fitted \sersic\ index close to 1),  \smass$_{\rm , bulge}$ will be smaller than \smass$_{\rm ,total}$.
-
-Given that the structure of our 32 AGN hosts are similar to inactive
+Considering that a significant stellar component of the high-$z$ AGNs have a disk component (i.e., AGN hosts with fitted \sersic\ index close to 1),  \smass$_{\rm , bulge}$ must be smaller than \smass$_{\rm ,total}$.
+
+Given that the structures of our 32 AGN hosts are similar to inactive
 galaxies at the same redshifts and stellar masses
@@
 a similar distribution which can be estimated using a single-\sersic\
-index \citep{Bruce2014}. With this B/T estimation, we can infer the
-bulge stellar mass of our AGN host.
+index \citep{Bruce2014}. We can then infer the bulge stellar mass of our
+AGN host, based on the B/T estimation.
 
@@
 single-\sersic\ index and B/T ratios for CANDELS inactive galaxies
-at the similar mass level, i.e \smass$\in [9.0, 11.5]$, using B/T
+at the similar mass level, i.e., \smass$\in [9.0, 11.5]$, using B/T
 measured by \citet{Dimauro2018}. {\bf We then adopt the Monte Carlo approach
-and take random sample of the \sersic\ index for each AGN, based on their
+and take a random sample of the \sersic\ index for each AGN, based on their
 inference in Table~\ref{tab:result_sersic}. In the next step, we randomly
 sample the B/T ratio based on its distribution in \citet{Dimauro2018}
-at sampling \sersic\ index. To avoid any unphysical faint bulge flux, we
+at the sampling \sersic\ index. To avoid any unphysical faint bulge flux, we
 set the lower limit for B/T ratio as $0.1$. 
@@
 \smass$_{\rm, bulge}$ to that of the \mbh\ and estimate the offset and $\gamma$. 
-We take 10,000 times of realization to make sure the distribution of the
+We take 10,000 times of realization to make sure the distribution of
 random sampling has become stable. Note that the Monte Carlo approach would
@@
 As expected, we find a stronger offset of
-$0.74\pm0.12$~dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
+$0.77\pm0.08$~dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
 local relation, which corresponds to an evolutionary trend with
 $\gamma = 1.86\pm0.30$. Since selection effects are independent of B/T in
-our framework we can apply our a-priori estimate of the selection
-effect correction by removing $0.21$~dex, leaving a significant offset
-of $0.53\pm0.12$. {\bf We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
+our framework, we can apply our prior estimate of the selection
+effect correction by removing $0.21$~dex, leaving still a significant offset
+of $0.56$~dex. {\bf We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
 the Monte Carlo approach in Figure~\ref{fig:gamma_hist}. Same as
@@
 Even with the uncertainty associated with our estimate of the
-bulge-to-total ratio it is clear that there is significant evolution
+bulge-to-total ratio, it is clear that there is a significant evolution
 in the \mbh\ -- \bmass\ relation, considering the
@@
 
-We list the inferred $\gamma$ using the different combination of sample in this section in
+We list the inferred $\gamma$ using the different sample combinations in this section in
 Table~\ref{table:diff_sample_gam}.
@@
 \caption{\label{fig:gamma_hist} 
-Illustration of the distribution from the $10,000$ time realization. {\it Left}: \mbh/\smass\ distribution for 32 high-$z$ sample, compared to the local one. {\it Right}: $\gamma$ distribution.
+Illustration of the distribution from the $10,000$ time realization.
+{\it Left}: \mbh/\smass\ distribution for 32 high-$z$ sample, compared to the local one.
+{\it Right}: $\gamma$ distribution, with median value (blue line) and $1\sigma$ region (dashed line) .
 }
@@
 We consider if the offset is related to the AGN activities.
-The straightforward way is to study such offset, i.e.
-$\Delta \log \mathcal M_{\rm BH}$, as a function of \mbh\ and Eddington ratios, showing in Figure~\ref{fig:offset_vs_MBH_edd}.
+The straightforward way is to study such offset, i.e., $\Delta \log \mathcal M_{\rm BH}$, as a function of \mbh\ and Eddington ratios, showing in Figure~\ref{fig:offset_vs_MBH_edd}.
 Interestingly, we visually see the trend that the offset turns to be larger with at value of \mbh.
@@
 
-In this work, we use state-of-the-art techniques to measure the host galaxy flux separating it from that of the point source.
-The fidelity of the host galaxy magnitude is high as demonstrated by the robustness with respect to the choice of PSF which is the main source of uncertainty.
+In this work, we use state-of-the-art techniques to measure the host galaxy flux, separating it from that of the point source.
+The fidelity of the host galaxy magnitude is high as demonstrated by the robustness with respect to the choice of PSF, which is the primary source of uncertainty.
 However, we introduce some uncertainty by adopting a simple stellar population template to derive the rest-frame R-band luminosity and stellar mass for the full population.
-In principle, if we had more information, we could improve on this source of uncertainty by adopting a specific stellar population model for each target.
-However, considering that the host magnitude in the \hst/ACS band is faint (host-to-total flux ratio $< 30\%$), the individual color that we measure is insufficient to further discriminate between templates and thus we adopt a single one for simplicity and to facilitate reproduction of our work.
+In principle, if we had more information on the color, we could improve on this source of uncertainty by adopting a specific stellar population model for each target.
+However, considering that the host magnitude in the \hst/ACS band is faint (host-to-total flux ratio $< 30\%$), the individual color that we measure is insufficient to further discriminate between templates, and thus we adopt a single one for simplicity and to facilitate reproduction of our work.
 
@@
 To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011} and  \citet{H+R04}.
-In the literature, other analyses of the local sample are available which could also be considered as the local anchor.
-We note that the different local samples have inconsistencies which could affect our measurement of the co-evolution.
+In the literature, other analyses of the local sample are available, which could also be considered as the local anchor.
+We note that the different local samples have inconsistencies, which could affect our measurement of the co-evolution.
 Since the local correlations are used to calibrate the single epoch black hole mass estimates, one needs to be self-consistent in the choice of local anchors and calibration of black hole mass estimators.
-Unfortunately, this is a thorny issue, since not all the local correlations are mutually consistent especially when considering different galaxy properties like luminosity, stellar mass, and velocity dispersion.
+Unfortunately, this is a thorny issue, since not all the local correlations are mutually consistent, especially when considering different galaxy properties like luminosity, stellar mass, and velocity dispersion.
 
@@
 We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset relative to our local sample.
-Note that a $+0.3$~dex difference could totally erase the $\Delta\log$\mbh\ for the high redshift sample as described in the last section, if it were independent from the black hole mass calibration.
+Note that a $+0.3$~dex difference could totally erase the $\Delta\log$\mbh\ for the high redshift sample as described in the last section, if it were independent of the black hole mass calibration.
 
 However, the \mbh-\sigstar\ relations by K13 are also offset by  $\sim+0.3$~dex with respect to those given by \citet{Woo2010}, which is the baseline for our adopted black hole mass estimators.
-Thus, if we were to adopt the K13 normalization instead, the \mbh\ of all the AGN sample should be increased by $\sim$0.3~dex.
+That is, if we were to adopt the K13 normalization instead, the \mbh\ of all the AGN sample should be increased by $\sim$0.3~dex at the same time.
 As a result, adopting a different local anchor would only globally affect the level of the \mbh\ to local and high-$z$ sample at the same time, with the result of leaving $\Delta\log$\mbh\ unchanged.
@@
 
-We find the average ratio between the mass of a supermassive black hole and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, by factor of $\sim2.2$ and $\sim2.5$ respectively, as compared to that in the local universe.
-However, taking into account selection bias, these correlations are
-consistent with those in the local universe within the 95\% confidence limits. 
+We find the average ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, by a factor of $\sim2.5$ and $\sim2.0$ respectively, as compared to that in the local universe.
+However, taking into account selection bias, these correlations are consistent with those in the local universe within the 95\% confidence limits.
 %Therefore, for a fixed black hole mass, the host galaxy total stellar mass and luminosity could be larger than in the local universe by a factor of two, or equal to the local universe which is consistent with no evolution.
@@
 Comparing to their \mbh, we find evolution with the ratio evolving as $(1+z)^{1.86\pm0.30}$, which is significant even when accounting for selection effects.
-We caution that the evolution of the bulge component is more uncertain than our measurement of the total galaxy components, since it is based on an estimate of the B/T ratio from the measured Sersic indices from a matched sample of inactive galaxies.
+We caution that the evolution of the bulge component is more uncertain than our measurement of the total galaxy components, since it is based on an estimate of the B/T ratio from the measured \sersic\ index based on a matched sample of inactive galaxies.
 Nevertheless, since the signal is stronger than for the integrated quantities, the measurement is more significant even given larger uncertainties.
@@
 If true, this may indicate that cosmic averaging of initially unrelated states \citep{Peng2007} are not driving the relation between SMBHs and their host galaxies, since then a larger scatter at higher redshifts would be expected.
-Thus, there is likely a connection between the two yet to be fully understood, contenders include AGN feedback or links to common gas reservoirs.
-
-Finally, the forthcoming launch of the {\it James Webb Space Telescope} ({\it JWST}) may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim7$) and thus trace the evolution of correlations at more distant universe.
+Thus, there is likely a connection between the two yet to be fully understood; contenders include AGN feedback or links to common gas reservoirs.
+
+Finally, the forthcoming launch of the {\it James Webb Space Telescope} ({\it JWST}) may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim7$) and thus trace the evolution of correlations at the more distant universe.
 Although, galaxies, as we know, are smaller at high-$z$ thus may remain challenging to detect under the glare of a luminous AGN.
-In the lower redshift Universe, wide area surveys with Subaru/HSC, LSST and WFIRST offer much promise to build samples for studying these mass ratios and dependencies on other factors (e.g., environment).
-
-%Our inference indicates the evidence of disk+bulge component, i.e.
-the ones with \sersic\ $n<2$, and the local comparing samples are bulge dominated sample, we hence conclude that the BHs 8-10~Gyrs ago reside in bulges, if not entire galaxies, which are less massive/luminous than today.
+In the lower redshift Universe, wide-area surveys with Subaru/HSC, LSST, and WFIRST offer much promise to build samples for studying these mass ratios and dependencies on other factors (e.g., environment).
+
+%Our inference indicates the evidence of disk+bulge component, i.e., the ones with \sersic\ $n<2$, and the local comparing samples are bulge dominated sample, we hence conclude that the BHs 8-10~Gyrs ago reside in bulges, if not entire galaxies, which are less massive/luminous than today.
 
@@
 We found a 0.3 dex systematic among different local sample \citep{Ben++10, Bennert++2011, H+R04, Kormendy13, Bentz2018}.
-Tough this systematic might not raise a severe issue in our study of $\Delta\log$\mbh\ (i.e.
-Section~\ref{sec:local_sys}), a solid sample served as the local anchor is still needed (Bennert et al., in prep).
+Tough this systematic might not raise a severe issue in our study of $\Delta\log$\mbh\ (i.e., Section~\ref{sec:local_sys}), a solid sample served as the local anchor is still needed (Bennert et al., in prep).
 On the other hand, comparing the observational measurements to the ones by the simulation could avoid not only the dependency to the local anchor, but also the bias by selection effect \citep{DeG++15, Khandai2015, Menci2014}.
@@
 
-XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
+XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT. VNB gratefully acknowledges assistance from a NASA grant associated with HST proposal GO 15215.
 
@@
 Having transferred the \lhost\ to today, we find that, as showing in Figure~\ref{fig:ML-vz}-(a), at fixed mass, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation.
-We fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 0.71 \pm 0.18$, as showing in Figure~\ref{fig:ML-vz}-(b).
+We fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 0.60 \pm 0.18$, as showing in Figure~\ref{fig:ML-vz}-(b).
 We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.3$, with flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
@@
 Column 2: Spectroscopic redshift.
-Column 3: WFC3 filter. Note that the targets from the COSMOS and (E)-CDF-S fields also have ACS imaging.
+Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS imaging.
 Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
@@
 Column~11: Host total stellar mass.
-Column~12: Bulge stellar mass, using \sersic\ index as B/T proxy, based on Section~\ref{sec:bh_bulge} and Figure~\ref{fig:BT-n_relation}.
+Column~12: Bulge stellar mass, using \sersic\ index as B/T proxy, see Section~\ref{sec:bh_bulge} for the details.
 }

### 2019-08-02 M_BH_relation/MM_all_vz.py

@@ -86,12 +86,18 @@ if style ==0:
                 s=580,marker="*",zorder=300, vmin=0.3, vmax=5, edgecolors='k')
 
     #Plot the median circle.
-    plt.scatter(np.log10(1+zs[9]),10**( MBs[9]- Mstar[9]),facecolors='none',
-                s=180,marker="o",zorder=900, vmin=0.3, vmax=5, edgecolors='green', linewidth='4',)    
-    plt.arrow(np.log10(1+zs[9]),10**( MBs[9]- Mstar[9]), 0,  -0.0013, zorder=900, head_length= 0.001374/8,head_width= 0.005,fc='k',ec='k')
-    plt.scatter(np.log10(1+zs[9]),10**( MBs[9]- Mstar[9]-0.21),facecolors='none',
-                s=180,marker="o",zorder=900, vmin=0.3, vmax=5, edgecolors='green', linewidth='4',)    
-        
+#    plt.scatter(np.log10(1+zs[9]),10**( MBs[9]- Mstar[9]),facecolors='none',
+#                s=180,marker="o",zorder=900, vmin=0.3, vmax=5, edgecolors='green', linewidth='4',)    
+#    plt.arrow(np.log10(1+zs[9]),10**( MBs[9]- Mstar[9]), 0,  -0.0013, zorder=900, head_length= 0.001374/8,head_width= 0.005,fc='k',ec='k')
+#    plt.scatter(np.log10(1+zs[9]),10**( MBs[9]- Mstar[9]-0.21),facecolors='none',
+#                s=180,marker="o",zorder=900, vmin=0.3, vmax=5, edgecolors='green', linewidth='4',)   
+    plt.scatter(np.log10(1+zs[9]), np.median(np.concatenate([10**(hloc[:,3]-hloc[:,1]),10**(bloc[:,3]-bloc[:,1])])),
+                facecolors='none', s=280,marker="o",zorder=900, vmin=0.3, vmax=5, edgecolors='blue', linewidth='6', alpha=0.5)       
+    plt.scatter(np.log10(1+zs[9]), np.median(np.concatenate([10**(hloc[:,3]-hloc[:,1]+0.21),10**(bloc[:,3]-bloc[:,1]+0.21)])),
+                facecolors='none', s=280,marker="o",zorder=900, vmin=0.3, vmax=5, edgecolors='blue', linewidth='6', alpha=0.5)      
[…]

### 2019-08-02 M_BH_relation/MM_all_vz_rest_ourownMBH.py

@@ -196,8 +196,8 @@ plt.show()
 #        print ID[i]
 
 #%%
-##calcualte the mean offset:
-#weighted_offset = np.sum(np.asarray(y_cosmos)*yerr_hz) / np.sum(yerr_hz)                              
-#rms_offset = np.sqrt(np.sum((np.asarray(y_cosmos)-weighted_offset)**2*yerr_hz) / np.sum(yerr_hz))
-##rms_offset = np.sqrt(np.mean((np.asarray(y_cosmos)-weighted_offset)**2)) #No error bar
-#print weighted_offset, rms_offset
+#calcualte the mean offset:
+weighted_offset = np.sum(np.asarray(y_cosmos)*yerr_hz) / np.sum(yerr_hz)                              
+rms_offset = np.sqrt(np.sum((np.asarray(y_cosmos)-weighted_offset)**2*yerr_hz) / np.sum(yerr_hz))
+#rms_offset = np.sqrt(np.mean((np.asarray(y_cosmos)-weighted_offset)**2)) #No error bar
+print weighted_offset, rms_offset/np.sqrt(32.)

### 2019-08-02 M_BH_relation/local_MM_vz.py

@@ -132,10 +132,10 @@ elif style ==1:
 Bkc=mlines.Line2D([], [], color='gray', ls='', marker='.', markersize=15)
 Hkc=mlines.Line2D([], [], color='black', ls='', marker='.', markersize=15)
 ######################
-#%%
-#calcualte the mean offset for the local:
-y_local=np.append(hloc[:,3]-(m_ml*hloc[:,1]+b_ml),bloc[:,3]-(m_ml*bloc[:,1]+b_ml))
-y_local_err = np.append((hloc[:,2]**2 + hloc[:,4]**2)**0.5, (bloc[:,2]**2 + bloc[:,4]**2)**0.5)
-weighted_offset = np.sum(np.asarray(y_local)*y_local_err) / np.sum(y_local_err)                              
-rms_offset = np.sqrt(np.sum((np.asarray(y_local)-weighted_offset)**2*y_local_err) / np.sum(y_local_err))
-print weighted_offset, rms_offset
+##%%
+##calcualte the mean offset for the local:
+#y_local=np.append(hloc[:,3]-(m_ml*hloc[:,1]+b_ml),bloc[:,3]-(m_ml*bloc[:,1]+b_ml))
+#y_local_err = np.append((hloc[:,2]**2 + hloc[:,4]**2)**0.5, (bloc[:,2]**2 + bloc[:,4]**2)**0.5)
+#weighted_offset = np.sum(np.asarray(y_local)*y_local_err) / np.sum(y_local_err)                              
+#rms_offset = np.sqrt(np.sum((np.asarray(y_local)-weighted_offset)**2*y_local_err) / np.sum(y_local_err))
+#print weighted_offset, rms_offset

### 2019-08-02 manuscript/manuscript.tex
Before sharing to John

@@
 Therefore, given the uncertainties, our results are in agreement with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter.
-Using a mass-matched sample of inactive galaxies to infer the bulge-to-total mass fraction we show that the bulge \mbh/\bmass~relation is significantly offset from the local one by a factor of $\sim$$+5.5$; this offset is still present even after accounting for selection effects.
+Using a mass-matched sample of inactive galaxies to infer the bulge-to-total mass fraction we show that the bulge \mbh/\bmass~relation is significantly offset from the local one by a factor of $\sim$$+5.5$; % 5.5 = 10^(1.86*log(2.5))
+this offset is still present even after accounting for selection effects.
 Thus, our observations are consistent with a scenario in which stellar mass is transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than the mass accretion onto the SMBH.

### 2019-08-05 manuscript/manuscript.tex
Before get tex from John

@@
 \altaffiltext{9}{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
-%\altaffiltext{7}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
-%\altaffiltext{8}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
 \begin{abstract}
@@
 \label{sec:introduction}
-%\citep[e.g.,][]{Park15,Kormendy13}
-
 Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass), and stellar velocity dispersion (\sigstar).
@@
 It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.
-
-%~\citep{DeG++15}.
-%We aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch close to the peak in the accretion history of SMBHs~\citep[e.g.,][]{Aird2015}.
 
@@
 
-%\section{Observations and data reduction}
-%\label{sec:data}
-%In this section, we summarize the sample selection, observations, and data reduction of our sample.
-
 \section{Experimental design}
 \label{sec:data}
-%Our study overcomes the limitations of previous studies in the following way.
-First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function.
-Second, we estimate \mbh\ using Balmer lines which avoids potential systematic uncertainties in the UV-based estimators.
-Third, our X-ray selected sample has lower nuclear-to-host ratios which facilitate the galaxy mass measurements.
-Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e., WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference.
-
 We utilize a sample size of 32 broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that have black hole mass measurements available and fall within deep extragalactic survey fields that offer rich ancillary data.
@@
 As a result, the estimation of the \mbh\ is achieved by these measurements, i.e., \mbh$\simeq G^{-1} R_{\rm BLR} \Delta V^2$ \citep{McLure2004}.
-
-%To avoid any systematic bias between samples in the literature, we compare the recipes implemented in \citet{Schulze2018} and \citet{Ding2017b}.
-We find that the \hbeta\ estimator is very consistent (\mbh\ r.m.s.
-$<0.03$~dex) between the two reference samples.
-We also find that the cross-calibration between the \halpha\ and \hbeta\ has better agreement in \citet{Schulze2018}.
-Thus, we adopt the scheme given in \citet{Schulze2018} that is based on the recalibration of these relations using luminous quasars out to high redshift \citep{Jun2015} :
 
@@
 
-%\subsubsection{AGN Emission Line}
-%\label{sec:bh_mass}
-% The introduction of the BH inferred by the board emission line.
-
-%\section{Analysis}
 \subsection{PSF library}
@@
 The dispersion of PSF shapes within our library provides us with a good representation of the level of uncertainty in our measurements resulting from the image decomposition.
-%In the next subsection, we carry out the AGN decomposition using each PSF.
-We rank their performance based on the goodness (i.e., $\chi^2$) so that the final inference of the host properties are weighted from the top-rank PSFs.
-
-%\label{sec:analysis}
-
-%\subsection{Surface Photometry}
-%\subsubsection{PSF library}    
-%\subsubsection{Surface Photometry modeling method}
 
@@
 \label{sec:analysis}
-%Introduce the lenstronomy. Model the PSF in each library.\\
-%Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
+
 We simultaneously fit the two-dimensional flux distribution of the central AGN and the underlying host galaxy.
@@
 
-%\begin{figure*}
-%\centering
-%{
-%\includegraphics[height=0.5\textwidth]{fig/flux_r_n_corner.pdf}
-%}
-%\caption{\label{fig:flux_r_n_corner}
-%Relations between the measured host galaxy parameters.}
-%\end{figure*}
-
 We apply this approach to all AGNs to determine the global characteristics of the hosts of type-1 AGNs at these high redshifts.
@@
 We note that the choice is not unique, and other combinations of ages and metallicities and star formation history could match the observed colors and would provide very similar R-band magnitudes, and also stellar masses \citep{Bell2000, Bell2001}.
-%(cite Bell \& de Jong 2001, 2003),
 
@@
 
-%{\bf [Include a full paragraph on the scatter]}
 As shown in these panels, the scatter of the high-$z$ correlation presents a similarity to the local relation.
@@
 The fact that the intrinsic scatter for the high-$z$ sample is no larger than the local one is against the scenario where the random merger is the origin of the correlation \citep{Peng2007}, indicating that there is likely to be a connection between the SMBHs and their host galaxies during their formation.
-
-%We summarize the inference of $\gamma$ using different combination of sample in Table~\ref{table:diff_sample_gam}.
-All the $\gamma$ by the observed \mbh-\smass\ are inferred as positive, indicating that the growth of the black hole predates that of the host bulge.
 
@@
 Histogram of the $\log($\mbh$)$ offset for the local samples and our 32 high-$z$ sample.
-The gray/red vertical line shows the mean value of the offset for the high-$z$ sample, before/after considering the selection effect.
-The median value of the offset is very close to the mean value ($+0.30$).
-%TT: we need to show the mean, not the median.
-Or at least both.
-The median excludes the pull from the higher points, which are probably what drives the inference later on, so for a proper comparison we need to include both.
+{\bf The gray vertical line shows the mean value of the offset for the high-$z$ sample, and the red vertical line shows the shift the expectation by the selection effect, even if there were no evolution.} The median value of the offset is very close to the mean value ($+0.30$).
 }
 \end{figure}
-
-%Our conclusion is that the considering the selection effect using framework by \citet{Schulze2011}, we get consistent \mbh-\smass\ with the local sample.
 
@@
 On the other hand, this method probes the importance of the scatter at high-$z$, which is complementary.
-%Thus each is complementary that should be stressed maybe in the abstract (see my suggested change).
 
@@
 Whereas we expect the negative tail to be suppressed by our selection function, and thus it should be accounted for in our treatment.
-%, it is true that those three objects contribute a large fraction of the object.
 If one computes the median offset instead of the mean, the offset is almost completely consistent with the expected bias.
@@
 
-%Then, we calculate the average B/T
-%ratio at different \sersic\ index to construct a relation for our
-%use, as shown in Figure~\ref{fig:BT-n_relation}. Taking this
-%relation, we estimate the B/T of our AGN sample using the \sersic\
-%index as proxy and infer their \smass$_{\rm, bulge}$ from the total
-%stellar mass.
-%We can now compare this \smass$_{\rm, bulge}$ to that
-%of the black hole \mbh.
 As expected, we find a stronger offset of
@@
 
-%{\color{blue}
-%\subsection{The origin of the offset}
-%{\color{red}[Xuheng:  Given their larger uncertainty, do we still want to present these figures?]}
-%We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift.
-We consider if the offset is related to the AGN activities.
-The straightforward way is to study such offset, i.e., $\Delta \log \mathcal M_{\rm BH}$, as a function of \mbh\ and Eddington ratios, showing in Figure~\ref{fig:offset_vs_MBH_edd}.
-Interestingly, we visually see the trend that the offset turns to be larger with at value of \mbh.
-However, at higher Eddington ratio, the offset turns to be lower.
-% {\color{red} Some interpretations need to be presented.}
-%}
-%\begin{figure*}
-%\centering
-%\begin{tabular}{c c}
-%\subfloat[Offset of the \mbh-\smass\ relation as a function of \mbh.]
-%{\includegraphics[height=0.5\textwidth]{fig/offset_vs_MBH.pdf}}&
-%\subfloat[Offset of the \mbh-\smass\ relation as a function of Eddington ratio.]
-%{\includegraphics[height=0.5\textwidth]{fig/offset_vs_Edd.pdf}}\\
-%\end{tabular}
-%\caption{\label{fig:offset_vs_MBH_edd} 
-%Illustration of the offset for high-$z$ \mbh-\smass\ sample as a function of \mbh\ (left) and Eddington ratio (right).}
-%\end{figure*} 
-%
-
 \subsection{Systematic errors}
@@
 
-%We highlight that, in this particular paper, we focus most on the decomposing of the AGN image to present our inference of the host.
-With the host inference, we then carry out a rapid analysis of the \mbh\ and host properties relations.
-The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.
-
 In any case, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates, and not by uncertainties in the photometry or stellar mass estimates.
@@
 This effort is currently in progress and when completed should enable us to completely eliminate this source of uncertainty \citep{Bennert11,Harris2012, Bennert2015}.
-
-%\begin{figure}
-%\centering
-%{\includegraphics[width=0.5\textwidth]{fig/local_MM_comparison.pdf}}
-%\caption{\label{fig:local_MM_comp} 
-%The local \mbh-\smass\ relations from different literature.
-The black and red line are the best-fit linear relation using the sample by combining B11+HR04 and B11+ K13, respectively, showing a 0.3~dex offset in the intercept value.
-%}
-%\end{figure}
 
@@
 However, taking into account selection bias, these correlations are consistent with those in the local universe within the 95\% confidence limits.
-%Therefore, for a fixed black hole mass, the host galaxy total stellar mass and luminosity could be larger than in the local universe by a factor of two, or equal to the local universe which is consistent with no evolution.
 Even with the remaining uncertainties in the corrections for selection, we are confident that any evolution in the \mbh/\smass\ relation is at the most a factor of two with the case of no evolution entirely plausible.
@@
 
-%Our inference indicates the evidence of disk+bulge component, i.e., the ones with \sersic\ $n<2$, and the local comparing samples are bulge dominated sample, we hence conclude that the BHs 8-10~Gyrs ago reside in bulges, if not entire galaxies, which are less massive/luminous than today.
-
-%Towards a better estimation of the evolution of the scaling relations, we address the limitations of this work.
-First, most of the host-total ration in the \hst/ACS band are low ($<20\%$), the fidelity of the host flux are thus limited at UV band.
-In addition, when deriving the \lhost\ and \smass, we adopt a universal stellar template to the overall galaxies based on the general inference between UV band and IR band, rather than carry out the SED fitting for each galaxy.
-Second, the local scaling relations that we currently adopted are not yet solid.
-We found a 0.3 dex systematic among different local sample \citep{Ben++10, Bennert++2011, H+R04, Kormendy13, Bentz2018}.
-Tough this systematic might not raise a severe issue in our study of $\Delta\log$\mbh\ (i.e., Section~\ref{sec:local_sys}), a solid sample served as the local anchor is still needed (Bennert et al., in prep).
-On the other hand, comparing the observational measurements to the ones by the simulation could avoid not only the dependency to the local anchor, but also the bias by selection effect \citep{DeG++15, Khandai2015, Menci2014}.
-To overcome these limitation, we are incorporating our measurement with the ground-based photometry to derive SED fitting, in order to compare with the sample by simulations, which will be presented in the coming up paper.
-
-%
-
-%\clearpage
 \section*{Acknowledgments}
@@
 
-{\color{red} More acknowledges to be updated.}
+%{\color{red} More acknowledges to be updated.}
 

### 2019-08-05 material/recover_figure1_in_paper/recover_figure1.py

@@ -97,7 +97,7 @@ x_cline = np.linspace(7.1, 8.5)
 y_line_3 = -1.1*(x_cline-7.5) -0.5
 #ax.plot(x_cline, y_line_3,'k--')
 plt.xlabel("log$(M_{BH}/M_{\odot})$",fontsize=25)
-plt.ylabel("log$L_{bol}/L_{Edd}$", fontsize=25) 
+plt.ylabel("log $L_{bol}/L_{Edd}$", fontsize=25) 
 plt.tick_params(labelsize=15)
 plt.xticks(np.arange(7.5,9.6,0.5))
 other_data = np.loadtxt('Peng_Decarli_data.txt')
@@ -177,7 +177,7 @@ ax_y.plot(x_cline, y_line_1, 'k--')
 plt.xticks(np.arange(-10,10,2))
 plt.xlim([int(rho_lam.min()),int(rho_lam.max())+1])
 plt.tick_params(labelsize=15)
-plt.xlabel("log$\phi(\lambda))$", fontsize=25) 
+plt.xlabel("log$\phi(\lambda)$", fontsize=25) 
 
 #%%
 # the xaxis of ax_x and yaxis of ax_y are shared with ax,
@@ -191,7 +191,7 @@ for tl in ax_y.get_yticklabels():
     tl.set_visible(False) 
 ax.set_xlim([7.4, 9.7])
 ax.set_ylim([-1.9, 0.3])
-#plt.savefig("AGN_selection.pdf")
+plt.savefig("AGN_selection.pdf")
 plt.show()
 
 #%%Print them for Andreas

### 2019-08-06 manuscript/manuscript.tex
Submit the paper to ApJ

@@
 
-\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{4}, Malte Schramm\altaffilmark{4}, Simon Birrer\altaffilmark{1}, Daeseong Park\altaffilmark{5}, Knud Jahnke\altaffilmark{6}, Vardha N.
-Bennert\altaffilmark{7}, Jeyhan S.
-Kartaltepe\altaffilmark{8}, Anton M.
-Koekemoer\altaffilmark{9},  Matthew A.
-Malkan\altaffilmark{1}  % {\color{blue} Federica Duras\altaffilmark{7, 8}, Angela Bongiorno\altaffilmark{8}}
+\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3,4}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{5}, Malte Schramm\altaffilmark{5}, Simon Birrer\altaffilmark{1}, Daeseong Park\altaffilmark{6}, Knud Jahnke\altaffilmark{7}, Vardha N.
+Bennert\altaffilmark{8}, Jeyhan S.
+Kartaltepe\altaffilmark{9}, Anton M.
+Koekemoer\altaffilmark{10},  Matthew A.
+Malkan\altaffilmark{1}, David Sanders\altaffilmark{11}
  }
@@
 \altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
-\altaffiltext{4}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
-\altaffiltext{5}{Korea Astronomy and Space Science Institute, Deajeon, 34055, Republic of Korea}
-\altaffiltext{6}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117, Heidelberg, Germany}
-\altaffiltext{7}{Physics Department, California Polytechnic State University, San Luis Obispo CA 93407, USA}
-\altaffiltext{8}{School of Physics and Astronomy, Rochester Institute of Technology, 84 Lomb Memorial Drive, Rochester, NY 14623, USA}
-\altaffiltext{9}{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
+\altaffiltext{4}{Department of Astronomy, School of Science, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan}
+\altaffiltext{5}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
+\altaffiltext{6}{Korea Astronomy and Space Science Institute, Deajeon, 34055, Republic of Korea}
+\altaffiltext{7}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117, Heidelberg, Germany}
+\altaffiltext{8}{Physics Department, California Polytechnic State University, San Luis Obispo CA 93407, USA}
+\altaffiltext{9}{School of Physics and Astronomy, Rochester Institute of Technology, 84 Lomb Memorial Drive, Rochester, NY 14623, USA}
+\altaffiltext{10}{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
+\altaffiltext{11}{Institute for Astronomy, University of Hawaii, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
 \begin{abstract}
@@
 A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates.
-For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
-By applying state-of-the-art tools to decompose the \hst\ image, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting.
-The black hole mass (\mbh) is determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators.
-We find that the  {\it observed} ratio of \mbh/\smass~is larger at $z\sim1.5$ by a factor of $\sim2.2$ as compared to that in the local universe, while the scatter is as low as in the local universe.
-However, when accounting for selection effects (estimated using two independent and complementary methods), we find that no-evolution is consistent with the data at the 95\% CL, both using our sample by itself and in combination with literature data.
+For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 \hbox{X-ray-selected} broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
+By applying state-of-the-art tools to decompose the \hst\ images, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting.
+The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators.
+We find the {\it observed} ratio of \mbh/\smass~to be $2.0\times$ larger at $z\sim1.5$ than in the local universe, while the scatter is equivalent between the two epochs.
+However, an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).
 The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
-Therefore, given the uncertainties, our results are in agreement with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter.
-Using a mass-matched sample of inactive galaxies to infer the bulge-to-total mass fraction we show that the bulge \mbh/\bmass~relation is significantly offset from the local one by a factor of $\sim$$+5.5$; % 5.5 = 10^(1.86*log(2.5))
-this offset is still present even after accounting for selection effects.
-Thus, our observations are consistent with a scenario in which stellar mass is transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than the mass accretion onto the SMBH.
+Therefore, our results are in agreement, considering the uncertainties, with a scenario where SMBHs and their total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter.
+Based on an inference of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is significantly offset from the local value by a factor of $+5.5$ which persists even after accounting for selection effects.
+Taken together, these observations are consistent with a scenario in which stellar mass is subsequently transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than mass accretion onto the SMBH.
 
@@
 \label{sec:introduction}
+
 Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass), and stellar velocity dispersion (\sigstar).
 The tightness of these correlations (also known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
-Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc).
-On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering either the active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or how the growth of these components is connected to the common gas supply~\citep{Cen2015, Menci2016}.
-On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, the statistical convergence from galaxy assembly alone (i.e., mergers) can reproduce the observed correlations.
-
-A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}.
-During the past decade, there has been much progress on this front at $z<1$ using type-1 AGNs.
-For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today.
-Similarly, studying the observation of the \mbh-\smass\ and \mbh-\sigstar\ relations, the works by \citet{Bennert11, Woo++08} find a positive evolution of \mbh, especially when the data are sufficiently robust to isolate the luminosity or stellar mass of the bulge or spheroidal component.
-Of similar results, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies; although, the accuracy of such an approach for luminous AGNs has not yet been well established.
+Currently, the physical mechanism that can produce such a tight relationship is unknown due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc).
+On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations, possibly by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}, not necessarily in a direct manner.
+On the other hand, there may not be a need for a physical coupling \citep{Peng2007, Jahnke2011, Hirschmann2010}, the statistical convergence from galaxy assembly alone (i.e., mergers) may reproduce the observed correlations.
+
+To understand the nature of these correlations, it is important to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}.
+During the past decade, there has been much progress on this front using type-1 AGNs.
+For example, it has been demonstrated at $z<1$ that at fixed \mbh\ the host galaxies are under luminous compared to today's hosts \citep{Park15, Tre++07, Pen++06qsob}.
+Similarly, \citet{Bennert11} and \citet{Woo++08} found a positive evolution of \mbh, especially when the data are sufficiently robust to isolate the luminosity or stellar mass of the bulge or spheroidal component.
+At $z>1$, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies.
+Although, the accuracy of such an approach for luminous AGNs has not yet been well established as discussed herein.
 If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.
@@
 However, there are studies \citep{Cisternas2011,SS13,Mechtley2016} based on \hst\  imaging of deep survey fields such as COSMOS and CDFS that report no evolution in the \mbh - \smass ~ mass ratio as compared to the local relation.
-In support, \citet{Sun2015} has re-analyzed the mass ratios for broad-line AGNs in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citet{Merloni2010} and finds no evolution when accounting for selection effects, as fully described in \citet{Schulze2014} who consider the black hole mass functions and Eddington rate distribution.
-
-In order to make progress, it is important to construct statistical high-$z$ samples that reduce as much as possible the uncertainties, and carefully consider selection effects and inherent systematic errors.
+In support, \citet{Sun2015} has re-analyzed the mass ratios for broad-line AGNs in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citet{Merloni2010} and finds no evolution when accounting for selection effects described in \citet{Schulze2014} which consider the black hole mass function and Eddington rate distribution of the sample at their respective epoch.
+
+To make substantial progress, it is important to construct statistical high-$z$ samples that reduce the uncertainties, and carefully consider selection effects and inherent systematic errors.
 First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method.
-In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as a non-gravitational component of the broad-line region (BLR) gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e., \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}.
-Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging.
-Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed AGNs, since lensing magnifies the host image to lensed arcs~\citep{Pen++06qsob, Ding2017a, Ding2017b}.
-Last but not least, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}.
-For instance, it has been demonstrated~\citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results would display \mbh - \smass\ with a steeper slope than random ones, suggesting the selection effects can exhibit faster evolution than a random sample.
-It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.
-
-In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to the highest redshifts where evolutionary effects should be strongest.
+In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as a non-gravitational component of the gas dynamics of the broad-line region (BLR), when compared to local samples with masses based on broad Balmer lines~\citep[i.e., \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}.
+Second, measurements of the host galaxy properties are challenging due to the overwhelming glare of the bright nuclear light.
+This ultimately requires careful modeling of the point spread function and, whenever possible, the use of lensed QSOs since the magnification increases the spatial resolution \citep{Pen++06qsob, Ding2017a, Ding2017b}.
+Especially not to be overlooked as in past studies, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}.
+For instance, it has been demonstrated by~\citet{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in a  \mbh - \smass\ relation with a steeper slope than if chosen randomly, suggesting the selection effects are the culprit rather than an intrinsically faster or even an existing evolution.
+It is also important to consider the selection function when comparing observed scaling relations with those from simulations \citep{DeG++15}.
+
+In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to higher redshifts where evolutionary effects should be strongest.
 In particular, samples based on 2D image analysis using \hst\ at $z>1$ are limited.
@@
 Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e., $\sim0.23$ dex,][]{Schulze2014}.
+This value is the minimum offset expected for a non-evolving mass ratio as described in Section~\ref{sec:sf_framework}.
 
 The paper is organized as follows.
-We briefly describe the sample selection and the BH masses of the sample in Section~\ref{sec:data}.
-We describe the observations and construction of a PSF library in Section~\ref{observation}.
-In Section~\ref{sec:analysis}, we decompose our sample and study the host galaxy surface photometry.
+We describe the sample selection and their BH masses in Section~\ref{sec:data}.
+We describe the new HST/WFC3 observations, available HST/ACS imaging, and construction of a PSF library in Section~\ref{observation}.
+In Section~\ref{sec:analysis}, we describe our method to decompose the rest-frame optical emission and measure the host galaxy surface photometry.
 In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population from which we apply to derive the rest-frame R-band \lhost\,~and \smass\ to compare with local relations.
@@
 Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~(\mbh/$M_{\odot})\lesssim8.5$.
-The bolometric luminosities are measured from AGN broad lines by \citet[][Section 3.3]{Schulze2018}, which are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
-The flux-limited nature of the sample results in higher Eddington ratios when \mbh\ is lower, as shown in Figure~\ref{fig:selection}.
+The bolometric luminosities are measured from the broad AGN lines by \citet[][Section 3.3]{Schulze2018}, which are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
+The flux-limited nature of the sample results in a slightly higher Eddington ratio distribution at lower \mbh\, as shown in Figure~\ref{fig:selection}.
 Moreover, we have a higher preference to select targets which have rest-frame UV images (i.e., \hst/ACS) as provided by \citet{Scoville2007} and \citet{Koekemoer2007} in the COSMOS field.
@@
 
-The \mbh\ of type-1 AGNs can be inferred using the so-called virial method~\citep{Peterson2004, Shen2013}.
+The \mbh\ of type-1 AGNs can be determined using the so-called virial method~\citep{Peterson2004, Shen2013}.
 The kinematics of the BLR trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas.
 Under these assumptions, the width of the emission-line provides the scale of the velocity dispersion ($\Delta V$), while the AGN continuum luminosity establishes an empirical scale of the BLR size ($R_{\rm BLR}$).
-As a result, the estimation of the \mbh\ is achieved by these measurements, i.e., \mbh$\simeq G^{-1} R_{\rm BLR} \Delta V^2$ \citep{McLure2004}.
-
-To avoid any systematic bias between samples in the literature, we aim to adopt a class of self-consistent estimators for our sample.
-We first compare the estimators implemented in \citet{Schulze2018} to those in \citet{Ding2017b}, and find that their \hbeta(FWHM(5100)) estimators are very consistent (\mbh\ r.m.s.
+The estimation of \mbh\ is then achieved using these measurements, i.e., \mbh$\simeq G^{-1} R_{\rm BLR} \Delta V^2$ \citep{McLure2004}.
+
+To avoid any systematic bias between samples in the literature, we adopt a class of self-consistent estimators for our analysis.
+We first compare the estimators implemented in \citet{Schulze2018} and \citet{Ding2017b}, and find very consistent \hbeta(FWHM(5100))-based masses (\mbh\ r.m.s.
 $<0.03$~dex).
-However, there is a $\sim~0.2$~dex inconsistency in their \halpha\ estimators.
-Thus, we utilize the AGNs in \citet{Schulze2018} that have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to determine which \halpha\ estimator has the best agreement between the two lines.
+However, there is a $\sim$0.2 dex inconsistency in their \halpha\ mass estimates.
+Therefore, we utilize the AGNs in \citet{Schulze2018} that have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to determine which \halpha\ estimator has the best agreement between the two lines.
 As a  result, the \halpha\ estimator in \citet{Schulze2018} has better agreement with \hbeta.
@@
 The key ingredient of this model are the local \mbh\ host-galaxy property correlations, the black hole mass function, and Eddington ratio distribution at the redshift of observation.
-The latter two quantities are estimated from the type-1 AGN distributions \citep{Schulze2015} and corrected to represent the parent population of all active SMBH hosts, thus including the obscured cases.
-
-Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model.
+The latter two quantities are estimated from the type-1 AGN distributions \citep{Schulze2015} and corrected to represent the parent population of all active SMBH hosts.
+%, thus including the obscured cases.
+
+Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model that include the local value of the mass \mbh/\smass ~ratio.
+To reiterate, an offset in the observed mass relations of 0.2 dex at $z\sim1.5$ can be considered consistent with no evolution in the mass ratio.
 This bias correction should be considered an approximate estimate, with an uncertainty that depends on the uncertainty of the inputs.
@@
 In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample.
-Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh}.
-For \mbh\ estimated from \Mgii\, we adopt the recipe by \citet{Ding2017b}.
-For all comparison AGN samples, we recalibrate the \mbh\ using the recipes given in Section~\ref{mbh}.
-For \mbh\ estimated using the \Mgii\ and  \hbeta$(\sigma_{\rm H\beta})$ lines, we adopt the recipes by \citet{Ding2017b}.
+Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh} including those estimated from \Mgii\ using the recipe in \citet{Ding2017b}.
 
@@
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
-\caption{\label{fig:AGN_decomp} AGN-host galaxy decomposition of COSMOS-CID1174 based on the \hst/WFC3 F140W image.The panels from left to right are as follows: (1) observed data, (2) best-fit model (AGN+host), (3) data minus the model PSF (i.e., host galaxy free of the AGN), (4) residuals divided by the variance and (5) 1-D surface brightness profiles (top) and the corresponding residual (bottom).
+\caption{\label{fig:AGN_decomp} AGN-host galaxy decomposition of COSMOS-CID1174 based on the \hst/WFC3 F140W image.The panels from left to right are as follows: (1) observed data, (2) best-fit model (AGN+host), (3) data minus the model PSF (i.e., host galaxy free of the AGN), (4) residuals divided by the variance and (5)~1-D surface brightness profiles (top) and the corresponding residual (bottom).
 The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects).
@@
 As shown in Figure~\ref{fig:hist_compare}, the results are consistent.
+For each AGN, we check the position of the top-ranked PSFs and find that they are unrelated to the AGN's position, which highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.
 
@@
 
-From our AGN-host decomposition, we detect the host galaxy essentially in all cases.
-\hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data-point source'' stamps) of Figures~\ref{fig:AGN_decomp} and Appendix~\ref{sec:restsample}.
-While some of the galaxies have nearby neighbors, most are isolated and do not show strong signs of interaction or ongoing mergers, {\bf which indicates the fueling of AGNs seems not from major mergers for our sample.} This is also relevant for model fitting with smooth \sersic\ profiles and the subsequent determination of the stellar mass.
+From our image decomposition, we detect the host galaxy essentially in all cases.
+\hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data-point source'' stamps) of Figure~\ref{fig:AGN_decomp} and in Appendix~\ref{sec:restsample} for the remaining cases.
+While some of the galaxies have nearby neighbors, most are isolated and do not show strong signs of interaction or ongoing mergers, which indicates the fueling mechanism of AGNs may not be from major mergers for our sample.
+This is also relevant for model fitting with smooth \sersic\ profiles and the subsequent determination of the stellar mass.
 In the following subsections, we describe the properties of our ensemble of type-1 AGN host galaxies.
@@
 Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
-{\bf The inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero.
+The inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero.
 This means the size inference of these three systems should really be considered an upper limit, rather than a measurement.
-However, the inference of their host luminosities and stellar masses are still reliable given the small scatter in the host flux ($<10\%$).}
-
-We compare the morphology of AGNs host galaxies to the inactive ones from the CANDELS/COSMOS imaging survey.
-We identify 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} using \galfit.
-Their stellar masses are derived based on 3-D-\hst/CANDELS spectroscopic survey~\citep{Momcheva2016, Brammer2012}, which are comparable to our AGNs host stellar ($9.5< \log (M_* /M_{\odot})< 11.5$) as estimated in Section~\ref{sec:mm}.
+However, the inference of their host luminosities and stellar masses are still reliable given the small scatter in the host flux ($<10\%$).
+
+We compare the morphology of AGNs host galaxies to inactive galaxies from the CANDELS imaging survey.
+We identify 4401 inactive galaxies within a redshift range ($1.2<z<1.7$), comparable to our AGN sample, whose \sersic\ measurements are provided by \citet{VDwel++2012} using \galfit.
+Their stellar masses are derived based on the 3-D-\hst/CANDELS spectroscopic survey~\citep{Momcheva2016, Brammer2012} and comparable to our AGN hosts ($9.5< \log (M_* /M_{\odot})< 11.5$; Section~\ref{sec:mm}).
 We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where we find no significant difference between their distributions and median value.
@@
 The blue curve is the predicted model by the $1$~Gyr stellar population.
-As comparison, we plot the predicted model by the $5$~Gyr stellar population.
+For comparison, we plot the predicted model for a $5$~Gyr stellar population that is definitely ruled out by our data.
 }
@@
 {\it Right}: \mbh/\smass\ as a function of redshift.
-{\bf In both panels, we use blue open circles to show the expected bias of the median value for the $\Delta \log$\mbh.
-We use framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework} and show that even if there were no evolution, but selection effect would shift the expectation towards the measurements.}}
+In both panels, we use blue open circles to show the expected bias of the median value for $\Delta \log$\mbh.
+We use framework of \citet{Schulze2011,Schulze2014} to show that even with no evolution selection effects would shift the expectation higher towards the measured values as indicated by the small arrow (Section~\ref{sec:sf_framework}.)}
 \end{figure*}
@@
 To quantitively make this comparison, we calculate the intrinsic scatter of their offset value, based on Equation~\ref{eq:infer_value}, and obtain $0.33$ for high-$z$ and $0.40$ for local samples, respectively.
-The fact that the intrinsic scatter for the high-$z$ sample is no larger than the local one is against the scenario where the random merger is the origin of the correlation \citep{Peng2007}, indicating that there is likely to be a connection between the SMBHs and their host galaxies during their formation.
+The fact that the intrinsic scatter for the high-$z$ sample is no larger than the local one may pose a challenge for explanations of scaling relations where random mergers are the origin of the correlation \citep{Peng2007,Jahnke2011}, indicating that there may likely be a connection between the SMBHs and their host galaxies during their formation.
 
@@
 Histogram of the $\log($\mbh$)$ offset for the local samples and our 32 high-$z$ sample.
-{\bf The gray vertical line shows the mean value of the offset for the high-$z$ sample, and the red vertical line shows the shift the expectation by the selection effect, even if there were no evolution.} The median value of the offset is very close to the mean value ($+0.30$).
+The gray vertical line shows the mean value of the offset for the high-$z$ sample, and the red vertical line shows the shift the expectation by the selection effect, even if there were no evolution.
+The median value of the offset is very close to the mean value ($+0.30$).
 }
@@
 
-In order to further evaluate the ``true" underlying evolution and its uncertainty, corrected for selection effects, taking into account the actual observations, we adopt an independent method based on the approach introduced by \citet{Tre++07} and developed by \citet{Ben++10}, \citet{Park15} and \citet{Ding2017b}.
+To further evaluate the ``true" underlying evolution and its uncertainty, corrected for selection effects, taking into account the actual observations, we adopt an independent method based on the approach introduced by \citet{Tre++07} and developed by \citet{Ben++10}, \citet{Park15} and \citet{Ding2017b}.
 The method parametrizes the evolution of the correlations between \mbh\ and host properties as an offset from the local one $\gamma$, and an intrinsic scatter \sint, which can be a free parameter or tied to the local relation.
@@
 \caption{\label{fig:select_effect} 
-Taking selection effects into account, figure illustrate the constraining on the evolution factor $\gamma$ of \mbh-\smass\ relation by Equation~\ref{eq:offset}, with intrinsic scatter \sint, using Monte Carlo simulation.
+Constraining the evolution factor $\gamma$ of \mbh-\smass\ relation (Equation~\ref{eq:offset}), with intrinsic scatter \sint, using a Monte Carlo simulation.
 The adopted sample includes our 32 AGNs and the intermediate redshift AGNs, using flat prior of \sint\ ({\it left} panel) and lognormal prior ({\it right} panel).
@@
 Considering that a significant stellar component of the high-$z$ AGNs have a disk component (i.e., AGN hosts with fitted \sersic\ index close to 1),  \smass$_{\rm , bulge}$ must be smaller than \smass$_{\rm ,total}$.
-
-Given that the structures of our 32 AGN hosts are similar to inactive
-galaxies at the same redshifts and stellar masses
-(Section~\ref{sec:result-hosts}), we expect their B/T ratios follow
-a similar distribution which can be estimated using a single-\sersic\
-index \citep{Bruce2014}. We can then infer the bulge stellar mass of our
-AGN host, based on the B/T estimation.
-
-Under these assumptions, we first collect the relation between the
-single-\sersic\ index and B/T ratios for CANDELS inactive galaxies
-at the similar mass level, i.e., \smass$\in [9.0, 11.5]$, using B/T
-measured by \citet{Dimauro2018}. {\bf We then adopt the Monte Carlo approach
-and take a random sample of the \sersic\ index for each AGN, based on their
-inference in Table~\ref{tab:result_sersic}. In the next step, we randomly
-sample the B/T ratio based on its distribution in \citet{Dimauro2018}
-at the sampling \sersic\ index. To avoid any unphysical faint bulge flux, we
-set the lower limit for B/T ratio as $0.1$. 
-To demonstrate the expected B/T ratio, we plot its averaged value at
-different \sersic\ index, as shown in Figure~\ref{fig:BT-n_relation}. 
-We list the sampling result for the \bmass\ in Table~\ref{tab:result_sersic}.
-
-In each realization, we compare the
-\smass$_{\rm, bulge}$ to that of the \mbh\ and estimate the offset and $\gamma$. 
-We take 10,000 times of realization to make sure the distribution of
-random sampling has become stable. Note that the Monte Carlo approach would
-take the scatter into account, including the \sersic\ index
-and its relation between B/T ratio.
-}
+Given that the structures of our AGN hosts are similar to inactive galaxies at equivalent redshifts and stellar masses (Section~\ref{sec:result-hosts}), we expect their B/T ratios to follow a similar distribution that can be estimated using a single-\sersic\ index \citep{Bruce2014}.
+We can then infer the bulge stellar mass of our AGN hosts based on the inferred B/T ratios.
+
+First, we establish a relation between the single-\sersic\ index and the B/T ratio using inactive galaxies from CANDELS at similar redshifts and stellar masses (Figure~\ref{fig:BT-n_relation}; \smass$\in [9.0, 11.5]$) using the B/T measurements of \citet{Dimauro2018}.
+In the figure, the red line indicates the average B/T ratio at a given \sersic\ index.
+We then implement a Monte Carlo approach by randomly sampling a Gaussian \sersic\ distribution for each AGN in our sample based on our measurements with 1$\sigma$ errors (Table~\ref{tab:result_sersic}).
+Next, we randomly sample the associated B/T ratio for a given \sersic\ index.
+To avoid the case of an unphysical faint bulge flux, we set the lower limit for B/T ratio as $0.1$.
+In each realization, we compare the \smass$_{\rm, bulge}$ to that of the \mbh\ and estimate the offset and $\gamma$.
+We use 10,000 realizations to make sure the distribution of random samples is stable.
+Note that the Monte Carlo approach would take the scatter into account, including the \sersic\ index and its relation with the B/T ratio.
+We list the resulting bulge masses \bmass\ in Table~\ref{tab:result_sersic}.
 
 As expected, we find a stronger offset of
-$0.77\pm0.08$~dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
+$\Delta \log \mathcal M_{\rm BH}^{bulge} = 0.77\pm0.08$~dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
 local relation, which corresponds to an evolutionary trend with
 $\gamma = 1.86\pm0.30$. Since selection effects are independent of B/T in
-our framework, we can apply our prior estimate of the selection
-effect correction by removing $0.21$~dex, leaving still a significant offset
-of $0.56$~dex. {\bf We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
-the Monte Carlo approach in Figure~\ref{fig:gamma_hist}. Same as
-Figure~\ref{fig:MM-vz}, we illustrate the offset between bulge and BH
-as a function of redshift, in Figure~\ref{fig:MM_bulge-vz}.}
+our framework, we can apply our prior estimate of the correction for selection effects by removing $0.21$~dex, leaving still a significant offset
+of $0.56$~dex. We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
+the Monte Carlo approach in Figure~\ref{fig:gamma_hist} and illustrate the offset between bulge and BH
+as a function of redshift in Figure~\ref{fig:MM_bulge-vz}.
 
@@
 based on optical data of a smaller sample of 11 objects in the same
-redshift range \citep[see][for similar results]{SS13, Jah++09, Cisternas2011}.
-
-We list the inferred $\gamma$ using the different sample combinations in this section in
+redshift range \citep[see][for similar results]{SS13, Jah++09, Cisternas2011}. We list the inferred $\gamma$ using the different sample combinations in this section in
 Table~\ref{table:diff_sample_gam}.
@@
 The red curve is the averaged B/T ratio at different \sersic\ index.
-{\bf Note that this curve is only for demonstrating the expected B/T value at different \sersic\ index.
-In this work we adopt the Monte Carlo approach to randomly sample the B/T to account for the scatter.}
+Note that this curve is only for demonstrating the expected B/T value at different \sersic\ index.
+In this work we adopt the Monte Carlo approach to randomly sample the B/T to account for the scatter.
 }
@@
 Same as Figure~\ref{fig:MM-vz}, but for \mbh-\bmass\ relations.
-{\bf For intermediate sample, \citet{Cisternas2011} haven't provide any inference for the bulge; the intermediate sample is consist of 27 objects by \citet{Bennert11} and \citet{SS13}.}}
+The intermediate sample consists of 27 objects from \citet{Bennert11} and \citet{SS13}.
+\citet{Cisternas2011} do not provide information to infer their bulge mass.}
 \end{figure*}
@@
 
-We find the average ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, by a factor of $\sim2.5$ and $\sim2.0$ respectively, as compared to that in the local universe.
+We find the average "observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, by a factor of $\sim2.5$ and $\sim2.0$ respectively, as compared to that in the local universe.
 However, taking into account selection bias, these correlations are consistent with those in the local universe within the 95\% confidence limits.
@@
 
-Considering the bulge component instead to be the main driver of the local correlations \citep{Bennert11, Woo++08}, we find that our high-$z$ AGN sample has significantly lower mass/luminosity bulges at fixed black hole mass than in the local universe.
+Considering the bulge component \citep{Bennert11, Woo++08} separately, we find that our high-$z$ AGN sample has significantly lower mass/luminosity bulges at fixed black hole mass than in the local universe.
 Comparing to their \mbh, we find evolution with the ratio evolving as $(1+z)^{1.86\pm0.30}$, which is significant even when accounting for selection effects.
@@
 \section*{Acknowledgments}
+
 Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
-These observations are associated with programs
-\#15115. Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555.
-
-The authors fully appreciate the discussions with Hyewon Suh, Takahiro Morishita and Peter Williams.
-
-XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT. VNB gratefully acknowledges assistance from a NASA grant associated with HST proposal GO 15215.
+These observations are associated with programs \#15115.
+Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555.
+The authors fully appreciate input from Luis Ho, Renyue Cen, Hyewon Suh, Takahiro Morishita and Peter Williams.
+XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
+VNB gratefully acknowledges assistance from a NASA grant associated with HST proposal GO 15215.
+JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
+A.S.
+is supported by the EACOA fellowship.
 
@@
 \tablewidth{0pt}
-\tablecaption{Inferred BH properties for the 32 systems} 
+\tablecaption{AGN properties} 
 \tablehead
@@
 \colhead{Target ID}&
-  \multicolumn{4}{c}{using emission line \halpha}&
-  \multicolumn{4}{c}{using emission line \hbeta} \\
+  \multicolumn{4}{c}{\halpha ~emission line}&
+  \multicolumn{4}{c}{\hbeta ~emission line} \\
   \cline{2-5}  \cline{6-9} \\
@@
 \tablewidth{0pt}
-\tablecaption{Host inference of CID1174} 
+\tablecaption{Host galaxy measurements of CID1174} 
 \tablehead{ 
@@
 \tablewidth{0pt}
-\tablecaption{Inferred host galaxy properties for the 32 systems.} 
+\tablecaption{Host galaxy properties} 
 \tablehead
@@
   \multicolumn{3}{c}{ACS/F814W} &
-   \multicolumn{2}{c}{host properties} \\
+   \multicolumn{2}{c}{Derived properties} \\
   \cline{2-6}  \cline{7-9} \cline{10-12}  \\

### 2019-09-03 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
Move folder place

\documentclass{natureprintstyle}
%\documentclass{nature}
\bibliographystyle{naturemag}
\usepackage{epsfig,caption}
\usepackage{color}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{amssymb}
\usepackage{rotating}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{float}

%\usepackage[switch]{lineno}
%\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% comment for selecting the best figures to go on web for:
%@arxiver{jvds_sami_vsigma_ellip_LOESS_Age_paper.pdf,jvds_sami_vsigma_ellip_LOESS_Age_transform_paper_resubmit.pdf} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%journal commands
\newcommand{\apj}{Astrophys. J.}
\newcommand{\spie}{Proc. SPIE}
\newcommand{\pasp}{Publ. Astron. Soc. Pac.}
\newcommand{\apjs}{Astrophys. J. Supp.}
\newcommand{\araa}{Annu. Rev. Astron. Astrophys.}
\newcommand{\mnras}{Mon. Not. R. Astron. Soc.}
\newcommand{\apjl}{Astrophys. J. Let.}
\newcommand{\aap}{Astron. Astrophys.}
\newcommand{\aj}{Astron. J.}
\newcommand{\nat}{Nature}
\newcommand{\na}{New Astron. Rev.}
\newcommand{\aaps}{A\&AS}
\newcommand{\procspie}{Proc. SPIE}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% my commands

\newcommand{\lcdm}{$\Lambda$CDM}
\newcommand{\hst}{{\it HST}}
\newcommand{\efr}{$R_{\mathrm{eff}}$}
\newcommand{\galfit}{{\sc Galfit}}
\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\lhost}{$L_{\rm host}$}
\newcommand{\mr}{$Mag_{\rm ~R}$}
\newcommand{\jcap}{Journal of Cosmology and Astroparticle Physics}
\newcommand{\halpha}{${\it H}\alpha$}
\newcommand{\hbeta}{${\it H}\beta$}
\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{{\sc Lenstronomy}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
%\newcommand{\kms}{km~s$^{\rm -1}$}
\newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
\newcommand{\sigstar}{{$\sigma_*$}}
\newcommand{\mstar}{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{
%From predictions to observation: scaling relations between supermassive black holes and their host galaxies at $1< z<2$
A successful observational test of black hole and galaxy co-evolution models since $z\sim1.7$
%The first comparison between the observation and simulation of the scaling relations between supermassive black holes and their host galaxies at $1.2< z<1.7$
}
\author{Xuheng Ding$^{1,2}$, 
Tommaso Treu$^{1}$, 
John Silverman$^{3, 4}$,
Aklant K. Bhowmick$^{5}$,
N. Menci$^{6}$,
Tiziana Di Matteo$^{5}$,
et. al.
}

\begin{document}

\maketitle

\let\thefootnote\relax\footnote{
\begin{affiliations}
\item {Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA} 
\item {School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\item {Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
\item {Department of Astronomy, School of Science, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan}
\item{McWilliams Center for Cosmology, Dept. of Physics, Carnegie Mellon University, Pittsburgh PA 15213, USA}
\item{INAF?Osservatorio Astronomico di Roma, via Frascati 33, I-00078 Monteporzio, Italy}
\end{affiliations}
}

\begin{abstract}
Supermassive black holes (BH) harbor at the center of galaxies with their masses correlated to the properties of the host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar) known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar). Observational results have indicated evidence that this correlation evolves with cosmic time, suggesting a scenario that the BH growth predates their host. In theory, positive evolution of BH is also predicted by several simulation projects independently. So far, the simulations have reproduced the relations which have a good agreement to the observational sample from local to intermediate redshift ($0.3<z<1$). It is crucial to extend this study to higher redshift ($z>1$), where the predicted relations are more sensitive to the initial simulating assumptions and any inconsistency could help to pinpoint the incorrect ones.
To this end, we use a sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) to make a direct comparison to the predicted sample from two independent state-of-the-art simulating projects, including MassiveBlack-II (MBII) and semi-analytic models (SAMs). We use \hst\ observed images to study the 32 AGNs in multi-bands and deriving the trustworthy stellar mass measurements and the reliable broad \halpha\ emission lines to estimate the \mbh. Taking the selection bias into account, %by adopting the same selection function to choose the simulating sample,
we find that both models agree well with the data, even though they use very different recipes. These agreements indicate the existence of a causal connection between BH and the host galaxy, which could not be explained by purely a stochastic process. To some extent, our result attests that this connection induces an ordering so that the more massive black holes are linked to the more massive masses. Moreover, we find the intrinsic scatter of our high-$z$ sample is not larger than the simulations and local ones, which is against the central limit theorem.

\end{abstract}

%\section{Introduction}
The discovery of the correlations between the masses (\mbh) of supermassive black holes (SMBH) and the properties of their host galaxies, such as absolute magnitude ($Mag$) and stellar mass (\mstar), indicates that the growth of BH could be connected to its host galaxy formation. So far, the origin that drives this connection is still unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim$10 kpc). A dominant interpretation is so-called AGN feedback, assuming that a small fraction of AGN energy injects to their surrounding gas that regulates the growth of SMBH and its host galaxy. In this scenario, the activity of AGN accretion heats and unbinds significant fractions of the gas and inhibits star formation. Some models have been proposed that the connection between SMBH and its host are connected not in a direct manner but assuming that they share a common gas supply~\cite{Cen2015, Menci2016}. On the other hand, without any physical mechanisms, the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations. In this central limit theorem, a stochastic cloud at high-$z$ (higher scatter) would end up with the scaling relations (lower scatter) as observed today.

To understand this connection, the recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have analyzed the scaling relations beyond the local redshift {($0.3<z<1$)} with active galactic nuclei (AGN) using {\it Hubble Space Telescope} ({\it HST}) and found an evolution that the growth of SMBHs predated to their host galaxies. However, the observational evidence of evolution at high-$z$ is under debated as it relies on our understanding of systematic uncertainties and selection effects. It has been realized that the improper way to consider the uncertainties and selection effects could result in an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.

%Why comparison between data and model.
%Summary of recently works.
%The reason to extend to high redshift.
Simulating models are the effective tools that help to understand this connection and rule out the assumptions which could not be satisfied with the observations. In the simulating test, the systematic uncertainties and selection bias would be easy to account for. Recent simulating studies by several projects have made predictions which is in good agreement with the analysis by the observations at intermediate redshift range. For example, the state-of-the-art cosmological hydrodynamical simulations of structure formation (MassiveBlackII) have compared the predicted scaling relations to the \hst\ observation at $0.3<z<1$ and predict a positive evolution that SMBH growth predates the host galaxy~\cite{DeG++15}. Several others works have investigated the scaling relations using large-volume simulations, also well matching the local relation with some redshift evolution, including approaches using the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014}. Besides hydrodynamic simulations, semi-analytic models~\cite{Menci2014, Menci2016} also have made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}. However, to date, the comparisons to the high-resolution (i.e., \hst) sample were still limited at $z<1$ due to the limitation of the observations.

%A good way to understand this connection is to rely on active galactic nuclei (AGN) and trace the scaling relations to higher redshifts, witnessing how and when does it happen. More recently, there is increasing observational evidence indicating the positive offset exist in the correlation at intermediate redshift range ($0.3<z<1$), implying that galaxies built up around the massive potential wells of mature BHs. Stimulated by the observations, theoretical efforts have been made to include the growth of \mbh\ in the framework of cosmological galaxy formation simulations, and generated the predictions of local scaling relations which match the observations well. Moreover, the simulations predict that the positive offset could be even stronger at redshift range $1<z<2$.

%Using the samples predicted by the simulation to compare to the observations is beneficial, in particular at high redshift. First, it helps to directly verify the validity of the initial physics prescriptions adopted in the simulation process, and point out the direction where to improve if needed. Second, in turn, the lessons learned in the simulations could be used to investigate the mechanism of the origin of the scaling relation. For example, the feedback originating in the surroundings of BHs, the major merging activities, and the growth of the \mbh\ and the stellar components as connected to the common gas supply have been invoked as the process leading to the co-evolution. Extending the comparison to high redshift help to explore the origin of the evolution directly. Furthermore, adopting the same selection function enable the particular comparison between two equivalent sample, so as to get rid of the systematic bias lead by the selection effects.

% The work that we want to do
	%Sample selection
	%The advantage of our measurements
	%Compare to which simulation? (some introduction)
	%Any expectation?
	%mention the scatter.
To extend, we collected a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}, to compare to the simulating models. The redshift range of our targets is chosen to be high enough ($z>1$) to detect the existence of the evolution offsets and make the comparison to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming. We selected our AGN sample in a well-defined window as in Figure~\ref{fig:AGN_select}, based on the \mbh\ and Eddington ratio. As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias and the Eddington ratio are above the 1\% level to ensure the homogeneity.

We measure reliable \mbh\ and host properties to overcome the systematic. Specifically, the \mbh\ of our sample are estimated using the published near-infrared spectroscopic observations of the broad \halpha\ emission lines, which removes the systematic with \Mgii\ or \Civ. For the inference of properties of the host galaxies, the X-ray selected sample has lower nuclear-to-host ratios at IR band, which facilitates the inference of the host light. We employ the \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt the state-of-the-art technique to perform the 2-D flux profile decomposition to infer the light of the host galaxy. Moreover, 21/23 systems have \hst/ACS imaging data, which enable us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar). 
%We furthermore combining them with the ground-based photometry to carry out the SED fitting, and thus derive the reliable host rest-frame R band luminosity and stellar mass.

\begin{figure}[t]
\includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
\caption{The selection function as used for choosing the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function.
}
\label{fig:AGN_select}
\end{figure}

To make the comparison to the simulating models, we adopt two independent simulating projects, including MassiveBlack-II (MBII) and semi-analytic models (SAM). These two models are based on independent model strategies, i.e., hydrodynamic simulation for MBII and semi-analytic model for SAM, respectively. The MassiveBlack-II (MBII) simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback. The large simulation volume enables the simulating objects to evolve independently; the high enough mass and spatial resolution meet the requirements for the object details. On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems. However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as (SAM). 
MBII and SAM have made successful predictions in previous works \cite{Menci2014, Menci2016, Khandai2015}. We refer the interested readers to these works for more details.

%\section*{Results}
%Selection effect into account
We collect the scaling relations by a comparable AGN sample in the MBII to compare with the observed ones. The simulated sample is selected at $z=1.5$ using a comparable selection window, as shown in Figure~\ref{fig:selectfunc}. We investigated the predicted relations of the \mbh-\mr\ and \mbh-\mstar\ by the MBII and compared to the observational constraints. In Figure~\ref{fig:MBII_comp}, we show the comparisons of both relations and find that the predicted scaling relations have an excellent agreement to the observations. We carry out the linear fitting of the observed sample and the {\it selection-effect-considered} sample using the same slope value. The mismatch of the interceptions between the two lines are relatively small within $1-\sigma$ level. We adopt the {\sc Limnux} to estimate the intrinsic scatter of both the sample. Interestingly, we find the observed sample have an intrinsic scatter of $0.13$~dex, which is even smaller than the one in the simulation, which is $0.23$~dex.

\begin{figure}[t]
\includegraphics[width=1.0\linewidth]{MBII_selectfunc.pdf}
\caption{The selection window as adopted for selecting the MBII simulated sample. The blue background clouds shows the overall sample at $z=1.5$. The sample that only located in the selection windows are selected, labeled red.
}
\label{fig:selectfunc}
\end{figure}
%comparison to simulation (flux ratio also)

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[height=0.5\linewidth]{MBII_ML_.pdf} &
\includegraphics[height=0.5\linewidth]{MBII_MM_.pdf} \\
\end{tabular}
\caption{
Comparing the scaling relations between the observed scaling relations to the predicted samples by the MBII simulation. In the left and right panel, we present the \mbh-\mr\ and \mbh-\mstar\ correlation, respectively. The blue grids are the overall galaxies that predicted in the MBII simulation and the red ones are selection effect considered. We red line shows the best-fit linear relations for the simulated selected sample. We fix the slope value to fit for the observed sample and find that the mismatch of the interceptions are within $1-\sigma$ difference for both relations. {\bf For the right panel, I currently adopt a 3 Gyrs template for the HST sample...}
}
\label{fig:MBII_comp}
\end{figure*}

The comparisons between the observed scaling relations to the SAM model are presented in Figure~\ref{fig:SAM_comp}. Rather than predict each individual simulated sample, the SAM model describes the possibility clouds to demonstrate the density distribution of the scaling relations. We use two sets of color contours to demonstrate the possibility distribution at $z=1.5$ epoch, before and after adopting the selection window. The comparisons show great consistency that the hot zones in the SAM {\it selection-effect-considered} contours at $\log($\mbh$)~\in[7.5, 8.56]$ are well matched to the observed relations. We do not estimate the scatter for SAM model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one.

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[trim = 0mm 0mm 26mm 0mm, clip, width=0.45\linewidth]{SAM_ML.pdf} &
\includegraphics[trim = 24mm 0mm 0mm 0mm, clip, width=0.45\linewidth]{SAM_MMstar.pdf} \\
\end{tabular}
\caption{ Similar to the Figure~\ref{fig:MBII_comp}, we compare the observation to the SAM models. The blue background contours show the overall sample distribution and the red ones are the relations after considering the selecting effect. We see that the yellow contours are well matched to the hot zones for the red contours.
}
\label{fig:SAM_comp}
\end{figure*}

To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples. For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3. For the simulated sample, we consider the AGN bolometric correction~\cite{Elvis1994} to estimate the AGN light flux at WFC3/F125W band. We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched each other. The median values for the flux ratio distribution of the observed, MBII, SAM sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively. We perform the Kolmogorov-Smirnov test the inferred p-values are 0.34 (for observed -- MBII) and 0.14 (for observed -- SAM), respectively. {\bf More interpretations}.

\begin{figure}[t]
\includegraphics[width=0.9\linewidth]{comp_host_ratio.pdf}
\caption{The comparison histogram of the host ratios among three referred samples, with median value indicated. The same selection effect are considered.
}
\label{fig:comp_hist}
\end{figure}

Without any physical mechanisms, the central limit theorem assumes that the scaling relations are the results by the random merger from a stochastic cloud at higher redshift. In this scenario, the scatter of the scaling relations has to be larger at higher redshift. However, the observed scatter of our high-$z$ sample do not present this feature. In fact, the obtained intrinsic scatter is only $\sim0.13$~dex, which is no more than the typical scatter at local relations in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}. Of course, the intrinsic scatter of our high-$z$ sample could be underestimated, since manually selected sample avoids the spreading of the properties and decrease the value of the scatter. Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), result in an overestimating of the error-budget and thus underestimating of intrinsic scatter. Still, even we do not take the uncertainties into account to calculate the scatter, the obtained value is $0.25$~dex, which is not larger than the local relations. Thus, the evidence of the low scatter in our measurements is likely to be true, which is against the central limit theorem and suggests that the physical mechanisms between the SMBH and its host galaxy are likely to exist.

Between the MBII and SAM models, they all demonstrate an excellent agreement to the observed data; however, they adopted very different assumptions, recipes, and initial conditions. From another perspective to understand this agreement, there has to be a causal link between SMBH and its host galaxy to generate an ordering during their evolution, so that more massive BHs are linked to more massive galaxies with some intrinsic scatter. Once the selection function is well defined, the tight correlations would show up along with the selected sample.

Limited by the observations and the fact they are in good agreements to MBII and SAM, one can not rule out one simulating model from the other. Of course, there are differences between two simulating models. For example, the SAM sample trends to have more scatter than the MBII, especially before applying any selection function. More scatter could arise in SAM because the black hole feeding in this model is merger driven and so there is more stochasticities. In particular, the SAM cloud extends to the high \mbh\ with low stellar mass, which may not exist. These objects are usually with low Eddington ratio; thus an extension of this study to this region would be useful to discriminate between models.

Extending the redshift range of this study would also be very beneficial, giving that the scaling relation in the simulations shows different evolution at the different stage of the Universe. For higher redshift, the {\it James Webb Space Telescope} may provide high-quality imaging data of AGNs at redshift up to $z\sim7$. In the low redshift Universe, wide-area surveys with Subaru/HSC, LSST, and WFIRST offer much promise to build samples for studying these mass ratios and dependencies on other factors (e.g., environment).

%\textcolor{blue}{The details of the results could be presented.\\
%0. Compare the color of the sample?\\
%1. 2D KS test? \\
%2. More insightful inference from the comparing?
%}

%Discuss the result, What does this mean?

% \textcolor{blue}{If the final results show such feature:}
%The result also shows that the \mbh-\mstar\ relation has less scatter than the \mbh-\lhost\ relation, suggesting that the BH relation with \mstar\ are more fundamental than \lhost.
%This successful experience leads one conjecture that the other prediction by the simulations could likely to be right. For example, regarding the stellar components of galaxy which is the origin that related to the growth of BH, it is likely that the bulge masses are tightly related.

%\section*{Discussion}
%Some discussions should be placed in this section.
%On the observation side:\\
%0. The inferred host flux ratio by SED decomposition is consistent to the 2-D image decomposition, indicating the fidelity of these approaches?\\
%1. HST seems to reach its higher limit. In the future, the JWST is very promising to realize the evolution scenario at even higher redshift.\\
%On the simulation side:
%\\0. Introduce some the other 
%\\1. How do we discuss the role of AGN feedback?.

\begin{center}
{\bf \Large \uppercase{Methods} }
\end{center}

%\textbf{Observation data.} Our 32 new AGN systems are selected from four X-ray coverage fields including COSMOS (Civano et al. 2016), (E)- CDFS-S (Lehmer et al. 2005; Xue et al. 2011), and SXDS (Ueda et al. 2008) at redshift range $1.2<z<1.7$. The X-ray selected sample have low nuclear-to-host ratios, which facilitates the extraction of the host properties. We adopt the \hst/WFC3 infrared channel to derive the high spatial resolution imaging data, to carry out the decomposition of the AGN-host using two-dimensional flux distribution. The details of the \hst\ observation and the study are presented in the companion paper. Moreover, 21/32 systems have \hst/ACS band, together with some other ground-based observations, which would provide the host information in the other bands. In the next section, we infer the reliable K-correction for the rest-frame R band luminosity and the SED to infer the stellar mass. The \mbh\ of our sample have been estimated by \halpha\ and \hbeta\ in the FMOS survey. Comparing to the \Mgii\ and \Civ, the \mbh\ by broad Balmer lines are more trustworthy. The estimated value of the \mbh\ are listed in the companion paper.
%\textcolor{blue}{Do we need to list the \mbh\ and host properties in a table in this paper?}

\textbf{Imaging data, decomposition and inference of host properties.} 
%1. Imaging data. 2. Inferring host light. 3. Color inference. Rest frame R band and stellar mass.
We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets, to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman). We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to co-add the final image with pixel scale as 0\farcs0642. To mitigate the contamination from both the sky and the detector, we adopt the {\sc photuils} tools to estimate and remove them accurately.

To address the bias which might be raised by the unknown PSF, we manually collect the isolated-unsaturated PSF-stars from the 32 observed fields, to assemble a PSF library for the fitting. To decompose each AGN image, we assume the unresolved active nuclei as the scaled point source and the host galaxy as the \sersic\ profile. We adopt imaging modeling tool \lenstronomy\cite{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one by one from the library. Based on the reduced $\chi^2$, we are capable of evaluating the performance of each PSF. We adopt the result from the top-eight PSFs and infer the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.

21/32 images in the COSMOS survey also have imaging data in the ACS/F814W with drizzled pixel scale as 0\farcs03, providing us the multi-band information. We decompose the AGN image in the ACS band to obtain the color of the host. We find that the 1Gyr template would well match their color from which we estimate the rest-frame R band luminosity and stellar mass.

%\textbf{SED fitting and host properties}
%We perform the SED fitting to derive the robust physical properties of the host galaxy, including the rest-frame R band luminosity and stellar mass. 
%21/32 AGN systems have rest-frame UV imaging data by \hst-ACS/F814W\cite{Scoville2007}. We perform the same approach to decompose the photometry of the host light at UV. Since the host inference by IR band is superior to the one by UV band, while fitting UV image, we fix the \reff\ and \sersic\ index as the value inferred by \hst/WFC3 to derive the host flux.
%We furthermore combine the \hst\ inference to the ground-based AGN photometry to carry out the SED fitting. \textcolor{blue}{Details and the figures need to be presented.}
%Adopting the best fit SED stellar template to the \hst/WFC3 flux, we derive the \lhost${,_R}$ and \mstar.

\textbf{Simulations.} 
Describe the approaches used in the simulation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{References}
\bibliography{references}

\begin{addendum}
 \item[Acknowledgements] 
%X. Ding acknowledges support by China Postdoctoral Science Foundation Funded Project (No. 2017M622501).

%
\item[Correspondence] %Correspondence and requests for materials should be addressed to Xuheng Ding ~(email:dxh@astro.ucla.edu).
\item[Author Contributions] xxx measure xxx, xxx extract the simulation from xx.
\end{addendum}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Additional information}
\textbf{Code availability.} The \lenstronomy, which is used to decompose the AGN image  
%The data reduction package used to process the SAMI data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr. To derive the stellar kinematic parameters and the lick absorption line strengths, we use the publicly available penalised pixel-fitting (pPXF) code from M. Capppellari: {http://www-astro.physics.ox.ac.uk/~mxc/software/\#ppxf}. For the adaptive LOESS smoothing, we use the code from M. Cappellari obtained from: http://www-astro.physics.ox.ac.uk/~mxc/software/\#loess

\textbf{Data availability.} All the inference of the AGN properties are presented in the companion paper.
%All reduced data-cubes in the GAMA fields used in this Letter are available on: http://datacentral.aao.gov.au/asvo/surveys/sami/, as part of the first SAMI Galaxy Survey data release. Stellar kinematic data products will become available in the second SAMI Galaxy Survey data release.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\clearpage
%\newpage
%\onecolumn
%\begin{center}
%{\bf \Large \uppercase{Supplementary information} }
%\end{center}
%
%\setcounter{figure}{0}
%\vspace{2cm}
%
%\begin{figure}[!h]
%\begin{center}
%\includegraphics[width=0.8\linewidth]{hst_sample_bhmf.pdf}
%\caption{
%The selection function of our observation data. Eddington ratios (LBol/LEdd) and BH masses (bottom panel) of our sample (in color) that fall well-below the knee of the BH mass function at z = 1.5 (top panel; Schulze et al. 2015). Dashed lines (vertical and horizontal) denote our selection window with the slanted line only shown to approximately illustrate the effect of a luminosity limit, inherent in the parent catalogs. For reference, we indicate the high-z luminous SDSS QSO samples (grey squares - Peng et al. 2006; grey circles - Decarli et al. 2010) with all falling above our chosen upper mass limit.
%}
%\label{fig:support}
%\end{center}
%\end{figure}

\end{document}

### 2019-09-03 NA_paper/manuscript_II/apj_temp/manuscript.tex
Move folder place

\documentclass[twocolumn]{aastex62}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand\s{$\sim$}
\newcommand{\e}{\'{e}}
\newcommand{\amen}[1]{\textbf{\textit{#1}}}

\usepackage{xcolor}

\shorttitle{From predictions to observation}
\shortauthors{Marian et al.}

\begin{document}

\def\lcdm{$\Lambda$CDM}
\def\hst{{\it HST}}
\def\efr{$R_{\mathrm{eff}}$}
\def\galfit{{\sc Galfit}}
\def\mbh{$\mathcal M_{\rm BH}$}
\def\lhost{$L_{\rm host}$}
\def\jcap{Journal of Cosmology and Astroparticle Physics}
\def\halpha{${\it H}\alpha$}
\def\hbeta{${\it H}\beta$}
\def\sersic{S\'ersic}
\def\lenstronomy{{\sc Lenstronomy}}
\def\Reff{{$R_{\mathrm{eff}}$}}
\def\kms{km~s$^{\rm -1}$}
\def\sigstar{{$\sigma_*$}}
\def\smass{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}

\title{From predictions to observation: scaling relations between supermassive black holes and their host galaxies at $1< z<2$}

\correspondingauthor{Xuheng Ding}
\email{dxh@astro.ucla.edu}

\author%[0000-0001-8917-2148]
{Xuheng Ding}
\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-
1547, USA}
\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}

\author%[0000-0001-8917-2148]
{Tommaso True}
\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-
1547, USA}

\author%[0000-0001-8917-2148]
{John Silverman}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

\author{ET AL.}

\begin{abstract}
Recent observations have discovered the \mbh-host relation which are likely to be evolving as a function of redshift. This evolution trends are also emerged in the simulations. A direct comparison between the observation and simulation is important to help understand the insight of the their physical coupling and their growth. The simulating result would also help to correct the selection effect in the observation.
Here, we use the scaling relation using 32 X-ray-selected broad-line (type-1) AGN at $1.2 < z < 1.7$ and compare to the simulation. We decomposition the AGN image using state-of-art to infer the host luminosity and combining multi-band AGN luminosities to infer the stellar mass. We adopt the same selection function as the 32 AGNs to select two group of AGN samples from two state-of-the-art simulation projects, MassiveBlack-II (MBII) and semi-analytic models (SAMs). %MBII is the highest resolution simulation of this size which includes a self-consistent model for star formation, black hole accretion and associated feedback. The SAMs is ... 
We study the \mbh-\lhost and \mbh-\smass\ and find that simulating samples by the two simulations are well agree with the observations. Given that the relation of our high-z samples are offset to the local, we further track the histories of the simulating samples and investigate the origin of their relation and evolution.

\end{abstract}

\keywords{keywords TBD}

\section{Introduction} \label{sec_intro}
The MBH-HOST relation by observation.

Introduce the mechanisms which could lead to this evolution.

In theory, the simulations have shown the similar trend, which could be a way to understand this relation and evolution.

In this work, we compare the observation to two state-of-the-art simulation projects.

Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} =
0.70$. Magnitudes are given in the AB system.

%\begin{figure*}[t]
%\centering
%\includegraphics[width = 18cm]{f01.pdf}
%\caption{Example of showing something.\textit{Left}: The some thing \textit{Right}: The some thing.}
%\label{fig:QSO_sample}
%\end{figure*}

\section{Comparison sample} \label{data}

\subsection{Observation data} 
We selected 32 new AGN systems from four X-ray coverage fields including COSMOS (Civano et al. 2016), (E)- CDFS-S (Lehmer et al. 2005; Xue et al. 2011), and SXDS (Ueda et al. 2008) at redshift range $1.2<z<1.7$. The X-ray selected sample have low nuclear-to-host ratios, which facilitates the extraction of the host properties. We adopt the \hst/WFC3 infrared channel to derive the high spatial resolution imaging data, to carry out the decomposition of the AGN-host using two-dimensional flux distribution. The details of the \hst\ observation and the study are presented in the companion paper. Moreover, 21/32 systems have \hst/ACS band, together with some other ground-based observations, which would provide the host information in the other bands. In the next section, we infer the reliable K-correction for the rest-frame R band luminosity and the SED to infer the stellar mass.

The \mbh\ of our sample have been estimated by \halpha\ and \hbeta\ in the FMOS survey. Comparing to the \Mgii\ and \Civ, the \mbh\ by broad Balmer lines are more trustworthy.
\textcolor{blue}{Do we need to list the \mbh\ and host properties in a table in this paper?}

\subsection{Simulating sample and the selection function} 
To compare with the observation, we adopt the sample from two state-of-the-art simulating projects, i.e., MassiveBlack-II (BHII) and ab-initio semi-analytic models (SAMs).

%Introduce BHII: The high resolution. In paper?, the simulation result shows that the evolution is exists since ... Some other interesting results.
The BHII is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion and associated feedback. The large simulation volume enable the simulating objects evolve independently; the high enough mass and spatial resolution meets the requirements for the object details. A variety of predictions by the simulation have been examined by comparing to the observations, including 
the Galaxy stellar mass function, quasar bolometric luminosity function (Khandai et al. 2015). %More recently, the simulated AGN systems 
%The simulating result:
The GSMF, The AGN bol luminosity; The M-Mstar relations. The AGNs compared to the observation (Aklant two papers).

%Introduce SAMs: Similarly, the simulation of SAMs shows that, the \mbh-host relation have stronger evidence in the bulge than disk...
On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems, but understanding the way of AGN feeding modes requires implementing the physics of nuclear gas inflows into cosmological models of galaxy formation. In turn, this requires an analytical description of such processes to be implemented into existing semi-analytic models.

We adopt a similar selection function to allow a comparing between equivalent samples. We plot the selection function of the observation data the the simulation data, in figure.
\begin{figure}[t]
\centering
\includegraphics[width = 7cm]{hst_sample_bhmf_v8.pdf}
\caption{The selection function of our observation data.
Eddington ratios (LBol/LEdd) and BH masses (bottom panel) of our sample (in color) that fall well-below the knee of the BH mass function at z = 1.5 (top panel; Schulze et al. 2015). Dashed lines (vertical and horizontal) denote our selection window with the slanted line only shown to approximately illustrate the effect of a luminosity limit, inherent in the parent catalogs. For reference, we indicate the high-z luminous SDSS QSO samples (grey squares - Peng et al. 2006; grey circles - Decarli et al. 2010) with all falling above our chosen upper mass limit.
}
\label{fig:obs_selectfunc}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width = 7cm]{BHII_selectfunc.pdf}
\caption{The sample selected from the BHII simulation.
}
\label{fig:bhII_selectfunc}
\end{figure}

\section{Result} 
\subsection{ML relation} 
1. The way to derive the MR magnitude.
2. Comparing the samples.

\begin{figure}[t]
\centering
\includegraphics[width =  7cm]{BHII_ML.pdf}
\caption{M-L relation by BHII }
\label{fig:BHII_ML}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width =  8cm]{SAM_ML.pdf}
\caption{M-L relation by SAM}
\label{fig:SAM_ML}
\end{figure}

\subsection{MM* relation} 
1. The SED to derive the Mstar.
2. Comparing the samples.

\begin{figure}[t]
\centering
\includegraphics[width =  8cm]{SAM_MMstar.pdf}
\caption{MMstar relation by SAM }
\label{fig:SAM_MM}
\end{figure}

\section{Summary \& Conclusions} \label{sec:summary}
We compared the inferred \mbh-host relations and compared with the simulations by

\acknowledgments

X. Ding acknowledges support by China Postdoctoral Science Foundation Funded Project (No. 2017M622501).

\software{
        corner,
        Matplotlib \citep{matplotlib},
        }

\newpage

%\appendix

%\section{section}\label{appendix_section}
%TEXTTEXTTEXTTEXTTEXTTEXTTEXTTEXTTEXT
%\newpage

\bibliography{reference}
%\input{reference.bbl}

\end{document}

### 2019-09-03 Comparsion/Comparison_MBHMR_scatter.py

@@ -1,121 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Mon May 27 08:45:53 2019
-
-@author: Dartoon
-"""
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-
-#%%Define the function to fit theas linear
-def lfit(x,m,c):
-    return m*x+c
-
-import scipy.optimize as op
-def lnlike(theta, x, y, err):
-    a, b, sint= theta
-    model = a * x + b
-    sigma2 = (err**2 + sint**2)
-    if sint>=0 :
-      return -0.5*(np.sum((y-model)**2/sigma2)+np.sum(np.log(sigma2))) 
-    else:
-      return -np.inf
-nll = lambda *args: -lnlike(*args)
-#result = op.minimize(nll, [1.036, -1.947, 0.3], args=(x, y, yerr))
-#m_ml, b_ml,sint_ml= result["x"]
-
-#from scipy.integrate import quad
-#h0=70.             #km/s/Mpc
-#om=0.3
-#c=299790.        #speed of light [km/s]
-#def EZ(z,om):
-#      return 1/np.sqrt(om*(1+z)**3+(1-om))
-#def EE(z):
-#      return quad(EZ, 0, z , args=(om))[0]
-#vec_EE=np.vectorize(EE)
-
-#%%Calculate the scatter for the Aklant MBH-Mr
-plt.figure(figsize=(8,6))
-import scipy
-h=0.7
-#r_band_magnitudes_overall=np.load('Aklant/Aklant_scripts/r_band_magnitude_overall_population.npy')
-r_band_magnitudes_selected=np.load('Aklant/Aklant_scripts/r_band_magnitude_selected_population.npy')
-L_r = (0.4*(4.61-r_band_magnitudes_selected)) #LR in AB
-
-##log10_bhmass_overall=np.load('Aklant/Aklant_scripts/log10_bhmass_overall_population.npy')
-##log10_bhmass_overall -= np.log10(h)
-log10_bhmass_selected=np.load('Aklant/Aklant_scripts/log10_bhmass_selected_population.npy')
-log10_bhmass_selected -= np.log10(h)   #remove the [/h]
[…]

### 2019-09-03 M_BH_relation/local_MM_vz.py

@@ -86,8 +86,6 @@ m_ml, b_ml,sint_ml= result["x"]
 #m_ml, b_ml = 1.12, -4.12  # Park's first use
 #m_ml, b_ml = 1.02, -2.91  # Park's inference from the two sample
 
-xp = np.array([5, 13])
-#plt.plot(xp, m_ml*xp+b_ml, 'r-')
 def lnprior(theta):
     m, b, sint	 = theta
     if -5.0 < m < 5 and -10 < b < 10.0 and 0 < sint < 10:

### 2019-09-03 NA_paper/Aklant/Compare_color_MoverZ.py

@@ -77,3 +77,17 @@ plt.tick_params(labelsize=25)
 plt.ylim([1.2, 2.8])
 plt.legend(scatterpoints=1,numpoints=1,loc=2,prop={'size':24},ncol=1)
 plt.show()
+
+#%%
+plt.figure(figsize=(15, 11))
+plt.scatter((10**Mstar_c/10**R_lumi_c)[zs_c>1.44], (host_mag_ACS_c)[zs_c>1.44],s=680, c ='green',
+            marker="*",zorder=100, vmin=0, vmax=7, edgecolors='white', label='WFC/F140W')
+plt.scatter((10**Mstar_c/10**R_lumi_c)[zs_c<1.44], (host_mag_ACS_c)[[zs_c<1.44]],s=280, c ='green',
+            marker="o",zorder=100, vmin=0, vmax=7, edgecolors='white', label='WFC/F125W')
+plt.ylabel("mag_$_{ACS}$",fontsize=35)
+plt.xlabel("(M_*/M_sun)/(L_R/L_Rsun)",fontsize=35)
+plt.tick_params(labelsize=25)
+#plt.ylim([1.2, 2.8])
+#plt.ylim(23.0, 20.75)  # 
+plt.legend(scatterpoints=1,numpoints=1,loc=2,prop={'size':24},ncol=1)
+plt.show()

### 2019-09-03 NA_paper/scripts/MBHII_ML.py

@@ -1,0 +1,142 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Aug 28 20:15:08 2019
+
+@author: Dartoon
+
+Plot the MBHII MBH-Mr relation and fit their scatter.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import copy
+import sys
+sys.path.insert(0,'../../py_tools')
+from load_result import load_MBH, load_host_p, load_err
+
+import matplotlib.lines as mlines
+from matplotlib import colors
+import matplotlib as mat
+mat.rcParams['font.family'] = 'STIXGeneral'
+
+import matplotlib as mpl
+#data=np.loadtxt('../AGN_host_inference_for_npy.txt')
+#print data
+h=0.7
+
+tab_list = ['CID1174', 'CID1281', 'CID206', 'CID216', 'CID237', 'CID255', 'CID3242', 'CID3570',
+            'CID452', 'CID454', 'CID50', 'CID543', 'CID597', 'CID607', 'CID70', 'LID1273',
+            'LID1538', 'LID360', 'XID2138', 'XID2202', 'XID2396', 'CDFS-1', 'CDFS-229',
+            'CDFS-321', 'CDFS-724', 'ECDFS-358', 'SXDS-X1136', 'SXDS-X50', 'SXDS-X717', 'SXDS-X735', 'SXDS-X763', 'SXDS-X969']
+ext_ID = {'XID2202':'LID1622', 'XID2138':'LID1820', 'XID2396':'LID1878', 'CDFS-321':'ECDFS-321'}
+tab_sub_list = copy.deepcopy(tab_list)
+for i in range(len(tab_sub_list)):
+    if tab_sub_list[i] in ext_ID.keys():
+        tab_sub_list[i] = ext_ID[tab_sub_list[i]]
+Lr, M_star, M_r = load_host_p(tab_list, folder = '../../')  # M_star by Chabrier 
+
+bh_mass_obs = load_MBH(tab_list,tab_sub_list, if_reportHb=0, folder = '../../') #+np.log10(h) 
+stellar_mass_obs=  np.log10(10**M_star / 0.54 * 0.91)#+np.log10(h)
+M_r_obs= M_r
[…]

### 2019-09-03 NA_paper/scripts/MBHII_MM.py

@@ -1,0 +1,147 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Aug 28 20:15:08 2019
+
+@author: Dartoon
+
+Plot the MBHII MBH-Mr relation and fit their scatter.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import copy
+import sys
+
+import matplotlib.lines as mlines
+from matplotlib import colors
+import matplotlib as mat
+mat.rcParams['font.family'] = 'STIXGeneral'
+
+sys.path.insert(0,'../../py_tools')
+from load_result import load_MBH, load_host_p, load_err
+
+import matplotlib as mpl
+#data=np.loadtxt('../AGN_host_inference_for_npy.txt')
+#print data
+h=0.7
+
+tab_list = ['CID1174', 'CID1281', 'CID206', 'CID216', 'CID237', 'CID255', 'CID3242', 'CID3570',
+            'CID452', 'CID454', 'CID50', 'CID543', 'CID597', 'CID607', 'CID70', 'LID1273',
+            'LID1538', 'LID360', 'XID2138', 'XID2202', 'XID2396', 'CDFS-1', 'CDFS-229',
+            'CDFS-321', 'CDFS-724', 'ECDFS-358', 'SXDS-X1136', 'SXDS-X50', 'SXDS-X717', 'SXDS-X735', 'SXDS-X763', 'SXDS-X969']
+ext_ID = {'XID2202':'LID1622', 'XID2138':'LID1820', 'XID2396':'LID1878', 'CDFS-321':'ECDFS-321'}
+tab_sub_list = copy.deepcopy(tab_list)
+for i in range(len(tab_sub_list)):
+    if tab_sub_list[i] in ext_ID.keys():
+        tab_sub_list[i] = ext_ID[tab_sub_list[i]]
+Lr, M_star, M_r = load_host_p(tab_list,temp='3Gyrs', folder = '../../')  # M_star by Chabrier 
+
+bh_mass_obs = load_MBH(tab_list,tab_sub_list, if_reportHb=0, folder = '../../') #+np.log10(h)
+stellar_mass_obs=  np.log10(10**M_star / 0.54 * 0.91) #+np.log10(h)
+stellar_mass_obs_err= load_err(prop='Mstar', ID=tab_list)
[…]

### 2019-09-03 py_tools/load_result.py

@@ -236,16 +236,26 @@ def load_host_p(ID, folder='../', temp='1Gyrs', dm = 0):
     from dmag import k_corr_R
     from filter_info import filt_info
     dm_k_R = []
-    for i in range(len(zs)):
-        dm_k_R.append(k_corr_R(zs[i],filt_info[ID[i]], galaxy_age = temp))
-    dm_k_R = np.asarray(dm_k_R) # Get the k-correction for each target as an array
+    if temp != '3Gyrs':
+        for i in range(len(zs)):
+            dm_k_R.append(k_corr_R(zs[i],filt_info[ID[i]], galaxy_age = temp))
+        dm_k_R = np.asarray(dm_k_R) # Get the k-correction for each target as an array
+    else:
+        for i in range(len(zs)):
+            dm_k_R.append( (k_corr_R(zs[i],filt_info[ID[i]], galaxy_age = '1Gyrs')+k_corr_R(zs[i],filt_info[ID[i]], galaxy_age = '5Gyrs'))/2. )
+        dm_k_R = np.asarray(dm_k_R) # Get the k-correction for each target as an array
     dl=(1+zs)*c*vec_EE(zs)/h0 *10**6   #in pc
     host_Mags = mags -5*(np.log10(dl)-1) + dm_k_R + dm*pass_dmag(zs) # This is in AB system
-    host_LR = 10 ** (0.4*(4.61-host_Mags)) #LR in AB
+    host_LR = np.log10(10 ** (0.4*(4.61-host_Mags))) #LR in AB
     host_Mags_Vega = host_Mags - 0.21  # Transfer to Vega system
     host_LR_Vega = 10 ** (0.4*(4.43-host_Mags_Vega)) #LR in Vega
-    Mstar = np.log10(host_LR_Vega * 0.54 * 0.684 * 1.4191)  
-    return np.log10(host_LR), Mstar, host_Mags
+    if temp =='1Gyrs':
+        Mstar = np.log10(host_LR_Vega * 0.54 * 0.684 * 1.4191)  
+    elif temp=='5Gyrs':
+        Mstar = np.log10(host_LR_Vega * 2.32 * 0.59 * 1.4191)
+    if temp =='3Gyrs':
+        Mstar = np.log10(host_LR_Vega * 1.50 * 0.60 * 1.4191)      
+    return host_LR, Mstar, host_Mags
 
 def load_MBH(ID, MB_ID, if_reportHb=0,folder = '..', return_line = 0):
     #ID change:

### 2019-09-10 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
Update paper and figures

@@
 \newcommand{\lhost}{$L_{\rm host}$}
-\newcommand{\mr}{$Mag_{\rm ~R}$}
+\newcommand{\mr}{Mag$_{\rm ~R}$}
 \newcommand{\jcap}{Journal of Cosmology and Astroparticle Physics}
@@
 The mismatch of the interceptions between the two lines are relatively small within $1-\sigma$ level.
-We adopt the {\sc Limnux} to estimate the intrinsic scatter of both the sample.
-Interestingly, we find the observed sample have an intrinsic scatter of $0.13$~dex, which is even smaller than the one in the simulation, which is $0.23$~dex.
+We adopt the {\sc Limnux} to estimate the intrinsic scatter for both sample.
+Interestingly, the observed sample have an intrinsic scatter of $0.13\pm0.10$~dex, which is not larger than the one in the MBII, which is $0.23\pm0.06$~dex.
 
@@
 \caption{The selection window as adopted for selecting the MBII simulated sample.
-The blue background clouds shows the overall sample at $z=1.5$.
-The sample that only located in the selection windows are selected, labeled red.
+The yellow background clouds shows the overall sample at $z=1.5$.
+The compared sample would be selected when they in the selection windows, i.e.
+red region.
 }
@@
 \begin{tabular}{c c}
-\includegraphics[height=0.5\linewidth]{MBII_ML_.pdf} &
-\includegraphics[height=0.5\linewidth]{MBII_MM_.pdf} \\
+\includegraphics[width=0.5\linewidth]{MBII_ML.pdf} &
+\includegraphics[width=0.5\linewidth]{MBII_MM.pdf} \\
 \end{tabular}
@@
 We fix the slope value to fit for the observed sample and find that the mismatch of the interceptions are within $1-\sigma$ difference for both relations.
-{\bf For the right panel, I currently adopt a 3 Gyrs template for the HST sample...}
+%{\bf For the right panel, I currently adopt a 3 Gyrs template for the HST sample...}
 }
@@
 
-To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
+To help understand if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
 For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3.
@@
 We perform the Kolmogorov-Smirnov test the inferred p-values are 0.34 (for observed -- MBII) and 0.14 (for observed -- SAM), respectively.
-{\bf More interpretations}.
+{\bf Xuheng: more interpretations needs to put here}.
 
@@
 We find that the 1Gyr template would well match their color from which we estimate the rest-frame R band luminosity and stellar mass.
+A Salpeter initial mass function is employed consistently to the observed and simulated sample.
 

### 2019-09-10 NA_paper/scripts/MBHII_ML.py

@@ -52,13 +52,13 @@ def lfit(x,m,c):
     return m*x+c
 
 import scipy.optimize
-f,ax=plt.subplots(1,1,figsize=(8,8))
+f,ax=plt.subplots(1,1,figsize=(11,10))
 
 obj=ax
 redshift=1.5
-#panel2=obj.hist2d(r_band_magnitudes_overall,bhmass_overall,
-#                  norm=mpl.colors.LogNorm(),cmap='Blues_r',bins=50,zorder=0,alpha=0.5)
-panel2=obj.scatter(r_band_magnitudes_overall,bhmass_overall,c='gray',alpha=0.5, label='Simulated population')
+panel2=obj.hist2d(r_band_magnitudes_overall,bhmass_overall,
+                  norm=mpl.colors.LogNorm(),cmap='copper',bins=50,zorder=0,alpha=0.5)
+#panel2=obj.scatter(r_band_magnitudes_overall,bhmass_overall,c='gray',alpha=0.5, label='Simulated population')
 
 ####Fit the overall sample (x as function of y):
 #fit=scipy.optimize.curve_fit(lfit,-r_band_magnitudes_overall,log10_bhmass_overall)
@@ -71,8 +71,8 @@ panel2=obj.scatter(r_band_magnitudes_overall,bhmass_overall,c='gray',alpha=0.5, 
 ##r_band_space_lb=lfit(lmbh_space,fit[0][0]-fit_err[0]/2,fit[0][1]-fit_err[1]/2)
 ##plt.fill_betweenx(lmbh_space,r_band_space_lb,r_band_space_ub,color='blue',alpha=0.3)
 
-#cbar=f.colorbar(panel2[3],ax=obj)
-#cbar.ax.tick_params(labelsize=30) 
+cbar=f.colorbar(panel2[3],ax=obj)
+cbar.ax.tick_params(labelsize=30) 
 
 obj.errorbar(r_band_magnitudes_selected,bhmass_selected,zorder=1,
              color='red',label='Simulated population',linestyle=' ',marker='o',ms=10,mec='k')
@@ -99,6 +99,22 @@ plt.plot(r_band_space,lmbh_space,color='green',linewidth=3)
 
 print "mismatch:", fit_fixm[0]- fit[0][1]
 
+
[…]

### 2019-09-10 NA_paper/scripts/figures_producer.py

@@ -1,0 +1,68 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Sep  4 21:12:28 2019
+
+@author: Dartoon
+
+Produce figures
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import matplotlib as mat
+import matplotlib as mpl
+mat.rcParams['font.family'] = 'STIXGeneral'
+
+import sys
+sys.path.insert(0,'../../py_tools')
+
+h=0.7
+
+bhmass_overall=np.loadtxt('../Aklant/new_sample/log10_bh_mass_full_population.txt') - np.log10(h) 
+bhmass_selected=np.loadtxt('../Aklant/new_sample/log10_bh_mass_selected_population.txt') - np.log10(h) 
+
+mstar_overall=np.loadtxt('../Aklant/new_sample/log10_stellar_mass_full_population.txt') - np.log10(h) 
+mstar_selected=np.loadtxt('../Aklant/new_sample/log10_stellar_mass_selected_population.txt') - np.log10(h) 
+
+Lbol_overall=np.loadtxt('../Aklant/new_sample/log10_L_bol_full_population.txt') - np.log10(h) 
+Lbol_selected=np.loadtxt('../Aklant/new_sample/log10_L_bol_selected_population.txt') - np.log10(h) 
+
+logLedd_overall = 38. + np.log10(1.2) + bhmass_overall
+logLedd_selected = 38. + np.log10(1.2) + bhmass_selected
+
+plt.figure(figsize=(11,9))
+#plt.scatter(bhmass_selected, Lbol_selected-logLedd_selected)
+
+plt.hist2d(bhmass_overall,Lbol_overall-logLedd_overall,
+                  norm=mpl.colors.LogNorm(),cmap='copper',bins=50,zorder=0,alpha=0.5)
+cbar = plt.colorbar()
+#cbar=f.colorbar(panel2[3],ax=obj)
+cbar.ax.tick_params(labelsize=30) 
+#
+xspace = np.linspace(6,10)
+plt.plot(xspace, 0*xspace,'k--',linewidth=3)
+plt.plot(xspace, 0*xspace-1.5,'k--',linewidth=3)
[…]

### 2019-09-10 NA_paper/scripts/my_selection_plots_MBII.py

@@ -1,0 +1,354 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Aug 28 20:15:08 2019
+
+@author: Dartoon
+
+Plot the MBHII MBH-Mr relation and fit their scatter.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import copy
+import sys
+
+import matplotlib.lines as mlines
+from matplotlib import colors
+import matplotlib as mat
+mat.rcParams['font.family'] = 'STIXGeneral'
+
+sys.path.insert(0,'../../py_tools')
+from load_result import load_MBH, load_host_p, load_err, load_Lbol
+import matplotlib as mpl
+h=0.7
+
+bhmass_overall=np.loadtxt('../Aklant/new_sample/log10_bh_mass_full_population.txt') - np.log10(h) 
+#bhmass_selected=np.loadtxt('../Aklant/new_sample/log10_bh_mass_selected_population.txt') - np.log10(h) 
+
+mstar_overall=np.loadtxt('../Aklant/new_sample/log10_stellar_mass_full_population.txt') - np.log10(h) 
+#mstar_selected=np.loadtxt('../Aklant/new_sample/log10_stellar_mass_selected_population.txt') - np.log10(h) 
+
+magr_overall=np.loadtxt('../Aklant/new_sample/log10_host_r_mag_full_population.txt')
+#r_band_magnitudes_selected=np.loadtxt('../Aklant/new_sample/log10_host_r_mag_selected_population.txt')
+
+Lbol_overall=np.loadtxt('../Aklant/new_sample/log10_L_bol_full_population.txt') - np.log10(h) 
+#Lbol_selected=np.loadtxt('../Aklant/new_sample/log10_L_bol_selected_population.txt') - np.log10(h) 
+
+logLedd_overall = 38. + np.log10(1.2) + bhmass_overall
+#logLedd_selected = 38. + np.log10(1.2) + bhmass_selected
+
+Eddr_overall = Lbol_overall-logLedd_overall
+
+###Add noise to the data: 
[…]

### 2019-09-11 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
Update paper and scatter input analysis

@@
 \includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
-\caption{The selection function as used for choosing the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function.
+\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function.
 }
@@
 %Selection effect into account
-We collect the scaling relations by a comparable AGN sample in the MBII to compare with the observed ones.
-The simulated sample is selected at $z=1.5$ using a comparable selection window, as shown in Figure~\ref{fig:selectfunc}.
+We select the AGNs in the MBII simulation at $z=1.5$ and collect their scaling relations to compare with the observed ones.
+To take the measurement uncertainty and the selection effect into account, we added the random noise to the simulated sample to mimic the scatter effect.
+The assumed uncertainties are $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex and $\Delta L_{\rm bol}$=0.03~dex, respectively, which is comparable to the measurement.
+We then select the sample that falls in the selection window, as shown in Figure~\ref{fig:selectfunc}.
 We investigated the predicted relations of the \mbh-\mr\ and \mbh-\mstar\ by the MBII and compared to the observational constraints.
@@
 The mismatch of the interceptions between the two lines are relatively small within $1-\sigma$ level.
-We adopt the {\sc Limnux} to estimate the intrinsic scatter for both sample.
+We adopt the {\sc Linmix} to estimate the intrinsic scatter for both sample.
 Interestingly, the observed sample have an intrinsic scatter of $0.13\pm0.10$~dex, which is not larger than the one in the MBII, which is $0.23\pm0.06$~dex.
@@
 The yellow background clouds shows the overall sample at $z=1.5$.
-The compared sample would be selected when they in the selection windows, i.e.
-red region.
-}
+We add the random uncertainty to the simulation and select the ones located in the selection window (i.e.
+red region).
+The green sample are the high-$z$ sample.}
 \label{fig:selectfunc}

### 2019-09-17 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
Update paper and the plots. SAM analysis included.

@@
 \newcommand{\lhost}{$L_{\rm host}$}
-\newcommand{\mr}{Mag$_{\rm ~R}$}
+\newcommand{\mr}{$Mag_{\rm ~R}$}
 \newcommand{\jcap}{Journal of Cosmology and Astroparticle Physics}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
 
@@
 \begin{abstract}
-Supermassive black holes (BH) harbor at the center of galaxies with their masses correlated to the properties of the host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar) known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar).
-Observational results have indicated evidence that this correlation evolves with cosmic time, suggesting a scenario that the BH growth predates their host.
+Supermassive black holes (BH) harbor at the center of galaxies with their masses (\mbh) correlated to the properties of the host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar) known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar).
+ %Observational results have indicated evidence that this correlation evolves with cosmic time, suggesting a scenario that the BH growth predates their host.
 In theory, positive evolution of BH is also predicted by several simulation projects independently.
-So far, the simulations have reproduced the relations which have a good agreement to the observational sample from local to intermediate redshift ($0.3<z<1$).
-It is crucial to extend this study to higher redshift ($z>1$), where the predicted relations are more sensitive to the initial simulating assumptions and any inconsistency could help to pinpoint the incorrect ones.
-To this end, we use a sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) to make a direct comparison to the predicted sample from two independent state-of-the-art simulating projects, including MassiveBlack-II (MBII) and semi-analytic models (SAMs).
-We use \hst\ observed images to study the 32 AGNs in multi-bands and deriving the trustworthy stellar mass measurements and the reliable broad \halpha\ emission lines to estimate the \mbh.
-Taking the selection bias into account, %by adopting the same selection function to choose the simulating sample,
-we find that both models agree well with the data, even though they use very different recipes.
-These agreements indicate the existence of a causal connection between BH and the host galaxy, which could not be explained by purely a stochastic process.
-To some extent, our result attests that this connection induces an ordering so that the more massive black holes are linked to the more massive masses.
-Moreover, we find the intrinsic scatter of our high-$z$ sample is not larger than the simulations and local ones, which is against the central limit theorem.
+So far, the simulations have reproduced the relations which have a good agreement to the observational sample from local to intermediate redshift ($z<1$).
+It is crucial to extend this study to higher redshift ($z>1$), where the predicted relations are more sensitive to the initial assumptions and any inconsistency would help to pinpoint the incorrect ones.
+To this end, we use a sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) to make a direct comparison to the predicted sample by two independent state-of-the-art simulation projects: MassiveBlack-II (MBII) and semi-analytic models (SAMs).
+We adopt \hst\ to take images of the 32 AGNs in multi-bands and deriving the trustworthy stellar mass and use the reliable broad \halpha\ emission lines by Subaru/FMOS to estimate the \mbh.
+Taking the measurement uncertainty and selection bias into account, %by adopting the same selection function to choose the simulating sample,
+we find that both models agree well with the data, in terms of the central distribution and scatters.
+Considering the two models use very different recipes, their agreements to the data indicate the existence of a causal connection between BH and the host galaxy, which could not be explained by purely a stochastic process.
+The intrinsic scatter of our high-$z$ sample is close to simulations and local ones, which is against the central limit theorem.
+To some extend, our result attests that there is a physical connection induces an ordering so that the more massive black holes are linked to the more massive masses.
 
@@
 %\section{Introduction}
-The discovery of the correlations between the masses (\mbh) of supermassive black holes (SMBH) and the properties of their host galaxies, such as absolute magnitude ($Mag$) and stellar mass (\mstar), indicates that the growth of BH could be connected to its host galaxy formation.
+The discovery of the correlations between the masses (\mbh) of supermassive black holes (SMBH) and the properties of their host galaxies, such as absolute magnitude ($Mag$) and stellar mass (\mstar), indicates that the growth of SMBH could be connected to its host galaxy formation.
 So far, the origin that drives this connection is still unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim$10 kpc).
@@
 In this scenario, the activity of AGN accretion heats and unbinds significant fractions of the gas and inhibits star formation.
-Some models have been proposed that the connection between SMBH and its host are connected not in a direct manner but assuming that they share a common gas supply~\cite{Cen2015, Menci2016}.
-On the other hand, without any physical mechanisms, the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations.
+In addition, there are other models have been proposed that the connection between SMBH and their hosts are connected not in a direct manner but assuming that they share a common gas supply~\cite{Cen2015, Menci2016}.
+Furthermore, without any physical mechanisms, it has been proposed that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations [ref].
 In this central limit theorem, a stochastic cloud at high-$z$ (higher scatter) would end up with the scaling relations (lower scatter) as observed today.
 
-To understand this connection, the recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have analyzed the scaling relations beyond the local redshift {($0.3<z<1$)} with active galactic nuclei (AGN) using {\it Hubble Space Telescope} ({\it HST}) and found an evolution that the growth of SMBHs predated to their host galaxies.
+To understand this connection, the recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have analyzed the scaling relations to intermediate redshift {($0.3<z<1$)} by studying the active galactic nuclei (AGN) using {\it Hubble Space Telescope} ({\it HST}) and found an evolution that the growth of SMBHs predated to their host galaxies.
 However, the observational evidence of evolution at high-$z$ is under debated as it relies on our understanding of systematic uncertainties and selection effects.
@@
 %The reason to extend to high redshift.
-Simulating models are the effective tools that help to understand this connection and rule out the assumptions which could not be satisfied with the observations.
-In the simulating test, the systematic uncertainties and selection bias would be easy to account for.
-Recent simulating studies by several projects have made predictions which is in good agreement with the analysis by the observations at intermediate redshift range.
+Simulation models are effective to help understand this connection and rule out the theories/assumptions which could not be verified by the observations.
+In the simulation test, the systematic uncertainties and selection bias would be easy to account for.
+Recent studies by several simulation projects have made predictions which is in good agreement with the analysis by the observations at intermediate redshift range.
 For example, the state-of-the-art cosmological hydrodynamical simulations of structure formation (MassiveBlackII) have compared the predicted scaling relations to the \hst\ observation at $0.3<z<1$ and predict a positive evolution that SMBH growth predates the host galaxy~\cite{DeG++15}.
-Several others works have investigated the scaling relations using large-volume simulations, also well matching the local relation with some redshift evolution, including approaches using the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014}.
+Several others works have investigated the scaling relations using large-volume simulations, resulting in well matches to the local relation with some redshift evolution, including approaches using the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014}.
 Besides hydrodynamic simulations, semi-analytic models~\cite{Menci2014, Menci2016} also have made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}.
-However, to date, the comparisons to the high-resolution (i.e., \hst) sample were still limited at $z<1$ due to the limitation of the observations.
-
-%A good way to understand this connection is to rely on active galactic nuclei (AGN) and trace the scaling relations to higher redshifts, witnessing how and when does it happen.
-More recently, there is increasing observational evidence indicating the positive offset exist in the correlation at intermediate redshift range ($0.3<z<1$), implying that galaxies built up around the massive potential wells of mature BHs.
-Stimulated by the observations, theoretical efforts have been made to include the growth of \mbh\ in the framework of cosmological galaxy formation simulations, and generated the predictions of local scaling relations which match the observations well.
-Moreover, the simulations predict that the positive offset could be even stronger at redshift range $1<z<2$.
-
-%Using the samples predicted by the simulation to compare to the observations is beneficial, in particular at high redshift.
-First, it helps to directly verify the validity of the initial physics prescriptions adopted in the simulation process, and point out the direction where to improve if needed.
-Second, in turn, the lessons learned in the simulations could be used to investigate the mechanism of the origin of the scaling relation.
-For example, the feedback originating in the surroundings of BHs, the major merging activities, and the growth of the \mbh\ and the stellar components as connected to the common gas supply have been invoked as the process leading to the co-evolution.
-Extending the comparison to high redshift help to explore the origin of the evolution directly.
-Furthermore, adopting the same selection function enable the particular comparison between two equivalent sample, so as to get rid of the systematic bias lead by the selection effects.
+However, to date, the comparisons to the scaling relations by high-resolution sample (i.e., imaged by \hst) are still limited at $z<1$ due to the limitation of the observations.
 
@@
 	%mention the scatter.
-To extend, we collected a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}, to compare to the simulating models.
+To extend the comparison to the simulation models to higher redshift, we collected a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from three X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}.
 The redshift range of our targets is chosen to be high enough ($z>1$) to detect the existence of the evolution offsets and make the comparison to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming.
-We selected our AGN sample in a well-defined window as in Figure~\ref{fig:AGN_select}, based on the \mbh\ and Eddington ratio.
-As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias and the Eddington ratio are above the 1\% level to ensure the homogeneity.
+We selected our AGN sample in a well-defined window as in Figure~\ref{fig:AGN_select}, based on the \mbh\ and Eddington ratio \ding{Do we plot figure1 again, or cite to the QSO I paper?}.
+As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias and the Eddington ratio are mostly above the 0.1 to ensure the homogeneity.
 
@@
 \includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
-\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function.
+\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function. \ding{More descriptions to put here.}
 }
@@
 
-To make the comparison to the simulating models, we adopt two independent simulating projects, including MassiveBlack-II (MBII) and semi-analytic models (SAM).
+To make the comparison, we adopt two independent simulation projects, including MassiveBlack-II (MBII) and semi-analytic models (SAM).
 These two models are based on independent model strategies, i.e., hydrodynamic simulation for MBII and semi-analytic model for SAM, respectively.
@@
 %Selection effect into account
-We select the AGNs in the MBII simulation at $z=1.5$ and collect their scaling relations to compare with the observed ones.
-To take the measurement uncertainty and the selection effect into account, we added the random noise to the simulated sample to mimic the scatter effect.
-The assumed uncertainties are $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex and $\Delta L_{\rm bol}$=0.03~dex, respectively, which is comparable to the measurement.
-We then select the sample that falls in the selection window, as shown in Figure~\ref{fig:selectfunc}.
-We investigated the predicted relations of the \mbh-\mr\ and \mbh-\mstar\ by the MBII and compared to the observational constraints.
-In Figure~\ref{fig:MBII_comp}, we show the comparisons of both relations and find that the predicted scaling relations have an excellent agreement to the observations.
-We carry out the linear fitting of the observed sample and the {\it selection-effect-considered} sample using the same slope value.
-The mismatch of the interceptions between the two lines are relatively small within $1-\sigma$ level.
-We adopt the {\sc Linmix} to estimate the intrinsic scatter for both sample.
-Interestingly, the observed sample have an intrinsic scatter of $0.13\pm0.10$~dex, which is not larger than the one in the MBII, which is $0.23\pm0.06$~dex.
+We collect a sample of AGNs in the MBII simulation at $z=1.5$ and compare their scaling relations the observed ones.
+To take the measurement uncertainty and the selection effect into account, we inject the {\it random} noise to the simulated sample to mimic the scattering effect that caused by the uncertainty.
+The assumed uncertainty levels are comparable to the realistic, which are $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex and $\Delta L_{\rm bol}$=0.03~dex, respectively.
+We then select the sample that falls into the selection window, as shown in Figure~\ref{fig:selectfunc}.
+We investigated the predicted scaling relations by the MBII, including \mbh-\mr\ and \mbh-\mstar, and compared them to the observational constraints, as shown in Figure~\ref{fig:MBII_comp}.
+From a quick glimpse, one can see that the samples are overlapped with each other, showing an agreement between the predicted scaling relations and observations.
+To quantify this agreement, we perform the linear fitting to the simulated relations and estimate the best-fit and 1$-\sigma$ confidence interval.
+We then use the same slope value to obtain the best-fit result for the observed sample.
+We find that for the \mbh-\mr\ relation, the linear fitting results are almost identical ($0.06$~dex mismatch).
+For the \mbh-\mstar relations, the mismatch ($0.15$~dex) is small and within 1$-\sigma$ level.
+We compare how the sample scatter to its central line and find that the simulations and the observations demonstrate a significant similarity.
+Given that the simulated samples have the same uncertainty and the selection effect, we expect the intrinsic scatter of the scaling relations to be at the same level, which it $0.25$~dex (see method section for details).
 
@@
 We do not estimate the scatter for SAM model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one.
+\ding{To be updated with Nicola's data.}
 
@@
 \begin{tabular}{c c}
-\includegraphics[trim = 0mm 0mm 26mm 0mm, clip, width=0.45\linewidth]{SAM_ML.pdf} &
-\includegraphics[trim = 24mm 0mm 0mm 0mm, clip, width=0.45\linewidth]{SAM_MMstar.pdf} \\
+\includegraphics[trim = 0mm 0mm 24mm 0mm, clip, width=0.45\linewidth]{SAM_ML.pdf} &
+\includegraphics[trim = 30.5mm 0mm 0mm 0mm, clip, width=0.45\linewidth]{SAM_MMstar.pdf} \\
 \end{tabular}
@@
 The median values for the flux ratio distribution of the observed, MBII, SAM sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively.
-We perform the Kolmogorov-Smirnov test the inferred p-values are 0.34 (for observed -- MBII) and 0.14 (for observed -- SAM), respectively.
-{\bf Xuheng: more interpretations needs to put here}.
+We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are 0.34 (for observed -- MBII) and 0.14 (for observed -- SAM), respectively.
+\ding{more interpretations needs to put here}.
 
@@
 
-Limited by the observations and the fact they are in good agreements to MBII and SAM, one can not rule out one simulating model from the other.
-Of course, there are differences between two simulating models.
+Limited by the observations and the fact they are in good agreements to MBII and SAM, one can not rule out one simulation model from the other.
+Of course, there are differences between two simulation models.
 For example, the SAM sample trends to have more scatter than the MBII, especially before applying any selection function.
@@
 
-\textbf{Simulations.} 
-Describe the approaches used in the simulation.
+%\textbf{Simulations.} 
+%Describe the approaches used in the simulation.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\textbf{Linear fitting and scatter comparison}.  
+%How the fitting is done. The comparing of the histogram and the KS test. The scatter. Figures.
+To quantitatively understand the consistency between the simulated scaling relations and the observing ones, we use linear fittings and compare their result.
+Since our selection window has hard cut on the \mbh\ value and the scatter on the host galaxies' properties are larger, we thus fit the host's properties as a function of \mbh.
+We adopt the {\sc Scipy} package to estimate the best-fit line and its 1-sigma region for the simulated sample.
+We use the sample slope value to fit for the observations.
+The comparing results are showing in Figure~\ref{fig:MBII_comp}.
+To estimate the scatter of the sample, we plot the histogram of the offset value of the sample that deviated from their best-fit.
+For MBII model, the result are shown in Figure~\ref{fig:offset_comp}.
+We perform the KS test between the simulation sample and observation sample, and find the p-value are $\sim0.3$ for both \mbh-\mr\ and \mbh-\mstar\ relations.
+Considering that the compared simulation sample have the same uncertainty level with same selection effect, we expect they have the same intrinsic scatter level.
+We adopt {\sc Linmux} to estimate the intrinsic scatter from the overall sample and obtain its value value is $0.25$~dex.
+
+\begin{figure*}[t]%[!b]
+\begin{tabular}{c c}
+\includegraphics[width=0.45\linewidth]{comp_scatter_ML.pdf} &
+\includegraphics[width=0.45\linewidth]{comp_scatter_MM.pdf} \\
+\end{tabular}
+\caption{The histogram comparison of the scatter of the sample offset to its best-fit relation.
+The standard derivations are identically equal to $0.3$~dex for both HST sample and MBII sample on both sides.
+}
+\label{fig:offset_comp}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-09-17 material/recover_figure1_in_paper/recover_figure1.py

@@ -92,12 +92,13 @@ y_line_1 = x_cline*0 + 0.0
 ax.plot(x_cline, y_line_1,'k--')
 y_cline = np.linspace(-20, 20, 10)
 x_line = y_cline*0 + 8.6
-ax.plot(x_line, y_cline,'r--')
+ax.plot(x_line, y_cline,'k--')
+ax.plot(y_cline*0 + 7.7, y_cline,'k--')
 x_cline = np.linspace(7.1, 8.5)
 y_line_3 = -1.1*(x_cline-7.5) -0.5
-#ax.plot(x_cline, y_line_3,'k--')
-plt.xlabel("log$(M_{BH}/M_{\odot})$",fontsize=25)
-plt.ylabel("log($L_{bol}/L_{Edd})$", fontsize=25) 
+ax.plot(x_cline, y_line_3,'k--')  #
+plt.xlabel(r"log(M$_{\rm BH}$/M$_{\odot})$",fontsize=25)
+plt.ylabel(r"log(L$_{\rm bol}$/L$_{\rm Edd}$)", fontsize=25) 
 plt.tick_params(labelsize=15)
 plt.xticks(np.arange(7.5,9.6,0.5))
 other_data = np.loadtxt('Peng_Decarli_data.txt')
@@ -153,7 +154,7 @@ mbh_rho = np.log10(mbh_rho)
 #mbh_rho_select = np.log10(mbh_rho_select)
 ax_x.plot(mbh_x,mbh_rho, 'k')
 #ax_x.plot(mbh_x,mbh_rho_select, 'b')
-ax_x.plot(x_line, y_cline,'r--')
+ax_x.plot(x_line, y_cline,'k--')
 #plt.yticks(np.arange(-10,10,1))
 plt.ylim([int(mbh_rho.min()),int(mbh_rho.max())+1])
 plt.tick_params(labelsize=15)
@@ -177,7 +178,7 @@ ax_y.plot(x_cline, y_line_1, 'k--')
 plt.xticks(np.arange(-10,10,2))
 plt.xlim([int(rho_lam.min()),int(rho_lam.max())+1])
 plt.tick_params(labelsize=15)
-plt.xlabel("log$\phi(\lambda)$", fontsize=25) 
+plt.xlabel(r"log${\rm \phi(\lambda)}$", fontsize=25) 
 
 #%%
 # the xaxis of ax_x and yaxis of ax_y are shared with ax,

### 2019-09-20 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
Update paper and text

@@
 Taking the measurement uncertainty and selection bias into account, %by adopting the same selection function to choose the simulating sample,
-we find that both models agree well with the data, in terms of the central distribution and scatters.
+we find that both models agree well with the data, \ding{However...} in terms of the central distribution and scatters.
 Considering the two models use very different recipes, their agreements to the data indicate the existence of a causal connection between BH and the host galaxy, which could not be explained by purely a stochastic process.
@@
 We selected our AGN sample in a well-defined window as in Figure~\ref{fig:AGN_select}, based on the \mbh\ and Eddington ratio \ding{Do we plot figure1 again, or cite to the QSO I paper?}.
-As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias and the Eddington ratio are mostly above the 0.1 to ensure the homogeneity.
+As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias and the Eddington ratio are mostly above $0.1$ to ensure the homogeneity.
 
@@
 \includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
-\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function. \ding{More descriptions to put here.}
+\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function. \ding{More descriptions needed if Figure1 is finally decided to shown.}
 }
@@
 
-To make the comparison, we adopt two independent simulation projects, including MassiveBlack-II (MBII) and semi-analytic models (SAM).
+To make the comparison, we adopt two independent simulation projects, including MassiveBlack-II (MBII)~\cite{Khandai2015} and semi-analytic models (SAM)~\cite{Menci2014}.
 These two models are based on independent model strategies, i.e., hydrodynamic simulation for MBII and semi-analytic model for SAM, respectively.
@@
 On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems.
-However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as (SAM).
-MBII and SAM have made successful predictions in previous works \cite{Menci2014, Menci2016, Khandai2015}. We refer the interested readers to these works for more details.
+However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as SAM.
+In previous works~\cite{Menci2014, Menci2016}[ref], MBII and SAM have made successful predictions.
+We refer the interested readers to these works for more details.
 
@@
 %Selection effect into account
-We collect a sample of AGNs in the MBII simulation at $z=1.5$ and compare their scaling relations the observed ones.
-To take the measurement uncertainty and the selection effect into account, we inject the {\it random} noise to the simulated sample to mimic the scattering effect that caused by the uncertainty.
-The assumed uncertainty levels are comparable to the realistic, which are $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex and $\Delta L_{\rm bol}$=0.03~dex, respectively.
-We then select the sample that falls into the selection window, as shown in Figure~\ref{fig:selectfunc}.
-We investigated the predicted scaling relations by the MBII, including \mbh-\mr\ and \mbh-\mstar, and compared them to the observational constraints, as shown in Figure~\ref{fig:MBII_comp}.
-From a quick glimpse, one can see that the samples are overlapped with each other, showing an agreement between the predicted scaling relations and observations.
-To quantify this agreement, we perform the linear fitting to the simulated relations and estimate the best-fit and 1$-\sigma$ confidence interval.
-We then use the same slope value to obtain the best-fit result for the observed sample.
-We find that for the \mbh-\mr\ relation, the linear fitting results are almost identical ($0.06$~dex mismatch).
-For the \mbh-\mstar relations, the mismatch ($0.15$~dex) is small and within 1$-\sigma$ level.
-We compare how the sample scatter to its central line and find that the simulations and the observations demonstrate a significant similarity.
-Given that the simulated samples have the same uncertainty and the selection effect, we expect the intrinsic scatter of the scaling relations to be at the same level, which it $0.25$~dex (see method section for details).
+To make comparison by the MBII project, we collect a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones.
+To ensure a fair comparison, we take the measurement uncertainty and the selection effect into account with the following process.
+First, we inject the random noise to the simulated sample to mimic the scattering effect that caused by the uncertainty.
+The assumed uncertainty levels are comparable to the realistic ones, i.e., $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex and $\Delta L_{\rm bol}$=0.03~dex, respectively.
+We then select the sample that falls into the same selection window, as shown in Figure~\ref{fig:selectfunc}.
+We investigated the predicted scaling relations, including \mbh-\mr\ and \mbh-\mstar, and compared them to the observational constraints, as shown in Figure~\ref{fig:MBII_comp}.
+From a quick glimpse, one can see that the samples are overlapped with each other, showing a sign of agreement.
+To quantify the level of agreement, we perform the linear regression to fit the simulated relations and estimate the best-fit and 1$-\sigma$ confidence interval.
+We use the same slope value to fit the best intercept value for the observed sample.
+We find that for the \mbh-\mr\ relation, the linear fitting results are almost identical, with $0.06$~dex mismatch.
+For the \mbh-\mstar\ relations, the mismatch ($0.15$~dex) is small and far below 1$-\sigma$ level.
+We also compare the sample by their scatter.
+Calculating the standard derivation of the residual, we find the simulations and the observations have the same scatter value $0.3$~dex.
+Considering that the simulated samples have the same uncertainty and the selection effect, we expect the intrinsic scatter of the scaling relations are similar, which it $0.25$~dex (see METHODS).
 
@@
 red region).
-The green sample are the high-$z$ sample.}
+The yellow dots are the observed sample.}
 \label{fig:selectfunc}
@@
 \end{tabular}
-\caption{
-Comparing the scaling relations between the observed scaling relations to the predicted samples by the MBII simulation.
-In the left and right panel, we present the \mbh-\mr\ and \mbh-\mstar\ correlation, respectively.
-The blue grids are the overall galaxies that predicted in the MBII simulation and the red ones are selection effect considered.
-We red line shows the best-fit linear relations for the simulated selected sample.
-We fix the slope value to fit for the observed sample and find that the mismatch of the interceptions are within $1-\sigma$ difference for both relations.
+\caption{  In the left and right panel, we present the \mbh-\mr\ and \mbh-\mstar\ correlation between the observed scaling relations (green dots) and the predicted samples (red dots) by the MBII simulation, respectively.
+The MBII predicted sample are treated to have the same uncertainty and selection effect as the observational ones.
+The red line is the best-fit result for the simulated sample, with colored region indicating the $1-\sigma$ confidence interval.
+We use the same slope value to fit for observed sample and the green line shows the best-fit result.
+The yellow grids in the background are the overall sample that predicted in the MBII simulation.
 %{\bf For the right panel, I currently adopt a 3 Gyrs template for the HST sample...}
@@
 
-The comparisons between the observed scaling relations to the SAM model are presented in Figure~\ref{fig:SAM_comp}.
-Rather than predict each individual simulated sample, the SAM model describes the possibility clouds to demonstrate the density distribution of the scaling relations.
-We use two sets of color contours to demonstrate the possibility distribution at $z=1.5$ epoch, before and after adopting the selection window.
-The comparisons show great consistency that the hot zones in the SAM {\it selection-effect-considered} contours at $\log($\mbh$)~\in[7.5, 8.56]$ are well matched to the observed relations.
-We do not estimate the scatter for SAM model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one.
-\ding{To be updated with Nicola's data.}
+We also make comparisons of our observed scaling relations to the predictions by SAM model.
+We consider the sample at $z=1.5$ epoch for two sample sets, including the overall sample and the selected sample.
+Rather than use N-body simulation to produce individual galaxies, the SAM model use the density clouds to describe the possibility of the samples, as shown in Figure~\ref{fig:SAM_comp}.
+We find that considering the selecting effect, the direct prediction by SAM is well matched to the observed relations.
+%We do not estimate the scatter for SAM model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one.
+\ding{This is not right yet.
+But if consider the scatter in the same way, the SAM have large scatter?}
+However this is not a proper comparisons yet, since this direct comparison does not include the scattering effect by the measurement uncertainty.
+To make a valid comparison, we generate a random the overall sample for SAM based on the possibility distribution.
+Then, same as MBII's case, we inject the random uncertainty to the sample to take the uncertainty effect into account and select the sample the selection window.
+The resulting comparisons are shown in Figure~\ref{fig:SAM_comp_withnoise}.
+We find that the best-fit result by the SAM model are well matched to the observation.
+However, the horizontal scatter of the SAM model are overwhelmingly larger.
+This larger scatter is a combination result by the SAM distribution, uncertainty and selection effect.
 
@@
 \end{tabular}
-\caption{ Similar to the Figure~\ref{fig:MBII_comp}, we compare the observation to the SAM models.
-The blue background contours show the overall sample distribution and the red ones are the relations after considering the selecting effect.
-We see that the yellow contours are well matched to the hot zones for the red contours.
+\caption{Similar to the Figure~\ref{fig:MBII_comp}, but for a direct comparison to the observation using SAM's model.
+The blue background contours show the possibility distribution for the overall sample, and the red contours indicate the distributions after considering the selecting effect.
+We presented our observational data as yellow dots.
+Note that this comparison has not taken the measurement uncertainties into account yet.
 }
@@
 
-To help understand if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
+\begin{figure*}[t]%[!b]
+\begin{tabular}{c c}
+\includegraphics[width=0.45\linewidth]{SAM_ML_consider_nois.pdf} &
+\includegraphics[width=0.45\linewidth]{SAM_MM_consider_nois.pdf} \\
+\end{tabular}
+\caption{Same as the Figure~\ref{fig:MBII_comp}, but for the SAM models.}
+\label{fig:SAM_comp_withnoise}
+\end{figure*}
+
+To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
 For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3.
@@
 We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are 0.34 (for observed -- MBII) and 0.14 (for observed -- SAM), respectively.
-\ding{more interpretations needs to put here}.
+This result indicates the three samples have similar host-to-total light distribution.
 
@@
 Without any physical mechanisms, the central limit theorem assumes that the scaling relations are the results by the random merger from a stochastic cloud at higher redshift.
-In this scenario, the scatter of the scaling relations has to be larger at higher redshift.
+In this scenario, the scatter of the scaling relations has to be larger with the increasing of redshift.
 However, the observed scatter of our high-$z$ sample do not present this feature.
-In fact, the obtained intrinsic scatter is only $\sim0.13$~dex, which is no more than the typical scatter at local relations in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}.
-Of course, the intrinsic scatter of our high-$z$ sample could be underestimated, since manually selected sample avoids the spreading of the properties and decrease the value of the scatter.
+In fact, our inferred intrinsic scatter of the observed sample is only $\sim0.25$~dex, which is no more than the typical scatter at local relations in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}.
+Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate which,
+since we use the MBII overall sample as proxy to estimate this value.
 Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), result in an overestimating of the error-budget and thus underestimating of intrinsic scatter.
-Still, even we do not take the uncertainties into account to calculate the scatter, the obtained value is $0.25$~dex, which is not larger than the local relations.
-Thus, the evidence of the low scatter in our measurements is likely to be true, which is against the central limit theorem and suggests that the physical mechanisms between the SMBH and its host galaxy are likely to exist.
+Still, the evidence of the low scatter in our measurements is likely to be true, which is against the central limit theorem and suggests that the physical mechanisms between the SMBH and its host galaxy are likely to exist.
 
-Between the MBII and SAM models, they all demonstrate an excellent agreement to the observed data; however, they adopted very different assumptions, recipes, and initial conditions.
+The MBII model and SAM model both demonstrate an excellent agreement to the observed data; however, they adopted very different assumptions, recipes, and initial conditions.
 From another perspective to understand this agreement, there has to be a causal link between SMBH and its host galaxy to generate an ordering during their evolution, so that more massive BHs are linked to more massive galaxies with some intrinsic scatter.
@@
 We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to co-add the final image with pixel scale as 0\farcs0642.
-To mitigate the contamination from both the sky and the detector, we adopt the {\sc photuils} tools to estimate and remove them accurately.
+To mitigate the contamination by the background light from both the sky and the detector, we adopt the {\sc photuils} tools to estimate and remove them accurately.
 
@@
 Based on the reduced $\chi^2$, we are capable of evaluating the performance of each PSF.
-We adopt the result from the top-eight PSFs and infer the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.
+We adopt the result from the top-ranked-eight PSFs and infer the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.
 
@@
 We decompose the AGN image in the ACS band to obtain the color of the host.
-We find that the 1Gyr template would well match their color from which we estimate the rest-frame R band luminosity and stellar mass.
+We find that the 1~Gyr template could well match their color from which we estimate the rest-frame R band luminosity and stellar mass.
 A Salpeter initial mass function is employed consistently to the observed and simulated sample.
@@
 %How the fitting is done. The comparing of the histogram and the KS test. The scatter. Figures.
-To quantitatively understand the consistency between the simulated scaling relations and the observing ones, we use linear fittings and compare their result.
-Since our selection window has hard cut on the \mbh\ value and the scatter on the host galaxies' properties are larger, we thus fit the host's properties as a function of \mbh.
-We adopt the {\sc Scipy} package to estimate the best-fit line and its 1-sigma region for the simulated sample.
-We use the sample slope value to fit for the observations.
-The comparing results are showing in Figure~\ref{fig:MBII_comp}.
-To estimate the scatter of the sample, we plot the histogram of the offset value of the sample that deviated from their best-fit.
-For MBII model, the result are shown in Figure~\ref{fig:offset_comp}.
-We perform the KS test between the simulation sample and observation sample, and find the p-value are $\sim0.3$ for both \mbh-\mr\ and \mbh-\mstar\ relations.
-Considering that the compared simulation sample have the same uncertainty level with same selection effect, we expect they have the same intrinsic scatter level.
-We adopt {\sc Linmux} to estimate the intrinsic scatter from the overall sample and obtain its value value is $0.25$~dex.
+To quantitatively compare the scaling relations between the simulations and the observations, we use linear line to fit their relations and compare the result.
+Our selection window has a hard cut on the \mbh\ value (vertical direction), and thus the scatter on the host galaxies' properties are larger (horizontal direction).
+Thus, we fit the host's properties (i.e.
+\mr\ and \mstar) as a function of \mbh.
+We adopt the {\sc Scipy} package to estimate the best-fit line and $1-\sigma$ confidence interval for the simulated sample, and use the sample slope value to fit for the observations.
+The comparing results are showing in Figure~\ref{fig:MBII_comp} and~\ref{fig:SAM_comp_withnoise}.
+To estimate the scatter of the sample, we plot the histogram of the residual value, which is the deviation of sample to their best-fit.
+The result are presented in Figure~\ref{fig:offset_comp}.
+We find the standard derivation for observed and MBII sample are both equal to $\sim0.3$~dex and for SAM the value is $\sim0.7$~dex.
+We perform the KS test between observed and MBII sample and infer the p-value as $\sim0.3$ for both \mbh-\mr\ and \mbh-\mstar\ relations.
+Compared to the observational constraints, the MBII sample is processed to have the same uncertainty level and selected by the same selection function; thus we expect the MBII sample and the observational sample have the same intrinsic scatter level.
+We adopt the python package {\sc Linmix} and estimate this intrinsic scatter using the MBII overall sample, result in $0.25$~dex.
 
@@
 \end{tabular}
-\caption{The histogram comparison of the scatter of the sample offset to its best-fit relation.
-The standard derivations are identically equal to $0.3$~dex for both HST sample and MBII sample on both sides.
+\caption{The histogram comparison of the scatter using residual value when fit as linear.
+The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, MBII sample and SAM sample, respectively.
+Compared to the observation and MBII, the horizontal scatters are much larger in SAM's prediction.
 }
@@
  \item[Acknowledgements] 
-%X. Ding acknowledges support by China Postdoctoral Science Foundation Funded Project (No. 2017M622501).
+Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
+These observations are associated with programs \#15115.
+Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555.
+The authors fully appreciate input from Simon Birrer, Matthew A.
+Malkan.
+XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
+JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
+A.S.
+is supported by the EACOA fellowship.
 
 %
-\item[Correspondence] %Correspondence and requests for materials should be addressed to Xuheng Ding ~(email:dxh@astro.ucla.edu).
-\item[Author Contributions] xxx measure xxx, xxx extract the simulation from xx.
+\item[Author Contributions] X.D.
+carried out the HST data analysis, led the comparison to the simulating models and was the principal author of the paper.
+T.T.
+and J.S.
+designed the HST project and selected the AGN sample.
+A.B.
+and T.D.
+ran the MBII simulation and provide the simulation data.
+N.M.
+ran the SAM model and provide and the SAM data.
+X.D, T.T, J.S., A.B., T.D., and N.M.
+interpreted the result.
+
 \end{addendum}
@@
 \textbf{Code availability.} The \lenstronomy, which is used to decompose the AGN image  
-%The data reduction package used to process the SAMI data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr.
+%The data reduction package used to process the SAM data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr.
 To derive the stellar kinematic parameters and the lick absorption line strengths, we use the publicly available penalised pixel-fitting (pPXF) code from M.
@@
 Stellar kinematic data products will become available in the second SAMI Galaxy Survey data release.
+
+\textbf{Correspondence and requests for materials} should be addressed to X.D.~(email:dxh@astro.ucla.edu).
 

### 2019-09-20 NA_paper/scripts/MBHII_MM_putnoise.py

@@ -1,177 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Wed Aug 28 20:15:08 2019
-
-@author: Dartoon
-
-Plot the MBHII MBH-Mr relation and fit their scatter.
-"""
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-import copy
-import sys
-
-import matplotlib.lines as mlines
-from matplotlib import colors
-import matplotlib as mat
-mat.rcParams['font.family'] = 'STIXGeneral'
-
-sys.path.insert(0,'../../py_tools')
-from load_result import load_MBH, load_host_p, load_err
-
-import matplotlib as mpl
-#data=np.loadtxt('../AGN_host_inference_for_npy.txt')
-#print data
-h=0.7
-
-tab_list = ['CID1174', 'CID1281', 'CID206', 'CID216', 'CID237', 'CID255', 'CID3242', 'CID3570',
-            'CID452', 'CID454', 'CID50', 'CID543', 'CID597', 'CID607', 'CID70', 'LID1273',
-            'LID1538', 'LID360', 'XID2138', 'XID2202', 'XID2396', 'CDFS-1', 'CDFS-229',
-            'CDFS-321', 'CDFS-724', 'ECDFS-358', 'SXDS-X1136', 'SXDS-X50', 'SXDS-X717', 'SXDS-X735', 'SXDS-X763', 'SXDS-X969']
-ext_ID = {'XID2202':'LID1622', 'XID2138':'LID1820', 'XID2396':'LID1878', 'CDFS-321':'ECDFS-321'}
-tab_sub_list = copy.deepcopy(tab_list)
-for i in range(len(tab_sub_list)):
-    if tab_sub_list[i] in ext_ID.keys():
-        tab_sub_list[i] = ext_ID[tab_sub_list[i]]
-Lr, M_star, M_r = load_host_p(tab_list,temp='1Gyrs', folder = '../../')  # M_star by Chabrier 
-
-bh_mass_obs = load_MBH(tab_list,tab_sub_list, if_reportHb=0, folder = '../../') #+np.log10(h)
-stellar_mass_obs=  np.log10(10**M_star / 0.54 * 0.91) #+np.log10(h)
-stellar_mass_obs_err= load_err(prop='Mstar', ID=tab_list)
-
-#M_r_obs= M_r
[…]

### 2019-09-20 NA_paper/scripts/my_selection_plots_SAM.py

@@ -16,7 +16,7 @@ import copy
 from load_result import load_MBH, load_host_p, load_err, load_Lbol
 import matplotlib as mpl
 from scipy import stats
-
+np.random.seed(5)  #12345
 
 data_overall = np.loadtxt('../Nicola/realization/lagn_lhost1.dat')
 
@@ -100,7 +100,7 @@ logLbol_obs = load_Lbol(ID=tab_list, folder = '../../')
 logLedd_obs = 38. + np.log10(1.2) + bh_mass_obs
 logEddR_obs = logLbol_obs - logLedd_obs
 
-plt.errorbar(bh_mass_obs, logEddR_obs, c='green',linestyle=' ',marker='o',ms=10,mec='k')
+plt.errorbar(bh_mass_obs, logEddR_obs, c='yellow',linestyle=' ',marker='o',ms=10,mec='k')
 plt.xlim([7.15,9.15])
 plt.ylim([-3,1])
 xfill = np.linspace(7.7, 8.6)
@@ -145,10 +145,10 @@ cbar=f.colorbar(panel2[3],ax=obj)
 cbar.ax.tick_params(labelsize=30) 
 
 obj.errorbar(mstar_selected,bhmass_selected,zorder=1,
-             color='red',label='Simulated population',linestyle=' ',marker='o',ms=10,mec='k')
+             color='red',label='SAM population',linestyle=' ',marker='o',ms=10,mec='k')
 obj.errorbar(stellar_mass_obs,bh_mass_obs, 
 #             xerr = [abs(M_r_obs_err[:,0]),abs(M_r_obs_err[:,1])], yerr=np.ones(len(bh_mass_obs))*0.4, 
-             zorder=1,color='green',label='Observed population',
+             zorder=100,color='yellow',label='Observed population',
              linestyle=' ',marker='o',ms=10,mec='k')
 
 ##Fit y as function of x
@@ -202,7 +202,7 @@ obj.tick_params(labelsize=30)
 obj.set_ylabel(r'log(M$_{\rm BH}$/M$_{\odot}$)',fontsize=30)
 obj.set_xlabel('log(M$_{*}$/M$_{\odot}$)',fontsize=30)
 obj.legend(loc='upper left',fontsize=21,numpoints=1)
-#plt.savefig("SAM_MM.pdf")
[…]

### 2019-09-21 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
Share to Tommaso

@@
 \item{McWilliams Center for Cosmology, Dept. of Physics, Carnegie Mellon University, Pittsburgh PA 15213, USA}
-\item{INAF?Osservatorio Astronomico di Roma, via Frascati 33, I-00078 Monteporzio, Italy}
+\item{INAF Osservatorio Astronomico di Roma, via Frascati 33, I-00078 Monteporzio, Italy}
 \end{affiliations}
@@
 In theory, positive evolution of BH is also predicted by several simulation projects independently.
-So far, the simulations have reproduced the relations which have a good agreement to the observational sample from local to intermediate redshift ($z<1$).
+So far, the simulations have reproduced these relations which have a good agreement to the observational sample from local to intermediate redshift ($z<1$).
 It is crucial to extend this study to higher redshift ($z>1$), where the predicted relations are more sensitive to the initial assumptions and any inconsistency would help to pinpoint the incorrect ones.
-To this end, we use a sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) to make a direct comparison to the predicted sample by two independent state-of-the-art simulation projects: MassiveBlack-II (MBII) and semi-analytic models (SAMs).
-We adopt \hst\ to take images of the 32 AGNs in multi-bands and deriving the trustworthy stellar mass and use the reliable broad \halpha\ emission lines by Subaru/FMOS to estimate the \mbh.
-Taking the measurement uncertainty and selection bias into account, %by adopting the same selection function to choose the simulating sample,
-we find that both models agree well with the data, \ding{However...} in terms of the central distribution and scatters.
-Considering the two models use very different recipes, their agreements to the data indicate the existence of a causal connection between BH and the host galaxy, which could not be explained by purely a stochastic process.
-The intrinsic scatter of our high-$z$ sample is close to simulations and local ones, which is against the central limit theorem.
-To some extend, our result attests that there is a physical connection induces an ordering so that the more massive black holes are linked to the more massive masses.
+To this end, we use a sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) to make a direct comparison to the predicted sample using two independent state-of-the-art simulation projects: MassiveBlack-II (MBII) and semi-analytic models (SAM).
+We adopt \hst\ to take the  AGN image in multi-bands to derive the trustworthy host galaxies properties and use the reliable broad \halpha\ emission lines by Subaru/FMOS to estimate the \mbh.
+Taking the selection bias into account, %by adopting the same selection function to choose the simulating sample,
+we find that both MBII and SAM agree well with the data, in terms of the central distribution.
+However, when taking the measurement uncertainty into account and comparing the scatter, the observations are more consistent with the MBII sample ($\sim0.3$~dex), than the SAM one ($\sim0.7$~dex).
+In this respect, our observational constraints are able to distinguish the two models, indicating that the recipe by MBII (AGN feedback driven) is more rather than the SAM one (galaxy interaction driven).
+Moreover, the intrinsic scatter of our high-$z$ sample is not larger than the local sample, which is against the central limit theorem (a purely stochastic process).
+To some extent, our result attests that there has to be a causal link between SMBH and its host galaxy to induce an ordering so that the more massive black holes are tightly linked to the more massive galaxies.
 
@@
 %\section{Introduction}
-The discovery of the correlations between the masses (\mbh) of supermassive black holes (SMBH) and the properties of their host galaxies, such as absolute magnitude ($Mag$) and stellar mass (\mstar), indicates that the growth of SMBH could be connected to its host galaxy formation.
+The discovery of the correlations between the masses (\mbh) of supermassive black holes (SMBH) and the properties of their host galaxies, such as absolute magnitude ($Mag$) and stellar mass (\mstar), indicates that the growth of SMBH could be connected to its host galaxy formation~\cite{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
 So far, the origin that drives this connection is still unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim$10 kpc).
@@
 In this scenario, the activity of AGN accretion heats and unbinds significant fractions of the gas and inhibits star formation.
-In addition, there are other models have been proposed that the connection between SMBH and their hosts are connected not in a direct manner but assuming that they share a common gas supply~\cite{Cen2015, Menci2016}.
-Furthermore, without any physical mechanisms, it has been proposed that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations [ref].
+In addition, there are other models that have been proposed that the connection between SMBH and their hosts are connected not in a direct manner but assuming that they share a common gas supply~\cite{Cen2015, Menci2016}.
+Furthermore, without any physical mechanisms, it has been proposed that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations~\cite{Peng2007, Jahnke2011, Hirschmann2010}.
 In this central limit theorem, a stochastic cloud at high-$z$ (higher scatter) would end up with the scaling relations (lower scatter) as observed today.
 
-To understand this connection, the recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have analyzed the scaling relations to intermediate redshift {($0.3<z<1$)} by studying the active galactic nuclei (AGN) using {\it Hubble Space Telescope} ({\it HST}) and found an evolution that the growth of SMBHs predated to their host galaxies.
-However, the observational evidence of evolution at high-$z$ is under debated as it relies on our understanding of systematic uncertainties and selection effects.
+To understand this connection, recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have analyzed the scaling relations to intermediate redshift {($0.3<z<1$)} by studying the active galactic nuclei (AGN) using {\it Hubble Space Telescope} ({\it HST}) and found an evolution that the growth of SMBHs predated to their host galaxies.
+However, the observational evidence of evolution at high-$z$ is under debated as it relies on our understanding of systematic uncertainties and selection effects~\cite{Lauer2007}.
 It has been realized that the improper way to consider the uncertainties and selection effects could result in an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.
@@
 Simulation models are effective to help understand this connection and rule out the theories/assumptions which could not be verified by the observations.
-In the simulation test, the systematic uncertainties and selection bias would be easy to account for.
-Recent studies by several simulation projects have made predictions which is in good agreement with the analysis by the observations at intermediate redshift range.
+In simulation test, the systematic uncertainties and selection bias would be easy to account for.
+Recent studies by several simulation projects have made predictions which are in good agreement with the observations at the intermediate redshift range ($z<1$).
 For example, the state-of-the-art cosmological hydrodynamical simulations of structure formation (MassiveBlackII) have compared the predicted scaling relations to the \hst\ observation at $0.3<z<1$ and predict a positive evolution that SMBH growth predates the host galaxy~\cite{DeG++15}.
 Several others works have investigated the scaling relations using large-volume simulations, resulting in well matches to the local relation with some redshift evolution, including approaches using the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014}.
-Besides hydrodynamic simulations, semi-analytic models~\cite{Menci2014, Menci2016} also have made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}.
-However, to date, the comparisons to the scaling relations by high-resolution sample (i.e., imaged by \hst) are still limited at $z<1$ due to the limitation of the observations.
+Besides hydrodynamic simulations, the semi-analytic models~\cite{Menci2014, Menci2016} also made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}.
+However, to date, the comparisons to the observed scaling relations by high-resolution \hst\ imaging sample are still limited within $z<1$ due to the limitation of the observations.
 
@@
 	%mention the scatter.
-To extend the comparison to the simulation models to higher redshift, we collected a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from three X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}.
+To extend the range, we studied a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from three X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}.
 The redshift range of our targets is chosen to be high enough ($z>1$) to detect the existence of the evolution offsets and make the comparison to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming.
-We selected our AGN sample in a well-defined window as in Figure~\ref{fig:AGN_select}, based on the \mbh\ and Eddington ratio \ding{Do we plot figure1 again, or cite to the QSO I paper?}.
-As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias and the Eddington ratio are mostly above $0.1$ to ensure the homogeneity.
+We selected our AGN sample in a well-defined window as in Figure~\ref{fig:AGN_select}, based on the \mbh\ and Eddington ratio \ding{Do we plot figure1 here again, or cite to the QSO I paper?}.
+As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias.
+In addition, the Eddington ratios are mostly above $0.1$ to ensure the homogeneity.
 
@@
 We employ the \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt the state-of-the-art technique to perform the 2-D flux profile decomposition to infer the light of the host galaxy.
-Moreover, 21/23 systems have \hst/ACS imaging data, which enable us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar).
+Moreover, 21/23 systems have \hst/ACS imaging data, which enable us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see Methods).
 %We furthermore combining them with the ground-based photometry to carry out the SED fitting, and thus derive the reliable host rest-frame R band luminosity and stellar mass.
@@
 \includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
-\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function. \ding{More descriptions needed if Figure1 is finally decided to shown.}
+\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function. \ding{More descriptions are needed if Figure1 is finally decided to show.}
 }
@@
 However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as SAM.
-In previous works~\cite{Menci2014, Menci2016}[ref], MBII and SAM have made successful predictions.
-We refer the interested readers to these works for more details.
+In previous works~\cite{Huang2018, DeG++15, Khandai2015, Bhowmick2019, Menci2014, Menci2016}, MBII and SAM have made high successful predictions, and we refer the interested readers to these works for more details.
 
@@
 %Selection effect into account
-To make comparison by the MBII project, we collect a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones.
-To ensure a fair comparison, we take the measurement uncertainty and the selection effect into account with the following process.
-First, we inject the random noise to the simulated sample to mimic the scattering effect that caused by the uncertainty.
-The assumed uncertainty levels are comparable to the realistic ones, i.e., $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex and $\Delta L_{\rm bol}$=0.03~dex, respectively.
-We then select the sample that falls into the same selection window, as shown in Figure~\ref{fig:selectfunc}.
+Based on MBII project, we collect a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones.
+We take the measurement uncertainty and the selection effect into account to ensure a fair comparison,  with the following process.
+First, we inject the random noise to the simulated sample to mimic the scattering effect caused by the uncertainty.
+The assumed uncertainties are set to be comparable to the realistic levels, i.e., $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex, and $\Delta L_{\rm bol}$=0.03~dex, respectively.
+We then select the sample that falls into the same targeting window to mimic the sample selection process, as shown in Figure~\ref{fig:selectfunc}.
 We investigated the predicted scaling relations, including \mbh-\mr\ and \mbh-\mstar, and compared them to the observational constraints, as shown in Figure~\ref{fig:MBII_comp}.
 From a quick glimpse, one can see that the samples are overlapped with each other, showing a sign of agreement.
-To quantify the level of agreement, we perform the linear regression to fit the simulated relations and estimate the best-fit and 1$-\sigma$ confidence interval.
-We use the same slope value to fit the best intercept value for the observed sample.
-We find that for the \mbh-\mr\ relation, the linear fitting results are almost identical, with $0.06$~dex mismatch.
+To quantify the level of agreement, we perform the linear regression to fit the simulated relations and estimate the best-fit inference and 1$-\sigma$ confidence interval.
+We use the same slope value to obtain the best-fit intercept value for the observed sample.
+We find that for the \mbh-\mr\ relation, the linear fitting results are almost identical, with only $0.06$~dex mismatch.
 For the \mbh-\mstar\ relations, the mismatch ($0.15$~dex) is small and far below 1$-\sigma$ level.
-We also compare the sample by their scatter.
-Calculating the standard derivation of the residual, we find the simulations and the observations have the same scatter value $0.3$~dex.
-Considering that the simulated samples have the same uncertainty and the selection effect, we expect the intrinsic scatter of the scaling relations are similar, which it $0.25$~dex (see METHODS).
+Furthermore, we compare the scatter of the sample by calculating the standard derivation of the residual in the linear regression.
+We find that the simulations and the observations have the same scatter level $0.3$~dex.
+Considering that the simulated samples have the same uncertainty and the selection effect, we expect the intrinsic scatter of the scaling relations are similar, which is $0.25$~dex (see METHODS).
 
@@
 \includegraphics[width=1.0\linewidth]{MBII_selectfunc.pdf}
-\caption{The selection window as adopted for selecting the MBII simulated sample.
+\caption{The same selection window as adopted for selecting the MBII simulated sample.
 The yellow background clouds shows the overall sample at $z=1.5$.
-We add the random uncertainty to the simulation and select the ones located in the selection window (i.e.
-red region).
-The yellow dots are the observed sample.}
+We add the random uncertainty to the simulation and select the ones fall into the targeting region (i.e.
+red colored).
+The yellow dots are the HST sample.}
 \label{fig:selectfunc}
@@
 \end{tabular}
-\caption{  In the left and right panel, we present the \mbh-\mr\ and \mbh-\mstar\ correlation between the observed scaling relations (green dots) and the predicted samples (red dots) by the MBII simulation, respectively.
-The MBII predicted sample are treated to have the same uncertainty and selection effect as the observational ones.
-The red line is the best-fit result for the simulated sample, with colored region indicating the $1-\sigma$ confidence interval.
-We use the same slope value to fit for observed sample and the green line shows the best-fit result.
+\caption{  In the left and right panel, we present the \mbh-\mr\ and \mbh-\mstar\ correlation between the observed scaling relations (yellow dots) and the predicted samples (red dots) by the MBII simulation, respectively.
+The MBII predicted sample is treated to have the same uncertainty and selection effect as the observational ones.
+The red line is the best-fit result for the simulated sample, with the red-color region indicating the $1-\sigma$ confidence interval.
+We use the same slope value to fit for the observed sample, and the green line shows the best-fit result.
 The yellow grids in the background are the overall sample that predicted in the MBII simulation.
@@
 
-We also make comparisons of our observed scaling relations to the predictions by SAM model.
-We consider the sample at $z=1.5$ epoch for two sample sets, including the overall sample and the selected sample.
-Rather than use N-body simulation to produce individual galaxies, the SAM model use the density clouds to describe the possibility of the samples, as shown in Figure~\ref{fig:SAM_comp}.
+We also make comparisons of our observed scaling relations to the predictions by the SAM model.
+Rather than N-body simulation, which produces individual simulating objects, the SAM model uses the density clouds to describe the possibility of the samples.
+We consider the sample at $z=1.5$ epoch for two sample sets, including the overall sample and the selected sample, as shown in Figure~\ref{fig:SAM_comp}.
 We find that considering the selecting effect, the direct prediction by SAM is well matched to the observed relations.
@@
 But if consider the scatter in the same way, the SAM have large scatter?}
-However this is not a proper comparisons yet, since this direct comparison does not include the scattering effect by the measurement uncertainty.
-To make a valid comparison, we generate a random the overall sample for SAM based on the possibility distribution.
+Yet this is not a proper comparison since the direct sample from SAM does not include the scattering effect by the measurement uncertainty.
+To make a valid comparison, we first randomly generate the overall sample for SAM based on the possibility clouds.
 Then, same as MBII's case, we inject the random uncertainty to the sample to take the uncertainty effect into account and select the sample the selection window.
 The resulting comparisons are shown in Figure~\ref{fig:SAM_comp_withnoise}.
-We find that the best-fit result by the SAM model are well matched to the observation.
-However, the horizontal scatter of the SAM model are overwhelmingly larger.
-This larger scatter is a combination result by the SAM distribution, uncertainty and selection effect.
+We find that the best-fit result by the SAM model is well matched to the observation.
+However, the scatter of the SAM model are overwhelmingly larger ($0.7$~dex) than the observation.
+This larger scatter is a combination result by the SAM distribution, uncertainty, and selection effect.
 
@@
 
-To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
+ \ding{We can put this paragraph into Method or even delete.} To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
 For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3.
@@
 \includegraphics[width=0.9\linewidth]{comp_host_ratio.pdf}
-\caption{The comparison histogram of the host ratios among three referred samples, with median value indicated. The same selection effect are considered.
+\caption{The comparison histogram of the host ratios among three referred samples, median value indicated. The same selection effect are considered for the simulation sample.
 }
@@
 
-Without any physical mechanisms, the central limit theorem assumes that the scaling relations are the results by the random merger from a stochastic cloud at higher redshift.
+In terms of their central distribution, the MBII simulation and SAM model both demonstrate an excellent agreement to the observational constraints.
+However, when considering the scattering effect by the measurement uncertainty, the scatter in MBII simulation is consistent to the observational one ($\sim0.3$~dex) and SAM sample has much larger scatter ($\sim0.7$~dex).
+Given that the two models adopt very different assumptions, recipes, and initial conditions, our result shows that the mechanism (AGN feedback driven) by MBII is more favorable.
+An explanation for the larger scatter in the SAM model is that its BH feeding is by merger driven with more stochasticities in the scaling relations.
+In particular, the SAM cloud extends to the high \mbh\ with low stellar mass, which may not exist.
+\ding{To Nicola: is that possible to change the assumption in SAM to make the relations tighter?} The consistency between MBII and observations indicates that there has to be a causal link between SMBH and its host galaxy to generate an ordering during their evolution; as a result, more massive BHs are linked to more massive galaxies {\it tightly}.
+
+Without any physical mechanisms, the central limit theorem~\cite{Peng2007, Jahnke2011, Hirschmann2010} assumes that the scaling relations are caused by the random merger from a stochastic cloud at earlier universe.
 In this scenario, the scatter of the scaling relations has to be larger with the increasing of redshift.
 However, the observed scatter of our high-$z$ sample do not present this feature.
-In fact, our inferred intrinsic scatter of the observed sample is only $\sim0.25$~dex, which is no more than the typical scatter at local relations in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}.
-Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate which,
-since we use the MBII overall sample as proxy to estimate this value.
-Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), result in an overestimating of the error-budget and thus underestimating of intrinsic scatter.
+In fact, our inferred intrinsic scatter of the observed sample is $\sim0.25$~dex, which is no more than the typical scatter at local relations in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}.
+Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the MBII overall sample as a proxy to estimate our value.
+Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), resulting in an overestimating of the error-budget and thus underestimating of intrinsic scatter.
 Still, the evidence of the low scatter in our measurements is likely to be true, which is against the central limit theorem and suggests that the physical mechanisms between the SMBH and its host galaxy are likely to exist.
 
-The MBII model and SAM model both demonstrate an excellent agreement to the observed data; however, they adopted very different assumptions, recipes, and initial conditions.
-From another perspective to understand this agreement, there has to be a causal link between SMBH and its host galaxy to generate an ordering during their evolution, so that more massive BHs are linked to more massive galaxies with some intrinsic scatter.
-Once the selection function is well defined, the tight correlations would show up along with the selected sample.
-
-Limited by the observations and the fact they are in good agreements to MBII and SAM, one can not rule out one simulation model from the other.
-Of course, there are differences between two simulation models.
-For example, the SAM sample trends to have more scatter than the MBII, especially before applying any selection function.
-More scatter could arise in SAM because the black hole feeding in this model is merger driven and so there is more stochasticities.
-In particular, the SAM cloud extends to the high \mbh\ with low stellar mass, which may not exist.
-These objects are usually with low Eddington ratio; thus an extension of this study to this region would be useful to discriminate between models.
-
-Extending the redshift range of this study would also be very beneficial, giving that the scaling relation in the simulations shows different evolution at the different stage of the Universe.
+Extending the redshift range of this study would be very beneficial to this study, giving that the scaling relation in the simulations shows different evolution at the different stage of the universe.
 For higher redshift, the {\it James Webb Space Telescope} may provide high-quality imaging data of AGNs at redshift up to $z\sim7$.
@@
 %1. Imaging data. 2. Inferring host light. 3. Color inference. Rest frame R band and stellar mass.
-We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets, to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman).
+The detailed description for the analysis is in the companion paper (referring as D19).
+Here we only present a quick overview of this study.
+We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ (according to the redshift of the targets) to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman).
 We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to co-add the final image with pixel scale as 0\farcs0642.
@@
 Based on the reduced $\chi^2$, we are capable of evaluating the performance of each PSF.
-We adopt the result from the top-ranked-eight PSFs and infer the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.
+We adopt the result from the top-ranked-eight PSFs and using the weighting process to obtain the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.
 
 21/32 images in the COSMOS survey also have imaging data in the ACS/F814W with drizzled pixel scale as 0\farcs03, providing us the multi-band information.
-We decompose the AGN image in the ACS band to obtain the color of the host.
-We find that the 1~Gyr template could well match their color from which we estimate the rest-frame R band luminosity and stellar mass.
+We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3's result to infer the host color.
+We find that the 1~Gyr template could well match their color, see Figure~5 in D19, from which we estimate the rest-frame R band luminosity and stellar mass.
 A Salpeter initial mass function is employed consistently to the observed and simulated sample.
@@
 %How the fitting is done. The comparing of the histogram and the KS test. The scatter. Figures.
-To quantitatively compare the scaling relations between the simulations and the observations, we use linear line to fit their relations and compare the result.
-Our selection window has a hard cut on the \mbh\ value (vertical direction), and thus the scatter on the host galaxies' properties are larger (horizontal direction).
-Thus, we fit the host's properties (i.e.
-\mr\ and \mstar) as a function of \mbh.
-We adopt the {\sc Scipy} package to estimate the best-fit line and $1-\sigma$ confidence interval for the simulated sample, and use the sample slope value to fit for the observations.
+To quantify the agreement between the simulation and the observation, we use a linear regression to fit their relations and compare the result.
+Our selection window has a hard cut on the \mbh\ value (i.e., vertical direction in Figure~\ref{fig:MBII_comp}), and thus the scatter on the host galaxies' properties are larger (horizontal direction).
+Thus, we fit the host's properties (i.e., \mr\ and \mstar) as a function of \mbh.
+We adopt the {\sc Scipy} package to estimate the best-fit inference and $1-\sigma$ confidence interval for the simulated sample.
+We then use the sample slope value to fit for the observations.
 The comparing results are showing in Figure~\ref{fig:MBII_comp} and~\ref{fig:SAM_comp_withnoise}.
-To estimate the scatter of the sample, we plot the histogram of the residual value, which is the deviation of sample to their best-fit.
-The result are presented in Figure~\ref{fig:offset_comp}.
-We find the standard derivation for observed and MBII sample are both equal to $\sim0.3$~dex and for SAM the value is $\sim0.7$~dex.
+To estimate the scatter of the sample, we plot the histogram of the residual, i.e., the sample deviation to their best-fit.
+The result is presented in Figure~\ref{fig:offset_comp}.
+We find the standard derivation for observed and MBII sample are consistent and both equal to $\sim0.3$~dex; however for SAM the scatter value is much larger ($\sim0.7$~dex).
 We perform the KS test between observed and MBII sample and infer the p-value as $\sim0.3$ for both \mbh-\mr\ and \mbh-\mstar\ relations.
-Compared to the observational constraints, the MBII sample is processed to have the same uncertainty level and selected by the same selection function; thus we expect the MBII sample and the observational sample have the same intrinsic scatter level.
-We adopt the python package {\sc Linmix} and estimate this intrinsic scatter using the MBII overall sample, result in $0.25$~dex.
+Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the MBII sample and the observational sample have the same intrinsic scatter level.
+We adopt the python package {\sc Linmix} and estimate this intrinsic scatter based on the MBII overall sample, and obtain $0.25$~dex.
 
@@
 The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, MBII sample and SAM sample, respectively.
-Compared to the observation and MBII, the horizontal scatters are much larger in SAM's prediction.
+Compared to the observation and MBII, the scatters are much larger in SAM's prediction.
 }
@@
 \section*{Additional information}
-\textbf{Code availability.} The \lenstronomy, which is used to decompose the AGN image  
+%\textbf{Code availability.} The \lenstronomy, which is used to decompose the AGN image  
 %The data reduction package used to process the SAM data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr.

### 2019-09-21 NA_paper/scripts/my_selection_plots_MBII.py

@@ -176,7 +176,7 @@ obj.errorbar(stellar_mass_obs,bh_mass_obs,
 #fit_fixm=scipy.optimize.curve_fit(lfit_fixm, x_obs, y_obs)
 ##fit_err=np.sqrt(np.diag(fit[1]))
 #y_obs_space=lfit_fixm(x_space,fit_fixm[0])
-#plt.plot(x_space,y_obs_space,color='green',linewidth=3)
+#plt.plot(x_space,y_obs_space,color='yellow',linewidth=3)
 #print "mismatch:", fit_fixm[0]- fit[0][1]
 
 #Fit x as function of y
@@ -196,7 +196,7 @@ x_obs, y_obs = stellar_mass_obs, bh_mass_obs
 fit_fixm=scipy.optimize.curve_fit(lfit_fixm, y_obs, x_obs)
 #fit_err=np.sqrt(np.diag(fit[1]))
 x_obs_space=lfit_fixm(y_space,fit_fixm[0])
-plt.plot(x_obs_space,y_space,color='green',linewidth=3)
+plt.plot(x_obs_space,y_space,color='yellow',linewidth=3)
 print "mismatch:", fit_fixm[0]- fit[0][1]  #In BH mass offset space
 
 
@@ -324,7 +324,7 @@ x_obs, y_obs = M_r_obs, bh_mass_obs
 fit_fixm_1=scipy.optimize.curve_fit(lfit_fixm_1, y_obs, x_obs)
 #fit_err_1=np.sqrt(np.diag(fit_1[1]))
 x_space_obs=lfit_fixm_1(y_space,fit_fixm_1[0])
-plt.plot(x_space_obs,y_space,color='green',linewidth=3)
+plt.plot(x_space_obs,y_space,color='yellow',linewidth=3)
 
 print "\n\nPlot M-Mag relation:"
 print "mismatch:", fit_fixm_1[0]- fit_1[0][1]

### 2019-09-21 NA_paper/scripts/my_selection_plots_SAM.py

@@ -188,7 +188,7 @@ x_obs, y_obs = stellar_mass_obs, bh_mass_obs
 fit_fixm=scipy.optimize.curve_fit(lfit_fixm, y_obs, x_obs)
 #fit_err=np.sqrt(np.diag(fit[1]))
 x_obs_space=lfit_fixm(y_space,fit_fixm[0])
-plt.plot(x_obs_space,y_space,color='green',linewidth=3)
+plt.plot(x_obs_space,y_space,color='yellow',linewidth=3)
 print "mismatch:", fit_fixm[0]- fit[0][1]  #In BH mass offset space
 
 
@@ -316,7 +316,7 @@ x_obs, y_obs = M_r_obs, bh_mass_obs
 fit_fixm_1=scipy.optimize.curve_fit(lfit_fixm_1, y_obs, x_obs)
 #fit_err_1=np.sqrt(np.diag(fit_1[1]))
 x_space_obs=lfit_fixm_1(y_space,fit_fixm_1[0])
-plt.plot(x_space_obs,y_space,color='green',linewidth=3)
+plt.plot(x_space_obs,y_space,color='yellow',linewidth=3)
 
 print "\n\nPlot M-Mag relation:"
 print "mismatch:", fit_fixm_1[0]- fit_1[0][1]

### 2019-09-30 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
Update paper and figures based on John's suggenstion

@@
 	%mention the scatter.
-To extend the range, we studied a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from three X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}.
+To extend the range, we have been studing a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from three X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008} (Ding et al.
+submitted - D19 hereafter ).
 The redshift range of our targets is chosen to be high enough ($z>1$) to detect the existence of the evolution offsets and make the comparison to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming.
-We selected our AGN sample in a well-defined window as in Figure~\ref{fig:AGN_select}, based on the \mbh\ and Eddington ratio \ding{Do we plot figure1 here again, or cite to the QSO I paper?}.
-As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias.
+We selected our AGN sample in a well-defined window based on the \mbh\ and Eddington ratio, as shown in Figure~1 in D19.
+As shown in that Figure, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias.
 In addition, the Eddington ratios are mostly above $0.1$ to ensure the homogeneity.
@@
 We employ the \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt the state-of-the-art technique to perform the 2-D flux profile decomposition to infer the light of the host galaxy.
-Moreover, 21/23 systems have \hst/ACS imaging data, which enable us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see Methods).
+Moreover, 21/23 systems have \hst/ACS imaging data, which enable us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see Methods and the descriptions in D19).
 %We furthermore combining them with the ground-based photometry to carry out the SED fitting, and thus derive the reliable host rest-frame R band luminosity and stellar mass.
 
-\begin{figure}[t]
-\includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
-\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function. \ding{More descriptions are needed if Figure1 is finally decided to show.}
-}
-\label{fig:AGN_select}
-\end{figure}
+%\begin{figure}[t]
+%\includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
+%\caption{The selection for the 32 AGN sample.
+The top and right panels are the BH mass function and Eddington ratio function.
+\ding{More descriptions are needed if Figure1 is finally decided to show.}
+%}
+%\label{fig:AGN_select}
+%\end{figure}
 
@@
 These two models are based on independent model strategies, i.e., hydrodynamic simulation for MBII and semi-analytic model for SAM, respectively.
-The MassiveBlack-II (MBII) simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
+The MBII simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
 The large simulation volume enables the simulating objects to evolve independently; the high enough mass and spatial resolution meet the requirements for the object details.
@@
 First, we inject the random noise to the simulated sample to mimic the scattering effect caused by the uncertainty.
-The assumed uncertainties are set to be comparable to the realistic levels, i.e., $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex, and $\Delta L_{\rm bol}$=0.03~dex, respectively.
+We assume uncertainties are comparable to the realistic levels, i.e., $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex, and $\Delta L_{\rm bol}$=0.03~dex, respectively.
 We then select the sample that falls into the same targeting window to mimic the sample selection process, as shown in Figure~\ref{fig:selectfunc}.
-We investigated the predicted scaling relations, including \mbh-\mr\ and \mbh-\mstar, and compared them to the observational constraints, as shown in Figure~\ref{fig:MBII_comp}.
+Considering that the mass relations between SMBH and its host are more substaintial, we focus on the predicted \mbh-\mstar relations and compared to the observational constraints, as shown in Figure~\ref{fig:MM_comp} (left panel).
 From a quick glimpse, one can see that the samples are overlapped with each other, showing a sign of agreement.
-To quantify the level of agreement, we perform the linear regression to fit the simulated relations and estimate the best-fit inference and 1$-\sigma$ confidence interval.
-We use the same slope value to obtain the best-fit intercept value for the observed sample.
-We find that for the \mbh-\mr\ relation, the linear fitting results are almost identical, with only $0.06$~dex mismatch.
-For the \mbh-\mstar\ relations, the mismatch ($0.15$~dex) is small and far below 1$-\sigma$ level.
+To quantify the agreement level, we perform the linear regression to fit the simulated relations and estimate the best-fit inference and 1$-\sigma$ confidence interval.
+To make direct comparison, we fix the same slope value and obtain the best-fit intercept value for the observation.
+We find that, for the \mbh-\mstar\ relations, the mismatch ($0.15$~dex) is small and far below 1$-\sigma$ level.
 Furthermore, we compare the scatter of the sample by calculating the standard derivation of the residual in the linear regression.
@@
 \begin{figure}[t]
-\includegraphics[width=1.0\linewidth]{MBII_selectfunc.pdf}
+\includegraphics[width=1.2\linewidth]{MBII_selectfunc.pdf}
 \caption{The same selection window as adopted for selecting the MBII simulated sample.
-The yellow background clouds shows the overall sample at $z=1.5$.
+The brown background clouds shows the overall MBII sample at $z=1.5$.
 We add the random uncertainty to the simulation and select the ones fall into the targeting region (i.e.
-red colored).
-The yellow dots are the HST sample.}
+blue colored).
+The orange dots are the \hst\ observed sample.}
 \label{fig:selectfunc}
@@
 \begin{tabular}{c c}
-\includegraphics[width=0.5\linewidth]{MBII_ML.pdf} &
-\includegraphics[width=0.5\linewidth]{MBII_MM.pdf} \\
+\includegraphics[trim = 0mm 0mm 65mm 0mm, clip, width=0.47\linewidth]{MBII_MM.pdf} &
+\includegraphics[trim = 0mm 0mm 65mm 0mm, clip, width=0.47\linewidth]{SAM_MM_consider_nois.pdf} \\
 \end{tabular}
-\caption{  In the left and right panel, we present the \mbh-\mr\ and \mbh-\mstar\ correlation between the observed scaling relations (yellow dots) and the predicted samples (red dots) by the MBII simulation, respectively.
-The MBII predicted sample is treated to have the same uncertainty and selection effect as the observational ones.
-The red line is the best-fit result for the simulated sample, with the red-color region indicating the $1-\sigma$ confidence interval.
-We use the same slope value to fit for the observed sample, and the green line shows the best-fit result.
-The yellow grids in the background are the overall sample that predicted in the MBII simulation.
-%{\bf For the right panel, I currently adopt a 3 Gyrs template for the HST sample...}
+\caption{In the left panel, we present the comparison of the  \mbh-\mstar\ correlation between the observation (orange dots) and the MBII predicted samples (blue dots).
+The predicted sample is treated to have the same uncertainty and selection effect as the observational ones.
+The blue line is the best-fit result for the MBII sample, with the colored region indicating the $1-\sigma$ confidence interval.
+We use the same slope value to fit for the observed sample, and the orange line shows the best-fit result.
+The brown grids in the background are the overall sample that predicted by the MBII simulation.
+We present the comparison with the SAM sample (green color) in the right panel.
 }
-\label{fig:MBII_comp}
+\label{fig:MM_comp}
 \end{figure*}
@@
 We also make comparisons of our observed scaling relations to the predictions by the SAM model.
-Rather than N-body simulation, which produces individual simulating objects, the SAM model uses the density clouds to describe the possibility of the samples.
-We consider the sample at $z=1.5$ epoch for two sample sets, including the overall sample and the selected sample, as shown in Figure~\ref{fig:SAM_comp}.
+Rather than N-body simulation which produces individual simulating objects, the SAM model uses the density clouds to describe the possibility of the samples.
+%We consider the sample at $z=1.5$ epoch for two sample sets, including the overall sample and the selected sample, as shown in Figure~\ref{fig:SAM_comp}.
 We find that considering the selecting effect, the direct prediction by SAM is well matched to the observed relations.
@@
 But if consider the scatter in the same way, the SAM have large scatter?}
-Yet this is not a proper comparison since the direct sample from SAM does not include the scattering effect by the measurement uncertainty.
-To make a valid comparison, we first randomly generate the overall sample for SAM based on the possibility clouds.
+%Yet this is not a proper comparison since the direct sample from SAM does not include the scattering effect by the measurement uncertainty.
+To make the direct comparison, we first randomly generate an overall SAM sample based on the possibility clouds at $z=1.5$ epoch.
 Then, same as MBII's case, we inject the random uncertainty to the sample to take the uncertainty effect into account and select the sample the selection window.
-The resulting comparisons are shown in Figure~\ref{fig:SAM_comp_withnoise}.
+The resulting comparison of the  \mbh-\mstar\ relation are shown in Figure~\ref{fig:MM_comp} (right panel).
 We find that the best-fit result by the SAM model is well matched to the observation.
@@
 
-\begin{figure*}[t]%[!b]
-\begin{tabular}{c c}
-\includegraphics[trim = 0mm 0mm 24mm 0mm, clip, width=0.45\linewidth]{SAM_ML.pdf} &
-\includegraphics[trim = 30.5mm 0mm 0mm 0mm, clip, width=0.45\linewidth]{SAM_MMstar.pdf} \\
-\end{tabular}
-\caption{Similar to the Figure~\ref{fig:MBII_comp}, but for a direct comparison to the observation using SAM's model.
+%\begin{figure*}[t]%[!b]
+%\begin{tabular}{c c}
+%\includegraphics[trim = 0mm 0mm 24mm 0mm, clip, width=0.45\linewidth]{SAM_ML.pdf} &
+%\includegraphics[trim = 30.5mm 0mm 0mm 0mm, clip, width=0.45\linewidth]{SAM_MMstar.pdf} \\
+%\end{tabular}
+%\caption{Similar to the Figure~\ref{fig:MM_comp}, but for a direct comparison to the observation using SAM's model.
 The blue background contours show the possibility distribution for the overall sample, and the red contours indicate the distributions after considering the selecting effect.
@@
 Note that this comparison has not taken the measurement uncertainties into account yet.
-}
-\label{fig:SAM_comp}
-\end{figure*}
+%}
+%\label{fig:SAM_comp}
+%\end{figure*}
 
-\begin{figure*}[t]%[!b]
-\begin{tabular}{c c}
-\includegraphics[width=0.45\linewidth]{SAM_ML_consider_nois.pdf} &
-\includegraphics[width=0.45\linewidth]{SAM_MM_consider_nois.pdf} \\
-\end{tabular}
-\caption{Same as the Figure~\ref{fig:MBII_comp}, but for the SAM models.}
-\label{fig:SAM_comp_withnoise}
-\end{figure*}
-
- \ding{We can put this paragraph into Method or even delete.} To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
+ \ding{We can put the following paragraph into Method or even remove it.} To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
 For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3.
@@
 %0. The inferred host flux ratio by SED decomposition is consistent to the 2-D image decomposition, indicating the fidelity of these approaches?\\
-%1. HST seems to reach its higher limit. In the future, the JWST is very promising to realize the evolution scenario at even higher redshift.\\
+%1. \hst\ seems to reach its higher limit. In the future, the JWST is very promising to realize the evolution scenario at even higher redshift.\\
 %On the simulation side:
@@
 To quantify the agreement between the simulation and the observation, we use a linear regression to fit their relations and compare the result.
-Our selection window has a hard cut on the \mbh\ value (i.e., vertical direction in Figure~\ref{fig:MBII_comp}), and thus the scatter on the host galaxies' properties are larger (horizontal direction).
-Thus, we fit the host's properties (i.e., \mr\ and \mstar) as a function of \mbh.
+Our selection window has a hard cut on the \mbh\ value (i.e., vertical direction in Figure~\ref{fig:MM_comp}), and thus the scatter on the host properties are larger (horizontal direction).
+Thus, we fit the host properties (i.e., \mstar) as a function of \mbh.
 We adopt the {\sc Scipy} package to estimate the best-fit inference and $1-\sigma$ confidence interval for the simulated sample.
 We then use the sample slope value to fit for the observations.
-The comparing results are showing in Figure~\ref{fig:MBII_comp} and~\ref{fig:SAM_comp_withnoise}.
+The comparing results are showing in Figure~\ref{fig:MM_comp}.
 To estimate the scatter of the sample, we plot the histogram of the residual, i.e., the sample deviation to their best-fit.
-The result is presented in Figure~\ref{fig:offset_comp}.
-We find the standard derivation for observed and MBII sample are consistent and both equal to $\sim0.3$~dex; however for SAM the scatter value is much larger ($\sim0.7$~dex).
-We perform the KS test between observed and MBII sample and infer the p-value as $\sim0.3$ for both \mbh-\mr\ and \mbh-\mstar\ relations.
+The result is presented in Figure~\ref{fig:offset_comp} (left panel).
+We find the standard derivation of the residual for observed and MBII sample are both equal to $\sim0.3$~dex; however, for SAM, the scatter value is much larger ($\sim0.7$~dex).
+We perform the KS test of the scatter distribution between observed and MBII sample and infer the p-value as $\sim0.3$.
 Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the MBII sample and the observational sample have the same intrinsic scatter level.
-We adopt the python package {\sc Linmix} and estimate this intrinsic scatter based on the MBII overall sample, and obtain $0.25$~dex.
+We adopt the python package {\sc Linmix} to estimate this intrinsic scatter based on the MBII overall sample and obtain $0.25$~dex.
+
+We also present the comparison of the \mbh-\mr\ relations in Figure~\ref{fig:ML_comp} and the comparison of the scatter in Figure~\ref{fig:offset_comp} (right panel).
+The results are similar to \mbh-\mstar\ relations.
+
+\begin{figure*}[t]%[!b]
+\begin{tabular}{c c}
+\includegraphics[trim = 0mm 0mm 61mm 0mm, clip, width=0.47\linewidth]{MBII_ML.pdf} &
+\includegraphics[trim = 0mm 0mm 61mm 0mm, clip, width=0.47\linewidth]{SAM_ML_consider_nois.pdf} \\
+\end{tabular}
+\caption{Same as the Figure~\ref{fig:MM_comp}, but for \mbh-\mr\ relation.}
+\label{fig:ML_comp}
+\end{figure*}
 
@@
 \end{tabular}
-\caption{The histogram comparison of the scatter using residual value when fit as linear.
-The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, MBII sample and SAM sample, respectively.
-Compared to the observation and MBII, the scatters are much larger in SAM's prediction.
+\caption{The histogram of the scatter (i.e., residuals in the linear relation).
+The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, MBII sample and SAM sample, respectively, for both \mbh-\mstar\ and \mbh-\mr\ relations.
 }
@@
 \item[Author Contributions] X.D.
-carried out the HST data analysis, led the comparison to the simulating models and was the principal author of the paper.
+carried out the \hst\ data analysis, led the comparison to the simulating models and was the principal author of the paper.
 T.T.
 and J.S.
-designed the HST project and selected the AGN sample.
+designed the \hst\ project and selected the AGN sample.
 A.B.

### 2019-09-30 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
Update abstract by John

@@
 \begin{abstract}
-Supermassive black holes (BH) harbor at the center of galaxies with their masses (\mbh) correlated to the properties of the host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar) known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar).
+Supermassive black holes (BH) are known to reside at the center of massive galaxies.
+In the local Universe, BH masses (\mbh) are tightly correlated to the properties of their host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar), known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar) that are not yet fully understood.
  %Observational results have indicated evidence that this correlation evolves with cosmic time, suggesting a scenario that the BH growth predates their host.
 In theory, positive evolution of BH is also predicted by several simulation projects independently.
-So far, the simulations have reproduced these relations which have a good agreement to the observational sample from local to intermediate redshift ($z<1$).
-It is crucial to extend this study to higher redshift ($z>1$), where the predicted relations are more sensitive to the initial assumptions and any inconsistency would help to pinpoint the incorrect ones.
-To this end, we use a sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) to make a direct comparison to the predicted sample using two independent state-of-the-art simulation projects: MassiveBlack-II (MBII) and semi-analytic models (SAM).
-We adopt \hst\ to take the  AGN image in multi-bands to derive the trustworthy host galaxies properties and use the reliable broad \halpha\ emission lines by Subaru/FMOS to estimate the \mbh.
-Taking the selection bias into account, %by adopting the same selection function to choose the simulating sample,
+Even so, simulations can reproduce these relations over the last eight billion years ($z\lesssim1$).
+However, it is crucial to extend comparisons between observational data and simulations to earlier cosmic epochs ($z>1$), where the predicted relations are more sensitive to the initial assumptions and any inconsistency would help to pinpoint missing physics.
+For this purpose, we have a unique sample of 32 broad-line Active Galactic Nuclei (AGN) at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with the broad \halpha\ emission line, as detected by Subaru/FMOS, providing an accurate assessment of \mbh ~while multi-band \hst\ imaging is used to derive the host galaxies properties (e.g., \mstar).
+We directly compare this sample with two independent state-of-the-art simulations: MassiveBlack-II (MBII) and a semi-analytic model (SAM).
+Taking the selection biases into account, %by adopting the same selection function to choose the simulating sample,
 we find that both MBII and SAM agree well with the data, in terms of the central distribution.
-However, when taking the measurement uncertainty into account and comparing the scatter, the observations are more consistent with the MBII sample ($\sim0.3$~dex), than the SAM one ($\sim0.7$~dex).
-In this respect, our observational constraints are able to distinguish the two models, indicating that the recipe by MBII (AGN feedback driven) is more rather than the SAM one (galaxy interaction driven).
-Moreover, the intrinsic scatter of our high-$z$ sample is not larger than the local sample, which is against the central limit theorem (a purely stochastic process).
+However, when considering measurement uncertainty and the scatter in the scaling relations, the observations are significantly more consistent with the MBII sample ($\sim0.3$~dex), than the SAM ($\sim0.7$~dex).
+In this respect, our observational constraints are able to distinguish between the two models, indicating that the recipe implemented by MBII (i.e., growth regulation through AGN feedback) is preferred over the SAM that does not include AGN feedback.
+Moreover, the intrinsic scatter of our high-$z$ sample is comparable to the local sample thus counter to the expectation from a scenario based on the central limit theorem (a purely stochastic process).
 To some extent, our result attests that there has to be a causal link between SMBH and its host galaxy to induce an ordering so that the more massive black holes are tightly linked to the more massive galaxies.

### 2019-10-03 manuscript/manuscript.tex
Update the stellar tempalte with 0.625 Gyr

@@
 \newcommand{\angstrom}{\text{\normalfont\AA}}
+\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
+
 \makeatletter
@@
 
-\item Black holes masses fall below the knee of the black hole mass function to minimize the selection biases.
-
-\item Eddington ratios are typically above 1\% for most of the sample to further ensure homogeneity.
-
-\item The lower nuclear-to-host ratios of our sample facilitates the galaxy mass measurements, given that they are 
-X-ray selected.
-
-\item \hst/WFC3 imaging of the host galaxy is above the 4000~\angstrom\ break and does not include the broad \halpha\ line (6563~\angstrom).
-This ensures sensitivity to the total stellar mass content.
+\item {\bf Black holes masses all meet the criteria that \mbh/$M_{\odot}\lesssim8.7$, which is below the knee of the black hole mass function to minimize the selection biases (see Figure~\ref{fig:selection}, top panel).} %fall below the knee of the black hole mass function to minimize the selection biases.
+
+\item {\bf Eddington ratios are all above $5\%$} to further ensure homogeneity.
+
+\item {\bf The host-to-total flux ratios typically above $30\%$ which facilitates the galaxy mass measurements, given that they are X-ray selected sample}.
+%The lower nuclear-to-host ratios of our sample facilitates the galaxy mass measurements, given that they are X-ray selected.
+
+\item \hst/WFC3 imaging of the host galaxy {\bf at rest-frame wavelength $\sim5500$~\angstrom, which} is above the $4000$~\angstrom\ break and does not include the broad \halpha\ line ($6563$~\angstrom{\bf ), which ensures} sensitivity to the total stellar mass content.
 This is somewhat coupled to the previous item in this list.
@@
 It is from this catalog that we primarily select our targets.
-We refer the reader to that paper for the details of continuum fitting and emission-line modeling.
-Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015}.
+{\bf The continuum fitting and emission-line modeling are also provided by this work through a common procedure for spectral model fits.
+This approach first correct the spectra for galactic extinction and shift to the rest-frame.
+The spectral regions in the near-IR were are strongly affected by OH emission, and thus they are masked while fitting.
+The spectrum are modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on the $\chi^2$ value.
+We refer the reader to that paper for more details.}
+Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} {\bf using a similar approach}.
 
@@
 We achieve to analyze this sample using the same approach, taking the 3 available frames.}.
-We use the {\sc photutils} tools to accurately estimate the background light which could come from both the sky and the detector.
 In Table~\ref{tab:objlist}, we list the details of the individual observations.
+
+{\bf Obtaining the \hst\ image,  we first account for the background light which could come from both the sky and the detector.
+In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm.
+Then, we remove the globe sky background light to obtain the clean image.
+To ensure the background light has been accurately subtracted, we investigate the surface brightness at the sampled empty area to ensure it is neither positive nor negative.}
+
+We carefully test the surface brightness at the empty area to ensure the
 
@@
 \item AGN imaging data. \\
--- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample.
+-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample\footnote{\bf In this aperture photometry process, we measure the AGN total flux in the aperture.
+By keep extending the aperture size, we note that the $1\farcs{}5$ is the limit region, beyond which the total light would not increase with the extending of aperture radius.}.
 By default, we extract an image of $61\times61$ pixels (i.e., $4''\times 4''$).
-If needed, a larger box size would be sufficient to include nearby objects.
+If needed, a larger box size would be {\bf selected to sufficiently} include nearby objects.
 \item Noise level map.\\
@@
 As shown in Figure~\ref{fig:hist_compare}, the results are consistent.
-For each AGN, we check the position of the top-ranked PSFs and find that they are unrelated to the AGN's position, which highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.
+For each AGN, we check the {\bf location on the detector for the top-ranked PSFs} and find that they are unrelated to the AGN's {\bf location in the detector.
+This is against the intuition that it is the PSFs who locates closer to the AGN that have better performance which} highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.
 
@@
 
-From our image decomposition, we detect the host galaxy essentially in all cases.
-\hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data-point source'' stamps) of Figure~\ref{fig:AGN_decomp} and in Appendix~\ref{sec:restsample} for the remaining cases.
+From our image decomposition, we detect the {\bf host galaxy in all cases at a distinguished level, expect one case (i.e., SXDS-X763) that has host-to-total flux ratios lower than $15\%$}.
+\hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data$-$point source'' stamps) of Figure~\ref{fig:AGN_decomp} and in Appendix~\ref{sec:restsample} for the remaining cases.
 While some of the galaxies have nearby neighbors, most are isolated and do not show strong signs of interaction or ongoing mergers, which indicates the fueling mechanism of AGNs may not be from major mergers for our sample.
@@
 \label{sec:result-hosts}
-As shown in Figure~\ref{fig:hist_compare}, the host-to-total flux ratio (total=host+nuclear) of the sample spans a wide range from $10\%$ to $90\%$ with most of the sample concentrated between $20\%$ to $50\%$ (median value $37\%$).
-Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the very few cases around 10\% should be considered as marginal detections.
+As shown in Figure~\ref{fig:hist_compare}, the host-to-total flux ratio (total$=$host$+$nuclear) of the sample spans a wide range from $10\%$ to $90\%$ with most of the sample concentrated between $20\%$ to $50\%$ (median value $37\%$).
+Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the {\bf five sample (i.e., CID255, CID50, LID360, CDFS-229, SXDS-X763) which have host-to-total flux ratios lower than $20\%$} should be considered as marginal detections.
 
@@
 \begin{tabular}{c c}
-{\includegraphics[height=0.4\textwidth]{fig/comp_gtemp_1Gyrs.pdf}}&
+{\includegraphics[height=0.4\textwidth]{fig/comp_gtemp.pdf}}&
 {\includegraphics[height=0.4\textwidth]{fig/colorVSz.pdf}}\\
@@
 As shown in these panels, the scatter of the high-$z$ correlation presents a similarity to the local relation.
-To quantitively make this comparison, we calculate the intrinsic scatter of their offset value, based on Equation~\ref{eq:infer_value}, and obtain $0.33$ for high-$z$ and $0.40$ for local samples, respectively.
+To quantitively make this comparison, we calculate the intrinsic scatter of their offset value, based on Equation~\ref{eq:infer_value}, and \ding{(This needs to be rewritten:) obtain $0.25$ for high-$z$ and $0.35$ for local samples}, respectively.
 The fact that the intrinsic scatter for the high-$z$ sample is no larger than the local one may pose a challenge for explanations of scaling relations where random mergers are the origin of the correlation \citep{Peng2007,Jahnke2011}, indicating that there may likely be a connection between the SMBHs and their host galaxies during their formation.
@@
 
-First, we establish a relation between the single-\sersic\ index and the B/T ratio using inactive galaxies from CANDELS at similar redshifts and stellar masses (Figure~\ref{fig:BT-n_relation}; \smass$\in [9.0, 11.5]$) using the B/T measurements of \citet{Dimauro2018}.
+First, we establish a relation between the single-\sersic\ index and the B/T ratio using inactive galaxies from CANDELS at similar redshifts and stellar masses (Figure~\ref{fig:BT-n_relation}; \smass$\in~[9.0, 11.5]$) using the B/T measurements of \citet{Dimauro2018}.
 In the figure, the red line indicates the average B/T ratio at a given \sersic\ index.
@@
 Thus, the choice of template is a subdominant source of error.
-A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.
+{\bf Note that large uncertainties of \mbh\ is not apparent in our figures, since we only select the AGN sample that have {\it measured} \mbh\ falls into our selection window.
+The detailed analysis on this effect is beyond the scope.
+In our forthcoming paper, we focus on the sample scatter.} A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.
 
@@
 \subfloat[\mbh-\lhost\ relation, evolution-corrected]
-{\includegraphics[height=0.5\textwidth]{fig/MBH-L_ev.pdf}}&
+{\includegraphics[height=0.45\textwidth]{fig/MBH-L_ev.pdf}}&
 \subfloat[offset in  $\log($\mbh$)$ (VS. \lhost) as a function of redshift]
-{\includegraphics[height=0.5\textwidth]{fig/MBH-L-vz.pdf}}\\
+{\includegraphics[height=0.45\textwidth]{fig/MBH-L-vz.pdf}}\\
 \subfloat[\mbh-\lhost, flat prior]
@@
 
-\begin{deluxetable*}{llccccc}
+\begin{deluxetable*}{llcccc}
 \tablecolumns{7}
@@
 \colhead{$DEC$}&
-\colhead{Observing date}&
-\colhead{Exposure time (s)}
+\colhead{Observing date}
 \\ 
@@
 \colhead{(5)} &
-\colhead{(6)} &
-\colhead{(7)}
+\colhead{(6)} 
 } 
@@
 %\\
-COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
-COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
-COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
-COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
-COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
-COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
-COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
-COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
-COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
-COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
-COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
-COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
-COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
-COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
-COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
-COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
-COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
-COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
-COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
-COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
-COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
-CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
-CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
-CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
-ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
-CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
-SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
-SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
-SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
-SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
-SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
-SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
+COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 \\
+COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 \\
+COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 \\
+COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 \\
+COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 \\
+COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 \\
+COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 \\
+COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 \\
+COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 \\
+COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 \\
+COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 \\
+COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 \\
+COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 \\
+COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 \\
+COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 \\
+COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 \\
+COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12\\
+COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 \\
+COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 \\
+COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 \\
+COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 \\
+CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 \\ 
+CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 \\ 
+CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18\\ 
+ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09\\ 
+CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 \\
+SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 \\ 
+SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29\\ 
+SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01\\ 
+SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 \\ 
+SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 \\ 
+SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 \\ 
 \enddata
@@
 Column 6: The observing start date.
-Column 7: Total exposure time.
+{\bf The total exposure time of each target is 2394s.}
 }
@@
 \begin{deluxetable*}
-{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.
+{@{\extracolsep{0pt}}lcccccccc}   % need for the gap between the clines.
 \tablecolumns{9}
@@
 \colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
-\colhead{(M$_{\odot}$)}& (log$\lambda$)&
+\colhead{(M$_{\odot}$)}& (log$( L_{\rm Bol}/L_{\rm Edd})$)&
 \colhead{(\kms)}& 
-\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$\lambda$)\\
+\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$(L_{\rm Bol}/L_{\rm Edd})$)\\
 \colhead{(1)}& 
@@
 Column 1: Object ID.
-Column 2-5: \halpha\ emission line width (FWHM), continuum luminosity, inferred \mbh\ and Eddington ratio.
+Column 2-5: \halpha\ emission line width (FWHM), {\bf \halpha\ luminosity}, inferred \mbh\ and Eddington ratio. %(or continuum line at $\rm L _{\lambda5100}$)
 Column 6-9: \hbeta\ emission line BH properties. 
-The typical uncertainty level for FWHM and $\log( \rm L _{\lambda})$ are $15\%$ and $\pm0.01$, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
+The typical uncertainty level for {\bf FWHM is $15\%$, and fo $\log( \rm L _{\lambda})$ is in-between $0.01\sim0.2$~dex}, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
 }

### 2019-10-03 M_BH_relation/ML_all_vz.py

@@ -217,8 +217,8 @@ value,sig=round(b_ml,2),round((np.percentile(samples,84,axis=0)[0]-np.percentile
 #value,sig = 0.66, 0.18
 #plt.text(0.15, -1.75, "$\Delta$log$M_{BH}$=$(%s\pm%s)$log$(1+z)$"%(value,sig),color='blue',fontsize=25)
 ##
-plt.xlabel("log$(1+z)$",fontsize=35)
-plt.ylabel("$\Delta$log$M_{BH}$ (vs $L_R$)",fontsize=35)
+plt.xlabel("log(1+z)",fontsize=45)
+plt.ylabel(r"$\Delta$logM$_{\rm BH}$ (vs L$_{\rm R}$)",fontsize=45)
 
 new_sample = mlines.Line2D([], [], color='tomato', ls='', marker='*', markersize=20,markeredgecolor='k')
 
@@ -229,14 +229,14 @@ xl=-0.01
 xh=np.log10(1+2.5)
 plt.axis([xl,xh,-2.0,3.5])
 plt.grid()
-plt.tick_params(labelsize=25)
+plt.tick_params(labelsize=35)
 
 ax2=ax.twiny()
 tticks=np.array([10**xl-1,0.5,1,1.5,2,10**xh-1])
 ax2.set_xticks([np.log(t+1) for t in tticks])  # for the entire scale
 ax2.set_xticklabels([0,0.5,1,1.5,2,2.5])  # 0 actuall is corresponds to 10**-0.01-1
-ax2.set_xlabel('$z$',fontsize=35)
-plt.tick_params(labelsize=25)
+ax2.set_xlabel('z',fontsize=45)
+plt.tick_params(labelsize=35)
 
 #if inp_peng == 1:
 #    plt.legend([HE0435,RXJ1131,park,SS13,Mg,H,C,unlens,Pkc, new_sample],['HE0435',\
@@ -256,5 +256,5 @@ plt.legend([Pkc, park, new_sample],[
 "Intermediate redshift AGNs",
 "This work"
 ],scatterpoints=1,numpoints=1,loc=2,prop={'size':30},ncol=2,handletextpad=0)
-#plt.savefig("MBH-L-vz.pdf")
+plt.savefig("MBH-L-vz.pdf")
 plt.show()

### 2019-10-03 M_BH_relation/MM_all.py

@@ -102,9 +102,9 @@ plt.errorbar(Mstar,MBs, xerr=[np.abs(Mstar_err)[:,0], np.abs(Mstar_err)[:,1]], y
 #cl.ax.get_yaxis().labelpad=35     #the distance of the colorbar titel from bar
 #cl.ax.tick_params(labelsize=30)   #the labe size
 
-plt.title("$M_{BH}-M_*$ relation",fontsize=35)
-plt.xlabel("log$(M_*/M_{\odot})$",fontsize=35)
-plt.ylabel("log$(M_{BH}/M_{\odot})$",fontsize=35)
+plt.title(r"M$_{\rm BH}-$M$_*$ relation",fontsize=35)
+plt.xlabel(r"log(M$_*$/M$_{\odot})$",fontsize=35)
+plt.ylabel(r'log(M$_{\rm BH}$/M$_{\odot}$)',fontsize=35)
 #plt.xticks(np.arange(5,16.5,0.5))
 #plt.yticks(np.arange(6,16.5,0.5))
 plt.xlim(9,12.5)

### 2019-10-03 NA_paper/scripts/my_selection_plots_SAM.py

@@ -89,7 +89,7 @@ tab_sub_list = copy.deepcopy(tab_list)
 for i in range(len(tab_sub_list)):
     if tab_sub_list[i] in ext_ID.keys():
         tab_sub_list[i] = ext_ID[tab_sub_list[i]]
-Lr, M_star, M_r = load_host_p(tab_list,temp='1Gyrs', folder = '../../')  # M_star by Chabrier 
+Lr, M_star, M_r = load_host_p(tab_list, folder = '../../')  # M_star by Chabrier 
 
 M_r_obs= M_r
 M_r_obs_err = load_err(prop='LR', ID=tab_list) / 0.4

### 2019-10-03 py_tools/load_result.py

@@ -226,7 +226,7 @@ def EE(z):
       return quad(EZ, 0, z , args=(om))[0]
 vec_EE=np.vectorize(EE)
 
-def load_host_p(ID, folder='../', temp='1Gyrs', dm = 0):
+def load_host_p(ID, folder='../', temp=['1Gyrs','0.625Gyrs'], dm = 0):
     '''
     Return the host properties including
     1. host LR, 2. M_star, 3. Host Rest frame R absolute mags
@@ -236,25 +236,32 @@ def load_host_p(ID, folder='../', temp='1Gyrs', dm = 0):
     from dmag import k_corr_R
     from filter_info import filt_info
     dm_k_R = []
-    if temp != '3Gyrs':
-        for i in range(len(zs)):
-            dm_k_R.append(k_corr_R(zs[i],filt_info[ID[i]], galaxy_age = temp))
-        dm_k_R = np.asarray(dm_k_R) # Get the k-correction for each target as an array
-    else:
-        for i in range(len(zs)):
+    
+    for i in range(len(zs)):
+        if zs[i]<=1.44:
+            galaxy_age = temp[0]
+        elif zs[i]>1.44:
+            galaxy_age = temp[1]
+        if galaxy_age != '3Gyrs':
+            dm_k_R.append(k_corr_R(zs[i],filt_info[ID[i]], galaxy_age = galaxy_age))
+        else:
             dm_k_R.append( (k_corr_R(zs[i],filt_info[ID[i]], galaxy_age = '1Gyrs')+k_corr_R(zs[i],filt_info[ID[i]], galaxy_age = '5Gyrs'))/2. )
-        dm_k_R = np.asarray(dm_k_R) # Get the k-correction for each target as an array
+    dm_k_R = np.asarray(dm_k_R) # Get the k-correction for each target as an array
     dl=(1+zs)*c*vec_EE(zs)/h0 *10**6   #in pc
     host_Mags = mags -5*(np.log10(dl)-1) + dm_k_R + dm*pass_dmag(zs) # This is in AB system
     host_LR = np.log10(10 ** (0.4*(4.61-host_Mags))) #LR in AB
     host_Mags_Vega = host_Mags - 0.21  # Transfer to Vega system
[…]

### 2019-10-04 manuscript/manuscript.tex
Update the paper today.

@@
 The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators.
-We find the {\it observed} ratio of \mbh/\smass~to be $2.0\times$ larger at $z\sim1.5$ than in the local universe, while the scatter is equivalent between the two epochs.
-However, an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).
-The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
+We find the {\it observed} ratio of \mbh/\smass~to {\bf be $2.5\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs.
+\ding{TBC: However, an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
 Therefore, our results are in agreement, considering the uncertainties, with a scenario where SMBHs and their total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter.
-Based on an inference of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is significantly offset from the local value by a factor of $+5.5$ which persists even after accounting for selection effects.
+Based on an inference of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is significantly offset from the local value {\bf by a factor of $+6.8$ which} persists even after accounting for selection effects.
 Taken together, these observations are consistent with a scenario in which stellar mass is subsequently transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than mass accretion onto the SMBH.
@@
 
-\item {\bf The host-to-total flux ratios typically above $30\%$ which facilitates the galaxy mass measurements, given that they are X-ray selected sample}.
+\item {\bf X-ray selected sample has host-to-total flux ratios typically above $30\%$ which facilitates the galaxy mass measurements.}.
 %The lower nuclear-to-host ratios of our sample facilitates the galaxy mass measurements, given that they are X-ray selected.
@@
 \item AGN imaging data. \\
--- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample\footnote{\bf In this aperture photometry process, we measure the AGN total flux in the aperture.
-By keep extending the aperture size, we note that the $1\farcs{}5$ is the limit region, beyond which the total light would not increase with the extending of aperture radius.}.
+-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample\footnote{\bf In this photometry process, we measure the AGN total flux in the aperture.
+By keep extending the aperture size, we note that the $1\farcs{}5$ is the limit region, beyond which the total aperture flux would not increase with the extending of aperture radius.}.
 By default, we extract an image of $61\times61$ pixels (i.e., $4''\times 4''$).
@@
 
-For $21/32$ AGNs, we have multi-band host magnitudes that enable us to select an appropriate stellar population template to determine rest-frame luminosities and stellar masses for the overall sample.
-To minimize the uncertainty associated with these corrections, we use this template to interpolate to the rest-frame R band which is very close to the observed wavelengths.
-We find that a $1$~Gyr stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} provides an excellent match to the observed colors of our sample (see Figure~\ref{fig:compare_temp}).
+For $21/32$ AGNs, we have multi-band host magnitudes that enable us to select {\bf the appropriate stellar population templates} to determine rest-frame luminosities and stellar masses for the overall sample.
+We find {\bf that the $1$~Gyr and the $0.625$~Gyr} stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} provides {\bf the excellent matches} to the observed colors of our sample {\bf at $z<1.44$ and $z>1.44$, respectively}  (see Figure~\ref{fig:compare_temp}).
+{\bf To minimize the uncertainty associated with these corrections, we adopt these two templates correspondingly to interpolate to the rest-frame R band which is very close to the observed wavelengths}.
 We note that the choice is not unique, and other combinations of ages and metallicities and star formation history could match the observed colors and would provide very similar R-band magnitudes, and also stellar masses \citep{Bell2000, Bell2001}.
@@
 \begin{tabular}{c c}
-{\includegraphics[height=0.4\textwidth]{fig/comp_gtemp.pdf}}&
-{\includegraphics[height=0.4\textwidth]{fig/colorVSz.pdf}}\\
+{\includegraphics[height=0.4\textwidth]{fig/colorVSz.pdf}}&
+{\includegraphics[height=0.4\textwidth]{fig/comp_gtemp.pdf}}\\
 \end{tabular}
 \caption{\label{fig:compare_temp} 
- {\it Left}: Comparison of the inferred rest-frame R band magnitude based on the adopted stellar population, using $21/32$ AGNs which have both WFC3 and ACS imaging data.
-{\it Right}: The observed color as a function of redshift.
+{\bf {\it Left}: The observed color as a function of redshift, based on $21/32$ AGNs which have both WFC3 and ACS imaging data.
 Note that the filter WFC3/F125W and WFC3/F140W are adopted for sample at $z<1.44$ and $z>1.44$, respectively.
-The blue curve is the predicted model by the $1$~Gyr stellar population.
-For comparison, we plot the predicted model for a $5$~Gyr stellar population that is definitely ruled out by our data.
+We also plot three predicted models including $5$~Gyr, $1$~Gyr and $0.625$~Gyr.
+Clearly, the $5$~Gyr stellar population is ruled out by our data, and we adopt the $1$~Gyr and $0.625$~Gyr for sample at $z<1.44$ and $z>1.44$, respectively.
+ {\it Right}: Comparison of the inferred rest-frame R band magnitude, based on the adopted stellar populations.
+ }
 }
@@
 
-Adopting the $1$~Gyr stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample.
+Adopting {\bf the $1$~Gyr and $0.625$~Gyr} stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample{\bf, based on the host inference at WFC3 band}.
 As mentioned above, since the WFC3 filter is already close to the rest-frame R-band, we expect the $M_R$ uncertainty introduced by this K-correction to be within $0.05$~mag.
@@
 
-Using the NIR imaging with \hst, we take the host luminosity along with color information to estimate the stellar mass content of each host galaxy based on the mass-to-light ratio of the adopted  $1$~Gyr stellar population.
+Using the NIR imaging with \hst, we take the host luminosity along with color information to estimate the stellar mass content of each host galaxy based on the mass-to-light ratio of the adopted  {\bf stellar populations}.
 The uncertainty level associated with the stellar mass is expected to be of order $0.1$~dex (changing the IMF would affect all our stellar masses systematically).
-We find $M_*$ ranges between $\log M_* \in [9.7, 11.3]$ ($M_{\odot}$).
+We find $M_*$ ranges {\bf between $\log (M_*/M_{\odot}) \in [9.7, 11.3]$}.
 These values are listed in Table~\ref{tab:result_sersic}.
@@
 \end{eqnarray} 
-Performing such a fit based on the {\it observed} data (i.e., no correction for selection effects), we obtain $\gamma  = 0.78 \pm 0.26$ that may be tentatively considered as evidence for evolution.
-Even with the exclusion of the few outliers, there is an evolution in the correlation with $\gamma  = 0.65 \pm 0.27$.
+Performing such a fit based on the {\it observed} data (i.e., no correction for selection effects), {\bf we obtain $\gamma  = 1.01 \pm 0.26$ that} may be tentatively considered as evidence for evolution.
+Even with the exclusion of the few outliers, there is an evolution in the {\bf correlation with $\gamma  = 0.89 \pm 0.27$}.
 The best-fit {\it observed} evolution model is shown in Figure~\ref{fig:MM-vz}.
@@
 A simple check using our prior estimate of the bias yields a similar result.
-The mean offset of the sample of 32 objects from the local relationship is $0.32\pm0.06$ dex, which would correspond to $\gamma=0.80\pm0.15$.
-However, after correcting for the selection bias ($0.21$~dex, see Section~\ref{sec:sf_framework}), the offset reduces to $0.11\pm0.06$ and thus $\gamma=0.28\pm0.15$, mildly positive but not significantly so, and consistent with the a posteriori method within the error bars and the uncertainty in the correction.
+The mean offset of the sample of 32 objects from the local {\bf relationship is $0.42\pm0.06$ dex, which would correspond to $\gamma=1.06\pm0.15$}.
+However, after correcting for the selection bias ($0.21$~dex, see Section~\ref{sec:sf_framework}), {\bf the offset reduces to $0.20\pm0.06$ and thus $\gamma=0.50\pm0.15$, }mildly positive but not significantly so, and consistent with the a posteriori method within the error bars and the uncertainty in the correction.
 We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
@@
 
-As expected, we find a stronger offset of
-$\Delta \log \mathcal M_{\rm BH}^{bulge} = 0.77\pm0.08$~dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
-local relation, which corresponds to an evolutionary trend with
-$\gamma = 1.86\pm0.30$. Since selection effects are independent of B/T in
-our framework, we can apply our prior estimate of the correction for selection effects by removing $0.21$~dex, leaving still a significant offset
-of $0.56$~dex. We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
+As expected, {\bf we find a stronger offset of
+$\Delta \log \mathcal M_{\rm BH}^{bulge} = 0.87\pm0.07$~dex } in \mbh/\smass$_{\rm, bulge}$ with respect to the
+local relation, which corresponds to an {\bf evolutionary trend with
+$\gamma = 2.09\pm0.30$}. Since selection effects are independent of B/T in
+our framework, we can apply our prior estimate of the correction for selection effects by removing $0.21$~dex, leaving still a {\bf significant offset
+of $0.67$~dex.} We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
 the Monte Carlo approach in Figure~\ref{fig:gamma_hist} and illustrate the offset between bulge and BH
@@
 This required us to collect PSF-stars across all the fields to build a library of PSFs.
-Using state-of-the-art image modeling tool \lenstronomy, we decomposed the AGN image in the 2-D plane taking each PSF in the library.
+Using state-of-the-art image modeling tool \lenstronomy, we decomposed the AGN image in the 2D plane taking each PSF in the library.
 We obtained the host properties (i.e., host flux, effective radius, \sersic\ index) using a weighted arithmetic mean based on the inference from the eight top-ranked PSFs.
-With additional \hst/ACS image in the optical, we identified the appropriate stellar population and derived the rest-frame R-band luminosity (\lhost) and stellar mass (\smass) of the host with the corresponding mass-to-light ratio.
+With additional \hst/ACS image in the optical, we identified the appropriate {\bf stellar populations} and derived the rest-frame R-band luminosity (\lhost) and stellar mass (\smass) of the host with the corresponding mass-to-light ratio.
 We then determine the mass relations at high-$z$ and establish any signs of evolution by combining our high-$z$ measurements with local and intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13, Cisternas2011}.
 
-We find the average "observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, by a factor of $\sim2.5$ and $\sim2.0$ respectively, as compared to that in the local universe.
-However, taking into account selection bias, these correlations are consistent with those in the local universe within the 95\% confidence limits.
+We find the average ``observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, {\bf by a factor of $\sim2.7$ and $\sim2.5$ respectively}, as compared to that in the local universe.
+\ding{TBC: However, taking into account selection bias, these correlations are consistent with those in the local universe within the 95\% confidence limits.
+}
 Even with the remaining uncertainties in the corrections for selection, we are confident that any evolution in the \mbh/\smass\ relation is at the most a factor of two with the case of no evolution entirely plausible.
@@
 Considering the bulge component \citep{Bennert11, Woo++08} separately, we find that our high-$z$ AGN sample has significantly lower mass/luminosity bulges at fixed black hole mass than in the local universe.
-Comparing to their \mbh, we find evolution with the ratio evolving as $(1+z)^{1.86\pm0.30}$, which is significant even when accounting for selection effects.
+Comparing to their \mbh, we find evolution with the {\bf ratio evolving as $(1+z)^{2.09\pm0.30}$,} which is significant even when accounting for selection effects.
 We caution that the evolution of the bulge component is more uncertain than our measurement of the total galaxy components, since it is based on an estimate of the B/T ratio from the measured \sersic\ index based on a matched sample of inactive galaxies.
@@
 Having transferred the \lhost\ to today, we find that, as showing in Figure~\ref{fig:ML-vz}-(a), at fixed mass, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation.
-We fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 0.60 \pm 0.18$, as showing in Figure~\ref{fig:ML-vz}-(b).
-We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.3$, with flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
+We fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and {\bf obtain $\gamma = 0.64 \pm 0.17$, } as showing in Figure~\ref{fig:ML-vz}-(b).
+We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and \ding{ TBD: obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.3$, with} flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
 
@@
 %\\
+COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 \\
+COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 \\
+COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 \\
+COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 \\
+COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 \\
+COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 \\
+COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 \\
+COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 \\
+COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 \\
+COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 \\
 COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 \\
-COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 \\
+COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 \\
 COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 \\
 COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 \\
-COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 \\
-COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 \\
-COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 \\
-COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 \\
-COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 \\
+COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 \\
+COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 \\
+COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 \\
+COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 \\
+COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 \\
 COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 \\
-COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 \\
-COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 \\
-COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 \\
-COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 \\
-COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 \\
-COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 \\
 COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12\\
-COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 \\
-COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 \\
-COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 \\
-COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 \\
+CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 \\
 CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 \\ 
+CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18\\ 
 CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 \\ 
-CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18\\ 
 ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09\\ 
-CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 \\
-SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 \\ 
 SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29\\ 
 SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01\\ 
+SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 \\ 
+SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 \\ 
 SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 \\ 
-SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 \\ 
 SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 \\ 
@@
 Column 6-9: \hbeta\ emission line BH properties. 
-The typical uncertainty level for {\bf FWHM is $15\%$, and fo $\log( \rm L _{\lambda})$ is in-between $0.01\sim0.2$~dex}, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
+The typical uncertainty level for {\bf FWHM is $15\%$, and for $\log( \rm L _{\lambda})$ is in-between $0.01\sim0.2$~dex}, respectively.
+The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
 }
@@
 \startdata 
-CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.05\substack{+0.15\\-0.11}$ &$10.78\substack{+0.18\\-0.15}$ & $10.36\substack{+0.41\\-0.54}$ \\[3pt]
-CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.41\substack{+0.15\\-0.11}$ &$10.14\substack{+0.18\\-0.15}$ & $9.91\substack{+0.28\\-0.50}$ \\[3pt]
-CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.86\substack{+0.52\\-0.23}$ &$10.59\substack{+0.53\\-0.25}$ & $10.27\substack{+0.54\\-0.61}$ \\[3pt]
-CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.05\substack{+0.03\\-0.03}$ &$10.78\substack{+0.10\\-0.10}$ & $10.66\substack{+0.15\\-0.25}$ \\[3pt]
-CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.18\substack{+0.11\\-0.09}$ &$10.91\substack{+0.14\\-0.13}$ & $10.77\substack{+0.20\\-0.34}$ \\[3pt]
-CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.08\substack{+0.15\\-0.11}$ &$10.81\substack{+0.18\\-0.15}$ & $10.65\substack{+0.23\\-0.36}$ \\[3pt]
-CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.16\substack{+0.14\\-0.11}$ &$10.89\substack{+0.17\\-0.15}$ & $10.76\substack{+0.21\\-0.28}$ \\[3pt]
+CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.01\substack{+0.15\\-0.11}$ &$10.63\substack{+0.18\\-0.15}$ & $10.21\substack{+0.40\\-0.53}$ \\[3pt]
+CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.38\substack{+0.15\\-0.11}$ &$10.00\substack{+0.18\\-0.15}$ & $9.77\substack{+0.28\\-0.51}$ \\[3pt]
+CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.83\substack{+0.52\\-0.23}$ &$10.45\substack{+0.53\\-0.25}$ & $10.14\substack{+0.52\\-0.62}$ \\[3pt]
+CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.01\substack{+0.03\\-0.03}$ &$10.63\substack{+0.10\\-0.10}$ & $10.52\substack{+0.15\\-0.25}$ \\[3pt]
+CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.13\substack{+0.11\\-0.09}$ &$10.75\substack{+0.14\\-0.13}$ & $10.60\substack{+0.20\\-0.34}$ \\[3pt]
+CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.03\substack{+0.15\\-0.11}$ &$10.65\substack{+0.18\\-0.15}$ & $10.48\substack{+0.23\\-0.35}$ \\[3pt]
+CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.12\substack{+0.14\\-0.11}$ &$10.75\substack{+0.17\\-0.15}$ & $10.62\substack{+0.19\\-0.29}$ \\[3pt]
 CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $10.98\substack{+0.02\\-0.02}$ &$10.71\substack{+0.10\\-0.10}$ & $9.78\substack{+0.68\\-0.13}$ \\[3pt]
-CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.13\substack{+0.03\\-0.03}$ &$10.86\substack{+0.10\\-0.10}$ & $10.14\substack{+0.48\\-0.30}$ \\[3pt]
-CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.11\substack{+0.04\\-0.04}$ &$10.84\substack{+0.10\\-0.10}$ & $9.91\substack{+0.74\\-0.14}$ \\[3pt]
-CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.07\substack{+0.35\\-0.19}$ &$10.80\substack{+0.36\\-0.21}$ & $10.51\substack{+0.4\\-0.57}$ \\[3pt]
-CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.70\substack{+0.16\\-0.12}$ &$10.43\substack{+0.19\\-0.15}$ & $9.55\substack{+0.63\\-0.23}$ \\[3pt]
-CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.73\substack{+0.22\\-0.15}$ &$10.46\substack{+0.24\\-0.18}$ & $9.97\substack{+0.44\\-0.49}$ \\[3pt]
-CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.02\substack{+0.23\\-0.15}$ &$10.75\substack{+0.25\\-0.18}$ & $10.55\substack{+0.29\\-0.40}$ \\[3pt]
-CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $10.98\substack{+0.12\\-0.10}$ &$10.72\substack{+0.16\\-0.14}$ & $10.54\substack{+0.22\\-0.36}$ \\[3pt]
-LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.32\substack{+0.09\\-0.07}$ &$11.05\substack{+0.13\\-0.12}$ & $10.29\substack{+0.58\\-0.28}$ \\[3pt]
-LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.12\substack{+0.09\\-0.08}$ &$10.86\substack{+0.13\\-0.12}$ & $10.66\substack{+0.23\\-0.38}$ \\[3pt]
-LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.08\substack{+0.06\\-0.05}$ &$10.81\substack{+0.11\\-0.11}$ & $9.91\substack{+0.67\\-0.16}$ \\[3pt]
-XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.89\substack{+0.07\\-0.06}$ &$10.63\substack{+0.12\\-0.12}$ & $9.85\substack{+0.57\\-0.27}$ \\[3pt]
-XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.15\substack{+0.12\\-0.10}$ &$10.88\substack{+0.16\\-0.14}$ & $10.73\substack{+0.21\\-0.32}$ \\[3pt]
-XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.12\substack{+0.26\\-0.16}$ &$10.85\substack{+0.28\\-0.19}$ & $10.15\substack{+0.59\\-0.41}$ \\[3pt]
+CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.13\substack{+0.03\\-0.03}$ &$10.86\substack{+0.10\\-0.10}$ & $10.13\substack{+0.48\\-0.29}$ \\[3pt]
+CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.07\substack{+0.04\\-0.04}$ &$10.70\substack{+0.10\\-0.10}$ & $9.77\substack{+0.74\\-0.15}$ \\[3pt]
+CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.07\substack{+0.35\\-0.19}$ &$10.80\substack{+0.36\\-0.21}$ & $10.51\substack{+0.41\\-0.56}$ \\[3pt]
+CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.70\substack{+0.16\\-0.12}$ &$10.43\substack{+0.19\\-0.15}$ & $9.55\substack{+0.64\\-0.24}$ \\[3pt]
+CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.73\substack{+0.22\\-0.15}$ &$10.46\substack{+0.24\\-0.18}$ & $9.98\substack{+0.44\\-0.49}$ \\[3pt]
+CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.02\substack{+0.23\\-0.15}$ &$10.75\substack{+0.25\\-0.18}$ & $10.57\substack{+0.29\\-0.41}$ \\[3pt]
+CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $10.93\substack{+0.12\\-0.10}$ &$10.55\substack{+0.16\\-0.14}$ & $10.38\substack{+0.22\\-0.34}$ \\[3pt]
+LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.27\substack{+0.09\\-0.07}$ &$10.89\substack{+0.13\\-0.12}$ & $10.13\substack{+0.58\\-0.28}$ \\[3pt]
+LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.09\substack{+0.09\\-0.08}$ &$10.71\substack{+0.13\\-0.12}$ & $10.52\substack{+0.22\\-0.37}$ \\[3pt]
+LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.04\substack{+0.06\\-0.05}$ &$10.66\substack{+0.11\\-0.11}$ & $9.76\substack{+0.65\\-0.16}$ \\[3pt]
+XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.85\substack{+0.07\\-0.06}$ &$10.48\substack{+0.12\\-0.12}$ & $9.71\substack{+0.57\\-0.28}$ \\[3pt]
+XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.11\substack{+0.12\\-0.10}$ &$10.74\substack{+0.16\\-0.14}$ & $10.58\substack{+0.21\\-0.33}$ \\[3pt]
+XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.07\substack{+0.26\\-0.16}$ &$10.69\substack{+0.28\\-0.19}$ & $10.00\substack{+0.58\\-0.40}$ \\[3pt]
 CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ...
@@
 & ...
-& $10.71\substack{+0.16\\-0.12}$ &$10.45\substack{+0.19\\-0.15}$ & $10.30\substack{+0.22\\-0.30}$ \\[3pt]
+& $10.66\substack{+0.16\\-0.12}$ &$10.29\substack{+0.19\\-0.15}$ & $10.14\substack{+0.22\\-0.31}$ \\[3pt]
 CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ...
@@
 & ...
-& $10.90\substack{+0.06\\-0.05}$ &$10.63\substack{+0.12\\-0.11}$ & $9.70\substack{+0.69\\-0.16}$ \\[3pt]
+& $10.90\substack{+0.06\\-0.05}$ &$10.63\substack{+0.12\\-0.11}$ & $9.71\substack{+0.70\\-0.16}$ \\[3pt]
 CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ...
@@
 & ...
-& $11.52\substack{+0.28\\-0.17}$ &$11.25\substack{+0.30\\-0.20}$ & $10.88\substack{+0.42\\-0.58}$ \\[3pt]
+& $11.48\substack{+0.28\\-0.17}$ &$11.10\substack{+0.30\\-0.20}$ & $10.72\substack{+0.42\\-0.58}$ \\[3pt]
 CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ...
@@
 & ...
-& $10.06\substack{+0.23\\-0.15}$ &$9.79\substack{+0.25\\-0.18}$ & $9.27\substack{+0.48\\-0.51}$ \\[3pt]
+& $10.06\substack{+0.23\\-0.15}$ &$9.79\substack{+0.25\\-0.18}$ & $9.25\substack{+0.48\\-0.48}$ \\[3pt]
 ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ...
@@
 & ...
-& $11.16\substack{+0.12\\-0.10}$ &$10.89\substack{+0.16\\-0.14}$ & $10.37\substack{+0.44\\-0.46}$ \\[3pt]
+& $11.11\substack{+0.12\\-0.10}$ &$10.73\substack{+0.16\\-0.14}$ & $10.22\substack{+0.44\\-0.47}$ \\[3pt]
 SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ...
@@
 & ...
-& $10.75\substack{+0.09\\-0.08}$ &$10.49\substack{+0.14\\-0.13}$ & $10.11\substack{+0.35\\-0.50}$ \\[3pt]
+& $10.75\substack{+0.09\\-0.08}$ &$10.49\substack{+0.14\\-0.13}$ & $10.10\substack{+0.36\\-0.48}$ \\[3pt]
 SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ...
@@
 & ...
-& $10.80\substack{+0.11\\-0.09}$ &$10.54\substack{+0.15\\-0.13}$ & $10.02\substack{+0.44\\-0.46}$ \\[3pt]
+& $10.80\substack{+0.11\\-0.09}$ &$10.54\substack{+0.15\\-0.13}$ & $10.01\substack{+0.45\\-0.46}$ \\[3pt]
 SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ...
@@
 & ...
-& $10.77\substack{+0.07\\-0.06}$ &$10.51\substack{+0.12\\-0.12}$ & $10.38\substack{+0.17\\-0.28}$ \\[3pt]
+& $10.77\substack{+0.07\\-0.06}$ &$10.51\substack{+0.12\\-0.12}$ & $10.38\substack{+0.18\\-0.29}$ \\[3pt]
 SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ...
@@
 & ...
-& $11.19\substack{+0.13\\-0.10}$ &$10.92\substack{+0.17\\-0.14}$ & $10.54\substack{+0.38\\-0.55}$ \\[3pt]
+& $11.16\substack{+0.13\\-0.10}$ &$10.78\substack{+0.17\\-0.14}$ & $10.42\substack{+0.36\\-0.56}$ \\[3pt]
 SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ...
@@
 & ...
-& $9.95\substack{+0.47\\-0.22}$ &$9.68\substack{+0.48\\-0.24}$ & $9.36\substack{+0.48\\-0.54}$ \\[3pt]
+& $9.95\substack{+0.47\\-0.22}$ &$9.68\substack{+0.48\\-0.24}$ & $9.35\substack{+0.48\\-0.56}$ \\[3pt]
 SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ...
@@
 & ...
-& $11.03\substack{+0.21\\-0.14}$ &$10.76\substack{+0.23\\-0.17}$ & $10.37\substack{+0.40\\-0.53}$ \\[3pt]
+& $10.99\substack{+0.21\\-0.14}$ &$10.61\substack{+0.23\\-0.17}$ & $10.21\substack{+0.40\\-0.54}$ \\[3pt]
 \enddata
@@
      \hline\hline
-32 AGNs + intermediate & No &  0.58$\pm$0.20 & 0.61$\pm$0.18 \\
-32 AGNs + intermediate& Yes & 0.80$\pm$0.40 & 0.50 $\pm$ 0.50 \\
-32 AGNs & No & 0.78$\pm$0.26  & 0.99$\pm$0.23\\
-32 AGNs& Yes & 1.20$\pm$0.80 & 1.60$\pm$0.80 \\
+32 AGNs + intermediate & No &  0.72$\pm$0.20 & 0.64$\pm$0.17 \\
+32 AGNs + intermediate& \ding{TBD: Yes} & 0.80$\pm$0.40 & 0.50 $\pm$ 0.50 \\
+32 AGNs & No & 1.01$\pm$0.26 & 1.07$\pm$0.23\\
+32 AGNs& \ding{TBD: Yes} & 1.20$\pm$0.80 & 1.60$\pm$0.80 \\
      \hline
@@
      \hline\hline
-32 AGNs & 0.78$\pm$0.26\\    
-30 AGNs (excluded outliers) & 0.65$\pm$0.27\\    
-32 AGNs + intermediate &  0.58$\pm$0.20\\
-32 AGNs bulge only & 1.86$\pm$0.30\\
+32 AGNs & 1.01$\pm$0.26\\    
+30 AGNs (excluded outliers) & 0.89$\pm$0.27\\    
+32 AGNs + intermediate &  0.72$\pm$0.20\\
+32 AGNs bulge only & 2.09$\pm$0.30\\
      \hline

### 2019-10-04 M_BH_relation/MM_all_vz_Kormlocal.py

@@ -24,7 +24,7 @@ sys.path.insert(0,'../py_tools')
 #==============================================================================
 # The seleting for dm and host_total and dmag are in this local
 #==============================================================================
-from local_MM_vz import *
+from local_MM_vz_Kormlocal import *
 #==============================================================================
 #input Park's data 
 #==============================================================================
@@ -34,15 +34,19 @@ from local_MM_vz import *
 #######in AB system, V band#######
 f0 ='data/SS13_MM.txt'
 ss = np.loadtxt(f0)[:,1:]  #0 redshift; 1 M*; 2 BH mass;
+ss[:,2] = ss[:,2] + 0.3  #!!!
 
 f1 ='data/B11_MM.txt'
 b11 = np.loadtxt(f1)[:,1:]  #0 redshift; 1 M*; 2 BH mass;
+b11[:,2] = b11[:,2] + 0.3  #!!!
 
 f2 = 'data/Cisternas_data.txt'
 cis11 = np.loadtxt(f2)  #0 redshift;
+cis11[:,1] = cis11[:,1] + 0.3  #!!!
 
-f3 = 'data/high_edd_agn.txt'
-Knud = np.loadtxt(f3)[:,2:]  # 0 redshift; 1 L_bol; 2 M_BH; 3 M_acc; 4 M_*
+#f3 = 'data/high_edd_agn.txt'
+#Knud = np.loadtxt(f3)[:,2:]  # 0 redshift; 1 L_bol; 2 M_BH; 3 M_acc; 4 M_*
+#Knud[:,2] =  Knud[:,2]+ 0.3  #!!!
 
 
 #%%
@@ -64,7 +68,7 @@ MB_ID = ['CDFS-1', 'CID543','CID70',  'SXDS-X735', 'CDFS-229', 'ECDFS-321', 'CID
 zs = np.asarray(load_zs(ID))
 host_n = np.array(load_n(ID, folder = '../'))[:,0]
 Mstar = load_host_p(ID)[1]
-MBs = load_MBH(ID,MB_ID,if_reportHb=0)
+MBs = load_MBH(ID,MB_ID,if_reportHb=0)  + 0.3  #!!!
 Mstar_err = load_err(prop = 'Mstar', ID=ID)
[…]

### 2019-10-04 M_BH_relation/read_bulge_MC_result.py

@@ -54,18 +54,24 @@ tab_list = ['CID1174', 'CID1281', 'CID206', 'CID216', 'CID237', 'CID255', 'CID32
 Mstar_err = []
 Mstar = []
 #plot the estimated bulge relation:
-for target in tab_list:
-    i = [i for i in range(len(ID)) if target == ID[i]][0]
+for i in range(len(ID)):
     hist_value = Mstar_samp[:,i]
     l =np.percentile(hist_value,16,axis=0)
     m =np.percentile(hist_value,50,axis=0)
     h =np.percentile(hist_value,84,axis=0)
     Mstar.append(m)
     Mstar_err.append([m-l, h-m])
-#    print "${0}\substack{+{1}\\-{2}}$".format(round(m,2), round(h-m,2), round(m-l,2))
 Mstar = np.asarray(Mstar)
 Mstar_err = np.asarray(Mstar_err)
-    
+
+for target in tab_list:
+    i = [i for i in range(len(ID)) if target == ID[i]][0]
+    hist_value = Mstar_samp[:,i]
+    l =np.percentile(hist_value,16,axis=0)
+    m =np.percentile(hist_value,50,axis=0)
+    h =np.percentile(hist_value,84,axis=0)
+#    print target, "{0}\substack+{1}-{2}".format(round(m,2), round(h-m,2), round(m-l,2))
+ 
 #%% Plot the bulge offset for BH relation
 host=plt.figure(figsize=(14.5,12))
 ax=host.add_subplot(111)   #to get the log(1+z) and z label
@@ -195,6 +201,8 @@ if style ==1:
                  yerr= yerr_highz,
                  color='tomato',ecolor='orange', fmt='.',markersize=1)  
 #plt.text(0.15, -1.75, "$\Delta$log$M_{BH}$=$(%s\pm%s)$log$(1+z)$"%(1.86,0.30),color='blue',fontsize=25)
+    value,sig=np.percentile(gamma,50,axis=0),round((np.percentile(gamma,84,axis=0)-np.percentile(gamma,16,axis=0))/2,2)
+#    print value, sig
 
 plt.xlabel("log(1+z)",fontsize=45)
 new_sample = mlines.Line2D([], [], color='tomato', ls='', marker='*', markersize=20,markeredgecolor='k')
@@ -229,11 +237,11 @@ plt.savefig("MBH-Mbulge-style{0}.pdf".format(style))
[…]

### 2019-10-04 analysis_Astrodrz/compare_K-correction.py

@@ -191,8 +191,8 @@ z_d = np.linspace(1.1,1.8,200)
 k_c_140_5gy = k_corr_R(z_d, filt = 'F140w', galaxy_age = '5Gyrs')
 k_c_814_5gy = k_corr_R(z_d, filt = 'F814w', galaxy_age = '5Gyrs')
 k_c_125_5gy = k_corr_R(z_d, filt = 'F125w', galaxy_age = '5Gyrs')
-plt.plot(z_d[z_d>1.44],(k_c_140_5gy-k_c_814_5gy)[z_d>1.44], 'r', label = '5 Gyr template', linewidth=3.0,alpha=0.4)
-plt.plot(z_d[z_d<1.44],(k_c_125_5gy-k_c_814_5gy)[z_d<1.44], 'r', linewidth=3.0,alpha=0.4)
+plt.plot(z_d[z_d>1.44],(k_c_140_5gy-k_c_814_5gy)[z_d>1.44], 'r--', label = '5 Gyr template', linewidth=3.0,alpha=0.4)
+plt.plot(z_d[z_d<1.44],(k_c_125_5gy-k_c_814_5gy)[z_d<1.44], 'r--', linewidth=3.0,alpha=0.4)
 
 k_c_140_1gy = k_corr_R(z_d, filt = 'F140w', galaxy_age = '1Gyrs')
 k_c_814_1gy = k_corr_R(z_d, filt = 'F814w', galaxy_age = '1Gyrs')
@@ -216,8 +216,8 @@ plt.plot(z_d[z_d<1.44],(k_c_125_1gy-k_c_814_1gy)[z_d<1.44], c='b', linewidth=4.0
 k_c_140_1gy = k_corr_R(z_d, filt = 'F140w', galaxy_age = '0.625Gyrs')
 k_c_814_1gy = k_corr_R(z_d, filt = 'F814w', galaxy_age = '0.625Gyrs')
 k_c_125_1gy = k_corr_R(z_d, filt = 'F125w', galaxy_age = '0.625Gyrs')
-plt.plot(z_d[z_d>1.44],(k_c_140_1gy-k_c_814_1gy)[z_d>1.44], label = '0.625 Gyr template', c='g', linewidth=4.0,alpha=0.5)
-plt.plot(z_d[z_d<1.44],(k_c_125_1gy-k_c_814_1gy)[z_d<1.44], c='g', linewidth=4.0,alpha=0.5)
[…]

### 2019-10-04 material/creat_table_for_manscript.py

@@ -318,7 +318,7 @@ from load_result import load_host_p, load_MBH
 #    print ID, round(result[0],2), round(result[1],2)
 def roots(a,b):
     return np.sqrt(a**2+b**2)
-lumi_s = load_host_p(tab_list, dm = 0, temp='1Gyrs')[0] #!!! This dm is important 
+lumi_s = load_host_p(tab_list, dm = 0)[0] #!!! This dm is important 
 print "LR:"
 for i in range(len(tab_list)):
     print(tab_list[i], 

### 2019-10-04 NA_paper/manuscript_II/qso_paperII.tex
Including the descriptions for MBII and SAM.

--- 2019-09-30 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
@@
 Taking the selection biases into account, %by adopting the same selection function to choose the simulating sample,
-we find that both MBII and SAM agree well with the data, in terms of the central distribution.
-However, when considering measurement uncertainty and the scatter in the scaling relations, the observations are significantly more consistent with the MBII sample ($\sim0.3$~dex), than the SAM ($\sim0.7$~dex).
-In this respect, our observational constraints are able to distinguish between the two models, indicating that the recipe implemented by MBII (i.e., growth regulation through AGN feedback) is preferred over the SAM that does not include AGN feedback.
+we find that both \texttt{MBII} and \texttt{SAM} agree well with the data, in terms of the central distribution.
+However, when considering measurement uncertainty and the scatter in the scaling relations, the observations are significantly more consistent with the \texttt{MBII} sample ($\sim0.3$~dex), than the \texttt{SAM} ($\sim0.7$~dex).
+In this respect, our observational constraints are able to distinguish between the two models, indicating that the recipe implemented by \texttt{MBII} (i.e., growth regulation through AGN feedback) is preferred over the \texttt{SAM} that does not include AGN feedback.
 Moreover, the intrinsic scatter of our high-$z$ sample is comparable to the local sample thus counter to the expectation from a scenario based on the central limit theorem (a purely stochastic process).
@@
 Recent studies by several simulation projects have made predictions which are in good agreement with the observations at the intermediate redshift range ($z<1$).
-For example, the state-of-the-art cosmological hydrodynamical simulations of structure formation (MassiveBlackII) have compared the predicted scaling relations to the \hst\ observation at $0.3<z<1$ and predict a positive evolution that SMBH growth predates the host galaxy~\cite{DeG++15}.
+For example, the state-of-the-art cosmological hydrodynamical simulations of structure formation (\texttt{MassiveBlackII}) have compared the predicted scaling relations to the \hst\ observation at $0.3<z<1$ and predict a positive evolution that SMBH growth predates the host galaxy~\cite{DeG++15}.
 Several others works have investigated the scaling relations using large-volume simulations, resulting in well matches to the local relation with some redshift evolution, including approaches using the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014}.
@@
 To make the comparison, we adopt two independent simulation projects, including MassiveBlack-II (MBII)~\cite{Khandai2015} and semi-analytic models (SAM)~\cite{Menci2014}.
-These two models are based on independent model strategies, i.e., hydrodynamic simulation for MBII and semi-analytic model for SAM, respectively.
-The MBII simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
+These two models are based on independent model strategies, i.e., hydrodynamic simulation for \texttt{MBII} and semi-analytic model for \texttt{SAM}, respectively.
+The \texttt{MBII} simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
 The large simulation volume enables the simulating objects to evolve independently; the high enough mass and spatial resolution meet the requirements for the object details.
 On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems.
-However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as SAM.
-In previous works~\cite{Huang2018, DeG++15, Khandai2015, Bhowmick2019, Menci2014, Menci2016}, MBII and SAM have made high successful predictions, and we refer the interested readers to these works for more details.
+However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as \texttt{SAM}.
+In previous works~\cite{Huang2018, DeG++15, Khandai2015, Bhowmick2019, Menci2014, Menci2016}, \texttt{MBII} and \texttt{SAM} have made high successful predictions, and we refer the interested readers to these works for more details.
 
@@
 %Selection effect into account
-Based on MBII project, we collect a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones.
+Based on \texttt{MBII} project, we collect a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones.
 We take the measurement uncertainty and the selection effect into account to ensure a fair comparison,  with the following process.
@@
 \includegraphics[width=1.2\linewidth]{MBII_selectfunc.pdf}
-\caption{The same selection window as adopted for selecting the MBII simulated sample.
-The brown background clouds shows the overall MBII sample at $z=1.5$.
+\caption{The same selection window as adopted for selecting the \texttt{MBII} simulated sample.
+The brown background clouds shows the overall \texttt{MBII} sample at $z=1.5$.
 We add the random uncertainty to the simulation and select the ones fall into the targeting region (i.e.
@@
 \end{tabular}
-\caption{In the left panel, we present the comparison of the  \mbh-\mstar\ correlation between the observation (orange dots) and the MBII predicted samples (blue dots).
+\caption{In the left panel, we present the comparison of the  \mbh-\mstar\ correlation between the observation (orange dots) and the \texttt{MBII} predicted samples (blue dots).
 The predicted sample is treated to have the same uncertainty and selection effect as the observational ones.
-The blue line is the best-fit result for the MBII sample, with the colored region indicating the $1-\sigma$ confidence interval.
+The blue line is the best-fit result for the \texttt{MBII} sample, with the colored region indicating the $1-\sigma$ confidence interval.
 We use the same slope value to fit for the observed sample, and the orange line shows the best-fit result.
-The brown grids in the background are the overall sample that predicted by the MBII simulation.
-We present the comparison with the SAM sample (green color) in the right panel.
+The brown grids in the background are the overall sample that predicted by the \texttt{MBII} simulation.
+We present the comparison with the \texttt{SAM} sample (green color) in the right panel.
 }
@@
 
-We also make comparisons of our observed scaling relations to the predictions by the SAM model.
-Rather than N-body simulation which produces individual simulating objects, the SAM model uses the density clouds to describe the possibility of the samples.
+We also make comparisons of our observed scaling relations to the predictions by the \texttt{SAM} model.
+Rather than N-body simulation which produces individual simulating objects, the \texttt{SAM} model uses the density clouds to describe the possibility of the samples.
 %We consider the sample at $z=1.5$ epoch for two sample sets, including the overall sample and the selected sample, as shown in Figure~\ref{fig:SAM_comp}.
-We find that considering the selecting effect, the direct prediction by SAM is well matched to the observed relations.
-%We do not estimate the scatter for SAM model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one.
+We find that considering the selecting effect, the direct prediction by \texttt{SAM} is well matched to the observed relations.
+%We do not estimate the scatter for \texttt{SAM} model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one.
 \ding{This is not right yet.
-But if consider the scatter in the same way, the SAM have large scatter?}
-%Yet this is not a proper comparison since the direct sample from SAM does not include the scattering effect by the measurement uncertainty.
-To make the direct comparison, we first randomly generate an overall SAM sample based on the possibility clouds at $z=1.5$ epoch.
-Then, same as MBII's case, we inject the random uncertainty to the sample to take the uncertainty effect into account and select the sample the selection window.
+But if consider the scatter in the same way, the \texttt{SAM} have large scatter?}
+%Yet this is not a proper comparison since the direct sample from \texttt{SAM} does not include the scattering effect by the measurement uncertainty.
+To make the direct comparison, we first randomly generate an overall \texttt{SAM} sample based on the possibility clouds at $z=1.5$ epoch.
+Then, same as \texttt{MBII}'s case, we inject the random uncertainty to the sample to take the uncertainty effect into account and select the sample the selection window.
 The resulting comparison of the  \mbh-\mstar\ relation are shown in Figure~\ref{fig:MM_comp} (right panel).
-We find that the best-fit result by the SAM model is well matched to the observation.
-However, the scatter of the SAM model are overwhelmingly larger ($0.7$~dex) than the observation.
-This larger scatter is a combination result by the SAM distribution, uncertainty, and selection effect.
+We find that the best-fit result by the \texttt{SAM} model is well matched to the observation.
+However, the scatter of the \texttt{SAM} model are overwhelmingly larger ($0.7$~dex) than the observation.
+This larger scatter is a combination result by the \texttt{SAM} distribution, uncertainty, and selection effect.
 
@@
 We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched each other.
-The median values for the flux ratio distribution of the observed, MBII, SAM sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively.
-We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are 0.34 (for observed -- MBII) and 0.14 (for observed -- SAM), respectively.
+The median values for the flux ratio distribution of the observed, \texttt{MBII}, \texttt{SAM} sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively.
+We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are 0.34 (for observed -- \texttt{MBII}) and 0.14 (for observed -- \texttt{SAM}), respectively.
 This result indicates the three samples have similar host-to-total light distribution.
@@
 
-In terms of their central distribution, the MBII simulation and SAM model both demonstrate an excellent agreement to the observational constraints.
-However, when considering the scattering effect by the measurement uncertainty, the scatter in MBII simulation is consistent to the observational one ($\sim0.3$~dex) and SAM sample has much larger scatter ($\sim0.7$~dex).
-Given that the two models adopt very different assumptions, recipes, and initial conditions, our result shows that the mechanism (AGN feedback driven) by MBII is more favorable.
-An explanation for the larger scatter in the SAM model is that its BH feeding is by merger driven with more stochasticities in the scaling relations.
-In particular, the SAM cloud extends to the high \mbh\ with low stellar mass, which may not exist.
-\ding{To Nicola: is that possible to change the assumption in SAM to make the relations tighter?} The consistency between MBII and observations indicates that there has to be a causal link between SMBH and its host galaxy to generate an ordering during their evolution; as a result, more massive BHs are linked to more massive galaxies {\it tightly}.
+In terms of their central distribution, the \texttt{MBII} simulation and \texttt{SAM} model both demonstrate an excellent agreement to the observational constraints.
+However, when considering the scattering effect by the measurement uncertainty, the scatter in \texttt{MBII} simulation is consistent to the observational one ($\sim0.3$~dex) and \texttt{SAM} sample has much larger scatter ($\sim0.7$~dex).
+Given that the two models adopt very different assumptions, recipes, and initial conditions, our result shows that the mechanism (AGN feedback driven) by \texttt{MBII} is more favorable.
+An explanation for the larger scatter in the \texttt{SAM} model is that its BH feeding is by merger driven with more stochasticities in the scaling relations.
+In particular, the \texttt{SAM} cloud extends to the high \mbh\ with low stellar mass, which may not exist.
+\ding{To Nicola: is that possible to change the assumption in \texttt{SAM} to make the relations tighter?} The consistency between \texttt{MBII} and observations indicates that there has to be a causal link between SMBH and its host galaxy to generate an ordering during their evolution; as a result, more massive BHs are linked to more massive galaxies {\it tightly}.
 
@@
 In fact, our inferred intrinsic scatter of the observed sample is $\sim0.25$~dex, which is no more than the typical scatter at local relations in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}.
-Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the MBII overall sample as a proxy to estimate our value.
+Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \texttt{MBII} overall sample as a proxy to estimate our value.
 Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), resulting in an overestimating of the error-budget and thus underestimating of intrinsic scatter.
@@
 
+\textbf{The \texttt{MassiveBlackII} (\texttt{MBII}) simulation}.  
+\texttt{MBII} is a high-resolution cosmological hydrodynamic simulation which ran from $z=159$ to $z=0.06$ using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\cite{2005MNRAS.364.1105S}.
+It has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles.
+The resolution elements for dark matter and gas have masses of $1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$ respectively.
+The base cosmology corresponds to the results of WMAP7 \cite{2011ApJS..192...18K} i.e.
+$\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.
+The simulation includes a full modeling of gravity + gas hydrodynamics, as well as a wide range of subgrid recipes for the modeling of star formation \cite{2003MNRAS.339..289S}, black hole growth and feedback processes.
+Haloes were identified using a Friends-of-Friends (FOF) group finder \cite{1985ApJ...292..371D}.
+Within these haloes, self-bound substructures/ subhaloes were identified using \texttt{SUBFIND} \cite{2005MNRAS.364.1105S}.
+Galaxies are identified to the stellar matter components of the subhaloes.
+
+For the modeling of black hole growth and associated feedback, we adopt the prescription in \cite{2005Natur.433..604D} and \cite{2005MNRAS.361..776S}.
+In particular, seed black holes of mass $5\times 10^{5}~M_{\odot}/h$ are inserted into haloes of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$~(if they do not already contain a black hole).
+Once seeded, black hole growth occurs via gas accretion at a rate given by $\dot{M}_{bh}={4\pi G^2 M_{bh}^2 \rho}/{(c_s^2+v_{bh}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the ISM gas~(cold phase); $v_{bh}$ is the relative velocity between the black hole and the gas in its vicinity.
+$10\%$~(radiative efficiency) of the accreted gas is released as radiation.
+The accretion rate is allowed to be mildly super-Eddington i.e.
+limited to two times the Eddington accretion rate.
+A fraction~($5\%$) of the radiated energy couples to the surrounding gas as blackhole~(or AGN) feedback \cite{2005Natur.433..604D}.
+For the modeling of black hole mergers, two black holes are considered to be merged if their separation distance is within the spatial resolution of the simulation~(the SPH smoothing length), and their relative speeds are lower than the local sound speed of the medium.
+
+For the galaxy photometry, the spectral energy distributions~(SEDs) of the host galaxies were first obtained by summing up the contributions from the individual star particles.
+The stellar SEDs were modelled using the \texttt{PEGASE-2}~\cite{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF.
+The galaxy SEDs are finally convolved with the desired filter function to obtain the broad band photometry~(SDSS $r$ band magnitude).
+
+For more details regarding the \texttt{MBII} simulation, we refer the reader to \cite{2015MNRAS.450.1349K}.
+
+\textbf{The semi-analytic model (\texttt{SAM}) model}.  
+We base on the semi-analytic model described in~\cite{Menci2016}, to which we refer for details; here we recall its key points. 
+The merging trees of dark matter haloes are generated through a Monte Carlo procedure adopting the merging rates given by the Extended Press \& Schechter formalism (see~\cite{Lacey1993}) assuming 
+a Cold Dark Matter power spectrum of perturbations.
+For each dark matter halo included into a larger halo we computed the dynamical friction process, to  determine whether it will survive as a satellite, or sink to the centre to increase the mass of the central dominant galaxy; binary interactions (fly-by and merging) among satellite sub-halos are also described by the model.
+In each halo, we compute the amount of gas which cools due to atomic processes.
+The cooled gas  settles into a rotationally supported disc as described in ~\cite{Mo1998}.
+The gas is converted into stars through three different channels: quiescent star formation, gradually converting the gas into stars over long timescales $\sim 1$ Gyr; starbursts following galaxy interactions, occurring on timescales $\lesssim 100$ Myr, associated to BH feeding; internal disc instabilities triggering loss of angular momentum resulting into gas inflows toward the centre, therefore feeding star formation and BH accretion.
+The energy released by the Supernovae associated to the total star formation returns a fraction of the disc gas into the hot phase (stellar feedback).
+
+The semi-analytic model includes BH growth from primordial seeds.
+These are assumed to originate from PopIII stars with a mass $M_{seed}=100\,M_{\odot}$ \cite{Madau2001}, and to be initially present in all galaxy progenitors.
+We consider two BH feeding modes: accretion triggered by galaxy interactions and internal disc instabilities.
+These are described in detail in \cite{Menci2016}, and briefly recalled below.\newline
+1) BH accretion triggered by interactions.
+The interaction rate $\tau_r^{-1}=n_T\,\Sigma (r_t,v_c,V)\,V_{rel} (V)$ for galaxies with relative velocity $V_{rel}$ and number density $n_T$ in a common DM halo determines the probability for encounters,
+either fly-by or  merging, through the corresponding cross sections $\Sigma$ given in Menci et al. (2014). The fraction of
+gas destabilized in each interaction corresponds to the loss $\Delta j$ of orbital angular momentum $j$, and depends on the mass ratio of the merging partners $M'/M$ and on the impact factor $b$.
+\newline
+2) BH accretion induced by disc instabilities. We assume these to arise  in  galaxies with disc mass exceeding $M_{crit} =  {v_{max}^2 R_{d}/ G \epsilon}$ 
+\cite{Efstathiou1982} with $\epsilon=0.75$, where $v_{max}$ is the maximum circular velocity associated to each halo \cite{Mo1998}. 
+Such a criterion strongly suppresses the probability for disc instabilities to occur not only in massive, gas-poor galaxies, but also in 
+dwarf galaxies characterized by small values of the gas-to-DM mass ratios.
+The instabilities induce loss of angular momentum resulting into strong inflows that we compute following the 
+description in \cite{Hopkins2011}, recast and extended as in \cite{Menci2014}.
+
+Finally, the \texttt{SAM} model includes a detailed treatment of AGN feedback, presented and discussed in \cite{Menci2008}.
+This is assumed to stem from the fast winds with velocity up to
+$10^{-1}c$ observed in the central regions of AGNs
+(see  \cite{Chartas2002, Pounds2003}).  
+These supersonic outflows compress the gas into a blast wave terminated by
+a leading shock front, which  moves outwards with a lower but still
+supersonic speed and sweeps out the surrounding medium. Eventually,
+this medium is expelled from the galaxy. The model follows in detail the expansion of the 
+blast wave through the galaxy disc, and computes the fraction of gas expelled from the galaxy.  
+These depend on the ratio $\Delta E/E$ between the  energy injected into the galactic gas 
+(taken to be proportional to the energy radiated by the 
+AGN through the efficiency \ding{right? $\epsilon_{AGN}=5\times 10^{-2}$) }
+and the thermal energy of the unperturbed gas (see \cite{Menci2008} for details).
+
 \textbf{Linear fitting and scatter comparison}.  
@@
 The result is presented in Figure~\ref{fig:offset_comp} (left panel).
-We find the standard derivation of the residual for observed and MBII sample are both equal to $\sim0.3$~dex; however, for SAM, the scatter value is much larger ($\sim0.7$~dex).
-We perform the KS test of the scatter distribution between observed and MBII sample and infer the p-value as $\sim0.3$.
-Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the MBII sample and the observational sample have the same intrinsic scatter level.
-We adopt the python package {\sc Linmix} to estimate this intrinsic scatter based on the MBII overall sample and obtain $0.25$~dex.
+We find the standard derivation of the residual for observed and \texttt{MBII} sample are both equal to $\sim0.3$~dex; however, for \texttt{SAM}, the scatter value is much larger ($\sim0.7$~dex).
+We perform the KS test of the scatter distribution between observed and \texttt{MBII} sample and infer the p-value as $\sim0.3$.
+Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \texttt{MBII} sample and the observational sample have the same intrinsic scatter level.
+We adopt the python package {\sc Linmix} to estimate this intrinsic scatter based on the \texttt{MBII} overall sample and obtain $0.25$~dex.
 
@@
 \caption{The histogram of the scatter (i.e., residuals in the linear relation).
-The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, MBII sample and SAM sample, respectively, for both \mbh-\mstar\ and \mbh-\mr\ relations.
+The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, \texttt{MBII} sample and \texttt{SAM} sample, respectively, for both \mbh-\mstar\ and \mbh-\mr\ relations.
 }
@@
 and T.D.
-ran the MBII simulation and provide the simulation data.
+ran the \texttt{MBII} simulation and provide the simulation data.
 N.M.
-ran the SAM model and provide and the SAM data.
+ran the \texttt{SAM} model and provide and the \texttt{SAM} data.
 X.D, T.T, J.S., A.B., T.D., and N.M.
@@
 %\textbf{Code availability.} The \lenstronomy, which is used to decompose the AGN image  
-%The data reduction package used to process the SAM data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr.
+%The data reduction package used to process the \texttt{SAM} data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr.
 To derive the stellar kinematic parameters and the lick absorption line strengths, we use the publicly available penalised pixel-fitting (pPXF) code from M.

### 2019-10-04 NA_paper/manuscript_II/qso_paperII.tex
Share this version to John and Tommaso

@@
 \newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
+\newcommand{\sam}{\texttt{SAM}}
+\newcommand{\mbii}{\texttt{MBII}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For this purpose, we have a unique sample of 32 broad-line Active Galactic Nuclei (AGN) at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with the broad \halpha\ emission line, as detected by Subaru/FMOS, providing an accurate assessment of \mbh ~while multi-band \hst\ imaging is used to derive the host galaxies properties (e.g., \mstar).
-We directly compare this sample with two independent state-of-the-art simulations: MassiveBlack-II (MBII) and a semi-analytic model (SAM).
+We directly compare this sample with two independent state-of-the-art simulations: \texttt{MassiveBlackII} (MBII) and a semi-analytic model (SAM).
 Taking the selection biases into account, %by adopting the same selection function to choose the simulating sample,
-we find that both \texttt{MBII} and \texttt{SAM} agree well with the data, in terms of the central distribution.
-However, when considering measurement uncertainty and the scatter in the scaling relations, the observations are significantly more consistent with the \texttt{MBII} sample ($\sim0.3$~dex), than the \texttt{SAM} ($\sim0.7$~dex).
-In this respect, our observational constraints are able to distinguish between the two models, indicating that the recipe implemented by \texttt{MBII} (i.e., growth regulation through AGN feedback) is preferred over the \texttt{SAM} that does not include AGN feedback.
-Moreover, the intrinsic scatter of our high-$z$ sample is comparable to the local sample thus counter to the expectation from a scenario based on the central limit theorem (a purely stochastic process).
+we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
+However, when considering measurement uncertainty and the scatter in the scaling relations, the observations are significantly more consistent with the \mbii\ sample ($\sim0.3$~dex), than the \sam\ ($\sim0.7$~dex).
+{\color{red} In this respect, our observational constraints are able to distinguish the recipe adopted between the two models.
+Though both of them have considered AGN feedback in their simualitons, \mbii\ considers this feedback as the its driven for the scaling relation, rather than the recipe by \sam\ (galaxy interaction driven).} Moreover, the intrinsic scatter of our high-$z$ sample is comparable to the local sample thus counter to the expectation from a scenario based on the central limit theorem (a purely stochastic process).
 To some extent, our result attests that there has to be a causal link between SMBH and its host galaxy to induce an ordering so that the more massive black holes are tightly linked to the more massive galaxies.
@@
 For example, the state-of-the-art cosmological hydrodynamical simulations of structure formation (\texttt{MassiveBlackII}) have compared the predicted scaling relations to the \hst\ observation at $0.3<z<1$ and predict a positive evolution that SMBH growth predates the host galaxy~\cite{DeG++15}.
-Several others works have investigated the scaling relations using large-volume simulations, resulting in well matches to the local relation with some redshift evolution, including approaches using the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014}.
+Several others works have investigated the scaling relations using large-volume simulations, resulting in well matches to the local relation with some redshift evolution, including approaches using the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014, Li2019}.
 Besides hydrodynamic simulations, the semi-analytic models~\cite{Menci2014, Menci2016} also made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}.
@@
 
-To make the comparison, we adopt two independent simulation projects, including MassiveBlack-II (MBII)~\cite{Khandai2015} and semi-analytic models (SAM)~\cite{Menci2014}.
-These two models are based on independent model strategies, i.e., hydrodynamic simulation for \texttt{MBII} and semi-analytic model for \texttt{SAM}, respectively.
-The \texttt{MBII} simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
+To make the comparison, we adopt two independent simulation projects, including \texttt{MassiveBlackII} (MBII)~\cite{Khandai2015} and semi-analytic models (SAM)~\cite{Menci2014}.
+These two models are based on independent model strategies, i.e., hydrodynamic simulation for \mbii\ and semi-analytic model for \sam, respectively.
+The \mbii\ simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
 The large simulation volume enables the simulating objects to evolve independently; the high enough mass and spatial resolution meet the requirements for the object details.
 On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems.
-However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as \texttt{SAM}.
-In previous works~\cite{Huang2018, DeG++15, Khandai2015, Bhowmick2019, Menci2014, Menci2016}, \texttt{MBII} and \texttt{SAM} have made high successful predictions, and we refer the interested readers to these works for more details.
+However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as \sam.
+In previous works~\cite{Huang2018, DeG++15, Khandai2015, Bhowmick2019, Menci2014, Menci2016}, \mbii\ and \sam\ have made high successful predictions, and we refer the interested readers to the Method section for more details.
 
@@
 %Selection effect into account
-Based on \texttt{MBII} project, we collect a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones.
+Based on \mbii\ project, we collect a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones.
 We take the measurement uncertainty and the selection effect into account to ensure a fair comparison,  with the following process.
@@
 To make direct comparison, we fix the same slope value and obtain the best-fit intercept value for the observation.
-We find that, for the \mbh-\mstar\ relations, the mismatch ($0.15$~dex) is small and far below 1$-\sigma$ level.
+We find that, for the \mbh-\mstar\ relations, there is a notable mismatch ($\sim0.4$~dex), however within 1$-\sigma$ level.
 Furthermore, we compare the scatter of the sample by calculating the standard derivation of the residual in the linear regression.
@@
 \includegraphics[width=1.2\linewidth]{MBII_selectfunc.pdf}
-\caption{The same selection window as adopted for selecting the \texttt{MBII} simulated sample.
-The brown background clouds shows the overall \texttt{MBII} sample at $z=1.5$.
+\caption{The same selection window as adopted for selecting the \mbii\ simulated sample.
+The brown background clouds shows the overall \mbii\ sample at $z=1.5$.
 We add the random uncertainty to the simulation and select the ones fall into the targeting region (i.e.
@@
 \end{tabular}
-\caption{In the left panel, we present the comparison of the  \mbh-\mstar\ correlation between the observation (orange dots) and the \texttt{MBII} predicted samples (blue dots).
+\caption{In the left panel, we present the comparison of the  \mbh-\mstar\ correlation between the observation (orange dots) and the \mbii\ predicted samples (blue dots).
 The predicted sample is treated to have the same uncertainty and selection effect as the observational ones.
-The blue line is the best-fit result for the \texttt{MBII} sample, with the colored region indicating the $1-\sigma$ confidence interval.
+The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the $1-\sigma$ confidence interval.
 We use the same slope value to fit for the observed sample, and the orange line shows the best-fit result.
-The brown grids in the background are the overall sample that predicted by the \texttt{MBII} simulation.
-We present the comparison with the \texttt{SAM} sample (green color) in the right panel.
+The brown grids in the background are the overall sample that predicted by the \mbii\ simulation.
+We present the comparison with the \sam\ sample (green color) in the right panel.
 }
@@
 
-We also make comparisons of our observed scaling relations to the predictions by the \texttt{SAM} model.
-Rather than N-body simulation which produces individual simulating objects, the \texttt{SAM} model uses the density clouds to describe the possibility of the samples.
+We also make comparisons of our observed scaling relations to the predictions by the \sam\ model.
+Rather than N-body simulation which produces individual simulating objects, the \sam\ model uses the density clouds to describe the possibility of the samples.
 %We consider the sample at $z=1.5$ epoch for two sample sets, including the overall sample and the selected sample, as shown in Figure~\ref{fig:SAM_comp}.
-We find that considering the selecting effect, the direct prediction by \texttt{SAM} is well matched to the observed relations.
-%We do not estimate the scatter for \texttt{SAM} model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one.
+We find that considering the selecting effect, the direct prediction by \sam\ is well matched to the observed relations.
+%We do not estimate the scatter for \sam\ model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one.
 \ding{This is not right yet.
-But if consider the scatter in the same way, the \texttt{SAM} have large scatter?}
-%Yet this is not a proper comparison since the direct sample from \texttt{SAM} does not include the scattering effect by the measurement uncertainty.
-To make the direct comparison, we first randomly generate an overall \texttt{SAM} sample based on the possibility clouds at $z=1.5$ epoch.
-Then, same as \texttt{MBII}'s case, we inject the random uncertainty to the sample to take the uncertainty effect into account and select the sample the selection window.
+But if consider the scatter in the same way, the \sam\ have large scatter?}
+%Yet this is not a proper comparison since the direct sample from \sam\ does not include the scattering effect by the measurement uncertainty.
+To make the direct comparison, we first randomly generate an overall \sam\ sample based on the possibility clouds at $z=1.5$ epoch.
+Then, same as the process in \mbii\ analysis, we inject the random uncertainty to the sample to take the uncertainty effect into account and select the sample the selection window.
 The resulting comparison of the  \mbh-\mstar\ relation are shown in Figure~\ref{fig:MM_comp} (right panel).
-We find that the best-fit result by the \texttt{SAM} model is well matched to the observation.
-However, the scatter of the \texttt{SAM} model are overwhelmingly larger ($0.7$~dex) than the observation.
-This larger scatter is a combination result by the \texttt{SAM} distribution, uncertainty, and selection effect.
+We find that the best-fit result by the \sam\ model is well matched to the observation.
+However, the scatter of the \sam\ model are overwhelmingly larger ($0.7$~dex) than the observation.
+This larger scatter is a combination result by the \sam\ distribution, uncertainty, and selection effect.
 
@@
 We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched each other.
-The median values for the flux ratio distribution of the observed, \texttt{MBII}, \texttt{SAM} sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively.
-We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are 0.34 (for observed -- \texttt{MBII}) and 0.14 (for observed -- \texttt{SAM}), respectively.
+The median values for the flux ratio distribution of the observed, \mbii, \sam\ sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively.
+We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are 0.34 (for observed -- \mbii) and 0.14 (for observed -- \sam), respectively.
 This result indicates the three samples have similar host-to-total light distribution.
@@
 
-In terms of their central distribution, the \texttt{MBII} simulation and \texttt{SAM} model both demonstrate an excellent agreement to the observational constraints.
-However, when considering the scattering effect by the measurement uncertainty, the scatter in \texttt{MBII} simulation is consistent to the observational one ($\sim0.3$~dex) and \texttt{SAM} sample has much larger scatter ($\sim0.7$~dex).
-Given that the two models adopt very different assumptions, recipes, and initial conditions, our result shows that the mechanism (AGN feedback driven) by \texttt{MBII} is more favorable.
-An explanation for the larger scatter in the \texttt{SAM} model is that its BH feeding is by merger driven with more stochasticities in the scaling relations.
-In particular, the \texttt{SAM} cloud extends to the high \mbh\ with low stellar mass, which may not exist.
-\ding{To Nicola: is that possible to change the assumption in \texttt{SAM} to make the relations tighter?} The consistency between \texttt{MBII} and observations indicates that there has to be a causal link between SMBH and its host galaxy to generate an ordering during their evolution; as a result, more massive BHs are linked to more massive galaxies {\it tightly}.
+{\color{red} In terms of their central distribution, the \mbii\ simulation and \sam\ model both demonstrate an excellent agreement to the observational constraints.
+When considering the scattering effect by the measurement uncertainty, the scatter in \mbii\ simulation is consistent to the observational one ($\sim0.3$~dex); however, \sam\ sample has much larger scatter ($\sim0.7$~dex).
+Given that the two models adopt different assumptions, recipes, and initial conditions, our result shows that the mechanism by \mbii\ is more favorable, in which the scaling relation is AGN feedback driven \ding{To Aklant and Tiziana, do you agree with this statement?}.
+Through \sam\ model also consider the AGN feedback, the feeding process for the BH accretion is merger driven with more stochasticities in the scaling relations, which may leads to the larger scatter.
+In particular, in the \sam\ model the encounters are assumed to trigger the feedback and the fraction of gas feeding the BH is related to the parameters of the 
+encounter.
+This introduces additional scatter since it depends on the properties of both interacting galaxies (see Method).
+As a result, the \sam\ cloud extends to the high \mbh\ with low stellar mass, which may not exist.
+\ding{To Nicola: is that possible to change the assumption in \sam\ to make the relations tighter?} The consistency between \mbii\ and observations indicates that there has to be a causal link between SMBH and its host galaxy to generate an ordering during their evolution; as a result, more massive BHs are linked to more massive galaxies {\it tightly}.
+}
 
@@
 In fact, our inferred intrinsic scatter of the observed sample is $\sim0.25$~dex, which is no more than the typical scatter at local relations in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}.
-Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \texttt{MBII} overall sample as a proxy to estimate our value.
+Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate our value.
 Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), resulting in an overestimating of the error-budget and thus underestimating of intrinsic scatter.
@@
 We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3's result to infer the host color.
-We find that the 1~Gyr template could well match their color, see Figure~5 in D19, from which we estimate the rest-frame R band luminosity and stellar mass.
-A Salpeter initial mass function is employed consistently to the observed and simulated sample.
+{\color{red} We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the rest-frame R band luminosity and stellar mass.} A Salpeter initial mass function is employed consistently to the observed and simulated sample.
 
@@
 
-\textbf{The \texttt{MassiveBlackII} (\texttt{MBII}) simulation}.  
-\texttt{MBII} is a high-resolution cosmological hydrodynamic simulation which ran from $z=159$ to $z=0.06$ using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\cite{2005MNRAS.364.1105S}.
+\textbf{The \texttt{MassiveBlackII} (\mbii) simulation}.  
+\mbii\ is a high-resolution cosmological hydrodynamic simulation which ran from $z~=~159$ to $z~=~0.06$ using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\cite{2005MNRAS.364.1105S}.
 It has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles.
-The resolution elements for dark matter and gas have masses of $1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$ respectively.
-The base cosmology corresponds to the results of WMAP7 \cite{2011ApJS..192...18K} i.e.
-$\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.
+The resolution elements for dark matter and gas have masses of $1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$, respectively.
+The base cosmology corresponds to the results of WMAP7 \cite{2011ApJS..192...18K}, i.e., $\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.
 The simulation includes a full modeling of gravity + gas hydrodynamics, as well as a wide range of subgrid recipes for the modeling of star formation \cite{2003MNRAS.339..289S}, black hole growth and feedback processes.
 Haloes were identified using a Friends-of-Friends (FOF) group finder \cite{1985ApJ...292..371D}.
-Within these haloes, self-bound substructures/ subhaloes were identified using \texttt{SUBFIND} \cite{2005MNRAS.364.1105S}.
+Within these haloes, self-bound substructures/subhaloes were identified using \texttt{SUBFIND} \cite{2005MNRAS.364.1105S}.
 Galaxies are identified to the stellar matter components of the subhaloes.
 
-For the modeling of black hole growth and associated feedback, we adopt the prescription in \cite{2005Natur.433..604D} and \cite{2005MNRAS.361..776S}.
+For the modeling of black hole growth and associated feedback, we adopt the prescription in the reference \cite{2005Natur.433..604D, 2005MNRAS.361..776S}.
 In particular, seed black holes of mass $5\times 10^{5}~M_{\odot}/h$ are inserted into haloes of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$~(if they do not already contain a black hole).
@@
 $10\%$~(radiative efficiency) of the accreted gas is released as radiation.
-The accretion rate is allowed to be mildly super-Eddington i.e.
-limited to two times the Eddington accretion rate.
-A fraction~($5\%$) of the radiated energy couples to the surrounding gas as blackhole~(or AGN) feedback \cite{2005Natur.433..604D}.
+The accretion rate is allowed to be mildly super-Eddington, i.e., limited to two times the Eddington accretion rate.
+A fraction~($5\%$) of the radiated energy couples to the surrounding gas as black hole~(or AGN) feedback \cite{2005Natur.433..604D}.
 For the modeling of black hole mergers, two black holes are considered to be merged if their separation distance is within the spatial resolution of the simulation~(the SPH smoothing length), and their relative speeds are lower than the local sound speed of the medium.
@@
 
-For more details regarding the \texttt{MBII} simulation, we refer the reader to \cite{2015MNRAS.450.1349K}.
+For more details regarding the \mbii\ simulation, we refer the reader to the reference~\cite{2015MNRAS.450.1349K}.
 
-\textbf{The semi-analytic model (\texttt{SAM}) model}.  
-We base on the semi-analytic model described in~\cite{Menci2016}, to which we refer for details; here we recall its key points. 
-The merging trees of dark matter haloes are generated through a Monte Carlo procedure adopting the merging rates given by the Extended Press \& Schechter formalism (see~\cite{Lacey1993}) assuming 
-a Cold Dark Matter power spectrum of perturbations.
+\textbf{The semi-analytic model (\sam)}. The \sam\ is based on the description in Menci et al. (2016)~\cite{Menci2016}, to which we refer for details; here we recall its key points. 
+The merging trees of dark matter haloes are generated through a Monte Carlo procedure adopting the merging rates given by the Extended Press \& Schechter formalism~\cite{Lacey1993} assuming a Cold Dark Matter power spectrum of perturbations.
 For each dark matter halo included into a larger halo we computed the dynamical friction process, to  determine whether it will survive as a satellite, or sink to the centre to increase the mass of the central dominant galaxy; binary interactions (fly-by and merging) among satellite sub-halos are also described by the model.
 In each halo, we compute the amount of gas which cools due to atomic processes.
-The cooled gas  settles into a rotationally supported disc as described in ~\cite{Mo1998}.
-The gas is converted into stars through three different channels: quiescent star formation, gradually converting the gas into stars over long timescales $\sim 1$ Gyr; starbursts following galaxy interactions, occurring on timescales $\lesssim 100$ Myr, associated to BH feeding; internal disc instabilities triggering loss of angular momentum resulting into gas inflows toward the centre, therefore feeding star formation and BH accretion.
+The cooled gas  settles into a rotationally supported disc as the descriptions in the reference~\cite{Mo1998}.
+The gas is converted into stars through three different channels: quiescent star formation, gradually converting the gas into stars over long timescales $\sim 1$~Gyr; starbursts following galaxy interactions, occurring on timescales $\lesssim 100$~Myr, associated to BH feeding; internal disc instabilities triggering loss of angular momentum resulting into gas inflows toward the centre, therefore feeding star formation and BH accretion.
 The energy released by the Supernovae associated to the total star formation returns a fraction of the disc gas into the hot phase (stellar feedback).
@@
 The semi-analytic model includes BH growth from primordial seeds.
-These are assumed to originate from PopIII stars with a mass $M_{seed}=100\,M_{\odot}$ \cite{Madau2001}, and to be initially present in all galaxy progenitors.
+These are assumed to originate from PopIII stars with a mass $M_{seed}=100\,M_{\odot}$~\cite{Madau2001}, and to be initially present in all galaxy progenitors.
 We consider two BH feeding modes: accretion triggered by galaxy interactions and internal disc instabilities.
-These are described in detail in \cite{Menci2016}, and briefly recalled below.\newline
+These are described in detail in our previous work~\cite{Menci2016}, and briefly recalled below.\newline
 1) BH accretion triggered by interactions.
 The interaction rate $\tau_r^{-1}=n_T\,\Sigma (r_t,v_c,V)\,V_{rel} (V)$ for galaxies with relative velocity $V_{rel}$ and number density $n_T$ in a common DM halo determines the probability for encounters,
-either fly-by or  merging, through the corresponding cross sections $\Sigma$ given in Menci et al. (2014). The fraction of
+either fly-by or  merging, through the corresponding cross sections $\Sigma$ given in Menci et al. (2014)~\cite{Menci2014}. The fraction of
 gas destabilized in each interaction corresponds to the loss $\Delta j$ of orbital angular momentum $j$, and depends on the mass ratio of the merging partners $M'/M$ and on the impact factor $b$.
 \newline
-2) BH accretion induced by disc instabilities. We assume these to arise  in  galaxies with disc mass exceeding $M_{crit} =  {v_{max}^2 R_{d}/ G \epsilon}$ 
-\cite{Efstathiou1982} with $\epsilon=0.75$, where $v_{max}$ is the maximum circular velocity associated to each halo \cite{Mo1998}. 
+2) BH accretion induced by disc instabilities.
+We assume these to arise  in  galaxies with disc mass exceeding~\cite{Efstathiou1982} $M_{crit} =  {v_{max}^2 R_{d}/ G \epsilon}$ with $\epsilon=0.75$, where $v_{max}$ is the maximum circular velocity associated to each halo \cite{Mo1998}.
 Such a criterion strongly suppresses the probability for disc instabilities to occur not only in massive, gas-poor galaxies, but also in 
@@
 The instabilities induce loss of angular momentum resulting into strong inflows that we compute following the 
-description in \cite{Hopkins2011}, recast and extended as in \cite{Menci2014}.
+description in Hopkins et al. (2011)~\cite{Hopkins2011}, recast and extended as in Menci et al. (2014)~\cite{Menci2014}.
 
-Finally, the \texttt{SAM} model includes a detailed treatment of AGN feedback, presented and discussed in \cite{Menci2008}.
+Finally, the \sam\ model includes a detailed treatment of AGN feedback, presented and discussed in Menci et al. (2008)~\cite{Menci2008}.
 This is assumed to stem from the fast winds with velocity up to
-$10^{-1}c$ observed in the central regions of AGNs
-(see  \cite{Chartas2002, Pounds2003}).  
+$10^{-1}c$ observed in the central regions of AGNs~\cite{Chartas2002, Pounds2003}.  
 These supersonic outflows compress the gas into a blast wave terminated by
@@
 (taken to be proportional to the energy radiated by the 
-AGN through the efficiency \ding{right? $\epsilon_{AGN}=5\times 10^{-2}$) }
-and the thermal energy of the unperturbed gas (see \cite{Menci2008} for details).
+AGN through the efficiency {\color{red} $\epsilon_{AGN}=5\times 10^{-2}$) }
+and the thermal energy of the unperturbed gas (see Menci et al. (2008)~\cite{Menci2008} for details).
 
@@
 The result is presented in Figure~\ref{fig:offset_comp} (left panel).
-We find the standard derivation of the residual for observed and \texttt{MBII} sample are both equal to $\sim0.3$~dex; however, for \texttt{SAM}, the scatter value is much larger ($\sim0.7$~dex).
-We perform the KS test of the scatter distribution between observed and \texttt{MBII} sample and infer the p-value as $\sim0.3$.
-Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \texttt{MBII} sample and the observational sample have the same intrinsic scatter level.
-We adopt the python package {\sc Linmix} to estimate this intrinsic scatter based on the \texttt{MBII} overall sample and obtain $0.25$~dex.
+We find the standard derivation of the residual for observed and \mbii\ sample are both equal to $\sim0.3$~dex; however, for \sam, the scatter value is much larger ($\sim0.7$~dex).
+We perform the KS test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.3$.
+Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \mbii\ sample and the observational sample have the same intrinsic scatter level.
+We adopt the python package {\sc Linmix} to estimate this intrinsic scatter based on the \mbii\ overall sample and obtain $0.25$~dex.
 
@@
 \caption{The histogram of the scatter (i.e., residuals in the linear relation).
-The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, \texttt{MBII} sample and \texttt{SAM} sample, respectively, for both \mbh-\mstar\ and \mbh-\mr\ relations.
+The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, \mbii\ sample and \sam\ sample, respectively, for both \mbh-\mstar\ and \mbh-\mr\ relations.
 }
@@
 Malkan.
-XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
+XD and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
 JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
@@
 is supported by the EACOA fellowship.
+\ding{More acknowledge.}
 
@@
 and T.D.
-ran the \texttt{MBII} simulation and provide the simulation data.
+ran the \mbii\ simulation and provide the simulation data.
 N.M.
-ran the \texttt{SAM} model and provide and the \texttt{SAM} data.
+ran the \sam\ model and provide and the \sam\ data.
 X.D, T.T, J.S., A.B., T.D., and N.M.
@@
 %\textbf{Code availability.} The \lenstronomy, which is used to decompose the AGN image  
-%The data reduction package used to process the \texttt{SAM} data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr.
+%The data reduction package used to process the \sam\ data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr.
 To derive the stellar kinematic parameters and the lick absorption line strengths, we use the publicly available penalised pixel-fitting (pPXF) code from M.

### 2019-10-07 manuscript/manuscript.tex
Finish udpate the paper based on the referee report!!!

@@
 \usepackage[caption=false]{subfig}
+\usepackage{booktabs}
 
@@
 The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators.
-We find the {\it observed} ratio of \mbh/\smass~to {\bf be $2.5\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs.
-\ding{TBC: However, an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
+We find the {\it observed} ratio of \mbh/\smass~to {\bf be $2.6\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs.
+\ding{(TB update based on Daeseong's result:) an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
 Therefore, our results are in agreement, considering the uncertainties, with a scenario where SMBHs and their total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter.
@@
 Second, measurements of the host galaxy properties are challenging due to the overwhelming glare of the bright nuclear light.
-This ultimately requires careful modeling of the point spread function and, whenever possible, the use of lensed QSOs since the magnification increases the spatial resolution \citep{Pen++06qsob, Ding2017a, Ding2017b}.
+This ultimately requires careful modeling of the point spread function and, whenever possible, the use of lensed {\bf AGNs} since the magnification increases the spatial resolution \citep{Pen++06qsob, Ding2017a, Ding2017b}.
 Especially not to be overlooked as in past studies, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}.
@@
 This value is the minimum offset expected for a non-evolving mass ratio as described in Section~\ref{sec:sf_framework}.
+{\bf Furthermore, we collect the most similar AGN sample from the local and intermediate redshift and re-calibrate their quantities based on a set of consistent recipes, which ensures our comparison results solid, see Section~\ref{sec:compare_sample}.}
 
@@
 We describe the sample selection and their BH masses in Section~\ref{sec:data}.
-We describe the new HST/WFC3 observations, available HST/ACS imaging, and construction of a PSF library in Section~\ref{observation}.
+We describe the new \hst/WFC3 observations, available \hst/ACS imaging, and construction of a PSF library in Section~\ref{observation}.
 In Section~\ref{sec:analysis}, we describe our method to decompose the rest-frame optical emission and measure the host galaxy surface photometry.
@@
 On the right, we illustrate the shape of the Eddington rate distribution at these redshifts from the same reference.
-For comparison, we plot the high-$z$ luminous SDSS QSO samples that have been studied with \hst\ ~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}, mainly at the high mass end.}
+For comparison, we plot the high-$z$ luminous SDSS {\bf AGN} samples that have been studied with \hst\ ~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}, mainly at the high mass end.}
 \end{figure}
@@
 In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan.
-Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh.
+Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range $0.9-1.8$~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh.
 Recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields.
@@
 $<0.03$~dex).
-However, there is a $\sim$0.2 dex inconsistency in their \halpha\ mass estimates.
+However, there is a $\sim0.2$ dex inconsistency in their \halpha\ mass estimates.
 Therefore, we utilize the AGNs in \citet{Schulze2018} that have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to determine which \halpha\ estimator has the best agreement between the two lines.
@@
 
-Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model that include the local value of the mass \mbh/\smass ~ratio.
+Adopting our specific selection limits into the framework {\bf (i.e., $\log($\mbh$/M_{\odot})\in[7.5, 8.56]$, $\log(L_{\rm bol}/L_{\odot})\in[45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$),} we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model that include the local value of the mass \mbh/\smass ~ratio.
 To reiterate, an offset in the observed mass relations of 0.2 dex at $z\sim1.5$ can be considered consistent with no evolution in the mass ratio.
@@
 The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$.
+{\bf The stellar mass of these 27 object have been estimated using multi-band imaging data, and we adopt them to compare the \mbh-\smass\ relation.}
  In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample.
 Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh} including those estimated from \Mgii\ using the recipe in \citet{Ding2017b}.
+
+{\bf The value for the all the \mbh-\lhost\ comparison sample are listed in \citet{Ding2017b} (in Table~1 and Table~2).
+The \mbh-\smass\ comparison sample are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.}
 
@@
 %Drizzling, background noise...
-For each target, we obtained six separate exposures of 399s (i.e., total exposure time 2394s).
-The six exposures were dithered and combined with the {\sc astrodrizzle} software package following standard procedures, and resulted in an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 and using a \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted.
+For each target, we obtained six separate exposures of $399$s (i.e., total exposure time $2394$s).
+The six exposures were dithered and combined with the {\sc astrodrizzle} software package following standard procedures, and resulted in an output pixel scale of $0\farcs{0642}$ by setting \texttt{pixfrac} parameter as $0.8$ and using a \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted.
 We achieve to analyze this sample using the same approach, taking the 3 available frames.}.
@@
 
-{\bf Obtaining the \hst\ image,  we first account for the background light which could come from both the sky and the detector.
+{\bf Having obtained the \hst\ image, we remove the background light which could come from both the sky and the detector.
 In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm.
-Then, we remove the globe sky background light to obtain the clean image.
-To ensure the background light has been accurately subtracted, we investigate the surface brightness at the sampled empty area to ensure it is neither positive nor negative.}
-
-We carefully test the surface brightness at the empty area to ensure the
+Then, we subtract the globe sky background light to obtain the clear image.
+To test the fidelity of this subtraction, we investigate the surface brightness at the empty regions and make sure it is neither positive nor negative.
+Finally, we extract postage stamp of the AGN image and PSF image to carry out the modeling process, see Section~\ref{sec:psf_library} and Section~\ref{sec:analysis}.}
 
@@
 Here, we utilize images taken with ACS/F814W filter.
-The final image is drizzled to 0\farcs{03} pixel scale.
+The final image is drizzled to $0\farcs{03}$ pixel scale.
 Given the multi-band images for our AGN, we are able to infer their host color and assess the contribution of both the young and old stellar population which ensures an accurate inference of rest-frame R-band luminosity (including a K-correction) and stellar mass \citep{Gallazzi2009}.
@@
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
-\caption{\label{fig:AGN_decomp} AGN-host galaxy decomposition of COSMOS-CID1174 based on the \hst/WFC3 F140W image.The panels from left to right are as follows: (1) observed data, (2) best-fit model (AGN+host), (3) data minus the model PSF (i.e., host galaxy free of the AGN), (4) residuals divided by the variance and (5)~1-D surface brightness profiles (top) and the corresponding residual (bottom).
+\caption{\label{fig:AGN_decomp} AGN-host galaxy decomposition of COSMOS-CID1174 based on the \hst/WFC3 F140W image.The panels from left to right are as follows: (1) observed data, (2) best-fit model (AGN$+$host), (3) data minus the model PSF (i.e., host galaxy free of the AGN), (4) residuals divided by the variance and (5)~1-D surface brightness profiles (top) and the corresponding residual (bottom).
 The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects).
@@
 The errors on the fit parameters are assessed by using different PSFs for each object in the sample.} \citep{PSO}.
-To avoid any unphysical results, we set the upper and lower limits on the parameters: effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, \sersic\ index $n\in[0.3,7]$.
+To avoid any unphysical results, we set the upper and lower limits on the parameters: effective radius \Reff~$\in[0\farcs{}1,1\farcs{0}]$, \sersic\ index $n\in[0.3,7]$.
 Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best-fit PSFs.
@@
 {
-\includegraphics[height=0.25\textwidth]{fig/hist_compare.pdf}
+\includegraphics[height=0.3\textwidth]{fig/hist_f_ratio_compare.pdf}\\
+\includegraphics[height=0.3\textwidth]{fig/hist_Reff_compare}\\
 }
 \caption{\label{fig:hist_compare} 
-Distribution of the host-to-total flux ratio when implementing a different number of top-ranked PSFs.}
+Distribution of the host-to-total flux ratio {\bf and effective radius} when implementing a different number of top-ranked PSFs.}
 \end{figure}
@@
 \label{sec:result-hosts}
-As shown in Figure~\ref{fig:hist_compare}, the host-to-total flux ratio (total$=$host$+$nuclear) of the sample spans a wide range from $10\%$ to $90\%$ with most of the sample concentrated between $20\%$ to $50\%$ (median value $37\%$).
+As shown in Figure~\ref{fig:hist_compare} {\bf (top panel)}, the host-to-total flux ratio (total$=$host$+$nuclear) of the sample spans a wide range from $10\%$ to $90\%$ with most of the sample concentrated between $20\%$ to $50\%$ (median value $37\%$).
 Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the {\bf five sample (i.e., CID255, CID50, LID360, CDFS-229, SXDS-X763) which have host-to-total flux ratios lower than $20\%$} should be considered as marginal detections.
 
-The distributions of effective radius \Reff\ and \sersic\ index are shown in Figure~\ref{fig:hist_rn}.
-These values are distributed within the allowed range and not concentrated on either the upper or lower bound.
+The distributions of effective radius \Reff\ {\bf are shown in Figure~\ref{fig:hist_compare} {\bf (bottom panel)}.
+Based on the sample redshift and the cosmological model, we calculate their physical scale in kpc unit.
+We plot them together with inferred \sersic\ index in Figure~\ref{fig:hist_rn}.} These values are distributed within the allowed range and not concentrated on either the upper or lower bound.
 The \Reff\ of our sample are between $\sim1-7$~kpc (peaked at $\sim2.2$~kpc).
@@
 Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
-The inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero.
+{\bf Seven systems have low effective radius \Reff$<0\farcs18$ that is within 3 pixels; we re-fit them with a \Reff\ $\in[0\farcs{}2,1\farcs{0}]$ prior and find that the inferred host flux barely changes ($<1\%$).
+In particular, the}
+inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero.
 This means the size inference of these three systems should really be considered an upper limit, rather than a measurement.
-However, the inference of their host luminosities and stellar masses are still reliable given the small scatter in the host flux ($<10\%$).
+However, the inference of their host luminosities and stellar masses are still reliable given {\bf the consistent result of our re-fitting test and} the small scatter in the host flux ($<10\%$).
 
@@
 We derive the rest-frame R band luminosity from $\log L_R/L_{R, \odot} = 0.4\times(M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}.
-$L_R$ ranges between $\log L_R \in [9.5, 11.5]$ ($L_{\odot,R}$) with individual values listed in Table~\ref{tab:result_sersic}.
+$L_R$ ranges {\bf between $\log (L_R/L_{\odot,R})  \in [9.5, 11.5]$ with} individual values listed in Table~\ref{tab:result_sersic}.
 
@@
 The black line and the blue colored equation indicates the best-fit result of the local sample as given in Equation~\ref{eq:MLlocal}, with $1\sigma$ confidence interval indicated by the gray region.
+{\bf The values for the comparison sample, including the local and the intermediate, are listed in \citet{Ding2017b}, Table 1 and 2.}
 }
@@
 \end{eqnarray} 
-Performing such a fit based on the {\it observed} data (i.e., no correction for selection effects), {\bf we obtain $\gamma  = 1.01 \pm 0.26$ that} may be tentatively considered as evidence for evolution.
+Performing such a fit based on the {\it observed} data (i.e., no correction for selection effects), {\bf we obtain $\gamma  = 1.03 \pm 0.25$ that} may be tentatively considered as evidence for evolution.
 Even with the exclusion of the few outliers, there is an evolution in the {\bf correlation with $\gamma  = 0.89 \pm 0.27$}.
@@
 The orange band is the intrinsic scatter of local linear relation.
-The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, with slope value $\gamma  = 0.78 \pm 0.26$.
+The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, {\bf with slope value $\gamma  = 1.03 \pm 0.25$}.
 {\it Right}: \mbh/\smass\ as a function of redshift.
 In both panels, we use blue open circles to show the expected bias of the median value for $\Delta \log$\mbh.
-We use framework of \citet{Schulze2011,Schulze2014} to show that even with no evolution selection effects would shift the expectation higher towards the measured values as indicated by the small arrow (Section~\ref{sec:sf_framework}.)}
+We use framework of \citet{Schulze2011,Schulze2014} to show that even with no evolution selection effects would shift the expectation higher towards the measured values as indicated by the small arrow (Section~\ref{sec:sf_framework}.) {\bf The local sample and intermediate sample are re-calibrated using self-consistent recipe and listed in Table~\ref{tab:comp_sample}.}}
 \end{figure*}
@@
 As shown in these panels, the scatter of the high-$z$ correlation presents a similarity to the local relation.
-To quantitively make this comparison, we calculate the intrinsic scatter of their offset value, based on Equation~\ref{eq:infer_value}, and \ding{(This needs to be rewritten:) obtain $0.25$ for high-$z$ and $0.35$ for local samples}, respectively.
-The fact that the intrinsic scatter for the high-$z$ sample is no larger than the local one may pose a challenge for explanations of scaling relations where random mergers are the origin of the correlation \citep{Peng2007,Jahnke2011}, indicating that there may likely be a connection between the SMBHs and their host galaxies during their formation.
+To quantitively make this comparison, {\bf we investigate the intrinsic scatter of our sample.
+Note that the {\it observed} high-$z$ sample has effects from both the measurement uncertainty and the narrow selection window, and thus one needs to take them both into account to extract the intrinsic scatter.
+We adopt the forward simulation process and find that when a simulated AGN sample has intrinsic scatter as $0.25$~dex,  the observed data (after considering the measurement uncertainty and the selection effect) would have the observational scatter at our level.
+We will give more descriptions in our forthcoming paper (Ding et al.
+in prep.), where we focus on the scatter of the sample}.
+The fact that the intrinsic scatter for the high-$z$ sample is no larger than the local one{\bf, which is $\sim0.35$~dex \citep{Gul++09},} may pose a challenge for explanations of scaling relations where random mergers are the origin of the correlation \citep{Peng2007,Jahnke2011}, indicating that there may likely be a connection between the SMBHs and their host galaxies during their formation.
 
@@
 
-First, we establish a relation between the single-\sersic\ index and the B/T ratio using inactive galaxies from CANDELS at similar redshifts and stellar masses (Figure~\ref{fig:BT-n_relation}; \smass$\in~[9.0, 11.5]$) using the B/T measurements of \citet{Dimauro2018}.
+First, we establish a relation between the single-\sersic\ index and the B/T ratio using inactive galaxies from CANDELS at similar redshifts and stellar masses {\bf (Figure~\ref{fig:BT-n_relation}; $\log (M_*/M_{\odot})\in~ [9.0, 11.5]$)} using the B/T measurements of \citet{Dimauro2018}.
 In the figure, the red line indicates the average B/T ratio at a given \sersic\ index.
@@
 \caption{\label{fig:BT-n_relation} 
-Relation between bulge-to-total stellar mass ratio and single-\sersic\ index using CANDELS inactive galaxies with \smass$\in [9.0, 11.5]$.
+Relation between bulge-to-total stellar mass ratio and single-\sersic\ index using CANDELS inactive galaxies {\bf with $\log (M_*/M_{\odot})\in~[9.0, 11.5]$}.
 The red curve is the averaged B/T ratio at different \sersic\ index.
@@
 Same as Figure~\ref{fig:MM-vz}, but for \mbh-\bmass\ relations.
-The intermediate sample consists of 27 objects from \citet{Bennert11} and \citet{SS13}.
+The intermediate sample consists of 27 objects from \citet{Bennert11} and \citet{SS13}{\bf , listed in Table~\ref{tab:comp_sample}}.
 \citet{Cisternas2011} do not provide information to infer their bulge mass.}
@@
 
-\subsection{Systematic errors}
+\subsection{Systematic errors}\label{sec:sysm_err}
 
@@
 The fidelity of the host galaxy magnitude is high as demonstrated by the robustness with respect to the choice of PSF, which is the primary source of uncertainty.
-However, we introduce some uncertainty by adopting a simple stellar population template to derive the rest-frame R-band luminosity and stellar mass for the full population.
+However, we introduce some uncertainty by adopting {\bf a common} simple stellar population {\bf templates} to derive the rest-frame R-band luminosity and stellar mass for the full population.
 In principle, if we had more information on the color, we could improve on this source of uncertainty by adopting a specific stellar population model for each target.
-However, considering that the host magnitude in the \hst/ACS band is faint (host-to-total flux ratio $< 30\%$), the individual color that we measure is insufficient to further discriminate between templates, and thus we adopt a single one for simplicity and to facilitate reproduction of our work.
+However, considering that the host magnitude in the \hst/ACS band is faint (host-to-total flux ratio $< 30\%$), the individual color that we measure is insufficient to further discriminate between templates, and thus we adopt {\bf the comment templates} for simplicity and to facilitate reproduction of our work.
 
@@
 Thus, the choice of template is a subdominant source of error.
-{\bf Note that large uncertainties of \mbh\ is not apparent in our figures, since we only select the AGN sample that have {\it measured} \mbh\ falls into our selection window.
+{\bf Note that the large uncertainties of \mbh\ is not apparent by the figures, since we only select the AGN sample that have {\it measured} \mbh\ falls into our selection window.
 The detailed analysis on this effect is beyond the scope.
@@
 To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011} and \citet{H+R04}.
-In the literature, other analyses of the local sample are available, which could also be considered as the local anchor.
+In the {\bf literature~\citep{Kormendy13, Bentz2018}}, other analyses of the local sample are available, which could also be considered as the local anchor.
 We note that the different local samples have inconsistencies, which could affect our measurement of the co-evolution.
-Since the local correlations are used to calibrate the single epoch black hole mass estimates, one needs to be self-consistent in the choice of local anchors and calibration of black hole mass estimators.
-Unfortunately, this is a thorny issue, since not all the local correlations are mutually consistent, especially when considering different galaxy properties like luminosity, stellar mass, and velocity dispersion.
-
-To illustrate the problem, we compare our local \mbh-\smass\ sample to that published in \citet{Kormendy13} (hereafter K13).
+{\bf In this paper, we aim to make the differential measurement as function of redshift.
+With this goal in mind, the consistency between the local and distant sample is crucial in terms of measurement procedure.
+This consistency is related to how measurement systematics and calibrations propagate between the galaxy dynamical masses v.s.
+galaxy stellar masses, bulge v.s.
+total and \mbh\ by single epoch v.s.
+reverberation v.s.
+dynamical.
+
+For example, since} the local correlations are used to calibrate the single epoch black hole mass estimates, one needs to be self-consistent in the choice of local anchors and calibration of black hole mass estimators.
+Unfortunately, this is a thorny issue, since not all the local correlations are mutually consistent, especially when considering different galaxy properties like luminosity, stellar mass, and velocity dispersion.{\bf To illustrate} the problem, we compare our local \mbh-\smass\ sample to that published in \citet{Kormendy13} (hereafter K13).
 We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset relative to our local sample.
 Note that a $+0.3$~dex difference could totally erase the $\Delta\log$\mbh\ for the high redshift sample as described in the last section, if it were independent of the black hole mass calibration.
-
-However, the \mbh-\sigstar\ relations by K13 are also offset by  $\sim+0.3$~dex with respect to those given by \citet{Woo2010}, which is the baseline for our adopted black hole mass estimators.
+{\bf However,} the \mbh-\sigstar\ relations by K13 are also offset by  $\sim+0.3$~dex with respect to those given by \citet{Woo2010}, which is the baseline for our adopted black hole mass estimators.
 That is, if we were to adopt the K13 normalization instead, the \mbh\ of all the AGN sample should be increased by $\sim$0.3~dex at the same time.
 As a result, adopting a different local anchor would only globally affect the level of the \mbh\ to local and high-$z$ sample at the same time, with the result of leaving $\Delta\log$\mbh\ unchanged.
+{\bf To qualitative present this point, we adopt the K13 local elliptical and classic bulge as the $z\sim0$ anchor and compared to the recalibrated the \mbh\ of our 32 AGNs sample.
+The inference of  $\gamma$ is $0.74\pm0.31$ which is consistent at $1-\sigma$ level with the one (i.e., $\gamma=1.03\pm0.25$ ) by current anchor.
+
+For the local by \citet{Bentz2018}, with different goal in mind, they decompose their host using more components than bulge$+$disk (e.g., Bar(s), Barlens, Ring(s)).
+This is beyond the comparison medium, i.e., bulge v.s.
+disk, of ours.
+Moreover, with a more manageable model, our inference gets ride of the overfitting issue.
+In spite of this, when adopting the \citet{Bentz2018} as local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution.
+ }
 
@@
 
-We find the average ``observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, {\bf by a factor of $\sim2.7$ and $\sim2.5$ respectively}, as compared to that in the local universe.
-\ding{TBC: However, taking into account selection bias, these correlations are consistent with those in the local universe within the 95\% confidence limits.
-}
+We find the average ``observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, {\bf by $0.41$~dex (a factor of $\sim2.7$) and  $0.43$~dex (a factor of $\sim2.6$), respectively}, as compared to that in the local universe.
+{\bf However, the selection effect could bias the inference at $+2.1$~dex level, while taking in to account, the offset to the local universe is no more significant.} 
+%these correlations are consistent with those in the local universe within the 95\% confidence limits. }
 Even with the remaining uncertainties in the corrections for selection, we are confident that any evolution in the \mbh/\smass\ relation is at the most a factor of two with the case of no evolution entirely plausible.
@@
 
+{\bf We summarize several limitations of this work.
+First, due to limited data qualities, we model the host proper as a single \sersic\ profile.
+The multi-components feature (e.g., disk$+$bulge) did not appear in the residual map, showing the multi-components information is overwhelmed by the noise level.
+Second, we adopt the common stellar templates to derive the host luminosity and stellar mass for overall sample, which introduces some uncertainty in the inference of the host properties.
+Even so, the uncertainty in the scaling relations is still dominated by the single epoch black hole mass estimates (see Section~\ref{sec:sysm_err} for detail).
+Third, for several AGN systems, their inferred host effective radius hit the lower limit, and thus the inference of their \Reff\ should be considered as upper limit.
+However, the inference of their host luminosities and stellar masses are still reliable, given our re-fitting test using different lower limit boundary and the low scatter of the host flux inference (see Section~\ref{sec:result-hosts}, second paragraph).
+Last, in the literature, there are several different sample could be choose as local anchor to the high-$z$ sample, which could changes the inference of the evolution value.
+In this work, we adopted the most similar local sample to those at high-$z$.
+We discussed the different anchors in detail and test to infer the evolution different anchors; all the inference show the positive evolution  (see Section~\ref{sec:local_sys}).}
+
 Given that the \smass$_{\rm ,total}$-\mbh\ relation is closer to or consistent with the local relation, the inferred evolution of the \bmass-\mbh\ correlations is qualitatively consistent with a scenario where the assembly of the black hole predates that of the bulge, which is processed by the transfer of stellar mass from the disk via mergers or secular processes \citep{Croton2006}.
@@
 Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555.
-The authors fully appreciate input from Luis Ho, Renyue Cen, Hyewon Suh, Takahiro Morishita and Peter Williams.
+
+{\bf The authors thank the anonymous referee for helpful suggestions and comments which improved the presentation of this paper.} We fully appreciate input from Luis Ho, Renyue Cen, Hyewon Suh, Takahiro Morishita and Peter Williams.
 XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
@@
 Having transferred the \lhost\ to today, we find that, as showing in Figure~\ref{fig:ML-vz}-(a), at fixed mass, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation.
-We fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and {\bf obtain $\gamma = 0.64 \pm 0.17$, } as showing in Figure~\ref{fig:ML-vz}-(b).
+{\bf Based on the 32 AGN systems, we fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 1.07\pm0.23$, } as showing in Figure~\ref{fig:ML-vz}-(b).
 We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and \ding{ TBD: obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.3$, with} flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
@@
 %Moreover, in the literature, the correlation of the \mbh-\smass\ is considered as more fundamental which would be more efficient to understand their co-evolution.
+
+\section{C. The \mbh-\smass\ comparison sample}\label{sec:comp_sample_value}
+We use the self-consistent recipes to re-calibrate our comparison sample. We list the values of all the comparison \mbh-\smass\ sample in the Table~\ref{tab:comp_sample}.
 
@@
 CID1174 & 1906 & 43.43 & 7.99 & -0.47 & 5898 & 44.76 & 8.83& -1.34 \\
-CID1281 & 1619 & 43.24 & 7.75 & -0.41 & ... & ... & ... & ... \\
-CID206 & 3334 & 43.48 & 8.53 & -0.97 & ... & ... & ...& ... \\
-CID216 & 2230 & 42.85 & 7.85 & -0.90 & ... & ... & ...& ... \\
-CID237 & 2112 & 43.86 & 8.29 & -0.36 & ... & ... & ...& ... \\
+CID1281 & 1619 & 43.24 & 7.75 & -0.41 & \nodata & \nodata & \nodata & \nodata \\
+CID206 & 3334 & 43.48 & 8.53 & -0.97 & \nodata & \nodata & \nodata& \nodata \\
+CID216 & 2230 & 42.85 & 7.85 & -0.90 & \nodata & \nodata & \nodata& \nodata \\
+CID237 & 2112 & 43.86 & 8.29 & -0.36 & \nodata & \nodata & \nodata& \nodata \\
 CID255 & 1932 & 43.99 & 8.27 & -0.22 & 3709 & 45.37 & 8.73& -0.60 \\
 CID3242 & 2543 & 43.83 & 8.45 & -0.55 & 3775 & 45.10 & 8.61& -0.75 \\
-CID3570 & 1959 & 43.16 & 7.89 & -0.63 & ... & ... & ...& ... \\
+CID3570 & 1959 & 43.16 & 7.89 & -0.63 & \nodata & \nodata & \nodata& \nodata \\
 CID452 & 3458 & 42.92 & 8.30 & -1.26 & 3127 & 44.63 & 8.22& -0.88 \\
-CID454 & 2824 & 43.34 & 8.31 & -0.88 & ... & ... & ...& ... \\
+CID454 & 2824 & 43.34 & 8.31 & -0.88 & \nodata & \nodata & \nodata& \nodata \\
 CID50 & 2340 & 43.94 & 8.42 & -0.42 & 1939 & 45.33 & 8.15& -0.06 \\
-CID543 & 2189 & 43.57 & 8.19 & -0.53 & ... & ... & ...& ... \\
-CID597 & 1656 & 43.33 & 7.81 & -0.39 & ... & ... & ...& ... \\
+CID543 & 2189 & 43.57 & 8.19 & -0.53 & \nodata & \nodata & \nodata& \nodata \\
+CID597 & 1656 & 43.33 & 7.81 & -0.39 & \nodata & \nodata & \nodata& \nodata \\
 CID607 & 3009 & 43.67 & 8.53 & -0.78 & 4242 & 44.78 & 8.56& -1.04 \\
 CID70 & 2480 & 43.51 & 8.27 & -0.68 & 3982 & 45.16 & 8.69& -0.77 \\
-LID1273 & 3224 & 43.61 & 8.56 & -0.87 & ... & ... & ...& ... \\
-LID1538 & 2941 & 43.60 & 8.47 & -0.79 & ... & ... & ...& ... \\
+LID1273 & 3224 & 43.61 & 8.56 & -0.87 & \nodata & \nodata & \nodata& \nodata \\
+LID1538 & 2941 & 43.60 & 8.47 & -0.79 & \nodata & \nodata & \nodata& \nodata \\
 LID360 & 2482 & 43.88 & 8.45 & -0.50 & 2869 & 45.09 & 8.37& -0.52 \\
 XID2138 & 3186 & 43.61 & 8.55 & -0.86 & 2945 & 44.81 & 8.25& -0.71 \\
-XID2202 & 2973 & 43.56 & 8.46 & -0.82 & ... & ... & ...& ... \\
+XID2202 & 2973 & 43.56 & 8.46 & -0.82 & \nodata & \nodata & \nodata& \nodata \\
 XID2396 & 2271 & 44.06 & 8.46 & -0.33 & 2658 & 45.50 & 8.51& -0.24 \\
-CDFS-1 & 2000 & 43.02 & 7.83 & -0.03 & ... & ... & ...& ... \\
-CDFS-229 & 2190 & 43.60 & 8.20 & -0.60 & ... & ... & ...& ... \\
-CDFS-321 & 2442 & 43.93 & 8.46 & -0.46 & ... & ... & ...& ... \\
-CDFS-724 & 2541 & 42.95 & 8.03 & -1.15 & ... & ... & ...& ... \\
-ECDFS-358 & 2237 & 43.40 & 8.12 & -0.64 & ... & ... & ...& ... \\
+CDFS-1 & 2000 & 43.02 & 7.83 & -0.03 & \nodata & \nodata & \nodata& \nodata \\
+CDFS-229 & 2190 & 43.60 & 8.20 & -0.60 & \nodata & \nodata & \nodata& \nodata \\
+CDFS-321 & 2442 & 43.93 & 8.46 & -0.46 & \nodata & \nodata & \nodata& \nodata \\
+CDFS-724 & 2541 & 42.95 & 8.03 & -1.15 & \nodata & \nodata & \nodata& \nodata \\
+ECDFS-358 & 2237 & 43.40 & 8.12 & -0.64 & \nodata & \nodata & \nodata& \nodata \\
 SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.81 & 6761 & 44.71 & 8.93& -1.49 \\
-SXDS-X50 & 1817 & 43.42 & 7.94 & -0.43 & ... & ... & ...& ... \\
-SXDS-X717 & 2931 & 43.05 & 8.20 & -1.05 & ... & ... & ...& ... \\
+SXDS-X50 & 1817 & 43.42 & 7.94 & -0.43 & \nodata & \nodata & \nodata& \nodata \\
+SXDS-X717 & 2931 & 43.05 & 8.20 & -1.05 & \nodata & \nodata & \nodata& \nodata \\
 SXDS-X735 & 2702 & 43.70 & 8.44 & -0.67 & 3520 & 45.07 & 8.54& -0.70 \\
@@
 XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.07\substack{+0.26\\-0.16}$ &$10.69\substack{+0.28\\-0.19}$ & $10.00\substack{+0.58\\-0.40}$ \\[3pt]
-CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ...
-& ...
-& ...
-& $10.66\substack{+0.16\\-0.12}$ &$10.29\substack{+0.19\\-0.15}$ & $10.14\substack{+0.22\\-0.31}$ \\[3pt]
-CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ...
-& ...
-& ...
-& $10.90\substack{+0.06\\-0.05}$ &$10.63\substack{+0.12\\-0.11}$ & $9.71\substack{+0.70\\-0.16}$ \\[3pt]
-CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ...
-& ...
-& ...
-& $11.48\substack{+0.28\\-0.17}$ &$11.10\substack{+0.30\\-0.20}$ & $10.72\substack{+0.42\\-0.58}$ \\[3pt]
-CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ...
-& ...
-& ...
-& $10.06\substack{+0.23\\-0.15}$ &$9.79\substack{+0.25\\-0.18}$ & $9.25\substack{+0.48\\-0.48}$ \\[3pt]
-ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ...
-& ...
-& ...
-& $11.11\substack{+0.12\\-0.10}$ &$10.73\substack{+0.16\\-0.14}$ & $10.22\substack{+0.44\\-0.47}$ \\[3pt]
-SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ...
-& ...
-& ...
-& $10.75\substack{+0.09\\-0.08}$ &$10.49\substack{+0.14\\-0.13}$ & $10.10\substack{+0.36\\-0.48}$ \\[3pt]
-SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ...
-& ...
-& ...
-& $10.80\substack{+0.11\\-0.09}$ &$10.54\substack{+0.15\\-0.13}$ & $10.01\substack{+0.45\\-0.46}$ \\[3pt]
-SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ...
-& ...
-& ...
-& $10.77\substack{+0.07\\-0.06}$ &$10.51\substack{+0.12\\-0.12}$ & $10.38\substack{+0.18\\-0.29}$ \\[3pt]
-SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ...
-& ...
-& ...
-& $11.16\substack{+0.13\\-0.10}$ &$10.78\substack{+0.17\\-0.14}$ & $10.42\substack{+0.36\\-0.56}$ \\[3pt]
-SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ...
-& ...
-& ...
-& $9.95\substack{+0.47\\-0.22}$ &$9.68\substack{+0.48\\-0.24}$ & $9.35\substack{+0.48\\-0.56}$ \\[3pt]
-SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ...
-& ...
-& ...
-& $10.99\substack{+0.21\\-0.14}$ &$10.61\substack{+0.23\\-0.17}$ & $10.21\substack{+0.40\\-0.54}$ \\[3pt]
+CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & \nodata & \nodata & \nodata & $10.66\substack{+0.16\\-0.12}$ &$10.29\substack{+0.19\\-0.15}$ & $10.14\substack{+0.22\\-0.31}$ \\[3pt]
+CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & \nodata & \nodata & \nodata & $10.90\substack{+0.06\\-0.05}$ &$10.63\substack{+0.12\\-0.11}$ & $9.71\substack{+0.70\\-0.16}$ \\[3pt]
+CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & \nodata & \nodata & \nodata & $11.48\substack{+0.28\\-0.17}$ &$11.10\substack{+0.30\\-0.20}$ & $10.72\substack{+0.42\\-0.58}$ \\[3pt]
+CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & \nodata & \nodata & \nodata & $10.06\substack{+0.23\\-0.15}$ &$9.79\substack{+0.25\\-0.18}$ & $9.25\substack{+0.48\\-0.48}$ \\[3pt]
+ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & \nodata & \nodata & \nodata & $11.11\substack{+0.12\\-0.10}$ &$10.73\substack{+0.16\\-0.14}$ & $10.22\substack{+0.44\\-0.47}$ \\[3pt]
+SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & \nodata & \nodata & \nodata & $10.75\substack{+0.09\\-0.08}$ &$10.49\substack{+0.14\\-0.13}$ & $10.10\substack{+0.36\\-0.48}$ \\[3pt]
+SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & \nodata & \nodata & \nodata & $10.80\substack{+0.11\\-0.09}$ &$10.54\substack{+0.15\\-0.13}$ & $10.01\substack{+0.45\\-0.46}$ \\[3pt]
+SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & \nodata & \nodata & \nodata & $10.77\substack{+0.07\\-0.06}$ &$10.51\substack{+0.12\\-0.12}$ & $10.38\substack{+0.18\\-0.29}$ \\[3pt]
+SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & \nodata & \nodata & \nodata & $11.16\substack{+0.13\\-0.10}$ &$10.78\substack{+0.17\\-0.14}$ & $10.42\substack{+0.36\\-0.56}$ \\[3pt]
+SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & \nodata & \nodata & \nodata & $9.95\substack{+0.47\\-0.22}$ &$9.68\substack{+0.48\\-0.24}$ & $9.35\substack{+0.48\\-0.56}$ \\[3pt]
+SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & \nodata & \nodata & \nodata & $10.99\substack{+0.21\\-0.14}$ &$10.61\substack{+0.23\\-0.17}$ & $10.21\substack{+0.40\\-0.54}$ \\[3pt]
 \enddata
@@
 32 AGNs + intermediate& \ding{TBD: Yes} & 0.80$\pm$0.40 & 0.50 $\pm$ 0.50 \\
-32 AGNs & No & 1.01$\pm$0.26 & 1.07$\pm$0.23\\
+32 AGNs & No & 1.03$\pm$0.25 & 1.07$\pm$0.23\\
 32 AGNs& \ding{TBD: Yes} & 1.20$\pm$0.80 & 1.60$\pm$0.80 \\
@@
      \hline\hline
-32 AGNs & 1.01$\pm$0.26\\    
+32 AGNs & 1.03$\pm$0.25\\    
 30 AGNs (excluded outliers) & 0.89$\pm$0.27\\    
@@
 
+\begin{table}
+\centering
+\caption{The summary for the comparison sample}\label{tab:comp_sample}
+\resizebox{18cm}{!}{
+\begin{minipage}{0.5\textwidth}
+\begin{tabular}{l c  p{2cm}c   c  }
+\hline\hline
+Object ID$^a$ & $z$ & $\log$\smass\ & $\log$\mbh \\
+&&$(M_{\odot}$)&$(M_{\odot}$)\\ \\
+\hline\hline
+\multicolumn{2}{l}{Local sample by \citet{H+R04}}\\
+\hline 
+M87 & 0.0037$^b$ & 11.78$^c$$\pm$0.18 & 9.48$\pm$0.2 \\
+NGC1068 & 0.0035 & 10.36$\pm$0.18 & 7.15$\pm$0.1 \\
+NGC3379 & 0.0025 & 10.83$\pm$0.18 & 8.00$\pm$0.1 \\
+NGC4374 & 0.0043 & 11.56$\pm$0.18 & 8.63$\pm$0.2 \\
+NGC4261 & 0.0073 & 11.56$\pm$0.18 & 8.72$\pm$0.3 \\
+NGC6251 & 0.0243 & 11.75$\pm$0.18 & 8.72$\pm$0.3 \\
+NGC7052 & 0.0136 & 11.46$\pm$0.18 & 8.52$\pm$0.2 \\
+NGC4742 & 0.0036 & 9.79$\pm$0.18 & 7.15$\pm$0.2 \\
+NGC821 & 0.0056 & 11.11$\pm$0.18 & 7.57$\pm$0.2 \\
+IC1459 & 0.0068 & 11.46$\pm$0.18 & 9.40$\pm$0.4 \\
+M31 & 0.0002 & 10.57$\pm$0.18 & 7.65$\pm$0.2 \\
+M32 & 0.0002 & 8.90$\pm$0.18 & 6.40$\pm$0.3 \\
+NGC1023 & 0.0027 & 10.84$\pm$0.18 & 7.64$\pm$0.5 \\
+NGC2778 & 0.0053 & 10.88$\pm$0.18 & 7.15$\pm$0.2 \\
+NGC3115 & 0.0023 & 11.08$\pm$0.18 & 9.00$\pm$0.2 \\
+NGC3245 & 0.0049 & 10.83$\pm$0.18 & 8.32$\pm$0.3 \\
+NGC3377 & 0.0026 & 10.20$\pm$0.18 & 8.00$\pm$0.6 \\
+NGC3384 & 0.0027 & 10.30$\pm$0.18 & 7.20$\pm$0.4 \\
+NGC3608 & 0.0053 & 10.99$\pm$0.18 & 8.28$\pm$0.3 \\
+NGC4291 & 0.0061 & 11.11$\pm$0.18 & 8.49$\pm$0.2 \\
+NGC4342 & 0.0036 & 10.08$\pm$0.18 & 8.48$\pm$0.2 \\
+NGC4473 & 0.0037 & 10.96$\pm$0.18 & 8.04$\pm$0.6 \\
+NGC4564 & 0.0035 & 10.64$\pm$0.18 & 7.75$\pm$0.4 \\
+NGC4594 & 0.0023 & 11.43$\pm$0.18 & 9.00$\pm$0.3 \\
+NGC4649 & 0.0039 & 11.69$\pm$0.18 & 9.30$\pm$0.0 \\
+NGC4697 & 0.0027 & 11.04$\pm$0.18 & 8.23$\pm$0.6 \\
+NGC5845 & 0.0060 & 10.57$\pm$0.18 & 8.38$\pm$0.1 \\
+NGC7332 & 0.0053 & 10.18$\pm$0.18 & 7.11$\pm$0.2 \\
+NGC7457 & 0.0031 & 9.85$\pm$0.18 & 6.54$\pm$0.1 \\
+Milky Way & 0.0000 & 10.04$\pm$0.18 & 6.57$\pm$0.2 \\
+\hline\hline
+\multicolumn{2}{l}{Local sample by \citet{Bennert++2011}}\\
+\hline
+0121$-$0102 & 0.0540 & 10.12$\pm$0.24 & 7.44$\pm$0.4 \\
+0206$-$0017 & 0.0430 & 10.95$\pm$0.23 & 8.01$\pm$0.4 \\
+0353$-$0623 & 0.0760 & 10.33$\pm$0.22 & 7.44$\pm$0.4 \\
+0802$+$3104 & 0.0410 & 10.38$\pm$0.23 & 7.17$\pm$0.4 \\
+0846$+$2522 & 0.0510 & 10.50$\pm$0.23 & 8.52$\pm$0.4 \\
+1042$+$0414 & 0.0524 & 10.32$\pm$0.23 & 6.98$\pm$0.4 \\
+1043$+$1105 & 0.0475 & 9.83$\pm$0.24 & 7.67$\pm$0.4 \\
+1049$+$2451 & 0.0550 & 10.41$\pm$0.23 & 7.84$\pm$0.4 \\
+1101$+$1102 & 0.0355 & 10.33$\pm$0.22 & 7.77$\pm$0.4 \\
+1116$+$4123 & 0.0210 & 10.20$\pm$0.22 & 7.37$\pm$0.4 \\
+1144$+$3653 & 0.0380 & 10.26$\pm$0.22 & 7.36$\pm$0.4 \\
+1210$+$3820 & 0.0229 & 9.94$\pm$0.24 & 7.50$\pm$0.4 \\
+1250$-$0249 & 0.0470 & 10.14$\pm$0.22 & 7.65$\pm$0.4 \\
+1323$+$2701 & 0.0559 & 9.65$\pm$0.22 & 6.98$\pm$0.4 \\
+1355$+$3834 & 0.0501 & 10.11$\pm$0.23 & 7.96$\pm$0.4 \\
+1405$-$0259 & 0.0541 & 10.04$\pm$0.23 & 7.08$\pm$0.4 \\
+1419$+$0754 & 0.0558 & 10.73$\pm$0.21 & 7.51$\pm$0.4 \\
+1434$+$4839 & 0.0365 & 10.30$\pm$0.24 & 7.48$\pm$0.4 \\
+1535$+$5754 & 0.0304 & 10.24$\pm$0.24 & 7.83$\pm$0.4 \\
+1545$+$1709 & 0.0481 & 9.92$\pm$0.22 & 7.28$\pm$0.4 \\
+1554$+$3238 & 0.0483 & 10.00$\pm$0.23 & 7.63$\pm$0.4 \\
+1557$+$0830 & 0.0465 & 9.82$\pm$0.23 & 7.55$\pm$0.4 \\
+1605$+$3305 & 0.0532 & 9.95$\pm$0.23 & 7.78$\pm$0.4 \\
+1606$+$3324 & 0.0585 & 10.33$\pm$0.22 & 7.22$\pm$0.4 \\
+1611$+$5211 & 0.0409 & 10.33$\pm$0.22 & 7.34$\pm$0.4 \\
+\hline\hline
+ \\\\ \\\\ \\
+
+\end{tabular}
+\end{minipage} \hfill
+
+\begin{minipage}{0.6\textwidth}
+\begin{tabular}{l c p{3cm}c c  }
+\hline\hline
+Object ID & $z$ & $\log$\smass\ & $\log$\mbh \\
+&&$(M_{\odot}$)&$(M_{\odot}$)\\ \\
+\hline\hline
+\multicolumn{3}{l}{Intermediate sample by \citet{Bennert11}}\\
+\hline
+J033252$-$275119 & 1.227 & 10.58(9.83)$^d$$\pm$0.2 & 8.87$\pm$0.4 \\
+J033243$-$274914 & 1.900 & 10.64(10.64)$\pm$0.2 & 9.17$\pm$0.4 \\
+J033239$-$274601 & 1.220 & 10.54(10.54)$\pm$0.2 & 8.24$\pm$0.4 \\
+J033226$-$274035 & 1.031 & 10.78(9.53)$\pm$0.2 & 7.85$\pm$0.4 \\
+J033225$-$274218 & 1.617 & 10.61(10.61)$\pm$0.2 & 8.08$\pm$0.4 \\
+J033210$-$274414 & 1.615 & 10.45(10.45)$\pm$0.2 & 8.30$\pm$0.4 \\
+J033200$-$274319 & 1.037 & 9.62(9.62)$\pm$0.2 & 7.75$\pm$0.4 \\
+J033229$-$274529 & 1.218 & 10.71(10.71)$\pm$0.2 & 8.37$\pm$0.4 \\
+J123553$+$621037 & 1.371 & 10.90(9.99)$\pm$0.2 & 8.27$\pm$0.4 \\
+J123618$+$621115 & 1.021 & 10.96(9.29)$\pm$0.2 & 8.35$\pm$0.4 \\
+J123707$+$622147 & 1.450 & 10.74(10.74)$\pm$0.2 & 8.77$\pm$0.4 \\
+\hline\hline
+\multicolumn{2}{l}{Intermediate sample by \citet{SS13}}\\
+\hline
+158 & 0.717 & 10.66(10.66)$\pm$0.2 & 6.94$\pm$0.4 \\
+170 & 1.065 & 9.80(9.50)$\pm$0.2 & 6.84$\pm$0.4 \\
+271 & 0.960 & 10.49(9.85)$\pm$0.2 & 7.12$\pm$0.4 \\
+273 & 0.970 & 10.29(10.29)$\pm$0.2 & 7.99$\pm$0.4 \\
+305 & 0.544 & 11.01(11.01)$\pm$0.2 & 8.38$\pm$0.4 \\
+333 & 1.044 & 10.33(9.87)$\pm$0.2 & 7.66$\pm$0.4 \\
+339 & 0.675 & 10.96(10.96)$\pm$0.2 & 7.60$\pm$0.4 \\
+348 & 0.569 & 10.55(10.15)$\pm$0.2 & 7.64$\pm$0.4 \\
+379 & 0.737 & 10.66(10.17)$\pm$0.2 & 8.90$\pm$0.4 \\
+413 & 0.664 & 10.19(9.80)$\pm$0.2 & 6.81$\pm$0.4 \\
+417 & 0.837 & 10.39(9.91)$\pm$0.2 & 8.11$\pm$0.4 \\
+465 & 0.740 & 10.76(10.14)$\pm$0.2 & 7.78$\pm$0.4 \\
+516 & 0.733 & 10.88(10.71)$\pm$0.2 & 7.66$\pm$0.4 \\
+540 & 0.622 & 10.88(10.57)$\pm$0.2 & 7.38$\pm$0.4 \\
+597 & 1.034 & 10.91(10.80)$\pm$0.2 & 7.87$\pm$0.4 \\
+712 & 0.841 & 11.34(11.19)$\pm$0.2 & 8.41$\pm$0.4 \\
+\hline\hline
+\multicolumn{2}{l}{Intermediate sample by \citet{Cisternas2011}}\\
+\hline
+J095817.54$+$021938.5 & 0.73 & 10.30$\pm$0.2 & 7.72$\pm$0.4 \\
+J095819.88$+$022903.6 & 0.34 & 11.23$\pm$0.2 & 8.29$\pm$0.4 \\
+J095831.65$+$024901.6 & 0.34 & 10.65$\pm$0.2 & 8.08$\pm$0.4 \\
+J095840.61$+$020426.6 & 0.34 & 11.02$\pm$0.2 & 8.39$\pm$0.4 \\
+J095845.80$+$024634.0 & 0.35 & 10.54$\pm$0.2 & 7.39$\pm$0.4 \\
+J095902.76$+$021906.5 & 0.34 & 11.14$\pm$0.2 & 8.66$\pm$0.4 \\
+J095909.53$+$021916.5 & 0.38 & 10.68$\pm$0.2 & 7.77$\pm$0.4 \\
+J095928.31$+$022106.9 & 0.35 & 10.95$\pm$0.2 & 7.24$\pm$0.4 \\
+J100002.21$+$021631.8 & 0.85 & 11.07$\pm$0.2 & 8.29$\pm$0.4 \\
+J100012.91$+$023522.8 & 0.70 & 11.17$\pm$0.2 & 8.15$\pm$0.4 \\
+J100014.55$+$023852.7 & 0.44 & 10.57$\pm$0.2 & 7.79$\pm$0.4 \\
+J100017.54$+$020012.6 & 0.35 & 10.47$\pm$0.2 & 7.59$\pm$0.4 \\
+J100025.25$+$015852.2 & 0.37 & 10.57$\pm$0.2 & 8.58$\pm$0.4 \\
+J100028.63$+$025112.7 & 0.77 & 10.86$\pm$0.2 & 8.49$\pm$0.4 \\
+J100029.69$+$022129.7 & 0.73 & 11.01$\pm$0.2 & 8.03$\pm$0.4 \\
+J100033.38$+$015237.2 & 0.83 & 10.81$\pm$0.2 & 8.07$\pm$0.4 \\
+J100033.49$+$013811.6 & 0.52 & 10.54$\pm$0.2 & 8.01$\pm$0.4 \\
+J100037.29$+$024950.6 & 0.73 & 10.36$\pm$0.2 & 7.41$\pm$0.4 \\
+J100043.15$+$020637.2 & 0.36 & 11.28$\pm$0.2 & 8.07$\pm$0.4 \\
+J100046.72$+$020404.5 & 0.55 & 11.08$\pm$0.2 & 7.75$\pm$0.4 \\
+J100058.71$+$022556.2 & 0.69 & 10.66$\pm$0.2 & 7.91$\pm$0.4 \\
+J100118.52$+$015543.0 & 0.53 & 10.84$\pm$0.2 & 8.22$\pm$0.4 \\
+J100141.09$+$021300.0 & 0.62 & 10.53$\pm$0.2 & 7.35$\pm$0.4 \\
+J100146.49$+$020256.7 & 0.67 & 10.75$\pm$0.2 & 7.73$\pm$0.4 \\
+J100202.22$+$024157.8 & 0.79 & 10.53$\pm$0.2 & 8.24$\pm$0.4 \\
+J100205.03$+$023731.5 & 0.52 & 11.15$\pm$0.2 & 8.38$\pm$0.4 \\
+J100212.11$+$014232.4 & 0.37 & 10.48$\pm$0.2 & 7.70$\pm$0.4 \\
+J100218.32$+$021053.1 & 0.55 & 11.20$\pm$0.2 & 8.61$\pm$0.4 \\
+J100230.06$+$014810.4 & 0.63 & 10.73$\pm$0.2 & 7.50$\pm$0.4 \\
+J100230.65$+$024427.6 & 0.82 & 10.77$\pm$0.2 & 7.82$\pm$0.4 \\
+J100232.13$+$023537.3 & 0.66 & 11.03$\pm$0.2 & 8.19$\pm$0.4 \\
+J100243.96$+$023428.6 & 0.38 & 11.08$\pm$0.2 & 8.25$\pm$0.4 \\
+\hline
+\end{tabular}
+\end{minipage}
+}
+\tablecomments{\\$^a$:  The object name is directly adopted from the reference.
+\\$^b$:  For the \citet{H+R04} sample, the redshift value is calculated from their physical Galaxy distance.
+\\$^c$:  The entire \smass\ for the local sample are the bulge masses.
+\\$^d$:  If applicable, the values in the bracket are the bulge mass.
+}
+\end{table}
+
 \end{document}

### 2019-10-07 M_BH_relation/print_table7.py

@@ -50,7 +50,7 @@ if inp_Cis ==1:
 plt.close()
 
 
-#%%Print 
+#%%Print HR
 hlocname = ['M87', 'NGC1068', 'NGC3379', 'NGC4374', 'NGC4261', 'NGC6251', 'NGC7052',
             'NGC4742', 'NGC821', 'IC1459', 'M31', 'M32', 'NGC1023', 'NGC2778', 'NGC3115',
             'NGC3245', 'NGC3377', 'NGC3384', 'NGC3608', 'NGC4291', 'NGC4342', 'NGC4473',
@@ -60,7 +60,7 @@ hlocname = ['M87', 'NGC1068', 'NGC3379', 'NGC4374', 'NGC4261', 'NGC6251', 'NGC70
 for i in range(len(hloc)):
     print hlocname[i] + " & {0:.4f} & {1:.2f}$\pm${2:.2f} & {3:.2f}$\pm${4:.1f} \\\\".format(hloc[i,0], hloc[i,1], hloc[i,2], hloc[i,3], hloc[i,4])
     
-#%%
+#%% B11 local
 blocname = ['0121$-$0102', '0206$-$0017', '0353$-$0623', '0802+3104', '0846+2522', '1042+0414',
             '1043+1105', '1049+2451', '1101+1102', '1116+4123', '1144+3653', '1210+3820',
             '1250$-$0249', '1323+2701', '1355+3834', '1405$-$0259', '1419+0754', '1434+4839',
@@ -68,17 +68,18 @@ blocname = ['0121$-$0102', '0206$-$0017', '0353$-$0623', '0802+3104', '0846+2522
 for i in range(len(bloc)):
     print blocname[i] + " & {0:.4f} & {1:.2f}$\pm${2:.2f} & {3:.2f}$\pm${4:.1f} \\\\".format(bloc[i,0], bloc[i,1], bloc[i,2], bloc[i,3], bloc[i,4])
 
-#%%
-
+#%% B11 
 b11name = ['J033252$-$275119', 'J033243$-$274914', 'J033239$-$274601', 'J033226$-$274035', 'J033225$-$274218', 'J033210$-$274414',
            'J033200$-$274319', 'J033229$-$274529', 'J123553$+$621037', 'J123618$+$621115', 'J123707$+$622147']
 for i in range(len(b11)):
[…]

### 2019-10-07 manuscript/manuscript.tex
Update while writing the "reply to the referee"

@@
 It is from this catalog that we primarily select our targets.
-{\bf The continuum fitting and emission-line modeling are also provided by this work through a common procedure for spectral model fits.
+{\bf The continuum fitting and emission-line modeling provided by this work are preformed through a common procedure for spectral model fits.
 This approach first correct the spectra for galactic extinction and shift to the rest-frame.
@@
 The sample by B10 consists of 19 AGN with the \mbh-\lhost\ relation determined with reliable \mbh\ masses using reverberation mapping with an uncertainty level $\sim0.15$ dex.
-The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
+{\bf Note that the B10 only provide the galaxy single V-band luminosity.
+In \citet{Ding2017b}, the galaxy R-band luminosity are derived based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
 To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04).
@@
 We select samples that were analyzed by members of our team to ensure uniform measurements.
-The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$.
-{\bf The stellar mass of these 27 object have been estimated using multi-band imaging data, and we adopt them to compare the \mbh-\smass\ relation.}
+The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using single-band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$ {\bf Same as B10's sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-correction from V-band based on the sample stellar template.
+Moreover, \citet{Bennert11} and \citet{SS13} estimate the stellar masses of their 27 objects using multi-band imaging data, and we adopt them as the \mbh-\smass\ comparison sample.}
  In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample.
@@
 
-{\bf The value for the all the \mbh-\lhost\ comparison sample are listed in \citet{Ding2017b} (in Table~1 and Table~2).
+{\bf The values for the all the \mbh-\lhost\ comparison sample are listed in \citet{Ding2017b} (in Table~1 and Table~2).
 The \mbh-\smass\ comparison sample are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.}
@@
 {\bf Having obtained the \hst\ image, we remove the background light which could come from both the sky and the detector.
-In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm.
+In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm, which effectively accounts for the gradient in the light distribution.
 Then, we subtract the globe sky background light to obtain the clear image.
@@
 Following common practice, we model the central AGN as a scaled point source and the host galaxy as a \sersic\ profile.
-Note that the actual morphologies of the host galaxies could be more complicated (e.g., bulge+disk).
+Note that the actual morphologies of the host galaxies could be more complicated (e.g., bulge$+$disk).
 However, the \sersic\ model is an adequate first-order approximation of the surface brightness distribution with a flexible parameterization that provides sufficient freedom to infer the total host flux even for our high redshift sample.
@@
 Thus, the choice of template is a subdominant source of error.
-{\bf Note that the large uncertainties of \mbh\ is not apparent by the figures, since we only select the AGN sample that have {\it measured} \mbh\ falls into our selection window.
-The detailed analysis on this effect is beyond the scope.
-In our forthcoming paper, we focus on the sample scatter.} A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.
+{\bf Note that the large uncertainties of \mbh\ is not apparent by the figures, since only the AGN sample that has {\it measured} \mbh\ falls into our selection window (i.e., $\log($\mbh$/M_{\odot})\in[7.5, 8.56]$) would be selected.} A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.
 
@@
 We note that the different local samples have inconsistencies, which could affect our measurement of the co-evolution.
-{\bf In this paper, we aim to make the differential measurement as function of redshift.
+{\bf We also note the limitations of the local sample we current adopted.
+For instance, the morphological features like strong bars in B10 were not considered in the decomposition, which might affect the inference of the bulge/disk properties.
+Also, the HR04 sample does not use color information to estimate the \smass of their sample, rather than use Jeans modeling.
+These issues have been addressed in the discussions in~\citet{Kormendy13} in detail.
+Even so, we adopt the B10 and HR04 as our comparison local sample given the following reasons.
+In this study, we aim to make the differential measurement as function of redshift.
 With this goal in mind, the consistency between the local and distant sample is crucial in terms of measurement procedure.
@@
 
-For the local by \citet{Bentz2018}, with different goal in mind, they decompose their host using more components than bulge$+$disk (e.g., Bar(s), Barlens, Ring(s)).
+For the local sample by \citet{Bentz2018}, with different goal in mind, they decompose their host using more components than bulge$+$disk (e.g., Bar(s), Barlens, Ring(s)).
 This is beyond the comparison medium, i.e., bulge v.s.
@@
 \centering
-\caption{The summary for the comparison sample}\label{tab:comp_sample}
+\caption{The summary for the comparison \mbh-\smass\ sample}\label{tab:comp_sample}
 \resizebox{18cm}{!}{

### 2019-10-07 manuscript/manuscript.tex
update before sharing to TT and JS

@@
 This value is the minimum offset expected for a non-evolving mass ratio as described in Section~\ref{sec:sf_framework}.
-{\bf Furthermore, we collect the most similar AGN sample from the local and intermediate redshift and re-calibrate their quantities based on a set of consistent recipes, which ensures our comparison results solid, see Section~\ref{sec:compare_sample}.}
+{\bf Furthermore, we collect the most similar AGN sample from the local and intermediate redshift from the literature, and re-calibrate their quantities based on a set of consistent recipes, which ensures our comparison results solid, as shown in Section~\ref{sec:compare_sample}.}
 
@@
 {\bf The continuum fitting and emission-line modeling provided by this work are preformed through a common procedure for spectral model fits.
-This approach first correct the spectra for galactic extinction and shift to the rest-frame.
+This approach first corrects the spectra for galactic extinction and shift to the rest-frame.
 The spectral regions in the near-IR were are strongly affected by OH emission, and thus they are masked while fitting.
-The spectrum are modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on the $\chi^2$ value.
+The spectrum is modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on the $\chi^2$ value.
 We refer the reader to that paper for more details.}
@@
 The sample by B10 consists of 19 AGN with the \mbh-\lhost\ relation determined with reliable \mbh\ masses using reverberation mapping with an uncertainty level $\sim0.15$ dex.
-{\bf Note that the B10 only provide the galaxy single V-band luminosity.
-In \citet{Ding2017b}, the galaxy R-band luminosity are derived based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
+{\bf Note that the B10 only provides the galaxy single V-band luminosity.
+In \citet{Ding2017b}, the galaxy R-band luminosity is derived based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
 To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04).
@@
 We select samples that were analyzed by members of our team to ensure uniform measurements.
-The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using single-band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$ {\bf Same as B10's sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-correction from V-band based on the sample stellar template.
+The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using single-band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$ {\bf Same as B10's sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-correction from V-band based on the same stellar template.
 Moreover, \citet{Bennert11} and \citet{SS13} estimate the stellar masses of their 27 objects using multi-band imaging data, and we adopt them as the \mbh-\smass\ comparison sample.}
@@
 
-{\bf The values for the all the \mbh-\lhost\ comparison sample are listed in \citet{Ding2017b} (in Table~1 and Table~2).
-The \mbh-\smass\ comparison sample are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.}
+{\bf The values for the all the \mbh-\lhost\ comparison samples are listed in \citet{Ding2017b} (Table~1 and Table~2 therein).
+The \mbh-\smass\ comparison samples are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.}
 
@@
 
-{\bf Having obtained the \hst\ image, we remove the background light which could come from both the sky and the detector.
+{\bf Having obtained the \hst\ image, we remove the background light, which could come from both the sky and the detector.
 In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm, which effectively accounts for the gradient in the light distribution.
-Then, we subtract the globe sky background light to obtain the clear image.
+Then, we subtract the globe sky background light to obtain a clear image.
 To test the fidelity of this subtraction, we investigate the surface brightness at the empty regions and make sure it is neither positive nor negative.
-Finally, we extract postage stamp of the AGN image and PSF image to carry out the modeling process, see Section~\ref{sec:psf_library} and Section~\ref{sec:analysis}.}
+Finally, we extract the postage stamp of the AGN image and PSF image to carry out the modeling process; see Section~\ref{sec:psf_library} and Section~\ref{sec:analysis}.}
 
@@
 For each AGN, we check the {\bf location on the detector for the top-ranked PSFs} and find that they are unrelated to the AGN's {\bf location in the detector.
-This is against the intuition that it is the PSFs who locates closer to the AGN that have better performance which} highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.
+This is against the intuition that it is the PSF who locates closer to the AGN that has a better performance, which} highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.
 
@@
 
-From our image decomposition, we detect the {\bf host galaxy in all cases at a distinguished level, expect one case (i.e., SXDS-X763) that has host-to-total flux ratios lower than $15\%$}.
+From our image decomposition, we detect the {\bf host galaxy in all cases at a distinguished level, except one case (i.e., SXDS-X763) that has host-to-total flux ratios lower than $15\%$}.
 \hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data$-$point source'' stamps) of Figure~\ref{fig:AGN_decomp} and in Appendix~\ref{sec:restsample} for the remaining cases.
@@
 This means the size inference of these three systems should really be considered an upper limit, rather than a measurement.
-However, the inference of their host luminosities and stellar masses are still reliable given {\bf the consistent result of our re-fitting test and} the small scatter in the host flux ($<10\%$).
+However, the inference of their host luminosities and stellar masses are still reliable given {\bf the consistency of the re-fitting results and} the small scatter in the host flux ($<10\%$).
 
@@
 For $21/32$ AGNs, we have multi-band host magnitudes that enable us to select {\bf the appropriate stellar population templates} to determine rest-frame luminosities and stellar masses for the overall sample.
-We find {\bf that the $1$~Gyr and the $0.625$~Gyr} stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} provides {\bf the excellent matches} to the observed colors of our sample {\bf at $z<1.44$ and $z>1.44$, respectively}  (see Figure~\ref{fig:compare_temp}).
+We find {\bf that the $1$~Gyr and the $0.625$~Gyr} stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} {\bf provide the excellent matches} to the observed colors of our sample {\bf at $z<1.44$ and $z>1.44$, respectively}  (see Figure~\ref{fig:compare_temp}).
 {\bf To minimize the uncertainty associated with these corrections, we adopt these two templates correspondingly to interpolate to the rest-frame R band which is very close to the observed wavelengths}.
@@
 These issues have been addressed in the discussions in~\citet{Kormendy13} in detail.
-Even so, we adopt the B10 and HR04 as our comparison local sample given the following reasons.
-In this study, we aim to make the differential measurement as function of redshift.
-With this goal in mind, the consistency between the local and distant sample is crucial in terms of measurement procedure.
+Even so, we adopt the B10 and HR04 as our comparison local sample, given the following reasons.
+In this study, we aim to make the differential measurement as a function of redshift.
+With this goal in mind, the consistency between the local and distant samples is crucial in terms of the measurement procedure.
 This consistency is related to how measurement systematics and calibrations propagate between the galaxy dynamical masses v.s.
@@
 
-For the local sample by \citet{Bentz2018}, with different goal in mind, they decompose their host using more components than bulge$+$disk (e.g., Bar(s), Barlens, Ring(s)).
+For the local sample by \citet{Bentz2018}, with a different goal in mind, they decompose their host using more components than bulge$+$disk (e.g., Bar(s), Barlens, Ring(s)).
 This is beyond the comparison medium, i.e., bulge v.s.
@@
 Moreover, with a more manageable model, our inference gets ride of the overfitting issue.
-In spite of this, when adopting the \citet{Bentz2018} as local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution.
+In spite of this, when adopting the \citet{Bentz2018} as the local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution.
  }
@@
 The multi-components feature (e.g., disk$+$bulge) did not appear in the residual map, showing the multi-components information is overwhelmed by the noise level.
-Second, we adopt the common stellar templates to derive the host luminosity and stellar mass for overall sample, which introduces some uncertainty in the inference of the host properties.
+Second, we adopt the universal stellar templates to derive the host luminosity and stellar mass for the overall sample, which introduces some uncertainty in the inference of the host properties.
 Even so, the uncertainty in the scaling relations is still dominated by the single epoch black hole mass estimates (see Section~\ref{sec:sysm_err} for detail).
-Third, for several AGN systems, their inferred host effective radius hit the lower limit, and thus the inference of their \Reff\ should be considered as upper limit.
+Third, for several AGN systems, their inferred host effective radius hit the lower limit, and thus the inference of their \Reff\ should be considered as the upper limit.
 However, the inference of their host luminosities and stellar masses are still reliable, given our re-fitting test using different lower limit boundary and the low scatter of the host flux inference (see Section~\ref{sec:result-hosts}, second paragraph).
-Last, in the literature, there are several different sample could be choose as local anchor to the high-$z$ sample, which could changes the inference of the evolution value.
+Last, in the literature, there are several different samples that could be chosen as the local anchor to the high-$z$ sample, which could change the inference of the evolution value.
 In this work, we adopted the most similar local sample to those at high-$z$.
-We discussed the different anchors in detail and test to infer the evolution different anchors; all the inference show the positive evolution  (see Section~\ref{sec:local_sys}).}
+We discussed the different anchors in detail and test to infer the evolution trend using different anchors; all the inference show the positive evolution  (see Section~\ref{sec:local_sys}).}
 

### 2019-10-11 manuscript/manuscript.tex
Before pull from Tommaso's edit

@@
 
-{\bf The authors thank the anonymous referee for helpful suggestions and comments which improved the presentation of this paper.} We fully appreciate input from Luis Ho, Renyue Cen, Hyewon Suh, Takahiro Morishita and Peter Williams.
+{\bf The authors thank the anonymous referee for helpful suggestions and comments which improved the presentation of this paper.
+We acknowledge the importance of the conference ``Particle Astrophysics and Cosmology Including Fundamental InteraCtions (PACIFIC-2013)" in preparing for this program.} We fully appreciate input from Luis Ho, Renyue Cen, Hyewon Suh, Takahiro Morishita and Peter Williams.
 XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
@@
 Column 6-9: \hbeta\ emission line BH properties. 
-The typical uncertainty level for {\bf FWHM is $15\%$, and for $\log( \rm L _{\lambda})$ is in-between $0.01\sim0.2$~dex}, respectively.
+The typical uncertainty level for {\bf FWHM is $15\%$, and for $\log( \rm L _{\lambda})$ is in the range $0.01\sim0.2$~dex}, respectively.
 The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.

### 2019-10-11 manuscript/manuscript.tex
Update based on TT's comments

@@
 Therefore, our results are in agreement, considering the uncertainties, with a scenario where SMBHs and their total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter.
-Based on an inference of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is significantly offset from the local value {\bf by a factor of $+6.8$ which} persists even after accounting for selection effects.
+Based on an inference of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is significantly offset from the local value {\bf by a factor of $\sim7$ which} persists even after accounting for selection effects.
 Taken together, these observations are consistent with a scenario in which stellar mass is subsequently transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than mass accretion onto the SMBH.
@@
 This value is the minimum offset expected for a non-evolving mass ratio as described in Section~\ref{sec:sf_framework}.
-{\bf Furthermore, we collect the most similar AGN sample from the local and intermediate redshift from the literature, and re-calibrate their quantities based on a set of consistent recipes, which ensures our comparison results solid, as shown in Section~\ref{sec:compare_sample}.}
+{\bf Furthermore, we collect from the literature comparison samples of intermediate-$z$ and local AGN, selected to have been analyzed with very similar methods to those applied in the distant sample.
+We recalibrate the relevant quantities from the literature based on a set of self-consistent recipes to ensure that our differential measurement of evolution is robust to calibration and methodological issues~\ref{sec:compare_sample}.}
 
@@
 
-\item {\bf Black holes masses all meet the criteria that \mbh/$M_{\odot}\lesssim8.7$, which is below the knee of the black hole mass function to minimize the selection biases (see Figure~\ref{fig:selection}, top panel).} %fall below the knee of the black hole mass function to minimize the selection biases.
-
-\item {\bf Eddington ratios are all above $5\%$} to further ensure homogeneity.
+\item {\bf Black holes masses \mbh/$M_{\odot}\lesssim8.7$, which is below the knee of the black hole mass function to minimize selection biases (see Figure~\ref{fig:selection}, top panel).} %fall below the knee of the black hole mass function to minimize the selection biases.
+
+\item {\bf Eddington ratios above $5\%$} to further ensure homogeneity.
 
@@
 It is from this catalog that we primarily select our targets.
-{\bf The continuum fitting and emission-line modeling provided by this work are preformed through a common procedure for spectral model fits.
-This approach first corrects the spectra for galactic extinction and shift to the rest-frame.
-The spectral regions in the near-IR were are strongly affected by OH emission, and thus they are masked while fitting.
-The spectrum is modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on the $\chi^2$ value.
+{\bf The continuum fitting and emission-line modeling provided by this work are performed through a common procedure for spectral model fits.
+This approach first corrects the spectra for galactic extinction and shifts them to the rest-frame.
+The spectral regions in the near-IR that are strongly affected by OH emission are masked.
+The spectrum is modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on $\chi^2$ minimization.
 We refer the reader to that paper for more details.}
@@
 {\bf Note that the B10 only provides the galaxy single V-band luminosity.
-In \citet{Ding2017b}, the galaxy R-band luminosity is derived based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
+\citet{Ding2017b} derive the galaxy R-band luminosity based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
 To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04).
@@
 We select samples that were analyzed by members of our team to ensure uniform measurements.
-The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using single-band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$ {\bf Same as B10's sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-correction from V-band based on the same stellar template.
+The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using single-band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$ {\bf .
+Similarly to B10's sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-correction from the V-band based on the same stellar template.
 Moreover, \citet{Bennert11} and \citet{SS13} estimate the stellar masses of their 27 objects using multi-band imaging data, and we adopt them as the \mbh-\smass\ comparison sample.}
@@
 
-{\bf The values for the all the \mbh-\lhost\ comparison samples are listed in \citet{Ding2017b} (Table~1 and Table~2 therein).
+{\bf The values for the all the \mbh-\lhost\ comparison samples are listed in the paper by \citet{Ding2017b} (Table~1 and Table~2 therein).
 The \mbh-\smass\ comparison samples are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.}
@@
 
-{\bf Having obtained the \hst\ image, we remove the background light, which could come from both the sky and the detector.
-In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm, which effectively accounts for the gradient in the light distribution.
-Then, we subtract the globe sky background light to obtain a clear image.
-To test the fidelity of this subtraction, we investigate the surface brightness at the empty regions and make sure it is neither positive nor negative.
+{\bf Having obtained the \hst\ image, we remove the background light, arising from the sky and the detector.
+In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm, which effectively accounts for gradient in the background distribution.
+Then, we subtract the derived  sky background light to obtain a clear image.
+To test the fidelity of this subtraction, we measure the surface brightness in the empty regions and verify that it is consistent with zero within the noise.
 Finally, we extract the postage stamp of the AGN image and PSF image to carry out the modeling process; see Section~\ref{sec:psf_library} and Section~\ref{sec:analysis}.}
@@
 \item AGN imaging data. \\
--- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample\footnote{\bf In this photometry process, we measure the AGN total flux in the aperture.
-By keep extending the aperture size, we note that the $1\farcs{}5$ is the limit region, beyond which the total aperture flux would not increase with the extending of aperture radius.}.
-By default, we extract an image of $61\times61$ pixels (i.e., $4''\times 4''$).
-If needed, a larger box size would be {\bf selected to sufficiently} include nearby objects.
+-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample\footnote{\bf The photometric aperture was determined as  a compromise between capture all the flux and keeping the background noise low and the computational time short.
+We found that extending the radius beyond $1\farcs5$ did not add any missing light, while it increased the noise and computational time.
+%By keep extending the aperture size, we note that the $1\farcs{}5$ is the limit region, beyond which the total aperture flux would not increase with the extending of aperture radius.
+}. By default, we extract an image of $61\times61$ pixels (i.e., $4''\times 4''$). If needed, a larger box size {\bf is selected to} include nearby objects. 
 \item Noise level map.\\
@@
 For each AGN, we check the {\bf location on the detector for the top-ranked PSFs} and find that they are unrelated to the AGN's {\bf location in the detector.
-This is against the intuition that it is the PSF who locates closer to the AGN that has a better performance, which} highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.
+This finding underscores that position on the detector is not the main factor driving the PSF shape.
+Other factors that are likely to be more significant are sub-pixel centering, intrinsic color of the star, and jitter and thermal status of the telescope during the observations.
+The complexity of the problem}
+highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.
 
@@
 
-From our image decomposition, we detect the {\bf host galaxy in all cases at a distinguished level, except one case (i.e., SXDS-X763) that has host-to-total flux ratios lower than $15\%$}.
+From our image decomposition, we detect the {\bf host galaxy in all cases at a significant level, except one case (i.e., SXDS-X763) that has host-to-total flux ratios lower than $15\%$}.
 \hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data$-$point source'' stamps) of Figure~\ref{fig:AGN_decomp} and in Appendix~\ref{sec:restsample} for the remaining cases.
@@
 As shown in Figure~\ref{fig:hist_compare} {\bf (top panel)}, the host-to-total flux ratio (total$=$host$+$nuclear) of the sample spans a wide range from $10\%$ to $90\%$ with most of the sample concentrated between $20\%$ to $50\%$ (median value $37\%$).
-Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the {\bf five sample (i.e., CID255, CID50, LID360, CDFS-229, SXDS-X763) which have host-to-total flux ratios lower than $20\%$} should be considered as marginal detections.
+Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the {\bf five systems (i.e., CID255, CID50, LID360, CDFS-229, SXDS-X763) which have host-to-total flux ratios lower than $20\%$} should be considered as marginal detections.
 
 The distributions of effective radius \Reff\ {\bf are shown in Figure~\ref{fig:hist_compare} {\bf (bottom panel)}.
-Based on the sample redshift and the cosmological model, we calculate their physical scale in kpc unit.
+Based on the redshift, we calculate the physical scale radius of each object in kpc assuming a standard cosmology.
 We plot them together with inferred \sersic\ index in Figure~\ref{fig:hist_rn}.} These values are distributed within the allowed range and not concentrated on either the upper or lower bound.
@@
 Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
-{\bf Seven systems have low effective radius \Reff$<0\farcs18$ that is within 3 pixels; we re-fit them with a \Reff\ $\in[0\farcs{}2,1\farcs{0}]$ prior and find that the inferred host flux barely changes ($<1\%$).
+{\bf Seven systems have effective radius \Reff$<0\farcs18$, i.e., smaller than 3 pixels.
+In order to check whether this affects our conclusions,  we re-fit them with a \Reff\ $\in[0\farcs{}2,1\farcs{0}]$ prior and find that the inferred host flux barely changes ($<1\%$).
 In particular, the}
@@
 {\bf {\it Left}: The observed color as a function of redshift, based on $21/32$ AGNs which have both WFC3 and ACS imaging data.
-Note that the filter WFC3/F125W and WFC3/F140W are adopted for sample at $z<1.44$ and $z>1.44$, respectively.
+Note that the filter  combinations WFC3/F125W and WFC3/F140W are adopted for galaxies at $z<1.44$ and $z>1.44$, respectively.
 We also plot three predicted models including $5$~Gyr, $1$~Gyr and $0.625$~Gyr.
-Clearly, the $5$~Gyr stellar population is ruled out by our data, and we adopt the $1$~Gyr and $0.625$~Gyr for sample at $z<1.44$ and $z>1.44$, respectively.
+Clearly, the $5$~Gyr stellar population is ruled out by our data, and we adopt the $1$~Gyr and $0.625$~Gyr for galaxies at $z<1.44$ and $z>1.44$, respectively.
  {\it Right}: Comparison of the inferred rest-frame R band magnitude, based on the adopted stellar populations.
@@
 The black line and the blue colored equation indicates the best-fit result of the local sample as given in Equation~\ref{eq:MLlocal}, with $1\sigma$ confidence interval indicated by the gray region.
-{\bf The values for the comparison sample, including the local and the intermediate, are listed in \citet{Ding2017b}, Table 1 and 2.}
+{\bf The values for the comparison samples at low and intermediate redshift are listed in \citet{Ding2017b}, Table 1 and 2.}
 }
@@
 In both panels, we use blue open circles to show the expected bias of the median value for $\Delta \log$\mbh.
-We use framework of \citet{Schulze2011,Schulze2014} to show that even with no evolution selection effects would shift the expectation higher towards the measured values as indicated by the small arrow (Section~\ref{sec:sf_framework}.) {\bf The local sample and intermediate sample are re-calibrated using self-consistent recipe and listed in Table~\ref{tab:comp_sample}.}}
+We use framework of \citet{Schulze2011,Schulze2014} to show that even with no evolution selection effects would shift the expectation higher towards the measured values as indicated by the small arrow (Section~\ref{sec:sf_framework}.) {\bf The measurements of the local and intermediate redshift samples are re-calibrated using self-consistent recipes and listed in Table~\ref{tab:comp_sample}.}}
 \end{figure*}
@@
 Note that the {\it observed} high-$z$ sample has effects from both the measurement uncertainty and the narrow selection window, and thus one needs to take them both into account to extract the intrinsic scatter.
-We adopt the forward simulation process and find that when a simulated AGN sample has intrinsic scatter as $0.25$~dex,  the observed data (after considering the measurement uncertainty and the selection effect) would have the observational scatter at our level.
-We will give more descriptions in our forthcoming paper (Ding et al.
-in prep.), where we focus on the scatter of the sample}.
+Based on our forward modeling framework, we find that our AGN sample has intrinsic scatter as $0.25$~dex on the vertical axis, taking into account the measurement uncertainty and the selection function.
+We will return to this topic in a forthcoming paper (Ding et al.
+in prep.), where we focus on the scatter of the sample, as a diagnostic of AGN-host galaxy feedback mechanism}.
 The fact that the intrinsic scatter for the high-$z$ sample is no larger than the local one{\bf, which is $\sim0.35$~dex \citep{Gul++09},} may pose a challenge for explanations of scaling relations where random mergers are the origin of the correlation \citep{Peng2007,Jahnke2011}, indicating that there may likely be a connection between the SMBHs and their host galaxies during their formation.
@@
 The mean offset of the sample of 32 objects from the local {\bf relationship is $0.42\pm0.06$ dex, which would correspond to $\gamma=1.06\pm0.15$}.
-However, after correcting for the selection bias ($0.21$~dex, see Section~\ref{sec:sf_framework}), {\bf the offset reduces to $0.20\pm0.06$ and thus $\gamma=0.50\pm0.15$, }mildly positive but not significantly so, and consistent with the a posteriori method within the error bars and the uncertainty in the correction.
-We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
+However, after correcting for the selection bias ($0.21$~dex, see Section~\ref{sec:sf_framework}), {\bf the offset reduces to $0.20\pm0.06$ and thus $\gamma=0.50\pm0.15$, marginally positive, but not conclusively inconsistent with the local value given the error bars and uncertainty in the correction.} We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
 Whereas we expect the negative tail to be suppressed by our selection function, and thus it should be accounted for in our treatment.
@@
 our framework, we can apply our prior estimate of the correction for selection effects by removing $0.21$~dex, leaving still a {\bf significant offset
-of $0.67$~dex.} We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
+of $0.67\pm0.07$~dex.} We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
 the Monte Carlo approach in Figure~\ref{fig:gamma_hist} and illustrate the offset between bulge and BH
@@
 \caption{\label{fig:gamma_hist} 
-Illustration of the distribution from the $10,000$ time realization.
+Illustration of the distribution from the $10,000$ time realizations.
 {\it Left}: \mbh/\smass\ distribution for 32 high-$z$ sample, compared to the local one.
@@
 In principle, if we had more information on the color, we could improve on this source of uncertainty by adopting a specific stellar population model for each target.
-However, considering that the host magnitude in the \hst/ACS band is faint (host-to-total flux ratio $< 30\%$), the individual color that we measure is insufficient to further discriminate between templates, and thus we adopt {\bf the comment templates} for simplicity and to facilitate reproduction of our work.
-
-In any case, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates, and not by uncertainties in the photometry or stellar mass estimates.
+However, considering that the host magnitude in the \hst/ACS band is faint (host-to-total flux ratio $< 30\%$), the individual color that we measure is insufficient to further discriminate between templates, and thus we adopt {\bf the common templates} for simplicity and to facilitate reproduction of our work.
+
+In any case, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates {\bf (i.e., $0.4$~dex)}, and not by uncertainties in the photometry or stellar mass estimates {\bf (i.e., typically $\sim0.15$~dex)}.
 Thus, the choice of template is a subdominant source of error.
-{\bf Note that the large uncertainties of \mbh\ is not apparent by the figures, since only the AGN sample that has {\it measured} \mbh\ falls into our selection window (i.e., $\log($\mbh$/M_{\odot})\in[7.5, 8.56]$) would be selected.} A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.
+{\bf Note that the large uncertainties of \mbh\ is not immediately apparent from the figures, since only the AGNs that have {\it measured} \mbh\ that fall into our selection window (i.e., $\log($\mbh$/M_{\odot})\in[7.5, 8.56]$) have been selected.} A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.
 
@@
 In the {\bf literature~\citep{Kormendy13, Bentz2018}}, other analyses of the local sample are available, which could also be considered as the local anchor.
-We note that the different local samples have inconsistencies, which could affect our measurement of the co-evolution.
-{\bf We also note the limitations of the local sample we current adopted.
-For instance, the morphological features like strong bars in B10 were not considered in the decomposition, which might affect the inference of the bulge/disk properties.
+{\bf However, from the point of view of our differential evolutionary measurement, we stress once again the importance of selecting local anchors that have been measured and calibrated in the most similar way to the distant high-$z$ samples.
+It is crucial that the black hole masses be obtained in the same of self-consistent manner, and it is also critical that the host/AGN decomposition be measured in the most similar way possible.
+
+Therefore, for these reason, the B10 and HR04 samples are the most appropriate for our goal, in spite of their limitations.
+For instance, B10 did not consider morphological features like strong bars in the decomposition.
+This choice might affect the inference of the bulge/disk properties in absolute terms, but it is the most similar decomposition to what is possible at high-$z$ where these features cannot be resolved.
 Also, the HR04 sample does not use color information to estimate the \smass of their sample, rather than use Jeans modeling.
-These issues have been addressed in the discussions in~\citet{Kormendy13} in detail.
-Even so, we adopt the B10 and HR04 as our comparison local sample, given the following reasons.
-In this study, we aim to make the differential measurement as a function of redshift.
-With this goal in mind, the consistency between the local and distant samples is crucial in terms of the measurement procedure.
-This consistency is related to how measurement systematics and calibrations propagate between the galaxy dynamical masses v.s.
-galaxy stellar masses, bulge v.s.
-total and \mbh\ by single epoch v.s.
-reverberation v.s.
-dynamical.
-
-For example, since} the local correlations are used to calibrate the single epoch black hole mass estimates, one needs to be self-consistent in the choice of local anchors and calibration of black hole mass estimators.
-Unfortunately, this is a thorny issue, since not all the local correlations are mutually consistent, especially when considering different galaxy properties like luminosity, stellar mass, and velocity dispersion.{\bf To illustrate} the problem, we compare our local \mbh-\smass\ sample to that published in \citet{Kormendy13} (hereafter K13).
-We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset relative to our local sample.
-Note that a $+0.3$~dex difference could totally erase the $\Delta\log$\mbh\ for the high redshift sample as described in the last section, if it were independent of the black hole mass calibration.
+This gives rise to systematic uncertainties related to the choice of the initial mass function for example, which need to be kept in mind.
+\citep[See][for more discussion of systematic issues in local samples]{Kormendy13}.
+
+The issue of consistent calibration of black hole masses is perhaps the most subtle and thorny.
+Not all the local correlations are mutually consistent, especially when considering different galaxy properties like luminosity, stellar mass, and velocity dispersion, and therefore a single self-consistent calibration is not possible.
+To illustrate} the problem, we compare our local \mbh-\smass\ sample to that published {\bf by} \citet{Kormendy13} (hereafter K13).
+We find that the \mbh-\smass\ measurements by K13 have a global $\sim+0.3$~dex offset relative to our local sample.
+Note that a $+0.3$~dex difference would almost erase the $\Delta\log$\mbh\ for the high redshift sample as described in the last section, if it were independent of the black hole mass calibration.
 {\bf However,} the \mbh-\sigstar\ relations by K13 are also offset by  $\sim+0.3$~dex with respect to those given by \citet{Woo2010}, which is the baseline for our adopted black hole mass estimators.
@@
 As a result, adopting a different local anchor would only globally affect the level of the \mbh\ to local and high-$z$ sample at the same time, with the result of leaving $\Delta\log$\mbh\ unchanged.
-{\bf To qualitative present this point, we adopt the K13 local elliptical and classic bulge as the $z\sim0$ anchor and compared to the recalibrated the \mbh\ of our 32 AGNs sample.
-The inference of  $\gamma$ is $0.74\pm0.31$ which is consistent at $1-\sigma$ level with the one (i.e., $\gamma=1.03\pm0.25$ ) by current anchor.
-
-For the local sample by \citet{Bentz2018}, with a different goal in mind, they decompose their host using more components than bulge$+$disk (e.g., Bar(s), Barlens, Ring(s)).
-This is beyond the comparison medium, i.e., bulge v.s.
-disk, of ours.
-Moreover, with a more manageable model, our inference gets ride of the overfitting issue.
-In spite of this, when adopting the \citet{Bentz2018} as the local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution.
+{\bf To illustrate this point further, we adopt the K13 local ellipticals and classical bulges as the $z\sim0$ anchor and compare to the recalibrated \mbh\ of our high-$z$ AGNs sample.
+The inference of  $\gamma$ changes to is $0.74\pm0.31$ which is consistent at $1-\sigma$ level with the one (i.e., $\gamma=1.03\pm0.25$ ) base on our current anchor.
+
+\citet{Bentz2018}, given the superior resolution of their data in the local universe, decomposed their host using more components than bulge$+$disk (e.g., Bar(s), Barlens, Ring(s)).
+This approach is impossible at high-$z$ given current data, and therefore their sample should not be used as local anchor, for consistency.
+Just for illustration, when adopting the \citet{Bentz2018} as the local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution, although as expected the amount of evolution is different for the reasons given above..
  }
@@
 We find the average ``observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, {\bf by $0.41$~dex (a factor of $\sim2.7$) and  $0.43$~dex (a factor of $\sim2.6$), respectively}, as compared to that in the local universe.
-{\bf However, the selection effect could bias the inference at $+2.1$~dex level, while taking in to account, the offset to the local universe is no more significant.} 
+{\bf However, taking into account uncertainties and the bias due to selection effect could bias, the offset to the local universe is only marginally significant.} 
 %these correlations are consistent with those in the local universe within the 95\% confidence limits. }
@@
 {\bf We summarize several limitations of this work.
-First, due to limited data qualities, we model the host proper as a single \sersic\ profile.
-The multi-components feature (e.g., disk$+$bulge) did not appear in the residual map, showing the multi-components information is overwhelmed by the noise level.
-Second, we adopt the universal stellar templates to derive the host luminosity and stellar mass for the overall sample, which introduces some uncertainty in the inference of the host properties.
-Even so, the uncertainty in the scaling relations is still dominated by the single epoch black hole mass estimates (see Section~\ref{sec:sysm_err} for detail).
-Third, for several AGN systems, their inferred host effective radius hit the lower limit, and thus the inference of their \Reff\ should be considered as the upper limit.
-However, the inference of their host luminosities and stellar masses are still reliable, given our re-fitting test using different lower limit boundary and the low scatter of the host flux inference (see Section~\ref{sec:result-hosts}, second paragraph).
-Last, in the literature, there are several different samples that could be chosen as the local anchor to the high-$z$ sample, which could change the inference of the evolution value.
-In this work, we adopted the most similar local sample to those at high-$z$.
-We discussed the different anchors in detail and test to infer the evolution trend using different anchors; all the inference show the positive evolution  (see Section~\ref{sec:local_sys}).}
+First, due to finite resolution of \hst, we model the host as a single \sersic\ profile.
+The residuals do not show evidence of additional components, indicating that our choice is appropriate given the noise and resolution of the data.
+However, we cannot exclude that more features would be revealed by higher quality data.
+
+Second, we adopt simple stellar population templates to derive the host luminosity and stellar mass for the sample, which introduces some uncertainty in the inference of the host properties.
+However, this source of uncertainty is subdominant with respect to that associated with single epoch black hole mass estimates (see Section~\ref{sec:sysm_err} for detail).
+
+Third, for a few AGN hosts, their inferred host effective radius hit the lower limit, and thus the inference of their \Reff\ should be considered as the upper limit.
+However, the inference of the host luminosity and stellar mass is still reliable in this cases, as shown by our test using different lower limit boundaries (see Section~\ref{sec:result-hosts}, second paragraph).
+
+Fourth and last, the choice of local anchor affects our inferred evolution at some level.
+We adopted as our baseline the local samples for which measurements have been made with a procedure that is most similar to the one we have applied at high-$z$, but other choices are possible.
+We investigated the impact of different choices for the local anchor in detail and we found that even though the numerical values can change somewhat, the inferred evolution is always positive  (see Section~\ref{sec:local_sys}).}
 
@@
 
-Finally, the forthcoming launch of the {\it James Webb Space Telescope} ({\it JWST}) may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim7$) and thus trace the evolution of correlations at the more distant universe.
+Finally, the forthcoming launch of the {\it James Webb Space Telescope} ({\it JWST}) and the first light of adaptive-optics assisted extremely large telescopes may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim7$) and thus trace the evolution of correlations at the more distant universe.
 Although, galaxies, as we know, are smaller at high-$z$ thus may remain challenging to detect under the glare of a luminous AGN.
@@
 
-{\bf The authors thank the anonymous referee for helpful suggestions and comments which improved the presentation of this paper.
+{\bf The authors thank the anonymous referee for helpful suggestions and comments which improved this paper.
 We acknowledge the importance of the conference ``Particle Astrophysics and Cosmology Including Fundamental InteraCtions (PACIFIC-2013)" in preparing for this program.} We fully appreciate input from Luis Ho, Renyue Cen, Hyewon Suh, Takahiro Morishita and Peter Williams.
@@
 
-\section{C. The \mbh-\smass\ comparison sample}\label{sec:comp_sample_value}
-We use the self-consistent recipes to re-calibrate our comparison sample. We list the values of all the comparison \mbh-\smass\ sample in the Table~\ref{tab:comp_sample}.
+{\bf \section{C. The \mbh-\smass\ comparison sample}\label{sec:comp_sample_value}
+We use the self-consistent recipes to re-calibrate the measurements of our comparison sample. We list the values of all the comparison \mbh-\smass\ sample in the Table~\ref{tab:comp_sample}.}
 
@@
 \centering
-\caption{The summary for the comparison \mbh-\smass\ sample}\label{tab:comp_sample}
+\caption{{\bf Data summary for the comparison \mbh-\smass\ sample}}\label{tab:comp_sample}
 \resizebox{18cm}{!}{
@@
 \tablecomments{\\$^a$:  The object name is directly adopted from the reference.
-\\$^b$:  For the \citet{H+R04} sample, the redshift value is calculated from their physical Galaxy distance.
-\\$^c$:  The entire \smass\ for the local sample are the bulge masses.
-\\$^d$:  If applicable, the values in the bracket are the bulge mass.
+\\$^b$:  For the \citet{H+R04} sample, the redshift value is calculated from the Galaxy distance, assuming perfect Hubble flow.
+\\$^c$:  \smass\ for the local sample are the bulge masses.
+\\$^d$:  If applicable, the values in brackets are the bulge mass.
 }

### 2019-10-17 manuscript/manuscript.tex
Update the offset value

@@
 The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators.
-We find the {\it observed} ratio of \mbh/\smass~to {\bf be $2.6\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs.
+We find the {\it observed} ratio of \mbh/\smass~to {\bf be $2.7\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs.
 \ding{(TB update based on Daeseong's result:) an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
@@
 In Figure~\ref{fig:MM-vz}, we plot the mass ratio as a function of redshift ({\it right} panel) and the mass ratio difference ($\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$ which is considered as the difference between the high redshift data and the best-fit local relation; {\it left} panel).
-For our high-$z$ sample, we find the averaged $\Delta \log \mathcal M_{\rm BH}$ to be $0.32$, a factor of two higher than the local mass ratio as indicated by the top blue circle in Figure~\ref{fig:MM-vz}.
+For our high-$z$ sample, we find the averaged $\Delta \log \mathcal M_{\rm BH}$ to {\bf be $0.43\pm0.06$, a factor of $~\sim2.7$ higher} than the local mass ratio as indicated by the top blue circle in Figure~\ref{fig:MM-vz}.
 
@@
 
-We find the average ``observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, {\bf by $0.41$~dex (a factor of $\sim2.7$) and  $0.43$~dex (a factor of $\sim2.6$), respectively}, as compared to that in the local universe.
+We find the average ``observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, {\bf by $0.41$~dex (a factor of $\sim2.6$) and  $0.43$~dex (a factor of $\sim2.7$), respectively}, as compared to that in the local universe.
 {\bf However, taking into account uncertainties and the bias due to selection effect could bias, the offset to the local universe is only marginally significant.} 

### 2019-10-25 manuscript/manuscript.tex
Update for resubmit (bold version)

@@
 
-Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., stellar mass \smass, luminosity \lhost) suggest an evolutionary connection.
+Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., {\bf total} stellar mass \smass, luminosity \lhost) suggest an evolutionary connection.
 A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates.
-For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 \hbox{X-ray-selected} broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
-By applying state-of-the-art tools to decompose the \hst\ images, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting.
+For this purpose, we {\bf acquired} {\it Hubble Space Telescope} imaging with WFC3 of 32 \hbox{X-ray-selected} broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
+By applying state-of-the-art tools to decompose the \hst\ images {\bf including available ACS data}, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting.
 The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators.
-We find the {\it observed} ratio of \mbh/\smass~to {\bf be $2.7\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs.
-\ding{(TB update based on Daeseong's result:) an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
-Therefore, our results are in agreement, considering the uncertainties, with a scenario where SMBHs and their total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter.
-Based on an inference of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is significantly offset from the local value {\bf by a factor of $\sim7$ which} persists even after accounting for selection effects.
+We find {\bf that} the {\it observed} ratio {\bf of \mbh\ to total \smass\ is $2.7\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs.
+{\bf A non-evolving mass ratio is consistent with the data at the 2-3$\sigma$ confidence level when accounting for selection effects (estimated using two independent and complementary methods), and their uncertainties.} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
+Therefore, our results {\bf cannot distinguish whether SMBHs and their total host stellar mass and luminosity proceed in lockstep or whether the growth of the former somewhat overshoots the latter, given the uncertainties.
+Based on a statistical estimate} of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is {\bf offset from the local value by a factor of $\sim7$ which} is significant even accounting for selection effects.
 Taken together, these observations are consistent with a scenario in which stellar mass is subsequently transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than mass accretion onto the SMBH.
@@
 
-Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass), and stellar velocity dispersion (\sigstar).
+Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to {\bf correlate} with the host properties, such as luminosity (\lhost), stellar mass (\smass), and stellar velocity dispersion (\sigstar).
 The tightness of these correlations (also known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
@@
 
-To understand the nature of these correlations, it is important to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}.
+To understand the nature of these correlations, it is important to study them as a function of redshift, determining how and when they {\bf emerge and evolve} over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}.
 During the past decade, there has been much progress on this front using type-1 AGNs.
-For example, it has been demonstrated at $z<1$ that at fixed \mbh\ the host galaxies are under luminous compared to today's hosts \citep{Park15, Tre++07, Pen++06qsob}.
+For example, it has been demonstrated that {\bf AGN host galaxies, at $z<1$ and for fixed \mbh, are} under luminous compared to today's hosts \citep{Park15, Tre++07, Pen++06qsob}.
 Similarly, \citet{Bennert11} and \citet{Woo++08} found a positive evolution of \mbh, especially when the data are sufficiently robust to isolate the luminosity or stellar mass of the bulge or spheroidal component.
@@
 If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.
-A possible mechanism to account for the latter part of the growth of the galaxy without increasing \mbh\ is the transfer of stellar mass from the disk to the bulge \citep{Bennert++2011} through bar instabilities or minor mergers.
+A possible mechanism to account for the latter part of the growth of the galaxy without increasing \mbh\ is the transfer of stellar mass from the disk to the {\bf bulge \citep{Jah++09,Bennert++2011,SS13} through} bar instabilities or minor mergers.
 
@@
 To date, the infrared capabilities of \hst/WFC3 have not been fully exploited on this topic.
-Here, we measure the properties of 32 host galaxies within a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS.
+Here, we measure the properties of 32 host galaxies {\bf with} a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS.
 Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e., $\sim0.23$ dex,][]{Schulze2014}.
@@
 {\bf Furthermore, we collect from the literature comparison samples of intermediate-$z$ and local AGN, selected to have been analyzed with very similar methods to those applied in the distant sample.
-We recalibrate the relevant quantities from the literature based on a set of self-consistent recipes to ensure that our differential measurement of evolution is robust to calibration and methodological issues~\ref{sec:compare_sample}.}
+We recalibrate the relevant quantities from the literature based on a set of self-consistent recipes to ensure that our differential measurement of evolution is robust to calibration and methodological issues (Section~\ref{sec:compare_sample}).}
 
@@
 \label{sec:data}
-We utilize a sample size of 32 broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that have black hole mass measurements available and fall within deep extragalactic survey fields that offer rich ancillary data.
+We utilize a sample size of 32 broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that have black hole mass {\bf measurements} and fall within deep extragalactic survey fields that offer rich ancillary data.
 Specifically, we focused on meeting the following criteria to overcome the limitations of previous studies:
@@
 
-\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., \halpha) which avoids potential systematic uncertainties in UV-based estimators \citep{Greene2005}.
-
-\item {\bf Black holes masses \mbh/$M_{\odot}\lesssim8.7$, which is below the knee of the black hole mass function to minimize selection biases (see Figure~\ref{fig:selection}, top panel).} %fall below the knee of the black hole mass function to minimize the selection biases.
+\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., \halpha) which {\bf avoid} potential systematic uncertainties in UV-based estimators \citep{Greene2005}.
+
+\item {\bf Black holes masses \mbh/$M_{\odot}\lesssim8.7$, are below the knee of the black hole mass function to minimize selection biases (see Figure~\ref{fig:selection}, top panel).} %fall below the knee of the black hole mass function to minimize the selection biases.
 
@@
 
-\item {\bf X-ray selected sample has host-to-total flux ratios typically above $30\%$ which facilitates the galaxy mass measurements.}.
-%The lower nuclear-to-host ratios of our sample facilitates the galaxy mass measurements, given that they are X-ray selected.
+\item {\bf X-ray selected sample has host-to-total flux ratios typically above $30\%$ which facilitates the galaxy mass measurements.} %The lower nuclear-to-host ratios of our sample facilitates the galaxy mass measurements, given that they are X-ray selected.
 
@@
 
-The 32 AGNs are initially selected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
+The 32 AGNs are initially selected by the X-ray observations {\bf of COSMOS}~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
 In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan.
@@
 The spectrum is modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on $\chi^2$ minimization.
-We refer the reader to that paper for more details.}
+We refer the reader to the aforementioned paper for further details.}
 Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} {\bf using a similar approach}.
 
-Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~(\mbh/$M_{\odot})\lesssim8.5$.
+{\bf Based on the \mbh\ estimates} described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~(\mbh/$M_{\odot})\lesssim8.5$.
 The bolometric luminosities are measured from the broad AGN lines by \citet[][Section 3.3]{Schulze2018}, which are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
@@
 While fourteen AGNs have emission line properties for both \halpha\ and \hbeta, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample.
-It is worth noting that the absolute flux calibration of the FMOS spectra is set to match ground-based IR imaging, UltraVISTA in the case of COSMOS, thus amounting to an effective aperture correction.
 While most recipes are calibrated against \hbeta\, the line is typically weaker than H$\alpha$, hence lower signal-to-noise.
 We provide the \mbh\ measurements together with the properties of the emission lines in Table~\ref{tab:result_mbh}.
+
+{\bf It is worth noting that the absolute flux calibration of the FMOS spectra is set to match the available ground-based IR imaging, UltraVISTA in the case of COSMOS.
+While an initial flux calibration is performed during the reduction of the FMOS data using calibration stars, there can be differential flux loss due to aperture effects, variable seeing conditions, and minor alignment issues with the instrument.
+The flux normalization is effectively an aperture correction in the J or H band depending on the source redshift.
+We note that this procedure does not correct for intrinsic variability that may induce an additional error of 0.2 mag.
+We refer the reader to Section 2.2 of \citet{Schulze2018} for full details on the flux calibration.}
 
@@
 The sample by B10 consists of 19 AGN with the \mbh-\lhost\ relation determined with reliable \mbh\ masses using reverberation mapping with an uncertainty level $\sim0.15$ dex.
-{\bf Note that the B10 only provides the galaxy single V-band luminosity.
+{\bf Note that B10 only provides the single galaxy V-band luminosity.
 \citet{Ding2017b} derive the galaxy R-band luminosity based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
@@
 We select samples that were analyzed by members of our team to ensure uniform measurements.
-The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using single-band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$ {\bf .
-Similarly to B10's sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-correction from the V-band based on the same stellar template.
+The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using a single band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$.
+{\bf Similar to the B10 sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-corrections from the V-band based on the same stellar template.
 Moreover, \citet{Bennert11} and \citet{SS13} estimate the stellar masses of their 27 objects using multi-band imaging data, and we adopt them as the \mbh-\smass\ comparison sample.}
@@
 \item AGN imaging data. \\
--- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample\footnote{\bf The photometric aperture was determined as  a compromise between capture all the flux and keeping the background noise low and the computational time short.
+-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample\footnote{\bf The photometric aperture was determined as a compromise between the detection of the total flux and a minimization of the background noise while keeping the computational time low.
 We found that extending the radius beyond $1\farcs5$ did not add any missing light, while it increased the noise and computational time.
@@
 As shown in Figure~\ref{fig:hist_compare}, the results are consistent.
-For each AGN, we check the {\bf location on the detector for the top-ranked PSFs} and find that they are unrelated to the AGN's {\bf location in the detector.
+For each AGN, we check the {\bf location on the detector for the top-ranked PSFs} and find that they are unrelated to the {\bf AGN position on the detector.
 This finding underscores that position on the detector is not the main factor driving the PSF shape.
-Other factors that are likely to be more significant are sub-pixel centering, intrinsic color of the star, and jitter and thermal status of the telescope during the observations.
+Other factors, likely to be more significant, are the sub-pixel centering, the intrinsic color of the star, and the jitter and thermal status of the telescope during the observations.
 The complexity of the problem}
@@
 
-From our image decomposition, we detect the {\bf host galaxy in all cases at a significant level, except one case (i.e., SXDS-X763) that has host-to-total flux ratios lower than $15\%$}.
+From our image decomposition, we detect the {\bf host galaxy in all cases at a significant level, except one case (i.e., SXDS-X763) that has a host-to-total flux ratio lower than $15\%$}.
 \hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data$-$point source'' stamps) of Figure~\ref{fig:AGN_decomp} and in Appendix~\ref{sec:restsample} for the remaining cases.
@@
 The distributions of effective radius \Reff\ {\bf are shown in Figure~\ref{fig:hist_compare} {\bf (bottom panel)}.
-Based on the redshift, we calculate the physical scale radius of each object in kpc assuming a standard cosmology.
-We plot them together with inferred \sersic\ index in Figure~\ref{fig:hist_rn}.} These values are distributed within the allowed range and not concentrated on either the upper or lower bound.
+Based on the redshift, we calculate the physical scale of the radius for each object in kpc assuming a standard cosmology.
+We plot them together with measured \sersic\ index in Figure~\ref{fig:hist_rn}.} These values are distributed within the allowed range and not concentrated on either the upper or lower bound.
 The \Reff\ of our sample are between $\sim1-7$~kpc (peaked at $\sim2.2$~kpc).
 Nearly half ($15/32$) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge.
-Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
+Five systems {\bf have} a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
 {\bf Seven systems have effective radius \Reff$<0\farcs18$, i.e., smaller than 3 pixels.
@@
 In particular, the}
-inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero.
+inferred \Reff\ for {\bf three} systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero.
 This means the size inference of these three systems should really be considered an upper limit, rather than a measurement.
@@
 We find {\bf that the $1$~Gyr and the $0.625$~Gyr} stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} {\bf provide the excellent matches} to the observed colors of our sample {\bf at $z<1.44$ and $z>1.44$, respectively}  (see Figure~\ref{fig:compare_temp}).
-{\bf To minimize the uncertainty associated with these corrections, we adopt these two templates correspondingly to interpolate to the rest-frame R band which is very close to the observed wavelengths}.
+{\bf To minimize the uncertainty associated with these corrections, we use these two templates to interpolate to the rest-frame R band which is very close to the observed wavelengths}.
 We note that the choice is not unique, and other combinations of ages and metallicities and star formation history could match the observed colors and would provide very similar R-band magnitudes, and also stellar masses \citep{Bell2000, Bell2001}.
@@
 
-Adopting {\bf the $1$~Gyr and $0.625$~Gyr} stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample{\bf, based on the host inference at WFC3 band}.
+Adopting {\bf the $1$~Gyr and $0.625$~Gyr} stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample{\bf, based on the host inference in the  WFC3 band}.
 As mentioned above, since the WFC3 filter is already close to the rest-frame R-band, we expect the $M_R$ uncertainty introduced by this K-correction to be within $0.05$~mag.
@@
 \end{eqnarray} 
-Performing such a fit based on the {\it observed} data (i.e., no correction for selection effects), {\bf we obtain $\gamma  = 1.03 \pm 0.25$ that} may be tentatively considered as evidence for evolution.
-Even with the exclusion of the few outliers, there is an evolution in the {\bf correlation with $\gamma  = 0.89 \pm 0.27$}.
+Performing such a fit based on the {\it observed} data (i.e., no correction for selection effects), {\bf we obtain $\gamma  = 1.03 \pm 0.25$.
+Even with the exclusion of the few outliers, the slope is significantly non-zero with $\gamma  = 0.89 \pm 0.27$}.
 The best-fit {\it observed} evolution model is shown in Figure~\ref{fig:MM-vz}.
@@
 A simple check using our prior estimate of the bias yields a similar result.
-The mean offset of the sample of 32 objects from the local {\bf relationship is $0.42\pm0.06$ dex, which would correspond to $\gamma=1.06\pm0.15$}.
-However, after correcting for the selection bias ($0.21$~dex, see Section~\ref{sec:sf_framework}), {\bf the offset reduces to $0.20\pm0.06$ and thus $\gamma=0.50\pm0.15$, marginally positive, but not conclusively inconsistent with the local value given the error bars and uncertainty in the correction.} We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
+The mean offset of the sample of 32 objects from the local {\bf relationship is $0.43\pm0.06$ dex, which would correspond to $\gamma=1.08\pm0.15$}.
+However, after correcting for the selection bias ($0.21$~dex, see Section~\ref{sec:sf_framework}), {\bf the offset reduces to $0.22\pm0.06$ and thus $\gamma=0.55\pm0.15$, marginally positive, but not conclusively inconsistent with the local value given the error bars and uncertainty in the correction.} We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
 Whereas we expect the negative tail to be suppressed by our selection function, and thus it should be accounted for in our treatment.
@@
 \subfloat[\mbh-\smass, flat prior]
-{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_flatprior.pdf}}&
+{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_flatprior_update.pdf}}&
 \subfloat[\mbh-\smass, lognormal prior]
-{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_lognormprior.pdf}}\\
+{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_lognormprior_update.pdf}}\\
 \end{tabular}
@@
 The adopted sample includes our 32 AGNs and the intermediate redshift AGNs, using flat prior of \sint\ ({\it left} panel) and lognormal prior ({\it right} panel).
+{\bf The colored regions indicate the 68 and 95\% confidence regions.}
 }
@@
 The fidelity of the host galaxy magnitude is high as demonstrated by the robustness with respect to the choice of PSF, which is the primary source of uncertainty.
-However, we introduce some uncertainty by adopting {\bf a common} simple stellar population {\bf templates} to derive the rest-frame R-band luminosity and stellar mass for the full population.
+However, we introduce some uncertainty by adopting {\bf two common} simple stellar population {\bf templates} to derive the rest-frame R-band luminosity and stellar mass for the full population.
 In principle, if we had more information on the color, we could improve on this source of uncertainty by adopting a specific stellar population model for each target.
@@
 In the {\bf literature~\citep{Kormendy13, Bentz2018}}, other analyses of the local sample are available, which could also be considered as the local anchor.
-{\bf However, from the point of view of our differential evolutionary measurement, we stress once again the importance of selecting local anchors that have been measured and calibrated in the most similar way to the distant high-$z$ samples.
+{\bf However, from the point of view of our differential evolutionary measurement, we stress once again the importance of selecting local anchors that have been measured and calibrated in a similar way to the distant high-$z$ samples.
 It is crucial that the black hole masses be obtained in the same of self-consistent manner, and it is also critical that the host/AGN decomposition be measured in the most similar way possible.
@@
 This choice might affect the inference of the bulge/disk properties in absolute terms, but it is the most similar decomposition to what is possible at high-$z$ where these features cannot be resolved.
-Also, the HR04 sample does not use color information to estimate the \smass of their sample, rather than use Jeans modeling.
+Also, the HR04 sample does not use color information to estimate the \smass~of their sample, rather than use Jeans modeling.
 This gives rise to systematic uncertainties related to the choice of the initial mass function for example, which need to be kept in mind.
-\citep[See][for more discussion of systematic issues in local samples]{Kormendy13}.
-
-The issue of consistent calibration of black hole masses is perhaps the most subtle and thorny.
+We refer the reader to \citet{Kormendy13} for more discussion of systematic issues in local samples.
+
+The issue of a consistent calibration of black hole masses is perhaps the most subtle and thorny.
 Not all the local correlations are mutually consistent, especially when considering different galaxy properties like luminosity, stellar mass, and velocity dispersion, and therefore a single self-consistent calibration is not possible.
@@
 {\bf To illustrate this point further, we adopt the K13 local ellipticals and classical bulges as the $z\sim0$ anchor and compare to the recalibrated \mbh\ of our high-$z$ AGNs sample.
-The inference of  $\gamma$ changes to is $0.74\pm0.31$ which is consistent at $1-\sigma$ level with the one (i.e., $\gamma=1.03\pm0.25$ ) base on our current anchor.
+The inference of  $\gamma$ changes to $0.74\pm0.31$ which is consistent at $1\sigma$ level with the value (i.e., $\gamma=1.03\pm0.25$ ) based on our chosen anchor.
 
@@
 This approach is impossible at high-$z$ given current data, and therefore their sample should not be used as local anchor, for consistency.
-Just for illustration, when adopting the \citet{Bentz2018} as the local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution, although as expected the amount of evolution is different for the reasons given above..
+Just for illustration, when adopting the \citet{Bentz2018} as the local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution, although as expected the amount of evolution is different for the reasons given above.
  }
@@
 
-Third, for a few AGN hosts, their inferred host effective radius hit the lower limit, and thus the inference of their \Reff\ should be considered as the upper limit.
-However, the inference of the host luminosity and stellar mass is still reliable in this cases, as shown by our test using different lower limit boundaries (see Section~\ref{sec:result-hosts}, second paragraph).
+Third, for a few AGN hosts, their inferred host effective radius hits the lower limit, and thus the inference of their \Reff\ should be considered as the upper limit.
+However, the inference of the host luminosity and stellar mass is still reliable in these cases, as shown by our test using different lower limit boundaries (Section~\ref{sec:result-hosts}).
 
@@
 
-Given that the \smass$_{\rm ,total}$-\mbh\ relation is closer to or consistent with the local relation, the inferred evolution of the \bmass-\mbh\ correlations is qualitatively consistent with a scenario where the assembly of the black hole predates that of the bulge, which is processed by the transfer of stellar mass from the disk via mergers or secular processes \citep{Croton2006}.
-The stellar mass need to build the bulge appears to be present in the disk component at high-$z$.
+Given that the \smass$_{\rm ,total}$-\mbh\ relation is closer to or consistent with the local relation, the inferred evolution of the \bmass-\mbh\ correlations is qualitatively consistent with a scenario where the assembly of the black hole predates that of the bulge, which is processed by the transfer of stellar mass from the disk via mergers or secular {\bf processes \citep{Jah++09,Bennert++2011,SS13}.
+}The stellar mass {\bf needed} to build the bulge appears to be present in the disk component at high-$z$.
 
@@
 XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
-VNB gratefully acknowledges assistance from a NASA grant associated with HST proposal GO 15215.
+{\bf TT acknowledges support by NSF through grant AST-1412315.} VNB gratefully acknowledges assistance from a NASA grant associated with HST proposal GO 15215.
 JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
@@
 {\bf Based on the 32 AGN systems, we fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 1.07\pm0.23$, } as showing in Figure~\ref{fig:ML-vz}-(b).
-We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and \ding{ TBD: obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.3$, with} flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
+We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and {\bf obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.4$, }with flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
 
@@
 \subfloat[\mbh-\lhost, flat prior]
-{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
+{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior_update.pdf}}&
 \subfloat[\mbh-\lhost, lognormal prior]
-{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
+{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior_update.pdf}}\\
 \end{tabular}
@@
 \centering
-    \caption{The summary for the different inference of $\gamma$.}\label{table:gamma_sf}
+    \caption{{\bf Summary of $\gamma$ inferences }}\label{table:gamma_sf}
      \resizebox{8cm}{!}{
@@
      \hline\hline
-32 AGNs + intermediate & No &  0.72$\pm$0.20 & 0.64$\pm$0.17 \\
-32 AGNs + intermediate& \ding{TBD: Yes} & 0.80$\pm$0.40 & 0.50 $\pm$ 0.50 \\
-32 AGNs & No & 1.03$\pm$0.25 & 1.07$\pm$0.23\\
-32 AGNs& \ding{TBD: Yes} & 1.20$\pm$0.80 & 1.60$\pm$0.80 \\
+32 AGNs + intermediate & No &  {\bf 0.72$\pm$0.20} & {\bf 0.64$\pm$0.17} \\
+32 AGNs + intermediate& Yes & {\bf 0.90$\pm$0.40} & {\bf0.50$\pm$0.50} \\
+32 AGNs & No & {\bf 1.03$\pm$0.25} & {\bf 1.07$\pm$0.23}\\
+32 AGNs& Yes & {\bf 1.50$\pm$0.80} &  {\bf 1.80$\pm$0.80} \\
      \hline
@@
 \centering
-    \caption{The inference of $\gamma$ for \mbh-\smass\ by different sample combination.}\label{table:diff_sample_gam}
+    \caption{ {\bf Observed $\gamma$ for \mbh-\smass\ without selection effect corrections }}\label{table:diff_sample_gam}
      \resizebox{5.5cm}{!}{
@@
      \hline\hline
-32 AGNs & 1.03$\pm$0.25\\    
-30 AGNs (excluded outliers) & 0.89$\pm$0.27\\    
-32 AGNs + intermediate &  0.72$\pm$0.20\\
-32 AGNs bulge only & 2.09$\pm$0.30\\
+32 AGNs & {\bf 1.03$\pm$0.25}\\    
+30 AGNs (excluded outliers) &  {\bf 0.89$\pm$0.27}\\    
+32 AGNs + intermediate &   {\bf 0.72$\pm$0.20}\\
+32 AGNs bulge only &  {\bf 2.09$\pm$0.30}\\
      \hline
      \end{tabular}}
-\tablecomments{These values are directly inference for the observation, which haven't yet taken the selection effect into account.}
+\tablecomments{These values are directly {\bf inferred for the observation, without corrections due to selection effects.}}
 \end{table}

### 2019-10-30 NA_paper/manuscript_II/qso_paperII.tex
Update qso_paperII.tex

@@
 %\section{Introduction}
-The discovery of the correlations between the masses (\mbh) of supermassive black holes (SMBH) and the properties of their host galaxies, such as absolute magnitude ($Mag$) and stellar mass (\mstar), indicates that the growth of SMBH could be connected to its host galaxy formation~\cite{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
+The discovery of the correlations between the masses (\mbh) of supermassive black holes (SMBH) and the properties of their host galaxies, such as absolute magnitude ($Mag$) and stellar mass (\mstar), indicates that the growth of SMBH could be connected to the formation of their host galaxies~\cite{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
 So far, the origin that drives this connection is still unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim$10 kpc).
-A dominant interpretation is so-called AGN feedback, assuming that a small fraction of AGN energy injects to their surrounding gas that regulates the growth of SMBH and its host galaxy.
-In this scenario, the activity of AGN accretion heats and unbinds significant fractions of the gas and inhibits star formation.
-In addition, there are other models that have been proposed that the connection between SMBH and their hosts are connected not in a direct manner but assuming that they share a common gas supply~\cite{Cen2015, Menci2016}.
-Furthermore, without any physical mechanisms, it has been proposed that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations~\cite{Peng2007, Jahnke2011, Hirschmann2010}.
-In this central limit theorem, a stochastic cloud at high-$z$ (higher scatter) would end up with the scaling relations (lower scatter) as observed today.
+A possible physical link may be feedback from an Active Galactic Nucleus (AGN) phase, assuming that a small fraction of the AGN energy is injected into their surrounding gas that regulates the growth of the SMBH and its host galaxy.
+In this scenario, AGN activity heats and unbinds a significant fraction of the gas and inhibits star formation.
+However, there are other models that have been proposed to explain the connection between SMBH and their hosts such as through an indirect manner where AGN accretion and star formation are fed through a common gas supply~\cite{Cen2015, Menci2016}.
+Furthermore, it has been proposed that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations without any direct physical mechanisms~\cite{Peng2007, Jahnke2011, Hirschmann2010}.
+From the central limit theorem, a stochastic cloud at high-$z$ (higher dispersion) would end up with scaling relations as observed today with lower dispersion.
 
-To understand this connection, recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have analyzed the scaling relations to intermediate redshift {($0.3<z<1$)} by studying the active galactic nuclei (AGN) using {\it Hubble Space Telescope} ({\it HST}) and found an evolution that the growth of SMBHs predated to their host galaxies.
-However, the observational evidence of evolution at high-$z$ is under debated as it relies on our understanding of systematic uncertainties and selection effects~\cite{Lauer2007}.
-It has been realized that the improper way to consider the uncertainties and selection effects could result in an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.
+To understand this connection, recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have measured the scaling relations out to intermediate redshift {($0.3\lesssim z \lesssim1$)} by studying AGN and their host galaxies with {\it Hubble Space Telescope} ({\it HST}) and found an 'observed' evolution in which the growth of SMBHs predates their host galaxies.
+However, the observational evidence of such evolution at high-$z$ is under debated since it depends on our understanding of systematic uncertainties and selection effects~\cite{Lauer2007}.
+It has been realized that an improper consideration of the uncertainties and selection effects will lead to an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.
 
@@
 %The reason to extend to high redshift.
-Simulation models are effective to help understand this connection and rule out the theories/assumptions which could not be verified by the observations.
-In simulation test, the systematic uncertainties and selection bias would be easy to account for.
-Recent studies by several simulation projects have made predictions which are in good agreement with the observations at the intermediate redshift range ($z<1$).
-For example, the state-of-the-art cosmological hydrodynamical simulations of structure formation (\texttt{MassiveBlackII}) have compared the predicted scaling relations to the \hst\ observation at $0.3<z<1$ and predict a positive evolution that SMBH growth predates the host galaxy~\cite{DeG++15}.
-Several others works have investigated the scaling relations using large-volume simulations, resulting in well matches to the local relation with some redshift evolution, including approaches using the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014, Li2019}.
-Besides hydrodynamic simulations, the semi-analytic models~\cite{Menci2014, Menci2016} also made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}.
+Simulations are effective at helping to understand this connection and rule out theories/assumptions that could not be definitively verified by observations alone.
+In particular, simulations can be used to quantify the impact of systematic uncertainties and selection biases with observational analysis.
+Recent studies, based on several simulation projects, have made predictions that are in good agreement with the observational data at intermediate redshifts ($z<1$).
+For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been utilized to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ that show a positive evolution where the SMBH growth predates that of its the host galaxy~\cite{DeG++15}.
+Several others works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014, Li2019}.
+Besides hydrodynamic simulations, semi-analytic models~\cite{Menci2014, Menci2016} have also made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}.
 However, to date, the comparisons to the observed scaling relations by high-resolution \hst\ imaging sample are still limited within $z<1$ due to the limitation of the observations.

### 2019-11-01 NA_paper/manuscript_II/qso_paperII.tex
make udpate before John eidt

@@
 Supermassive black holes (BH) are known to reside at the center of massive galaxies.
-In the local Universe, BH masses (\mbh) are tightly correlated to the properties of their host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar), known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar) that are not yet fully understood.
- %Observational results have indicated evidence that this correlation evolves with cosmic time, suggesting a scenario that the BH growth predates their host.
-In theory, positive evolution of BH is also predicted by several simulation projects independently.
-Even so, simulations can reproduce these relations over the last eight billion years ($z\lesssim1$).
-However, it is crucial to extend comparisons between observational data and simulations to earlier cosmic epochs ($z>1$), where the predicted relations are more sensitive to the initial assumptions and any inconsistency would help to pinpoint missing physics.
-For this purpose, we have a unique sample of 32 broad-line Active Galactic Nuclei (AGN) at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with the broad \halpha\ emission line, as detected by Subaru/FMOS, providing an accurate assessment of \mbh ~while multi-band \hst\ imaging is used to derive the host galaxies properties (e.g., \mstar).
-We directly compare this sample with two independent state-of-the-art simulations: \texttt{MassiveBlackII} (MBII) and a semi-analytic model (SAM).
+In the local Universe, BH masses (\mbh) are tightly correlated to the properties of their host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar), known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar).
+The origin of this correlation is still not fully understood, and one promising way to reveal it is to use simulation.
+During the past few years, simulation have successfully reproduced the observational relations over the last eight billion years ($z\lesssim1$).
+However, due to the limitation of high-$z$ measurements, the simulations haven't yet make the comparison to the observations at earlier cosmic epochs ($z>1$), where the predictions are more sensitive to the initial assumptions and any inconsistency would help to pinpoint missing physics.
+For this purpose, we adopted a unique sample of 32 broad-line Active Galactic Nuclei (AGN) at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with the broad \halpha\ emission line as detected by Subaru/FMOS, providing an accurate assessment of \mbh, while multi-band \hst\ imaging is taken to derive the host galaxies properties (e.g., \mstar).
+We directly compare the measurements to two independent state-of-the-art simulations: \texttt{MassiveBlackII} (MBII) and semi-analytic model (SAM).
 Taking the selection biases into account, %by adopting the same selection function to choose the simulating sample,
 we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
-However, when considering measurement uncertainty and the scatter in the scaling relations, the observations are significantly more consistent with the \mbii\ sample ($\sim0.3$~dex), than the \sam\ ($\sim0.7$~dex).
-{\color{red} In this respect, our observational constraints are able to distinguish the recipe adopted between the two models.
-Though both of them have considered AGN feedback in their simualitons, \mbii\ considers this feedback as the its driven for the scaling relation, rather than the recipe by \sam\ (galaxy interaction driven).} Moreover, the intrinsic scatter of our high-$z$ sample is comparable to the local sample thus counter to the expectation from a scenario based on the central limit theorem (a purely stochastic process).
-To some extent, our result attests that there has to be a causal link between SMBH and its host galaxy to induce an ordering so that the more massive black holes are tightly linked to the more massive galaxies.
+However, when considering the measurement uncertainty and comparing the scatters, the observations are significantly more consistent with the \mbii\ sample ($\sim0.3$~dex), than the \sam\ ($\sim0.7$~dex).
+{\color{red} In this respect, our observational constraints are able to distinguish the recipe adopted between the two projects.
+For example, in the \mbii, it is the AGN feedback that drives the scaling relations, while in the \sam\ it is galaxy merger driven.} Moreover, the intrinsic scatter of our high-$z$ sample is comparable to the local sample thus counter to the expectation from a scenario based on the central limit theorem (a purely stochastic process).
+To some extent, our result attests that it is the AGN feedback that establishs a causal link between SMBH and its host galaxy to induce an ordering so that the more massive black holes are tightly linked to the more massive galaxies.
 
@@
 
-To understand this connection, recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have measured the scaling relations out to intermediate redshift {($0.3\lesssim z \lesssim1$)} by studying AGN and their host galaxies with {\it Hubble Space Telescope} ({\it HST}) and found an 'observed' evolution in which the growth of SMBHs predates their host galaxies.
+To understand this connection, recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have measured the scaling relations out to intermediate redshift {($0.3\lesssim z \lesssim1$)} by studying AGN and their host galaxies with {\it Hubble Space Telescope} ({\it HST}) and found an `observed' evolution in which the growth of SMBHs predates their host galaxies.
 However, the observational evidence of such evolution at high-$z$ is under debated since it depends on our understanding of systematic uncertainties and selection effects~\cite{Lauer2007}.
@@
 In particular, simulations can be used to quantify the impact of systematic uncertainties and selection biases with observational analysis.
-Recent studies, based on several simulation projects, have made predictions that are in good agreement with the observational data at intermediate redshifts ($z<1$).
+Recent studies, based on several simulation projects, have made predictions that are in good agreement with the observational data at intermediate redshifts ($z\lesssim1$).
 For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been utilized to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ that show a positive evolution where the SMBH growth predates that of its the host galaxy~\cite{DeG++15}.
-Several others works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014, Li2019}.
+Several other works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014, Li2019}.
 Besides hydrodynamic simulations, semi-analytic models~\cite{Menci2014, Menci2016} have also made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}.
@@
 	%mention the scatter.
-To extend the range, we have been studing a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from three X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008} (Ding et al.
-submitted - D19 hereafter ).
+To extend the range, we have been studying a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from three X-ray coverage fields (D19~\cite{Ding2019} hereafter), including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}.
 The redshift range of our targets is chosen to be high enough ($z>1$) to detect the existence of the evolution offsets and make the comparison to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming.
@@
 To make the comparison, we adopt two independent simulation projects, including \texttt{MassiveBlackII} (MBII)~\cite{Khandai2015} and semi-analytic models (SAM)~\cite{Menci2014}.
-These two models are based on independent model strategies, i.e., hydrodynamic simulation for \mbii\ and semi-analytic model for \sam, respectively.
+These two simulations are based on independent model strategies, i.e., hydrodynamic simulation for \mbii\ and semi-analytic model for \sam, respectively.
 The \mbii\ simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
@@
 However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as \sam.
-In previous works~\cite{Huang2018, DeG++15, Khandai2015, Bhowmick2019, Menci2014, Menci2016}, \mbii\ and \sam\ have made high successful predictions, and we refer the interested readers to the Method section for more details.
+In previous works, \mbii~\cite{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\cite{Menci2014, Menci2016} have made high successful predictions, and we refer the interested readers to the Method section for more details.
 
@@
 We assume uncertainties are comparable to the realistic levels, i.e., $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex, and $\Delta L_{\rm bol}$=0.03~dex, respectively.
-We then select the sample that falls into the same targeting window to mimic the sample selection process, as shown in Figure~\ref{fig:selectfunc}.
+We then select the sample that falls into the same targeting window to mimic the realistic sample selection process, as shown in Figure~\ref{fig:selectfunc}.
 Considering that the mass relations between SMBH and its host are more substaintial, we focus on the predicted \mbh-\mstar relations and compared to the observational constraints, as shown in Figure~\ref{fig:MM_comp} (left panel).
@@
 
-{\color{red} In terms of their central distribution, the \mbii\ simulation and \sam\ model both demonstrate an excellent agreement to the observational constraints.
+{\bf In terms of their central distribution, the \mbii\ simulation and \sam\ model both demonstrate an excellent agreement to the observational constraints.
 When considering the scattering effect by the measurement uncertainty, the scatter in \mbii\ simulation is consistent to the observational one ($\sim0.3$~dex); however, \sam\ sample has much larger scatter ($\sim0.7$~dex).
-Given that the two models adopt different assumptions, recipes, and initial conditions, our result shows that the mechanism by \mbii\ is more favorable, in which the scaling relation is AGN feedback driven \ding{To Aklant and Tiziana, do you agree with this statement?}.
-Through \sam\ model also consider the AGN feedback, the feeding process for the BH accretion is merger driven with more stochasticities in the scaling relations, which may leads to the larger scatter.
-In particular, in the \sam\ model the encounters are assumed to trigger the feedback and the fraction of gas feeding the BH is related to the parameters of the 
+Given that the two models adopt different assumptions, recipes, and initial conditions, our result shows that the mechanism by \mbii\ is more favorable, in which it is the AGN feedback that drives the scaling relation \ding{To Aklant and Tiziana, do you agree with this statement?}.
+Though \sam\ model also consider the AGN feedback, the feeding process for the SMBH accretion is still galaxies merger driven with more stochasticities in the scaling relations, which may leads to the larger scatter.
+In particular, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the
 encounter.
@@
 As a result, the \sam\ cloud extends to the high \mbh\ with low stellar mass, which may not exist.
-\ding{To Nicola: is that possible to change the assumption in \sam\ to make the relations tighter?} The consistency between \mbii\ and observations indicates that there has to be a causal link between SMBH and its host galaxy to generate an ordering during their evolution; as a result, more massive BHs are linked to more massive galaxies {\it tightly}.
+\ding{To Nicola: do you want to include your new 2D model in the paper?} The consistency between \mbii\ and observations indicates that there has to be a causal link (i.e., AGN feedback) between SMBH and its host galaxy to generate an ordering during their evolution; as a result, more massive BHs are linked to more massive galaxies {\it tightly}.
 }
@@
 In fact, our inferred intrinsic scatter of the observed sample is $\sim0.25$~dex, which is no more than the typical scatter at local relations in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}.
-Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate our value.
+Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level for the real data.
 Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), resulting in an overestimating of the error-budget and thus underestimating of intrinsic scatter.
@@
 We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3's result to infer the host color.
-{\color{red} We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the rest-frame R band luminosity and stellar mass.} A Salpeter initial mass function is employed consistently to the observed and simulated sample.
+{\bf We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the rest-frame R band luminosity and stellar mass.} A Salpeter initial mass function is employed consistently to the observed and simulated sample.
 
@@
 To quantify the agreement between the simulation and the observation, we use a linear regression to fit their relations and compare the result.
-Our selection window has a hard cut on the \mbh\ value (i.e., vertical direction in Figure~\ref{fig:MM_comp}), and thus the scatter on the host properties are larger (horizontal direction).
+Our selection window has a hard cut on the \mbh\ value (i.e., vertical direction in Figure~\ref{fig:selectfunc}), and thus the scatter on the host properties are larger (horizontal direction).
 Thus, we fit the host properties (i.e., \mstar) as a function of \mbh.
@@
 We then use the sample slope value to fit for the observations.
-The comparing results are showing in Figure~\ref{fig:MM_comp}.
-To estimate the scatter of the sample, we plot the histogram of the residual, i.e., the sample deviation to their best-fit.
+The comparison results are showing in Figure~\ref{fig:MM_comp}.
+To estimate the scatter of the sample, we plot the histogram of the residual distribution, i.e., the sample deviation to their best-fit.
 The result is presented in Figure~\ref{fig:offset_comp} (left panel).
@@
 Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \mbii\ sample and the observational sample have the same intrinsic scatter level.
-We adopt the python package {\sc Linmix} to estimate this intrinsic scatter based on the \mbii\ overall sample and obtain $0.25$~dex.
+We adopt the python package {\sc Linmix} to estimate this intrinsic scatter based on the \mbii\ overall sample and obtain the level as $0.25$~dex.
 

### 2019-11-13 manuscript/manuscript.tex
Update the paper reference by Anton's comments.

@@
 
+\newcommand{\red}[1]{{\bf \textcolor{red}{[#1]}}} 
+\newcommand{\blue}[1]{{\bf \textcolor{blue}{[#1]}}}
+
 \makeatletter
@@
 \includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
-\caption{\label{fig:AGN_decomp} AGN-host galaxy decomposition of COSMOS-CID1174 based on the \hst/WFC3 F140W image.The panels from left to right are as follows: (1) observed data, (2) best-fit model (AGN$+$host), (3) data minus the model PSF (i.e., host galaxy free of the AGN), (4) residuals divided by the variance and (5)~1-D surface brightness profiles (top) and the corresponding residual (bottom).
+\caption{\label{fig:AGN_decomp} AGN-host galaxy decomposition of COSMOS-CID1174 based on the \hst/WFC3 F140W image.
+The panels from left to right are as follows: (1) observed data, (2) best-fit model (AGN$+$host), (3) data minus the model PSF (i.e., host galaxy free of the AGN), (4) residuals divided by the variance and (5)~1-D surface brightness profiles (top) and the corresponding residual (bottom).
 The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects).
@@
 
-We compare the morphology of AGNs host galaxies to inactive galaxies from the CANDELS imaging survey.
-We identify 4401 inactive galaxies within a redshift range ($1.2<z<1.7$), comparable to our AGN sample, whose \sersic\ measurements are provided by \citet{VDwel++2012} using \galfit.
-Their stellar masses are derived based on the 3-D-\hst/CANDELS spectroscopic survey~\citep{Momcheva2016, Brammer2012} and comparable to our AGN hosts ($9.5< \log (M_* /M_{\odot})< 11.5$; Section~\ref{sec:mm}).
+We compare the morphology of AGNs host galaxies to inactive galaxies from the \textcolor{red}{CANDELS survey~\citep{Grogin2011, Koekemoer2011}.} We identify 4401 inactive galaxies within a redshift range ($1.2<z<1.7$), comparable to our AGN sample, whose \sersic\ measurements are provided by \citet{VDwel++2012} using \galfit.
+Their stellar masses are derived based on the \textcolor{red}{3-D-\hst\ spectroscopic survey}~\citep{Momcheva2016, Brammer2012} and comparable to our AGN hosts ($9.5< \log (M_* /M_{\odot})< 11.5$; Section~\ref{sec:mm}).
 We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where we find no significant difference between their distributions and median value.

### 2019-11-13 NA_paper/manuscript_II/qso_paperII.tex
Update by TT's edits

@@
 \begin{abstract}
-Supermassive black holes (BH) are known to reside at the center of massive galaxies.
-In the local Universe, BH masses (\mbh) are tightly correlated to the properties of their host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar), known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar).
-The origin of this correlation is still not fully understood, and one promising way to reveal it is to use simulation.
-During the past few years, simulation have successfully reproduced the observational relations over the last eight billion years ($z\lesssim1$).
-However, due to the limitation of high-$z$ measurements, the simulations haven't yet make the comparison to the observations at earlier cosmic epochs ($z>1$), where the predictions are more sensitive to the initial assumptions and any inconsistency would help to pinpoint missing physics.
-For this purpose, we adopted a unique sample of 32 broad-line Active Galactic Nuclei (AGN) at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with the broad \halpha\ emission line as detected by Subaru/FMOS, providing an accurate assessment of \mbh, while multi-band \hst\ imaging is taken to derive the host galaxies properties (e.g., \mstar).
-We directly compare the measurements to two independent state-of-the-art simulations: \texttt{MassiveBlackII} (MBII) and semi-analytic model (SAM).
-Taking the selection biases into account, %by adopting the same selection function to choose the simulating sample,
-we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
-However, when considering the measurement uncertainty and comparing the scatters, the observations are significantly more consistent with the \mbii\ sample ($\sim0.3$~dex), than the \sam\ ($\sim0.7$~dex).
-{\color{red} In this respect, our observational constraints are able to distinguish the recipe adopted between the two projects.
-For example, in the \mbii, it is the AGN feedback that drives the scaling relations, while in the \sam\ it is galaxy merger driven.} Moreover, the intrinsic scatter of our high-$z$ sample is comparable to the local sample thus counter to the expectation from a scenario based on the central limit theorem (a purely stochastic process).
-To some extent, our result attests that it is the AGN feedback that establishs a causal link between SMBH and its host galaxy to induce an ordering so that the more massive black holes are tightly linked to the more massive galaxies.
+Supermassive black holes (SMBHs) ubiquitously occupy the center of massive galaxies in the local Universe and beyond.
+Their growth in mass (\mbh) appears to be closely linked to the physical properties of their host galaxies\cite{Mag++98, F+M00, M+H03, H+R04, Gul++09}, in particular the relation between \mbh ~and stellar mass.
+With the origin of this correlation far from being fully understood, simulations have been a promising means to further interpret the observations over the last eight billion years ($z\lesssim1$) thus enabling substantial progress in this field.
+Constraints at higher redshifts ($z>1$), when most of the SMBHs acquired their mass, are more sensitive to initial conditions and the growth meachanisms and thus may be able to identify inaccurate or missing physics in the models.
+For this purpose, we have constructed a unique sample of 32 actively-accreting SMBHs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with accurate BH and stellar masses with the latter based on multi-band \hst\ imaging.
+We directly compare the measurements with two independent state-of-the-art simulations: \texttt{MassiveBlackII} (MBII) and a semi-analytic model (SAM).
+After applying the observational selection function to models to account for bias, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
+However, accounting for observational errors, the dispersion in the mass ratio between \mbh~and \mstar~is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex) one.
+{\color{red} Hence, our observations can distinguish between the different recipes adopted in the models.
+The mass relations in \mbii\ are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to galaxy merger events.} Moreover, the intrinsic scatter in the mass ratio of our high-$z$ sample is comparable to that observed in local sample, all but ruling out the proposed scenario the correlations are purely stochastic in nature arising from some sort of cosmic central limit theorem.
+Our results support the hypothesis AGN feedback is responsible for a causal link between the SMBH and its host galaxy such that the mass of black holes and that of their host galaxies are tightly correlated.
 
@@
 %\section{Introduction}
-The discovery of the correlations between the masses (\mbh) of supermassive black holes (SMBH) and the properties of their host galaxies, such as absolute magnitude ($Mag$) and stellar mass (\mstar), indicates that the growth of SMBH could be connected to the formation of their host galaxies~\cite{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
-So far, the origin that drives this connection is still unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim$10 kpc).
-A possible physical link may be feedback from an Active Galactic Nucleus (AGN) phase, assuming that a small fraction of the AGN energy is injected into their surrounding gas that regulates the growth of the SMBH and its host galaxy.
+
+Various models have been proposed to explain the connection between SMBH and their host galaxies.
+A possible physical link may be feedback from an Active Galactic Nucleus (AGN) phase, assuming that a fraction of the AGN energy is injected into their surrounding gas thus regulating the growth of the SMBH and its host galaxy.
 In this scenario, AGN activity heats and unbinds a significant fraction of the gas and inhibits star formation.
-However, there are other models that have been proposed to explain the connection between SMBH and their hosts such as through an indirect manner where AGN accretion and star formation are fed through a common gas supply~\cite{Cen2015, Menci2016}.
-Furthermore, it has been proposed that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations without any direct physical mechanisms~\cite{Peng2007, Jahnke2011, Hirschmann2010}.
+An alternatively and more indirect connection is one where AGN accretion and star formation are fed through a common gas supply~\cite{Cen2015, Menci2016}.
+A completely different view holds that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations without any direct physical mechanisms~\cite{Peng2007, Jahnke2011, Hirschmann2010}.
 From the central limit theorem, a stochastic cloud at high-$z$ (higher dispersion) would end up with scaling relations as observed today with lower dispersion.
@@
 To understand this connection, recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have measured the scaling relations out to intermediate redshift {($0.3\lesssim z \lesssim1$)} by studying AGN and their host galaxies with {\it Hubble Space Telescope} ({\it HST}) and found an `observed' evolution in which the growth of SMBHs predates their host galaxies.
-However, the observational evidence of such evolution at high-$z$ is under debated since it depends on our understanding of systematic uncertainties and selection effects~\cite{Lauer2007}.
-It has been realized that an improper consideration of the uncertainties and selection effects will lead to an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.
+However, the observational evidence of such evolution at higher-$z$ is under debate since it depends on our understanding of systematic uncertainties and selection effects~\cite{Tre++07,Lauer2007}.
+Clearly, an improper consideration of the uncertainties and selection effects will lead to an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.
 
@@
 Simulations are effective at helping to understand this connection and rule out theories/assumptions that could not be definitively verified by observations alone.
-In particular, simulations can be used to quantify the impact of systematic uncertainties and selection biases with observational analysis.
-Recent studies, based on several simulation projects, have made predictions that are in good agreement with the observational data at intermediate redshifts ($z\lesssim1$).
+In particular, simulations can be used to quantify the impact of systematic uncertainties and selection biases with observational data.
+Recent studies, based on several simulations, show agreement with the observational data at intermediate redshifts ($z\lesssim1$).
 For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been utilized to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ that show a positive evolution where the SMBH growth predates that of its the host galaxy~\cite{DeG++15}.
@@
 Besides hydrodynamic simulations, semi-analytic models~\cite{Menci2014, Menci2016} have also made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}.
-However, to date, the comparisons to the observed scaling relations by high-resolution \hst\ imaging sample are still limited within $z<1$ due to the limitation of the observations.
+However, comparisons between simulations and the observed scaling relations, based on high-resolution \hst\ imaging, are still mostly limited to $z<1$ due to prior limitations of observational data.
 
@@
 	%mention the scatter.
-To extend the range, we have been studying a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from three X-ray coverage fields (D19~\cite{Ding2019} hereafter), including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}.
-The redshift range of our targets is chosen to be high enough ($z>1$) to detect the existence of the evolution offsets and make the comparison to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming.
+To push our knowledge of the mass relations to earlier epochs, we have been analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields (D19~\cite{Ding2019} hereafter), namely COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}.
+The redshift range of our targets is chosen to be high enough ($z>1$) to establish the mass ratios of accreting SMBHs and to make direct comparisons to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy.
 We selected our AGN sample in a well-defined window based on the \mbh\ and Eddington ratio, as shown in Figure~1 in D19.
 As shown in that Figure, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias.
-In addition, the Eddington ratios are mostly above $0.1$ to ensure the homogeneity.
+In addition, the Eddington ratios are mostly above $0.1$ to ensure homogeneity.
 
-We measure reliable \mbh\ and host properties to overcome the systematic.
-Specifically, the \mbh\ of our sample are estimated using the published near-infrared spectroscopic observations of the broad \halpha\ emission lines, which removes the systematic with \Mgii\ or \Civ.
-For the inference of properties of the host galaxies, the X-ray selected sample has lower nuclear-to-host ratios at IR band, which facilitates the inference of the host light.
-We employ the \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt the state-of-the-art technique to perform the 2-D flux profile decomposition to infer the light of the host galaxy.
+We measure reliable \mbh\ and host properties (i.e., \mstar) with a quantitative assessment of systematic effects.
+Specifically, \mbh\ is determined using published near-infrared spectroscopic observations of the broad \halpha\ emission line, which eliminates potential systematic uncertainties that may arise from switching to Balmer lines in the local universe to the \Mgii\ or \Civ UV lines for distant galaxies.
+Regarding the detection of the host galaxies, the X-ray selected nature of the sample results in slightly lower nuclear-to-host ratios, which facilitates the inference of the host light.
+We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy.
 Moreover, 21/23 systems have \hst/ACS imaging data, which enable us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see Methods and the descriptions in D19).
@@
 
-To make the comparison, we adopt two independent simulation projects, including \texttt{MassiveBlackII} (MBII)~\cite{Khandai2015} and semi-analytic models (SAM)~\cite{Menci2014}.
-These two simulations are based on independent model strategies, i.e., hydrodynamic simulation for \mbii\ and semi-analytic model for \sam, respectively.
+To compare with simulations, we use two independent efforts, \texttt{MassiveBlackII} (MBII)~\cite{Khandai2015} and a semi-analytic model (SAM)~\cite{Menci2014}.
+These simulations are based on independent model strategies, i.e., hydrodynamic simulation for \mbii\ and semi-analytic model for \sam, respectively.
 The \mbii\ simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
-The large simulation volume enables the simulating objects to evolve independently; the high enough mass and spatial resolution meet the requirements for the object details.
-On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems.
-However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as \sam.
+The large simulation volume enables the model galaxies and SMBHs to evolve independently; the large dynamic range in mass and high spatial resolution meet the requirements to investigate their individual galaxies.
+While high-resolution N-body simulations can study specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam.
 In previous works, \mbii~\cite{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\cite{Menci2014, Menci2016} have made high successful predictions, and we refer the interested readers to the Method section for more details.
@@
 %Selection effect into account
-Based on \mbii\ project, we collect a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones.
-We take the measurement uncertainty and the selection effect into account to ensure a fair comparison,  with the following process.
-First, we inject the random noise to the simulated sample to mimic the scattering effect caused by the uncertainty.
-We assume uncertainties are comparable to the realistic levels, i.e., $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex, and $\Delta L_{\rm bol}$=0.03~dex, respectively.
-We then select the sample that falls into the same targeting window to mimic the realistic sample selection process, as shown in Figure~\ref{fig:selectfunc}.
-Considering that the mass relations between SMBH and its host are more substaintial, we focus on the predicted \mbh-\mstar relations and compared to the observational constraints, as shown in Figure~\ref{fig:MM_comp} (left panel).
-From a quick glimpse, one can see that the samples are overlapped with each other, showing a sign of agreement.
-To quantify the agreement level, we perform the linear regression to fit the simulated relations and estimate the best-fit inference and 1$-\sigma$ confidence interval.
-To make direct comparison, we fix the same slope value and obtain the best-fit intercept value for the observation.
-We find that, for the \mbh-\mstar\ relations, there is a notable mismatch ($\sim0.4$~dex), however within 1$-\sigma$ level.
-Furthermore, we compare the scatter of the sample by calculating the standard derivation of the residual in the linear regression.
-We find that the simulations and the observations have the same scatter level $0.3$~dex.
-Considering that the simulated samples have the same uncertainty and the selection effect, we expect the intrinsic scatter of the scaling relations are similar, which is $0.25$~dex (see METHODS).
+Using \mbii\, we identify a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones.
+We take the measurement uncertainty and selection biases into account to ensure a fair comparison.
+First, we inject random noise to the simulated sample to mimic the scatter in our data due to measurement errors, i.e., $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex, and $\Delta L_{\rm bol}$=0.03~dex, respectively.
+We then select the sample that falls into the same targeting window to match the observed sample (Figure~\ref{fig:selectfunc}).
+
+In Figure~\ref{fig:MM_comp} (left panel), we compare the relation \mbh--\mstar~between observations and the \mbii\ simulation.
+First, it is clear that the simulated and observed samples are in good agreement.
+To quantify the agreement level, we perform a linear regression to fit the simulated relations and estimate the best-fit inference and 1$-\sigma$ confidence interval.
+To make a direct comparison, we fix the same slope value and obtain the best-fit intercept value for the observation.
+We find that the \mbh-\mstar\ relations are in agreement within the relatively large uncertainties.
+Furthermore, we compare the scatter of the sample by calculating the standard derivation of the residuals of the linear regression.
+We find that the simulations and the observations have the same amount of scatter $0.25-0.3$~dex.(see METHODS).
 
@@
 \caption{The same selection window as adopted for selecting the \mbii\ simulated sample.
-The brown background clouds shows the overall \mbii\ sample at $z=1.5$.
+The brown background cloud shows the overall \mbii\ sample at $z=1.5$.
 We add the random uncertainty to the simulation and select the ones fall into the targeting region (i.e.
@@
 \end{tabular}
-\caption{In the left panel, we present the comparison of the  \mbh-\mstar\ correlation between the observation (orange dots) and the \mbii\ predicted samples (blue dots).
-The predicted sample is treated to have the same uncertainty and selection effect as the observational ones.
+\caption{(Left) Comparison of the observed (orange dots) and simulated (blue dots) \mbh--\mstar\ relation.
 The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the $1-\sigma$ confidence interval.
-We use the same slope value to fit for the observed sample, and the orange line shows the best-fit result.
-The brown grids in the background are the overall sample that predicted by the \mbii\ simulation.
-We present the comparison with the \sam\ sample (green color) in the right panel.
-}
+By fixing the slope to match the simulated data, the orange line shows the best-fit result for the observed data set.
+The grey cells in the background show the full \mbii\ simulated SMBHs.
+(Right) The equivalent plot is displayed for the \sam\ sample (green color) in the right panel.}
 \label{fig:MM_comp}
@@
 
-We also make comparisons of our observed scaling relations to the predictions by the \sam\ model.
+We also compare our data to the predictions by the \sam\ model.
 Rather than N-body simulation which produces individual simulating objects, the \sam\ model uses the density clouds to describe the possibility of the samples.
@@
 %Yet this is not a proper comparison since the direct sample from \sam\ does not include the scattering effect by the measurement uncertainty.
-To make the direct comparison, we first randomly generate an overall \sam\ sample based on the possibility clouds at $z=1.5$ epoch.
-Then, same as the process in \mbii\ analysis, we inject the random uncertainty to the sample to take the uncertainty effect into account and select the sample the selection window.
+To make a direct comparison, we first randomly generate an overall \sam\ sample based on the probability clouds at $z=1.5$.
+Then, as in the \mbii\ analysis, we inject random scatter in the sample to account for uncertainties and apply the observational selection function.
 The resulting comparison of the  \mbh-\mstar\ relation are shown in Figure~\ref{fig:MM_comp} (right panel).
 We find that the best-fit result by the \sam\ model is well matched to the observation.
-However, the scatter of the \sam\ model are overwhelmingly larger ($0.7$~dex) than the observation.
-This larger scatter is a combination result by the \sam\ distribution, uncertainty, and selection effect.
+However, the scatter of the \sam\ model is significantly larger ($0.7$~dex) than observed (this is the total scatter accounting for the intrinsic scatter in the \sam\ distribution, observational uncertainties, and selection effects).
 
@@
 For the simulated sample, we consider the AGN bolometric correction~\cite{Elvis1994} to estimate the AGN light flux at WFC3/F125W band.
-We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched each other.
+We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched to each other.
 The median values for the flux ratio distribution of the observed, \mbii, \sam\ sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively.
 We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are 0.34 (for observed -- \mbii) and 0.14 (for observed -- \sam), respectively.
-This result indicates the three samples have similar host-to-total light distribution.
+This result indicates the three samples have similar host-to-total light ratio distribution.
 
@@
 \includegraphics[width=0.9\linewidth]{comp_host_ratio.pdf}
-\caption{The comparison histogram of the host ratios among three referred samples, median value indicated. The same selection effect are considered for the simulation sample.
+\caption{Comparison of the host to total flux ratio distribution for the three referred samples, median value indicated.
+The observational selection function is applied to the simulated samples to allow for a fair comparison.
 }
@@
 
-{\bf In terms of their central distribution, the \mbii\ simulation and \sam\ model both demonstrate an excellent agreement to the observational constraints.
-When considering the scattering effect by the measurement uncertainty, the scatter in \mbii\ simulation is consistent to the observational one ($\sim0.3$~dex); however, \sam\ sample has much larger scatter ($\sim0.7$~dex).
-Given that the two models adopt different assumptions, recipes, and initial conditions, our result shows that the mechanism by \mbii\ is more favorable, in which it is the AGN feedback that drives the scaling relation \ding{To Aklant and Tiziana, do you agree with this statement?}.
-Though \sam\ model also consider the AGN feedback, the feeding process for the SMBH accretion is still galaxies merger driven with more stochasticities in the scaling relations, which may leads to the larger scatter.
-In particular, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the
-encounter.
+{\bf In terms of their central distribution, the \mbii\ simulation and \sam\ model are both in agreement with the observational data.
+However, the scatter distinguishes between the two models.
+The  the scatter in \mbii\ simulation is consistent to the observational one ($\sim0.3$~dex), while \sam\ sample has significantly larger scatter ($\sim0.7$~dex).
+Thus, the implementation of AGN feedback in \mbii\ passes our stringent observational test.
+The \sam\ model also consider the AGN feedback.
+However, in contrast to \mbii, the feeding process for the SMBH accretion is driven by galaxy mergers, and thus may be more stochastic and lead to the larger scatter.
+More specifically, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the  encounter.
 This introduces additional scatter since it depends on the properties of both interacting galaxies (see Method).
 As a result, the \sam\ cloud extends to the high \mbh\ with low stellar mass, which may not exist.
-\ding{To Nicola: do you want to include your new 2D model in the paper?} The consistency between \mbii\ and observations indicates that there has to be a causal link (i.e., AGN feedback) between SMBH and its host galaxy to generate an ordering during their evolution; as a result, more massive BHs are linked to more massive galaxies {\it tightly}.
+\ding{To Nicola: do you want to include your new 2D model in the paper?} The consistency between \mbii\ and observations provides important observational evidence in support of the hypothesis that there is a causal link (i.e., AGN feedback) between the evolution of SMBH and that of their host galaxies.
 }
 
-Without any physical mechanisms, the central limit theorem~\cite{Peng2007, Jahnke2011, Hirschmann2010} assumes that the scaling relations are caused by the random merger from a stochastic cloud at earlier universe.
-In this scenario, the scatter of the scaling relations has to be larger with the increasing of redshift.
-However, the observed scatter of our high-$z$ sample do not present this feature.
-In fact, our inferred intrinsic scatter of the observed sample is $\sim0.25$~dex, which is no more than the typical scatter at local relations in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}.
-Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level for the real data.
-Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), resulting in an overestimating of the error-budget and thus underestimating of intrinsic scatter.
-Still, the evidence of the low scatter in our measurements is likely to be true, which is against the central limit theorem and suggests that the physical mechanisms between the SMBH and its host galaxy are likely to exist.
+Without any physical mechanisms, it has been shown that just due to the the central limit theorem~\cite{Peng2007, Jahnke2011, Hirschmann2010} scaling relations may emerge from random mergers, starting from a stochastic cloud in the early universe.
+In this scenario, the scatter of the scaling relations has to increase with redshift.
+Our observations contradict this hypothesis.
+In fact, our inferred intrinsic scatter of the observed sample is $\sim0.25$~dex, which is no more than the typical scatter of local relations reported in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}.
+Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level for the real data, but it is unlikely that systematic errors would conspire to {\it reduce} scatter.
+Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), resulting in an overestimating of the error-budget and thus underestimating of intrinsic scatter, but again it is hard to imagine that the \halpha\ \mbh\ estimators be much more precise than an factor of two.
 
-Extending the redshift range of this study would be very beneficial to this study, giving that the scaling relation in the simulations shows different evolution at the different stage of the universe.
+Extending this study to even higher redshift would be very beneficial, probing closer to the epoch of formation of massive galaxies and supermassive blackes.
 For higher redshift, the {\it James Webb Space Telescope} may provide high-quality imaging data of AGNs at redshift up to $z\sim7$.
@@
 %1. Imaging data. 2. Inferring host light. 3. Color inference. Rest frame R band and stellar mass.
-The detailed description for the analysis is in the companion paper (referring as D19).
-Here we only present a quick overview of this study.
+A detailed description of the \hst\ data analysis can be found in a companion paper (D19).
+Here we only present a brief summary of that study.
 We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ (according to the redshift of the targets) to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman).

### 2019-11-19 NA_paper/manuscript_II/qso_paperII.tex
Before edit NA paper

@@
 \usepackage{float}
+\usepackage{soul}
 
@@
 \newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}} 
-
+\newcommand{\aklant}[1]{\textcolor{blue}{[{\bf AKB}: #1]}} 
 \title{
@@
 Tommaso Treu$^{1}$, 
-John Silverman$^{3, 4}$,
+John D. Silverman$^{3, 4}$,
 Aklant K. Bhowmick$^{5}$,
@@
 With the origin of this correlation far from being fully understood, simulations have been a promising means to further interpret the observations over the last eight billion years ($z\lesssim1$) thus enabling substantial progress in this field.
-Constraints at higher redshifts ($z>1$), when most of the SMBHs acquired their mass, are more sensitive to initial conditions and the growth meachanisms and thus may be able to identify inaccurate or missing physics in the models.
+Constraints at higher redshifts ($z>1$), when most of the SMBHs acquired their mass, are more sensitive to initial conditions and the growth mechanisms and thus may be able to identify inaccurate or missing physics in the models.
 For this purpose, we have constructed a unique sample of 32 actively-accreting SMBHs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with accurate BH and stellar masses with the latter based on multi-band \hst\ imaging.
-We directly compare the measurements with two independent state-of-the-art simulations: \texttt{MassiveBlackII} (MBII) and a semi-analytic model (SAM).
+We directly compare the measurements with two independent state-of-the-art simulations: \texttt{MassiveBlackII} (MBII) \aklant{hydrodynamic simulation} and a semi-analytic model (SAM).
 After applying the observational selection function to models to account for bias, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
@@
 {\color{red} Hence, our observations can distinguish between the different recipes adopted in the models.
-The mass relations in \mbii\ are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to galaxy merger events.} Moreover, the intrinsic scatter in the mass ratio of our high-$z$ sample is comparable to that observed in local sample, all but ruling out the proposed scenario the correlations are purely stochastic in nature arising from some sort of cosmic central limit theorem.
-Our results support the hypothesis AGN feedback is responsible for a causal link between the SMBH and its host galaxy such that the mass of black holes and that of their host galaxies are tightly correlated.
+The mass relations in \mbii ~are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to galaxy merger events.} Moreover, the intrinsic scatter in the mass ratio of our high-$z$ sample is comparable to that observed in local sample, all but ruling out the proposed scenario the correlations are purely stochastic in nature arising from some sort of cosmic central limit theorem.
+Our results support the hypothesis \aklant{of} AGN feedback \st{is} \aklant{being} responsible for a causal link between the SMBH and its host galaxy \st{such that the mass of black holes and that of their host galaxies are tightly correlated} \aklant{resulting in a tight correlation between their respective masses}.
 
@@
 However, the observational evidence of such evolution at higher-$z$ is under debate since it depends on our understanding of systematic uncertainties and selection effects~\cite{Tre++07,Lauer2007}.
-Clearly, an improper consideration of the uncertainties and selection effects will lead to an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.
+\st{Clearly} \aklant{Therefore}, an improper consideration of the uncertainties and selection effects \st{will} may lead to an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.
+\aklant{Comment: `Overestimate of the evolution' sounds a bit odd.
+Consider rewriting this last sentence}
 
@@
 %The reason to extend to high redshift.
-Simulations are effective at helping to understand this connection and rule out theories/assumptions that could not be definitively verified by observations alone.
+Simulations are effective at helping to understand this connection and rule out theories/ assumptions that could not be definitively verified by observations alone.
 In particular, simulations can be used to quantify the impact of systematic uncertainties and selection biases with observational data.
@@
 We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy.
-Moreover, 21/23 systems have \hst/ACS imaging data, which enable us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see Methods and the descriptions in D19).
+Moreover, 21/23 systems have \hst/ACS imaging data, which enable us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see METHODS and the descriptions in D19).
 %We furthermore combining them with the ground-based photometry to carry out the SED fitting, and thus derive the reliable host rest-frame R band luminosity and stellar mass.
@@
 While high-resolution N-body simulations can study specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam.
-In previous works, \mbii~\cite{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\cite{Menci2014, Menci2016} have made high successful predictions, and we refer the interested readers to the Method section for more details.
+In previous works, \mbii~\cite{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\cite{Menci2014, Menci2016} have made high successful predictions, and we refer the interested readers to the METHODS section for more details.
 
@@
 First, it is clear that the simulated and observed samples are in good agreement.
-To quantify the agreement level, we perform a linear regression to fit the simulated relations and estimate the best-fit inference and 1$-\sigma$ confidence interval.
+{\bf To quantify the agreement level, we perform a linear regression to fit the simulated relations and estimate the best-fit inference.
 To make a direct comparison, we fix the same slope value and obtain the best-fit intercept value for the observation.
-We find that the \mbh-\mstar\ relations are in agreement within the relatively large uncertainties.
-Furthermore, we compare the scatter of the sample by calculating the standard derivation of the residuals of the linear regression.
-We find that the simulations and the observations have the same amount of scatter $0.25-0.3$~dex.(see METHODS).
+We find that the \mbh-\mstar\ relations are in agreement within the relatively large scatter of the sample.} Furthermore, we compare the scatter by calculating the standard derivation of the residuals of the linear regression.
+We find that the simulations and the observations have the same amount of scatter $0.25-0.3$~dex (see METHODS).
 
@@
 \caption{(Left) Comparison of the observed (orange dots) and simulated (blue dots) \mbh--\mstar\ relation.
-The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the $1-\sigma$ confidence interval.
+The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the {\bf standard derivation of the sample}.
 By fixing the slope to match the simulated data, the orange line shows the best-fit result for the observed data set.
@@
 
-{\bf In terms of their central distribution, the \mbii\ simulation and \sam\ model are both in agreement with the observational data.
+In terms of their central distribution, the \mbii\ simulation and \sam\ model are both in agreement with the observational data.
 However, the scatter distinguishes between the two models.
@@
 More specifically, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the  encounter.
-This introduces additional scatter since it depends on the properties of both interacting galaxies (see Method).
+This introduces additional scatter since it depends on the properties of both interacting galaxies (see METHODS).
 As a result, the \sam\ cloud extends to the high \mbh\ with low stellar mass, which may not exist.
 \ding{To Nicola: do you want to include your new 2D model in the paper?} The consistency between \mbii\ and observations provides important observational evidence in support of the hypothesis that there is a causal link (i.e., AGN feedback) between the evolution of SMBH and that of their host galaxies.
-}
 
@@
 
-\textbf{Imaging data, decomposition and inference of host properties.} 
+\textbf{HST Observations.} 
 %1. Imaging data. 2. Inferring host light. 3. Color inference. Rest frame R band and stellar mass.
@@
 
-21/32 images in the COSMOS survey also have imaging data in the ACS/F814W with drizzled pixel scale as 0\farcs03, providing us the multi-band information.
+The COSMOS survey provides \hst\ ACS/F814W imaging data for 21 of 32 AGN in our sample with a drizzled pixel scale as 0\farcs03.
 We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3's result to infer the host color.
-{\bf We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the rest-frame R band luminosity and stellar mass.} A Salpeter initial mass function is employed consistently to the observed and simulated sample.
+We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the rest-frame R band luminosity and stellar mass.
+A Salpeter initial mass function is employed consistently to the observed and simulated sample.
 
@@
 
-\textbf{The \texttt{MassiveBlackII} (\mbii) simulation}.  
-\mbii\ is a high-resolution cosmological hydrodynamic simulation which ran from $z~=~159$ to $z~=~0.06$ using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\cite{2005MNRAS.364.1105S}.
+\textbf{\texttt{MassiveBlackII} (\mbii) simulation}.  
+\mbii\ is a high-resolution cosmological hydrodynamic simulation using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\cite{2005MNRAS.364.1105S}.
 It has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles.
@@
 
-For the modeling of black hole growth and associated feedback, we adopt the prescription in the reference \cite{2005Natur.433..604D, 2005MNRAS.361..776S}.
+For the modeling of black hole growth, a feedback prescription is adopted as detailed in the literature \cite{2005Natur.433..604D, 2005MNRAS.361..776S}.
 In particular, seed black holes of mass $5\times 10^{5}~M_{\odot}/h$ are inserted into haloes of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$~(if they do not already contain a black hole).
@@
 The galaxy SEDs are finally convolved with the desired filter function to obtain the broad band photometry~(SDSS $r$ band magnitude).
+For further details regarding the \mbii\ simulation, we refer the reader to the reference~\cite{2015MNRAS.450.1349K}.
 
-For more details regarding the \mbii\ simulation, we refer the reader to the reference~\cite{2015MNRAS.450.1349K}.
-
-\textbf{The semi-analytic model (\sam)}. The \sam\ is based on the description in Menci et al. (2016)~\cite{Menci2016}, to which we refer for details; here we recall its key points. 
-The merging trees of dark matter haloes are generated through a Monte Carlo procedure adopting the merging rates given by the Extended Press \& Schechter formalism~\cite{Lacey1993} assuming a Cold Dark Matter power spectrum of perturbations.
-For each dark matter halo included into a larger halo we computed the dynamical friction process, to  determine whether it will survive as a satellite, or sink to the centre to increase the mass of the central dominant galaxy; binary interactions (fly-by and merging) among satellite sub-halos are also described by the model.
-In each halo, we compute the amount of gas which cools due to atomic processes.
-The cooled gas  settles into a rotationally supported disc as the descriptions in the reference~\cite{Mo1998}.
-The gas is converted into stars through three different channels: quiescent star formation, gradually converting the gas into stars over long timescales $\sim 1$~Gyr; starbursts following galaxy interactions, occurring on timescales $\lesssim 100$~Myr, associated to BH feeding; internal disc instabilities triggering loss of angular momentum resulting into gas inflows toward the centre, therefore feeding star formation and BH accretion.
-The energy released by the Supernovae associated to the total star formation returns a fraction of the disc gas into the hot phase (stellar feedback).
+\textbf{Semi-analytic model (\sam)}.
+The \sam\ is fully described in Menci et al.
+(2016)~\cite{Menci2016}.
+Here, we highlight the main points with respect to our study.
+The merger trees of dark matter haloes are generated through a Monte Carlo procedure by adopting merger rates using an Extended Press \& Schechter formalism~\cite{Lacey1993} assuming a Cold Dark Matter power spectrum of perturbations.
+For dark matter halos  that merge with a larger halo, we assess the impact of dynamical friction to determine whether it will survive as a satellite, or sink to the centre to increase the mass of the central dominant galaxy; binary interactions (fly-by and merging), among satellite sub-halos, are also described by the model.
+In each halo, we compute the amount of gas which cools due through atomic processes and settles into a rotationally-supported disk~\cite{Mo1998}.
+The gas is converted into stars through three different channels: (1) quiescent star formation gradually converting the gas into stars over long timescales $\sim 1$~Gyr, (2) starbursts following galaxy interactions, occurring on timescales $\lesssim 100$~Myr, associated to BH feeding, (3) internal disc instabilities triggering loss of angular momentum resulting into gas inflows toward the centre thus feeding star formation and BH accretion.
+The energy released by the supernovae associated with the total star formation returns a fraction of the disc gas into a hot phase (stellar feedback).
 
@@
 We consider two BH feeding modes: accretion triggered by galaxy interactions and internal disc instabilities.
-These are described in detail in our previous work~\cite{Menci2016}, and briefly recalled below.\newline
+These are described in detail in our previous work~\cite{Menci2016}, and briefly described below.\newline
 1) BH accretion triggered by interactions.

### 2019-11-19 NA_paper/scripts/my_selection_plots_SAM.py

@@ -21,6 +21,7 @@ mat.rcParams['font.family'] = 'STIXGeneral'
 np.random.seed(5)  #12345
 
 data_overall = np.loadtxt('../Nicola/realization/lagn_lhost1.dat')
+#data_overall = np.loadtxt('../Nicola/realization/lagn_lhost_2D.dat')
 
 bhmass_overall=data_overall[:,-1]
 Lbol_overall=np.log10(data_overall[:,-2]*10**45.)
@@ -182,7 +183,7 @@ x_space=lfit(y_space,fit[0][0],fit[0][1])   #y_space become to x_space
 plt.plot(x_space, y_space, color='green',linewidth=3)
 x_space_ub=lfit(y_space,fit[0][0]+fit_err[0]/2,fit[0][1]+fit_err[1]/2)
 x_space_lb=lfit(y_space,fit[0][0]-fit_err[0]/2,fit[0][1]-fit_err[1]/2)
-plt.fill_betweenx(y_space,x_space_lb,x_space_ub,color='green',alpha=0.15)
+#plt.fill_betweenx(y_space,x_space_lb,x_space_ub,color='green',alpha=0.15)
 def lfit_fixm(y,c):
     m_0 = fit[0][0]
     return m_0*y+c
@@ -193,6 +194,14 @@ x_obs_space=lfit_fixm(y_space,fit_fixm[0])
 plt.plot(x_obs_space,y_space,color='orange',linewidth=3)
 print "mismatch:", fit_fixm[0]- fit[0][1]  #In BH mass offset space
 
+# Plot the fitting scatter 
+x_space_ub=lfit(y_space,fit[0][0],fit[0][1]+0.72)     #Values are measured in the next box
+x_space_lb=lfit(y_space,fit[0][0],fit[0][1]-0.72)
+plt.fill_betweenx(y_space,x_space_lb,x_space_ub,color='green',alpha=0.35)
+#print "mismatch:", fit_fixm[0]- fit[0][1]  #In BH mass offset space
+x_space_ub=lfit_fixm(y_space,fit_fixm[0]+0.3247)
+x_space_lb=lfit_fixm(y_space,fit_fixm[0]-0.3247)
+plt.fill_betweenx(y_space,x_space_lb,x_space_ub,color='orange',alpha=0.35)
 
[…]

### 2019-11-20 NA_paper/manuscript_II/qso_paperII.tex
TT edit based on Aklant and Nicola comments.

@@
 For this purpose, we have constructed a unique sample of 32 actively-accreting SMBHs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with accurate BH and stellar masses with the latter based on multi-band \hst\ imaging.
-We directly compare the measurements with two independent state-of-the-art simulations: \texttt{MassiveBlackII} (MBII) \aklant{hydrodynamic simulation} and a semi-analytic model (SAM).
+We directly compare the measurements with two independent state-of-the-art project, the hydrodynamic simulation \texttt{MassiveBlackII} (MBII) and the semi-analytic model (SAM).
 After applying the observational selection function to models to account for bias, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
 However, accounting for observational errors, the dispersion in the mass ratio between \mbh~and \mstar~is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex) one.
-{\color{red} Hence, our observations can distinguish between the different recipes adopted in the models.
-The mass relations in \mbii ~are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to galaxy merger events.} Moreover, the intrinsic scatter in the mass ratio of our high-$z$ sample is comparable to that observed in local sample, all but ruling out the proposed scenario the correlations are purely stochastic in nature arising from some sort of cosmic central limit theorem.
-Our results support the hypothesis \aklant{of} AGN feedback \st{is} \aklant{being} responsible for a causal link between the SMBH and its host galaxy \st{such that the mass of black holes and that of their host galaxies are tightly correlated} \aklant{resulting in a tight correlation between their respective masses}.
+Hence, our observations can distinguish between the different recipes adopted in the models.
+The mass relations in \mbii ~are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to galaxy merger events triggering nuclear activity.
+Moreover, the intrinsic scatter in the mass ratio of our high-$z$ sample is comparable to that observed in local sample, all but ruling out the proposed scenario the correlations are purely stochastic in nature arising from some sort of cosmic central limit theorem.
+Our results support the hypothesis of AGN feedback being responsible for a causal link between the SMBH and its host galaxy resulting in a tight correlation between their respective masses.
 
@@
 However, the observational evidence of such evolution at higher-$z$ is under debate since it depends on our understanding of systematic uncertainties and selection effects~\cite{Tre++07,Lauer2007}.
-\st{Clearly} \aklant{Therefore}, an improper consideration of the uncertainties and selection effects \st{will} may lead to an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.
-\aklant{Comment: `Overestimate of the evolution' sounds a bit odd.
-Consider rewriting this last sentence}
+Therefore, an improper consideration of the uncertainties and selection effects may lead to an {\it apparent} evolution and result in an overestimate of the significance of the evolution\cite{Volonteri2011}.
 
@@
 We measure reliable \mbh\ and host properties (i.e., \mstar) with a quantitative assessment of systematic effects.
-Specifically, \mbh\ is determined using published near-infrared spectroscopic observations of the broad \halpha\ emission line, which eliminates potential systematic uncertainties that may arise from switching to Balmer lines in the local universe to the \Mgii\ or \Civ UV lines for distant galaxies.
+Specifically, \mbh\ is determined using published near-infrared spectroscopic observations of the broad \halpha\ emission line, which eliminates potential systematic uncertainties that may arise from switching to Balmer lines in the local universe to the \Mgii\ or \Civ\ UV lines for distant galaxies.
 Regarding the detection of the host galaxies, the X-ray selected nature of the sample results in slightly lower nuclear-to-host ratios, which facilitates the inference of the host light.
@@
 
+{\bf We note that the absolute determination of stellar mass carries significant uncertainty, both observationally and theoretically.
+Depending on definitions of stellar mass, on the assumed initial mass function, and possibly on the implementation of star formation in the models, the absolute value of \mstar (hence the absolute normalization, i.e., \mbh/\mstar) can vary by up to a factor of two.
+In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by this uncertainty.
+Thus, in this work, we mainly focus on the scatter as a diagnostic tool, even though in the future more information could be extracted by this kind of comparison if the %absolute stellar mass could be constrained more accurately in the simulations.}
+better measures~(i.e. more consistent with techniques for determining observed \mstar) of stellar masses can be defined for the simulated galaxies.}
+
 %\section*{Results}
@@
 First, it is clear that the simulated and observed samples are in good agreement.
-{\bf To quantify the agreement level, we perform a linear regression to fit the simulated relations and estimate the best-fit inference.
+To quantify the agreement level, we perform a linear regression to fit the simulated relations and estimate the best-fit inference.
 To make a direct comparison, we fix the same slope value and obtain the best-fit intercept value for the observation.
-We find that the \mbh-\mstar\ relations are in agreement within the relatively large scatter of the sample.} Furthermore, we compare the scatter by calculating the standard derivation of the residuals of the linear regression.
+We find that the \mbh-\mstar\ relations are in agreement within the relatively large scatter of the sample.
+Furthermore, we compare the scatter by calculating the standard derivation of the residuals of the linear regression.
 We find that the simulations and the observations have the same amount of scatter $0.25-0.3$~dex (see METHODS).

### 2019-11-20 manuscript/manuscript.tex
For the final submission, bf version

--- 2019-10-25 manuscript/manuscript.tex
@@
 
+\newcommand{\red}[1]{{\bf \textcolor{red}{[#1]}}}
+\newcommand{\blue}[1]{{\bf \textcolor{blue}{[#1]}}}
+
 \makeatletter
@@
 
-Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., {\bf total} stellar mass \smass, luminosity \lhost) suggest an evolutionary connection.
+Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., total stellar mass \smass, luminosity \lhost) suggest an evolutionary connection.
 A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates.
-For this purpose, we {\bf acquired} {\it Hubble Space Telescope} imaging with WFC3 of 32 \hbox{X-ray-selected} broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
-By applying state-of-the-art tools to decompose the \hst\ images {\bf including available ACS data}, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting.
+For this purpose, we acquired {\it Hubble Space Telescope} imaging with WFC3 of 32 \hbox{X-ray-selected} broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields.
+By applying state-of-the-art tools to decompose the \hst\ images including available ACS data, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting.
 The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators.
-We find {\bf that} the {\it observed} ratio {\bf of \mbh\ to total \smass\ is $2.7\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs.
-{\bf A non-evolving mass ratio is consistent with the data at the 2-3$\sigma$ confidence level when accounting for selection effects (estimated using two independent and complementary methods), and their uncertainties.} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
-Therefore, our results {\bf cannot distinguish whether SMBHs and their total host stellar mass and luminosity proceed in lockstep or whether the growth of the former somewhat overshoots the latter, given the uncertainties.
-Based on a statistical estimate} of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is {\bf offset from the local value by a factor of $\sim7$ which} is significant even accounting for selection effects.
+We find that the {\it observed} ratio of \mbh\ to total \smass\ is $2.7\times$ larger at $z\sim1.5$ than in the local universe, while the scatter is equivalent between the two epochs.
+A non-evolving mass ratio is consistent with the data at the 2-3$\sigma$ confidence level when accounting for selection effects (estimated using two independent and complementary methods), and their uncertainties.
+The relationship between \mbh\ and host galaxy total luminosity paints a similar picture.
+Therefore, our results cannot distinguish whether SMBHs and their total host stellar mass and luminosity proceed in lockstep or whether the growth of the former somewhat overshoots the latter, given the uncertainties.
+Based on a statistical estimate of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is offset from the local value by a factor of $\sim7$ which is significant even accounting for selection effects.
 Taken together, these observations are consistent with a scenario in which stellar mass is subsequently transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than mass accretion onto the SMBH.
@@
 
-Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to {\bf correlate} with the host properties, such as luminosity (\lhost), stellar mass (\smass), and stellar velocity dispersion (\sigstar).
+Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to correlate with the host properties, such as luminosity (\lhost), stellar mass (\smass), and stellar velocity dispersion (\sigstar).
 The tightness of these correlations (also known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
@@
 
-To understand the nature of these correlations, it is important to study them as a function of redshift, determining how and when they {\bf emerge and evolve} over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}.
+To understand the nature of these correlations, it is important to study them as a function of redshift, determining how and when they emerge and evolve over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}.
 During the past decade, there has been much progress on this front using type-1 AGNs.
-For example, it has been demonstrated that {\bf AGN host galaxies, at $z<1$ and for fixed \mbh, are} under luminous compared to today's hosts \citep{Park15, Tre++07, Pen++06qsob}.
+For example, it has been demonstrated that AGN host galaxies, at $z<1$ and for fixed \mbh, are under luminous compared to today's hosts \citep{Park15, Tre++07, Pen++06qsob}.
 Similarly, \citet{Bennert11} and \citet{Woo++08} found a positive evolution of \mbh, especially when the data are sufficiently robust to isolate the luminosity or stellar mass of the bulge or spheroidal component.
@@
 If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.
-A possible mechanism to account for the latter part of the growth of the galaxy without increasing \mbh\ is the transfer of stellar mass from the disk to the {\bf bulge \citep{Jah++09,Bennert++2011,SS13} through} bar instabilities or minor mergers.
+A possible mechanism to account for the latter part of the growth of the galaxy without increasing \mbh\ is the transfer of stellar mass from the disk to the bulge \citep{Jah++09,Bennert++2011,SS13} through bar instabilities or minor mergers.
 
@@
 Second, measurements of the host galaxy properties are challenging due to the overwhelming glare of the bright nuclear light.
-This ultimately requires careful modeling of the point spread function and, whenever possible, the use of lensed {\bf AGNs} since the magnification increases the spatial resolution \citep{Pen++06qsob, Ding2017a, Ding2017b}.
+This ultimately requires careful modeling of the point spread function and, whenever possible, the use of lensed AGNs since the magnification increases the spatial resolution \citep{Pen++06qsob, Ding2017a, Ding2017b}.
 Especially not to be overlooked as in past studies, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}.
@@
 To date, the infrared capabilities of \hst/WFC3 have not been fully exploited on this topic.
-Here, we measure the properties of 32 host galaxies {\bf with} a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS.
+Here, we measure the properties of 32 host galaxies with a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS.
 Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e., $\sim0.23$ dex,][]{Schulze2014}.
 This value is the minimum offset expected for a non-evolving mass ratio as described in Section~\ref{sec:sf_framework}.
-{\bf Furthermore, we collect from the literature comparison samples of intermediate-$z$ and local AGN, selected to have been analyzed with very similar methods to those applied in the distant sample.
-We recalibrate the relevant quantities from the literature based on a set of self-consistent recipes to ensure that our differential measurement of evolution is robust to calibration and methodological issues (Section~\ref{sec:compare_sample}).}
+Furthermore, we collect from the literature comparison samples of intermediate-$z$ and local AGN, selected to have been analyzed with very similar methods to those applied in the distant sample.
+We recalibrate the relevant quantities from the literature based on a set of self-consistent recipes to ensure that our differential measurement of evolution is robust to calibration and methodological issues (Section~\ref{sec:compare_sample}).
 
@@
 \label{sec:data}
-We utilize a sample size of 32 broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that have black hole mass {\bf measurements} and fall within deep extragalactic survey fields that offer rich ancillary data.
+We utilize a sample size of 32 broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that have black hole mass measurements and fall within deep extragalactic survey fields that offer rich ancillary data.
 Specifically, we focused on meeting the following criteria to overcome the limitations of previous studies:
@@
 
-\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., \halpha) which {\bf avoid} potential systematic uncertainties in UV-based estimators \citep{Greene2005}.
-
-\item {\bf Black holes masses \mbh/$M_{\odot}\lesssim8.7$, are below the knee of the black hole mass function to minimize selection biases (see Figure~\ref{fig:selection}, top panel).} %fall below the knee of the black hole mass function to minimize the selection biases.
-
-\item {\bf Eddington ratios above $5\%$} to further ensure homogeneity.
-
-\item {\bf X-ray selected sample has host-to-total flux ratios typically above $30\%$ which facilitates the galaxy mass measurements.} %The lower nuclear-to-host ratios of our sample facilitates the galaxy mass measurements, given that they are X-ray selected.
-
-\item \hst/WFC3 imaging of the host galaxy {\bf at rest-frame wavelength $\sim5500$~\angstrom, which} is above the $4000$~\angstrom\ break and does not include the broad \halpha\ line ($6563$~\angstrom{\bf ), which ensures} sensitivity to the total stellar mass content.
+\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., \halpha) which avoid potential systematic uncertainties in UV-based estimators \citep{Greene2005}.
+
+\item Black holes masses \mbh/$M_{\odot}\lesssim8.7$, are below the knee of the black hole mass function to minimize selection biases (see Figure~\ref{fig:selection}, top panel).
+%fall below the knee of the black hole mass function to minimize the selection biases.
+
+\item Eddington ratios above $5\%$ to further ensure homogeneity.
+
+\item X-ray selected sample has host-to-total flux ratios typically above $30\%$ which facilitates the galaxy mass measurements.
+%The lower nuclear-to-host ratios of our sample facilitates the galaxy mass measurements, given that they are X-ray selected.
+
+\item \hst/WFC3 imaging of the host galaxy at rest-frame wavelength $\sim5500$~\angstrom, which is above the $4000$~\angstrom\ break and does not include the broad \halpha\ line ($6563$~\angstrom), which ensures sensitivity to the total stellar mass content.
 This is somewhat coupled to the previous item in this list.
@@
 On the right, we illustrate the shape of the Eddington rate distribution at these redshifts from the same reference.
-For comparison, we plot the high-$z$ luminous SDSS {\bf AGN} samples that have been studied with \hst\ ~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}, mainly at the high mass end.}
+For comparison, we plot the high-$z$ luminous SDSS AGN samples that have been studied with \hst\ ~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}, mainly at the high mass end.}
 \end{figure}
@@
 
-The 32 AGNs are initially selected by the X-ray observations {\bf of COSMOS}~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
+The 32 AGNs are initially selected by the X-ray observations of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields.
 In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan.
@@
 It is from this catalog that we primarily select our targets.
-{\bf The continuum fitting and emission-line modeling provided by this work are performed through a common procedure for spectral model fits.
+The continuum fitting and emission-line modeling provided by this work are performed through a common procedure for spectral model fits.
 This approach first corrects the spectra for galactic extinction and shifts them to the rest-frame.
@@
 The spectrum is modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on $\chi^2$ minimization.
-We refer the reader to the aforementioned paper for further details.}
-Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} {\bf using a similar approach}.
-
-{\bf Based on the \mbh\ estimates} described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~(\mbh/$M_{\odot})\lesssim8.5$.
+We refer the reader to the aforementioned paper for further details.
+Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} using a similar approach.
+
+Based on the \mbh\ estimates described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~(\mbh/$M_{\odot})\lesssim8.5$.
 The bolometric luminosities are measured from the broad AGN lines by \citet[][Section 3.3]{Schulze2018}, which are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$.
@@
 \log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
-&~+~& 2.0 \log \left(\frac{\rm FWHM(5100)}{1000 ~{\rm km~s^{-1}}}\right) .
+&~+~& 2.0 \log \left(\frac{\rm FWHM({\bf H\beta })}{1000 ~{\rm km~s^{-1}}}\right) .
 \end {eqnarray}
@@
 
-{\bf It is worth noting that the absolute flux calibration of the FMOS spectra is set to match the available ground-based IR imaging, UltraVISTA in the case of COSMOS.
+It is worth noting that the absolute flux calibration of the FMOS spectra is set to match the available ground-based IR imaging, UltraVISTA in the case of COSMOS.
 While an initial flux calibration is performed during the reduction of the FMOS data using calibration stars, there can be differential flux loss due to aperture effects, variable seeing conditions, and minor alignment issues with the instrument.
@@
 We note that this procedure does not correct for intrinsic variability that may induce an additional error of 0.2 mag.
-We refer the reader to Section 2.2 of \citet{Schulze2018} for full details on the flux calibration.}
+We refer the reader to Section 2.2 of \citet{Schulze2018} for full details on the flux calibration.
 
@@
 
-Adopting our specific selection limits into the framework {\bf (i.e., $\log($\mbh$/M_{\odot})\in[7.5, 8.56]$, $\log(L_{\rm bol}/L_{\odot})\in[45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$),} we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model that include the local value of the mass \mbh/\smass ~ratio.
+Adopting our specific selection limits into the framework (i.e., $\log($\mbh$/M_{\odot})\in[7.5, 8.56]$, $\log(L_{\rm bol}/L_{\odot})\in[45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model that include the local value of the mass \mbh/\smass ~ratio.
 To reiterate, an offset in the observed mass relations of 0.2 dex at $z\sim1.5$ can be considered consistent with no evolution in the mass ratio.
@@
 The sample by B10 consists of 19 AGN with the \mbh-\lhost\ relation determined with reliable \mbh\ masses using reverberation mapping with an uncertainty level $\sim0.15$ dex.
-{\bf Note that B10 only provides the single galaxy V-band luminosity.
-\citet{Ding2017b} derive the galaxy R-band luminosity based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).} The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
+Note that B10 only provides the single galaxy V-band luminosity.
+\citet{Ding2017b} derive the galaxy R-band luminosity based on the same early-type galaxy template spectrum adopted by B10 using K-correction (see Section~3.2 therein).
+The work of B11 contains 25 local active AGNs, where the \mbh\ are measured using the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex).
 To track the local \smass\ and \mbh\  relations to higher values, we include 30 inactive galaxies (mainly ellipticals or S0) from \citet{H+R04} (hereafter HR04).
@@
 We select samples that were analyzed by members of our team to ensure uniform measurements.
-The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} {\bf using a single band which are} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$.
-{\bf Similar to the B10 sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-corrections from the V-band based on the same stellar template.
-Moreover, \citet{Bennert11} and \citet{SS13} estimate the stellar masses of their 27 objects using multi-band imaging data, and we adopt them as the \mbh-\smass\ comparison sample.}
+The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} using a single band which are applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$.
+Similar to the B10 sample, the R-band luminosities of these intermediate redshift systems (79 in total) are obtained by \citet{Ding2017b} using K-corrections from the V-band based on the same stellar template.
+Moreover, \citet{Bennert11} and \citet{SS13} estimate the stellar masses of their 27 objects using multi-band imaging data, and we adopt them as the \mbh-\smass\ comparison sample.
  In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample.
@@
 
-{\bf The values for the all the \mbh-\lhost\ comparison samples are listed in the paper by \citet{Ding2017b} (Table~1 and Table~2 therein).
-The \mbh-\smass\ comparison samples are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.}
+The values for the all the \mbh-\lhost\ comparison samples are listed in the paper by \citet{Ding2017b} (Table~1 and Table~2 therein).
+The \mbh-\smass\ comparison samples are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.
 
@@
 
-{\bf Having obtained the \hst\ image, we remove the background light, arising from the sky and the detector.
+Having obtained the \hst\ image, we remove the background light, arising from the sky and the detector.
 In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm, which effectively accounts for gradient in the background distribution.
@@
 To test the fidelity of this subtraction, we measure the surface brightness in the empty regions and verify that it is consistent with zero within the noise.
-Finally, we extract the postage stamp of the AGN image and PSF image to carry out the modeling process; see Section~\ref{sec:psf_library} and Section~\ref{sec:analysis}.}
+Finally, we extract the postage stamp of the AGN image and PSF image to carry out the modeling process; see Section~\ref{sec:psf_library} and Section~\ref{sec:analysis}.
 
@@
 \item AGN imaging data. \\
--- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample\footnote{\bf The photometric aperture was determined as a compromise between the detection of the total flux and a minimization of the background noise while keeping the computational time low.
+-- Using aperture photometry, we find that an aperture size with radius $\sim1\farcs{}5$ sufficiently covers the AGN emission of our sample\footnote{The photometric aperture was determined as a compromise between the detection of the total flux and a minimization of the background noise while keeping the computational time low.
 We found that extending the radius beyond $1\farcs5$ did not add any missing light, while it increased the noise and computational time.
 %By keep extending the aperture size, we note that the $1\farcs{}5$ is the limit region, beyond which the total aperture flux would not increase with the extending of aperture radius.
-}. By default, we extract an image of $61\times61$ pixels (i.e., $4''\times 4''$). If needed, a larger box size {\bf is selected to} include nearby objects. 
+}. By default, we extract an image of $61\times61$ pixels (i.e., $4''\times 4''$). If needed, a larger box size is selected to include nearby objects. 
 \item Noise level map.\\
@@
 As shown in Figure~\ref{fig:hist_compare}, the results are consistent.
-For each AGN, we check the {\bf location on the detector for the top-ranked PSFs} and find that they are unrelated to the {\bf AGN position on the detector.
+For each AGN, we check the location on the detector for the top-ranked PSFs and find that they are unrelated to the AGN position on the detector.
 This finding underscores that position on the detector is not the main factor driving the PSF shape.
 Other factors, likely to be more significant, are the sub-pixel centering, the intrinsic color of the star, and the jitter and thermal status of the telescope during the observations.
-The complexity of the problem}
+The complexity of the problem
 highlights the necessity of decomposing the AGN using all the available PSF-stars from the entire program.
@@
 \caption{\label{fig:hist_compare} 
-Distribution of the host-to-total flux ratio {\bf and effective radius} when implementing a different number of top-ranked PSFs.}
+Distribution of the host-to-total flux ratio and effective radius when implementing a different number of top-ranked PSFs.}
 \end{figure}
@@
 
-From our image decomposition, we detect the {\bf host galaxy in all cases at a significant level, except one case (i.e., SXDS-X763) that has a host-to-total flux ratio lower than $15\%$}.
+From our image decomposition, we detect the host galaxy in all cases at a significant level, except one case (i.e., SXDS-X763) that has a host-to-total flux ratio lower than $15\%$.
 \hst/WFC3 images with the AGN component removed are presented in the third panel (i.e., the ``data$-$point source'' stamps) of Figure~\ref{fig:AGN_decomp} and in Appendix~\ref{sec:restsample} for the remaining cases.
@@
 \label{sec:result-hosts}
-As shown in Figure~\ref{fig:hist_compare} {\bf (top panel)}, the host-to-total flux ratio (total$=$host$+$nuclear) of the sample spans a wide range from $10\%$ to $90\%$ with most of the sample concentrated between $20\%$ to $50\%$ (median value $37\%$).
-Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the {\bf five systems (i.e., CID255, CID50, LID360, CDFS-229, SXDS-X763) which have host-to-total flux ratios lower than $20\%$} should be considered as marginal detections.
-
-The distributions of effective radius \Reff\ {\bf are shown in Figure~\ref{fig:hist_compare} {\bf (bottom panel)}.
+As shown in Figure~\ref{fig:hist_compare} (top panel), the host-to-total flux ratio (total$=$host$+$nuclear) of the sample spans a wide range from $10\%$ to $90\%$ with most of the sample concentrated between $20\%$ to $50\%$ (median value $37\%$).
+Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the five systems (i.e., CID255, CID50, LID360, CDFS-229, SXDS-X763) which have host-to-total flux ratios lower than $20\%$ should be considered as marginal detections.
+
+The distributions of effective radius \Reff\ are shown in Figure~\ref{fig:hist_compare} (bottom panel).
 Based on the redshift, we calculate the physical scale of the radius for each object in kpc assuming a standard cosmology.
-We plot them together with measured \sersic\ index in Figure~\ref{fig:hist_rn}.} These values are distributed within the allowed range and not concentrated on either the upper or lower bound.
+We plot them together with measured \sersic\ index in Figure~\ref{fig:hist_rn}.
+These values are distributed within the allowed range and not concentrated on either the upper or lower bound.
 The \Reff\ of our sample are between $\sim1-7$~kpc (peaked at $\sim2.2$~kpc).
 Nearly half ($15/32$) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge.
-Five systems {\bf have} a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
-{\bf Seven systems have effective radius \Reff$<0\farcs18$, i.e., smaller than 3 pixels.
+Five systems have a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).
+Seven systems have effective radius \Reff$<0\farcs18$, i.e., smaller than 3 pixels.
 In order to check whether this affects our conclusions,  we re-fit them with a \Reff\ $\in[0\farcs{}2,1\farcs{0}]$ prior and find that the inferred host flux barely changes ($<1\%$).
-In particular, the}
-inferred \Reff\ for {\bf three} systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero.
+In particular, the
+inferred \Reff\ for three systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero.
 This means the size inference of these three systems should really be considered an upper limit, rather than a measurement.
-However, the inference of their host luminosities and stellar masses are still reliable given {\bf the consistency of the re-fitting results and} the small scatter in the host flux ($<10\%$).
-
-We compare the morphology of AGNs host galaxies to inactive galaxies from the CANDELS imaging survey.
-We identify 4401 inactive galaxies within a redshift range ($1.2<z<1.7$), comparable to our AGN sample, whose \sersic\ measurements are provided by \citet{VDwel++2012} using \galfit.
-Their stellar masses are derived based on the 3-D-\hst/CANDELS spectroscopic survey~\citep{Momcheva2016, Brammer2012} and comparable to our AGN hosts ($9.5< \log (M_* /M_{\odot})< 11.5$; Section~\ref{sec:mm}).
+However, the inference of their host luminosities and stellar masses are still reliable given the consistency of the re-fitting results and the small scatter in the host flux ($<10\%$).
+
+We compare the morphology of AGNs host galaxies to inactive galaxies from the {\bf CANDELS survey~\citep{Grogin2011, Koekemoer2011}.} We identify 4401 inactive galaxies within a redshift range ($1.2<z<1.7$), comparable to our AGN sample, whose \sersic\ measurements are provided by \citet{VDwel++2012} using \galfit.
+Their stellar masses are derived based on the {\bf 3-D-\hst\ spectroscopic survey~\citep{Momcheva2016, Brammer2012} } and comparable to our AGN hosts ($9.5< \log (M_* /M_{\odot})< 11.5$; Section~\ref{sec:mm}).
 We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where we find no significant difference between their distributions and median value.
@@
 
-For $21/32$ AGNs, we have multi-band host magnitudes that enable us to select {\bf the appropriate stellar population templates} to determine rest-frame luminosities and stellar masses for the overall sample.
-We find {\bf that the $1$~Gyr and the $0.625$~Gyr} stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} {\bf provide the excellent matches} to the observed colors of our sample {\bf at $z<1.44$ and $z>1.44$, respectively}  (see Figure~\ref{fig:compare_temp}).
-{\bf To minimize the uncertainty associated with these corrections, we use these two templates to interpolate to the rest-frame R band which is very close to the observed wavelengths}.
+For $21/32$ AGNs, we have multi-band host magnitudes that enable us to select the appropriate stellar population templates to determine rest-frame luminosities and stellar masses for the overall sample.
+We find that the $1$~Gyr and the $0.625$~Gyr stellar population with solar metallicity and a Chabrier IMF~\citep{Bruzual2003} provide the excellent matches to the observed colors of our sample at $z<1.44$ and $z>1.44$, respectively  (see Figure~\ref{fig:compare_temp}).
+To minimize the uncertainty associated with these corrections, we use these two templates to interpolate to the rest-frame R band which is very close to the observed wavelengths.
 We note that the choice is not unique, and other combinations of ages and metallicities and star formation history could match the observed colors and would provide very similar R-band magnitudes, and also stellar masses \citep{Bell2000, Bell2001}.
@@
 \caption{\label{fig:compare_temp} 
-{\bf {\it Left}: The observed color as a function of redshift, based on $21/32$ AGNs which have both WFC3 and ACS imaging data.
+{\it Left}: The observed color as a function of redshift, based on $21/32$ AGNs which have both WFC3 and ACS imaging data.
 Note that the filter  combinations WFC3/F125W and WFC3/F140W are adopted for galaxies at $z<1.44$ and $z>1.44$, respectively.
@@
 }
-}
 \end{figure*}
@@
 
-Adopting {\bf the $1$~Gyr and $0.625$~Gyr} stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample{\bf, based on the host inference in the  WFC3 band}.
+Adopting the $1$~Gyr and $0.625$~Gyr stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample, based on the host inference in the  WFC3 band.
 As mentioned above, since the WFC3 filter is already close to the rest-frame R-band, we expect the $M_R$ uncertainty introduced by this K-correction to be within $0.05$~mag.
 We derive the rest-frame R band luminosity from $\log L_R/L_{R, \odot} = 0.4\times(M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}.
-$L_R$ ranges {\bf between $\log (L_R/L_{\odot,R})  \in [9.5, 11.5]$ with} individual values listed in Table~\ref{tab:result_sersic}.
+$L_R$ ranges between $\log (L_R/L_{\odot,R})  \in [9.5, 11.5]$ with individual values listed in Table~\ref{tab:result_sersic}.
 
@@
 The black line and the blue colored equation indicates the best-fit result of the local sample as given in Equation~\ref{eq:MLlocal}, with $1\sigma$ confidence interval indicated by the gray region.
-{\bf The values for the comparison samples at low and intermediate redshift are listed in \citet{Ding2017b}, Table 1 and 2.}
+The values for the comparison samples at low and intermediate redshift are listed in \citet{Ding2017b}, Table 1 and 2.
 }
@@
 
-Using the NIR imaging with \hst, we take the host luminosity along with color information to estimate the stellar mass content of each host galaxy based on the mass-to-light ratio of the adopted  {\bf stellar populations}.
+Using the NIR imaging with \hst, we take the host luminosity along with color information to estimate the stellar mass content of each host galaxy based on the mass-to-light ratio of the adopted stellar populations.
 The uncertainty level associated with the stellar mass is expected to be of order $0.1$~dex (changing the IMF would affect all our stellar masses systematically).
-We find $M_*$ ranges {\bf between $\log (M_*/M_{\odot}) \in [9.7, 11.3]$}.
+We find $M_*$ ranges between $\log (M_*/M_{\odot}) \in [9.7, 11.3]$.
 These values are listed in Table~\ref{tab:result_sersic}.
@@
 In Figure~\ref{fig:MM-vz}, we plot the mass ratio as a function of redshift ({\it right} panel) and the mass ratio difference ($\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$ which is considered as the difference between the high redshift data and the best-fit local relation; {\it left} panel).
-For our high-$z$ sample, we find the averaged $\Delta \log \mathcal M_{\rm BH}$ to {\bf be $0.43\pm0.06$, a factor of $~\sim2.7$ higher} than the local mass ratio as indicated by the top blue circle in Figure~\ref{fig:MM-vz}.
+For our high-$z$ sample, we find the averaged $\Delta \log \mathcal M_{\rm BH}$ to be $0.43\pm0.06$, a factor of $~\sim2.7$ higher than the local mass ratio as indicated by the top blue circle in Figure~\ref{fig:MM-vz}.
 
@@
 \end{eqnarray} 
-Performing such a fit based on the {\it observed} data (i.e., no correction for selection effects), {\bf we obtain $\gamma  = 1.03 \pm 0.25$.
-Even with the exclusion of the few outliers, the slope is significantly non-zero with $\gamma  = 0.89 \pm 0.27$}.
+Performing such a fit based on the {\it observed} data (i.e., no correction for selection effects), we obtain $\gamma  = 1.03 \pm 0.25$.
+Even with the exclusion of the few outliers, the slope is significantly non-zero with $\gamma  = 0.89 \pm 0.27$.
 The best-fit {\it observed} evolution model is shown in Figure~\ref{fig:MM-vz}.
@@
 The orange band is the intrinsic scatter of local linear relation.
-The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, {\bf with slope value $\gamma  = 1.03 \pm 0.25$}.
+The red line and gray band are the best-fit and $1\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs, with slope value $\gamma  = 1.03 \pm 0.25$.
 {\it Right}: \mbh/\smass\ as a function of redshift.
 In both panels, we use blue open circles to show the expected bias of the median value for $\Delta \log$\mbh.
-We use framework of \citet{Schulze2011,Schulze2014} to show that even with no evolution selection effects would shift the expectation higher towards the measured values as indicated by the small arrow (Section~\ref{sec:sf_framework}.) {\bf The measurements of the local and intermediate redshift samples are re-calibrated using self-consistent recipes and listed in Table~\ref{tab:comp_sample}.}}
+We use framework of \citet{Schulze2011,Schulze2014} to show that even with no evolution selection effects would shift the expectation higher towards the measured values as indicated by the small arrow (Section~\ref{sec:sf_framework}.) The measurements of the local and intermediate redshift samples are re-calibrated using self-consistent recipes and listed in Table~\ref{tab:comp_sample}.}
 \end{figure*}
@@
 As shown in these panels, the scatter of the high-$z$ correlation presents a similarity to the local relation.
-To quantitively make this comparison, {\bf we investigate the intrinsic scatter of our sample.
+To quantitively make this comparison, we investigate the intrinsic scatter of our sample.
 Note that the {\it observed} high-$z$ sample has effects from both the measurement uncertainty and the narrow selection window, and thus one needs to take them both into account to extract the intrinsic scatter.
@@
 We will return to this topic in a forthcoming paper (Ding et al.
-in prep.), where we focus on the scatter of the sample, as a diagnostic of AGN-host galaxy feedback mechanism}.
-The fact that the intrinsic scatter for the high-$z$ sample is no larger than the local one{\bf, which is $\sim0.35$~dex \citep{Gul++09},} may pose a challenge for explanations of scaling relations where random mergers are the origin of the correlation \citep{Peng2007,Jahnke2011}, indicating that there may likely be a connection between the SMBHs and their host galaxies during their formation.
+in prep.), where we focus on the scatter of the sample, as a diagnostic of AGN-host galaxy feedback mechanism.
+The fact that the intrinsic scatter for the high-$z$ sample is no larger than the local one, which is $\sim0.35$~dex \citep{Gul++09}, may pose a challenge for explanations of scaling relations where random mergers are the origin of the correlation \citep{Peng2007,Jahnke2011}, indicating that there may likely be a connection between the SMBHs and their host galaxies during their formation.
 
@@
 A simple check using our prior estimate of the bias yields a similar result.
-The mean offset of the sample of 32 objects from the local {\bf relationship is $0.43\pm0.06$ dex, which would correspond to $\gamma=1.08\pm0.15$}.
-However, after correcting for the selection bias ($0.21$~dex, see Section~\ref{sec:sf_framework}), {\bf the offset reduces to $0.22\pm0.06$ and thus $\gamma=0.55\pm0.15$, marginally positive, but not conclusively inconsistent with the local value given the error bars and uncertainty in the correction.} We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
+The mean offset of the sample of 32 objects from the local relationship is $0.43\pm0.06$ dex, which would correspond to $\gamma=1.08\pm0.15$.
+However, after correcting for the selection bias ($0.21$~dex, see Section~\ref{sec:sf_framework}), the offset reduces to $0.22\pm0.06$ and thus $\gamma=0.55\pm0.15$, marginally positive, but not conclusively inconsistent with the local value given the error bars and uncertainty in the correction.
+We also note that the distribution of offsets shown in Figure~\ref{fig:offset_hist} displays a positive asymmetric tail.
 Whereas we expect the negative tail to be suppressed by our selection function, and thus it should be accounted for in our treatment.
@@
 The adopted sample includes our 32 AGNs and the intermediate redshift AGNs, using flat prior of \sint\ ({\it left} panel) and lognormal prior ({\it right} panel).
-{\bf The colored regions indicate the 68 and 95\% confidence regions.}
+The colored regions indicate the 68 and 95\% confidence regions.
 }
@@
 
-First, we establish a relation between the single-\sersic\ index and the B/T ratio using inactive galaxies from CANDELS at similar redshifts and stellar masses {\bf (Figure~\ref{fig:BT-n_relation}; $\log (M_*/M_{\odot})\in~ [9.0, 11.5]$)} using the B/T measurements of \citet{Dimauro2018}.
+First, we establish a relation between the single-\sersic\ index and the B/T ratio using inactive galaxies from CANDELS at similar redshifts and stellar masses (Figure~\ref{fig:BT-n_relation}; $\log (M_*/M_{\odot})\in~ [9.0, 11.5]$) using the B/T measurements of \citet{Dimauro2018}.
 In the figure, the red line indicates the average B/T ratio at a given \sersic\ index.
@@
 
-As expected, {\bf we find a stronger offset of
-$\Delta \log \mathcal M_{\rm BH}^{bulge} = 0.87\pm0.07$~dex } in \mbh/\smass$_{\rm, bulge}$ with respect to the
-local relation, which corresponds to an {\bf evolutionary trend with
-$\gamma = 2.09\pm0.30$}. Since selection effects are independent of B/T in
-our framework, we can apply our prior estimate of the correction for selection effects by removing $0.21$~dex, leaving still a {\bf significant offset
-of $0.67\pm0.07$~dex.} We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
+As expected, we find a stronger offset of
+$\Delta \log \mathcal M_{\rm BH}^{bulge} = 0.87\pm0.07$~dex in \mbh/\smass$_{\rm, bulge}$ with respect to the
+local relation, which corresponds to an evolutionary trend with
+$\gamma = 2.09\pm0.30$. Since selection effects are independent of B/T in
+our framework, we can apply our prior estimate of the correction for selection effects by removing $0.21$~dex, leaving still a significant offset of $0.67\pm0.07$~dex.
+We show the histogram of  \mbh/\smass\ and $\gamma$ inferred by
 the Monte Carlo approach in Figure~\ref{fig:gamma_hist} and illustrate the offset between bulge and BH
@@
 \caption{\label{fig:BT-n_relation} 
-Relation between bulge-to-total stellar mass ratio and single-\sersic\ index using CANDELS inactive galaxies {\bf with $\log (M_*/M_{\odot})\in~[9.0, 11.5]$}.
+Relation between bulge-to-total stellar mass ratio and single-\sersic\ index using CANDELS inactive galaxies with $\log (M_*/M_{\odot})\in~[9.0, 11.5]$.
 The red curve is the averaged B/T ratio at different \sersic\ index.
@@
 Same as Figure~\ref{fig:MM-vz}, but for \mbh-\bmass\ relations.
-The intermediate sample consists of 27 objects from \citet{Bennert11} and \citet{SS13}{\bf , listed in Table~\ref{tab:comp_sample}}.
+The intermediate sample consists of 27 objects from \citet{Bennert11} and \citet{SS13}, listed in Table~\ref{tab:comp_sample}.
 \citet{Cisternas2011} do not provide information to infer their bulge mass.}
@@
 The fidelity of the host galaxy magnitude is high as demonstrated by the robustness with respect to the choice of PSF, which is the primary source of uncertainty.
-However, we introduce some uncertainty by adopting {\bf two common} simple stellar population {\bf templates} to derive the rest-frame R-band luminosity and stellar mass for the full population.
+However, we introduce some uncertainty by adopting two common simple stellar population templates to derive the rest-frame R-band luminosity and stellar mass for the full population.
 In principle, if we had more information on the color, we could improve on this source of uncertainty by adopting a specific stellar population model for each target.
-However, considering that the host magnitude in the \hst/ACS band is faint (host-to-total flux ratio $< 30\%$), the individual color that we measure is insufficient to further discriminate between templates, and thus we adopt {\bf the common templates} for simplicity and to facilitate reproduction of our work.
-
-In any case, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates {\bf (i.e., $0.4$~dex)}, and not by uncertainties in the photometry or stellar mass estimates {\bf (i.e., typically $\sim0.15$~dex)}.
+However, considering that the host magnitude in the \hst/ACS band is faint (host-to-total flux ratio $< 30\%$), the individual color that we measure is insufficient to further discriminate between templates, and thus we adopt the common templates for simplicity and to facilitate reproduction of our work.
+
+In any case, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates (i.e., $0.4$~dex), and not by uncertainties in the photometry or stellar mass estimates (i.e., typically $\sim0.15$~dex).
 Thus, the choice of template is a subdominant source of error.
-{\bf Note that the large uncertainties of \mbh\ is not immediately apparent from the figures, since only the AGNs that have {\it measured} \mbh\ that fall into our selection window (i.e., $\log($\mbh$/M_{\odot})\in[7.5, 8.56]$) have been selected.} A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.
+Note that the large uncertainties of \mbh\ is not immediately apparent from the figures, since only the AGNs that have {\it measured} \mbh\ that fall into our selection window (i.e., $\log($\mbh$/M_{\odot})\in[7.5, 8.56]$) have been selected.
+A posteriori, the fact that the intrinsic scatter we observe is not larger than the one in the local universe is consistent with this statement.
 
@@
 To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011} and \citet{H+R04}.
-In the {\bf literature~\citep{Kormendy13, Bentz2018}}, other analyses of the local sample are available, which could also be considered as the local anchor.
-{\bf However, from the point of view of our differential evolutionary measurement, we stress once again the importance of selecting local anchors that have been measured and calibrated in a similar way to the distant high-$z$ samples.
+In the literature~\citep{Kormendy13, Bentz2018}, other analyses of the local sample are available, which could also be considered as the local anchor.
+However, from the point of view of our differential evolutionary measurement, we stress once again the importance of selecting local anchors that have been measured and calibrated in a similar way to the distant high-$z$ samples.
 It is crucial that the black hole masses be obtained in the same of self-consistent manner, and it is also critical that the host/AGN decomposition be measured in the most similar way possible.
@@
 Not all the local correlations are mutually consistent, especially when considering different galaxy properties like luminosity, stellar mass, and velocity dispersion, and therefore a single self-consistent calibration is not possible.
-To illustrate} the problem, we compare our local \mbh-\smass\ sample to that published {\bf by} \citet{Kormendy13} (hereafter K13).
+To illustrate the problem, we compare our local \mbh-\smass\ sample to that published by \citet{Kormendy13} (hereafter K13).
 We find that the \mbh-\smass\ measurements by K13 have a global $\sim+0.3$~dex offset relative to our local sample.
 Note that a $+0.3$~dex difference would almost erase the $\Delta\log$\mbh\ for the high redshift sample as described in the last section, if it were independent of the black hole mass calibration.
-{\bf However,} the \mbh-\sigstar\ relations by K13 are also offset by  $\sim+0.3$~dex with respect to those given by \citet{Woo2010}, which is the baseline for our adopted black hole mass estimators.
+However, the \mbh-\sigstar\ relations by K13 are also offset by  $\sim+0.3$~dex with respect to those given by \citet{Woo2010}, which is the baseline for our adopted black hole mass estimators.
 That is, if we were to adopt the K13 normalization instead, the \mbh\ of all the AGN sample should be increased by $\sim$0.3~dex at the same time.
 As a result, adopting a different local anchor would only globally affect the level of the \mbh\ to local and high-$z$ sample at the same time, with the result of leaving $\Delta\log$\mbh\ unchanged.
-{\bf To illustrate this point further, we adopt the K13 local ellipticals and classical bulges as the $z\sim0$ anchor and compare to the recalibrated \mbh\ of our high-$z$ AGNs sample.
+To illustrate this point further, we adopt the K13 local ellipticals and classical bulges as the $z\sim0$ anchor and compare to the recalibrated \mbh\ of our high-$z$ AGNs sample.
 The inference of  $\gamma$ changes to $0.74\pm0.31$ which is consistent at $1\sigma$ level with the value (i.e., $\gamma=1.03\pm0.25$ ) based on our chosen anchor.
@@
 Just for illustration, when adopting the \citet{Bentz2018} as the local anchor, we obtain $\gamma = 2.12\pm 0.32$ using the 32 AGNs, indicating still a positive evolution, although as expected the amount of evolution is different for the reasons given above.
- }
 
@@
 We obtained the host properties (i.e., host flux, effective radius, \sersic\ index) using a weighted arithmetic mean based on the inference from the eight top-ranked PSFs.
-With additional \hst/ACS image in the optical, we identified the appropriate {\bf stellar populations} and derived the rest-frame R-band luminosity (\lhost) and stellar mass (\smass) of the host with the corresponding mass-to-light ratio.
+With additional \hst/ACS image in the optical, we identified the appropriate stellar populations and derived the rest-frame R-band luminosity (\lhost) and stellar mass (\smass) of the host with the corresponding mass-to-light ratio.
 We then determine the mass relations at high-$z$ and establish any signs of evolution by combining our high-$z$ measurements with local and intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13, Cisternas2011}.
 
-We find the average ``observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, {\bf by $0.41$~dex (a factor of $\sim2.6$) and  $0.43$~dex (a factor of $\sim2.7$), respectively}, as compared to that in the local universe.
-{\bf However, taking into account uncertainties and the bias due to selection effect could bias, the offset to the local universe is only marginally significant.} 
+We find the average ``observed" ratio between the mass of a SMBH and either their total host luminosity or total stellar mass is larger at $z\sim1.5$, by $0.41$~dex (a factor of $\sim2.6$) and  $0.43$~dex (a factor of $\sim2.7$), respectively, as compared to that in the local universe.
+However, taking into account uncertainties and the bias due to selection effect could bias, the offset to the local universe is only marginally significant.
 %these correlations are consistent with those in the local universe within the 95\% confidence limits. }
@@
 Considering the bulge component \citep{Bennert11, Woo++08} separately, we find that our high-$z$ AGN sample has significantly lower mass/luminosity bulges at fixed black hole mass than in the local universe.
-Comparing to their \mbh, we find evolution with the {\bf ratio evolving as $(1+z)^{2.09\pm0.30}$,} which is significant even when accounting for selection effects.
+Comparing to their \mbh, we find evolution with the ratio evolving as $(1+z)^{2.09\pm0.30}$, which is significant even when accounting for selection effects.
 We caution that the evolution of the bulge component is more uncertain than our measurement of the total galaxy components, since it is based on an estimate of the B/T ratio from the measured \sersic\ index based on a matched sample of inactive galaxies.
@@
 
-{\bf We summarize several limitations of this work.
+We summarize several limitations of this work.
 First, due to finite resolution of \hst, we model the host as a single \sersic\ profile.
@@
 We adopted as our baseline the local samples for which measurements have been made with a procedure that is most similar to the one we have applied at high-$z$, but other choices are possible.
-We investigated the impact of different choices for the local anchor in detail and we found that even though the numerical values can change somewhat, the inferred evolution is always positive  (see Section~\ref{sec:local_sys}).}
-
-Given that the \smass$_{\rm ,total}$-\mbh\ relation is closer to or consistent with the local relation, the inferred evolution of the \bmass-\mbh\ correlations is qualitatively consistent with a scenario where the assembly of the black hole predates that of the bulge, which is processed by the transfer of stellar mass from the disk via mergers or secular {\bf processes \citep{Jah++09,Bennert++2011,SS13}.
-}The stellar mass {\bf needed} to build the bulge appears to be present in the disk component at high-$z$.
+We investigated the impact of different choices for the local anchor in detail and we found that even though the numerical values can change somewhat, the inferred evolution is always positive  (see Section~\ref{sec:local_sys}).
+
+Given that the \smass$_{\rm ,total}$-\mbh\ relation is closer to or consistent with the local relation, the inferred evolution of the \bmass-\mbh\ correlations is qualitatively consistent with a scenario where the assembly of the black hole predates that of the bulge, which is processed by the transfer of stellar mass from the disk via mergers or secular processes \citep{Jah++09,Bennert++2011,SS13}.
+The stellar mass needed to build the bulge appears to be present in the disk component at high-$z$.
 
@@
 
-{\bf The authors thank the anonymous referee for helpful suggestions and comments which improved this paper.
-We acknowledge the importance of the conference ``Particle Astrophysics and Cosmology Including Fundamental InteraCtions (PACIFIC-2013)" in preparing for this program.} We fully appreciate input from Luis Ho, Renyue Cen, Hyewon Suh, Takahiro Morishita and Peter Williams.
+The authors thank the anonymous referee for helpful suggestions and comments which improved this paper.
+We acknowledge the importance of the conference ``Particle Astrophysics and Cosmology Including Fundamental InteraCtions (PACIFIC-2013)" in preparing for this program.
+We fully appreciate input from Luis Ho, Renyue Cen, Hyewon Suh, Takahiro Morishita and Peter Williams.
 XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
-{\bf TT acknowledges support by NSF through grant AST-1412315.} VNB gratefully acknowledges assistance from a NASA grant associated with HST proposal GO 15215.
+TT acknowledges support by NSF through grant AST-1412315.
+VNB gratefully acknowledges assistance from a NASA grant associated with HST proposal GO 15215.
 JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
@@
 \bibliographystyle{apj.bst}
-\bibliography{references}
+%\bibliography{references}
+\input{manuscript.bbl}
 
@@
 Having transferred the \lhost\ to today, we find that, as showing in Figure~\ref{fig:ML-vz}-(a), at fixed mass, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation.
-{\bf Based on the 32 AGN systems, we fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 1.07\pm0.23$, } as showing in Figure~\ref{fig:ML-vz}-(b).
-We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and {\bf obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.4$, }with flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
+Based on the 32 AGN systems, we fit the offset as a function of redshift in form as Equation~\ref{eq:offset} and obtain $\gamma = 1.07\pm0.23$, as showing in Figure~\ref{fig:ML-vz}-(b).
+We further consider the selection effect using the previous approach as introduced in Section~\ref{select_eff}, and obtain $\gamma = 0.5\pm0.5$ and $\gamma = 0.6\pm0.4$, with flat and lognormal prior, respectively, as showing in Figure~\ref{fig:ML-vz}-(c), (d).
 
@@
 
-{\bf \section{C. The \mbh-\smass\ comparison sample}\label{sec:comp_sample_value}
-We use the self-consistent recipes to re-calibrate the measurements of our comparison sample. We list the values of all the comparison \mbh-\smass\ sample in the Table~\ref{tab:comp_sample}.}
+\section{C. The \mbh-\smass\ comparison sample}\label{sec:comp_sample_value}
+We use the self-consistent recipes to re-calibrate the measurements of our comparison sample. We list the values of all the comparison \mbh-\smass\ sample in the Table~\ref{tab:comp_sample}.
 
@@
 Column 6: The observing start date.
-{\bf The total exposure time of each target is 2394s.}
+The total exposure time of each target is 2394s.
 }
@@
 \colhead{}& 
-\colhead{FWHM}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
-\colhead{FWHM(5100)}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
+\colhead{{\bf FWHM($H\alpha$)}}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
+\colhead{{\bf FWHM($H\beta$)}}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
 \colhead{}& 
@@
 Column 1: Object ID.
-Column 2-5: \halpha\ emission line width (FWHM), {\bf \halpha\ luminosity}, inferred \mbh\ and Eddington ratio. %(or continuum line at $\rm L _{\lambda5100}$)
+Column 2-5: \halpha\ emission line width (FWHM), \halpha\ luminosity, inferred \mbh\ and Eddington ratio. %(or continuum line at $\rm L _{\lambda5100}$)
 Column 6-9: \hbeta\ emission line BH properties. 
-The typical uncertainty level for {\bf FWHM is $15\%$, and for $\log( \rm L _{\lambda})$ is in the range $0.01\sim0.2$~dex}, respectively.
-The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
+The typical uncertainty level for FWHM is $15\%$, and for $\log( \rm L _{\lambda})$ is in the range $0.01\sim0.2$~dex, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
 }
@@
 \centering
-    \caption{{\bf Summary of $\gamma$ inferences }}\label{table:gamma_sf}
+    \caption{Summary of $\gamma$ inferences}\label{table:gamma_sf}
      \resizebox{8cm}{!}{
@@
      \hline\hline
-32 AGNs + intermediate & No &  {\bf 0.72$\pm$0.20} & {\bf 0.64$\pm$0.17} \\
-32 AGNs + intermediate& Yes & {\bf 0.90$\pm$0.40} & {\bf0.50$\pm$0.50} \\
-32 AGNs & No & {\bf 1.03$\pm$0.25} & {\bf 1.07$\pm$0.23}\\
-32 AGNs& Yes & {\bf 1.50$\pm$0.80} &  {\bf 1.80$\pm$0.80} \\
+32 AGNs + intermediate & No &  0.72$\pm$0.20 & 0.64$\pm$0.17 \\
+32 AGNs + intermediate& Yes & 0.90$\pm$0.40 & 0.50$\pm$0.50 \\
+32 AGNs & No & 1.03$\pm$0.25 & 1.07$\pm$0.23\\
+32 AGNs& Yes & 1.50$\pm$0.80 & 1.80$\pm$0.80 \\
      \hline
@@
 \centering
-    \caption{ {\bf Observed $\gamma$ for \mbh-\smass\ without selection effect corrections }}\label{table:diff_sample_gam}
+    \caption{Observed $\gamma$ for \mbh-\smass\ without selection effect corrections}\label{table:diff_sample_gam}
      \resizebox{5.5cm}{!}{
@@
      \hline\hline
-32 AGNs & {\bf 1.03$\pm$0.25}\\    
-30 AGNs (excluded outliers) &  {\bf 0.89$\pm$0.27}\\    
-32 AGNs + intermediate &   {\bf 0.72$\pm$0.20}\\
-32 AGNs bulge only &  {\bf 2.09$\pm$0.30}\\
+32 AGNs & 1.03$\pm$0.25\\    
+30 AGNs (excluded outliers) &  0.89$\pm$0.27\\    
+32 AGNs + intermediate &   0.72$\pm$0.20\\
+32 AGNs bulge only &  2.09$\pm$0.30\\
      \hline
      \end{tabular}}
-\tablecomments{These values are directly {\bf inferred for the observation, without corrections due to selection effects.}}
+\tablecomments{These values are directly inferred for the observation, without corrections due to selection effects.}
 \end{table}
@@
 \centering
-\caption{{\bf Data summary for the comparison \mbh-\smass\ sample}}\label{tab:comp_sample}
+\caption{Data summary for the comparison \mbh-\smass\ sample}\label{tab:comp_sample}
 \resizebox{18cm}{!}{

### 2019-11-21 NA_paper/manuscript_II/qso_paperII.tex
Update NA paper before final circulaiton

@@
 \newcommand{\aklant}[1]{\textcolor{blue}{[{\bf AKB}: #1]}}
+
+\newcommand{\red}[1]{{ \textcolor{red}{#1}}}
+\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
+
 \title{
@@
 John D. Silverman$^{3, 4}$,
-Aklant K. Bhowmick$^{5}$,
-N. Menci$^{6}$,
+Aklant K. Bhowmick$^{5,6}$,
+N. Menci$^{7}$,
 Tiziana Di Matteo$^{5}$,
@@
 \item{McWilliams Center for Cosmology, Dept. of Physics, Carnegie Mellon University, Pittsburgh PA 15213, USA}
+\item{Department of Physics, University of Florida, Gainesville, FL 32611, USA}
 \item{INAF Osservatorio Astronomico di Roma, via Frascati 33, I-00078 Monteporzio, Italy}
@@
 For this purpose, we have constructed a unique sample of 32 actively-accreting SMBHs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with accurate BH and stellar masses with the latter based on multi-band \hst\ imaging.
-We directly compare the measurements with two independent state-of-the-art project, the hydrodynamic simulation \texttt{MassiveBlackII} (MBII) and the semi-analytic model (SAM).
+We directly compare the measurements with two independent state-of-the-art project, the hydrodynamic simulation \texttt{MassiveBlackII} (\mbii) and the semi-analytic model (\sam).
 After applying the observational selection function to models to account for bias, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
@@
 Hence, our observations can distinguish between the different recipes adopted in the models.
-The mass relations in \mbii ~are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to galaxy merger events triggering nuclear activity.
+The mass relations in \mbii ~are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to \blue{galaxy merger events triggering nuclear activity}.
 Moreover, the intrinsic scatter in the mass ratio of our high-$z$ sample is comparable to that observed in local sample, all but ruling out the proposed scenario the correlations are purely stochastic in nature arising from some sort of cosmic central limit theorem.
@@
 
-To compare with simulations, we use two independent efforts, \texttt{MassiveBlackII} (MBII)~\cite{Khandai2015} and a semi-analytic model (SAM)~\cite{Menci2014}.
+To compare with simulations, we use two independent efforts, the \texttt{MassiveBlackII} (\texttt{MBII})~\cite{Khandai2015} and the semi-analytic model (\texttt{SAM})~\cite{Menci2014}.
 These simulations are based on independent model strategies, i.e., hydrodynamic simulation for \mbii\ and semi-analytic model for \sam, respectively.
@@
 
-{\bf We note that the absolute determination of stellar mass carries significant uncertainty, both observationally and theoretically.
-Depending on definitions of stellar mass, on the assumed initial mass function, and possibly on the implementation of star formation in the models, the absolute value of \mstar (hence the absolute normalization, i.e., \mbh/\mstar) can vary by up to a factor of two.
+We note that the absolute determination of stellar mass carries significant uncertainty, both observationally and theoretically.
+Depending on definitions of stellar mass, on the assumed initial mass function, and possibly on the implementation of star formation in the models, the absolute value of \mstar\ (hence the absolute normalization, i.e., \mbh/\mstar) can vary by up to a factor of two.
 In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by this uncertainty.
 Thus, in this work, we mainly focus on the scatter as a diagnostic tool, even though in the future more information could be extracted by this kind of comparison if the %absolute stellar mass could be constrained more accurately in the simulations.}
-better measures~(i.e. more consistent with techniques for determining observed \mstar) of stellar masses can be defined for the simulated galaxies.}
+better measures~(i.e. more consistent with techniques for determining observed \mstar) of stellar masses can be defined for the simulated galaxies.
 
@@
 %Selection effect into account
-Using \mbii\, we identify a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones.
+Using \mbii, we identify a sample of simulated AGNs at $z=1.5$ (see METHOD) and compare their predicted scaling relations to the observed ones.
 We take the measurement uncertainty and selection biases into account to ensure a fair comparison.
-First, we inject random noise to the simulated sample to mimic the scatter in our data due to measurement errors, i.e., $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex, and $\Delta L_{\rm bol}$=0.03~dex, respectively.
+First, we inject random noise to the simulated sample to mimic the scatter in our data due to measurement errors, i.e., $\Delta$\mbh $=0.4$~dex, $\Delta$\mr$=0.3$~dex, $\Delta$\mstar$=0.17$~dex, and $\Delta L_{\rm bol}=0.03$~dex, respectively.
 We then select the sample that falls into the same targeting window to match the observed sample (Figure~\ref{fig:selectfunc}).
@@
 \caption{(Left) Comparison of the observed (orange dots) and simulated (blue dots) \mbh--\mstar\ relation.
-The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the {\bf standard derivation of the sample}.
+The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the standard derivation of the residual.
 By fixing the slope to match the simulated data, the orange line shows the best-fit result for the observed data set.
@@
 
- \ding{We can put the following paragraph into Method or even remove it.} To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
+To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
 For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3.
@@
 The median values for the flux ratio distribution of the observed, \mbii, \sam\ sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively.
-We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are 0.34 (for observed -- \mbii) and 0.14 (for observed -- \sam), respectively.
+We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are $0.34$ (for observed -- \mbii) and $0.14$ (for observed -- \sam), respectively.
 This result indicates the three samples have similar host-to-total light ratio distribution.
@@
 The \sam\ model also consider the AGN feedback.
-However, in contrast to \mbii, the feeding process for the SMBH accretion is driven by galaxy mergers, and thus may be more stochastic and lead to the larger scatter.
+However, in contrast to \mbii, the feeding process for the SMBH accretion is driven \blue{by the 2-body interaction of galaxy mergers}, and thus may be more stochastic and lead to the larger scatter.
 More specifically, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the  encounter.
@@
 As a result, the \sam\ cloud extends to the high \mbh\ with low stellar mass, which may not exist.
-\ding{To Nicola: do you want to include your new 2D model in the paper?} The consistency between \mbii\ and observations provides important observational evidence in support of the hypothesis that there is a causal link (i.e., AGN feedback) between the evolution of SMBH and that of their host galaxies.
+The consistency between \mbii\ and observations provides important observational evidence in support of the hypothesis that there is a causal link (i.e., AGN feedback) between the evolution of SMBH and that of their host galaxies.
 
@@
 
-\textbf{\texttt{MassiveBlackII} (\mbii) simulation}.  
-\mbii\ is a high-resolution cosmological hydrodynamic simulation using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\cite{2005MNRAS.364.1105S}.
+\textbf{\texttt{MassiveBlackII} simulation}.  
+The MassiveBlackII (\mbii) is a high-resolution cosmological hydrodynamic simulation using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\cite{2005MNRAS.364.1105S}.
 It has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles.
@@
 The galaxy SEDs are finally convolved with the desired filter function to obtain the broad band photometry~(SDSS $r$ band magnitude).
+
+\blue{To adopt the appropriate proxy in the \mbii\ simulation as stellar mass and compare to the observational datasets, we follow the common practice and collect the stellar mass within a 3D spherical aperture of 30 kpc.
+It has been shown that the stellar mass by this definition is more standard, which produces the stellar mass function that is consistent with observational constraints~\cite{Pillepich2018}.
+Further, the stellar mass in this physical aperture provides good agreement to those within Petrosian radii in observations \cite{Schaye2015}.
+}
+
 For further details regarding the \mbii\ simulation, we refer the reader to the reference~\cite{2015MNRAS.450.1349K}.
 
-\textbf{Semi-analytic model (\sam)}.
-The \sam\ is fully described in Menci et al.
+\textbf{Semi-analytic model}.
+The Semi-analytic model (\sam) is fully described in Menci et al.
 (2016)~\cite{Menci2016}.
@@
 (taken to be proportional to the energy radiated by the 
-AGN through the efficiency {\color{red} $\epsilon_{AGN}=5\times 10^{-2}$) }
+AGN through the efficiency $\epsilon_{AGN}=5\times 10^{-2}$)
 and the thermal energy of the unperturbed gas (see Menci et al. (2008)~\cite{Menci2008} for details).
@@
 To estimate the scatter of the sample, we plot the histogram of the residual distribution, i.e., the sample deviation to their best-fit.
-The result is presented in Figure~\ref{fig:offset_comp} (left panel).
+The result is presented in Figure~\ref{fig:offset_comp}.
 We find the standard derivation of the residual for observed and \mbii\ sample are both equal to $\sim0.3$~dex; however, for \sam, the scatter value is much larger ($\sim0.7$~dex).
-We perform the KS test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.3$.
+We perform the KS test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$.
 Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \mbii\ sample and the observational sample have the same intrinsic scatter level.
@@
 JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
-A.S.
-is supported by the EACOA fellowship.
-\ding{More acknowledge.}
 

### 2019-11-21 NA_paper/scripts/my_selection_plots_MBII.py

@@ -26,7 +26,8 @@ h=0.7
 bhmass_overall=np.loadtxt('../Aklant/new_sample_half_Reff/log10_bh_mass_full_population.txt') - np.log10(h) 
 #bhmass_selected=np.loadtxt('../Aklant/new_sample/log10_bh_mass_selected_population.txt') - np.log10(h) 
 
-mstar_overall=np.loadtxt('../Aklant/new_sample_half_Reff/log10_stellar_mass_full_population_within_half_light.txt') - np.log10(h) 
+#mstar_overall=np.loadtxt('../Aklant/new_sample_half_Reff/log10_stellar_mass_full_population_within_half_light.txt') - np.log10(h) 
+mstar_overall=np.loadtxt('../Aklant/new_sample_30kpc/log10_stellar_mass_full_population_within_30kpc.txt') - np.log10(h) 
 #mstar_selected=np.loadtxt('../Aklant/new_sample/log10_stellar_mass_selected_population.txt') - np.log10(h) 
 
 magr_overall=np.loadtxt('../Aklant/new_sample_half_Reff/log10_host_r_mag_full_population.txt')
@@ -215,7 +216,7 @@ plt.fill_betweenx(y_space,x_space_lb,x_space_ub,color='orange',alpha=0.35,zorder
 obj.set_yticks([7.5,8.0,8.5,9.0])
 obj.set_xticks([10,10.5,11,11.5,12])
 #obj.set_xticklabels(['-18','-20','-22','-24','-26'])
-ax.set_xlim(9.5,12.3)  #
+ax.set_xlim(9.7,11.9)  #
 ax.set_ylim(7.2, 9.4)  #
 obj.tick_params(labelsize=30)
 #ax.set_rasterized(True)
@@ -228,6 +229,7 @@ plt.show()
 
 #%%
 '''
+#This is the estimation for the selected sample, not the OVERALL sample.
 import linmix
 x = mstar_selected
 xsig = np.zeros(len(bhmass_selected))+dMstar
@@ -354,9 +356,9 @@ print "\n\nPlot M-Mag relation:"
 print "mismatch:", fit_fixm_1[0]- fit_1[0][1]
 
 obj.set_yticks([7.5,8.0,8.5,9.0])
-obj.set_xticks([-18, -20,-22,-24,-26])
+obj.set_xticks([-20,-21, -22, -23, -24, -25])
[…]

### 2019-11-21 NA_paper/scripts/my_selection_plots_SAM.py

@@ -206,7 +206,7 @@ plt.fill_betweenx(y_space,x_space_lb,x_space_ub,color='orange',alpha=0.35)
 obj.set_yticks([7.5,8.0,8.5,9.0])
 obj.set_xticks([10,10.5,11,11.5,12])
 #obj.set_xticklabels(['-18','-20','-22','-24','-26'])
-ax.set_xlim(9.5,12.3)  #
+ax.set_xlim(9.7,11.9)  #
 ax.set_ylim(7.2, 9.4)  #
 obj.tick_params(labelsize=30)
 #ax.set_rasterized(True)
@@ -344,9 +344,9 @@ print "\n\nPlot M-Mag relation:"
 print "mismatch:", fit_fixm_1[0]- fit_1[0][1]
 
 obj.set_yticks([7.5,8.0,8.5,9.0])
-obj.set_xticks([-18, -20,-22,-24,-26])
+obj.set_xticks([-20,-21, -22, -23, -24, -25])
 #obj.set_xticklabels(['-18','-20','-22','-24','-26'])
-ax.set_xlim(-19.8, -26)  # 
+ax.set_xlim(-19.8, -25.5)  # 
 ax.set_ylim(7.2, 9.4)  # 
 
 obj.tick_params(labelsize=30)
@@ -378,40 +378,40 @@ print "KS:", stats.ks_2samp((r_band_magnitudes_selected - lfit(bhmass_selected,f
 
 
 
-#%%Plot the 1-D hist for Mstar, R_Mag and MBH and do the K-S test in 1D.
-
-plt.figure(figsize=(8,6))
-plt.hist(bhmass_selected ,histtype=u'step',normed=True,
-         label=('SAM BH sample'), linewidth = 2, color='orange')
-plt.hist(bh_mass_obs , histtype=u'step',normed=True,
-         label=('HST BH sample'), linewidth = 2, color='green')
-plt.tick_params(labelsize=20)
-plt.legend(prop={'size':20})
-plt.yticks([])
-plt.show()
-print stats.ks_2samp(bhmass_selected, bh_mass_obs).pvalue
-
-plt.figure(figsize=(8,6))
-plt.hist(mstar_selected ,histtype=u'step',normed=True,
-         label=('SAM M* sample'), linewidth = 2, color='orange')
-plt.hist(stellar_mass_obs , histtype=u'step',normed=True,
-         label=('HST M* sample'), linewidth = 2, color='green')
[…]

### 2019-11-21 manuscript/manuscript.tex
Remove the bold face

@@
 \log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
-&~+~& 2.0 \log \left(\frac{\rm FWHM({\bf H\beta })}{1000 ~{\rm km~s^{-1}}}\right) .
+&~+~& 2.0 \log \left(\frac{\rm FWHM(H\beta)}{1000 ~{\rm km~s^{-1}}}\right) .
 \end {eqnarray}
@@
 
-We compare the morphology of AGNs host galaxies to inactive galaxies from the {\bf CANDELS survey~\citep{Grogin2011, Koekemoer2011}.} We identify 4401 inactive galaxies within a redshift range ($1.2<z<1.7$), comparable to our AGN sample, whose \sersic\ measurements are provided by \citet{VDwel++2012} using \galfit.
-Their stellar masses are derived based on the {\bf 3-D-\hst\ spectroscopic survey~\citep{Momcheva2016, Brammer2012} } and comparable to our AGN hosts ($9.5< \log (M_* /M_{\odot})< 11.5$; Section~\ref{sec:mm}).
+We compare the morphology of AGNs host galaxies to inactive galaxies from the CANDELS survey~\citep{Grogin2011, Koekemoer2011}.
+We identify 4401 inactive galaxies within a redshift range ($1.2<z<1.7$), comparable to our AGN sample, whose \sersic\ measurements are provided by \citet{VDwel++2012} using \galfit.
+Their stellar masses are derived based on the 3-D-\hst\ spectroscopic survey~\citep{Momcheva2016, Brammer2012} and comparable to our AGN hosts ($9.5< \log (M_* /M_{\odot})< 11.5$; Section~\ref{sec:mm}).
 We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where we find no significant difference between their distributions and median value.
@@
 \bibliographystyle{apj.bst}
-%\bibliography{references}
-\input{manuscript.bbl}
+\bibliography{references}
+%\input{manuscript.bbl}
 
@@
 \colhead{}& 
-\colhead{{\bf FWHM($H\alpha$)}}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
-\colhead{{\bf FWHM($H\beta$)}}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
+\colhead{FWHM($H\alpha$)}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
+\colhead{FWHM($H\beta$)}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
 \colhead{}& 

### 2019-11-25 NA_paper/manuscript_II/manuscript.tex
Submit NA

--- 2019-11-21 NA_paper/manuscript_II/qso_paperII.tex
@@
 N. Menci$^{7}$,
-Tiziana Di Matteo$^{5}$,
-et. al.
+Tiziana Di Matteo$^{5}$
 }
@@
 Supermassive black holes (SMBHs) ubiquitously occupy the center of massive galaxies in the local Universe and beyond.
-Their growth in mass (\mbh) appears to be closely linked to the physical properties of their host galaxies\cite{Mag++98, F+M00, M+H03, H+R04, Gul++09}, in particular the relation between \mbh ~and stellar mass.
+Their growth in mass (\mbh) appears to be closely linked to the physical properties of their host galaxies\cite{Mag++98, F+M00, M+H03, H+R04, Gul++09}, in particular the relation between \mbh ~and stellar mass (\mstar).
 With the origin of this correlation far from being fully understood, simulations have been a promising means to further interpret the observations over the last eight billion years ($z\lesssim1$) thus enabling substantial progress in this field.
@@
 For this purpose, we have constructed a unique sample of 32 actively-accreting SMBHs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with accurate BH and stellar masses with the latter based on multi-band \hst\ imaging.
-We directly compare the measurements with two independent state-of-the-art project, the hydrodynamic simulation \texttt{MassiveBlackII} (\mbii) and the semi-analytic model (\sam).
+We directly compare the measurements with two independent state-of-the-art projects, the hydrodynamic simulation \texttt{MassiveBlackII} (\mbii) and the semi-analytic model (\sam).
 After applying the observational selection function to models to account for bias, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
-However, accounting for observational errors, the dispersion in the mass ratio between \mbh~and \mstar~is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex) one.
+However, accounting for observational errors, the dispersion in the mass ratio between \mbh\ and \mstar\ is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex) one.
 Hence, our observations can distinguish between the different recipes adopted in the models.
-The mass relations in \mbii ~are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to \blue{galaxy merger events triggering nuclear activity}.
-Moreover, the intrinsic scatter in the mass ratio of our high-$z$ sample is comparable to that observed in local sample, all but ruling out the proposed scenario the correlations are purely stochastic in nature arising from some sort of cosmic central limit theorem.
-Our results support the hypothesis of AGN feedback being responsible for a causal link between the SMBH and its host galaxy resulting in a tight correlation between their respective masses.
+The mass relations in \mbii ~are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to galaxy merger events triggering nuclear activity.
+Moreover, the intrinsic scatter in the mass ratio of our high-$z$ sample is comparable to that observed in the local sample, all but ruling out the proposed scenario the correlations are purely stochastic in nature arising from some sort of cosmic central limit theorem.
+Our results support the hypothesis of AGN feedback being responsible for a causal link between the SMBH and its host galaxy, resulting in a tight correlation between their respective masses.
 
@@
 A completely different view holds that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations without any direct physical mechanisms~\cite{Peng2007, Jahnke2011, Hirschmann2010}.
-From the central limit theorem, a stochastic cloud at high-$z$ (higher dispersion) would end up with scaling relations as observed today with lower dispersion.
+From this central limit theorem, a stochastic cloud at high-$z$ (higher dispersion) would end up with scaling relations as observed today with lower dispersion.
 
@@
 %The reason to extend to high redshift.
-Simulations are effective at helping to understand this connection and rule out theories/ assumptions that could not be definitively verified by observations alone.
+Simulations are effective at helping to understand this connection and rule out theories and assumptions that could not be definitively verified by observations alone.
 In particular, simulations can be used to quantify the impact of systematic uncertainties and selection biases with observational data.
@@
 	%mention the scatter.
-To push our knowledge of the mass relations to earlier epochs, we have been analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields (D19~\cite{Ding2019} hereafter), namely COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}.
+To push our knowledge of the mass relations to earlier epochs, we have been analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields, namely COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008} (D19~\cite{Ding2019} hereafter).
 The redshift range of our targets is chosen to be high enough ($z>1$) to establish the mass ratios of accreting SMBHs and to make direct comparisons to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy.
@@
 We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy.
-Moreover, 21/23 systems have \hst/ACS imaging data, which enable us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see METHODS and the descriptions in D19).
+Moreover, 21/23 systems have \hst/ACS imaging data, which enables us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see METHODS and the descriptions in D19).
 %We furthermore combining them with the ground-based photometry to carry out the SED fitting, and thus derive the reliable host rest-frame R band luminosity and stellar mass.
@@
 While high-resolution N-body simulations can study specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam.
-In previous works, \mbii~\cite{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\cite{Menci2014, Menci2016} have made high successful predictions, and we refer the interested readers to the METHODS section for more details.
+In previous works, \mbii~\cite{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\cite{Menci2014, Menci2016} have made high successful predictions; we refer the interested readers to the METHODS section for more details.
 
@@
 Thus, in this work, we mainly focus on the scatter as a diagnostic tool, even though in the future more information could be extracted by this kind of comparison if the %absolute stellar mass could be constrained more accurately in the simulations.}
-better measures~(i.e. more consistent with techniques for determining observed \mstar) of stellar masses can be defined for the simulated galaxies.
+better measures~(i.e., more consistent with techniques for determining observed \mstar) of stellar masses can be defined for the simulated galaxies.
 
@@
 \caption{The same selection window as adopted for selecting the \mbii\ simulated sample.
-The brown background cloud shows the overall \mbii\ sample at $z=1.5$.
-We add the random uncertainty to the simulation and select the ones fall into the targeting region (i.e.
-blue colored).
+The brown background cloud shows the simulated number density of the overall \mbii\ sample at $z=1.5$.
+We add the random uncertainty to the simulation and select the ones fall into the targeting region (i.e., blue colored).
 The orange dots are the \hst\ observed sample.}
@@
 The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the standard derivation of the residual.
-By fixing the slope to match the simulated data, the orange line shows the best-fit result for the observed data set.
+By fixing the slope to match the simulated data, the orange color shows the result for the observed data set.
 The grey cells in the background show the full \mbii\ simulated SMBHs.
@@
 The \sam\ model also consider the AGN feedback.
-However, in contrast to \mbii, the feeding process for the SMBH accretion is driven \blue{by the 2-body interaction of galaxy mergers}, and thus may be more stochastic and lead to the larger scatter.
-More specifically, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the  encounter.
-This introduces additional scatter since it depends on the properties of both interacting galaxies (see METHODS).
+However, in contrast to \mbii, the feeding process for the SMBH accretion is driven by the 2-body interaction of galaxy mergers, and thus may be more stochastic and lead to the larger scatter.
+More specifically, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the  encounter, which introduces additional scatter since it depends on the properties of both interacting galaxies (see METHODS).
 As a result, the \sam\ cloud extends to the high \mbh\ with low stellar mass, which may not exist.
@@
 In fact, our inferred intrinsic scatter of the observed sample is $\sim0.25$~dex, which is no more than the typical scatter of local relations reported in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}.
-Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level for the real data, but it is unlikely that systematic errors would conspire to {\it reduce} scatter.
+Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level of intrinsic scatter for the real data, but it is unlikely that systematic errors would conspire to {\it reduce} scatter.
 Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), resulting in an overestimating of the error-budget and thus underestimating of intrinsic scatter, but again it is hard to imagine that the \halpha\ \mbh\ estimators be much more precise than an factor of two.
@@
 %1. Imaging data. 2. Inferring host light. 3. Color inference. Rest frame R band and stellar mass.
-A detailed description of the \hst\ data analysis can be found in a companion paper (D19).
+A detailed description of the \hst\ data analysis can be found in a companion paper (D19~\cite{Ding2019}).
 Here we only present a brief summary of that study.
@@
 To decompose each AGN image, we assume the unresolved active nuclei as the scaled point source and the host galaxy as the \sersic\ profile.
-We adopt imaging modeling tool \lenstronomy\cite{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one by one from the library.
+We adopt imaging modeling tool \lenstronomy\cite{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one by one from the collected PSF library.
 Based on the reduced $\chi^2$, we are capable of evaluating the performance of each PSF.
@@
 
-\blue{To adopt the appropriate proxy in the \mbii\ simulation as stellar mass and compare to the observational datasets, we follow the common practice and collect the stellar mass within a 3D spherical aperture of 30 kpc.
-It has been shown that the stellar mass by this definition is more standard, which produces the stellar mass function that is consistent with observational constraints~\cite{Pillepich2018}.
-Further, the stellar mass in this physical aperture provides good agreement to those within Petrosian radii in observations \cite{Schaye2015}.
-}
+We follow the common practice and adopt the stellar mass within a 3D spherical aperture of 30 kpc to adopt as the more faithful proxy of the observed stellar mass in the \mbii\ simulation.
+It has been shown that this definition of the stellar produces a stellar mass function that is consistent with observational constraints~\cite{Pillepich2018}.
+Further, the stellar mass in this physical aperture provides good agreement to those measured within Petrosian radii in observational studies \cite{Schaye2015}.
 
@@
 Thus, we fit the host properties (i.e., \mstar) as a function of \mbh.
-We adopt the {\sc Scipy} package to estimate the best-fit inference and $1-\sigma$ confidence interval for the simulated sample.
+We adopt the {\sc Scipy} package to estimate the best-fit inference for the simulated sample.
 We then use the sample slope value to fit for the observations.
-The comparison results are showing in Figure~\ref{fig:MM_comp}.
-To estimate the scatter of the sample, we plot the histogram of the residual distribution, i.e., the sample deviation to their best-fit.
-The result is presented in Figure~\ref{fig:offset_comp}.
+The comparison results are showing in Figure~\ref{fig:MM_comp}, with the standard derivation of the residual indicated by the colored regions.
+To present the scatter of the sample, we also plot the histogram of the residual distribution, i.e., the sample deviation to their best-fit.
+The result is presented in Figure~\ref{fig:offset_comp} (left panel).
 We find the standard derivation of the residual for observed and \mbii\ sample are both equal to $\sim0.3$~dex; however, for \sam, the scatter value is much larger ($\sim0.7$~dex).
@@
 Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \mbii\ sample and the observational sample have the same intrinsic scatter level.
-We adopt the python package {\sc Linmix} to estimate this intrinsic scatter based on the \mbii\ overall sample and obtain the level as $0.25$~dex.
+We adopt the python package {\sc Linmix}\cite{Kelly2007} to estimate this intrinsic scatter based on the \mbii\ overall sample and obtain the level as $0.25$~dex.
 
@@
 \begin{tabular}{c c}
-\includegraphics[width=0.45\linewidth]{comp_scatter_ML.pdf} &
-\includegraphics[width=0.45\linewidth]{comp_scatter_MM.pdf} \\
+\includegraphics[width=0.45\linewidth]{comp_scatter_MM.pdf} &
+\includegraphics[width=0.45\linewidth]{comp_scatter_ML.pdf} \\
 \end{tabular}
@@
 JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
+TDM acknowledges funding from NSF ACI-1614853,  NSF AST-1616168 NASA ATP 80NSSC18K101 and NASA ATP 17-0123.
+We acknowledge support from INAF under PRIN SKA/ CTA FORECaST and PRIN SKA-CTA-INAF ASTRI/CTA Data Challenge.
 
@@
 and J.S.
-designed the \hst\ project and selected the AGN sample.
+designed the \hst\ project, selected the AGN sample, and wrote parts of the paper.
 A.B.
 and T.D.
-ran the \mbii\ simulation and provide the simulation data.
+ran the \mbii\ simulation and provide the  \mbii\ data.
 N.M.

### 2020-01-27 QSOII_paper/ApJ_manuscript/manuscript.tex
Update to change the template from NA to ApJ and consider the comments from Referee

--- 2019-11-25 NA_paper/manuscript_II/manuscript.tex
@@
-\documentclass{natureprintstyle}
-%\documentclass{nature}
-\bibliographystyle{naturemag}
-\usepackage{epsfig,caption}
-\usepackage{color}
-\usepackage{bm}
-\usepackage{graphicx}
-\usepackage{longtable}
-\usepackage{amssymb}
-\usepackage{rotating}
-\usepackage{latexsym}
-\usepackage{hyperref}
-\usepackage{float}
-\usepackage{soul}
-
-%\usepackage[switch]{lineno}
-%\linenumbers
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% comment for selecting the best figures to go on web for:
-%@arxiver{jvds_sami_vsigma_ellip_LOESS_Age_paper.pdf,jvds_sami_vsigma_ellip_LOESS_Age_transform_paper_resubmit.pdf} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%journal commands
-\newcommand{\apj}{Astrophys. J.}
-\newcommand{\spie}{Proc. SPIE}
-\newcommand{\pasp}{Publ. Astron. Soc. Pac.}
-\newcommand{\apjs}{Astrophys. J. Supp.}
-\newcommand{\araa}{Annu. Rev. Astron. Astrophys.}
-\newcommand{\mnras}{Mon. Not. R. Astron. Soc.}
-\newcommand{\apjl}{Astrophys. J. Let.}
-\newcommand{\aap}{Astron. Astrophys.}
-\newcommand{\aj}{Astron. J.}
-\newcommand{\nat}{Nature}
-\newcommand{\na}{New Astron. Rev.}
-\newcommand{\aaps}{A\&AS}
-\newcommand{\procspie}{Proc. SPIE}
+\documentclass[twocolumn,trackchanges]{aastex63}
+\newcommand{\vdag}{(v)^\dagger}
+\newcommand\aastex{AAS\TeX}
+\newcommand\latex{La\TeX}
 
@@
 % my commands
-
 \newcommand{\lcdm}{$\Lambda$CDM}
@@
 \newcommand{\mr}{$Mag_{\rm ~R}$}
-\newcommand{\jcap}{Journal of Cosmology and Astroparticle Physics}
 \newcommand{\halpha}{${\it H}\alpha$}
@@
 \newcommand{\reff}{{$R_{\mathrm{eff}}$}}
-%\newcommand{\kms}{km~s$^{\rm -1}$}
+\newcommand{\kmsMpc}{km~s$^{\rm -1}$~Mpc$^{\rm -1}$}
 \newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
@@
 \newcommand{\Civ}{C$_{\rm IV}$}
-\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
+%\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
 \newcommand{\sam}{\texttt{SAM}}
 \newcommand{\mbii}{\texttt{MBII}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
+\newcommand{\todo}[1]{\textcolor{red}{[{\bf Todo}: #1]}}  
+\newcommand{\aklant}[1]{\textcolor{blue}{[{\bf AKB}: #1]}} 
+\newcommand{\red}[1]{{ \textcolor{red}{#1}}}
+\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
+\newcommand{\pink}[1]{{ \textcolor{magenta}{#1}}}
+
+%% Reintroduced the \received and \accepted commands from AASTeX v5.2
+%\received{June 1, 2019}
+%\revised{January 10, 2019}
+%\accepted{\today}
+%% Command to document which AAS Journal the manuscript was submitted to.
+%% Adds "Submitted to " the argument.
+\submitjournal{ApJ}
+\shorttitle{A Successful Observational Test}
+\shortauthors{Ding et al.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}} 
-\newcommand{\aklant}[1]{\textcolor{blue}{[{\bf AKB}: #1]}}
-
-\newcommand{\red}[1]{{ \textcolor{red}{#1}}}
-\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
-
-\title{
-%From predictions to observation: scaling relations between supermassive black holes and their host galaxies at $1< z<2$
-A successful observational test of black hole and galaxy co-evolution models since $z\sim1.7$
-%The first comparison between the observation and simulation of the scaling relations between supermassive black holes and their host galaxies at $1.2< z<1.7$
-}
-\author{Xuheng Ding$^{1,2}$, 
-Tommaso Treu$^{1}$, 
-John D. Silverman$^{3, 4}$,
-Aklant K. Bhowmick$^{5,6}$,
-N. Menci$^{7}$,
-Tiziana Di Matteo$^{5}$
-}
+% my commands
 
 \begin{document}
+\title{A successful observational test of black hole and galaxy co-evolution models since $z\sim1.7$}
 
-\maketitle
+\correspondingauthor{Xuheng Ding}
+\email{dxh@astro.ucla.edu}
 
-\let\thefootnote\relax\footnote{
-\begin{affiliations}
-\item {Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA} 
-\item {School of Physics and Technology, Wuhan University, Wuhan 430072, China}
-\item {Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
-\item {Department of Astronomy, School of Science, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan}
-\item{McWilliams Center for Cosmology, Dept. of Physics, Carnegie Mellon University, Pittsburgh PA 15213, USA}
-\item{Department of Physics, University of Florida, Gainesville, FL 32611, USA}
-\item{INAF Osservatorio Astronomico di Roma, via Frascati 33, I-00078 Monteporzio, Italy}
-\end{affiliations}
-}
+\author[0000-0001-8917-2148]{Xuheng Ding}
+\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
+
+\author[0000-0002-8460-0390]{Tommaso Treu}
+\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
+
+\author[0000-0002-0000-6977]{John D. Silverman}
+\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan} 
+\affiliation{Department of Astronomy, School of Science, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan}
+
+\author[0000-0002-7080-2864]{Aklant K. Bhowmick}
+\affiliation{McWilliams Center for Cosmology, Dept. of Physics, Carnegie Mellon University, Pittsburgh PA 15213, USA}
+\affiliation{Department of Physics, University of Florida, Gainesville, FL 32611, USA}
+
+\author{N. Menci}
+\affiliation{INAF Osservatorio Astronomico di Roma, via Frascati 33, I-00078 Monteporzio, Italy}
+
+\author[0000-0002-6462-5734]{Tiziana Di Matteo}
+\affiliation{McWilliams Center for Cosmology, Dept. of Physics, Carnegie Mellon University, Pittsburgh PA 15213, USA}
 
 \begin{abstract}
-Supermassive black holes (SMBHs) ubiquitously occupy the center of massive galaxies in the local Universe and beyond.
-Their growth in mass (\mbh) appears to be closely linked to the physical properties of their host galaxies\cite{Mag++98, F+M00, M+H03, H+R04, Gul++09}, in particular the relation between \mbh ~and stellar mass (\mstar).
-With the origin of this correlation far from being fully understood, simulations have been a promising means to further interpret the observations over the last eight billion years ($z\lesssim1$) thus enabling substantial progress in this field.
+%\red{Background to be re-written}
+%With the origin of this correlation far from being fully understood, simulations have been a promising means to further interpret the observations over the last eight billion years ($z\lesssim1$) thus enabling substantial progress in this field.
 Constraints at higher redshifts ($z>1$), when most of the SMBHs acquired their mass, are more sensitive to initial conditions and the growth mechanisms and thus may be able to identify inaccurate or missing physics in the models.
 For this purpose, we have constructed a unique sample of 32 actively-accreting SMBHs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with accurate BH and stellar masses with the latter based on multi-band \hst\ imaging.
-We directly compare the measurements with two independent state-of-the-art projects, the hydrodynamic simulation \texttt{MassiveBlackII} (\mbii) and the semi-analytic model (\sam).
-After applying the observational selection function to models to account for bias, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
+\pink{To examine the scaling relations between the mass of a supermassive black hole (SMBH) and its host galaxy properties, we adopt the recent measurements based on 32 X-ray-selected broad-line Active Galactic Nucleus (AGNs) at $1.2<z<1.7$, and} make direct comparison with two independent state-of-the-art projects, including the hydrodynamic simulation \texttt{MassiveBlackII} (\mbii) and the semi-analytic model (\sam).
+After applying the observational selection function to the simulations to account for the bias, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
 However, accounting for observational errors, the dispersion in the mass ratio between \mbh\ and \mstar\ is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex) one.
 Hence, our observations can distinguish between the different recipes adopted in the models.
-The mass relations in \mbii ~are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to galaxy merger events triggering nuclear activity.
+The mass relations in the \mbii\ are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to galaxy merger events triggering nuclear activity.
 Moreover, the intrinsic scatter in the mass ratio of our high-$z$ sample is comparable to that observed in the local sample, all but ruling out the proposed scenario the correlations are purely stochastic in nature arising from some sort of cosmic central limit theorem.
@@
 
-%\section{Introduction}
+%% Keywords should appear after the \end{abstract} command. 
+%% See the online documentation for the full list of available subject
+%% keywords and the rules for their use.
+\keywords{Galaxy evolution(594), Active galaxies(17)}
 
-Various models have been proposed to explain the connection between SMBH and their host galaxies.
+%% From the front matter, we move on to the body of the paper.
+%% Sections are demarcated by \section and \subsection, respectively.
+%% Observe the use of the LaTeX \label
+%% command after the \subsection to give a symbolic KEY to the
+%% subsection for cross-referencing in a \ref command.
+%% You can use LaTeX's \ref and \label commands to keep track of
+%% cross-references to sections, equations, tables, and figures.
+%% That way, if you change the order of any elements, LaTeX will
+%% automatically renumber them.
+%%
+%% We recommend that authors also use the natbib ~\citep
+%% and ~\citet commands to identify citations.  The citations are
+%% tied to the reference list via symbolic KEYs. The KEY corresponds
+%% to the KEY in the \bibitem in the reference list below.
+
+\section{Introduction} \label{sec:intro}
+\blue{Supermassive black holes (SMBHs) ubiquitously occupy the center of massive galaxies in the local Universe and beyond.
+Their growth in mass (\mbh) appears to be closely linked to the physical properties of their host galaxies, in particular the relation between \mbh ~and stellar mass (\mstar)~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}, indicating a physical coupling during their co-evolution.}
+Various models have been proposed to explain this connection between SMBH and their host galaxies.
 A possible physical link may be feedback from an Active Galactic Nucleus (AGN) phase, assuming that a fraction of the AGN energy is injected into their surrounding gas thus regulating the growth of the SMBH and its host galaxy.
 In this scenario, AGN activity heats and unbinds a significant fraction of the gas and inhibits star formation.
-An alternatively and more indirect connection is one where AGN accretion and star formation are fed through a common gas supply~\cite{Cen2015, Menci2016}.
-A completely different view holds that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations without any direct physical mechanisms~\cite{Peng2007, Jahnke2011, Hirschmann2010}.
+An alternatively and more indirect connection is one where AGN accretion and star formation are fed through a common gas supply~\citep{Cen2015, Menci2016}.
+A completely different view holds that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations without any direct physical mechanisms~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
 From this central limit theorem, a stochastic cloud at high-$z$ (higher dispersion) would end up with scaling relations as observed today with lower dispersion.
 
-To understand this connection, recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have measured the scaling relations out to intermediate redshift {($0.3\lesssim z \lesssim1$)} by studying AGN and their host galaxies with {\it Hubble Space Telescope} ({\it HST}) and found an `observed' evolution in which the growth of SMBHs predates their host galaxies.
-However, the observational evidence of such evolution at higher-$z$ is under debate since it depends on our understanding of systematic uncertainties and selection effects~\cite{Tre++07,Lauer2007}.
-Therefore, an improper consideration of the uncertainties and selection effects may lead to an {\it apparent} evolution and result in an overestimate of the significance of the evolution\cite{Volonteri2011}.
+To understand this connection, recent works~\citep{Park15, Tre++07, Bennert11, Woo++08} have measured the scaling relations out to intermediate redshift {($0.3\lesssim z \lesssim1$)} by studying AGN and their host galaxies with {\it Hubble Space Telescope} ({\it HST}) and found an {\it observed} evolution in which the growth of SMBHs predates their host galaxies.
+However, the observational evidence of such evolution at higher-$z$ is under debate since it depends on our understanding of systematic uncertainties and selection effects~\citep{Tre++07,Lauer2007}.
+Therefore, an improper consideration of the uncertainties and selection effects may lead to an {\it apparent} evolution and result in an overestimate of the significance of the evolution~\citep{Volonteri2011}.
 
@@
 Recent studies, based on several simulations, show agreement with the observational data at intermediate redshifts ($z\lesssim1$).
-For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been utilized to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ that show a positive evolution where the SMBH growth predates that of its the host galaxy~\cite{DeG++15}.
-Several other works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014, Li2019}.
-Besides hydrodynamic simulations, semi-analytic models~\cite{Menci2014, Menci2016} have also made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}.
+For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been utilized to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ that show a positive evolution where the SMBH growth predates that of its the host galaxy~\citep{DeG++15}.
+Several other works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\citep{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\citep{Schaye2015}, and Illustris moving mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019}.
+Besides hydrodynamic simulations, semi-analytic models~\citep[][\ding{Hi Nicola, do you think we can refer Thomas2019 here as another semi-analytic model?}]{Menci2014, Menci2016, Thomas2019} have also made remarkable progress and recovered the local scaling relations~\citep{Kormendy13}.
 However, comparisons between simulations and the observed scaling relations, based on high-resolution \hst\ imaging, are still mostly limited to $z<1$ due to prior limitations of observational data.
 
+\blue{
+In this study, we push our knowledge of the mass relations to earlier epochs.
+We establish the mass ratios between the SMBHs and their host using 32 type-1 AGNs and make direct comparisons to the predicted type-1 AGNs based on two independent state-of-the-art numerical simulations.}
+\ding{The referee \#2 asks us to comment on what kinds of biases may be introducing since we use only type-1 AGNs. Xuheng thinks this request is trivial and let's ignore this.}
+\blue{The redshift range of our targets is chosen to be high enough ($z>1$) when most of the SMBHs acquired their mass, are more sensitive to initial
+conditions and the growth mechanisms and thus may be able to identify inaccurate or missing physics in the models,  while low enough ($z<2$) to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy.
+We describe the observed and simulated targets in Section~\ref{sec:sample}.
+The comparison result are shown in Section~\ref{sec:result} with conclusion presented in Section~\ref{sec:conclusion}.
+Throughout this paper, we adopt a standard concordance
+cosmology with $H_0 = 70$~\kmsMpc
+, $\Omega_m = 0.30$,
+and $\Omega_\Lambda = 0.70$. A Salpeter initial mass function is employed consistently to the
+observed and simulated sample.
+}
+
+\pink{
+\section{Sample: Observation and Simulation}~\label{sec:sample}
 % The work that we want to do
@@
 	%mention the scatter.
-To push our knowledge of the mass relations to earlier epochs, we have been analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields, namely COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008} (D19~\cite{Ding2019} hereafter).
-The redshift range of our targets is chosen to be high enough ($z>1$) to establish the mass ratios of accreting SMBHs and to make direct comparisons to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy.
+In this section, we introduce the comparison samples of the scaling relations, using the observed data (Section~\ref{hst_sample}) and the predicted ones using two independent numerical simulations (Section~\ref{sample_sim}).}
+
+\subsection{HST Observational data}\label{hst_sample}
+
+We have been analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} (D19~\citep{Ding2019} hereafter).
 We selected our AGN sample in a well-defined window based on the \mbh\ and Eddington ratio, as shown in Figure~1 in D19.
@@
 Regarding the detection of the host galaxies, the X-ray selected nature of the sample results in slightly lower nuclear-to-host ratios, which facilitates the inference of the host light.
-We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy.
+%We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy.
 Moreover, 21/23 systems have \hst/ACS imaging data, which enables us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see METHODS and the descriptions in D19).
-%We furthermore combining them with the ground-based photometry to carry out the SED fitting, and thus derive the reliable host rest-frame R band luminosity and stellar mass.
 
-%\begin{figure}[t]
-%\includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
-%\caption{The selection for the 32 AGN sample.
-The top and right panels are the BH mass function and Eddington ratio function.
-\ding{More descriptions are needed if Figure1 is finally decided to show.}
-%}
-%\label{fig:AGN_select}
-%\end{figure}
+\blue{We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy.
+A detailed description of the \hst\ data analysis can be found in a companion paper ~\citep[][D19 hereafter]{Ding2019}.
+Here we only present a brief summary of that study.
+We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ (according to the redshift of the targets) to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman).
+We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to co-add the final image with pixel scale as 0\farcs0642.
+To mitigate the contamination by the background light from both the sky and the detector, we adopt the {\sc photuils} tools to estimate and remove them accurately.}
 
-To compare with simulations, we use two independent efforts, the \texttt{MassiveBlackII} (\texttt{MBII})~\cite{Khandai2015} and the semi-analytic model (\texttt{SAM})~\cite{Menci2014}.
+\blue{To address the bias which might be raised by the unknown PSF, we manually collect the isolated-unsaturated PSF-stars from the 32 observed fields, to assemble a PSF library for the fitting.
+To decompose each AGN image, we assume the unresolved active nuclei as the scaled point source and the host galaxy as the \sersic\ profile.
+We adopt imaging modeling tool \lenstronomy~\citep{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one by one from the collected PSF library.
+Based on the reduced $\chi^2$, we are capable of evaluating the performance of each PSF.
+We adopt the result from the top-ranked-eight PSFs and using the weighting process to obtain the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.}
+
+\blue{The COSMOS survey provides \hst\ ACS/F814W imaging data for 21 of 32 AGN in our sample with a drizzled pixel scale as 0\farcs03.
+We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3's result to infer the host color.
+We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar).}
+
+\pink{We note that in \citet{Sun2015}, a sample of 69 type-1 AGN has been studied to measure the mass relations at redshift range $0<z<2$.
+Nevertheless, aiming at achieving a direct comparison to the simulations, we selected not to take their sample given that their sample is chosen with the incongruous selection function.
+Moreover, their \mstar\ is inferred by fitting the spectral energy distribution, and \mbh\ is estimated using different broad lines (i.e., \hbeta\ and \Mgii), which could both introduce larger systematics.}
+
+\subsection{Numerical simulations}\label{sample_sim}
+To compare with simulations, we use two independent efforts, the \texttt{MassiveBlackII} (\texttt{MBII})~\citep{Khandai2015} and the semi-analytic model (\texttt{SAM})~\citep{Menci2014}.
 These simulations are based on independent model strategies, i.e., hydrodynamic simulation for \mbii\ and semi-analytic model for \sam, respectively.
+
 The \mbii\ simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
@@
 While high-resolution N-body simulations can study specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam.
-In previous works, \mbii~\cite{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\cite{Menci2014, Menci2016} have made high successful predictions; we refer the interested readers to the METHODS section for more details.
+In previous works, \mbii~\citep{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\citep{Menci2014, Menci2016} have made high successful predictions.
+\blue{In the following two sections, we present the detailed information of the two simulation projects.}
+
+\subsubsection{\texttt{MassiveBlackII} simulation}
+The MassiveBlackII (\mbii) is a high-resolution cosmological hydrodynamic simulation using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\citep{2005MNRAS.364.1105S}.
+It has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles.
+The resolution elements for dark matter and gas have masses of $1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$, respectively.
+The base cosmology corresponds to the results of WMAP7 ~\citep{2011ApJS..192...18K}, i.e., $\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.
+The simulation includes a full modeling of gravity + gas hydrodynamics, as well as a wide range of subgrid recipes for the modeling of star formation ~\citep{2003MNRAS.339..289S}, black hole growth and feedback processes.
+Haloes were identified using a Friends-of-Friends (FOF) group finder ~\citep{1985ApJ...292..371D}.
+Within these haloes, self-bound substructures/subhaloes were identified using \texttt{SUBFIND} ~\citep{2005MNRAS.364.1105S}.
+Galaxies are identified to the stellar matter components of the subhaloes.
+
+For the modeling of black hole growth, a feedback prescription is adopted as detailed in the literature ~\citep{2005Natur.433..604D, 2005MNRAS.361..776S}.
+In particular, seed black holes of mass $5\times 10^{5}~M_{\odot}/h$ are inserted into haloes of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$~(if they do not already contain a black hole).
+Once seeded, black hole growth occurs via gas accretion at a rate given by $\dot{M}_{bh}={4\pi G^2 M_{bh}^2 \rho}/{(c_s^2+v_{bh}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the ISM gas~(cold phase); $v_{bh}$ is the relative velocity between the black hole and the gas in its vicinity.
+$10\%$~(radiative efficiency) of the accreted gas is released as radiation.
+The accretion rate is allowed to be mildly super-Eddington, i.e., limited to two times the Eddington accretion rate.
+A fraction~($5\%$) of the radiated energy couples to the surrounding gas as black hole~(or AGN) feedback ~\citep{2005Natur.433..604D}.
+For the modeling of black hole mergers, two black holes are considered to be merged if their separation distance is within the spatial resolution of the simulation~(the SPH smoothing length), and their relative speeds are lower than the local sound speed of the medium.
+
+For the galaxy photometry, the spectral energy distributions~(SEDs) of the host galaxies were first obtained by summing up the contributions from the individual star particles.
+The stellar SEDs were modelled using the \texttt{PEGASE-2}~\citep{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF.
+The galaxy SEDs are finally convolved with the desired filter function to obtain the broad band photometry~(SDSS $r$ band magnitude).
+
+We follow the common practice and adopt the stellar mass within a 3D spherical aperture of 30 kpc to adopt as the more faithful proxy of the observed stellar mass in the \mbii\ simulation.
+It has been shown that this definition of the stellar produces a stellar mass function that is consistent with observational constraints~\citep{Pillepich2018}.
+Further, the stellar mass in this physical aperture provides good agreement to those measured within Petrosian radii in observational studies ~\citep{Schaye2015}.
+
+For further details regarding the \mbii\ simulation, we refer the reader to the reference~\citep{2015MNRAS.450.1349K}.
+
+\subsubsection{Semi-analytic model}
+\label{sec_intro_SAM}
+The Semi-analytic model (\sam) is fully described in~\citet{Menci2016}.
+Here, we highlight the main points with respect to our study.
+The merger trees of dark matter haloes are generated through a Monte Carlo procedure by adopting merger rates using an Extended Press \& Schechter formalism~\citep{Lacey1993} assuming a Cold Dark Matter power spectrum of perturbations.
+For dark matter halos  that merge with a larger halo, we assess the impact of dynamical friction to determine whether it will survive as a satellite, or sink to the centre to increase the mass of the central dominant galaxy; binary interactions (fly-by and merging), among satellite sub-halos, are also described by the model.
+In each halo, we compute the amount of gas which cools due through atomic processes and settles into a rotationally-supported disk~\citep{Mo1998}.
+The gas is converted into stars through three different channels: (1) quiescent star formation gradually converting the gas into stars over long timescales $\sim 1$~Gyr, (2) starbursts following galaxy interactions, occurring on timescales $\lesssim 100$~Myr, associated to BH feeding, (3) internal disc instabilities triggering loss of angular momentum resulting into gas inflows toward the centre thus feeding star formation and BH accretion.
+The energy released by the supernovae associated with the total star formation returns a fraction of the disc gas into a hot phase (stellar feedback).
+
+The semi-analytic model includes BH growth from primordial seeds.
+These are assumed to originate from PopIII stars with a mass $M_{seed}=100\,M_{\odot}$~\citep{Madau2001}, and to be initially present in all galaxy progenitors.
+We consider two BH feeding modes: accretion triggered by galaxy interactions and internal disc instabilities.
+These are described in detail in our previous work~\citep{Menci2016}, and briefly described below.\newline
+1) BH accretion triggered by interactions.
+The interaction rate $\tau_r^{-1}=n_T\,\Sigma (r_t,v_c,V)\,V_{rel} (V)$ for galaxies with relative velocity $V_{rel}$ and number density $n_T$ in a common DM halo determines the probability for encounters,
+either fly-by or  merging, through the corresponding cross sections $\Sigma$ given in~\citet{Menci2014}. The fraction of
+gas destabilized in each interaction corresponds to the loss $\Delta j$ of orbital angular momentum $j$, and depends on the mass ratio of the merging partners $M'/M$ and on the impact factor $b$.
+\newline
+2) BH accretion induced by disc instabilities.
+We assume these to arise  in  galaxies with disc mass exceeding~\citep{Efstathiou1982} $M_{crit} =  {v_{max}^2 R_{d}/ G \epsilon}$ with $\epsilon=0.75$, where $v_{max}$ is the maximum circular velocity associated to each halo ~\citep{Mo1998}.
+Such a criterion strongly suppresses the probability for disc instabilities to occur not only in massive, gas-poor galaxies, but also in 
+dwarf galaxies characterized by small values of the gas-to-DM mass ratios.
+The instabilities induce loss of angular momentum resulting into strong inflows that we compute following the 
+description in~\citet{Hopkins2011}, recast and extended as in~\citet{Menci2014}.
+
+Finally, the \sam\ model includes a detailed treatment of AGN feedback, presented and discussed in~\citet{Menci2008}.
+This is assumed to stem from the fast winds with velocity up to
+$10^{-1}c$ observed in the central regions of AGNs~\citep{Chartas2002, Pounds2003}.  
+These supersonic outflows compress the gas into a blast wave terminated by
+a leading shock front, which  moves outwards with a lower but still
+supersonic speed and sweeps out the surrounding medium. Eventually,
+this medium is expelled from the galaxy. The model follows in detail the expansion of the 
+blast wave through the galaxy disc, and computes the fraction of gas expelled from the galaxy.  
+These depend on the ratio $\Delta E/E$ between the  energy injected into the galactic gas 
+(taken to be proportional to the energy radiated by the 
+AGN through the efficiency $\epsilon_{AGN}=5\times 10^{-2}$)
+and the thermal energy of the unperturbed gas (see~\citep{Menci2008} for details).
 
@@
 
-%\section*{Results}
+\section{Comparison Results}
+\label{sec:result}
 %Selection effect into account
-Using \mbii, we identify a sample of simulated AGNs at $z=1.5$ (see METHOD) and compare their predicted scaling relations to the observed ones.
+Using \mbii, we identify a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones.
 We take the measurement uncertainty and selection biases into account to ensure a fair comparison.
@@
 
-In Figure~\ref{fig:MM_comp} (left panel), we compare the relation \mbh--\mstar~between observations and the \mbii\ simulation.
-First, it is clear that the simulated and observed samples are in good agreement.
-To quantify the agreement level, we perform a linear regression to fit the simulated relations and estimate the best-fit inference.
+We compare the relation \mbh--\mstar~between observations and the \mbii\ simulation. First, it is clear that the simulated and observed samples are in good agreement. 
+\blue{To quantify the agreement between the simulation and the observation, we use a linear regression to fit their relations and compare the result.
+Our selection window has a hard cut on the \mbh\ value (i.e., vertical direction in Figure~\ref{fig:selectfunc}), and thus the scatter on the host properties are larger (horizontal direction).
+Thus, we fit the host properties (i.e., \mstar) as a function of \mbh.
+We adopt the {\sc Scipy} package to estimate the best-fit inference for the simulated sample.
+We then fit for the observations based on the same slope value.
+The comparison results are showing in Figure~\ref{fig:MM_comp} (left panel), with the standard derivation of the residual indicated by the colored regions.}
+\pink{To estimate the {\it observed} scatter of the sample, we calculate the standard deviation of the fitting residual based on \mstar\ (i.e., along the $x$-axis).}\blue{The histogram of the residual is presented in Figure~\ref{fig:offset_comp} (left panel).
+We find the standard derivation of the residual for observed and \mbii\ sample are at the same level and both equal to $\sim0.3$~dex.}\pink{We test to vary the fixed slope value by its uncertainty level but found the corresponding {\it observed} scatters barely changed ($<1\%$), meaning that the inferred scatter weakly depends on the fitted slope.
+Note that, with a different definition of the {\it observed} scatter, the measured value could be different.
+In this particular work, we simply apply a common standard (i.e., consider the measured residual in \mstar) to achieve a direct comparison between different samples.}\blue{We perform the Kolmogorov-Smirnov (KS) test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$.
+Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \mbii\ sample and the observational sample have the same intrinsic scatter level.
+We adopt the python package {\sc Linmix}~\citep{Kelly2007} to estimate this {\it intrinsic} scatter based on the \mbii\ overall sample and obtain the level as $0.25$~dex.
+}
+%Overlapped part when change template to ApJ:To quantify the agreement level, we perform a linear regression to fit the simulated relations and estimate the best-fit inference.
 To make a direct comparison, we fix the same slope value and obtain the best-fit intercept value for the observation.
@@
 We also compare our data to the predictions by the \sam\ model.
-Rather than N-body simulation which produces individual simulating objects, the \sam\ model uses the density clouds to describe the possibility of the samples.
-%We consider the sample at $z=1.5$ epoch for two sample sets, including the overall sample and the selected sample, as shown in Figure~\ref{fig:SAM_comp}.
-We find that considering the selecting effect, the direct prediction by \sam\ is well matched to the observed relations.
-%We do not estimate the scatter for \sam\ model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one.
-\ding{This is not right yet.
-But if consider the scatter in the same way, the \sam\ have large scatter?}
-%Yet this is not a proper comparison since the direct sample from \sam\ does not include the scattering effect by the measurement uncertainty.
-To make a direct comparison, we first randomly generate an overall \sam\ sample based on the probability clouds at $z=1.5$.
+Rather than N-body simulation which produces individual simulating objects, the \sam\ model\pink{uses the interaction-driven model~\citep{Menci2014} to calculate the number density of the galaxies.} To make a direct comparison, we first randomly produce an overall sample based on the \pink{\sam\ predicted number density} at $z=1.5$.
 Then, as in the \mbii\ analysis, we inject random scatter in the sample to account for uncertainties and apply the observational selection function.
@@
 We find that the best-fit result by the \sam\ model is well matched to the observation.
-However, the scatter of the \sam\ model is significantly larger ($0.7$~dex) than observed (this is the total scatter accounting for the intrinsic scatter in the \sam\ distribution, observational uncertainties, and selection effects).
+However, the scatter of the \sam\ model is significantly larger ($\sim0.7$~dex) than observed (this is the total scatter accounting for the intrinsic scatter in the \sam\ distribution, observational uncertainties, and selection effects).
 
+ \ding{Do we want to mention that the inferred slope of the MBII is much steeper than the SAM ones?
+It is a little complicated, since we have a limited MBH range and fitted slope value may be related to the scatter of the sample.
+Maybe we can currently ignore this and let's see the feedback by the referee.}
 %\begin{figure*}[t]%[!b]
@@
 
+\blue{We also present the comparison of the \mbh-\mr\ relations in Figure~\ref{fig:ML_comp} and the comparison of the scatter in Figure~\ref{fig:offset_comp} (right panel).
+The results are similar to \mbh-\mstar\ relations.}
+
+\begin{figure*}[t]%[!b]
+\begin{tabular}{c c}
+\includegraphics[trim = 0mm 0mm 61mm 0mm, clip, width=0.47\linewidth]{MBII_ML.pdf} &
+\includegraphics[trim = 0mm 0mm 61mm 0mm, clip, width=0.47\linewidth]{SAM_ML_consider_nois.pdf} \\
+\end{tabular}
+\caption{Same as the Figure~\ref{fig:MM_comp}, but for \mbh-\mr\ relation.}
+\label{fig:ML_comp}
+\end{figure*}
+
+\begin{figure*}[t]%[!b]
+\begin{tabular}{c c}
+\includegraphics[width=0.45\linewidth]{comp_scatter_MM.pdf} &
+\includegraphics[width=0.45\linewidth]{comp_scatter_ML.pdf} \\
+\end{tabular}
+\caption{The histogram of the scatter (i.e., residuals in the linear relation).
+The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, \mbii\ sample and \sam\ sample, respectively, for both \mbh-\mstar\ and \mbh-\mr\ relations.
+}
+\label{fig:offset_comp}
+\end{figure*}
+
 To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
 For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3.
-For the simulated sample, we consider the AGN bolometric correction~\cite{Elvis1994} to estimate the AGN light flux at WFC3/F125W band.
+For the simulated sample, we consider the AGN bolometric correction~\citep{Elvis1994} to estimate the AGN light flux at WFC3/F125W band.
 We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched to each other.
 The median values for the flux ratio distribution of the observed, \mbii, \sam\ sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively.
-We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are $0.34$ (for observed -- \mbii) and $0.14$ (for observed -- \sam), respectively.
-This result indicates the three samples have similar host-to-total light ratio distribution.
+We perform the KS test the inferred p-values are $0.34$ (for observed -- \mbii) and $0.14$ (for observed -- \sam), respectively.\pink{These results indicate that one cannot reject the hypothesis that the distributions of the three samples are the same at $10\%$.}
 
@@
 
+\section{Concluding Remarks}
+\label{sec:conclusion}
 In terms of their central distribution, the \mbii\ simulation and \sam\ model are both in agreement with the observational data.
@@
 However, in contrast to \mbii, the feeding process for the SMBH accretion is driven by the 2-body interaction of galaxy mergers, and thus may be more stochastic and lead to the larger scatter.
-More specifically, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the  encounter, which introduces additional scatter since it depends on the properties of both interacting galaxies (see METHODS).
+More specifically, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the  encounter, which introduces additional scatter since it depends on the properties of both interacting galaxies (see Section~\ref{sec_intro_SAM}).
 As a result, the \sam\ cloud extends to the high \mbh\ with low stellar mass, which may not exist.
@@
 
-Without any physical mechanisms, it has been shown that just due to the the central limit theorem~\cite{Peng2007, Jahnke2011, Hirschmann2010} scaling relations may emerge from random mergers, starting from a stochastic cloud in the early universe.
+%The difference in the SAM and MBII are not only AGN feedback. 
+% It is still unclear how much different in scatter between MBII and SAM is due to the AGN feedback. A directly work using one simulation is needed to be done.
+\pink{The fact that one model (i.e., \sam) does not agree with the observed dispersion is not direct evidence that supports all the physical assumptions implemented in the other model (i.e., \mbii), especially when these two models adopt completely different numerical techniques.
+At present, it is still unclear how much difference in the observed scatter between \mbii\ and \sam\ is due to the different recipes of triggering, hierarchical merging, gas fueling, and AGN feedback.
+For instance, even without introducing AGN feedback, the predictions by \citet{2017MNRAS.464.2840A} could also have low scatter products in their simulation.
+It will be more insightful to carry out a comparative test based on one numerical model that using different the AGN feedback assumptions, and setting all the other conditions as the same \citep[see][as a glimpse]{Hopkins2009}.
+}
+
+Without any physical mechanisms, it has been shown that just due to the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010} scaling relations may emerge from random mergers, starting from a stochastic cloud in the early universe.
 In this scenario, the scatter of the scaling relations has to increase with redshift.
-Our observations contradict this hypothesis.
-In fact, our inferred intrinsic scatter of the observed sample is $\sim0.25$~dex, which is no more than the typical scatter of local relations reported in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}.
-Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level of intrinsic scatter for the real data, but it is unlikely that systematic errors would conspire to {\it reduce} scatter.
+Our observations contradict this hypothesis.\pink{In fact, the inferred {\it intrinsic} scatter of our observed sample (i.e., $\sim0.25$~dex) is even no more significant than the typical scatter of local relations reported in the literature ~\citep[][i.e., $\gtrsim0.35$~dex]{Kormendy13, Gul++09, Reines2015}.} Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level of intrinsic scatter for the real data, but it is unlikely that systematic errors would conspire to {\it reduce} scatter.
 Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), resulting in an overestimating of the error-budget and thus underestimating of intrinsic scatter, but again it is hard to imagine that the \halpha\ \mbh\ estimators be much more precise than an factor of two.
 
-Extending this study to even higher redshift would be very beneficial, probing closer to the epoch of formation of massive galaxies and supermassive blackes.
+Extending this study to even higher redshift would be very beneficial, probing closer to the epoch of formation of massive galaxies and SMBHs.
 For higher redshift, the {\it James Webb Space Telescope} may provide high-quality imaging data of AGNs at redshift up to $z\sim7$.
@@
 %\\1. How do we discuss the role of AGN feedback?.
-
-\begin{center}
-{\bf \Large \uppercase{Methods} }
-\end{center}
-
-%\textbf{Observation data.} Our 32 new AGN systems are selected from four X-ray coverage fields including COSMOS (Civano et al.
-2016), (E)- CDFS-S (Lehmer et al.
-2005; Xue et al.
-2011), and SXDS (Ueda et al.
-2008) at redshift range $1.2<z<1.7$.
-The X-ray selected sample have low nuclear-to-host ratios, which facilitates the extraction of the host properties.
-We adopt the \hst/WFC3 infrared channel to derive the high spatial resolution imaging data, to carry out the decomposition of the AGN-host using two-dimensional flux distribution.
-The details of the \hst\ observation and the study are presented in the companion paper.
-Moreover, 21/32 systems have \hst/ACS band, together with some other ground-based observations, which would provide the host information in the other bands.
-In the next section, we infer the reliable K-correction for the rest-frame R band luminosity and the SED to infer the stellar mass.
-The \mbh\ of our sample have been estimated by \halpha\ and \hbeta\ in the FMOS survey.
-Comparing to the \Mgii\ and \Civ, the \mbh\ by broad Balmer lines are more trustworthy.
-The estimated value of the \mbh\ are listed in the companion paper.
-%\textcolor{blue}{Do we need to list the \mbh\ and host properties in a table in this paper?}
-
-\textbf{HST Observations.} 
-%1. Imaging data. 2. Inferring host light. 3. Color inference. Rest frame R band and stellar mass.
-A detailed description of the \hst\ data analysis can be found in a companion paper (D19~\cite{Ding2019}).
-Here we only present a brief summary of that study.
-We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ (according to the redshift of the targets) to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman).
-We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to co-add the final image with pixel scale as 0\farcs0642.
-To mitigate the contamination by the background light from both the sky and the detector, we adopt the {\sc photuils} tools to estimate and remove them accurately.
-
-To address the bias which might be raised by the unknown PSF, we manually collect the isolated-unsaturated PSF-stars from the 32 observed fields, to assemble a PSF library for the fitting.
-To decompose each AGN image, we assume the unresolved active nuclei as the scaled point source and the host galaxy as the \sersic\ profile.
-We adopt imaging modeling tool \lenstronomy\cite{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one by one from the collected PSF library.
-Based on the reduced $\chi^2$, we are capable of evaluating the performance of each PSF.
-We adopt the result from the top-ranked-eight PSFs and using the weighting process to obtain the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.
-
-The COSMOS survey provides \hst\ ACS/F814W imaging data for 21 of 32 AGN in our sample with a drizzled pixel scale as 0\farcs03.
-We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3's result to infer the host color.
-We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the rest-frame R band luminosity and stellar mass.
-A Salpeter initial mass function is employed consistently to the observed and simulated sample.
-
-%\textbf{SED fitting and host properties}
-%We perform the SED fitting to derive the robust physical properties of the host galaxy, including the rest-frame R band luminosity and stellar mass. 
-%21/32 AGN systems have rest-frame UV imaging data by \hst-ACS/F814W\cite{Scoville2007}.
-We perform the same approach to decompose the photometry of the host light at UV.
-Since the host inference by IR band is superior to the one by UV band, while fitting UV image, we fix the \reff\ and \sersic\ index as the value inferred by \hst/WFC3 to derive the host flux.
-%We furthermore combine the \hst\ inference to the ground-based AGN photometry to carry out the SED fitting. \textcolor{blue}{Details and the figures need to be presented.}
-%Adopting the best fit SED stellar template to the \hst/WFC3 flux, we derive the \lhost${,_R}$ and \mstar.
-
-%\textbf{Simulations.} 
-%Describe the approaches used in the simulation.
-
-\textbf{\texttt{MassiveBlackII} simulation}.  
-The MassiveBlackII (\mbii) is a high-resolution cosmological hydrodynamic simulation using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\cite{2005MNRAS.364.1105S}.
-It has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles.
-The resolution elements for dark matter and gas have masses of $1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$, respectively.
-The base cosmology corresponds to the results of WMAP7 \cite{2011ApJS..192...18K}, i.e., $\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.
-The simulation includes a full modeling of gravity + gas hydrodynamics, as well as a wide range of subgrid recipes for the modeling of star formation \cite{2003MNRAS.339..289S}, black hole growth and feedback processes.
-Haloes were identified using a Friends-of-Friends (FOF) group finder \cite{1985ApJ...292..371D}.
-Within these haloes, self-bound substructures/subhaloes were identified using \texttt{SUBFIND} \cite{2005MNRAS.364.1105S}.
-Galaxies are identified to the stellar matter components of the subhaloes.
-
-For the modeling of black hole growth, a feedback prescription is adopted as detailed in the literature \cite{2005Natur.433..604D, 2005MNRAS.361..776S}.
-In particular, seed black holes of mass $5\times 10^{5}~M_{\odot}/h$ are inserted into haloes of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$~(if they do not already contain a black hole).
-Once seeded, black hole growth occurs via gas accretion at a rate given by $\dot{M}_{bh}={4\pi G^2 M_{bh}^2 \rho}/{(c_s^2+v_{bh}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the ISM gas~(cold phase); $v_{bh}$ is the relative velocity between the black hole and the gas in its vicinity.
-$10\%$~(radiative efficiency) of the accreted gas is released as radiation.
-The accretion rate is allowed to be mildly super-Eddington, i.e., limited to two times the Eddington accretion rate.
-A fraction~($5\%$) of the radiated energy couples to the surrounding gas as black hole~(or AGN) feedback \cite{2005Natur.433..604D}.
-For the modeling of black hole mergers, two black holes are considered to be merged if their separation distance is within the spatial resolution of the simulation~(the SPH smoothing length), and their relative speeds are lower than the local sound speed of the medium.
-
-For the galaxy photometry, the spectral energy distributions~(SEDs) of the host galaxies were first obtained by summing up the contributions from the individual star particles.
-The stellar SEDs were modelled using the \texttt{PEGASE-2}~\cite{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF.
-The galaxy SEDs are finally convolved with the desired filter function to obtain the broad band photometry~(SDSS $r$ band magnitude).
-
-We follow the common practice and adopt the stellar mass within a 3D spherical aperture of 30 kpc to adopt as the more faithful proxy of the observed stellar mass in the \mbii\ simulation.
-It has been shown that this definition of the stellar produces a stellar mass function that is consistent with observational constraints~\cite{Pillepich2018}.
-Further, the stellar mass in this physical aperture provides good agreement to those measured within Petrosian radii in observational studies \cite{Schaye2015}.
-
-For further details regarding the \mbii\ simulation, we refer the reader to the reference~\cite{2015MNRAS.450.1349K}.
-
-\textbf{Semi-analytic model}.
-The Semi-analytic model (\sam) is fully described in Menci et al.
-(2016)~\cite{Menci2016}.
-Here, we highlight the main points with respect to our study.
-The merger trees of dark matter haloes are generated through a Monte Carlo procedure by adopting merger rates using an Extended Press \& Schechter formalism~\cite{Lacey1993} assuming a Cold Dark Matter power spectrum of perturbations.
-For dark matter halos  that merge with a larger halo, we assess the impact of dynamical friction to determine whether it will survive as a satellite, or sink to the centre to increase the mass of the central dominant galaxy; binary interactions (fly-by and merging), among satellite sub-halos, are also described by the model.
-In each halo, we compute the amount of gas which cools due through atomic processes and settles into a rotationally-supported disk~\cite{Mo1998}.
-The gas is converted into stars through three different channels: (1) quiescent star formation gradually converting the gas into stars over long timescales $\sim 1$~Gyr, (2) starbursts following galaxy interactions, occurring on timescales $\lesssim 100$~Myr, associated to BH feeding, (3) internal disc instabilities triggering loss of angular momentum resulting into gas inflows toward the centre thus feeding star formation and BH accretion.
-The energy released by the supernovae associated with the total star formation returns a fraction of the disc gas into a hot phase (stellar feedback).
-
-The semi-analytic model includes BH growth from primordial seeds.
-These are assumed to originate from PopIII stars with a mass $M_{seed}=100\,M_{\odot}$~\cite{Madau2001}, and to be initially present in all galaxy progenitors.
-We consider two BH feeding modes: accretion triggered by galaxy interactions and internal disc instabilities.
-These are described in detail in our previous work~\cite{Menci2016}, and briefly described below.\newline
-1) BH accretion triggered by interactions.
-The interaction rate $\tau_r^{-1}=n_T\,\Sigma (r_t,v_c,V)\,V_{rel} (V)$ for galaxies with relative velocity $V_{rel}$ and number density $n_T$ in a common DM halo determines the probability for encounters,
-either fly-by or  merging, through the corresponding cross sections $\Sigma$ given in Menci et al. (2014)~\cite{Menci2014}. The fraction of
-gas destabilized in each interaction corresponds to the loss $\Delta j$ of orbital angular momentum $j$, and depends on the mass ratio of the merging partners $M'/M$ and on the impact factor $b$.
-\newline
-2) BH accretion induced by disc instabilities.
-We assume these to arise  in  galaxies with disc mass exceeding~\cite{Efstathiou1982} $M_{crit} =  {v_{max}^2 R_{d}/ G \epsilon}$ with $\epsilon=0.75$, where $v_{max}$ is the maximum circular velocity associated to each halo \cite{Mo1998}.
-Such a criterion strongly suppresses the probability for disc instabilities to occur not only in massive, gas-poor galaxies, but also in 
-dwarf galaxies characterized by small values of the gas-to-DM mass ratios.
-The instabilities induce loss of angular momentum resulting into strong inflows that we compute following the 
-description in Hopkins et al. (2011)~\cite{Hopkins2011}, recast and extended as in Menci et al. (2014)~\cite{Menci2014}.
-
-Finally, the \sam\ model includes a detailed treatment of AGN feedback, presented and discussed in Menci et al. (2008)~\cite{Menci2008}.
-This is assumed to stem from the fast winds with velocity up to
-$10^{-1}c$ observed in the central regions of AGNs~\cite{Chartas2002, Pounds2003}.  
-These supersonic outflows compress the gas into a blast wave terminated by
-a leading shock front, which  moves outwards with a lower but still
-supersonic speed and sweeps out the surrounding medium. Eventually,
-this medium is expelled from the galaxy. The model follows in detail the expansion of the 
-blast wave through the galaxy disc, and computes the fraction of gas expelled from the galaxy.  
-These depend on the ratio $\Delta E/E$ between the  energy injected into the galactic gas 
-(taken to be proportional to the energy radiated by the 
-AGN through the efficiency $\epsilon_{AGN}=5\times 10^{-2}$)
-and the thermal energy of the unperturbed gas (see Menci et al. (2008)~\cite{Menci2008} for details).
-
-\textbf{Linear fitting and scatter comparison}.  
-%How the fitting is done. The comparing of the histogram and the KS test. The scatter. Figures.
-To quantify the agreement between the simulation and the observation, we use a linear regression to fit their relations and compare the result.
-Our selection window has a hard cut on the \mbh\ value (i.e., vertical direction in Figure~\ref{fig:selectfunc}), and thus the scatter on the host properties are larger (horizontal direction).
-Thus, we fit the host properties (i.e., \mstar) as a function of \mbh.
-We adopt the {\sc Scipy} package to estimate the best-fit inference for the simulated sample.
-We then use the sample slope value to fit for the observations.
-The comparison results are showing in Figure~\ref{fig:MM_comp}, with the standard derivation of the residual indicated by the colored regions.
-To present the scatter of the sample, we also plot the histogram of the residual distribution, i.e., the sample deviation to their best-fit.
-The result is presented in Figure~\ref{fig:offset_comp} (left panel).
-We find the standard derivation of the residual for observed and \mbii\ sample are both equal to $\sim0.3$~dex; however, for \sam, the scatter value is much larger ($\sim0.7$~dex).
-We perform the KS test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$.
-Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \mbii\ sample and the observational sample have the same intrinsic scatter level.
-We adopt the python package {\sc Linmix}\cite{Kelly2007} to estimate this intrinsic scatter based on the \mbii\ overall sample and obtain the level as $0.25$~dex.
-
-We also present the comparison of the \mbh-\mr\ relations in Figure~\ref{fig:ML_comp} and the comparison of the scatter in Figure~\ref{fig:offset_comp} (right panel).
-The results are similar to \mbh-\mstar\ relations.
-
-\begin{figure*}[t]%[!b]
-\begin{tabular}{c c}
-\includegraphics[trim = 0mm 0mm 61mm 0mm, clip, width=0.47\linewidth]{MBII_ML.pdf} &
-\includegraphics[trim = 0mm 0mm 61mm 0mm, clip, width=0.47\linewidth]{SAM_ML_consider_nois.pdf} \\
-\end{tabular}
-\caption{Same as the Figure~\ref{fig:MM_comp}, but for \mbh-\mr\ relation.}
-\label{fig:ML_comp}
-\end{figure*}
-
-\begin{figure*}[t]%[!b]
-\begin{tabular}{c c}
-\includegraphics[width=0.45\linewidth]{comp_scatter_MM.pdf} &
-\includegraphics[width=0.45\linewidth]{comp_scatter_ML.pdf} \\
-\end{tabular}
-\caption{The histogram of the scatter (i.e., residuals in the linear relation).
-The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, \mbii\ sample and \sam\ sample, respectively, for both \mbh-\mstar\ and \mbh-\mr\ relations.
-}
-\label{fig:offset_comp}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{References}
-\bibliography{references}
-
-\begin{addendum}
- \item[Acknowledgements] 
+\acknowledgments
+\ding{How do we present our thanks to the three NA referees properly?}
 Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
@@
 
-%
-\item[Author Contributions] X.D.
-carried out the \hst\ data analysis, led the comparison to the simulating models and was the principal author of the paper.
-T.T.
-and J.S.
-designed the \hst\ project, selected the AGN sample, and wrote parts of the paper.
-A.B.
-and T.D.
-ran the \mbii\ simulation and provide the  \mbii\ data.
-N.M.
-ran the \sam\ model and provide and the \sam\ data.
-X.D, T.T, J.S., A.B., T.D., and N.M.
-interpreted the result.
+\bibliography{reference}
+%\bibliographystyle{aasjournal}
 
-\end{addendum}
+%% This command is needed to show the entire author+affiliation list when
+%% the collaboration and author truncation commands are used.  It has to
+%% go at the end of the manuscript.
+%\allauthors
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Additional information}
-%\textbf{Code availability.} The \lenstronomy, which is used to decompose the AGN image  
-%The data reduction package used to process the \sam\ data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr.
-To derive the stellar kinematic parameters and the lick absorption line strengths, we use the publicly available penalised pixel-fitting (pPXF) code from M.
-Capppellari: {http://www-astro.physics.ox.ac.uk/~mxc/software/\#ppxf}.
-For the adaptive LOESS smoothing, we use the code from M.
-Cappellari obtained from: http://www-astro.physics.ox.ac.uk/~mxc/software/\#loess
-
-\textbf{Data availability.} All the inference of the AGN properties are presented in the companion paper.
-%All reduced data-cubes in the GAMA fields used in this Letter are available on: http://datacentral.aao.gov.au/asvo/surveys/sami/, as part of the first SAMI Galaxy Survey data release.
-Stellar kinematic data products will become available in the second SAMI Galaxy Survey data release.
-
-\textbf{Correspondence and requests for materials} should be addressed to X.D.~(email:dxh@astro.ucla.edu).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\clearpage
-%\newpage
-%\onecolumn
-%\begin{center}
-%{\bf \Large \uppercase{Supplementary information} }
-%\end{center}
-%
-%\setcounter{figure}{0}
-%\vspace{2cm}
-%
-%\begin{figure}[!h]
-%\begin{center}
-%\includegraphics[width=0.8\linewidth]{hst_sample_bhmf.pdf}
-%\caption{
-%The selection function of our observation data.
-Eddington ratios (LBol/LEdd) and BH masses (bottom panel) of our sample (in color) that fall well-below the knee of the BH mass function at z = 1.5 (top panel; Schulze et al.
-2015).
-Dashed lines (vertical and horizontal) denote our selection window with the slanted line only shown to approximately illustrate the effect of a luminosity limit, inherent in the parent catalogs.
-For reference, we indicate the high-z luminous SDSS QSO samples (grey squares - Peng et al.
-2006; grey circles - Decarli et al.
-2010) with all falling above our chosen upper mass limit.
-%}
-%\label{fig:support}
-%\end{center}
-%\end{figure}
+%% Include this line if you are using the \added, \replaced, \deleted
+%% commands to see a summary list of all changes at the end of the article.
+%\listofchanges
 
 \end{document}
+
+% End of file `sample63.tex'.

### 2020-01-30 QSOII_paper/ApJ_manuscript/manuscript.tex
Update manuscript.tex

@@
 	%mention the scatter.
-In this section, we introduce the comparison samples of the scaling relations, using the observed data (Section~\ref{hst_sample}) and the predicted ones using two independent numerical simulations (Section~\ref{sample_sim}).}
+In this section, we introduce our comparison samples, including the observed scaling relations (Section~\ref{hst_sample}) and the predicted ones by two independent numerical simulations (Section~\ref{sample_sim}).}
 

### 2020-02-17 QSOII_paper/ApJ_manuscript/version_control/before_submit_color.tex
Prepare to submit to ApJ

--- 2020-01-30 QSOII_paper/ApJ_manuscript/manuscript.tex
@@
 \submitjournal{ApJ}
-\shorttitle{A Successful Observational Test}
+\shorttitle{Confronting co-evolution theory with observations}
 \shortauthors{Ding et al.}
@@
 \begin{document}
-\title{A successful observational test of black hole and galaxy co-evolution models since $z\sim1.7$}
+%\title{An observational test of black hole and galaxy co-evolution models since $z\sim1.7$}
+
+\title{Testing the fidelity of simulations of black hole - galaxy co-evolution at $z\sim1.5$ with observations}
 
@@
 
-\author{N. Menci}
+\author[0000-0002-4096-2680]{N. Menci}
 \affiliation{INAF Osservatorio Astronomico di Roma, via Frascati 33, I-00078 Monteporzio, Italy}
@@
 For this purpose, we have constructed a unique sample of 32 actively-accreting SMBHs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with accurate BH and stellar masses with the latter based on multi-band \hst\ imaging.
-\pink{To examine the scaling relations between the mass of a supermassive black hole (SMBH) and its host galaxy properties, we adopt the recent measurements based on 32 X-ray-selected broad-line Active Galactic Nucleus (AGNs) at $1.2<z<1.7$, and} make direct comparison with two independent state-of-the-art projects, including the hydrodynamic simulation \texttt{MassiveBlackII} (\mbii) and the semi-analytic model (\sam).
-After applying the observational selection function to the simulations to account for the bias, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
-However, accounting for observational errors, the dispersion in the mass ratio between \mbh\ and \mstar\ is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex) one.
+\pink{We examine the scaling relations between the mass of a supermassive black hole (SMBH) and its host galaxy properties at $1.2<z<1.7$ using both observational data and simulations.
+Recent measurements of 32 X-ray-selected broad-line Active Galactic Nucleus (AGNs)} are compared with two independent state-of-the-art efforts, including the hydrodynamic simulation \texttt{MassiveBlackII} (\mbii) and a semi-analytic model (\sam).
+After applying an observational selection function to the simulations, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
+However, the dispersion in the mass ratio between \mbh\ and \mstar\ is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex), even when accounting for observational uncertainties.
 Hence, our observations can distinguish between the different recipes adopted in the models.
@@
 In this scenario, AGN activity heats and unbinds a significant fraction of the gas and inhibits star formation.
-An alternatively and more indirect connection is one where AGN accretion and star formation are fed through a common gas supply~\citep{Cen2015, Menci2016}.
+An alternative and more indirect connection is one where AGN accretion and star formation are fed through a common gas supply~\citep{Cen2015, Menci2016}.
 A completely different view holds that the statistical convergence from galaxy assembly alone (i.e., dry mergers) may reproduce the observed correlations without any direct physical mechanisms~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
@@
 
-To understand this connection, recent works~\citep{Park15, Tre++07, Bennert11, Woo++08} have measured the scaling relations out to intermediate redshift {($0.3\lesssim z \lesssim1$)} by studying AGN and their host galaxies with {\it Hubble Space Telescope} ({\it HST}) and found an {\it observed} evolution in which the growth of SMBHs predates their host galaxies.
-However, the observational evidence of such evolution at higher-$z$ is under debate since it depends on our understanding of systematic uncertainties and selection effects~\citep{Tre++07,Lauer2007}.
-Therefore, an improper consideration of the uncertainties and selection effects may lead to an {\it apparent} evolution and result in an overestimate of the significance of the evolution~\citep{Volonteri2011}.
+Considerable efforts have been undertaken to establish the scaling relations out to high redshift ($z \lesssim2$) using the {\it Hubble Space Telescope} ({\it HST}) to detect the host galaxies of AGN \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08,Jahnke2009,Bennert11,Schramm2013,Park15,Mechtley2016,Ding2019}.
+While some studies find an {\it observed} evolution in which the growth of SMBHs predates their host galaxies, there are equally as many claims of no evolution when considering the total stellar mass of the host.
+For all studies, an understanding of the systematic uncertainties and selection effects~\citep{Tre++07,Lauer2007,Schulze2014} need to be considered to avoid an {\it apparent} evolution that may overestimate the significance of the evolution~\citep{Volonteri2011}.
 
@@
 %The reason to extend to high redshift.
-Simulations are effective at helping to understand this connection and rule out theories and assumptions that could not be definitively verified by observations alone.
+
+Simulations can effectively aid in our understanding of this connection by ruling out theories and assumptions that could not be definitively verified by observations alone.
 In particular, simulations can be used to quantify the impact of systematic uncertainties and selection biases with observational data.
-Recent studies, based on several simulations, show agreement with the observational data at intermediate redshifts ($z\lesssim1$).
-For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been utilized to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ that show a positive evolution where the SMBH growth predates that of its the host galaxy~\citep{DeG++15}.
+For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been used to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ which show a positive evolution where the SMBH growth predates that of its the host galaxy~\citep{DeG++15}.
 Several other works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\citep{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\citep{Schaye2015}, and Illustris moving mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019}.
-Besides hydrodynamic simulations, semi-analytic models~\citep[][\ding{Hi Nicola, do you think we can refer Thomas2019 here as another semi-analytic model?}]{Menci2014, Menci2016, Thomas2019} have also made remarkable progress and recovered the local scaling relations~\citep{Kormendy13}.
-However, comparisons between simulations and the observed scaling relations, based on high-resolution \hst\ imaging, are still mostly limited to $z<1$ due to prior limitations of observational data.
+Besides hydrodynamic simulations, semi-analytic models~\citep[][\ding{Hi Nicola, do you think we can refer Thomas2019 here as another semi-analytic model?
+{\bf Nicola}: Hi Xuheng: no I think this is a N-body simulation, with a specific recipe for sub-grid physics.
+I would move Thomas 2019 at the end of the previous paragraph, mentioning it among the simulations}]{Menci2014, Menci2016, Thomas2019} have also made remarkable progress and recovered the local scaling relations~\citep{Kormendy13}.
+These comparisons between simulations and the observed scaling relations, based on high-resolution \hst\ imaging, have been carried out mainly at $z<1$ due to prior limitations of the availability of observational data.
 
 \blue{
-In this study, we push our knowledge of the mass relations to earlier epochs.
-We establish the mass ratios between the SMBHs and their host using 32 type-1 AGNs and make direct comparisons to the predicted type-1 AGNs based on two independent state-of-the-art numerical simulations.}
+In this study, we directly compare the mass ratios between SMBHs and their host galaxies of 32 type-1 (broad-line) AGNs from our recent observational study at $z\sim1.5$ \citep{Ding2019} to the predictions based on two independent state-of-the-art numerical simulations.}
 \ding{The referee \#2 asks us to comment on what kinds of biases may be introducing since we use only type-1 AGNs. Xuheng thinks this request is trivial and let's ignore this.}
-\blue{The redshift range of our targets is chosen to be high enough ($z>1$) when most of the SMBHs acquired their mass, are more sensitive to initial
-conditions and the growth mechanisms and thus may be able to identify inaccurate or missing physics in the models,  while low enough ($z<2$) to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy.
-We describe the observed and simulated targets in Section~\ref{sec:sample}.
-The comparison result are shown in Section~\ref{sec:result} with conclusion presented in Section~\ref{sec:conclusion}.
+\blue{The redshift range of our targets is chosen to be high enough ($z>1$) when most of the SMBHs acquired their mass thus sensitive to initial
+conditions and growth mechanisms, possibly allowing an identification of inaccurate or missing physics in the models.
+The redshift range is low enough ($z<2$) to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy with HST.
+We describe the observed and simulated galaxies and their black holes in Section~\ref{sec:sample}.
+The comparisons between data and simulations are shown in Section~\ref{sec:result} and conclusion presented in Section~\ref{sec:conclusion}.
 Throughout this paper, we adopt a standard concordance
@@
 \pink{
-\section{Sample: Observation and Simulation}~\label{sec:sample}
+\section{Sample: Observations and Simulations}~\label{sec:sample}
 % The work that we want to do
@@
 
-We have been analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} (D19~\citep{Ding2019} hereafter).
+We have been constructing and analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} (D19~\citep{Ding2019} hereafter).
 We selected our AGN sample in a well-defined window based on the \mbh\ and Eddington ratio, as shown in Figure~1 in D19.
-As shown in that Figure, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias.
+As shown in that Figure, the \mbh\ are well below the knee of the BH mass distribution to avoid a strong selection bias.
 In addition, the Eddington ratios are mostly above $0.1$ to ensure homogeneity.
@@
 We measure reliable \mbh\ and host properties (i.e., \mstar) with a quantitative assessment of systematic effects.
-Specifically, \mbh\ is determined using published near-infrared spectroscopic observations of the broad \halpha\ emission line, which eliminates potential systematic uncertainties that may arise from switching to Balmer lines in the local universe to the \Mgii\ or \Civ\ UV lines for distant galaxies.
+Specifically, \mbh\ is determined using published near-infrared spectroscopic observations of the broad \halpha\ emission line, which eliminates potential systematic uncertainties that may arise from switching between Balmer lines in the local universe to the \Mgii\ or \Civ\ UV lines for distant galaxies.
 Regarding the detection of the host galaxies, the X-ray selected nature of the sample results in slightly lower nuclear-to-host ratios, which facilitates the inference of the host light.
@@
 
-\blue{We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy.
-A detailed description of the \hst\ data analysis can be found in a companion paper ~\citep[][D19 hereafter]{Ding2019}.
-Here we only present a brief summary of that study.
-We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ (according to the redshift of the targets) to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman).
-We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to co-add the final image with pixel scale as 0\farcs0642.
-To mitigate the contamination by the background light from both the sky and the detector, we adopt the {\sc photuils} tools to estimate and remove them accurately.}
+\blue{To detect their host galaxies, we used \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) infrared imaging data for 32 AGN systems (HST Program GO-15115).
+The filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ were employed, according to the redshift of each target.
+Six dithered exposures with a total exposure time $\sim2394s$ were co-added using the {\sc astrodrizzle} software package to generate a final image with a pixel scale as 0\farcs0642.
+We implemented the {\sc photuils} tools to remove contamination due to background light from both the sky and the detector.
+A full detailed description of the \hst\ data analysis can be found in a companion paper ~\citep[][D19 hereafter]{Ding2019}.}
 
-\blue{To address the bias which might be raised by the unknown PSF, we manually collect the isolated-unsaturated PSF-stars from the 32 observed fields, to assemble a PSF library for the fitting.
-To decompose each AGN image, we assume the unresolved active nuclei as the scaled point source and the host galaxy as the \sersic\ profile.
-We adopt imaging modeling tool \lenstronomy~\citep{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one by one from the collected PSF library.
+\blue{We implemented state-of-the-art techniques to perform 2-D flux profile decomposition to disentangle the host emission from the AGN.
+To address biases with respect to the accuracy of the point-spread function (PSF), we collected 2D profiles of isolated and unsaturated stars from the 32 observed HST fields to assemble a PSF library for the fitting routine.
+To decompose each AGN image, we assume the unresolved active nuclei as scaled point source and the host galaxy as a \sersic\ profile.
+We ran the imaging modeling tool \lenstronomy~\citep{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one-by-one from the collected PSF library.
 Based on the reduced $\chi^2$, we are capable of evaluating the performance of each PSF.
-We adopt the result from the top-ranked-eight PSFs and using the weighting process to obtain the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.}
+We adopt the result from the top-ranked-eight PSFs and used a weighting process to obtain the host properties, including flux, \reff, \sersic\ index.}
 
 \blue{The COSMOS survey provides \hst\ ACS/F814W imaging data for 21 of 32 AGN in our sample with a drizzled pixel scale as 0\farcs03.
-We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3's result to infer the host color.
-We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar).}
+We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3 result to infer the host color.
+We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the colors of the host to derive the rest frame R-band magnitude (\mr) and the stellar mass (\mstar)-to-light ratio.}
 
-\pink{We note that in \citet{Sun2015}, a sample of 69 type-1 AGN has been studied to measure the mass relations at redshift range $0<z<2$.
-Nevertheless, aiming at achieving a direct comparison to the simulations, we selected not to take their sample given that their sample is chosen with the incongruous selection function.
-Moreover, their \mstar\ is inferred by fitting the spectral energy distribution, and \mbh\ is estimated using different broad lines (i.e., \hbeta\ and \Mgii), which could both introduce larger systematics.}
+\pink{We remark that the observational data used in this study is limited to our carefully-constructed sample with a well-understood selection function and 2D assessment of the host galaxy emission from space-based imaging.
+While there exists larger data sets such as \citet{Sun2015} and others, we refrain from including cases where the host galaxy was assessed using fitting of the spectral energy distribution with broad-band photometry from the ground since there are likely higher levels of uncertainty with respect to cases with an AGN of considerable luminosity.
+However, we recognize that there has yet been definitive evidence for inherent problems with these methods.}
 
@@
 The \mbii\ simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
-The large simulation volume enables the model galaxies and SMBHs to evolve independently; the large dynamic range in mass and high spatial resolution meet the requirements to investigate their individual galaxies.
-While high-resolution N-body simulations can study specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam.
-In previous works, \mbii~\citep{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\citep{Menci2014, Menci2016} have made high successful predictions.
-\blue{In the following two sections, we present the detailed information of the two simulation projects.}
+The large simulation volume enables the model galaxies and SMBHs to evolve independently; the large dynamic range in mass and high spatial resolution meet the requirements to study individual galaxies.
+While high-resolution N-body simulations can describe specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam.
+In previous works, \mbii~\citep{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\citep{Menci2014, Menci2016} have made highly successful predictions.
+\blue{In the following two sections, we present detailed information on the two simulation projects.}
 
 \subsubsection{\texttt{MassiveBlackII} simulation}
-The MassiveBlackII (\mbii) is a high-resolution cosmological hydrodynamic simulation using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\citep{2005MNRAS.364.1105S}.
+MassiveBlackII (\mbii) is a high-resolution cosmological hydrodynamic simulation using Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\citep{2005MNRAS.364.1105S}.
 It has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles.
@@
 Within these haloes, self-bound substructures/subhaloes were identified using \texttt{SUBFIND} ~\citep{2005MNRAS.364.1105S}.
-Galaxies are identified to the stellar matter components of the subhaloes.
+Galaxies are identified with the stellar matter components of subhaloes.
 
@@
 Once seeded, black hole growth occurs via gas accretion at a rate given by $\dot{M}_{bh}={4\pi G^2 M_{bh}^2 \rho}/{(c_s^2+v_{bh}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the ISM gas~(cold phase); $v_{bh}$ is the relative velocity between the black hole and the gas in its vicinity.
-$10\%$~(radiative efficiency) of the accreted gas is released as radiation.
+A radiative efficiency of $10\%$ of the accreted gas is released as radiation.
 The accretion rate is allowed to be mildly super-Eddington, i.e., limited to two times the Eddington accretion rate.
@@
 The stellar SEDs were modelled using the \texttt{PEGASE-2}~\citep{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF.
-The galaxy SEDs are finally convolved with the desired filter function to obtain the broad band photometry~(SDSS $r$ band magnitude).
+The galaxy SEDs are finally convolved with the desired filter function to obtain the broad band photometry~(SDSS $r$-band magnitude).
 
-We follow the common practice and adopt the stellar mass within a 3D spherical aperture of 30 kpc to adopt as the more faithful proxy of the observed stellar mass in the \mbii\ simulation.
-It has been shown that this definition of the stellar produces a stellar mass function that is consistent with observational constraints~\citep{Pillepich2018}.
-Further, the stellar mass in this physical aperture provides good agreement to those measured within Petrosian radii in observational studies ~\citep{Schaye2015}.
-
+Following common practice, the stellar mass is determined within a 3D spherical aperture of 30 kpc as a proxy of the observed stellar mass in the \mbii\ simulation.
+It has been shown that this definition reproduces a stellar mass function that is consistent with observational measurements~\citep{Pillepich2018}.
+Furthermore, the stellar mass in this physical aperture provides good agreement to those measured within Petrosian radii in observational studies ~\citep{Schaye2015}.
 For further details regarding the \mbii\ simulation, we refer the reader to the reference~\citep{2015MNRAS.450.1349K}.
@@
 
-We compare the relation \mbh--\mstar~between observations and the \mbii\ simulation. First, it is clear that the simulated and observed samples are in good agreement. 
-\blue{To quantify the agreement between the simulation and the observation, we use a linear regression to fit their relations and compare the result.
+In the left panel of Figure~\ref{fig:MM_comp}, we compare the relation \mbh--\mstar~between observations and the \mbii\ simulation.
+It is clear that the simulated and observed samples are in good agreement.
+\blue{To quantify the agreement between the simulated and observed data, we use a linear regression to fit their relations.
 Our selection window has a hard cut on the \mbh\ value (i.e., vertical direction in Figure~\ref{fig:selectfunc}), and thus the scatter on the host properties are larger (horizontal direction).
@@
 We adopt the {\sc Scipy} package to estimate the best-fit inference for the simulated sample.
-We then fit for the observations based on the same slope value.
-The comparison results are showing in Figure~\ref{fig:MM_comp} (left panel), with the standard derivation of the residual indicated by the colored regions.}
-\pink{To estimate the {\it observed} scatter of the sample, we calculate the standard deviation of the fitting residual based on \mstar\ (i.e., along the $x$-axis).}\blue{The histogram of the residual is presented in Figure~\ref{fig:offset_comp} (left panel).
-We find the standard derivation of the residual for observed and \mbii\ sample are at the same level and both equal to $\sim0.3$~dex.}\pink{We test to vary the fixed slope value by its uncertainty level but found the corresponding {\it observed} scatters barely changed ($<1\%$), meaning that the inferred scatter weakly depends on the fitted slope.
-Note that, with a different definition of the {\it observed} scatter, the measured value could be different.
-In this particular work, we simply apply a common standard (i.e., consider the measured residual in \mstar) to achieve a direct comparison between different samples.}\blue{We perform the Kolmogorov-Smirnov (KS) test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$.
+We then fit the observations based on the same slope value.
+The comparison results are shown in Figure~\ref{fig:MM_comp} (left panel), with the standard deviation of the residual indicated by the colored regions.}
+\pink{To estimate the {\it observed} scatter of the sample, we calculate the standard deviation of the fitted residual based on \mstar\ (i.e., along the $x$-axis).}\blue{The histogram of the residual is presented in Figure~\ref{fig:offset_comp} (left panel).
+We find the standard deviation of the residual for observed and \mbii\ sample are similar, i.e., both equal to $\sim0.3$~dex.}\pink{We manually change the slope value by its uncertainty level and find that the corresponding {\it observed} scatter barely changes ($<1\%$), meaning that the inferred scatter weakly depends on the fixed slope.
+{\bf Xuheng to JDS: is it clear now?
+- We note that with different definitions to calculate the scatter, the inferred value may result in a more pronounced difference.} In this particular work, we simply apply a common standard method (i.e., consideration of the measured residual in \mstar) to achieve a direct comparison between different samples.} \blue{We perform the Kolmogorov-Smirnov (KS) test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$.
 Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \mbii\ sample and the observational sample have the same intrinsic scatter level.
-We adopt the python package {\sc Linmix}~\citep{Kelly2007} to estimate this {\it intrinsic} scatter based on the \mbii\ overall sample and obtain the level as $0.25$~dex.
+We adopt the python package {\sc Linmix}~\citep{Kelly2007} to estimate the {\it intrinsic} scatter based on the \mbii\ overall sample and obtain a level of $0.25$~dex.
 }
@@
 \includegraphics[width=1.2\linewidth]{MBII_selectfunc.pdf}
-\caption{The same selection window as adopted for selecting the \mbii\ simulated sample.
-The brown background cloud shows the simulated number density of the overall \mbii\ sample at $z=1.5$.
-We add the random uncertainty to the simulation and select the ones fall into the targeting region (i.e., blue colored).
-The orange dots are the \hst\ observed sample.}
+\caption{Equivalent selection window adopted for the HST-observed and  \mbii\ simulated samples.
+The background cloud (in light brown/grey) shows the simulated number density of the overall \mbii\ sample at $z=1.5$.
+We added random uncertainty to the simulation and select those that fall into the target region (i.e., small blue circles).
+The small orange circles are the \hst\ observed sample.}
 \label{fig:selectfunc}
@@
 \caption{(Left) Comparison of the observed (orange dots) and simulated (blue dots) \mbh--\mstar\ relation.
-The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the standard derivation of the residual.
+The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the standard deviation of the residual.
 By fixing the slope to match the simulated data, the orange color shows the result for the observed data set.
@@
 
-We also compare our data to the predictions by the \sam\ model.
-Rather than N-body simulation which produces individual simulating objects, the \sam\ model\pink{uses the interaction-driven model~\citep{Menci2014} to calculate the number density of the galaxies.} To make a direct comparison, we first randomly produce an overall sample based on the \pink{\sam\ predicted number density} at $z=1.5$.
+We also compare our data to predictions by the \sam\ .
+In contrast to N-body simulations which produce individual objects, the \sam\ \pink{uses an interaction-driven model~\citep{Menci2014} to calculate the number density of the galaxies.} To make a direct comparison, we first randomly produce an overall sample based on the \pink{\sam\ predicted number density} at $z=1.5$.
 Then, as in the \mbii\ analysis, we inject random scatter in the sample to account for uncertainties and apply the observational selection function.
-The resulting comparison of the  \mbh-\mstar\ relation are shown in Figure~\ref{fig:MM_comp} (right panel).
+The resulting comparison of the  \mbh-\mstar\ relation is shown in Figure~\ref{fig:MM_comp} (right panel).
 We find that the best-fit result by the \sam\ model is well matched to the observation.
@@
 It is a little complicated, since we have a limited MBH range and fitted slope value may be related to the scatter of the sample.
-Maybe we can currently ignore this and let's see the feedback by the referee.}
+Maybe we can currently ignore this and let's see the feedback by the referee.
+{\bf Nicola}: ok, I agree}
 %\begin{figure*}[t]%[!b]
@@
 \caption{The histogram of the scatter (i.e., residuals in the linear relation).
-The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, \mbii\ sample and \sam\ sample, respectively, for both \mbh-\mstar\ and \mbh-\mr\ relations.
+The standard deviation for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, \mbii\ sample and \sam\ sample, respectively, for both \mbh-\mstar\ and \mbh-\mr\ relations.
 }
@@
 
-To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
-For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3.
-For the simulated sample, we consider the AGN bolometric correction~\citep{Elvis1994} to estimate the AGN light flux at WFC3/F125W band.
-We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched to each other.
+To test if any unexpected selection effects exist, we compare the distribution of the host-to-total flux ratio among these three samples.
+For the observed sample, we calculate the flux ratio in the \hst/WFC3 band.
+For the simulated sample, we consider the AGN bolometric correction~\citep{Elvis1994} to estimate the AGN flux in the WFC3/F125W band.
+We compare their host-total flux distribution in Figure~\ref{fig:comp_hist} and find that the three samples are well matched to each other.
 The median values for the flux ratio distribution of the observed, \mbii, \sam\ sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively.
@@
 \includegraphics[width=0.9\linewidth]{comp_host_ratio.pdf}
-\caption{Comparison of the host to total flux ratio distribution for the three referred samples, median value indicated.
+\caption{Comparison of the host-to-total flux ratio distribution for the three referred samples, median value indicated.
 The observational selection function is applied to the simulated samples to allow for a fair comparison.
@@
 In terms of their central distribution, the \mbii\ simulation and \sam\ model are both in agreement with the observational data.
-However, the scatter distinguishes between the two models.
-The  the scatter in \mbii\ simulation is consistent to the observational one ($\sim0.3$~dex), while \sam\ sample has significantly larger scatter ($\sim0.7$~dex).
+However, the scatter indicates a difference between the two models.
+The  the scatter in \mbii\ simulation is consistent with that in the observations ($\sim0.3$~dex), while \sam\ sample has a significantly larger amount of scatter ($\sim0.7$~dex).
 Thus, the implementation of AGN feedback in \mbii\ passes our stringent observational test.
-The \sam\ model also consider the AGN feedback.
-However, in contrast to \mbii, the feeding process for the SMBH accretion is driven by the 2-body interaction of galaxy mergers, and thus may be more stochastic and lead to the larger scatter.
+The \sam\ model also includes the AGN feedback.
+However, in contrast to \mbii, the feeding process for SMBH accretion is driven by the 2-body interaction of galaxy mergers, and thus may be more stochastic and lead to larger scatter.
 More specifically, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the encounter, which introduces additional scatter since it depends on the properties of both interacting galaxies (see Section~\ref{sec_intro_SAM}).
@@
 The consistency between \mbii\ and observations provides important observational evidence in support of the hypothesis that there is a causal link (i.e., AGN feedback) between the evolution of SMBH and that of their host galaxies.
+It may also indicate that mergers do not play a dominate role in fueling SMBHs as supported by many observational studies \citep{Ellison2011, Silverman2011,Mechtley2016,Goulding2018}.
 
@@
 At present, it is still unclear how much difference in the observed scatter between \mbii\ and \sam\ is due to the different recipes of triggering, hierarchical merging, gas fueling, and AGN feedback.
-For instance, even without introducing AGN feedback, the predictions by \citet{2017MNRAS.464.2840A} could also have low scatter products in their simulation.
-It will be more insightful to carry out a comparative test based on one numerical model that using different the AGN feedback assumptions, and setting all the other conditions as the same \citep[see][as a glimpse]{Hopkins2009}.
+For instance, even without introducing AGN feedback, the predictions by \citet{2017MNRAS.464.2840A} \textcolor{green}{- based on torques owing to disc instabilities as
+ drivers for black hole feeding -} could also have low scatter products in their simulation.}
+\textcolor{green}{This may indicate that the origin of the smaller scatter in the N-body simulations is related to fact that the considered feeding mechanisms (Bondi accretion or disc instabilities) depend only on the properties of the black hole and host galaxy.
+This strongly differs from the SAM assumption that two-body process (interactions) are the main trigger for black hole accretion.
+As for the role of feedback, }\pink{
+it will be more insightful to carry out a comparative test based on one numerical model and altering the AGN feedback prescription, while fixing all other conditions \citep[see][]{Hopkins2009}.
 }
 
-Without any physical mechanisms, it has been shown that just due to the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010} scaling relations may emerge from random mergers, starting from a stochastic cloud in the early universe.
-In this scenario, the scatter of the scaling relations has to increase with redshift.
+Without a direct physical mechanism, it has been shown that, due to the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010}, scaling relations may emerge from random mergers, starting from a stochastic cloud in the early universe.
+Under this scenario, the scatter of the scaling relations has to increase with redshift.
 Our observations contradict this hypothesis.\pink{In fact, the inferred {\it intrinsic} scatter of our observed sample (i.e., $\sim0.25$~dex) is even no more significant than the typical scatter of local relations reported in the literature ~\citep[][i.e., $\gtrsim0.35$~dex]{Kormendy13, Gul++09, Reines2015}.} Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level of intrinsic scatter for the real data, but it is unlikely that systematic errors would conspire to {\it reduce} scatter.

### 2020-02-19 QSOII_paper/ApJ_manuscript/version_control/arxiv_first_sub/manuscript.tex
Submit paper to ApJ

--- 2020-02-17 QSOII_paper/ApJ_manuscript/version_control/before_submit_color.tex
@@
 \newcommand{\red}[1]{{ \textcolor{red}{#1}}}
-\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
-\newcommand{\pink}[1]{{ \textcolor{magenta}{#1}}}
+%\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
+%\newcommand{\pink}[1]{{ \textcolor{magenta}{#1}}}
+\newcommand{\blue}[1]{{{#1}}}
+\newcommand{\pink}[1]{{{#1}}}
 
@@
 After applying an observational selection function to the simulations, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
-However, the dispersion in the mass ratio between \mbh\ and \mstar\ is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex), even when accounting for observational uncertainties.
+However, the dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex), even when accounting for observational uncertainties.
 Hence, our observations can distinguish between the different recipes adopted in the models.
@@
 
-Considerable efforts have been undertaken to establish the scaling relations out to high redshift ($z \lesssim2$) using the {\it Hubble Space Telescope} ({\it HST}) to detect the host galaxies of AGN \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08,Jahnke2009,Bennert11,Schramm2013,Park15,Mechtley2016,Ding2019}.
+Considerable efforts have been undertaken to establish the scaling relations out to high redshift ($z \lesssim2$) using the {\it Hubble Space Telescope} (\hst) to detect the host galaxies of AGN \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08,Jahnke2009,Bennert11,Schramm2013,Park15,Mechtley2016,Ding2019}.
 While some studies find an {\it observed} evolution in which the growth of SMBHs predates their host galaxies, there are equally as many claims of no evolution when considering the total stellar mass of the host.
@@
 For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been used to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ which show a positive evolution where the SMBH growth predates that of its the host galaxy~\citep{DeG++15}.
-Several other works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\citep{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\citep{Schaye2015}, and Illustris moving mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019}.
-Besides hydrodynamic simulations, semi-analytic models~\citep[][\ding{Hi Nicola, do you think we can refer Thomas2019 here as another semi-analytic model?
-{\bf Nicola}: Hi Xuheng: no I think this is a N-body simulation, with a specific recipe for sub-grid physics.
-I would move Thomas 2019 at the end of the previous paragraph, mentioning it among the simulations}]{Menci2014, Menci2016, Thomas2019} have also made remarkable progress and recovered the local scaling relations~\citep{Kormendy13}.
+Several other works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\citep{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\citep{Schaye2015}, Illustris moving mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019} and SIMBA simulation~\citep{Thomas2019}.
+Besides hydrodynamic simulations, semi-analytic models~\citep[e.g.,][]{Menci2014, Menci2016} have also made remarkable progress and recovered the local scaling relations~\citep{Kormendy13}.
 These comparisons between simulations and the observed scaling relations, based on high-resolution \hst\ imaging, have been carried out mainly at $z<1$ due to prior limitations of the availability of observational data.
@@
 \blue{
-In this study, we directly compare the mass ratios between SMBHs and their host galaxies of 32 type-1 (broad-line) AGNs from our recent observational study at $z\sim1.5$ \citep{Ding2019} to the predictions based on two independent state-of-the-art numerical simulations.}
-\ding{The referee \#2 asks us to comment on what kinds of biases may be introducing since we use only type-1 AGNs. Xuheng thinks this request is trivial and let's ignore this.}
-\blue{The redshift range of our targets is chosen to be high enough ($z>1$) when most of the SMBHs acquired their mass thus sensitive to initial
+In this study, we directly compare the mass ratios between SMBHs and their host galaxies of 32 type-1 (broad-line) AGNs from our recent observational study at $z\sim1.5$ \citep{Ding2019} to the predictions based on two independent state-of-the-art numerical simulations.} The redshift range of our targets is chosen to be high enough ($z>1$) when most of the SMBHs acquired their mass thus sensitive to initial
 conditions and growth mechanisms, possibly allowing an identification of inaccurate or missing physics in the models.
-The redshift range is low enough ($z<2$) to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy with HST.
+The redshift range is low enough ($z<2$) to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy with \hst.
 We describe the observed and simulated galaxies and their black holes in Section~\ref{sec:sample}.
@@
 observed and simulated sample.
-}
 
@@
 
-\subsection{HST Observational data}\label{hst_sample}
+\subsection{\hst\ Observational data}\label{hst_sample}
 
@@
 
-\blue{We implemented state-of-the-art techniques to perform 2-D flux profile decomposition to disentangle the host emission from the AGN.
-To address biases with respect to the accuracy of the point-spread function (PSF), we collected 2D profiles of isolated and unsaturated stars from the 32 observed HST fields to assemble a PSF library for the fitting routine.
+\blue{We implemented state-of-the-art techniques to perform 2D flux profile decomposition to disentangle the host emission from the AGN.
+To address biases with respect to the accuracy of the point-spread function (PSF), we collected 2D profiles of isolated and unsaturated stars from the 32 observed \hst\ fields to assemble a PSF library for the fitting routine.
 To decompose each AGN image, we assume the unresolved active nuclei as scaled point source and the host galaxy as a \sersic\ profile.
-We ran the imaging modeling tool \lenstronomy~\citep{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one-by-one from the collected PSF library.
+We ran the imaging modeling tool \lenstronomy~\citep{lenstronomy} to simultaneously fit their 2D flux distribution, taking each PSF one-by-one from the collected PSF library.
 Based on the reduced $\chi^2$, we are capable of evaluating the performance of each PSF.
@@
 \pink{We remark that the observational data used in this study is limited to our carefully-constructed sample with a well-understood selection function and 2D assessment of the host galaxy emission from space-based imaging.
-While there exists larger data sets such as \citet{Sun2015} and others, we refrain from including cases where the host galaxy was assessed using fitting of the spectral energy distribution with broad-band photometry from the ground since there are likely higher levels of uncertainty with respect to cases with an AGN of considerable luminosity.
+While there exists larger data sets such as \citet{Sun2015} and others, we refrain from including cases where the host galaxy was assessed using fitting of the spectral energy distribution~(SED) with broad-band photometry from the ground since there are likely higher levels of uncertainty with respect to cases with an AGN of considerable luminosity.
 However, we recognize that there has yet been definitive evidence for inherent problems with these methods.}
@@
 
-For the galaxy photometry, the spectral energy distributions~(SEDs) of the host galaxies were first obtained by summing up the contributions from the individual star particles.
+For the galaxy photometry, the SEDs of the host galaxies were first obtained by summing up the contributions from the individual star particles.
 The stellar SEDs were modelled using the \texttt{PEGASE-2}~\citep{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF.
@@
 In each halo, we compute the amount of gas which cools due through atomic processes and settles into a rotationally-supported disk~\citep{Mo1998}.
-The gas is converted into stars through three different channels: (1) quiescent star formation gradually converting the gas into stars over long timescales $\sim 1$~Gyr, (2) starbursts following galaxy interactions, occurring on timescales $\lesssim 100$~Myr, associated to BH feeding, (3) internal disc instabilities triggering loss of angular momentum resulting into gas inflows toward the centre thus feeding star formation and BH accretion.
+The gas is converted into stars through three different channels: (1) quiescent star formation gradually converting the gas into stars over long timescales $\sim 1$~Gyr, (2) starbursts following galaxy interactions, occurring on timescales $\lesssim 100$~Myr, associated to BH feeding, (3)~internal disc instabilities triggering loss of angular momentum resulting into gas inflows toward the centre thus feeding star formation and BH accretion.
 The energy released by the supernovae associated with the total star formation returns a fraction of the disc gas into a hot phase (stellar feedback).
@@
 The comparison results are shown in Figure~\ref{fig:MM_comp} (left panel), with the standard deviation of the residual indicated by the colored regions.}
-\pink{To estimate the {\it observed} scatter of the sample, we calculate the standard deviation of the fitted residual based on \mstar\ (i.e., along the $x$-axis).}\blue{The histogram of the residual is presented in Figure~\ref{fig:offset_comp} (left panel).
-We find the standard deviation of the residual for observed and \mbii\ sample are similar, i.e., both equal to $\sim0.3$~dex.}\pink{We manually change the slope value by its uncertainty level and find that the corresponding {\it observed} scatter barely changes ($<1\%$), meaning that the inferred scatter weakly depends on the fixed slope.
-{\bf Xuheng to JDS: is it clear now?
-- We note that with different definitions to calculate the scatter, the inferred value may result in a more pronounced difference.} In this particular work, we simply apply a common standard method (i.e., consideration of the measured residual in \mstar) to achieve a direct comparison between different samples.} \blue{We perform the Kolmogorov-Smirnov (KS) test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$.
+\pink{To estimate the {\it observed} scatter of the sample, we calculate the standard deviation of the fitted residual based on \mstar\ (i.e., along the $x$-axis).} \blue{The histogram of the residual is presented in Figure~\ref{fig:offset_comp} (left panel).
+We find the standard deviation of the residual for observed and \mbii\ sample are similar, i.e., both equal to $\sim0.3$~dex.} \pink{We manually change the slope value by its uncertainty level and find that the corresponding {\it observed} scatter barely changes ($<1\%$), meaning that the inferred scatter weakly depends on the fixed slope.
+We note that with different definitions to calculate the scatter, the inferred value may result in a more pronounced difference.
+In this particular work, we simply apply a common standard method (i.e., consideration of the measured residual in \mstar) to achieve a direct comparison between different samples.} \blue{We perform the Kolmogorov-Smirnov (KS) test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$.
 Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \mbii\ sample and the observational sample have the same intrinsic scatter level.
@@
 \includegraphics[width=1.2\linewidth]{MBII_selectfunc.pdf}
-\caption{Equivalent selection window adopted for the HST-observed and  \mbii\ simulated samples.
+\caption{Equivalent selection window adopted for the \hst-observed and  \mbii\ simulated samples.
 The background cloud (in light brown/grey) shows the simulated number density of the overall \mbii\ sample at $z=1.5$.
@@
 
-We also compare our data to predictions by the \sam\ .
+We also compare our data to predictions by the \sam.
 In contrast to N-body simulations which produce individual objects, the \sam\ \pink{uses an interaction-driven model~\citep{Menci2014} to calculate the number density of the galaxies.} To make a direct comparison, we first randomly produce an overall sample based on the \pink{\sam\ predicted number density} at $z=1.5$.
@@
 
- \ding{Do we want to mention that the inferred slope of the MBII is much steeper than the SAM ones?
-It is a little complicated, since we have a limited MBH range and fitted slope value may be related to the scatter of the sample.
-Maybe we can currently ignore this and let's see the feedback by the referee.
-{\bf Nicola}: ok, I agree}
 %\begin{figure*}[t]%[!b]
@@
 The median values for the flux ratio distribution of the observed, \mbii, \sam\ sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively.
-We perform the KS test the inferred p-values are $0.34$ (for observed -- \mbii) and $0.14$ (for observed -- \sam), respectively.\pink{These results indicate that one cannot reject the hypothesis that the distributions of the three samples are the same at $10\%$.}
+We perform the KS test the inferred p-values are $0.34$ (for observed -- \mbii) and $0.14$ (for observed -- \sam), respectively.
+\pink{These results indicate that one cannot reject the hypothesis that the distributions of the three samples are the same at $10\%$.}
 
@@
 At present, it is still unclear how much difference in the observed scatter between \mbii\ and \sam\ is due to the different recipes of triggering, hierarchical merging, gas fueling, and AGN feedback.
-For instance, even without introducing AGN feedback, the predictions by \citet{2017MNRAS.464.2840A} \textcolor{green}{- based on torques owing to disc instabilities as
- drivers for black hole feeding -} could also have low scatter products in their simulation.}
-\textcolor{green}{This may indicate that the origin of the smaller scatter in the N-body simulations is related to fact that the considered feeding mechanisms (Bondi accretion or disc instabilities) depend only on the properties of the black hole and host galaxy.
+For instance, even without introducing AGN feedback, the predictions by \citet{2017MNRAS.464.2840A}- based on torques owing to disc instabilities as
+ drivers for black hole feeding - could also have low scatter products in their simulation.}
+This may indicate that the origin of the smaller scatter in the N-body simulations is related to fact that the considered feeding mechanisms (Bondi accretion or disc instabilities) depend only on the properties of the black hole and host galaxy.
 This strongly differs from the SAM assumption that two-body process (interactions) are the main trigger for black hole accretion.
-As for the role of feedback, }\pink{
-it will be more insightful to carry out a comparative test based on one numerical model and altering the AGN feedback prescription, while fixing all other conditions \citep[see][]{Hopkins2009}.
+As for the role of feedback, \pink{it will be more insightful to carry out a comparative test based on one numerical model and altering the AGN feedback prescription, while fixing all other conditions \citep[see][]{Hopkins2009}.
 }
@@
 Under this scenario, the scatter of the scaling relations has to increase with redshift.
-Our observations contradict this hypothesis.\pink{In fact, the inferred {\it intrinsic} scatter of our observed sample (i.e., $\sim0.25$~dex) is even no more significant than the typical scatter of local relations reported in the literature ~\citep[][i.e., $\gtrsim0.35$~dex]{Kormendy13, Gul++09, Reines2015}.} Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level of intrinsic scatter for the real data, but it is unlikely that systematic errors would conspire to {\it reduce} scatter.
+Our observations contradict this hypothesis.
+\pink{In fact, the inferred {\it intrinsic} scatter of our observed sample (i.e., $\sim0.25$~dex) is even no more significant than the typical scatter of local relations reported in the literature ~\citep[][i.e., $\gtrsim0.35$~dex]{Kormendy13, Gul++09, Reines2015}.} Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level of intrinsic scatter for the real data, but it is unlikely that systematic errors would conspire to {\it reduce} scatter.
 Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), resulting in an overestimating of the error-budget and thus underestimating of intrinsic scatter, but again it is hard to imagine that the \halpha\ \mbh\ estimators be much more precise than an factor of two.
@@
 \acknowledgments
-\ding{How do we present our thanks to the three NA referees properly?}
 Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
@@
 
-\bibliography{reference}
+%\bibliography{reference}
+\input{manuscript.bbl}
 %\bibliographystyle{aasjournal}

### 2020-04-21 QSOII_paper/ApJ_manuscript/manuscript.tex
Upload referee report and remove color marks

@@
 \newcommand{\pink}[1]{{ \textcolor{magenta}{#1}}}
+%\newcommand{\blue}[1]{{{#1}}}
+%\newcommand{\pink}[1]{{{#1}}}
 
@@
 For this purpose, we have constructed a unique sample of 32 actively-accreting SMBHs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with accurate BH and stellar masses with the latter based on multi-band \hst\ imaging.
-\pink{To examine the scaling relations between the mass of a supermassive black hole (SMBH) and its host galaxy properties, we adopt the recent measurements based on 32 X-ray-selected broad-line Active Galactic Nucleus (AGNs) at $1.2<z<1.7$, and} make direct comparison with two independent state-of-the-art projects, including the hydrodynamic simulation \texttt{MassiveBlackII} (\mbii) and the semi-analytic model (\sam).
-After applying the observational selection function to the simulations to account for the bias, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
-However, accounting for observational errors, the dispersion in the mass ratio between \mbh\ and \mstar\ is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex) one.
+We examine the scaling relations between the mass of a supermassive black hole (SMBH) and its host galaxy properties at $1.2<z<1.7$ using both observational data and simulations.
+Recent measurements of 32 X-ray-selected broad-line Active Galactic Nucleus (AGNs) are compared with two independent state-of-the-art efforts, including the hydrodynamic simulation \texttt{MassiveBlackII} (\mbii) and a semi-analytic model (\sam).
+After applying an observational selection function to the simulations, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution.
+However, the dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex), even when accounting for observational uncertainties.
 Hence, our observations can distinguish between the different recipes adopted in the models.
@@
 \section{Introduction} \label{sec:intro}
-\blue{Supermassive black holes (SMBHs) ubiquitously occupy the center of massive galaxies in the local Universe and beyond.
-Their growth in mass (\mbh) appears to be closely linked to the physical properties of their host galaxies, in particular the relation between \mbh ~and stellar mass (\mstar)~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}, indicating a physical coupling during their co-evolution.}
+Supermassive black holes (SMBHs) ubiquitously occupy the center of massive galaxies in the local Universe and beyond.
+Their growth in mass (\mbh) appears to be closely linked to the physical properties of their host galaxies, in particular the relation between \mbh ~and stellar mass (\mstar)~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}, indicating a physical coupling during their co-evolution.
 Various models have been proposed to explain this connection between SMBH and their host galaxies.
@@
 
-To understand this connection, recent works~\citep{Park15, Tre++07, Bennert11, Woo++08} have measured the scaling relations out to intermediate redshift {($0.3\lesssim z \lesssim1$)} by studying AGN and their host galaxies with {\it Hubble Space Telescope} ({\it HST}) and found an {\it observed} evolution in which the growth of SMBHs predates their host galaxies.
-However, the observational evidence of such evolution at higher-$z$ is under debate since it depends on our understanding of systematic uncertainties and selection effects~\citep{Tre++07,Lauer2007}.
-Therefore, an improper consideration of the uncertainties and selection effects may lead to an {\it apparent} evolution and result in an overestimate of the significance of the evolution~\citep{Volonteri2011}.
+Considerable efforts have been undertaken to establish the scaling relations out to high redshift ($z \lesssim2$) using the {\it Hubble Space Telescope} (\hst) to detect the host galaxies of AGN \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08,Jahnke2009,Bennert11,Schramm2013,Park15,Mechtley2016,Ding2019}.
+While some studies find an {\it observed} evolution in which the growth of SMBHs predates their host galaxies, there are equally as many claims of no evolution when considering the total stellar mass of the host.
+For all studies, an understanding of the systematic uncertainties and selection effects~\citep{Tre++07,Lauer2007,Schulze2014} need to be considered to avoid an {\it apparent} evolution that may overestimate the significance of the evolution~\citep{Volonteri2011}.
 
@@
 %The reason to extend to high redshift.
-Simulations are effective at helping to understand this connection and rule out theories and assumptions that could not be definitively verified by observations alone.
+
+Simulations can effectively aid in our understanding of this connection by ruling out theories and assumptions that could not be definitively verified by observations alone.
 In particular, simulations can be used to quantify the impact of systematic uncertainties and selection biases with observational data.
-Recent studies, based on several simulations, show agreement with the observational data at intermediate redshifts ($z\lesssim1$).
-For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been utilized to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ that show a positive evolution where the SMBH growth predates that of its the host galaxy~\citep{DeG++15}.
-Several other works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\citep{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\citep{Schaye2015}, and Illustris moving mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019}.
-Besides hydrodynamic simulations, semi-analytic models~\citep[][\ding{Hi Nicola, do you think we can refer Thomas2019 here as another semi-analytic model?}]{Menci2014, Menci2016, Thomas2019} have also made remarkable progress and recovered the local scaling relations~\citep{Kormendy13}.
-However, comparisons between simulations and the observed scaling relations, based on high-resolution \hst\ imaging, are still mostly limited to $z<1$ due to prior limitations of observational data.
+For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been used to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ which show a positive evolution where the SMBH growth predates that of its the host galaxy~\citep{DeG++15}.
+Several other works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\citep{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\citep{Schaye2015}, Illustris moving mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019} and SIMBA simulation~\citep{Thomas2019}.
+Besides hydrodynamic simulations, semi-analytic models~\citep[e.g.,][]{Menci2014, Menci2016} have also made remarkable progress and recovered the local scaling relations~\citep{Kormendy13}.
+These comparisons between simulations and the observed scaling relations, based on high-resolution \hst\ imaging, have been carried out mainly at $z<1$ due to prior limitations of the availability of observational data.
 
-\blue{
-In this study, we push our knowledge of the mass relations to earlier epochs.
-We establish the mass ratios between the SMBHs and their host using 32 type-1 AGNs and make direct comparisons to the predicted type-1 AGNs based on two independent state-of-the-art numerical simulations.}
-\ding{The referee \#2 asks us to comment on what kinds of biases may be introducing since we use only type-1 AGNs. Xuheng thinks this request is trivial and let's ignore this.}
-\blue{The redshift range of our targets is chosen to be high enough ($z>1$) when most of the SMBHs acquired their mass, are more sensitive to initial
-conditions and the growth mechanisms and thus may be able to identify inaccurate or missing physics in the models,  while low enough ($z<2$) to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy.
-We describe the observed and simulated targets in Section~\ref{sec:sample}.
-The comparison result are shown in Section~\ref{sec:result} with conclusion presented in Section~\ref{sec:conclusion}.
+In this study, we directly compare the mass ratios between SMBHs and their host galaxies of 32 type-1 (broad-line) AGNs from our recent observational study at $z\sim1.5$ \citep{Ding2019} to the predictions based on two independent state-of-the-art numerical simulations.
+The redshift range of our targets is chosen to be high enough ($z>1$) when most of the SMBHs acquired their mass thus sensitive to initial
+conditions and growth mechanisms, possibly allowing an identification of inaccurate or missing physics in the models.
+The redshift range is low enough ($z<2$) to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy with \hst.
+We describe the observed and simulated galaxies and their black holes in Section~\ref{sec:sample}.
+The comparisons between data and simulations are shown in Section~\ref{sec:result} and conclusion presented in Section~\ref{sec:conclusion}.
 Throughout this paper, we adopt a standard concordance
@@
 observed and simulated sample.
-}
 
-\pink{
-\section{Sample: Observation and Simulation}~\label{sec:sample}
+\section{Sample: Observations and Simulations}~\label{sec:sample}
 % The work that we want to do
@@
 	%mention the scatter.
-In this section, we introduce our comparison samples, including the observed scaling relations (Section~\ref{hst_sample}) and the predicted ones by two independent numerical simulations (Section~\ref{sample_sim}).}
+In this section, we introduce our comparison samples, including the observed scaling relations (Section~\ref{hst_sample}) and the predicted ones by two independent numerical simulations (Section~\ref{sample_sim}).
 
-\subsection{HST Observational data}\label{hst_sample}
+\subsection{\hst\ Observational data}\label{hst_sample}
 
-We have been analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} (D19~\citep{Ding2019} hereafter).
+We have been constructing and analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} (D19~\citep{Ding2019} hereafter).
 We selected our AGN sample in a well-defined window based on the \mbh\ and Eddington ratio, as shown in Figure~1 in D19.
-As shown in that Figure, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias.
+As shown in that Figure, the \mbh\ are well below the knee of the BH mass distribution to avoid a strong selection bias.
 In addition, the Eddington ratios are mostly above $0.1$ to ensure homogeneity.
@@
 
-\blue{We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy.
-A detailed description of the \hst\ data analysis can be found in a companion paper ~\citep[][D19 hereafter]{Ding2019}.
-Here we only present a brief summary of that study.
-We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ (according to the redshift of the targets) to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman).
-We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to co-add the final image with pixel scale as 0\farcs0642.
-To mitigate the contamination by the background light from both the sky and the detector, we adopt the {\sc photuils} tools to estimate and remove them accurately.}
+To detect their host galaxies, we used \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) infrared imaging data for 32 AGN systems (HST Program GO-15115).
+The filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ were employed, according to the redshift of each target.
+Six dithered exposures with a total exposure time $\sim2394s$ were co-added using the {\sc astrodrizzle} software package to generate a final image with a pixel scale as 0\farcs0642.
+We implemented the {\sc photuils} tools to remove contamination due to background light from both the sky and the detector.
+A full detailed description of the \hst\ data analysis can be found in a companion paper ~\citep[][D19 hereafter]{Ding2019}.
 
-\blue{To address the bias which might be raised by the unknown PSF, we manually collect the isolated-unsaturated PSF-stars from the 32 observed fields, to assemble a PSF library for the fitting.
-To decompose each AGN image, we assume the unresolved active nuclei as the scaled point source and the host galaxy as the \sersic\ profile.
-We adopt imaging modeling tool \lenstronomy~\citep{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one by one from the collected PSF library.
+We implemented state-of-the-art techniques to perform 2D flux profile decomposition to disentangle the host emission from the AGN.
+To address biases with respect to the accuracy of the point-spread function (PSF), we collected 2D profiles of isolated and unsaturated stars from the 32 observed \hst\ fields to assemble a PSF library for the fitting routine.
+To decompose each AGN image, we assume the unresolved active nuclei as scaled point source and the host galaxy as a \sersic\ profile.
+We ran the imaging modeling tool \lenstronomy~\citep{lenstronomy} to simultaneously fit their 2D flux distribution, taking each PSF one-by-one from the collected PSF library.
 Based on the reduced $\chi^2$, we are capable of evaluating the performance of each PSF.
-We adopt the result from the top-ranked-eight PSFs and using the weighting process to obtain the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.}
+We adopt the result from the top-ranked-eight PSFs and used a weighting process to obtain the host properties, including flux, \reff, \sersic\ index.
 
-\blue{The COSMOS survey provides \hst\ ACS/F814W imaging data for 21 of 32 AGN in our sample with a drizzled pixel scale as 0\farcs03.
-We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3's result to infer the host color.
-We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar).}
+The COSMOS survey provides \hst\ ACS/F814W imaging data for 21 of 32 AGN in our sample with a drizzled pixel scale as 0\farcs03.
+We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3 result to infer the host color.
+We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the colors of the host to derive the rest frame R-band magnitude (\mr) and the stellar mass (\mstar)-to-light ratio.
 
-\pink{We note that in \citet{Sun2015}, a sample of 69 type-1 AGN has been studied to measure the mass relations at redshift range $0<z<2$.
-Nevertheless, aiming at achieving a direct comparison to the simulations, we selected not to take their sample given that their sample is chosen with the incongruous selection function.
-Moreover, their \mstar\ is inferred by fitting the spectral energy distribution, and \mbh\ is estimated using different broad lines (i.e., \hbeta\ and \Mgii), which could both introduce larger systematics.}
+We remark that the observational data used in this study is limited to our carefully-constructed sample with a well-understood selection function and 2D assessment of the host galaxy emission from space-based imaging.
+While there exists larger data sets such as \citet{Sun2015} and others, we refrain from including cases where the host galaxy was assessed using fitting of the spectral energy distribution~(SED) with broad-band photometry from the ground since there are likely higher levels of uncertainty with respect to cases with an AGN of considerable luminosity.
+However, we recognize that there has yet been definitive evidence for inherent problems with these methods.
 
@@
 The \mbii\ simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
-The large simulation volume enables the model galaxies and SMBHs to evolve independently; the large dynamic range in mass and high spatial resolution meet the requirements to investigate their individual galaxies.
-While high-resolution N-body simulations can study specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam.
-In previous works, \mbii~\citep{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\citep{Menci2014, Menci2016} have made high successful predictions.
-\blue{In the following two sections, we present the detailed information of the two simulation projects.}
+The large simulation volume enables the model galaxies and SMBHs to evolve independently; the large dynamic range in mass and high spatial resolution meet the requirements to study individual galaxies.
+While high-resolution N-body simulations can describe specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam.
+In previous works, \mbii~\citep{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\citep{Menci2014, Menci2016} have made highly successful predictions.
+In the following two sections, we present detailed information on the two simulation projects.
 
 \subsubsection{\texttt{MassiveBlackII} simulation}
-The MassiveBlackII (\mbii) is a high-resolution cosmological hydrodynamic simulation using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\citep{2005MNRAS.364.1105S}.
+MassiveBlackII (\mbii) is a high-resolution cosmological hydrodynamic simulation using Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\citep{2005MNRAS.364.1105S}.
 It has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles.
@@
 
-For the galaxy photometry, the spectral energy distributions~(SEDs) of the host galaxies were first obtained by summing up the contributions from the individual star particles.
+For the galaxy photometry, the SEDs of the host galaxies were first obtained by summing up the contributions from the individual star particles.
 The stellar SEDs were modelled using the \texttt{PEGASE-2}~\citep{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF.
-The galaxy SEDs are finally convolved with the desired filter function to obtain the broad band photometry~(SDSS $r$ band magnitude).
+The galaxy SEDs are finally convolved with the desired filter function to obtain the broad band photometry~(SDSS $r$-band magnitude).
 
-We follow the common practice and adopt the stellar mass within a 3D spherical aperture of 30 kpc to adopt as the more faithful proxy of the observed stellar mass in the \mbii\ simulation.
-It has been shown that this definition of the stellar produces a stellar mass function that is consistent with observational constraints~\citep{Pillepich2018}.
-Further, the stellar mass in this physical aperture provides good agreement to those measured within Petrosian radii in observational studies ~\citep{Schaye2015}.
-
+Following common practice, the stellar mass is determined within a 3D spherical aperture of 30 kpc as a proxy of the observed stellar mass in the \mbii\ simulation.
+It has been shown that this definition reproduces a stellar mass function that is consistent with observational measurements~\citep{Pillepich2018}.
+Furthermore, the stellar mass in this physical aperture provides good agreement to those measured within Petrosian radii in observational studies ~\citep{Schaye2015}.
 For further details regarding the \mbii\ simulation, we refer the reader to the reference~\citep{2015MNRAS.450.1349K}.
@@
 
-We compare the relation \mbh--\mstar~between observations and the \mbii\ simulation. First, it is clear that the simulated and observed samples are in good agreement. 
-\blue{To quantify the agreement between the simulation and the observation, we use a linear regression to fit their relations and compare the result.
+In the left panel of Figure~\ref{fig:MM_comp}, we compare the relation \mbh--\mstar~between observations and the \mbii\ simulation.
+It is clear that the simulated and observed samples are in good agreement.
+To quantify the agreement between the simulated and observed data, we use a linear regression to fit their relations.
 Our selection window has a hard cut on the \mbh\ value (i.e., vertical direction in Figure~\ref{fig:selectfunc}), and thus the scatter on the host properties are larger (horizontal direction).
@@
 We adopt the {\sc Scipy} package to estimate the best-fit inference for the simulated sample.
-We then fit for the observations based on the same slope value.
-The comparison results are showing in Figure~\ref{fig:MM_comp} (left panel), with the standard derivation of the residual indicated by the colored regions.}
-\pink{To estimate the {\it observed} scatter of the sample, we calculate the standard deviation of the fitting residual based on \mstar\ (i.e., along the $x$-axis).}\blue{The histogram of the residual is presented in Figure~\ref{fig:offset_comp} (left panel).
-We find the standard derivation of the residual for observed and \mbii\ sample are at the same level and both equal to $\sim0.3$~dex.}\pink{We test to vary the fixed slope value by its uncertainty level but found the corresponding {\it observed} scatters barely changed ($<1\%$), meaning that the inferred scatter weakly depends on the fitted slope.
-Note that, with a different definition of the {\it observed} scatter, the measured value could be different.
-In this particular work, we simply apply a common standard (i.e., consider the measured residual in \mstar) to achieve a direct comparison between different samples.}\blue{We perform the Kolmogorov-Smirnov (KS) test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$.
+We then fit the observations based on the same slope value.
+The comparison results are shown in Figure~\ref{fig:MM_comp} (left panel), with the standard deviation of the residual indicated by the colored regions.
+To estimate the {\it observed} scatter of the sample, we calculate the standard deviation of the fitted residual based on \mstar\ (i.e., along the $x$-axis).
+The histogram of the residual is presented in Figure~\ref{fig:offset_comp} (left panel).
+We find the standard deviation of the residual for observed and \mbii\ sample are similar, i.e., both equal to $\sim0.3$~dex.
+We manually change the slope value by its uncertainty level and find that the corresponding {\it observed} scatter barely changes ($<1\%$), meaning that the inferred scatter weakly depends on the fixed slope.
+We note that with different definitions to calculate the scatter, the inferred value may result in a more pronounced difference.
+In this particular work, we simply apply a common standard method (i.e., consideration of the measured residual in \mstar) to achieve a direct comparison between different samples.
+We perform the Kolmogorov-Smirnov (KS) test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$.
 Considering that the simulation sample has been processed to have the same uncertainty level and selection effect, we expect the \mbii\ sample and the observational sample have the same intrinsic scatter level.
-We adopt the python package {\sc Linmix}~\citep{Kelly2007} to estimate this {\it intrinsic} scatter based on the \mbii\ overall sample and obtain the level as $0.25$~dex.
-}
+We adopt the python package {\sc Linmix}~\citep{Kelly2007} to estimate the {\it intrinsic} scatter based on the \mbii\ overall sample and obtain a level of $0.25$~dex.
+
 %Overlapped part when change template to ApJ:To quantify the agreement level, we perform a linear regression to fit the simulated relations and estimate the best-fit inference.
@@
 \includegraphics[width=1.2\linewidth]{MBII_selectfunc.pdf}
-\caption{The same selection window as adopted for selecting the \mbii\ simulated sample.
-The brown background cloud shows the simulated number density of the overall \mbii\ sample at $z=1.5$.
-We add the random uncertainty to the simulation and select the ones fall into the targeting region (i.e., blue colored).
-The orange dots are the \hst\ observed sample.}
+\caption{Equivalent selection window adopted for the \hst-observed and  \mbii\ simulated samples.
+The background cloud (in light brown/grey) shows the simulated number density of the overall \mbii\ sample at $z=1.5$.
+We added random uncertainty to the simulation and select those that fall into the target region (i.e., small blue circles).
+The small orange circles are the \hst\ observed sample.}
 \label{fig:selectfunc}
@@
 
-We also compare our data to the predictions by the \sam\ model.
-Rather than N-body simulation which produces individual simulating objects, the \sam\ model\pink{uses the interaction-driven model~\citep{Menci2014} to calculate the number density of the galaxies.} To make a direct comparison, we first randomly produce an overall sample based on the \pink{\sam\ predicted number density} at $z=1.5$.
+We also compare our data to predictions by the \sam.
+In contrast to N-body simulations which produce individual objects, the \sam\ uses an interaction-driven model~\citep{Menci2014} to calculate the number density of the galaxies.
+To make a direct comparison, we first randomly produce an overall sample based on the \sam\ predicted number density at $z=1.5$.
 Then, as in the \mbii\ analysis, we inject random scatter in the sample to account for uncertainties and apply the observational selection function.
-The resulting comparison of the  \mbh-\mstar\ relation are shown in Figure~\ref{fig:MM_comp} (right panel).
+The resulting comparison of the  \mbh-\mstar\ relation is shown in Figure~\ref{fig:MM_comp} (right panel).
 We find that the best-fit result by the \sam\ model is well matched to the observation.
@@
 
- \ding{Do we want to mention that the inferred slope of the MBII is much steeper than the SAM ones?
-It is a little complicated, since we have a limited MBH range and fitted slope value may be related to the scatter of the sample.
-Maybe we can currently ignore this and let's see the feedback by the referee.}
 %\begin{figure*}[t]%[!b]
@@
 
-\blue{We also present the comparison of the \mbh-\mr\ relations in Figure~\ref{fig:ML_comp} and the comparison of the scatter in Figure~\ref{fig:offset_comp} (right panel).
-The results are similar to \mbh-\mstar\ relations.}
+We also present the comparison of the \mbh-\mr\ relations in Figure~\ref{fig:ML_comp} and the comparison of the scatter in Figure~\ref{fig:offset_comp} (right panel).
+The results are similar to \mbh-\mstar\ relations.
 
@@
 
-To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples.
-For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3.
-For the simulated sample, we consider the AGN bolometric correction~\citep{Elvis1994} to estimate the AGN light flux at WFC3/F125W band.
-We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched to each other.
+To test if any unexpected selection effects exist, we compare the distribution of the host-to-total flux ratio among these three samples.
+For the observed sample, we calculate the flux ratio in the \hst/WFC3 band.
+For the simulated sample, we consider the AGN bolometric correction~\citep{Elvis1994} to estimate the AGN flux in the WFC3/F125W band.
+We compare their host-total flux distribution in Figure~\ref{fig:comp_hist} and find that the three samples are well matched to each other.
 The median values for the flux ratio distribution of the observed, \mbii, \sam\ sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively.
-We perform the KS test the inferred p-values are $0.34$ (for observed -- \mbii) and $0.14$ (for observed -- \sam), respectively.\pink{These results indicate that one cannot reject the hypothesis that the distributions of the three samples are the same at $10\%$.}
+We perform the KS test the inferred p-values are $0.34$ (for observed -- \mbii) and $0.14$ (for observed -- \sam), respectively.
+These results indicate that one cannot reject the hypothesis that the distributions of the three samples are the same at $10\%$.
 
@@
 % It is still unclear how much different in scatter between MBII and SAM is due to the AGN feedback. A directly work using one simulation is needed to be done.
-\pink{The fact that one model (i.e., \sam) does not agree with the observed dispersion is not direct evidence that supports all the physical assumptions implemented in the other model (i.e., \mbii), especially when these two models adopt completely different numerical techniques.
+The fact that one model (i.e., \sam) does not agree with the observed dispersion is not direct evidence that supports all the physical assumptions implemented in the other model (i.e., \mbii), especially when these two models adopt completely different numerical techniques.
 At present, it is still unclear how much difference in the observed scatter between \mbii\ and \sam\ is due to the different recipes of triggering, hierarchical merging, gas fueling, and AGN feedback.
-For instance, even without introducing AGN feedback, the predictions by \citet{2017MNRAS.464.2840A} could also have low scatter products in their simulation.
-It will be more insightful to carry out a comparative test based on one numerical model that using different the AGN feedback assumptions, and setting all the other conditions as the same \citep[see][as a glimpse]{Hopkins2009}.
-}
+For instance, even without introducing AGN feedback, the predictions by \citet{2017MNRAS.464.2840A}- based on torques owing to disc instabilities as
+ drivers for black hole feeding - could also have low scatter products in their simulation.
+This may indicate that the origin of the smaller scatter in the N-body simulations is related to fact that the considered feeding mechanisms (Bondi accretion or disc instabilities) depend only on the properties of the black hole and host galaxy.
+This strongly differs from the SAM assumption that two-body process (interactions) are the main trigger for black hole accretion.
+As for the role of feedback, it will be more insightful to carry out a comparative test based on one numerical model and altering the AGN feedback prescription, while fixing all other conditions \citep[see][]{Hopkins2009}.
 
-Without any physical mechanisms, it has been shown that just due to the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010} scaling relations may emerge from random mergers, starting from a stochastic cloud in the early universe.
-In this scenario, the scatter of the scaling relations has to increase with redshift.
-Our observations contradict this hypothesis.\pink{In fact, the inferred {\it intrinsic} scatter of our observed sample (i.e., $\sim0.25$~dex) is even no more significant than the typical scatter of local relations reported in the literature ~\citep[][i.e., $\gtrsim0.35$~dex]{Kormendy13, Gul++09, Reines2015}.} Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level of intrinsic scatter for the real data, but it is unlikely that systematic errors would conspire to {\it reduce} scatter.
+Without a direct physical mechanism, it has been shown that, due to the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010}, scaling relations may emerge from random mergers, starting from a stochastic cloud in the early universe.
+Under this scenario, the scatter of the scaling relations has to increase with redshift.
+Our observations contradict this hypothesis.
+In fact, the inferred {\it intrinsic} scatter of our observed sample (i.e., $\sim0.25$~dex) is even no more significant than the typical scatter of local relations reported in the literature ~\citep[][i.e., $\gtrsim0.35$~dex]{Kormendy13, Gul++09, Reines2015}.
+Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate, since we use the \mbii\ overall sample as a proxy to estimate the level of intrinsic scatter for the real data, but it is unlikely that systematic errors would conspire to {\it reduce} scatter.
 Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), resulting in an overestimating of the error-budget and thus underestimating of intrinsic scatter, but again it is hard to imagine that the \halpha\ \mbh\ estimators be much more precise than an factor of two.

### 2020-04-24 QSOII_paper/ApJ_manuscript/manuscript.tex
Update for revising the paper

@@
 \newcommand{\red}[1]{{ \textcolor{red}{#1}}}
-\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
-\newcommand{\pink}[1]{{ \textcolor{magenta}{#1}}}
+\newcommand{\blue}[1]{{\textcolor{blue}{\bf #1}}}
+\newcommand{\pink}[1]{{\textcolor{magenta}{#1}}}
 %\newcommand{\blue}[1]{{{#1}}}
@@
 
-Considerable efforts have been undertaken to establish the scaling relations out to high redshift ($z \lesssim2$) using the {\it Hubble Space Telescope} (\hst) to detect the host galaxies of AGN \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08,Jahnke2009,Bennert11,Schramm2013,Park15,Mechtley2016,Ding2019}.
+Considerable efforts have been undertaken to establish the scaling relations out to high redshift ($z \lesssim2$) using the {\it Hubble Space Telescope} (\hst) to detect the host galaxies of AGN \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08,Jahnke2009,Bennert11,Schramm2013,Park15,Mechtley2016,Ding2020}.
 While some studies find an {\it observed} evolution in which the growth of SMBHs predates their host galaxies, there are equally as many claims of no evolution when considering the total stellar mass of the host.
@@
 
-In this study, we directly compare the mass ratios between SMBHs and their host galaxies of 32 type-1 (broad-line) AGNs from our recent observational study at $z\sim1.5$ \citep{Ding2019} to the predictions based on two independent state-of-the-art numerical simulations.
-The redshift range of our targets is chosen to be high enough ($z>1$) when most of the SMBHs acquired their mass thus sensitive to initial
-conditions and growth mechanisms, possibly allowing an identification of inaccurate or missing physics in the models.
-The redshift range is low enough ($z<2$) to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy with \hst.
+In this study, we directly compare the mass ratios between SMBHs and their host galaxies of 32 type-1 (broad-line) AGNs from our recent observational study at $z\sim1.5$ \citep{Ding2020} to the predictions based on two independent state-of-the-art numerical simulations.
+\blue{The redshift range of our targets is chosen ($z<2$) when most of the SMBHs acquired their mass thus insensitive to initial conditions and growth mechanisms, which allows an identification of inaccurate or missing physics in the models.
+This redshift range is also low enough} to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy with \hst.
 We describe the observed and simulated galaxies and their black holes in Section~\ref{sec:sample}.
@@
 
-We have been constructing and analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} (D19~\citep{Ding2019} hereafter).
-We selected our AGN sample in a well-defined window based on the \mbh\ and Eddington ratio, as shown in Figure~1 in D19.
+We have been constructing and analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} \citep[][\blue{hereafter D20}]{Ding2020}.
+We selected our AGN sample in a well-defined window based on the \mbh\ and Eddington ratio, as shown in Figure~1 in \blue{D20}.
 As shown in that Figure, the \mbh\ are well below the knee of the BH mass distribution to avoid a strong selection bias.
@@
 %We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy.
-Moreover, 21/23 systems have \hst/ACS imaging data, which enables us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see METHODS and the descriptions in D19).
+Moreover, 21/23 systems have \hst/ACS imaging data, which enables us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see METHODS and the descriptions in \blue{D20}).
 
@@
 We implemented the {\sc photuils} tools to remove contamination due to background light from both the sky and the detector.
-A full detailed description of the \hst\ data analysis can be found in a companion paper ~\citep[][D19 hereafter]{Ding2019}.
+A full detailed description of the \hst\ data analysis can be found in \blue{the companion paper (D20)}.
 
@@
 We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3 result to infer the host color.
-We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the colors of the host to derive the rest frame R-band magnitude (\mr) and the stellar mass (\mstar)-to-light ratio.
+We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in \blue{D20}, from which we estimate the colors of the host to derive the rest frame R-band magnitude (\mr) and the stellar mass (\mstar)-to-light ratio.
 
@@
 The \mbii\ simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
-The large simulation volume enables the model galaxies and SMBHs to evolve independently; the large dynamic range in mass and high spatial resolution meet the requirements to study individual galaxies.
+\blue{The large simulation volume enables the Fourier density modes on the largest scales to evolve independently;} the large dynamic range in mass and high spatial resolution meet the requirements to study individual galaxies.
 While high-resolution N-body simulations can describe specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam.
@@
 Haloes were identified using a Friends-of-Friends (FOF) group finder ~\citep{1985ApJ...292..371D}.
-Within these haloes, self-bound substructures/subhaloes were identified using \texttt{SUBFIND} ~\citep{2005MNRAS.364.1105S}.
+Within these haloes, self-bound substructures/subhaloes were identified using \texttt{SUBFIND} ~\citep{Springel2001, 2005MNRAS.364.1105S}.
 Galaxies are identified with the stellar matter components of subhaloes.
@@
 A fraction~($5\%$) of the radiated energy couples to the surrounding gas as black hole~(or AGN) feedback ~\citep{2005Natur.433..604D}.
-For the modeling of black hole mergers, two black holes are considered to be merged if their separation distance is within the spatial resolution of the simulation~(the SPH smoothing length), and their relative speeds are lower than the local sound speed of the medium.
+\blue{Note that unlike some previous work, the accretion rate in \mbii\ follows the prescription in~\citet{Pelupessy2007} which does not use any artificial boost factor.} For the modeling of black hole mergers, two black holes are considered to be merged if their separation distance is within the spatial resolution of the simulation~(the SPH smoothing length), and their relative speeds are lower than the local sound speed of the medium.
 
@@
 We manually change the slope value by its uncertainty level and find that the corresponding {\it observed} scatter barely changes ($<1\%$), meaning that the inferred scatter weakly depends on the fixed slope.
-We note that with different definitions to calculate the scatter, the inferred value may result in a more pronounced difference.
+\blue{To understand how much of the scatter is from the random noise, we measure the scatter \mbii\ without injecting any noise to the data.
+Adopting the same selecting window and using the linear regression approach, we estimate the scatter value as $\sim0.1$~dex.
+Note that this $\sim0.1$~dex scatter level is also controlled by our selection window, which shouldn't be considered as the intrinsic scatter of the overall sample.} We note that with different definitions to calculate the scatter, the inferred value may result in a more pronounced difference.
 In this particular work, we simply apply a common standard method (i.e., consideration of the measured residual in \mstar) to achieve a direct comparison between different samples.
@@
 \begin{tabular}{c c}
-\includegraphics[trim = 0mm 0mm 65mm 0mm, clip, width=0.47\linewidth]{MBII_MM.pdf} &
-\includegraphics[trim = 0mm 0mm 65mm 0mm, clip, width=0.47\linewidth]{SAM_MM_consider_nois.pdf} \\
+\includegraphics[trim = 0mm 0mm 65mm 0mm, clip, width=0.47\linewidth]{MBII_MM.png} &
+\includegraphics[trim = 0mm 0mm 65mm 0mm, clip, width=0.47\linewidth]{SAM_MM_consider_nois.png} \\
 \end{tabular}
@@
 The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the standard deviation of the residual.
-By fixing the slope to match the simulated data, the orange color shows the result for the observed data set.
+\blue{The background cloud (in light brown/grey) shows the simulated number density, as Figure~\ref{fig:selectfunc}.} By fixing the slope to match the simulated data, the orange color shows the result for the observed data set.
 The grey cells in the background show the full \mbii\ simulated SMBHs.
@@
 However, the scatter of the \sam\ model is significantly larger ($\sim0.7$~dex) than observed (this is the total scatter accounting for the intrinsic scatter in the \sam\ distribution, observational uncertainties, and selection effects).
+\blue{Even without injecting random noise to \sam\ data, we find the scatter (considering selection effect) would up to $\sim0.6$~dex.}
 
@@
 \begin{tabular}{c c}
-\includegraphics[trim = 0mm 0mm 61mm 0mm, clip, width=0.47\linewidth]{MBII_ML.pdf} &
-\includegraphics[trim = 0mm 0mm 61mm 0mm, clip, width=0.47\linewidth]{SAM_ML_consider_nois.pdf} \\
+\includegraphics[trim = 0mm 0mm 61mm 0mm, clip, width=0.47\linewidth]{MBII_ML.png} &
+\includegraphics[trim = 0mm 0mm 61mm 0mm, clip, width=0.47\linewidth]{SAM_ML_consider_nois.png} \\
 \end{tabular}
@@
 At present, it is still unclear how much difference in the observed scatter between \mbii\ and \sam\ is due to the different recipes of triggering, hierarchical merging, gas fueling, and AGN feedback.
-For instance, even without introducing AGN feedback, the predictions by \citet{2017MNRAS.464.2840A}- based on torques owing to disc instabilities as
+For instance, even without introducing AGN feedback, the predictions by \citet{2017MNRAS.464.2840A} - based on torques owing to disc instabilities as
  drivers for black hole feeding - could also have low scatter products in their simulation.
 This may indicate that the origin of the smaller scatter in the N-body simulations is related to fact that the considered feeding mechanisms (Bondi accretion or disc instabilities) depend only on the properties of the black hole and host galaxy.
-This strongly differs from the SAM assumption that two-body process (interactions) are the main trigger for black hole accretion.
+This strongly differs from the \sam\ assumption that two-body process (interactions) are the main trigger for black hole accretion. 
 As for the role of feedback, it will be more insightful to carry out a comparative test based on one numerical model and altering the AGN feedback prescription, while fixing all other conditions \citep[see][]{Hopkins2009}.
+
+\blue{Implementing new physical assumptions to \sam\ is not straightforward to solve the tension as discovered in the scatter. 
+%In practice, if one adjust the physical parameters in the SAM model, the scatter would not be as a tunable output. 
+Increasing, for example, the efficiency of AGN feedback would change the colors of massive galaxies, while changing the Supernovae feedback efficiency would result in a different slope of the galaxy luminosity functions at the faint end.
+Most importantly, these changes would not appreciably affect the scatter, which originates from the assumption of interactions as triggers for BH accretion.
+In the \sam\ model, it is possible to switch to disk instabilities as triggers for accretion.
+However, this channel alone would not be able to yield the accretion rates necessary to power the most luminous quasars~\citep[see][]{Menci2014}.
+Implementing ``ad-hoc'', i.e., completely phenomenological and parametrized laws for the accretion, would require a long-lasting work on tuning the possible parameters exploring the impact of each choice not only on the observables connected to AGN, but also on the properties of the galaxy populations (e.g., colors, luminosity functions, etc.).
+In addition, such a new approach with massive efforts would possibly not provide deeper insights on the physical mechanisms driving the AGN-galaxy connection.}
 
@@
 Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), resulting in an overestimating of the error-budget and thus underestimating of intrinsic scatter, but again it is hard to imagine that the \halpha\ \mbh\ estimators be much more precise than an factor of two.
+
+\blue{The redshifts of our 32 AGN systems cover the range $1.2<z<1.7$.
+It would be equally interesting to consider the evolution trend of the mass relation within this redshift range and make comparion with the simulation ones.
+Unfortunately, the limited sample size couldn't provide sufficient resolution at this board redshift range (see Figure~8 in D20).
+Thus, we only consider the sample with a single redshift bin at $z\sim1.5$ to compare with the simulations and the local measurements.}
 
@@
 %\\1. How do we discuss the role of AGN feedback?.
+
 \acknowledgments

### 2020-04-24 QSOII_paper/scripts/my_selection_plots_MBII.py

@@ -64,7 +64,7 @@ Lbol_select_noi = Lbol_overall_noi[select_window]
 Eddr_select_noi = Eddr_overall_noi[select_window]
 
 #Now can just plot the figure1 from figures_producer.py
-plt.figure(figsize=(11,9))
+fig, ax = plt.subplots(figsize=(11,9))
 plt.hist2d(bhmass_overall,Eddr_overall,norm=mpl.colors.LogNorm(),cmap='copper',bins=50,zorder=0,alpha=0.5)
 cbar = plt.colorbar()
 cbar.ax.tick_params(labelsize=30) 
@@ -119,10 +119,17 @@ y_sline2 = xfill*0-1.5
 y4 = np.maximum(yfill_sline, y_sline2)
 plt.fill_between(xfill, y4, y2=0, color='steelblue', alpha='0.5', zorder=-1)
 plt.tick_params(labelsize=30)
+
+from matplotlib.ticker import AutoMinorLocator
+ax.xaxis.set_minor_locator(AutoMinorLocator())
+plt.tick_params(which='both', width=2, top=True, right=True,direction='in')
+plt.tick_params(which='major', length=10)
+plt.tick_params(which='minor', length=6)#, color='r’)
+
 plt.ylabel(r"log(L$_{\rm bol}$/L$_{\rm Edd}$)",fontsize=30)
 plt.xlabel(r'log(M$_{\rm BH}$/M$_{\odot}$)',fontsize=30)
 plt.legend(loc='upper right',fontsize=21,numpoints=1)
-#plt.savefig('MBII_selectfunc.pdf')
+plt.savefig('MBII_selectfunc.pdf')
 plt.show()
 
 #%%Plot MM data
@@ -170,7 +177,7 @@ x_obs_space=lfit_fixm(y_space,fit_fixm[0])
 print "mismatch:", fit_fixm[0]- fit[0][1]  #In BH mass offset space
 
 #Plot the 1-D scatter for MM.
-plt.figure(figsize=(8,7))
+fig, ax = plt.subplots(figsize=(8,7))
 plt.hist(stellar_mass_obs - lfit_fixm(bh_mass_obs,fit_fixm[0]), histtype=u'step',normed=True,
          label=('HST sample'), linewidth = 2, color='orange')
 plt.hist(mstar_selected - lfit(bhmass_selected,fit[0][0],fit[0][1]),histtype=u'step',normed=True,
[…]

### 2020-04-29 QSOII_paper/ApJ_manuscript/manuscript.tex
Tommaso's edits

@@
 In this study, we directly compare the mass ratios between SMBHs and their host galaxies of 32 type-1 (broad-line) AGNs from our recent observational study at $z\sim1.5$ \citep{Ding2020} to the predictions based on two independent state-of-the-art numerical simulations.
-\blue{The redshift range of our targets is chosen ($z<2$) when most of the SMBHs acquired their mass thus insensitive to initial conditions and growth mechanisms, which allows an identification of inaccurate or missing physics in the models.
+\blue{The redshift range of our targets is chosen ($z<2$) to coincide with the epoch when most of the SMBHs acquired their mass.
+This choice minimizes sensitivity to initial conditions and growth mechanisms, which in turn allows for an identification of inaccurate or missing physics in the models.
 This redshift range is also low enough} to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy with \hst.
@@
 We implemented the {\sc photuils} tools to remove contamination due to background light from both the sky and the detector.
-A full detailed description of the \hst\ data analysis can be found in \blue{the companion paper (D20)}.
+A full detailed description of the \hst\ data analysis can be found in \blue{a companion paper (D20)}.
 
@@
 We manually change the slope value by its uncertainty level and find that the corresponding {\it observed} scatter barely changes ($<1\%$), meaning that the inferred scatter weakly depends on the fixed slope.
-\blue{To understand how much of the scatter is from the random noise, we measure the scatter \mbii\ without injecting any noise to the data.
+\blue{To understand how much of the scatter derives from random noise, we measure the scatter of \mbii\ without injecting any noise in the data.
 Adopting the same selecting window and using the linear regression approach, we estimate the scatter value as $\sim0.1$~dex.
-Note that this $\sim0.1$~dex scatter level is also controlled by our selection window, which shouldn't be considered as the intrinsic scatter of the overall sample.} We note that with different definitions to calculate the scatter, the inferred value may result in a more pronounced difference.
-In this particular work, we simply apply a common standard method (i.e., consideration of the measured residual in \mstar) to achieve a direct comparison between different samples.
+Note that this $\sim0.1$~dex scatter level is also controlled by our selection window, and thus it should not be considered as the intrinsic scatter of the overall sample.} In this particular work, we simply apply a common standard method (i.e., consideration of the measured residual in \mstar) to achieve a direct comparison between different samples.
 We perform the Kolmogorov-Smirnov (KS) test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$.
@@
 However, the scatter of the \sam\ model is significantly larger ($\sim0.7$~dex) than observed (this is the total scatter accounting for the intrinsic scatter in the \sam\ distribution, observational uncertainties, and selection effects).
-\blue{Even without injecting random noise to \sam\ data, we find the scatter (considering selection effect) would up to $\sim0.6$~dex.}
+\blue{Even without injecting random noise to \sam\ data, we find that the scatter (considering selection effects) would be $\sim0.6$~dex.}
 
@@
 
-\blue{Implementing new physical assumptions to \sam\ is not straightforward to solve the tension as discovered in the scatter. 
+\blue{It is not straightforward to implementing new physical assumptions to \sam\  in order to solve the tension as discovered in the scatter. 
 %In practice, if one adjust the physical parameters in the SAM model, the scatter would not be as a tunable output. 
-Increasing, for example, the efficiency of AGN feedback would change the colors of massive galaxies, while changing the Supernovae feedback efficiency would result in a different slope of the galaxy luminosity functions at the faint end.
+Increasing, for example, the efficiency of AGN feedback would change the colors of massive galaxies, while changing the Supernovae feedback efficiency would result in a different slope of the galaxy luminosity functions at the faint end, which are constrained by other data.
 Most importantly, these changes would not appreciably affect the scatter, which originates from the assumption of interactions as triggers for BH accretion.
@@
 However, this channel alone would not be able to yield the accretion rates necessary to power the most luminous quasars~\citep[see][]{Menci2014}.
-Implementing ``ad-hoc'', i.e., completely phenomenological and parametrized laws for the accretion, would require a long-lasting work on tuning the possible parameters exploring the impact of each choice not only on the observables connected to AGN, but also on the properties of the galaxy populations (e.g., colors, luminosity functions, etc.).
+Implementing ``ad-hoc'', i.e., completely phenomenological and parametrized laws for the accretion, would require a long and detailed exploration of the possible parameters and the impact of each choice not only on the observables connected to AGN, but also on the properties of the galaxy populations (e.g., colors, luminosity functions, etc.).
 In addition, such a new approach with massive efforts would possibly not provide deeper insights on the physical mechanisms driving the AGN-galaxy connection.}
@@
 
-\blue{The redshifts of our 32 AGN systems cover the range $1.2<z<1.7$.
-It would be equally interesting to consider the evolution trend of the mass relation within this redshift range and make comparion with the simulation ones.
-Unfortunately, the limited sample size couldn't provide sufficient resolution at this board redshift range (see Figure~8 in D20).
+\blue{Our sample of 32 AGN systems covers the range $1.2<z<1.7$.
+In principle it would be interesting to consider the evolution trend of the mass relation within the redshift range and make comparisons with the simulation as a function of cosmic time.
+Unfortunately, the limited sample size and precision of the measurement are not sufficient to resolve the evolution within this redshift range (see Figure~8 in D20).
 Thus, we only consider the sample with a single redshift bin at $z\sim1.5$ to compare with the simulations and the local measurements.}

### 2020-05-11 QSOII_paper/ApJ_manuscript/manuscript.tex
Update manuscript.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
-\newcommand{\todo}[1]{\textcolor{red}{[{\bf Todo}: #1]}}  
-\newcommand{\aklant}[1]{\textcolor{blue}{[{\bf AKB}: #1]}} 
-\newcommand{\red}[1]{{ \textcolor{red}{#1}}}
-\newcommand{\blue}[1]{{\textcolor{blue}{\bf #1}}}
-\newcommand{\pink}[1]{{\textcolor{magenta}{#1}}}
 %\newcommand{\blue}[1]{{{#1}}}
@@
 In this study, we directly compare the mass ratios between SMBHs and their host galaxies of 32 type-1 (broad-line) AGNs from our recent observational study at $z\sim1.5$ \citep{Ding2020} to the predictions based on two independent state-of-the-art numerical simulations.
-\blue{The redshift range of our targets is chosen ($z<2$) to coincide with the epoch when most of the SMBHs acquired their mass.
+The redshift range of our targets is chosen ($z<2$) to coincide with the epoch when most of the SMBHs acquired their mass.
 This choice minimizes sensitivity to initial conditions and growth mechanisms, which in turn allows for an identification of inaccurate or missing physics in the models.
-This redshift range is also low enough} to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy with \hst.
+This redshift range is also low enough to limit the effect of surface brightness dimming that would lower the success rate of detecting the underlying host galaxy with \hst.
 We describe the observed and simulated galaxies and their black holes in Section~\ref{sec:sample}.
@@
 
-We have been constructing and analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} \citep[][\blue{hereafter D20}]{Ding2020}.
-We selected our AGN sample in a well-defined window based on the \mbh\ and Eddington ratio, as shown in Figure~1 in \blue{D20}.
+We have been constructing and analyzing a sample of 32 \hst-observed AGN systems over the redshift range $1.2<z<1.7$ from three deep survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} \citep[][hereafter D20]{Ding2020}.
+We selected our AGN sample in a well-defined window based on the \mbh\ and Eddington ratio, as shown in Figure~1 in D20.
 As shown in that Figure, the \mbh\ are well below the knee of the BH mass distribution to avoid a strong selection bias.
@@
 %We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy.
-Moreover, 21/23 systems have \hst/ACS imaging data, which enables us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see METHODS and the descriptions in \blue{D20}).
+Moreover, 21/23 systems have \hst/ACS imaging data, which enables us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see METHODS and the descriptions in D20).
 
@@
 We implemented the {\sc photuils} tools to remove contamination due to background light from both the sky and the detector.
-A full detailed description of the \hst\ data analysis can be found in \blue{a companion paper (D20)}.
+A full detailed description of the \hst\ data analysis can be found in a companion paper (D20).
 
@@
 We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3 result to infer the host color.
-We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in \blue{D20}, from which we estimate the colors of the host to derive the rest frame R-band magnitude (\mr) and the stellar mass (\mstar)-to-light ratio.
+We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D20, from which we estimate the colors of the host to derive the rest frame R-band magnitude (\mr) and the stellar mass (\mstar)-to-light ratio.
 
@@
 The \mbii\ simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback.
-\blue{The large simulation volume enables the Fourier density modes on the largest scales to evolve independently;} the large dynamic range in mass and high spatial resolution meet the requirements to study individual galaxies.
+The large simulation volume enables the Fourier density modes on the largest scales to evolve independently; the large dynamic range in mass and high spatial resolution meet the requirements to study individual galaxies.
 While high-resolution N-body simulations can describe specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam.
@@
 A fraction~($5\%$) of the radiated energy couples to the surrounding gas as black hole~(or AGN) feedback ~\citep{2005Natur.433..604D}.
-\blue{Note that unlike some previous work, the accretion rate in \mbii\ follows the prescription in~\citet{Pelupessy2007} which does not use any artificial boost factor.} For the modeling of black hole mergers, two black holes are considered to be merged if their separation distance is within the spatial resolution of the simulation~(the SPH smoothing length), and their relative speeds are lower than the local sound speed of the medium.
+Note that unlike some previous work, the accretion rate in \mbii\ follows the prescription in~\citet{Pelupessy2007} which does not use any artificial boost factor.
+For the modeling of black hole mergers, two black holes are considered to be merged if their separation distance is within the spatial resolution of the simulation~(the SPH smoothing length), and their relative speeds are lower than the local sound speed of the medium.
 
@@
 We manually change the slope value by its uncertainty level and find that the corresponding {\it observed} scatter barely changes ($<1\%$), meaning that the inferred scatter weakly depends on the fixed slope.
-\blue{To understand how much of the scatter derives from random noise, we measure the scatter of \mbii\ without injecting any noise in the data.
+To understand how much of the scatter derives from random noise, we measure the scatter of \mbii\ without injecting any noise in the data.
 Adopting the same selecting window and using the linear regression approach, we estimate the scatter value as $\sim0.1$~dex.
-Note that this $\sim0.1$~dex scatter level is also controlled by our selection window, and thus it should not be considered as the intrinsic scatter of the overall sample.} In this particular work, we simply apply a common standard method (i.e., consideration of the measured residual in \mstar) to achieve a direct comparison between different samples.
+Note that this $\sim0.1$~dex scatter level is also controlled by our selection window, and thus it should not be considered as the intrinsic scatter of the overall sample.
+In this particular work, we simply apply a common standard method (i.e., consideration of the measured residual in \mstar) to achieve a direct comparison between different samples.
 We perform the Kolmogorov-Smirnov (KS) test of the scatter distribution between observed and \mbii\ sample and infer the p-value as $\sim0.1$.
@@
 The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the standard deviation of the residual.
-\blue{The background cloud (in light brown/grey) shows the simulated number density, as Figure~\ref{fig:selectfunc}.} By fixing the slope to match the simulated data, the orange color shows the result for the observed data set.
+The background cloud (in light brown/grey) shows the simulated number density, as Figure~\ref{fig:selectfunc}.
+By fixing the slope to match the simulated data, the orange color shows the result for the observed data set.
 The grey cells in the background show the full \mbii\ simulated SMBHs.
@@
 However, the scatter of the \sam\ model is significantly larger ($\sim0.7$~dex) than observed (this is the total scatter accounting for the intrinsic scatter in the \sam\ distribution, observational uncertainties, and selection effects).
-\blue{Even without injecting random noise to \sam\ data, we find that the scatter (considering selection effects) would be $\sim0.6$~dex.}
+Even without injecting random noise to \sam\ data, we find that the scatter (considering selection effects) would be $\sim0.6$~dex.
 
@@
 
-\blue{It is not straightforward to implementing new physical assumptions to \sam\  in order to solve the tension as discovered in the scatter. 
+It is not straightforward to implementing new physical assumptions to \sam\  in order to solve the tension as discovered in the scatter. 
 %In practice, if one adjust the physical parameters in the SAM model, the scatter would not be as a tunable output. 
@@
 Implementing ``ad-hoc'', i.e., completely phenomenological and parametrized laws for the accretion, would require a long and detailed exploration of the possible parameters and the impact of each choice not only on the observables connected to AGN, but also on the properties of the galaxy populations (e.g., colors, luminosity functions, etc.).
-In addition, such a new approach with massive efforts would possibly not provide deeper insights on the physical mechanisms driving the AGN-galaxy connection.}
+In addition, such a new approach with massive efforts would possibly not provide deeper insights on the physical mechanisms driving the AGN-galaxy connection.
 
@@
 
-\blue{Our sample of 32 AGN systems covers the range $1.2<z<1.7$.
+Our sample of 32 AGN systems covers the range $1.2<z<1.7$.
 In principle it would be interesting to consider the evolution trend of the mass relation within the redshift range and make comparisons with the simulation as a function of cosmic time.
 Unfortunately, the limited sample size and precision of the measurement are not sufficient to resolve the evolution within this redshift range (see Figure~8 in D20).
-Thus, we only consider the sample with a single redshift bin at $z\sim1.5$ to compare with the simulations and the local measurements.}
+Thus, we only consider the sample with a single redshift bin at $z\sim1.5$ to compare with the simulations and the local measurements.
 

### 2020-09-28 py_tools/mask_objects.py
Last updates

@@ -108,8 +108,6 @@ def mask_obj(img, snr=3.0, exp_sz= 1.2, plt_show = True):
     dis_sq = [np.sqrt((apertures[i].positions[0][0]-center_img)**2+(apertures[i].positions[0][1]-center_img)**2) for i in range(len(apertures))]
     dis_sq = np.asarray(dis_sq)
     c_index= np.where(dis_sq == dis_sq.min())[0][0]
-    #from astropy.visualization.mpl_normalize import ImageNormalize
-    #norm = ImageNormalize(stretch=SqrtStretch())
     fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(12.5, 10))
     ax1.imshow(img, origin='lower', cmap=my_cmap, norm=LogNorm(), vmin=vmin, vmax=vmax)
     ax1.set_title('Data')
